### 2025-04-08 01_tidying_data.qmd
Update before optimising

---
title: "Tidying data"
format: html
editor: visual
---

Setup

```{r}

library(tidyverse)
library(here)
library(terra)
library(qs)

#model functions
source("src/dir.R")
source("src/model_functions.R")

#species of interest

species <- c("atlantic_salmon", 
             "general_salmonid", 
             "european_seabass", 
             "gilthead_seabream", 
             "large_yellow_croaker", 
             "japanese_seabass",
             "japanese_amberjack",
             "general_grouper",
             "pompano",
             "milkfish")

source(here("src/spatial_templates.R"))

```

Make repo structure

```{r}

create_repo(this_path = here())

```

Make input and output folder structure for species of interest

```{r}

#deploy data folder structure for species

map(.x = species, .f = create_species_folders)

```

Pull in mariculture locations data from Clawson et al 2022 and save the species groups of interest

```{r}

farm_locations <- read.csv(file.path(rdsi_dir, "raw_data/aquaculture-locations/all_marine_aquaculture_farms_sources_final.csv")) |> 
  filter(species_group %in% c("Salmonidae fish", "General marine fish"))

qsave(x = farm_locations, file = "data/_general_data/farm_locations/locations.qs")

```

Modify Feed characterisation and save to all species forcings

```{r}

#import food characterisation data - this is calculated in an independent google drive document

diet = "reference"

Food_charactisation_list <- 
  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
  select(-c(5)) |> 
  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
  group_by(species) |> 
  group_split()

map(.x = Food_charactisation_list, .f = \(this_species_food){

  this_species <- this_species_food$species |> unique()

  this_species_food_df <- 
    this_species_food |> 
    relocate(prop, .before = "nutrient") |> 
    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
    mutate(prop = as.double(prop)) |> 
    select(-species)

  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")

})

#now repeat for future feed

diet = "future"

Food_charactisation_list <- 
  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
  group_by(species) |> 
  group_split()

map(.x = Food_charactisation_list, .f = \(this_species_food){

  this_species <- this_species_food$species |> unique()

  this_species_food_df <- 
    this_species_food |> 
    relocate(prop, .before = "nutrient") |> 
    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
    mutate(prop = as.double(prop)) |> 
    select(-species)

  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")

})

#now repeat for past feed

diet = "past"

Food_charactisation_list <- 
  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
  group_by(species) |> 
  group_split()

map(.x = Food_charactisation_list, .f = \(this_species_food){

  this_species <- this_species_food$species |> unique()

  this_species_food_df <- 
    this_species_food |> 
    relocate(prop, .before = "nutrient") |> 
    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
    mutate(prop = as.double(prop)) |> 
    select(-species)

  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")

})

```

Daily SST data from NASA - GHRSST Level 4 MUR 0.25deg Global Foundation Sea Surface Temperature Analysis

```{r}

nasa_dir <- "/mnt/rdsi/raw_data/NASA/GHRSST_L4_MUR_0.25_SST/"

#rename the NASA files

#SST_files <- list.files(file.path(rdsi_dir, "raw_data/NASA/GHRSST_L4_MUR_0.25_SST"), full.names = FALSE, pattern = ".nc")

# map(SST_files, \(this_file){
#   file.rename(from = file.path(nasa_dir, this_file), to = file.path(nasa_dir, sub('^(.{4})(.*)$', '\\1_\\2',  this_file)))
# })

SST_files <- list.files(file.path(rdsi_dir, "raw_data/NASA/GHRSST_L4_MUR_0.25_SST"), full.names = TRUE, pattern = ".nc")

# this_file <- SST_files[[1]]
# 
# this_year=2013

#initialise lists for each year

years <- c(2010:2019)
year_lists <- vector(mode ="list", length = length(years))

# Add annual files to a list of files for each year

for(y in 1:length(years)){

  this_year <- years[y]

  this_years_files <- SST_files[grep(paste0(this_year, "_"), SST_files)]

  this_years_files <- this_years_files[!grepl(paste0(this_year, "_0229"), this_years_files)]

  year_lists[[y]] <- this_years_files

}

# Extract the daily files for each year and rasterize in a stack

days <- c(1:365)

this_day <- days[1]

rast_list = vector(mode = "list", length = length(days))

map(days, \(this_day){

  this_days_file_list <- sapply(year_lists, "[[", this_day)

  message("SST layer for Day ", this_day)

  this_day_stack <- rast(this_days_file_list, subds = "analysed_sst")

  this_day_mean_rast <- app(this_day_stack, "mean", na.rm=TRUE)-273.15

  writeRaster(this_day_mean_rast, filename = sprintf(here("data/_general_data/SST/SST_rasters/sst_nasa_mur_L4_0.25_mean2010-2019_day_%s.tif"), this_day))

})

#now gapfill the saved rasters

raw_SST_files <- list.files("data/_general_data/SST/SST_rasters/", full.names = TRUE)

#test function
#this_file <- raw_SST_files[[1]]

map(.x = raw_SST_files, .f = \(this_file){

  saveName <-  basename(this_file)

  message("Gapfilling ", saveName)

  this_rast <- rast(this_file)

  this_gf_rast <- focal(this_rast, w=7, fun = "mean", na.policy = "only")

  writeRaster(this_gf_rast, filename = sprintf("data/_general_data/SST/SST_gf_rasters/%s", saveName))

})

```

Pull in spp vulnerability to eutrophication data - save to salmon folder

```{r}

vuln_scores <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv")) |> 
  select(vuln_gf_id, eutrophication_nutrient_pollution)

vuln_sd <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_sd.csv")) |> 
  select(vuln_gf_id, eutrophication_nutrient_pollution) |> rename(sd=eutrophication_nutrient_pollution)

vuln_tx <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_tx.csv"))

full_vuln_df <- 
  vuln_scores |> 
  left_join(vuln_sd) |> 
  left_join(vuln_tx)

qsave(x = full_vuln_df, file = here("data/_general_data/species_layers/vulnerabilities/marine_spp_vulnerabilities_eutrophication.qs"))

```

Pull in spp distribution data from Aquamaps

```{r}

aquamaps_0.5d <- data.table::fread(file.path(rdsi_data_dir, "aquamaps/aquamaps_0.6_depth_prepped.csv"))

#all cells have an id. These id's can be used to isolate only the cells of relevance for the salmon farming locations.
filter(aquamaps_0.5d, is.na(cell_id))

#save to project
qsave(x = aquamaps_0.5d, file = here("data/_general_data/species_layers/distribution/aquamaps_0.5d.qs"))

```

### 2025-04-08 03_assessing_species_potential.qmd
Update before optimising

---
title: "Assessing species potential"
format: html
editor: source
---

Set up

```{r setup}
library(tidyverse)
library(here)
library(janitor)
library(countrycode)
library(rnaturalearth)

source("src/dir.R")
```

Pull in FAO data for aquaculture production.

```{r}
aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))

(aquaculture_prod <- 
  aquaculture_raw |> 
  clean_names() |> 
  select(c(1:7, starts_with("x"))) |> 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
  mutate(year = gsub(pattern="x", replacement = "", year)) |> 
  filter(year %in% c(2015:2020)) |> 
  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) |> 
  summarise(production = sum(production)) |> 
    ungroup() |> 
     filter(environment_name=="Marine" & 
           !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                         "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
         !grepl("seaweeds" , asfis_species_name_3),
         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
     group_by(asfis_species_name_2) |> 
     summarise(production = mean(production)) |> 
  arrange(-production) |> 
    mutate(cum_prop = cumsum(production)/sum(production),
           prop = production/sum(production))
)

ggplot(aquaculture_prod |> slice(1:20))+
  aes(x = reorder(asfis_species_name_2, cum_prop), y = cum_prop)+
  geom_col(fill = "dodgerblue3")+
  theme_bw()+
  theme(text = element_text(size=8),
    axis.text.x = element_text(angle=45, hjust = 1))+
  labs(x = "", y = "Prop. global marine finfish aquaculture")

ggsave("explore/cottrell_explore/global_proportion_finfish.jpg", dpi = 600, width = 18, height = 12, units="cm")

#

(aquaculture_country_prod <- 
  aquaculture_raw |> 
  clean_names() |> 
  select(c(1:7, starts_with("x"))) |> 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
  mutate(year = gsub(pattern="x", replacement = "", year)) |> 
  filter(year %in% c(2015:2020)) |> 
  group_by(country_name, asfis_species_name_2, asfis_species_name_3, environment_name, year) |> 
  summarise(production = sum(production)) |> 
    ungroup() |> 
     filter(environment_name=="Marine" & 
           !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                         "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
         !grepl("seaweeds" , asfis_species_name_3),
         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
     group_by(country_name, asfis_species_name_2) |> 
     summarise(production = mean(production)) |> 
  arrange(-production) |> 
    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
    ungroup() |> 
    mutate(prop = production/sum(production)) |> 
    group_by(country_name) |> 
    nest() |> 
    mutate(country_production =  map(data, ~(sum(.$production)))) |> 
    unnest(cols = c(data, country_production)) |> 
    ungroup() |> 
    arrange(-country_production)
)

top_20_countries <- unique(aquaculture_country_prod$country_name)[1:20]
top_20_spp <- aquaculture_prod |> 
                  slice(1:20) |> 
                  pull(asfis_species_name_2) |> 
                  unique()

ggplot(aquaculture_country_prod |> 
         filter(country_name %in% top_20_countries & 
                  asfis_species_name_2 %in% top_20_spp) |> 
         mutate(asfis_species_name_2 = factor(asfis_species_name_2, levels = top_20_spp)))+
  aes(x = reorder(asfis_species_name_2, -prop), y = production, fill = country_name)+
  geom_col()+
  theme_bw()+
  theme(text = element_text(size=8),
    axis.text.x = element_text(angle=45, hjust = 1),
    legend.key.size = unit(0.4, "cm"))+
  labs(x = "", y = "Prop. global marine finfish aquaculture", fill = "")

ggsave("explore/cottrell_explore/global_proportion_finfish_by_country.jpg", dpi = 600, width = 18, height = 12, units="cm")

aquaculture_prod |> filter(grepl("rouper", asfis_species_name_2))
```

Species decided on:

| Common name | Scientific name |
|:----------------|:------------------------------------------------------|
| Atlantic salmon | Salmo salar |
| Other salmonids | Generalised multi-species model - incl. Oncorhynchus mykiss and Oncorhynchus kisutch (Coho) |
| European seabass | Dicentrarchus labrax |
| Gilthead seabream | Sparus aurata |
| Large Yellow Croaker | Larimichthys crocea |
| Japanese seabass | Lateolabrax japonicus |
| Japanese amberjack | Seriola quinqueradiata |
| Groupers | Generalised mutli-species model |
| Pompano | Trachinotus blochii |
| Milkfish | Chanos chanos |

### 2025-04-08 07_methods_and_supplementaries/07_methods_and_supplementaries.qmd
Update before optimising

---
title: "Model inner workings - for methods and supplementary sections"
author: Tormey Reimer
date: last-modified
bibliography: ["../resources/refs.bib", "../resources/manual-refs.bib"]
format: 
  html:
    theme: simplex
    css: ["../resources/extra.css"]
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 350px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em
  # pdf:
  #   papersize: a4
  #   linestretch: 1.15
  #   link-citations: true
  #   keep-tex: true
  #   template-partials:
  #     - "C:/Users/treimer/Documents/R-temp-files/local_to_global_mariculture_modelling/resources/title.tex"
  #   include-in-header:
  #     file: "C:/Users/treimer/Documents/R-temp-files/local_to_global_mariculture_modelling/resources/header_extra.tex"

filters:
  - acronyms

execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true

knitr: 
  opts_chunk:
    fig.align: center

editor: source
---

# Introduction

```{r setup}
#| include: false
#| cache: false
#| eval: true

packs <- unique(c('magrittr', 'dplyr', 'tidyr', 'stringr', 'ggplot2', 'here', 'ggpubr', 'patchwork', 'qs', 'arrow', 'targets', 'sf', 'terra', 'rnaturalearth', 'rnaturalearthdata', 'dtplyr', 'furrr', 'RColorBrewer', 'conflicted'))
pacman::p_load(char = packs)

conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)

source(here("src/spatial_templates.R"))
source(here("src/model_functions.R"))

# Sys.setenv(TAR_PROJECT = "project_main")
base_path <- file.path("C:", "Users", "treimer", "Documents", "R-temp-files", "local_to_global_mariculture_modelling")
targets_store <- file.path(base_path, "targets", "_targets_individual")
farm_IDs <- tar_read(farm_IDs, store = targets_store)
b1 <- sample(length(farm_IDs), 100, replace = F)
b2 <- b1 + length(farm_IDs)
b3 <- b2 + length(farm_IDs)
b <- c(b1, b2, b3)
```

# Temporary questions to answer:

-   Do the fish reach harvest size within a reasonable amount of time?
    -   If not, are they growing for the correct amount of time, starting at the correct weight?
-   Is their FCE/FCR reasonably close to experimental data?
-   Is their SGR reasonably close to experimental data?

# Model approach

# Water temp

```{r water-temp-data}
#| code-summary: Load and cache data to avoid spending a long time on it every render.

# This is the full idealised year (2 years?) of temperature data
sst <- file.path(base_path, "data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()

# This is the actual temperature curve for the farming period
farm_temp <- tar_read(example_individual, store = targets_store, branches = b1)
```

Originally, all salmon were transferred to grow-out cages (model began) on January 1st. This isn't particularly realistic. Now, all farms begin the modelling period in spring (1st of May in the northern hemisphere, 1st of October in the southern hemisphere).

```{r fig-water-temp}
#| fig-cap: Water temperature for the production period, starting at either DOY 121 (1st May, northern hemisphere) or DOY 274 (1st October, southern hemisphere).

farm_temp %>% 
  ggplot(aes(x = prod_days, y = water_temp, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(0, 550, 50)) +
  labs(x = "Day of production cycle", y = expression("Water temperature ("*degree*"C)"))
```

# Weight

```{r weight-related-data}
#| code-summary: Load and cache data to avoid spending a long time on it every render.

species_params <- tar_read(species_params, store = targets_store)
pop_params <- tar_read(pop_params, store = targets_store)
weight <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
SGR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
FCR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)

weight_smolt <- weight %>% 
  filter(prod_days == 152 & feed == "reference") %>% 
  group_by(feed) %>% 
  reframe(final_weight = mean(weight))
weight_ocean <- weight %>% 
  filter(prod_days == max(prod_days) & feed == "reference") %>% 
  group_by(feed) %>% 
  reframe(final_weight = mean(weight),
          final_wt_sd = sd(weight))
```

@fig-ref-weight shows the change in weight for 100 individuals grown at different farms. Within the first 5 months (post-smolt period) the fish grow from `r unname(pop_params['meanW'])`g to `r round(weight_smolt$final_weight, 1)`g, or approximately `r round(weight_smolt$final_weight/125, 1)`$\times$ their starting weight. By the end of the production cycle (730 days) the fish have grown to a mean of `r round(weight_ocean$final_weight, 1)` g with a SD of `r round(weight_ocean$final_wt_sd, 1)` g. 
<!-- This is not quite what's needed - I'm expecting individual weights to at least approximate the mean commercial weight of 5kg. -->

```{r fig-ref-weight}
#| fig-cap: Weight of single individuals grown at 100 random farms across the production period, starting at either DOY 121 (1st May, northern hemisphere) or DOY 274 (1st October, southern hemisphere).

weight %>% 
  mutate(feed == "reference") %>% 
  ggplot(aes(x = prod_days, y = weight, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  scale_y_continuous(breaks = seq(0, 7500, 500)) +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(0, 550, 150)) +
  labs(x = "Day of production cycle", y = "Individual weight (g)")
```

```{r fig-ref-SGR}
#| fig-cap: Specific growth rate of single individuals grown at 100 random farms across the production period, starting at either DOY 121 (1st May, northern hemisphere) or DOY 274 (1st October, southern hemisphere).

SGR %>% 
  mutate(feed == "reference") %>% 
  ggplot(aes(x = prod_days, y = SGR, colour = as.factor(farm_ID))) +
  geom_line(linewidth = 0.75) +
  scale_y_continuous(breaks = seq(0, 2.5, 0.25)) +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(0, 550, 50)) +
  labs(x = "Day of production cycle", y = expression("SGR"))
```

```{r fig-ref-FCR}
#| fig-cap: FCR of 25 random farms across the production period, starting at either DOY 121 (1st May) or DOY 274 (1st October).

FCR %>% 
  mutate(feed == "reference") %>% 
  filter(FCR < 50 & FCR > -50) %>% 
  group_by(prod_days) %>% 
  reframe(sd = sd(FCR),
          FCR = mean(FCR)) %>% 
  ggplot(aes(x = prod_days, y = FCR, ymin = FCR-sd, ymax = FCR+sd)) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(alpha = 0.25) +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = seq(0, 550, 50)) +
  labs(x = "Day of production cycle", y = expression("FCR"))
```

# General fish functions

@fig-functional-response-to-temperature shows the metabolic response of all salmon to temperature (affecting their relative metabolism), and @fig-feeding-rate-with-temperature shows how the salmons' feeding rate changes with temperature.

```{r fig-functional-response-to-temperature}
#| fig-cap: Metabolic response of all salmon to temperature within the model.

df <- data.frame(water_temp = seq(-5, 30, 0.25))
df$resp <- exp(species_params['pk']*df$water_temp)

df %>% 
  ggplot(aes(x = water_temp, y = resp)) +
  geom_line(linewidth = 0.75) +
  scale_y_continuous(breaks = seq(0,5,0.5)) +
  scale_x_continuous(breaks = seq(-10,35,5)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Temperature response") +
  theme_classic() +
  theme(text = element_text(colour = "black", family = "serif", size = 12))
```

$$
cat = \epsilon_{O_2} \times k_0 \times T_{resp} \times W^n \times \omega
$$

Relative feeding rate is temperature-dependent and calculated via:

$$
FR_{rel} = e^{b(T_w-T_{opt})} \times \bigg[\frac{T_{max}-T_w}{T_{max}-T_{opt}}\bigg]^{b(T_{max}-T_{opt})}
$$

where $T_{opt}$ is the optimum feeding temperature, $T_{max}$ is the maximum feeding temperature (lethal temperature), $T_w$ is the current water temperature, and $b$ is a species-specific shape coefficient.

```{r fig-feeding-rate-with-temperature}
#| fig-cap: Changes in salmons feeding rate with temperature. The dashed line shows the optimum feeding temperature for salmon while the dotted lines show the minimum and maximum feeding temperatures.

df <- data.frame(water_temp = seq(-5, 30, 0.25))
df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)

df %>% 
  ggplot(aes(x = water_temp, y = feeding)) +
  geom_line(linewidth = 0.75) +
  geom_vline(aes(xintercept = species_params["Toa"]), linetype = "dashed") +
  geom_vline(aes(xintercept = species_params["Taa"]), linetype = "dotted") +
  geom_vline(aes(xintercept = species_params["Tma"]), linetype = "dotted") +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative feeding rate") +
  theme_classic() +
  theme(text = element_text(colour = "black", family = "serif", size = 12))
```

# Feed data

```{r feed-raw-data}
#| code-summary: Load and cache data to avoid spending a long time on it every render.

feed_params_protein <- tar_read(feed_params_protein, store = targets_store)
feed_params_carbs <- tar_read(feed_params_carbs, store = targets_store)
feed_params_lipids <- tar_read(feed_params_lipids, store = targets_store)
```

Incorporated the individual digestibility of each ingredient and switched to tracking ingredients separately instead of feed – this unfortunately makes the model run slower but I think it will be worth it once the digestibility coefficients from the experiments are incorporated.

```{r feed-data}

ref_feed <- list(
    feed_params_protein[[1]] %>% 
      mutate(feed = "reference", type = "protein") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_carbs[[1]] %>% 
      mutate(feed = "reference", type = "carb") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_lipids[[1]] %>% 
      mutate(feed = "reference", type = "lipid") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest))
) %>% bind_rows()
past_feed <- list(
    feed_params_protein[[2]] %>% 
      mutate(feed = "past", type = "protein") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_carbs[[2]] %>% 
      mutate(feed = "past", type = "carb") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_lipids[[2]] %>% 
      mutate(feed = "past", type = "lipid") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest))
) %>% bind_rows()
fut_feed <- list(
    feed_params_protein[[3]] %>% 
      mutate(feed = "future", type = "protein") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_carbs[[3]] %>% 
      mutate(feed = "future", type = "carb") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest)),
  feed_params_lipids[[3]] %>% 
      mutate(feed = "future", type = "lipid") %>% group_by(feed, type) %>% 
      reframe(proportion = sum(proportion),
              macro = sum(macro),
              digest = sum(digest))
) %>% bind_rows()

feeds <- rbind(ref_feed, past_feed, fut_feed)
```

```{r fig-compare-feeds-composition}
#| fig-cap: Feed composition

```

```{r fig-compare-feeds-digestibility}

```

# Individual runs

I set up some “example fish” to speed up future model adjustments – basically fish that are the average of their whole farm, easier than running 5000 fish per farm while I’m making changes.

## Food provided vs food eaten

```{r food-raw-data}
#| code-summary: Load and cache data to avoid spending a long time on it every render.

#c(b1, b2, b3))
ing_pot <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
ing_act <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
food_prov <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
```

Within the model, salmon have a maximum ingestion potential (based on their weight and individualised feeding rate). The actual food ingested is 97% of their ingestion potential (food encounter efficiency) or the total food provided, whichever is less. @fig-food-prov-theoretical shows an example of how food provided scales with potential individual ingestion.

```{r fig-food-prov-theoretical}
#| fig-cap: Example of food provided based on potential ingestion (where feeding rate ranges from 0 to 1). This curve is constructed with a single fish of mean starting weight (125 g) and average maximum ingestion rate (0.035). The dashed line shows food provision == potential ingestion.

df <- data.frame(rel_feeding = seq(0,1,0.01)) %>% 
mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * rel_feeding,
       food_prov = NA)
for (i in 1:nrow(df)) {
  df$food_prov[i] <- food_prov_rate(rel_feeding = df$rel_feeding[i], ing_pot = df$ing_pot[i], 
                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
}
lin <- seq(0,max(df$ing_pot),length.out=101)

df %>% 
  ggplot(aes(x = ing_pot, y = food_prov)) +
  geom_line(linewidth = 0.75) +
  geom_line(aes(x = lin, y = lin), linetype = "dashed") +
  theme_classic() +
  scale_x_continuous(breaks = seq(0,1.5, 0.25), limits = c(0,max(df$food_prov))) +
  scale_y_continuous(breaks = seq(0,1.5, 0.25)) +
  labs(x = "Potential ingestion (g)", y = "Food provided (g)")
```

```{r feed-nums}

prov <- merge(ing_pot, ing_act, by = c("farm_ID", "feed", "days", "prod_days")) %>% 
  merge(food_prov, by = c("farm_ID", "feed", "days", "prod_days")) %>% 
  mutate(uneaten = food_prov - ing_act,
         uneaten_perc = uneaten/food_prov) %>% 
  select(-c(food_prov, ing_act))

# Therefore, uneaten feed can be quite high (up to \~30%) when relative feeding is $\leq$10%. But generally, the median amount of uneaten food is `r round(100*median(prov$uneaten_perc), 1)`% (@fig-uneaten-feed).
```

```{r fig-uneaten-feed}
#| fig-cap: Difference between food provided and actual ingestion (i.e. total food ingestion efficiency) for 100 random farms.

prov %>% 
  ggplot(aes(x = ing_pot, y = 100*uneaten_perc, colour = feed)) +
  geom_point() +
  theme_classic() +
  scale_colour_brewer(palette = "Set1") +
  theme_classic() +
  labs(x = "Potential feed ingestion (g)", y = "Uneaten food (% of provided)")
```

# Parameters for Atlantic salmon

```{r salmon params}
#| code-summary: lsdkjfk
#| eval: true

params <- tar_read(sens_all_params, store = targets_store)
pnames <- names(params)
```

| Parameter | Value | Units | Description | Reference | Comment | 
|:-------:|:----:|:----:|-------------------|-------------|---------------------------|
| $\alpha$ | `r unname(params['alpha'])` | - | Feeding catabolism coefficient | @broekhuizen_modelling_1994 | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) | 
| $\epsilon_{P}$ | `r unname(params['epsprot'])` | J g protein-1 | Energy content of protein | @baldan_r_2018 | | 
| $\epsilon_{L}$ | `r unname(params['epslip'])` | J g lipid-1 | Energy content of lipid | @baldan_r_2018 | | 
| $\epsilon_{C}$ | `r unname(params['epscarb'])` | J g carbohydrate-1 | Energy content of carbohydrate | @baldan_r_2018 | | 
| $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2-1 | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 | | 
| $pk$ | `r unname(params['pk'])` | d-1 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 | | 
| $k_0$ | `r unname(params['k0'])` | degree C-1 | Fasting catabolism at 0 Celsius degree | @macnaughton_using_2019 | | 
| $m$ | `r unname(params['m'])` | - | Weight exponent for the anabolism | @broekhuizen_modelling_1994 | *Salmo trutta* (temps: 8–13$^{\circ}$C) | 
| $n$ | `r unname(params['n'])` | - | Weight exponent for the catabolism | @baldan_r_2018 | | 
| $\beta C$ | `r unname(params['betac'])` | - | Shape coefficient for the feeding function | @jonsson_thermal_2001 | Fish size range: 2.25$\pm$0.49 – 11.5$\pm$5.29 g, temperature ranges: 5–24$\^{\circ}$C. Coefficent for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) | 
| $T_{max}$ | `r unname(params['Tma'])` | C | Maximum lethal temperature | @poletto_unusual_2017 | Juvenile Chinook salmon (19.8$\pm$0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) | 
| $T_{opt}$ | `r unname(params['Toa'])` | C | Optimal temperature | @jonsson_thermal_2001 | Fish size range: 2.25$\pm$0.49 – 11.5$\pm$5.29 g, temperature ranges: 5–24$^{^\circ}$C.
Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0$\pm$14.6 g, temps: 6, 10, 14, 18${\circ}$C | 
| $T_{min}$ | `r unname(params['Taa'])` | C | Lowest feeding temperature | @vadboncoeur_lowering_2023 | Fish essentially stop feeding when below 2$^{\circ}$C | | $\omega$ | `r unname(params['omega'])` | g O2 / g | Oxygen consumption:weight loss ratio | @baldan_r_2018 | Calibrated value | 
| $a$ | `r unname(params['a'])` | J g tissue-1 | Energy content of fish tissue | @van_tien_development_2016 | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 | 
| $k$ | `r unname(params['k'])` | - | Weight exponent for energy content | @van_tien_development_2016 | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 | 
| $eff$ | `r unname(params['eff'])` | - | Food ingestion efficiency | @uglem_does_2020 | Range: 95-97% ingestion efficiency | 
| $\overline{W}$ | `r unname(params['meanW'])` | g | Dry weight mean | @dempsey_estimating_2023 | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers | 
| $\Delta{W}$ | `r unname(params['deltaW'])` | g | Dry weight standard deviation | @dempsey_estimating_2023 | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers | 
| $Wlb$ | `r unname(params['Wlb'])` | g | Dry weight lower bound | Reference | | 
| $\overline{I_{max}}$ | `r unname(params['meanImax'])` | g g-1 fish day-1 | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) | | 
| $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g-1 fish day-1 | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) | | 
| $mort$ | `r unname(params['mortmyt'])` | d-1 | Natural mortality rate | @tvete_towards_2023 | |
: Params

## Sensitivity

In the following plots, a value > 0 indicates that increasing that parameter increases the output variable while a negative value indicates that increasing the parameter decreases the variable. The sensitivity follows a power relationship, such that output$_1$ $\propto$ output$_0^{S}$.

```{r param sensitivity data}
#| code-summary: Load sensitivity data

sens_wt <- file.path("..", "data", "atlantic_salmon", "data_products", "weight_parameter_sensitivity.parquet") %>% 
  read_parquet() %>% 
  mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
# sens_dw <- file.path("data", "atlantic_salmon", "data_products", "dw_parameter_sensitivity.parquet") %>% 
#   read_parquet() %>% 
#   mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
# sens_excr <- file.path("data", "atlantic_salmon", "data_products", "excreted_parameter_sensitivity.parquet") %>% 
#   read_parquet() %>% 
#   mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
# sens_uneat <- file.path("data", "atlantic_salmon", "data_products", "uneaten_parameter_sensitivity.parquet") %>% 
#   read_parquet() %>% 
#   mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
```

Looking at @fig-param-sens-weight:

* The most sensitive parameter by far is $m$ the weight exponent for anabolism, followed closely by $n$ the weight exponent for catabolism
* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon. There must be more up-to-date measurements for Atlantic salmon in particular.

```{r fig-param-sens-weight}
#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on individual fish weight at the end of the production period.

(
  p_sens <- sens_wt %>% 
    ggplot(aes(x = adj_param, y = sens, ymin = sens-sd, ymax = sens+sd)) +
    geom_col(alpha = 0.35, colour = "black") +
    geom_errorbar(width = 0.3) +
    geom_hline(aes(yintercept = 0), linetype = "dashed") +
    scale_y_continuous(breaks = seq(-20,30,5)) +
    labs(x = "Adjusted parameter", y = "Sensitivity") +
    theme_classic() + theme(legend.position = "none", 
          strip.text = element_blank(), 
          aspect.ratio = 0.8,
          text = element_text(size = 12)) +
    coord_flip()
 )
```

```{r fig-param-sens-dw}
#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on the mean daily weight change of individual fish across the entire production period.
#| eval: false

p_sens %+% sens_dw
```

```{r fig-param-sens-excr}
#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on the total excretion (g protein, carbs and lipids) of an individual fish across the entire production period.
#| eval: false

p_sens %+% sens_excr
```

```{r fig-param-sens-uneat}
#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on the total uneaten feed (g) of an individual fish across the entire production period.
#| eval: false

p_sens %+% sens_uneat
```

# References

### 2025-04-08 08_manuscript/08_manuscript.qmd
Update before optimising

---
title: "Local to global N input modelling"
# Author roles: "writing – original draft", "writing – review & editing", "formal analysis", "funding acquisition", "conceptualization", "data curation", "investigation", "methodology", "project administration", "resources", "software", "supervision", "validation", "visualization"
author:
  - name: Tormey Reimer
    orcid: 0000-0002-5983-2798
    corresponding: true
    email: tormey.reimer@utas.edu.au
    role: 
      - methodology: supporting
      - analysis: lead
      - writing: lead
    affil-id: [1,2]
  - name: Richard S. Cottrell
    orcid: 0000-0002-6499-7503
    corresponding: false
    roles: 
      - conceptualization: lead
      - methodology: lead
      - writing: supporting
    # affil-id: [1,2]
  - name: Alexandra Johne
    orcid: 0000-0002-2816-7983
    corresponding: false
    roles: 
      - methodology: supporting
    affil-id: 3
  - name: Sowdamini Sesha Prasad
    # orcid: 
    corresponding: false
    roles: 
      - methodology: supporting
    # affil-id: [3,2]
  - name: Marceau Cormery
    # orcid: 
    corresponding: false
    roles: 
      - methodology: supporting
    # affil-id: [3,2]
  - name: Gage Clawson
    # orcid: 
    corresponding: false
    roles: 
      - methodology: supporting
    # affil-id: [3,2]
  - name: Scott Hadley
    # orcid: 
    corresponding: false
    roles: 
      - methodology: supporting
    # affil-id: [3,2]
  - name: Helen Hamilton
    # orcid: 
    corresponding: false
    roles: 
      - conceptualization: supporting
    # affil-id: [3,2]
  - name: Benjamin S. Halpern
    # orcid: 
    corresponding: false
    roles: 
      - conceptualization: supporting
    # affil-id: [3,2]
  - name: Catriona Macleod
    # orcid: 
    corresponding: false
    roles: 
      - conceptualization: supporting
    # affil-id: [3,2]
  - name: Camille White
    # orcid: 
    corresponding: false
    roles: 
      - conceptualization: supporting
    # affil-id: [3,2]
  - name: Julia L. Blanchard
    # orcid: 
    corresponding: false
    roles: 
      - conceptualization: supporting
      - methodology: supporting
      - analysis: supporting
      - editing: supporting
    # affil-id: [3,2]

affiliations:
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Fisheries & Aquaculture
    address: 29 Nubeena Crescent
    city: Taroona
    region: TAS
    country: Australia
    postal-code: 7053
    url: https://www.imas.utas.edu.au/
  - id: 2
    name: Centre for Marine Socioecology
    url: https://marinesocioecology.org/
  - id: 1
    name: Institute for Marine and Antarctic Studies
    group: Ecology & Biodiversity
    # address: 29 Nubeena Crescent
    # city: Taroona
    # region: TAS
    # country: Australia
    # postal-code: 7053
    url: https://www.imas.utas.edu.au/
  # - id: 3
  #   name: Heriott-Watt University, Institute for Life and Earth Sciences
  #   department: School of Energy, Geoscience, Infrastructure and Society
  #   address: Franklin Road
  #   city: Stromness
  #   region: Orkney
  #   country: United Kingdom
  #   postal-code: KW16 3AN
  #   url: https://www.hw.ac.uk/
# keywords:
#   - keyword
#   - keyword
# abstract: |
#   Any new aquaculture venture...
# plain-language-summary: |
#   Plain language summary goes here....
# key-points:
#   - Point 1
#   - Point 2
bibliography: ["../resources/refs.bib", "../resources/manual-refs.bib"]

format: 
  html:
    theme: simplex
    css: ["../resources/extra.css"]
    code-fold: true
    code-overflow: wrap
    toc: true
    toc-expand: true
    toc-location: left
    lang: en-GB
    grid:
      sidebar-width: 350px
      body-width: 1200px
      margin-width: 250px
      gutter-width: 2em
  # pdf:
  #   papersize: a4
  #   linestretch: 1.15
  #   link-citations: true
  #   keep-tex: true
  #   template-partials:
  #     - "../resources/title.tex"
  #   include-in-header:
  #     file: "../resources/header_extra.tex"

filters:
  - acronyms

execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true

knitr: 
  opts_chunk:
    fig.align: center

editor: source
---

```{r setup}
#| include: false
#| cache: false
#| eval: true

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(here)
library(ggpubr)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(dtplyr)
library(furrr)
library(RColorBrewer)
library(purrr)
library(future)
library(readxl)
library(units)
library(conflicted)
library(lubridate)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()
```

# Introduction

Aquaculture is now the dominant form of aquatic animal food (herein ‘seafood’) production and is expected to be the primary way we meet future seafood demand. Freshwater systems will likely continue to provide the majority of farmed seafood but marine aquaculture is also poised to expand substantially in numerous areas. Farmed marine fish and invertebrates are produced near exclusively in coastal waters, and nearly three quarters of this production is dependent on human-made feeds. Nearshore locations and feed inputs are necessary to maintain profitable and productive farming operations but coastal aquaculture generates a number of challenges. In the crowded coastal zone, aquaculture operations can conflict with other stakeholder uses such as recreation, fishing, renewable energy, transport, and tourism. 
And while farming marine fish typically generates a far smaller nutrient footprint than livestock farming, the overt nature of aquaculture in nearshore regions and evidence of  localised nutrient impacts around fish farms remains a primary public and scientific concern. Identifying strategies that reduce ecosystem impacts from fish farm waste therefore represents an important goal for improving marine aquaculture sustainability and maintaining the sector’s social licence to operate.

Aquaculture feeds represent an important lever for reducing nutrient waste impacts around fish farms. Like all farmed animals, fish and invertebrates must digest the nutrients contained in feeds before they can be used for growth. Any nutrients left undigested are egested as solid waste, and dissolved wastes are excreted as metabolic waste products. Further, some feed inevitably remains uneaten and is lost to the surrounding ecosystem. Particulate organic matter (both feed and faeces) that settles can simplify benthic communities as the oxygen demand from its decomposition drives the production of sulphides that kill less mobile faunal, encouraging a lower diversity of opportunistic scavengers and the growth of bacterial mats (e.g., Beggiatoa spp). Thus, the chemical composition of the ingredients used in aquaculture feeds and their digestibility for the farmed species has significant implications for the nature and reactivity of the waste generate by marine aquaculture.

Firstly the overall volume of nutrient waste is dictated by the nature and intensity of production, that is the farm size, the density of farmed animals and the feed requirements and efficiency of the species grown. SecondlDeposition of waste is heavily influenced by water depth and current speed at the farming site. Once

As farmed fish and invertebrates are fed, whatever

Nutand its impact on marine ecosystems is influenced by many factors. 
* Farm size
* Depth
* Current speed
* Benthic impact - sediment type/faunal assemblages/wider marine community
* High turnover environments - nitrogen enriched areas
* Feed influences all of these things

The primary source of organic waste from fed aquaculture production comes from the excretion and faeces of the farmed animals and through uneaten feed that dissolves in the water column or settles on the benthos. The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals.

## P2

* Waste from aquaculture farms and it’s impact is influenced by many things but the composition of feeds plays a central role.
* Waste from aquaculture farms has multiple sources. 
* The primary source of organic waste comes from the faeces and excretion of the fish or invertebrates.
* Uneaten feed produced another key source.
* The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals
* Many marine fish are naturally carnivorous so diets used to be high in fishmeal and oil but increasing fishmeal and oil prices along with concerns over the sustainability of marine ingredients have led to a reduction in their use across multiple farmed taxa
* In lieu of fishmeal and oil, many plant-based ingredients such as soy protein concentrate, canola oil, and wheat gluten have replaced them. 
* Changes in feed composition influences the digestibility of the nutrients held in each feed and can alter the composition of waste.
* Of particular concern are changes (increases) to the presence of reactive nitrogen and phosphorus in coastal waters that could have an effect on eutrophication.

## P3

* Whether or not nutrients lead to eutrophication depends on the sensitivity of the receiving environment
* Ecosystems that are already enriched through natural processes and whose biota is well adapted to substantial fluxes in available nutrients (e.g. upwelling zones, dynamic coastal communities) may be less sensitive while oligotrophic ecosystem are likely to see considerable changes under nutrient enrichment scenarios.
* To understand the impact of aquaculture waste under present day or future scenarios we need to quantify the volume, nature, and location of mariculture waste and determine the sensitivity of the receiving environments to that waste. Yet only recent estimates even give us the estimated location of marine farms let alone the volume of nature of the waste produced.
To address this gap, we use existing maps of mariculture location with a bioenergtic model

# Methods

## Farm temperature forcings

## Model and approach

We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus. 
The model simulates growth at an individual level, calculating the change in individual weight through time using:

$$
\frac{dw}{dt} = \frac{A-C}{\epsilon}
$$

Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population. Size differences were achieved through different initial starting weights and ingestion rates for different finfish species. All individuals have a fixed mortality rate to simulate stocking and harvesting.

* Farms with mean temperature < 4$^\circ$ were excluded

## Parameterisation for Atlantic salmon

```{r salmon params}
#| code-summary: Get parameter and sensitivity data
#| eval: true

pop_params <- tar_read(pop_params, store = "../05_targets_farm")
species_params <- tar_read(species_params, store = "../05_targets_farm")
params <- c(pop_params, species_params)
pnames <- names(params)
sens_excr <- file.path("..", "data", "atlantic_salmon", "data_products", "excreted_parameter_sensitivity.parquet") %>%
  read_parquet() %>%
  mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
```

Table @tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.

| Parameter | Value | Units | Description | Reference | 
|:-------:|:----:|:----:|----------------|-------------------------|
| $\alpha$ | `r unname(params['alpha'])` | - | Feeding catabolism coefficient | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| $\epsilon_{P}$ | `r unname(params['epsprot'])` | J g protein-1 | Energy content of protein | @baldan_r_2018 | 
| $\epsilon_{L}$ | `r unname(params['epslip'])` | J g lipid-1 | Energy content of lipid | @baldan_r_2018 |
| $\epsilon_{C}$ | `r unname(params['epscarb'])` | J g carbohydrate-1 | Energy content of carbohydrate | @baldan_r_2018 |
| $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2-1 | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
| $pk$ | `r unname(params['pk'])` | d-1 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
| $k_0$ | `r unname(params['k0'])` | degree C-1 | Fasting catabolism at 0 Celsius degree | @macnaughton_using_2019 |
| $m$ | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
| $n$ | `r unname(params['n'])` | - | Weight exponent for catabolism | @baldan_r_2018 |
| $\beta C$ | `r unname(params['betac'])` | - | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C. Coefficent for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] | 
| $T_{max}$ | `r unname(params['Tma'])` | C | Maximum lethal temperature | Juvenile Chinook salmon (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
| $T_{opt}$ | `r unname(params['Toa'])` | C | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001]. Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0 $\pm$ 14.6 g, temps: 6, 10, 14, 18${\circ}$C | 
| $T_{min}$ | `r unname(params['Taa'])` | C | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] | 
| $\omega$ | `r unname(params['omega'])` | g O2 / g | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
| $a$ | `r unname(params['a'])` | J g tissue-1 | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $k$ | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
| $eff$ | `r unname(params['eff'])` | - | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
| $\overline{W}$ | `r unname(params['meanW'])` | g | Dry weight mean | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] | 
| $\Delta{W}$ | `r unname(params['deltaW'])` | g | Dry weight standard deviation | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] | 
| $\overline{I_{max}}$ | `r unname(params['meanImax'])` | g g-1 fish day-1 | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
| $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g-1 fish day-1 | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
| $mort$ | `r unname(params['mortmyt'])` | d-1 | Natural mortality rate | @tvete_towards_2023 |
: Growth parameters for Atlantic salmon {#tbl-params}

Looking at @fig-param-sens-weight:

* The most sensitive parameter by far is $m$ the weight exponent for anabolism, followed closely by $n$ the weight exponent for catabolism
* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon. There must be more up-to-date measurements for Atlantic salmon in particular.

```{r fig-param-sens-weight}
#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on total farm excreted nutrients over the whole production period.

sens_excr %>% 
  ggplot(aes(x = adj_param, y = sens, ymin = sens-sd, ymax = sens+sd)) +
  geom_col(alpha = 0.35, colour = "black") +
  geom_errorbar(width = 0.3) +
  geom_hline(aes(yintercept = 0), linetype = "dashed") +
  scale_y_continuous(breaks = seq(-20,30,5)) +
  labs(x = "Adjusted parameter", y = "Sensitivity") +
  theme_classic() + theme(legend.position = "none", 
        strip.text = element_blank(), 
        aspect.ratio = 0.8,
        text = element_text(size = 12)) +
  coord_flip()
```

## Population and biomass estimates

New method is to take the average predicted individual harvest size for each farm, then working backwards with the standard mortality rate to generate a population for each farm that will produce the correct tonnage for each farm. @fig-harvest-size shows the  average individual harvest size at each farm as predicted by the fish-growth model, which was used to create the population inputs for the farm-level growth curves.

```{r fig-harvest-size}
#| fig-cap: Frequency distribution of harvest sizes across global farms, as predicted by the fish growth model

farm_harvest_size <- tar_read(farm_harvest_size, store = "../04_targets_individual")

ggplot(farm_harvest_size, aes(x = weight/1000)) + 
  geom_histogram(colour = "black", fill = "salmon", alpha = 0.5) + 
  theme_classic() + 
  scale_x_continuous(breaks = seq(0, 8, 1), limits = c(1.25, 7.75)) + 
  labs(y = "Frequency", x = "Individual weight (kg)")
```

This means that the population estimates aren't actual fish numbers, they're just a method that allows each farm location to approximate of the correct tonnage produced while to allowing comparisons between the different feeds.

## Species vulnerability layers

# Statistical analysis & code availability

All analysis was conducted in R version `r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

# References

### 2025-04-08 XX_species_layers.qmd
Update before optimising

---
title: "05_species_layers"
format: html
editor: source
---

```{r}
library(tidyverse)
library(here)
library(janitor)
library(terra)
library(sf)
library(qs)
library(countrycode)
library(terra)
library(stars)
library(furrr)
library(rnaturalearth)

source("src/dir.R")
source("src/spatial_templates.R")
```

Pull in the species vulnerability data

```{r}
full_vuln_df <- qread(file = here("data/_general_data/species_layers/vulnerabilities/marine_spp_vulnerabilities_eutrophication.qs"))

```

Determine which cells will be relevant for species layers to reduce the size necessary for aquamaps data.

```{r}

this_species <- "atlantic_salmon"

reference_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/reference/nitrogen_summary.qs"))

reference_feed_total_N <- reference_point_df |> dplyr::select(geometry, total_N_mean)

#salmon_locations_transform <- st_transform(salmon_locations, crs = "ESRI:54016")

salmon_farm_rast <- rasterize(x = reference_feed_total_N, y = base_rast, field = "total_N_mean", fun = sum)

salmon_farm_nutrient_df <- terra::as.data.frame(x= salmon_farm_rast, xy = TRUE) |> 
  rename(nitrogen = sum)

#cell_ids_for_farms <- salmon_farm_df$cell_id |> unique()

```

#Now reproject all species rasters into the equal area (Gall) projection and then aggregate them again.

```{r}
aquamaps_0.5 <- qread(here("data/_general_data/species_layers/distribution/aquamaps_0.5d.qs"))

aquamaps_spp <- unique(aquamaps_0.5$species)

# aquamaps_vuln_df <- 
#   aquamaps_0.5 |> left_join(full_vuln_df)

rm(aquamaps_0.5)

#check for no data
aquamaps_vuln_df |> filter(is.na(eutrophication_nutrient_pollution)) |> pull(species) |> unique() |> length()

species_match <- inner_join(aquamaps_0.5, full_vuln_df, by = c("species"))

# aquamap_spp_list <- 
#   aquamaps_0.5 |> 
#   select(CenterLong, CenterLat, Probability, species) |> 
#   group_by(species) |> 
#   group_split()
# 
# # remove the big file
# rm(aquamaps_0.5)

# #test function
# this_species_df <- aquamap_spp_list[[19173]]

salmon_vect <- vect(reference_feed_total_N)

#Crop for east canada
east_canada_rast <- rasterize(x = salmon_vect, y = rast(res = 0.5), field = "total_N_mean", fun = sum) |> crop(ext(east_canada_bbox))|> subst(NA, -999)
east_canada_df <- terra::as.data.frame(east_canada_rast, xy =TRUE) |> 
  left_join(species_match, by = c("x" = "CenterLong", "y" = "CenterLat")) |> 
  rename(nitrogen = sum) |> 
  mutate(nitrogen = case_when(nitrogen ==-999 ~ NA,
                              TRUE ~ nitrogen)) |>  
  mutate(region = "East Canada")

#Crop for west canada
west_canada_rast <- rasterize(x = salmon_vect, y = rast(res = 0.5), field = "total_N_mean", fun = sum) |> crop(ext(west_canada_bbox)) |> subst(NA, -999)
west_canada_df <- terra::as.data.frame(west_canada_rast, xy =TRUE) |> 
  left_join(species_match, by = c("x" = "CenterLong", "y" = "CenterLat")) |> 
  rename(nitrogen = sum) |> 
  mutate(nitrogen = case_when(nitrogen ==-999 ~ NA,
                              TRUE ~ nitrogen)) |> 
  mutate(region = "West Canada")

#Crop for Chile
chile_rast <- rasterize(x = salmon_vect, y = rast(res = 0.5), field = "total_N_mean", fun = sum) |> crop(ext(chile_bbox))|> subst(NA, -999)
chile_df <- terra::as.data.frame(chile_rast, xy =TRUE) |> 
  left_join(species_match, by = c("x" = "CenterLong", "y" = "CenterLat")) |> 
  rename(nitrogen = sum) |> 
  mutate(nitrogen = case_when(nitrogen ==-999 ~ NA,
                              TRUE ~ nitrogen)) |>
  mutate(region = "Chile")

#Crop for europe - iceland
europe_iceland_rast <- rasterize(x = salmon_vect, y = rast(res = 0.5),field = "total_N_mean", fun = sum) |> crop(ext(europe_iceland_bbox)) |> subst(NA,-999)
europe_iceland_df <- terra::as.data.frame(europe_iceland_rast, xy =TRUE) |> 
  left_join(species_match, by = c("x" = "CenterLong", "y" = "CenterLat")) |> 
  rename(nitrogen = sum) |> 
 mutate(nitrogen = case_when(nitrogen ==-999 ~ NA,
                              TRUE ~ nitrogen)) |> 
  mutate(region = "Europe & Iceland")

#Crop for australia
australia_rast <- rasterize(x = salmon_vect, y = rast(res = 0.5), field = "total_N_mean", fun = sum) |> crop(ext(australia_bbox))|> subst(NA, -999)
australia_df <- terra::as.data.frame(australia_rast, xy =TRUE) |> 
  left_join(species_match, by = c("x" = "CenterLong", "y" = "CenterLat")) |> 
  rename(nitrogen = sum) |> 
  mutate(nitrogen = case_when(nitrogen ==-999 ~ NA,
                              TRUE ~ nitrogen)) |> 
  mutate(region = "Australia")

all_regions_df <- 
  bind_rows(east_canada_df, 
          west_canada_df, 
          chile_df,
          europe_iceland_df,
          australia_df) |> 
  mutate(norm_nitrogen = (nitrogen-min(nitrogen, na.rm = TRUE))/(max(nitrogen, na.rm = TRUE)-min(nitrogen, na.rm = TRUE))) |> 
  mutate(impact = norm_nitrogen*eutrophication_nutrient_pollution)

qsave(x=all_regions_df, file = "data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs")

europe_iceland_df |> filter(!is.na(nitrogen))
```

reproject_aquamaps_lyrs \<- (this_species_df){

this_sp \<- unique(this_species_df\$species)

save_name \<- sprintf("data/*general_data/species_layers/reprojected_distributions/species_dist_gall*%s.qs", this_sp)

if(!file.exists(save_name) & nrow(this_species_df)\>2){

```         
message("Processing reprojection for ", this_sp)

#create points from coords and transform to gall projection
this_sp_points <- st_as_sf(this_species_df, coords = c("CenterLong", "CenterLat"), crs = "EPSG:4326") |> st_transform(crs = "ESRI:54016")

#specify resolution
target_res <- 10000

#extent of points
this_sp_ext <- st_bbox(this_sp_points)

#create blank grid in gall ext and resolution
this_blank_grid <- st_as_stars(this_sp_ext, dx = target_res, dy = target_res, values = 1 , crs = "ESRI:54016")

#rasterize over blank grid
this_spp_rast <- st_rasterize(this_sp_points, template = this_blank_grid)

#convert
this_sp_gall_df <- as.data.frame(this_spp_rast, xy = TRUE) |> 
  mutate(species = this_sp)

qsave(x = this_sp_gall_df, file = save_name)
```

}}

#multicore run for species

future::plan(strategy = "multisession", workers = parallel::detectCores()-2)

map(.x = aquamap_spp_list, .f = reproject_aquamaps_lyrs)

aquamap_spp_list\[\[19173\]\]

\`\`\`

### 2025-04-08 00_model_functions.R

@@ -1,0 +1,615 @@
+### Functions modified from Baldan et al 2018 R package for aquaculture. 
+### https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0195732
+### https://github.com/cran/RAC/tree/master/R
+
+# Load required packages silently
+suppressPackageStartupMessages({
+  library(qs)
+  library(qs2) 
+  library(terra)
+  library(readxl)
+})
+
+fixnum <- function(n, digits = 4) {
+  str_flatten(c(rep("0", digits-nchar(as.character(n))), as.character(n)))
+}
+
+# Parameters definition
+# species_params['alpha']         [-] Feeding catabolism coefficient
+# species_params['betaprot']      [-] Assimilation coefficient for protein - SUPERCEEDED by digestibility coefficient
+# species_params['betalip']       [-] Assimilation coefficient for lipid - SUPERCEEDED by digestibility coefficient
+# species_params['betacarb']      [-] Assimilation coefficient for carbohydrates - SUPERCEEDED by digestibility coefficient
+# species_params['epsprot']       [J/gprot] Energy content of protein
+# species_params['epslip']        [J/glip] Energy content of lipid
+# species_params['epscarb']       [J/gcarb] Energy content of carbohydrate
+# species_params['epsO2']         [J/gO2] Energy consumed by the respiration of 1g of oxygen
+# species_params['pk']            [1/day] Temperature coefficient for the fasting catabolism
+# species_params['k0']            [1/Celsius degree] Fasting catabolism at 0 Celsius degree
+# species_params['m']             [-] Weight exponent for the anabolism
+# species_params['n']             [-] Weight exponent for the catabolism
+# species_params['betac']         [-] Shape coefficient for the H(Tw) function
+# species_params['Tma']           [Celsius degree] Maximum lethal temperature  
+# species_params['Toa']           [Celsius degree] Optimal temperature
+# species_params['Taa']           [Celsius degree] Lowest feeding temperature
[…]

### 2025-04-08 03_run_atlantic_salmon_model.R

@@ -1,538 +1,0 @@
-# Setup -----------------------------------------------------------------------------------------------------------
-# library(tidyverse)
-library(magrittr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggplot2)
-library(terra)
-library(qs)
-library(here)
-library(sf)
-library(purrr)
-library(furrr)
-library(targets)
-library(future)
-library(arrow)
-library(readxl)
-library(units)
-library(conflicted)
-conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
-
-# functions
-source("src/model_functions.R")
-fixnum <- function(n, digits = 4) {str_flatten(c(rep("0", digits-nchar(as.character(n))), as.character(n)))}
-
-# species paths
-this_species <- "atlantic_salmon"
-this_path <- sprintf("data/%s", this_species)
-
-# STEP 1: Temperature forcings ------------------------------------------------------------------------------------
-# You don't need to do this again unless you make changes - all the important stuff is saved
-# Prep temperature forcings for each farm site
-# production_cycle <- read.csv("data/_general_data/production_cycles/production_cycle.csv") %>% 
-#   filter(species == this_species) %>% 
-#   rename(production_cycle_length = days) %>% 
-#   pull(production_cycle_length)
-production_cycle <- 1100
-
-farms <-  qread("data/_general_data/farm_locations/locations_w_species_fao_area_stocking.qs") %>% 
-  filter(model_name == this_species) %>% 
-  select(-row_num) %>% 
-  mutate(farm_id = row_number())
-
-hemi <- cbind(farms$farm_id, sf::st_coordinates(farms$geometry)) %>% 
-  as.data.frame() %>% rename(farm_ID = V1, lon = X, lat = Y) %>% 
-  write_parquet("data/_general_data/farm_locations/farm_coords.parquet")
-
-day_number <- seq(1:production_cycle)
-
-temp_data <- purrr::map_dfc(.x = day_number, .f = function(day_number){
-  rast_day_number <- if_else(day_number <= 365, true = day_number, false = day_number-365)
-  rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
[…]

### 2025-04-08 04_targets_individual.R

@@ -1,0 +1,235 @@
+suppressMessages(suppressWarnings(library(targets)))
+suppressMessages(suppressWarnings(library(crew)))
+suppressMessages(suppressWarnings(library(mirai)))
+suppressMessages(suppressWarnings(library(arrow)))
+suppressMessages(suppressWarnings(library(sf)))
+suppressMessages(suppressWarnings(library(dplyr)))
+suppressMessages(suppressWarnings(library(tidyr)))
+suppressMessages(suppressWarnings(library(terra))) # do not remove
+suppressMessages(suppressWarnings(library(magrittr)))
+suppressMessages(suppressWarnings(library(conflicted)))
+suppressMessages(suppressWarnings(library(units)))
+conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+
+tar_option_set(
+  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
+  format = "qs", 
+  controller = crew_controller_local(workers = 10, seconds_idle = 10),
+  workspace_on_error = TRUE
+)
+
+tar_source("00_model_functions.R")
+
+# Paths -----------------------------------------------------------------------------------------------------------
+this_species <- "atlantic_salmon"
+this_path <- file.path("data", this_species)
+google_path <- "C:/Users/treimer/OneDrive - University of Tasmania/Sustainable Aquafeeds/Data from Google Drive"
+
+# Begin targets pipeline ------------------------------------------------------------------------------------------
+list(
+  tar_target(farm_data_file, "data/_general_data/SST/farm_SST_extracted.parquet", format = "file"),
+  tar_target(farm_coord_file, "data/_general_data/farm_locations/farm_coords.parquet", format = "file"),
+  tar_target(farms_to_omit_file, sprintf("data/_general_data/farm_locations/%s_farms_to_omit.qs", this_species), format = "file"),
+  tar_target(farms_to_omit, qs::qread(farms_to_omit_file)),
+  tar_target(
+    farm_IDs, 
+    farm_data_file %>% 
+      read_parquet() %>% 
+      filter(!farm_id %in% farms_to_omit) %>% 
+      distinct(farm_id) %>% 
+      # slice_sample(n = 272) %>% 
+      as.vector() %>% unlist() %>% unname()
+  ),
+  tar_target(
[…]

### 2025-04-08 05_targets_farm.R

@@ -1,0 +1,381 @@
+suppressMessages(suppressWarnings(library(targets)))
+suppressMessages(suppressWarnings(library(crew)))
+suppressMessages(suppressWarnings(library(mirai)))
+suppressMessages(suppressWarnings(library(arrow)))
+suppressMessages(suppressWarnings(library(sf)))
+suppressMessages(suppressWarnings(library(dplyr)))
+suppressMessages(suppressWarnings(library(tidyr)))
+suppressMessages(suppressWarnings(library(terra))) # do not remove
+suppressMessages(suppressWarnings(library(magrittr)))
+suppressMessages(suppressWarnings(library(conflicted)))
+conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+
+tar_option_set(
+  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
+  format = "qs", 
+  controller = crew_controller_local(workers = 3),
+  workspace_on_error = TRUE
+)
+
+tar_source("00_model_functions.R")
+
+# Paths -----------------------------------------------------------------------------------------------------------
+gendata_path <- file.path("data", "_general_data")
+this_species <- "atlantic_salmon"
+species_path <- file.path("data", this_species)
+
+# Global objects --------------------------------------------------------------------------------------------------
+farm_harvest_size <- tar_read(farm_harvest_size, store = "04_targets_individual") %>% 
+  select(c(farm_ID, weight))
+
+# Begin targets pipeline ------------------------------------------------------------------------------------------
+list(
+  tar_target(farm_data_file, file.path(gendata_path, "SST", "farm_SST_extracted.parquet"), format = "file"),
+  tar_target(farm_coord_file, file.path(gendata_path, "farm_locations", "farm_coords.parquet"), format = "file"),
+  tar_target(farms_to_omit_file, sprintf(file.path(gendata_path, "farm_locations", "%s_farms_to_omit.qs"), this_species), format = "file"),
+  tar_target(farms_to_omit, qs::qread(farms_to_omit_file)),
+  tar_target(
+    farm_IDs, 
[…]

### 2025-04-08 06_run_atlantic_salmon_model.R

@@ -1,0 +1,716 @@
+# Setup -----------------------------------------------------------------------------------------------------------
+# library(tidyverse)
+library(magrittr)
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(terra)
+library(qs)
+library(here)
+library(sf)
+library(purrr)
+library(furrr)
+library(targets)
+library(future)
+library(arrow)
+library(readxl)
+library(units)
+library(conflicted)
+conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
+
+# functions
+source("00_model_functions.R")
+
+# species paths
+this_species <- "atlantic_salmon"
+this_path <- sprintf("data/%s", this_species)
+
+# STEP 1: Temperature forcings ------------------------------------------------------------------------------------
+# You don't need to do this again unless you make changes - all the important stuff is saved
+# Prep temperature forcings for each farm site
+# production_cycle <- read.csv("data/_general_data/production_cycles/production_cycle.csv") %>% 
+#   filter(species == this_species) %>% 
+#   rename(production_cycle_length = days) %>% 
+#   pull(production_cycle_length)
+production_cycle <- 1100
+
+farms <-  qread("data/_general_data/farm_locations/locations_w_species_fao_area_stocking.qs") %>% 
+  filter(model_name == this_species) %>% 
+  select(-row_num) %>% 
+  mutate(farm_id = row_number())
+
+hemi <- cbind(farms$farm_id, sf::st_coordinates(farms$geometry)) %>% 
+  as.data.frame() %>% rename(farm_ID = V1, lon = X, lat = Y) %>% 
+  write_parquet("data/_general_data/farm_locations/farm_coords.parquet")
+
+day_number <- seq(1:production_cycle)
+
+temp_data <- purrr::map_dfc(.x = day_number, .f = function(day_number){
+  rast_day_number <- if_else(day_number <= 365, true = day_number, false = day_number-365)
+  rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
+  rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
[…]

### 2025-04-08 XX_spatial_templates.R

@@ -1,0 +1,19 @@
+#Template rasters
+
+
+base_rast <- rast(res = 0.5)
+values(base_rast) <- 1:ncell(base_rast)
+
+
+gall_rast <- rast(ext(-20037508, 20037508, -10000000, 10000000), 
+                  resolution = 10000, 
+                  crs = "ESRI:54016")
+
+values(gall_rast) <- 1:ncell(gall_rast)
+
+#bounding boxes
+east_canada_bbox <- c(xmin = -75, xmax = -45, ymin = 39, ymax = 54)
+west_canada_bbox <- c(xmin =-140, xmax = -115, ymin = 45, ymax = 57)
+chile_bbox <- c(xmin = -82, xmax = -63, ymin = -57, ymax = -18)
+europe_iceland_bbox <- c(xmin = -29, xmax = 48, ymin = 46, ymax = 73)
+australia_bbox <- c(xmin = 143, xmax = 149, ymin = -44, ymax = -40)

### 2025-04-08 testing.R

@@ -1,0 +1,149 @@
+# Load required packages
+suppressMessages(suppressWarnings({
+  library(future)
+  library(furrr)
+  library(arrow)
+  library(sf)
+  library(dplyr)
+  library(tidyr)
+  library(terra)
+  library(magrittr)
+  library(stringr)
+  library(ggplot2)
+  library(matrixStats)
+  library(tibble)
+  library(readxl)
+  library(tictoc)
+}))
+
+conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = TRUE)
+
+# Source model functions
+source("00_model_functions.R")
+
+# Set up parallel processing
+plan(multisession, workers = future::availableCores() - 1)
+
+# Define paths
+gendata_path <- file.path("data", "_general_data")
+this_species <- "atlantic_salmon"
+species_path <- file.path("data", this_species)
+
+# Load farm harvest size data (generated from mean individual modelling)
+farm_harvest_size <- tar_read(farm_harvest_size, store = "04_targets_individual") %>%
+  select(c(farm_ID, weight))
+
+# Load and prepare farm data
+farm_data <- read_parquet(file.path(gendata_path, "SST", "farm_SST_extracted.parquet")) %>% 
+  select(data_year, tonnes_per_farm, daily_mort_rate, farm_id, day, temp_c) %>% 
+  mutate(day = str_split_i(day, "day_", 2) %>% as.numeric())
+farms_to_omit <- qs::qread(sprintf(file.path(gendata_path, "farm_locations", "%s_farms_to_omit.qs"), this_species))
+
+# Get farm IDs
+farm_IDs <- farm_data %>%
+  filter(!farm_id %in% farms_to_omit) %>%
+  distinct(farm_id) %>%
+  slice_sample(n = 10) %>%
+  pull(farm_id)
+
+# Define time parameters
+times_N <- c("t_start" = 121, "t_end" = 121+547, "dt" = 1)
+times_S <- c("t_start" = 274, "t_end" = 274+547, "dt" = 1)
+
+# Load and prepare farm coordinates
+farm_coords <- read_parquet(file.path(gendata_path, "farm_locations", "farm_coords.parquet")) %>%
+  mutate(t_start = case_when(lat > 0 ~ times_N['t_start'], TRUE ~ times_S['t_start']),
+         t_end = case_when(lat > 0 ~ times_N['t_end'], TRUE ~ times_S['t_end']))
+
+# Process farm time series data in parallel
+tic()
[…]

### 2025-04-25 08_manuscript/_manuscript/08_manuscript.qmd
Updates

--- 2025-04-08 08_manuscript/08_manuscript.qmd
@@
   cache: true
+  freeze: auto
 
@@
 
+```{r global-variables}
+#| include: false
+#| eval: true
+
+source(here("00_model_functions.R"))
+
+indi_store <- here() %>% file.path("04_targets_individual")
+farm_store <- here() %>% file.path("05_targets_farm")
+
+species_params <- tar_read(species_params, store = indi_store)
+pop_params <- tar_read(pop_params, store = farm_store)
+
+farm_outputs <- here() %>% file.path("data", "atlantic_salmon", "data_products", "model_outputs_farm")
+coho_outputs <- here() %>% file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohort")
+```
+
 # Introduction
+
+[This is a note create with the `aside` class.]{.aside}
 
@@
 
+```{r fig-farm-mean-temps}
+#| fig-caption: Colours show farm site mean temperature
+
+worldmap <- ne_countries(scale = "medium", returnclass = "sf")
+farms_to_omit <- here() %>% 
+  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_farms_to_omit.qs") %>% 
+  qread()
+
+farms_w_temp_df <- here() %>% 
+  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
+  qread() %>% 
+  filter(!farm_id %in% farms_to_omit) %>% 
+  mutate(country = as.factor(country),
+         species_group = as.factor(species_group),
+         data_type = as.factor(data_type),
+         data_type_2 = as.factor(data_type_2),
+         model_name = as.factor(model_name),
+         F_CODE = as.factor(F_CODE),
+         day = str_split_i(day, "_", 2) %>% as.integer())
+
+farm_temp_means <- farms_w_temp_df %>% 
+  select(iso3c, country, farm_id, temp_c)
+farm_temp_means_1 <- farms_w_temp_df %>% 
+  filter(day == 1) %>% 
+  select(geometry)
+
+farm_temp_means <- farm_temp_means %>% 
+  group_by(iso3c, country, farm_id) %>% 
+  reframe(temp_c = meanna(temp_c))
+
+farm_temp_means <- cbind(farm_temp_means, farm_temp_means_1)
+
+ggplot(data = worldmap, aes(geometry = geometry)) +
+  geom_sf(fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(colour = temp_c), size = 1.5) +
+  coord_sf() +
+  theme_classic() 
+```
+
+```{r fig-farm_temp_means-2}
+farm_temp_means %>%
+  mutate(
+    coords = st_coordinates(geometry),
+    longitude = coords[,1],
+    latitude = coords[,2]
+  ) %>%
+  select(-coords) %>% 
+  ggplot(aes(y = temp_c, x = abs(latitude), colour = country)) +
+  geom_point() +
+  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Temperature ("*degree*"C)")) +
+  theme_classic() +
+  theme(legend.position = "bottom", legend.title = element_blank())
+```
+
 ## Model and approach
@@
 
-* Farms with mean temperature < 4$^\circ$ were excluded
+* Farms with a mean temperature of $\leq 6^\circ$C were excluded.
+```{r farms omitted}
+farms_to_omit <- here() %>% file.path("data/_general_data/farm_locations/atlantic_salmon_farms_to_omit.qs") %>% 
+  qread()
+```
+
+[Need to put the cohort concept (and harvest timing) in here.]{.aside}
+
+```{r fig-cohorts}
+#| fig-cap: Example of cohorts
+
+fnms <- coho_outputs %>% 
+  list.files(full.names = T) %>% 
+  str_subset("biomass")
+
+df <- fnms[1] %>% read_parquet() %>% 
+  filter(feed == "reference") %>% 
+  mutate(mean = set_units(mean, "g") %>% set_units("t"),
+         sd = set_units(sd, "g") %>% set_units("t"))
+
+ggplot(df, aes(x = yday, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(linetype = "dotted", alpha = 0) +
+  scale_x_continuous(breaks = seq(0, 2000, 200)) +
+  labs(y = "Farm biomass", x = "Day of the year") +
+  theme_classic() +
+  theme(legend.position = "none", aspect.ratio = 0.75)
+
+yrs <- max(df$yday)/365
+harvests <- df %>% 
+  group_by(cohort) %>% 
+  reframe(mean = maxna(mean),
+          sd = maxna(sd))
+
+sum(harvests$mean)/yrs
+mean(harvests$sd)/yrs
+```
+
+### Feeding rate
+
+```{r fig-functional-response-to-temperature}
+#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
+
+df <- data.frame(water_temp = seq(-5, 26, 0.25))
+df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)
+df <- df %>% 
+mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * feeding,
+       food_prov = NA)
+for (i in 1:nrow(df)) {
+  df$food_prov[i] <- food_prov_rate(pop_params = pop_params, rel_feeding = df$feeding[i], ing_pot = df$ing_pot[i], 
+                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
+}
+df$ing_pot <- df$ing_pot/maxna(df$ing_pot)
+df$food_prov <- df$food_prov/maxna(df$ing_pot)
+
+df %>% 
+  ggplot(aes(x = water_temp, y = ing_pot)) +
+  geom_line(linewidth = 0.75) +
+  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
+  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
+  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
+  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
+  theme_classic() +
+  theme(text = element_text(colour = "black", family = "serif", size = 12))
+```
 
@@
 
-pop_params <- tar_read(pop_params, store = "../05_targets_farm")
-species_params <- tar_read(species_params, store = "../05_targets_farm")
 params <- c(pop_params, species_params)
 pnames <- names(params)
-sens_excr <- file.path("..", "data", "atlantic_salmon", "data_products", "excreted_parameter_sensitivity.parquet") %>%
+sens_excr <- here() %>% file.path("data", "atlantic_salmon", "data_products", "excreted_parameter_sensitivity.parquet") %>%
   read_parquet() %>%
@@
 | Parameter | Value | Units | Description | Reference | 
-|:-------:|:----:|:----:|----------------|-------------------------|
+|:-------:|:----:|:----:|:----------------|:-------------------------|
 | $\alpha$ | `r unname(params['alpha'])` | - | Feeding catabolism coefficient | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] | 
-| $\epsilon_{P}$ | `r unname(params['epsprot'])` | J g protein-1 | Energy content of protein | @baldan_r_2018 | 
-| $\epsilon_{L}$ | `r unname(params['epslip'])` | J g lipid-1 | Energy content of lipid | @baldan_r_2018 |
-| $\epsilon_{C}$ | `r unname(params['epscarb'])` | J g carbohydrate-1 | Energy content of carbohydrate | @baldan_r_2018 |
-| $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2-1 | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
-| $pk$ | `r unname(params['pk'])` | d-1 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
-| $k_0$ | `r unname(params['k0'])` | degree C-1 | Fasting catabolism at 0 Celsius degree | @macnaughton_using_2019 |
+| $\epsilon_{P}$ | `r unname(params['epsprot'])` | J g protein$^{-1}$ | Energy content of protein | @baldan_r_2018 | 
+| $\epsilon_{L}$ | `r unname(params['epslip'])` | J g lipid$^{-1}$ | Energy content of lipid | @baldan_r_2018 |
+| $\epsilon_{C}$ | `r unname(params['epscarb'])` | J g carbohydrate$^{-1}$ | Energy content of carbohydrate | @baldan_r_2018 |
+| $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2$^{-1}$ | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
+| $pk$ | `r unname(params['pk'])` | d$^{-1}$ | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
+| $k_0$ | `r unname(params['k0'])` | - | Fasting catabolism at 0 $^{^\circ}$C | @macnaughton_using_2019 |
 | $m$ | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
@@
 Coefficent for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
-| $T_{max}$ | `r unname(params['Tma'])` | C | Maximum lethal temperature | Juvenile Chinook salmon (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
-| $T_{opt}$ | `r unname(params['Toa'])` | C | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
+| $T_{max}$ | `r unname(params['Tma'])` | $^{^\circ}$C | Maximum lethal temperature | Juvenile *Oncorhynchus tshawytscha* (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
+| $T_{opt}$ | `r unname(params['Toa'])` | $^{^\circ}$C | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
 Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0 $\pm$ 14.6 g, temps: 6, 10, 14, 18${\circ}$C |
-| $T_{min}$ | `r unname(params['Taa'])` | C | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] | 
+| $T_{min}$ | `r unname(params['Taa'])` | $^{^\circ}$C | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] | 
 | $\omega$ | `r unname(params['omega'])` | g O2 / g | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
-| $a$ | `r unname(params['a'])` | J g tissue-1 | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
+| $a$ | `r unname(params['a'])` | J g tissue$^{-1}$ | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
 | $k$ | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
@@
 | $\Delta{W}$ | `r unname(params['deltaW'])` | g | Dry weight standard deviation | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\overline{I_{max}}$ | `r unname(params['meanImax'])` | g g-1 fish day-1 | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g-1 fish day-1 | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $mort$ | `r unname(params['mortmyt'])` | d-1 | Natural mortality rate | @tvete_towards_2023 |
+| $\overline{I_{max}}$ | `r unname(params['meanImax'])` | g g$^{-1}$ fish day$^{-1}$ | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
+| $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g$^{-1}$ fish day$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
+| $mort$ | `r unname(params['mortmyt'])` | d$^{-1}$ | Natural mortality rate | @tvete_towards_2023 |
 : Growth parameters for Atlantic salmon {#tbl-params}
@@
   ggplot(aes(x = adj_param, y = sens, ymin = sens-sd, ymax = sens+sd)) +
-  geom_col(alpha = 0.35, colour = "black") +
+  geom_col(colour = "black", fill = "salmon", alpha = 0.5) +
   geom_errorbar(width = 0.3) +
@@
 
-farm_harvest_size <- tar_read(farm_harvest_size, store = "../04_targets_individual")
-
-ggplot(farm_harvest_size, aes(x = weight/1000)) + 
-  geom_histogram(colour = "black", fill = "salmon", alpha = 0.5) + 
+pdata <- here() %>% file.path("data", "atlantic_salmon", "data_products", "harvest_size.parquet") %>% read_parquet()
+pdata %>% 
+  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
+  select(c(farm_ID, weight)) %>% 
+  ggplot(aes(x = weight)) +
+  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.5) +
+  scale_y_continuous(limits = c(0,500)) +
+  labs(y = "Frequency", x = "Harvest weight") +
   theme_classic() +
-  scale_x_continuous(breaks = seq(0, 8, 1), limits = c(1.25, 7.75)) + 
-  labs(y = "Frequency", x = "Individual weight (kg)")
+  theme(legend.position = "none", aspect.ratio = 0.75)
 ```
@@
 ## Species vulnerability layers
+
+# Results
+
+* Main point is the difference between feeds. 
+* This should be expressed in t/t salmon, so farm biomass is also important.
+* Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
+
+# Biomass produced
+
+```{r biomass produced}
+fnms <- farm_outputs %>% 
+  list.files(full.names = T) %>% 
+  str_subset("biomass")
+
+dfs <- list()
+for (fid in seq_along(fnms)) {
+  dfs[[fid]] <- fnms[fid] %>% 
+    read_parquet() %>% 
+    filter(days == max(days)) %>% 
+    mutate(mean = mean %>% set_units("g") %>% set_units("t"),
+           sd = sd %>% set_units("g") %>% set_units("t"))
+}
+df <- bind_rows(dfs)
+df_mean <- df %>% 
+  select(-c(days, sd)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(future_diff = (future - reference)/reference,
+         past_diff = (past - reference)/reference) %>% 
+  select(-c(reference, past, future)) %>% 
+  pivot_longer(names_to = "feed", values_to = "mean", cols = c(future_diff, past_diff))
+df_sd <- df %>% 
+  select(-c(days, mean)) %>% 
+  pivot_wider(names_from = feed, values_from = sd) %>% 
+  mutate(future_diff = (future - reference)/reference,
+         past_diff = (past - reference)/reference) %>% 
+  select(-c(reference, past, future)) %>% 
+  pivot_longer(names_to = "feed", values_to = "sd", cols = c(future_diff, past_diff))
+df <- merge(df_mean, df_sd, by = c("farm_ID", "feed"))
+```
+
+# Locations
 

### 2025-04-25 00_model_functions.R

@@ -10,9 +10,13 @@ suppressPackageStartupMessages({
   library(readxl)
 })
 
-fixnum <- function(n, digits = 4) {
-  str_flatten(c(rep("0", digits-nchar(as.character(n))), as.character(n)))
-}
+fixnum <- function(n, digits = 4) {str_flatten(c(rep("0", digits-nchar(as.character(n))), as.character(n)))}
+meanna <- function(x, ...) mean(x, na.rm = TRUE, ...)
+minna <- function(x, ...) min(x, na.rm = TRUE, ...)
+maxna <- function(x, ...) max(x, na.rm = TRUE, ...)
+sdna <- function(x, ...) sd(x, na.rm = TRUE, ...)
+sumna <- function(x, ...) sum(x, na.rm = TRUE, ...)
+medianna <- function(x, ...) median(x, na.rm = TRUE, ...)
 
 # Parameters definition
 # species_params['alpha']         [-] Feeding catabolism coefficient
@@ -37,92 +41,153 @@ fixnum <- function(n, digits = 4) {
 # species_params['eff']           [-] Food ingestion efficiency
 # species_params['fcr']           [-] Food conversion ratio
 
-feeding_rate <- function(water_temp, species_params){
-  exp(species_params['betac']*(water_temp-species_params['Toa'])) * 
-    ((species_params['Tma']-water_temp)/(species_params['Tma']-species_params['Toa']))^(species_params['betac']*(species_params['Tma']-species_params['Toa']))
+get_farms <- function(farms_file, farm_ID, this_species){
+  qread(farms_file) %>% 
+    filter(model_name == this_species) %>% 
+    select(-row_num) %>% 
+    mutate(farm_id = row_number()) %>% 
+    filter(farm_id == farm_ID)
 }
 
-food_prov_rate <- function(rel_feeding, ing_pot, ing_pot_10){
-  ifelse(
-    rel_feeding > 0.1, 
-    yes = ing_pot + rnorm(1, 0.035, 0.0075)*ing_pot, 
-    no = ing_pot_10 # no = 0.25 * 0.066 * weight^0.75
-  )
+get_feed_params <- function(file){
+  df <- read.csv(file, header = F)
+  values <- as.numeric(df$V1)
+  names(values) <- df$V2
+  values <- values[!is.na(values)]
+  return(values)
+}
+
+generate_pop <- function(harvest_n, mort, times) {
+  
+  ts <- seq(times['t_start'], times['t_end'], by = times['dt'])   # Integration times
[…]

### 2025-04-25 04_targets_individual.R

@@ -1,15 +1,17 @@
-suppressMessages(suppressWarnings(library(targets)))
-suppressMessages(suppressWarnings(library(crew)))
-suppressMessages(suppressWarnings(library(mirai)))
-suppressMessages(suppressWarnings(library(arrow)))
-suppressMessages(suppressWarnings(library(sf)))
-suppressMessages(suppressWarnings(library(dplyr)))
-suppressMessages(suppressWarnings(library(tidyr)))
-suppressMessages(suppressWarnings(library(terra))) # do not remove
-suppressMessages(suppressWarnings(library(magrittr)))
-suppressMessages(suppressWarnings(library(conflicted)))
-suppressMessages(suppressWarnings(library(units)))
-conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+suppressMessages(suppressWarnings(suppressPackageStartupMessages({
+  library(targets)
+  library(crew)
+  library(mirai)
+  library(arrow)
+  library(sf)
+  library(dplyr)
+  library(tidyr)
+  library(terra) # do not remove
+  library(magrittr)
+  library(conflicted)
+  library(units)
+  conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+})))
 
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
@@ -113,33 +115,33 @@ list(
   ),
   
 ## Example individuals --------------------------------------------------------------------------------------------
-  tar_target(
-    example_individual,
-    command = {
-      df <- fish_growth(
-        pop_params = pop_params,
-        species_params = species_params,
-        water_temp = farm_temp,
-        feed_params = list(
-          Proteins = feed_params_protein,
-          Carbohydrates = feed_params_carbs,
-          Lipids = feed_params_lipids
-        ),
-        times = farm_times,
-        init_weight = pop_params["meanW"],
-        ingmax = pop_params["meanImax"]
-      )
-      df %>% 
-        as.data.frame() %>% remove_rownames() %>% 
-        mutate(SGR = 100 * (exp((log(weight)-log(weight[1]))/(days-days[1])) - 1),
-               FCR = food_prov/dw) %>% 
[…]

### 2025-04-25 05_targets_farm.R

@@ -1,19 +1,21 @@
-suppressMessages(suppressWarnings(library(targets)))
-suppressMessages(suppressWarnings(library(crew)))
-suppressMessages(suppressWarnings(library(mirai)))
-suppressMessages(suppressWarnings(library(arrow)))
-suppressMessages(suppressWarnings(library(sf)))
-suppressMessages(suppressWarnings(library(dplyr)))
-suppressMessages(suppressWarnings(library(tidyr)))
-suppressMessages(suppressWarnings(library(terra))) # do not remove
-suppressMessages(suppressWarnings(library(magrittr)))
-suppressMessages(suppressWarnings(library(conflicted)))
-conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+suppressMessages(suppressWarnings(suppressPackageStartupMessages({
+  library(targets)
+  library(crew)
+  library(mirai)
+  library(arrow)
+  library(sf)
+  library(dplyr)
+  library(tidyr)
+  library(terra) # do not remove
+  library(magrittr)
+  library(conflicted)
+  conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+})))
 
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 3),
+  controller = crew_controller_local(workers = 16),
   workspace_on_error = TRUE
 )
 
@@ -40,7 +42,7 @@ list(
       read_parquet() %>% 
       filter(!farm_id %in% farms_to_omit) %>% 
       distinct(farm_id) %>% 
-      slice_sample(n = 1125) %>%
+      # slice_sample(n = 350) %>%
       as.vector() %>% unlist() %>% unname()
   ),
   tar_target(
@@ -61,9 +63,11 @@ list(
       mutate(t_start = case_when(lat > 0 ~ times_N['t_start'], TRUE ~ times_S['t_start']),
              t_end = case_when(lat > 0 ~ times_N['t_end'], TRUE ~ times_S['t_end']))
   ),
-  tar_target(farm_times, 
[…]

### 2025-04-25 06_run_atlantic_salmon_model.R

@@ -1,31 +1,35 @@
 # Setup -----------------------------------------------------------------------------------------------------------
-# library(tidyverse)
-library(magrittr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggplot2)
-library(terra)
-library(qs)
-library(here)
-library(sf)
-library(purrr)
-library(furrr)
-library(targets)
-library(future)
-library(arrow)
-library(readxl)
-library(units)
-library(conflicted)
-conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
+suppressPackageStartupMessages({
+  library(magrittr)
+  library(dplyr)
+  library(tidyr)
+  library(stringr)
+  library(ggplot2)
+  library(terra)
+  library(qs)
+  library(here)
+  library(sf)
+  library(purrr)
+  library(furrr)
+  library(targets)
+  library(future)
+  library(arrow)
+  library(readxl)
+  library(units)
+  library(tictoc)
+  library(conflicted)
+  conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
+})
 
 # functions
 source("00_model_functions.R")
 
 # species paths
 this_species <- "atlantic_salmon"
-this_path <- sprintf("data/%s", this_species)
-
+this_path <- file.path("data", this_species)
+fig_path <- file.path(this_path, "figures")
+prod_path <- file.path(this_path, "data_products")
+  
 # STEP 1: Temperature forcings ------------------------------------------------------------------------------------
 # You don't need to do this again unless you make changes - all the important stuff is saved
 # Prep temperature forcings for each farm site
@@ -121,7 +125,7 @@ mean_farm_temp <- farm_list %>%
   })
 
 farms_to_omit <- mean_farm_temp %>% 
-  filter(mean_temp < 4) %>% 
+  filter(mean_temp <= 6) %>% 
   pull(farm_id)
 
 qsave(x = farms_to_omit, 
@@ -132,20 +136,20 @@ qsave(x = farms_to_omit,
 ## Example individuals --------------------------------------------------------------------------------------------
 Sys.setenv(TAR_PROJECT = "project_individual")
 # tar_visnetwork()
[…]

### 2025-04-25 10_data_analysis.R

@@ -1,0 +1,57 @@
+# Setup -----------------------------------------------------------------------------------------------------------
+suppressPackageStartupMessages({
+  library(magrittr)
+  library(dplyr)
+  library(tidyr)
+  library(stringr)
+  library(terra)
+  library(qs)
+  library(here)
+  library(arrow)
+  library(units)
+  library(ggplot2)
+  library(sf)
+  library(rnaturalearth)
+  library(rnaturalearthdata)
+  library(conflicted)
+  conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
+})
+
+# This script aims to take the outputs from the model and answer specific questions 
+# Paths & globals -------------------------------------------------------------------------------------------------
+source("00_model_functions.R")
+
+coho_path <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohorts")
+
+# * Main point is the difference between feeds. 
+# * This should be expressed in t/t salmon, so farm biomass is also important.
+# * Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
+
+# Biomass produced ------------------------------------------------------------------------------------------------
+# How accurately is the model producing the correct biomass production levels?
+# Here, "cohorts" is going to become "farms", or more accurately, farm outputs per 2-year cycle with overlaps (cohort 2) 
+
+farm_info_ts <- file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
+  qread() %>% 
+  filter(day == "day_1") %>% 
+  mutate(country = as.factor(country),
+         species_group = as.factor(species_group),
+         data_type = as.factor(data_type),
+         data_type_2 = as.factor(data_type_2),
+         model_name = as.factor(model_name),
+         F_CODE = as.factor(F_CODE),
+         day = str_split_i(day, "_", 2) %>% as.integer())
+hist(farm_info$tonnes_per_farm)
+
+
+coho_biom <- file.path(coho_path) %>% 
+  list.files(full.names = T) %>% 
+  str_subset("biomass")
+
+
+
+# Difference between feeds ----------------------------------------------------------------------------------------
+
+
+
+

### 2025-04-25 testing.R

@@ -14,6 +14,7 @@ suppressMessages(suppressWarnings({
   library(tibble)
   library(readxl)
   library(tictoc)
+  library(conflicted)
 }))
 
 conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = TRUE)
@@ -22,7 +23,7 @@ conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = TRUE)
 source("00_model_functions.R")
 
 # Set up parallel processing
-plan(multisession, workers = future::availableCores() - 1)
+plan(multisession, workers = future::availableCores() - 2)
 
 # Define paths
 gendata_path <- file.path("data", "_general_data")
@@ -30,7 +31,7 @@ this_species <- "atlantic_salmon"
 species_path <- file.path("data", this_species)
 
 # Load farm harvest size data (generated from mean individual modelling)
-farm_harvest_size <- tar_read(farm_harvest_size, store = "04_targets_individual") %>%
+farm_harvest_size <- targets::tar_read(farm_harvest_size, store = "04_targets_individual") %>%
   select(c(farm_ID, weight))
 
 # Load and prepare farm data
@@ -104,14 +105,13 @@ feed_profiles <- future_map(feed_types, function(ft) {
 toc() # 0.5 sec elapsed
 
 # Run main farm growth calculations in parallel
-tic()
 main_farm_growth <- future_map(farm_IDs, function(id) {
-  farm_temp <- farm_ts_data[[which(farm_IDs == id)]]$temp_c
   farm_times <- c(
     farm_coords$t_start[farm_coords$farm_ID == id],
     farm_coords$t_end[farm_coords$farm_ID == id],
     dt = 1
   )
+  farm_temp <- farm_ts_data[[which(farm_IDs == id)]]$temp_c[farm_times['t_start']:farm_times['t_end']]
   
   N_population <- generate_pop(
     harvest_n = (farm_data$tonnes_per_farm[farm_data$farm_id == id][1]*10^6)/
@@ -120,30 +120,72 @@ main_farm_growth <- future_map(farm_IDs, function(id) {
     times = farm_times
   )
   
-  result <- future_map(feed_types, function(ft) {
-    feed_idx <- which(feed_types == ft)
-    farm_growth(
-      pop_params = pop_params,
-      species_params = species_params,
-      water_temp = farm_temp,
-      feed_params = list(
[…]

### 2025-05-04 XX_visualisation.qmd
Full runthrough and renaming scripts

---
title: "05_visualisation"
format: html
editor: source

execute:
  eval: false
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup, eval=T, cache=T}
library(tidyverse)
library(here)
library(ggpubr)
library(patchwork)
library(qs)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(dtplyr)
library(future)
library(furrr)
library(RColorBrewer)

source("src/spatial_templates.R")
```

Rasterise reference feed data

REFERENCE FEED: Nitrogen per tonne

```{r}

reference_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/reference/nitrogen_summary.qs")) |> 
  mutate(N_per_biomass_mean = total_N_mean/biomass_mean)

reference_feed_mean_N <- reference_point_df |> dplyr::select(geometry, N_per_biomass_mean)

base_rast <- rast(res=1)

total_N_rast_ref <- rasterize(x = reference_feed_mean_N, y = base_rast, field = "N_per_biomass_mean", fun = mean)

total_N_rast_df_ref <- terra::as.data.frame(x= total_N_rast_ref, xy = TRUE)

#max values to scale legend nby

total_N_rast_df_ref |> pull(mean) |> max()

# map nitrogen per tonne
reference_N_tonne <- ggplot()+
  geom_tile(data = total_N_rast_df_ref, aes(x = x, y = y, fill = mean))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
   theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: reference"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,0.8))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

#histogram

reference_hist <- ggplot()+
  geom_histogram(data = reference_point_df, aes(x = N_per_biomass_mean), fill = "darkgreen")+
  theme_pubr()+
  labs(subtitle = "Feed: plant-dominant")+
  scale_x_continuous(limits = c(-0.1, 1))

```

PAST FEED: Nitrogen per tonne

```{r}

past_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/past/nitrogen_summary.qs")) |> 
  mutate(N_per_biomass_mean = total_N_mean/biomass_mean)

past_feed_mean_N <- past_point_df |> 
  dplyr::select(geometry, N_per_biomass_mean)

base_rast <- rast(res=1)

total_N_rast_past <- rasterize(x = past_feed_mean_N, y = base_rast, field = "N_per_biomass_mean", fun = mean)

total_N_rast_df_past <- terra::as.data.frame(x= total_N_rast_past, xy = TRUE)

#max value for legend 
total_N_rast_df_past |> pull(mean) |> max()

#map nitrogen per tonne
past_N_tonne <- 
  ggplot()+
  geom_tile(data = total_N_rast_df_past, aes(x = x, y = y, fill = mean))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
   theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: past"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,0.8))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

#histogram of nitrogen per tonne

past_hist <- ggplot()+
  geom_histogram(data = past_point_df, aes(x = N_per_biomass_mean), fill = "darkblue")+
  theme_pubr()+
  labs(subtitle = "Feed: fish-dominant")+
  scale_x_continuous(limits = c(-0.1, 1))

```

FUTURE FEED: Nitrogen per tonne

```{r}

future_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/future/nitrogen_summary.qs")) |> 
  mutate(N_per_biomass_mean = total_N_mean/biomass_mean)

future_feed_mean_N <- future_point_df |> 
  dplyr::select(geometry, N_per_biomass_mean)

base_rast <- rast(res=1)

total_N_rast_future <- rasterize(x = future_feed_mean_N, y = base_rast, field = "N_per_biomass_mean", fun = mean)

total_N_rast_df_future <- terra::as.data.frame(x= total_N_rast_future, xy = TRUE)

#Map the per unit nitrogen

# max values to base legend off
total_N_rast_df_future |> pull(mean) |> max()

future_N_tonne <- 
  ggplot()+
  geom_tile(data = total_N_rast_df_future, aes(x = x, y = y, fill = mean))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
  theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: future"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,0.8))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

example_legend <- get_legend(future_N_tonne)

ggsave(filename = sprintf(here("explore/cottrell_explore/N_per_tonne_%s.jpg"), this_feed), dpi = 300, device = "jpg", width = 5, height =3)

#histogram of nitrogen per tonne

future_hist <- ggplot()+
  geom_histogram(data = future_point_df, aes(x = N_per_biomass_mean), fill = "firebrick4")+
  theme_pubr()+
  labs(subtitle = "Feed: novels-dominant")+
  scale_x_continuous(limits = c(-0.1, 1))

```

PLotting: Nitrogen per tonne

```{r}

# Maps of N per tonne
maps <- reference_N_tonne /
          past_N_tonne/
          future_N_tonne +
  plot_layout(ncol=1, 
              nrow = 3,
              guides = "collect") & 
  theme(legend.position = "bottom")

ggsave(filename = here("explore/cottrell_explore/N_per_tonne_all_feeds_maps.jpg"), dpi = 300, device = "jpg", width = 5, height =9)

hists <- reference_hist /
          past_hist/
          future_hist +
  plot_layout(ncol=1, 
              nrow = 3,
              guides = "collect") & 
  theme(legend.position = "bottom")

ggsave(filename = here("explore/cottrell_explore/N_per_tonne_all_feeds_hist.jpg"), dpi = 300, device = "jpg", width = 5, height =9)

```

REFERENCE FEED: Total nitrogen

```{r}

reference_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/reference/nitrogen_summary.qs"))

reference_feed_total_N <- reference_point_df |> dplyr::select(geometry, total_N_mean)

base_rast <- rast(res=1)

total_N_rast_ref <- rasterize(x = reference_feed_total_N, y = base_rast, field = "total_N_mean", fun = sum)

total_N_rast_df_ref <- terra::as.data.frame(x= total_N_rast_ref, xy = TRUE)

#max values to scale legend nby

total_N_rast_df_ref |> pull(sum) |> max()

# map nitrogen per tonne
reference_total_N <- ggplot()+
  geom_tile(data = total_N_rast_df_ref, aes(x = x, y = y, fill = sum))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
   theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: reference"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,10000))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

#histogram

reference_point_df |> pull(total_N_mean) |> max()

reference_hist <- ggplot()+
  geom_histogram(data = reference_point_df, aes(x = total_N_mean), fill = "darkgreen")+
  theme_pubr()+
  labs(subtitle = "Feed: plant-dominant")+
  scale_x_continuous(limits = c(0, 270))+
  geom_vline(xintercept = median(reference_point_df$total_N_mean), linetype = "dashed")

```

PAST FEED: Total nitrogen

```{r}

past_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/past/nitrogen_summary.qs"))

past_feed_total_N <- past_point_df |> 
  dplyr::select(geometry, total_N_mean)

base_rast <- rast(res=1)

total_N_rast_past <- rasterize(x = past_feed_total_N, y = base_rast, field = "total_N_mean", fun = sum)

total_N_rast_df_past <- terra::as.data.frame(x= total_N_rast_past, xy = TRUE)

#max value for legend 
total_N_rast_df_past |> pull(sum) |> max()

#map total nitrogen
past_total_N <- 
  ggplot()+
  geom_tile(data = total_N_rast_df_past, aes(x = x, y = y, fill = sum))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
   theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: past"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,10000))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

#histogram of nitrogen per tonne

past_point_df |> pull(total_N_mean) |> max()

past_hist <- ggplot()+
  geom_histogram(data = past_point_df, aes(x = total_N_mean), fill = "darkblue")+
  theme_pubr()+
  labs(subtitle = "Feed: fish-dominant")+
  scale_x_continuous(limits = c(0,270))+
  geom_vline(xintercept = median(past_point_df$total_N_mean), linetype = "dashed")

```

FUTURE FEED: Total nitrogen

```{r}

future_point_df<- qread(here("data/atlantic_salmon/data_products/model_summaries/future/nitrogen_summary.qs"))

future_feed_total_N <- future_point_df |> 
  dplyr::select(geometry, total_N_mean)

base_rast <- rast(res=1)

total_N_rast_future <- rasterize(x = future_feed_total_N, y = base_rast, field = "total_N_mean", fun = sum)

total_N_rast_df_future <- terra::as.data.frame(x= total_N_rast_future, xy = TRUE)

#Map the per unit nitrogen

# max values to base legend off
total_N_rast_df_future |> pull(sum) |> max()

future_total_N <- 
  ggplot()+
  geom_tile(data = total_N_rast_df_future, aes(x = x, y = y, fill = sum))+
  geom_sf(data = ne_countries(scale = "large", returnclass = "sf"), colour = NA, fill = "grey95")+
  theme_void()+
  theme(legend.position = "bottom", 
        legend.title = element_text(size=10))+
  labs(subtitle = paste("Feed: future"))+
  scale_fill_gradientn(colors = rev(brewer.pal(n = 9, name = "YlOrRd")), limits = c(0,10000))+
  guides(fill = guide_colorbar(height = 0.1, unit = "in"))

example_legend <- get_legend(future_N_tonne)

#histogram of nitrogen per tonne

future_point_df |> pull(total_N_mean) |> max()

future_hist <- ggplot()+
  geom_histogram(data = future_point_df, aes(x = total_N_mean), fill = "firebrick4")+
  theme_pubr()+
  labs(subtitle = "Feed: novels-dominant")+
  scale_x_continuous(limits = c(0,270))+
  geom_vline(xintercept = median(future_point_df$total_N_mean), linetype = "dashed")

```

```{r}

# Maps of N per tonne
maps <- reference_total_N /
          past_total_N/
          future_total_N +
  plot_layout(ncol=1, 
              nrow = 3,
              guides = "collect") & 
  theme(legend.position = "bottom")

ggsave(filename = here("explore/cottrell_explore/total_N_all_feeds_maps.jpg"), dpi = 300, device = "jpg", width = 5, height =9)

hists <- reference_hist /
          past_hist/
          future_hist +
  plot_layout(ncol=1, 
              nrow = 3,
              guides = "collect") & 
  theme(legend.position = "bottom")

ggsave(filename = here("explore/cottrell_explore/total_N_all_feeds_hist.jpg"), dpi = 300, device = "jpg", width = 5, height =9)

```

#SPECIES IMPACTS

```{r}

east_canada_sp_impact <- qread("data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs") |> filter(region == "East Canada") |> group_by(x,y) |> summarise(mean_impact = mean(impact, na.rm =TRUE))

ggplot()+
  geom_tile(data = east_canada_sp_impact, 
            aes(x = x, y = y, fill = mean_impact))+
  geom_sf(data = ne_countries(scale="medium", returnclass = "sf") |> st_crop(east_canada_bbox))+
  scale_fill_gradientn(colours = c("yellow", "orange", "red"))

ggsave("explore/cottrell_explore/east_canada_spp_impact.jpg", device= "jpg", dpi=300, width = 20, height = 10, units="cm")

west_canada_sp_impact <- qread("data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs") |> filter(region == "West Canada") |> group_by(x,y) |> summarise(mean_impact = mean(impact, na.rm =TRUE))

ggplot()+
  geom_tile(data = west_canada_sp_impact, 
            aes(x = x, y = y, fill = mean_impact))+
  geom_sf(data = ne_countries(scale="medium", returnclass = "sf") |> st_crop(west_canada_bbox))+
  scale_fill_gradientn(colours = c("yellow", "orange", "red"))

ggsave("explore/cottrell_explore/west_canada_spp_impact.jpg", device= "jpg", dpi=300, width = 15, height = 10, units="cm")

europe_iceland_sp_impact <- qread("data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs") |> filter(region == "Europe & Iceland") |> group_by(x,y) |> summarise(mean_impact = mean(impact, na.rm =TRUE))

ggplot()+
  geom_tile(data = europe_iceland_sp_impact, 
            aes(x = x, y = y, fill = mean_impact))+
  geom_sf(data = ne_countries(scale=50, returnclass = "sf", continent = "Europe") |> st_crop(europe_iceland_bbox), fill = "grey70")+
  scale_fill_gradientn(colours = c("yellow", "orange", "red"))

ggsave("explore/cottrell_explore/europe_iceland_spp_impact.jpg", device= "jpg", dpi=300, width = 17, height = 10, units="cm")

chile_sp_impact <- qread("data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs") |> filter(region == "Chile") |> group_by(x,y) |> summarise(mean_impact = mean(impact, na.rm =TRUE))

ggplot()+
  geom_tile(data = chile_sp_impact, 
            aes(x = x, y = y, fill = mean_impact))+
  geom_sf(data = ne_countries(scale=50, returnclass = "sf") |> st_crop(chile_bbox), fill = "grey70")+
  scale_fill_gradientn(colours = c("yellow", "orange", "red"))

ggsave("explore/cottrell_explore/chile_spp_impact.jpg", device= "jpg", dpi=300, width = 12, height = 16, units="cm")

aus_sp_impact <- qread("data/atlantic_salmon/data_products/spatial_summaries/all_regions.qs") |> filter(region == "Australia") |> group_by(x,y) |> summarise(mean_impact = mean(impact, na.rm =TRUE))

ggplot()+
  geom_tile(data = aus_sp_impact, 
            aes(x = x, y = y, fill = mean_impact))+
  geom_sf(data = ne_countries(scale=50, returnclass = "sf") |> st_crop(australia_bbox), fill = "grey70")+
  scale_fill_gradientn(colours = c("yellow", "orange", "red"))+
  theme_bw()

ggsave("explore/cottrell_explore/tas_spp_impact.jpg", device= "jpg", dpi=300, width = 17, height = 10, units="cm")

```

### 2025-05-04 00_model_functions.R

@@ -10,6 +10,7 @@ suppressPackageStartupMessages({
   library(readxl)
 })
 
+make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
 fixnum <- function(n, digits = 4) {str_flatten(c(rep("0", digits-nchar(as.character(n))), as.character(n)))}
 meanna <- function(x, ...) mean(x, na.rm = TRUE, ...)
 minna <- function(x, ...) min(x, na.rm = TRUE, ...)

### 2025-05-04 04_targets_individual.R

@@ -16,7 +16,7 @@ suppressMessages(suppressWarnings(suppressPackageStartupMessages({
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 10, seconds_idle = 10),
+  controller = crew_controller_local(workers = parallelly::availableCores()-2, seconds_idle = 10),
   workspace_on_error = TRUE
 )
 

### 2025-05-04 05_targets_farm.R

@@ -15,7 +15,7 @@ suppressMessages(suppressWarnings(suppressPackageStartupMessages({
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 8),
+  controller = crew_controller_local(workers = parallelly::availableCores()-2),
   workspace_on_error = TRUE
 )
 

### 2025-05-04 05_targets_individual.R

@@ -1,237 +1,0 @@
-suppressMessages(suppressWarnings(suppressPackageStartupMessages({
-  library(targets)
-  library(crew)
-  library(mirai)
-  library(arrow)
-  library(sf)
-  library(dplyr)
-  library(tidyr)
-  library(terra) # do not remove
-  library(magrittr)
-  library(conflicted)
-  library(units)
-  conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
-})))
-
-tar_option_set(
-  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
-  format = "qs", 
-  controller = crew_controller_local(workers = 15, seconds_idle = 10),
-  workspace_on_error = TRUE
-)
-
-tar_source("00_model_functions.R")
-
-# Paths -----------------------------------------------------------------------------------------------------------
-this_species <- "atlantic_salmon"
-this_path <- file.path("data", this_species)
-google_path <- "C:/Users/treimer/OneDrive - University of Tasmania/Sustainable Aquafeeds/Data from Google Drive"
-
-# Begin targets pipeline ------------------------------------------------------------------------------------------
-list(
-  tar_target(farm_data_file, "data/_general_data/SST/farm_SST_extracted.parquet", format = "file"),
-  tar_target(farm_coord_file, "data/_general_data/farm_locations/farm_coords.parquet", format = "file"),
-  tar_target(farms_to_omit_file, sprintf("data/_general_data/farm_locations/%s_farms_to_omit.qs", this_species), format = "file"),
-  tar_target(farms_to_omit, qs::qread(farms_to_omit_file)),
-  tar_target(
-    farm_IDs, 
-    farm_data_file %>% 
-      read_parquet() %>% 
-      filter(!farm_id %in% farms_to_omit) %>% 
-      distinct(farm_id) %>% 
-      # slice_sample(n = 272) %>% 
-      as.vector() %>% unlist() %>% unname()
-  ),
-  tar_target(
-    farm_ts_data, 
-    read_parquet(farm_data_file) %>% 
-      select(c(farm_id, day, temp_c)) %>% 
-      mutate(day = str_split_i(day, "day_", 2) %>% as.numeric()) %>% 
-      filter(farm_id == farm_IDs),
-    pattern = farm_IDs
-  ),
-  
[…]

### 2025-05-04 06_run_atlantic_salmon_model.R

@@ -193,153 +193,24 @@ uneat_ls %>% bind_rows() %>% write_parquet(file.path("data", "atlantic_salmon", 
 Sys.setenv(TAR_PROJECT = "project_farm")
 # tar_visnetwork()
 tar_validate()
-tar_prune()
+# tar_prune()
 upd <- tar_outdated(branches = F)
 tar_make(reporter = "balanced", seconds_meta_append = 300)
 
 overwrite <- T
 source("10_process_targets_outputs.R")
 
-# Analysis & plotting ---------------------------------------------------------------------------------------------
+# Analysis --------------------------------------------------------------------------------------------------------
 ## Harvest size ---------------------------------------------------------------------------------------------------
-pdata <- tar_read(farm_harvest_size, store = "04_targets_individual")
-write_parquet(pdata, file.path("data", "atlantic_salmon", "data_products", "harvest_size.parquet"))
+pdata <- tar_read(farm_harvest_size, store = "04_targets_individual") %>% 
+  write_parquet(file.path("data", "atlantic_salmon", "data_products", "harvest_size.parquet"))
+rm(pdata)
 
-## Previously processed data --------------------------------------------------------------------------------------
+## Combining previously processed data ----------------------------------------------------------------------------
 Sys.setenv(TAR_PROJECT = "project_farm")
-farm_IDs <- tar_read(farm_IDs)
-feed_types <- tar_read(feed_types)
-data_path_1 <- file.path(prod_path, "model_outputs_farm")
-data_path_2 <- file.path(prod_path, "model_outputs_cohort")
-dest_path_1 <- file.path(prod_path, "figures", "farms")
-dest_path_2 <- file.path(prod_path, "figures", "cohorts")
 
-make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
-
[…]

### 2025-05-04 06_targets_farm.R

@@ -1,220 +1,0 @@
-suppressMessages(suppressWarnings(suppressPackageStartupMessages({
-  library(targets)
-  library(crew)
-  library(mirai)
-  library(arrow)
-  library(sf)
-  library(dplyr)
-  library(tidyr)
-  library(terra) # do not remove
-  library(magrittr)
-  library(conflicted)
-  conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
-})))
-
-tar_option_set(
-  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "future", "furrr", "ggplot2", "matrixStats", "tibble"), 
-  format = "qs", 
-  controller = crew_controller_local(workers = 16, seconds_idle = 60),
-  workspace_on_error = TRUE
-)
-
-tar_source("00_model_functions.R")
-
-# Paths -----------------------------------------------------------------------------------------------------------
-gendata_path <- file.path("data", "_general_data")
-this_species <- "atlantic_salmon"
-species_path <- file.path("data", this_species)
-
-# Global objects --------------------------------------------------------------------------------------------------
-farm_harvest_size <- tar_read(farm_harvest_size, store = "_targets_individual") %>% 
-  select(c(farm_ID, weight))
-
-# Begin targets pipeline ------------------------------------------------------------------------------------------
-list(
-  tar_target(farm_data_file, file.path(gendata_path, "SST", "farm_SST_extracted.parquet"), format = "file"),
-  tar_target(farm_coord_file, file.path(gendata_path, "farm_locations", "farm_coords.parquet"), format = "file"),
-  tar_target(farms_to_omit_file, sprintf(file.path(gendata_path, "farm_locations", "%s_farms_to_omit.qs"), this_species), format = "file"),
-  tar_target(farms_to_omit, qs::qread(farms_to_omit_file)),
-  tar_target(
-    farm_IDs, 
-    farm_data_file %>% 
-      read_parquet() %>% 
-      filter(!farm_id %in% farms_to_omit) %>% 
-      distinct(farm_id) %>% 
-      # slice_sample(n = 350) %>%
-      as.vector() %>% unlist() %>% unname()
-  ),
-  tar_target(
-    farm_ts_data, 
-    read_parquet(farm_data_file) %>% 
[…]

### 2025-05-04 10_data_analysis.R

@@ -1,202 +1,0 @@
-# Setup -----------------------------------------------------------------------------------------------------------
-suppressPackageStartupMessages({
-  library(magrittr)
-  library(dplyr)
-  library(tidyr)
-  library(stringr)
-  library(terra)
-  library(qs)
-  library(here)
-  library(arrow)
-  library(units)
-  library(ggplot2)
-  library(sf)
-  library(rnaturalearth)
-  library(rnaturalearthdata)
-  library(conflicted)
-  library(furrr)
-  library(future)
-  conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
-})
-
-# This script aims to take the outputs from the model and answer specific questions 
-# Paths & globals -------------------------------------------------------------------------------------------------
-source("00_model_functions.R")
-
-coho_path <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohort")
-proc_path <- file.path("data", "atlantic_salmon", "data_products", "processed_data")
-
-# * Main point is the difference between feeds. 
-# * This should be expressed in t/t salmon, so farm biomass is also important.
-# * Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
-
-# Biomass produced ------------------------------------------------------------------------------------------------
-# How accurately is the model producing the correct biomass production levels?
-
-farm_info <- file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
-  qread() %>% 
-  filter(day == "day_1") %>% 
-  mutate(country = as.factor(country),
-         day = str_split_i(day, "_", 2) %>% as.integer()) %>% 
-  dplyr::select(-c(model_name, F_CODE, data_year, data_source, details, data_type_2, data_type, species_group, harvest_n, stocking_n, harvest_size_t, daily_mort_rate, day))
-
-hist(farm_info$tonnes_per_farm)
-
-coho_biom_fnms <- file.path(coho_path) %>% 
-  list.files(full.names = T) %>% 
[…]

### 2025-05-04 10_process_targets_outputs.R

@@ -5,11 +5,15 @@ library(tictoc)
 library(furrr)
 library(future)
 
-farm_IDs <- tar_read(farm_IDs)[1:10]
+source("00_model_functions.R")
+
+farm_IDs <- tar_read(farm_IDs)
 feed_types <- tar_read(feed_types)
 
 dest_path_farm <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_farm")
+if (!dir.exists(dest_path_farm)) {dir.create(dest_path_farm)}
 dest_path_cohort <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohort")
+if (!dir.exists(dest_path_cohort)) {dir.create(dest_path_cohort)}
 
 # Set up parallel processing
 plan(multisession, workers = parallel::detectCores() - 10)
@@ -32,20 +36,19 @@ process_farm <- function(fid) {
     
     walk(seq_along(stats), function(st) {
       if (overwrite == T | !file.exists(fnames_farms[st])) {
-        df <- list(
-          df_1[[st]] %>%
-            as.data.frame() %>%
-            rename(mean = V1, sd = V2) %>% 
-            mutate(feed = feed_types[1], days = 1:548),
-          df_2[[st]] %>%
-            as.data.frame() %>%
-            rename(mean = V1, sd = V2) %>% 
-            mutate(feed = feed_types[2], days = 1:548),
-          df_3[[st]] %>%
-            as.data.frame() %>%
-            rename(mean = V1, sd = V2) %>% 
-            mutate(feed = feed_types[3], days = 1:548)
-        ) %>% bind_rows() %>% 
+        df_11 <- df_1[[st]] %>%
+          as.data.frame() %>%
+          rename(mean = V1, sd = V2) %>% 
+          mutate(feed = feed_types[1], days = 1:548)
+        df_21 <- df_2[[st]] %>%
+          as.data.frame() %>%
+          rename(mean = V1, sd = V2) %>% 
+          mutate(feed = feed_types[2], days = 1:548)
+        df_31 <- df_3[[st]] %>%
+          as.data.frame() %>%
+          rename(mean = V1, sd = V2) %>% 
+          mutate(feed = feed_types[3], days = 1:548)
+        df <- rbind(df_11, df_21, df_31) %>% 
           relocate(days, .before = mean) %>% 
           mutate(farm_ID = farm_IDs[fid], 
[…]

### 2025-05-04 11_process_targets_outputs_2.R

@@ -1,0 +1,90 @@
+library(targets)
+library(dplyr)
+library(arrow)
+library(tictoc)
+library(furrr)
+library(future)
+
+source("00_model_functions.R")
+
+farm_IDs <- tar_read(farm_IDs)
+feed_types <- tar_read(feed_types)
+
+data_path_farm <- file.path(prod_path, "model_outputs_farm")
+data_path_cohort <- file.path(prod_path, "model_outputs_cohort")
+dest_path_farm <- file.path(prod_path, "processed_farm")
+if (!dir.exists(dest_path_farm)) {dir.create(dest_path_farm)}
+dest_path_cohort <- file.path(prod_path, "processed_cohort")
+if (!dir.exists(dest_path_cohort)) {dir.create(dest_path_cohort)}
+
+# Set up parallel processing
+plan(multisession, workers = parallel::detectCores() - 10)
+
+# Farm processing - not currently in use
+# farm_stats <- c("weight_stat", "biomass_stat", "dw_stat", "SGR_stat", "E_somat_stat", "P_excr_stat", "L_excr_stat", 
+#                 "C_excr_stat", "P_uneat_stat", "L_uneat_stat", "C_uneat_stat", "ing_act_stat", "anab_stat", 
+#                 "catab_stat", "NH4_stat", "O2_stat", "food_prov_stat", "rel_feeding_stat", "T_response_stat")
+# # List all the files output from targets processing
+# farm_files <- list()
+# for (s in seq_along(farm_stats)) {
+#   farm_files[[s]] <- list.files(data_path_farm, full.names = T) %>% 
+#     str_subset(farm_stats[s])
+# }
+# # Processing here?
+# rm(farm_files)
+
+# Cohorts processing ---------------------------------------------------------------------------------------------------
+cohort_files <- list.files(data_path_cohort, full.names = T)
+
+## Uneaten feed --------------------------------------------------------------------------------------------------------
+# Function to combine uneaten feed
+process_uneat <- function(fid) {
+  par_name <- file.path(dest_path_cohort, paste0("total_uneat_stat_", fixnum(farm_IDs[fid]), ".parquet"))
+  if (overwrite == T | !file.exists(par_name)) {
+    fnms <- cohort_files %>% 
+      str_subset(fixnum(farm_IDs[fid])) %>% 
+      str_subset("uneat")
+    
+    df <- list(
[…]

### 2025-05-04 12_data_analysis.R

@@ -1,0 +1,202 @@
+# Setup -----------------------------------------------------------------------------------------------------------
+suppressPackageStartupMessages({
+  library(magrittr)
+  library(dplyr)
+  library(tidyr)
+  library(stringr)
+  library(terra)
+  library(qs)
+  library(here)
+  library(arrow)
+  library(units)
+  library(ggplot2)
+  library(sf)
+  library(rnaturalearth)
+  library(rnaturalearthdata)
+  library(conflicted)
+  library(furrr)
+  library(future)
+  conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
+})
+
+# This script aims to take the outputs from the model and answer specific questions 
+# Paths & globals -------------------------------------------------------------------------------------------------
+source("00_model_functions.R")
+
+coho_path <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohort")
+proc_path <- file.path("data", "atlantic_salmon", "data_products", "processed_data")
+
+# * Main point is the difference between feeds. 
+# * This should be expressed in t/t salmon, so farm biomass is also important.
+# * Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
+
+# Biomass produced ------------------------------------------------------------------------------------------------
+# How accurately is the model producing the correct biomass production levels?
+
+farm_info <- file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
+  qread() %>% 
+  filter(day == "day_1") %>% 
+  mutate(country = as.factor(country),
+         day = str_split_i(day, "_", 2) %>% as.integer()) %>% 
+  dplyr::select(-c(model_name, F_CODE, data_year, data_source, details, data_type_2, data_type, species_group, harvest_n, stocking_n, harvest_size_t, daily_mort_rate, day))
+
+hist(farm_info$tonnes_per_farm)
+
+coho_biom_fnms <- file.path(coho_path) %>% 
+  list.files(full.names = T) %>% 
[…]

### 2025-05-16 08_manuscript/08_manuscript.qmd
New output structure in manuscript

@@
 library(ggplot2)
+library(ggh4x)
 library(here)
@@
 
+```{r global-variables}
+#| include: false
+#| eval: true
+
+source(here("00_model_functions.R"))
+
+# Input paths
+input_farm_coords_path <- here() %>% file.path("data", "_general_data", "farm_locations")
+input_farm_sst_path <- here() %>% file.path("data", "_general_data", "SST")
+input_species_param_path <- here() %>% file.path("data", "atlantic_salmon", "params")
+input_feed_profile_path <- here() %>% file.path("data", "_general_data", "diets")
+
+# Output paths
+output_farm_data_path <- here() %>% file.path("outputs", "farm_data")
+output_species_data_path <- here() %>% file.path("outputs", "species_data")
+output_sens_data_path <- here() %>% file.path("outputs", "sensitivity_data")
+output_farm_growth_data_path <- here() %>% file.path("outputs", "farm_growth_data")
+output_cohort_growth_data_path <- here() %>% file.path("outputs", "cohort_growth_data")
+
+# Filenames
+farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
+species_params_file <- file.path(output_species_data_path, "species_params.qs")
+pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
+feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
+sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
+sens_results_files <- file.path(output_sens_data_path) %>% str_subset("results")
+
+species_params <- qread(species_params_file)
+pop_params <- qread(pop_params_file)
+```
+
 # Introduction
+
+[This is a note create with the `aside` class.]{.aside}
 
@@
 
+```{r farm temperature data}
+farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
+farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
+farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread()
+farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
+  rename(farm_ID = farm_id)
+
+farm_temp_means <- farm_ts_data %>% 
+  group_by(farm_ID) %>% 
+  reframe(mean_temp = mean(temp_c)) %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  dplyr::filter(!farm_ID %in% farms_to_omit)
+
+overall_mean <- mean(farm_temp_means$mean_temp)
+overall_sd <- sd(farm_temp_means$mean_temp)
+```
+
+```{r fig-farm-mean-temps}
+#| fig-caption: Colours show farm site mean temperature
+
+worldmap <- ne_countries(scale = "medium", returnclass = "sf")
+farms_to_omit <- here() %>% 
+  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_farms_to_omit.qs") %>% 
+  qread()
+
+farms_w_temp_df <- here() %>% 
+  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
+  qread() %>% 
+  filter(!farm_id %in% farms_to_omit) %>% 
+  mutate(country = as.factor(country),
+         species_group = as.factor(species_group),
+         data_type = as.factor(data_type),
+         data_type_2 = as.factor(data_type_2),
+         model_name = as.factor(model_name),
+         F_CODE = as.factor(F_CODE),
+         day = str_split_i(day, "_", 2) %>% as.integer())
+
+farm_temp_means <- farms_w_temp_df %>% 
+  select(iso3c, country, farm_id, temp_c)
+farm_temp_means_1 <- farms_w_temp_df %>% 
+  filter(day == 1) %>% 
+  select(geometry)
+
+farm_temp_means <- farm_temp_means %>% 
+  group_by(iso3c, country, farm_id) %>% 
+  reframe(temp_c = meanna(temp_c))
+
+farm_temp_means <- cbind(farm_temp_means, farm_temp_means_1)
+
+ggplot(data = worldmap, aes(geometry = geometry)) +
+  geom_sf(fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(colour = temp_c), size = 1.5) +
+  coord_sf() +
+  theme_classic()
+
+  theme_classic() +
+  theme(legend.position = "bottom", legend.title = element_blank())
+```
+
 ## Model and approach
@@
 
-* Farms with mean temperature < 4$^\circ$ were excluded
+* Farms with a mean temperature of $\leq 6^\circ$C were excluded - a total of `r as.integer(length(farms_to_omit))` farms.
+
+[Need to put the cohort concept (and harvest timing) in here.]{.aside}
+
+```{r fig-cohorts}
+#| fig-cap: Example of cohorts
+
+fnms <- output_cohort_growth_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("biomass")
+
+df <- fnms[1] %>% read_parquet() %>% 
+  filter(feed == "reference") %>% 
+  mutate(mean = set_units(mean, "g") %>% set_units("t"),
+         sd = set_units(sd, "g") %>% set_units("t"))
+
+ggplot(df, aes(x = yday, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(linetype = "dotted", alpha = 0) +
+  scale_x_continuous(breaks = seq(0, 2000, 200)) +
+  labs(y = "Farm biomass", x = "Day of the year") +
+  theme_classic() +
+  theme(legend.position = "none", aspect.ratio = 0.75)
+
+yrs <- max(df$yday)/365
+harvests <- df %>% 
+  group_by(cohort) %>% 
+  reframe(mean = maxna(mean),
+          sd = maxna(sd))
+
+sum(harvests$mean)/yrs
+mean(harvests$sd)/yrs
+```
+
+### Feeding rate
+
+```{r fig-functional-response-to-temperature}
+#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
+
+df <- data.frame(water_temp = seq(-5, 26, 0.25))
+df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)
+df <- df %>% 
+mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * feeding,
+       food_prov = NA)
+for (i in 1:nrow(df)) {
+  df$food_prov[i] <- food_prov_rate(pop_params = pop_params, rel_feeding = df$feeding[i], ing_pot = df$ing_pot[i], 
+                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
+}
+df$ing_pot <- df$ing_pot/maxna(df$ing_pot)
+df$food_prov <- df$food_prov/maxna(df$ing_pot)
+
+df %>% 
+  ggplot(aes(x = water_temp, y = ing_pot)) +
+  geom_line(linewidth = 0.75) +
+  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
+  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
+  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
+  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
+  theme_classic() +
+  theme(text = element_text(colour = "black", family = "serif", size = 12))
+```
 
@@
 
-pop_params <- tar_read(pop_params, store = "../05_targets_farm")
-species_params <- tar_read(species_params, store = "../05_targets_farm")
-params <- c(pop_params, species_params)
-pnames <- names(params)
-sens_excr <- file.path("..", "data", "atlantic_salmon", "data_products", "excreted_parameter_sensitivity.parquet") %>%
-  read_parquet() %>%
-  mutate(adj_param = factor(adj_param, levels = rev(adj_param)))
+params <- file.path(output_species_data_path, "sens_params.qs") %>% qs::qread()
+
+param_names <- tibble::tribble(
+  ~name,        ~lab,
+  "alpha",      bquote(alpha),
+  "epsprot",    bquote(epsilon["P"]),
+  "epslip",     bquote(epsilon["L"]),
+  "epscarb",    bquote(epsilon["C"]),
+  "epsO2",      bquote(epsilon["O"[2]]),
+  "pk",         bquote("pk"),
+  "k0",         bquote("k"[0]),
+  "m",          bquote("m"),
+  "n",          bquote("n"),
+  "betac",      bquote(beta*"C"),
+  "Tma",        bquote("T"["max"]),
+  "Toa",        bquote("T"["opt"]),
+  "Taa",        bquote("T"["min"]),
+  "omega",      bquote(omega),
+  "a",          bquote("a"),
+  "k",          bquote("k"),
+  "eff",        bquote("eff"),
+  "meanW",      bquote(bar("W")),
+  "deltaW",     bquote(Delta*"W"), 
+  "meanImax",   bquote(bar("I"["max"])),
+  "deltaImax",  bquote(Delta*"I"["max"]),
+  "overFmean",  bquote(bar("F")),
+  "overFdelta", bquote(Delta*"F"),
+  "mortmyt",    bquote("mort")
+)
 ```
@@
 
-farm_harvest_size <- tar_read(farm_harvest_size, store = "../04_targets_individual")
-
-ggplot(farm_harvest_size, aes(x = weight/1000)) + 
-  geom_histogram(colour = "black", fill = "salmon", alpha = 0.5) + 
+file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
+  qread() %>% 
+  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
+  select(c(farm_ID, weight)) %>% 
+  ggplot(aes(x = weight)) +
+  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.5) +
+  scale_y_continuous(limits = c(0,500)) +
+  labs(y = "Frequency", x = "Harvest weight") +
   theme_classic() +
-  scale_x_continuous(breaks = seq(0, 8, 1), limits = c(1.25, 7.75)) + 
-  labs(y = "Frequency", x = "Individual weight (kg)")
+  theme(legend.position = "none", aspect.ratio = 0.75)
 ```

### 2025-05-16 08_manuscript/08_manuscript.qmd
Mean temperature display options

@@
 
+Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD)
+
 ```{r fig-farm-mean-temps}
-#| fig-caption: Colours show farm site mean temperature
+#| fig-cap: Options for showingf arm site mean temperatures.
+(Top left) Mean temperature by latitude across countries.
+(Top right) Distribution of mean temperatures by hemisphere.
+(Bottom) Global distribution of mean temperatures.
+#| fig-height: 6
+#| fig-width: 6
 
 worldmap <- ne_countries(scale = "medium", returnclass = "sf")
-farms_to_omit <- here() %>% 
-  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_farms_to_omit.qs") %>% 
-  qread()
 
-farms_w_temp_df <- here() %>% 
-  file.path("data", "_general_data", "farm_locations", "atlantic_salmon_locations_w_temps.qs") %>% 
-  qread() %>% 
-  filter(!farm_id %in% farms_to_omit) %>% 
-  mutate(country = as.factor(country),
-         species_group = as.factor(species_group),
-         data_type = as.factor(data_type),
-         data_type_2 = as.factor(data_type_2),
-         model_name = as.factor(model_name),
-         F_CODE = as.factor(F_CODE),
-         day = str_split_i(day, "_", 2) %>% as.integer())
-
-farm_temp_means <- farms_w_temp_df %>% 
-  select(iso3c, country, farm_id, temp_c)
-farm_temp_means_1 <- farms_w_temp_df %>% 
-  filter(day == 1) %>% 
-  select(geometry)
-
-farm_temp_means <- farm_temp_means %>% 
-  group_by(iso3c, country, farm_id) %>% 
-  reframe(temp_c = meanna(temp_c))
-
-farm_temp_means <- cbind(farm_temp_means, farm_temp_means_1)
-
-ggplot(data = worldmap, aes(geometry = geometry)) +
+p1 <- ggplot(data = worldmap, aes(geometry = geometry)) +
   geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = temp_c), size = 1.5) +
+  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
   coord_sf() +
@@
 
+p2 <- farm_temp_means %>% 
+  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
+  geom_point(size = 2.5) +
+  scale_colour_brewer(palette = "Set1") +
+  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
   theme_classic() +
-  theme(legend.position = "bottom", legend.title = element_blank())
+  theme(legend.position = "top", legend.title = element_blank())
+
+p3 <- farm_temp_means %>% 
+  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
+  ggplot(aes(x = mean_temp, fill = hemisphere)) +
+  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
+  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
+  theme_classic() +
+  theme(legend.position = "top", legend.title = element_blank())
+
+(p2 + p3) / p1 + plot_layout(heights = c(1, 1.5))
 ```

### 2025-05-16 08_manuscript/08_manuscript.qmd
Parameter name fixes

@@
 | $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2$^{-1}$ | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
-| $pk$ | `r unname(params['pk'])` | d$^{-1}$ | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
+| pk | `r unname(params['pk'])` | d$^{-1}$ | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
 | $k_0$ | `r unname(params['k0'])` | - | Fasting catabolism at 0 $^{^\circ}$C | @macnaughton_using_2019 |
-| $m$ | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| $n$ | `r unname(params['n'])` | - | Weight exponent for catabolism | @baldan_r_2018 |
+| m | `r unname(params['m'])` | - | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
+| n | `r unname(params['n'])` | - | Weight exponent for catabolism | @baldan_r_2018 |
 | $\beta C$ | `r unname(params['betac'])` | - | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C.
@@
 | $\omega$ | `r unname(params['omega'])` | g O2 / g | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
-| $a$ | `r unname(params['a'])` | J g tissue$^{-1}$ | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| $k$ | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| $eff$ | `r unname(params['eff'])` | - | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
+| a | `r unname(params['a'])` | J g tissue$^{-1}$ | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
+| k | `r unname(params['k'])` | - | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
+| eff | `r unname(params['eff'])` | - | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
 | $\overline{W}$ | `r unname(params['meanW'])` | g | Dry weight mean | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
@@
 | $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g$^{-1}$ fish day$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $mort$ | `r unname(params['mortmyt'])` | d$^{-1}$ | Natural mortality rate | @tvete_towards_2023 |
-: Growth parameters for Atlantic salmon {#tbl-params}
+| $\overline{F}$ | `r unname(params['overFmean'])` | g g$^{-1}$ fish$ | Overfeeding rate mean |    |
+| $\Delta{F}$ | `r unname(params['overFdelta'])` | g g$^{-1}$ fish$ | Overfeeding rate standard deviation |    |
+| mort | `r unname(params['mortmyt'])` | d$^{-1}$ | Natural mortality rate | @tvete_towards_2023 |
+: Model growth parameters for Atlantic salmon {#tbl-params}
 

### 2025-05-16 08_manuscript/08_manuscript.qmd
Nicer harvest size figure

@@
   ggplot(aes(x = weight)) +
-  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.5) +
+  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
   scale_y_continuous(limits = c(0,500)) +
@@
   theme_classic() +
-  theme(legend.position = "none", aspect.ratio = 0.75)
+  theme(
+    legend.position = "none", 
+    aspect.ratio = 0.75
+  )
 ```

### 2025-05-16 08_manuscript/08_manuscript.qmd
Parameter sensitivity section

@@
 
+### Testing parameter sensitivity
+
+Parameter sensitivity was tested by varying each parameter in Table @tbl-params by $\pm 10$% and calculating sensitivity as:
+
+$$
+S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}
+$$
+
+where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
+
+* All parameters in Table @tbl-params were tested across all farms (all temperatures)
+* Used a population of 100 in each farm
+
+```{r sensitivity data}
+sens_weight <- output_sens_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("results") %>% 
+  str_subset("weight") %>% 
+  qs::qread()
+
+sens_excr <- output_sens_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("results") %>% 
+  str_subset("total_excr") %>% 
+  qs::qread()
+
+sens_data <- rbind(sens_weight, sens_excr) %>% 
+  mutate(adj_param = factor(adj_param, levels = param_names$name))
+```
+
 Looking at @fig-param-sens-weight:
 
-* The most sensitive parameter by far is $m$ the weight exponent for anabolism, followed closely by $n$ the weight exponent for catabolism
+* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
 * These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
@@
 ```{r fig-param-sens-weight}
-#| fig-cap: Impact of varying each model parameter from 0.9-1.1 on total farm excreted nutrients over the whole production period.
+#| fig-cap: Impact of increasing each model parameter by 10% on final farm biomass (red) and total excreted nutrients (blue) over the whole production period.
 
-sens_excr %>% 
-  ggplot(aes(x = adj_param, y = sens, ymin = sens-sd, ymax = sens+sd)) +
-  geom_col(colour = "black", fill = "salmon", alpha = 0.5) +
-  geom_errorbar(width = 0.3) +
+sens_data %>% 
+  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
+  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
+  geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
   geom_hline(aes(yintercept = 0), linetype = "dashed") +
-  scale_y_continuous(breaks = seq(-20,30,5)) +
+  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
+  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
+  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
+  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
   labs(x = "Adjusted parameter", y = "Sensitivity") +
-  theme_classic() + theme(legend.position = "none", 
+  theme_classic() + 
+  theme(legend.position = "none", 
         strip.text = element_blank(), 
         aspect.ratio = 0.8,
-        text = element_text(size = 12)) +
+        text = element_text(size = 12),
+        axis.title.y = element_blank()) +
   coord_flip()

### 2025-05-27 06.1_run_individual.R
Data analysis start

@@ -25,7 +25,7 @@ conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
 # plan(multisession, workers = parallelly::availableCores()-1)
 
 # Basic configuration
-overwrite <- T
+overwrite <- F
 this_species <- "atlantic_salmon"
 
 # Directory structure
@@ -203,16 +203,18 @@ reference_feed <- feed_params[["reference"]]
 factors <- c(0.9, 1, 1.1)
 sens_params_names <- names(sens_all_params)
 
+Sys.setenv(TAR_PROJECT = "project_sensitivities")
 rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
 targets::tar_make(
-  store = "_targets_sensitivities",
-  script = "_targets_sensitivities.R",
   reporter = "balanced",
   callr_function = NULL
 )
 
 overwrite <- T
-sens_results <- tar_read(tar_sens_results, store = "_targets_sensitivities") %>% 
+sens_results <- rbind(
+  tar_read(tar_sens_results_spec),
+  tar_read(tar_sens_results_pop)
+  ) %>% 
   mutate(measure = as.factor(measure),
          adj_param = factor(adj_param, levels = sens_params_names))
 sens_measures <- levels(sens_results$measure)

### 2025-05-27 _targets_farmruns.R

@@ -1,0 +1,189 @@
+library(targets)
+library(crew)
+
+tar_option_set(
+  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
+  format = "qs", 
+  controller = crew_controller_local(workers = 16),
+  workspace_on_error = TRUE
+)
+
+# Helper function to process each matrix
+farm_to_cohort <- function(matrix, time_offset = 0) {
+  matrix %>% 
+    as.data.frame() %>% 
+    rename(t = V1, mean = V2, sd = V3) %>%
+    mutate(t = t + time_offset)
+}
+
+# Process each time period (current, +365 days, +730 days)
+combine_cohorts <- function(lst) {
+  bind_rows(farm_to_cohort(lst[[i]], 0),
+            farm_to_cohort(lst[[i]], 365),
+            farm_to_cohort(lst[[i]], 730))
+}
+
+list(
+# Prepare parameters ----------------------------------------------------------------------------------------------
+  tar_target(
+    tar_farm_IDs,
+    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) #%>% sample(500)
+  ),
+
+  tar_target(
+    tar_common_params, 
+    command = c(
+      't_start' = farm_coords$t_start[farm_coords$farm_ID == tar_farm_IDs],
+      't_end' = farm_coords$t_end[farm_coords$farm_ID == tar_farm_IDs],
+      'nruns' = 5000
+    ),
+    pattern = tar_farm_IDs
+  ),
+  
+  tar_target(
+    tar_farm_ts,
+    command = {
+      farm_ts_data %>%
+        dplyr::filter(farm_ID == tar_farm_IDs) %>%
+        dplyr::filter(between(day, tar_common_params['t_start'], tar_common_params['t_end']))
+    },
+    pattern = map(tar_farm_IDs, tar_common_params)
+  ),
+  
+  tar_target(
+    tar_static_data, 
+    file.path(input_farm_coords_path, str_c(this_species, "_locations_w_temps.qs")) %>% 
+      qs::qread() %>% 
+      distinct(farm_id, tonnes_per_farm) %>% 
+      mutate(tonnes_per_farm = tonnes_per_farm %>% units::set_units("t") %>% units::set_units("g") %>% units::drop_units())
+  ),
+  tar_target(
+    tar_harvest_size,
[…]

### 2025-05-27 08_manuscript/_manuscript/manuscript.qmd
MS to use new data

--- 2025-05-16 08_manuscript/08_manuscript.qmd
@@
 #   - Point 2
-bibliography: ["../resources/refs.bib", "../resources/manual-refs.bib"]
+bibliography: ["refs.bib", "manual-refs.bib"]
 
@@
     theme: simplex
-    css: ["../resources/extra.css"]
+    css: ["extra.css"]
     code-fold: true
@@
   #   template-partials:
-  #     - "../resources/title.tex"
+  #     - "title.tex"
   #   include-in-header:
-  #     file: "../resources/header_extra.tex"
+  #     file: "header_extra.tex"
 
@@
 #| include: false
+#| eval: true
 #| cache: false
-#| eval: true
+#| message: false
 
@@
 # This markdown uses TinyTex - install with tinytex::install_tinytex()
+
+install_unit("gfish")
+install_unit("kgfish", "1000 gfish")
+install_unit("tfish", "1000 kgfish")
 ```
@@
 output_cohort_growth_data_path <- here() %>% file.path("outputs", "cohort_growth_data")
+data_analysis_path <- here() %>% file.path("outputs", "data_analysis")
 
@@
 
+```{r farm info}
+#| code-summary: Get general farm info
+
+farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
+farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
+farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread() %>% 
+    mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N") %>% as.factor())
+
+farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
+  rename(farm_ID = farm_id)
+```
+
 ## Farm temperature forcings
@@
 ```{r farm temperature data}
-farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
-farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
-farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread()
-farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
-  rename(farm_ID = farm_id)
+#| code-summary: Get the farm temperature forcings
 
@@
 overall_sd <- sd(farm_temp_means$mean_temp)
+
+rm(farm_ts_data)
 ```
 
-Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD)
+Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD).
+Farms with a mean temperature of $\leq 6^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms).
+The total number of farms included in this analysis was therefore `r nrow(farm_temp_means)`.
 
 ```{r fig-farm-mean-temps}
-#| fig-cap: Options for showingf arm site mean temperatures.
-(Top left) Mean temperature by latitude across countries.
-(Top right) Distribution of mean temperatures by hemisphere.
-(Bottom) Global distribution of mean temperatures.
+#| fig-cap: |
+#|   Potential options for showing farm site mean temperatures.
+Top left: Mean temperature by latitude across countries.
+Top right: Frequency distribution of mean temperatures by hemisphere.
+Bottom: global distribution of mean temperatures.
 #| fig-height: 6
@@
 
-* Farms with a mean temperature of $\leq 6^\circ$C were excluded - a total of `r as.integer(length(farms_to_omit))` farms.
-
 [Need to put the cohort concept (and harvest timing) in here.]{.aside}
@@
 #| fig-cap: Example of cohorts
+#| eval: false
 
@@
 ```
+
+## Production parameters
+
+* Salmon cohorts were always grown for 548 days
+* Salmon cohorts were put out in annually Spring, on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` when farm latitude < 0 and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` when farm latitude > 0.
+* Cohorts were put out every year, such that there was an annual overlap of 183 days where one cohort was nearing harvest and another was being initialised.
 
@@
 
-Parameter sensitivity was tested by varying each parameter in Table @tbl-params by $\pm 10$% and calculating sensitivity as:
+Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as:
 
@@
   geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
-  geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
+  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
   geom_hline(aes(yintercept = 0), linetype = "dashed") +
@@
 
+## Biomass produced
+
+```{r biomass produced}
+#| fig-cap: Modelled vs observed salmon biomass produced
+
+coho_biom <- qs::qread(file.path(data_analysis_path, "biomass_produced_comparison.qs"))
+
+coho_biom %>% 
+  ggplot(aes(x = tonnes_per_farm, y = mean, colour = country)) +
+  geom_point(size = 2.5) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+  theme_classic() +
+  scale_x_continuous(limits = c(0,1700)) +
+  scale_y_continuous(limits = c(0,1700)) +
+  scale_colour_brewer(palette = "Set1") +
+  labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
+  theme_classic() +
+  theme(legend.position = "top", legend.title = element_blank())
+```
+
 ## Species vulnerability layers
@@
 
-* Main point is the difference between feeds. 
-* This should be expressed in t/t salmon, so farm biomass is also important.
+* Main point is the difference between feeds (kg/t salmon).
 * Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
 
-# Biomass produced
+## Excreted faeces
 
-```{r biomass produced}
-fnms <- farm_outputs %>% 
-  list.files(full.names = T) %>% 
-  str_subset("biomass")
+```{r excreted faeces data}
+#| code-summary: Load and prep all excretion data
 
-dfs <- list()
-for (fid in seq_along(fnms)) {
-  dfs[[fid]] <- fnms[fid] %>% 
-    read_parquet() %>% 
-    filter(days == max(days)) %>% 
-    mutate(mean = mean %>% set_units("g") %>% set_units("t"),
-           sd = sd %>% set_units("g") %>% set_units("t"))
-}
-df <- bind_rows(dfs)
-df_mean <- df %>% 
-  select(-c(days, sd)) %>% 
-  pivot_wider(names_from = feed, values_from = mean) %>% 
-  mutate(future_diff = (future - reference)/reference,
-         past_diff = (past - reference)/reference) %>% 
-  select(-c(reference, past, future)) %>% 
-  pivot_longer(names_to = "feed", values_to = "mean", cols = c(future_diff, past_diff))
-df_sd <- df %>% 
-  select(-c(days, mean)) %>% 
-  pivot_wider(names_from = feed, values_from = sd) %>% 
-  mutate(future_diff = (future - reference)/reference,
-         past_diff = (past - reference)/reference) %>% 
-  select(-c(reference, past, future)) %>% 
-  pivot_longer(names_to = "feed", values_to = "sd", cols = c(future_diff, past_diff))
-df <- merge(df_mean, df_sd, by = c("farm_ID", "feed"))
+fnms <- farmrun_reference_files <- file.path(output_cohort_growth_data_path) %>% 
+  list.files(full.names = T)
+
+# qs::qread(fnms[1]) %>% names()
+weight <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["weight_stat"]]})
+biomass <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["biomass_stat"]]})
+
+# The following reads in all the total excretion data, pairs it with the farm coordinates, and converts the mean and sd values into values/biomass
+excr_total <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["total_excr_stat"]]}) %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  mutate(sd.x = sd.x/mean.x,
+         sd.y = sd.x/mean.y,
+         mean.x = set_units(mean.x, "g d-1"),
+         mean.y = set_units(mean.y, "gfish"),
+         mean = mean.x/mean.y,
+         sd_pc = sqrt(sd.x^2+sd.y^2),
+         sd = sd_pc * mean,
+         prod_day = case_when(hemisphere == "S" ~ t-(274+365)+1, T ~ t-(121+365)+1)) %>% 
+  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
+
+excr_P <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["P_excr_stat"]]}) %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  mutate(sd.x = sd.x/mean.x,
+         sd.y = sd.x/mean.y,
+         mean.x = set_units(mean.x, "g d-1"),
+         mean.y = set_units(mean.y, "gfish"),
+         mean = mean.x/mean.y,
+         sd_pc = sqrt(sd.x^2+sd.y^2),
+         sd = sd_pc * mean) %>% 
+  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
+
+excr_L <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["L_excr_stat"]]}) %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  mutate(sd.x = sd.x/mean.x,
+         sd.y = sd.x/mean.y,
+         mean.x = set_units(mean.x, "g d-1"),
+         mean.y = set_units(mean.y, "gfish"),
+         mean = mean.x/mean.y,
+         sd_pc = sqrt(sd.x^2+sd.y^2),
+         sd = sd_pc * mean) %>% 
+  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
+
+excr_C <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["C_excr_stat"]]}) %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  mutate(sd.x = sd.x/mean.x,
+         sd.y = sd.x/mean.y,
+         mean.x = set_units(mean.x, "g d-1"),
+         mean.y = set_units(mean.y, "gfish"),
+         mean = mean.x/mean.y,
+         sd_pc = sqrt(sd.x^2+sd.y^2),
+         sd = sd_pc * mean) %>% 
+  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
 ```
 
-# Locations
+### Total amount
+
+```{r fig-total-excr-diff_perc, class.chunk = "aside"}
+#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.
+
+df <- excr_total %>% 
+  select(-c(sd, sd_pc)) %>% 
+  pivot_wider(names_from = "feed", values_from = "mean") %>% 
+  mutate(past = past-reference,
+         future = future-reference) %>% 
+  pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
+  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
+         diff_perc = drop_units(diff/reference))
+
+summ <- df %>%
+  group_by(hemisphere, feed) %>% 
+  reframe(mean = 100*meanna(diff_perc) %>% round(3),
+          min = 100*meanna(diff_perc) %>% round(3),
+          max = 100*maxna(diff_perc) %>% round(3))
+
+df %>% 
+  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
+  geom_point() + 
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  facet_grid(~feed) +
+  theme_classic()
+```
+
+There was very little variation in the percentage difference (from reference) excreted with increasing overall excretion (@fig-total-excr-diff_perc), or through time (@fig-total-excr-diff_perc_2). 
+The difference in total excretion for the past feed ranged from 
+`r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
+`r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%.
+
+```{r fig-total-excr-diff_perc_2, class.chunk = "aside"}
+#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.
+
+df %>% 
+  group_by(prod_day, feed, hemisphere) %>% 
+  reframe(diff_perc_mean = meanna(diff_perc),
+          diff_perc_sd = sdna(diff_perc)) %>% 
+  ggplot(aes(x = prod_day, y = diff_perc_mean, ymin = diff_perc_mean-diff_perc_sd, ymax = diff_perc_mean+diff_perc_sd, 
+             colour = as.factor(hemisphere), fill = as.factor(hemisphere))) +
+  geom_line() + 
+  geom_ribbon(alpha = 0.25) +
+  geom_hline(yintercept = 0, linetype = "dashed") +
+  facet_grid(~feed) +
+  theme_classic()
+```
+
+However, the actual difference in excreted faeces varied by feed, time in the production cycle, and location of the farm [@fig-total-excr-act_diff].
+
+```{r fig-total-excr-act_diff}
+#| fig-width: 6.25
+#| fig-height: 5.25
+#| fig-cap: Mean actual difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.
+
+df <- excr_total %>% 
+  select(-c(sd, sd_pc)) %>% 
+  pivot_wider(names_from = "feed", values_from = "mean") %>% 
+  mutate(past = past-reference,
+         future = future-reference) %>% 
+  pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
+  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
+         diff = set_units(diff, "kg tfish-1 d-1"))
+
+summ <- df %>%
+  group_by(hemisphere, feed) %>% 
+  reframe(mean = meanna(diff) %>% round(3),
+          min = meanna(diff) %>% round(3),
+          max = maxna(diff) %>% round(3))
+
+df %>% 
+  group_by(hemisphere, feed, prod_day) %>% 
+  reframe(mean_diff = meanna(diff),
+          sd_diff = sdna(diff) %>% set_units("kg tfish-1 d-1")) %>% 
+  ggplot(aes(x = prod_day, y = mean_diff, ymin = mean_diff-sd_diff, ymax = mean_diff+sd_diff, colour = hemisphere, fill = hemisphere)) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(alpha = 0.25) +
+  facet_wrap(~feed) +
+  theme_classic()
+```
+
+## Uneaten feed (amount & composition)
+
+## Total nutrients (amount & source)
+
+```{r patchwork map}
+worldmap <- ne_countries(scale = "large", returnclass = "sf")
+
+AUS_bounds <- c(144, 149.5, -39.75, -44)
+CAN1_bounds <- c(-132, -122, 47.75, 54.25)
+CAN2_bounds <- c(-70, -54, 43, 48.5)
+CHI_bounds <- c(-77.5, -62.5, -56, -25)
+EUR_bounds <- c(-26, 30, 51, 71)
+
+p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
+  geom_sf(fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
+  coord_sf() +
+  theme_classic()
+
+no_margins <- function() {
+  theme(legend.position = "none", 
+        plot.margin = margin(),
+        axis.title = element_blank())
+}
+
+p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
+p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
+p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
+p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
+p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()
+
+subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
+finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
+  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
+  theme(plot.margin = margin(0, 0, 0, 0))
+finalplot
+```
 
@@
 
-All analysis was conducted in R version `r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+Major packages used include terra [@terra], targets [@targets], future [@future], furrr [@furrr], and the tidyverse [@tidyverse].
 For a full list of R packages used see the lockfile on [Github](https://www.github.com).

### 2025-05-30 06.0_run_atlantic_salmon_model.R
Progress - possible switch to Nectar for pipeline

@@ -36,15 +36,15 @@ source("04_extracting_temperatures.R")
 ## Individuals ----------------------------------------------------------------------------------------------------
 source("06.1_run_individual.R")
 
+### Harvest size ---------------------------------------------------------------------------------------------------
+tar_read(farm_harvest_size, store = "04_targets_individual") %>% 
+  write_parquet(file.path("data", "atlantic_salmon", "data_products", "harvest_size.parquet"))
+
 ## Farm growth ----------------------------------------------------------------------------------------------------
 source("06.2_run_farms.R")
 
 # source("10_process_targets_outputs.R")
 # Analysis --------------------------------------------------------------------------------------------------------
-## Harvest size ---------------------------------------------------------------------------------------------------
-pdata <- tar_read(farm_harvest_size, store = "04_targets_individual") %>% 
-  write_parquet(file.path("data", "atlantic_salmon", "data_products", "harvest_size.parquet"))
-rm(pdata)
 
 ## Combining previously processed data ----------------------------------------------------------------------------
 Sys.setenv(TAR_PROJECT = "project_farm")

### 2025-05-30 06.2_run_farms.R

@@ -116,7 +116,6 @@ stat_names <- c("weight_stat", "dw_stat", "water_temp_stat", "T_response_stat", 
 Sys.setenv(TAR_PROJECT = "project_farmruns")
 rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
 targets::tar_make(
-  names = contains("farmrun"), 
   reporter = "balanced",
   callr_function = NULL,
   seconds_meta_append = 90

### 2025-05-30 _targets_farmruns.R

@@ -4,7 +4,7 @@ library(crew)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 16),
+  controller = crew_controller_local(workers = 10),
   workspace_on_error = TRUE
 )
 
@@ -27,7 +27,7 @@ list(
 # Prepare parameters ----------------------------------------------------------------------------------------------
   tar_target(
     tar_farm_IDs,
-    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) #%>% sample(500)
+    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) #%>% sample(750)
   ),
 
   tar_target(

### 2025-05-30 _targets_sensitivities.R

@@ -5,7 +5,7 @@ library(parallelly)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 10),
+  controller = crew_controller_local(workers = 16),
   workspace_on_error = TRUE
 )
 
@@ -19,8 +19,7 @@ list(
   tar_target(tar_param_names_pop, c("meanW", "deltaW", "meanImax", "deltaImax", "overFmean", "overFdelta")),
   tar_target(
     tar_param_names_spec,
-    sens_params_names[!sens_params_names %in% tar_param_names_pop] %>% 
-    sample(4)
+    sens_params_names[!sens_params_names %in% tar_param_names_pop]
   ),
   
   tar_target(

### 2025-06-04 _manuscript.qmd
Move manuscript files to root for deployment

--- 2025-05-27 08_manuscript/_manuscript/manuscript.qmd
@@
     fig.align: center
+    fig.width: 8.5
 
@@
 library(rnaturalearthdata)
+library(rnaturalearthhires)
 library(dtplyr)
@@
 library(lubridate)
+library(RColorBrewer)
 conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
@@
 #| include: false
-#| eval: true
 
@@
 
-[This is a note create with the `aside` class.]{.aside}
+[This intro is copied verbatim from work done during one of the early workshops.]{.aside}
 
@@
 # Methods
+## Model and approach
+
+[Unfinished.
+Need to work out how much should be transposed from @baldan_r_2018.
+One thing that definitely needs to be stated is the individual ingredient (rather than whole food) tracking, the use of cohorts, and the new method for calculating population.]{.aside}
+
+We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
+The model simulates growth at an individual level, calculating the change in individual weight through time using:
+
+$$
+\frac{dw}{dt} = \frac{A-C}{\epsilon}
+$$
+
+Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
+Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
+Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
+All individuals have a fixed mortality rate to simulate stocking and harvesting.
+
+## Farm temperature forcings
 
@@
   rename(farm_ID = farm_id)
+
+sorted_countries <- farm_coords %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  group_by(country) %>% 
+  reframe(av_lat = mean(lat)) %>% 
+  arrange(-av_lat) %>% 
+  pull(country) %>% 
+  unique()
 ```
-
-## Farm temperature forcings
 
@@
 Bottom: global distribution of mean temperatures.
-#| fig-height: 6
-#| fig-width: 6
+#| fig-height: 9
+#| fig-width: 9.5
 
@@
   ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
-  geom_point(size = 2.5) +
+  geom_point(size = 2) +
   scale_colour_brewer(palette = "Set1") +
@@
 ```
-
-## Model and approach
-
-We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
-The model simulates growth at an individual level, calculating the change in individual weight through time using:
-
-$$
-\frac{dw}{dt} = \frac{A-C}{\epsilon}
-$$
-
-Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
-Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
-Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
-All individuals have a fixed mortality rate to simulate stocking and harvesting.
 
@@
 
+To detail here:
+
+* Functional response to temperature (species-specific)
+* Overfeeding parameters and how they come into play
+* Deminstration of how feeding response and actual food given vary with temperature?
+
 ```{r fig-functional-response-to-temperature}
+#| eval: false
 #| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
@@
 * Salmon cohorts were always grown for 548 days
-* Salmon cohorts were put out in annually Spring, on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` when farm latitude < 0 and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` when farm latitude > 0.
-* Cohorts were put out every year, such that there was an annual overlap of 183 days where one cohort was nearing harvest and another was being initialised.
+* Salmon cohorts were initialised Spring.
+This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
+* Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
 
@@
 
-Table @tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
+tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
 
@@
 
-### Testing parameter sensitivity
+### Parameter sensitivity
 
@@
 
+## Modelled experimental feeds {#sec-feeds}
+
+```{r feeds}
+feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
+feed_params <- file.path(output_species_data_path, "feed_params.qs") %>% qs::qread()
+
+df <- feed_params[["reference"]]
+contribP_1 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
+tP_1 <- sum(contribP_1)
+digestP_1 <- sum(df[["Proteins"]]$digest * contribP_1)/tP_1
+
+contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
+tL_1 <- sum(contribL_1)
+digestL <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1
+
+contribC_1 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
+tC_1 <- sum(contribC_1)
+digestC_1 <- sum(df[["Carbohydrates"]]$digest * contribC_1)/tC_1
+
+df <- feed_params[["past"]]
+contribP_2 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
+tP_2 <- sum(contribP_2)
+digestP_2 <- sum(df[["Proteins"]]$digest * contribP_2)/tP_2
+
+contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
+tL_2 <- sum(contribL_2)
+digestL <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2
+
+contribC_2 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
+tC_2 <- sum(contribC_2)
+digestC_2 <- sum(df[["Carbohydrates"]]$digest * contribC_2)/tC_2
+
+df <- feed_params[["future"]]
+contribP_3 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
+tP_3 <- sum(contribP_3)
+digestP_3 <- sum(df[["Proteins"]]$digest * contribP_3)/tP_3
+
+contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
+tL_3 <- sum(contribL_3)
+digestL <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3
+
+contribC_3 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
+tC_3 <- sum(contribC_3)
+digestC_3 <- sum(df[["Carbohydrates"]]$digest * contribC_3)/tC_3
+```
+
+[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed]{.aside}
+
+* Feed came from [@cottrell_origins_nodate; @cottrell_global_2020]
+* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
+* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
+* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
+* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
+* Within the reference feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
+* Within the reference feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
+
 ## Population and biomass estimates
 
-New method is to take the average predicted individual harvest size for each farm, then working backwards with the standard mortality rate to generate a population for each farm that will produce the correct tonnage for each farm.
-@fig-harvest-size shows the  average individual harvest size at each farm as predicted by the fish-growth model, which was used to create the population inputs for the farm-level growth curves.
+```{r pop-biom-data}
+coho_biom <- file.path(data_analysis_path, "biomass_produced_comparison.qs") %>% 
+  qs::qread()
+harv_size <- file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
+  qread()
 
-```{r fig-harvest-size}
+coho_biom_summ <- coho_biom %>% 
+  mutate(perc_diff = 100*(mean - tonnes_per_farm)/tonnes_per_farm)
+```
+
+Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed).
+A population timeseries was the generated using the standard mortality rate (`r unname(params['mortmyt'])` d$^{-1}$).
+Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.
+
+@fig-harvest-size shows the distribution of average individual harvest sizes across farms used to create the population timeseries as predicted by the fish-growth model.
+
+```{r fig-harvest-size, class.chunk = "aside"}
 #| fig-cap: Frequency distribution of harvest sizes across global farms, as predicted by the fish growth model
 
-file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
-  qread() %>% 
+harv_size %>% 
   mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
@@
 
-This means that the population estimates aren't actual fish numbers, they're just a method that allows each farm location to approximate of the correct tonnage produced while to allowing comparisons between the different feeds.
+By this method, farm biomass as predicted by the model slightly overestimated farm tonnage.
+Predicted farm biomass was `r round(min(coho_biom_summ$perc_diff),1)`-`r round(max(coho_biom_summ$perc_diff),1)` higher than tonnage produced (@fig-biomass-produced).
+This variation was not correlated with mean farm temperature or total tonnage produced (@fig-biomass-variation).
 
-## Biomass produced
+```{r fig-biomass-variation, class.chunk = "aside"}
+plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
+plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
+```
 
-```{r biomass produced}
+```{r fig-biomass-produced, class.chunk = "aside"}
 #| fig-cap: Modelled vs observed salmon biomass produced
-
-coho_biom <- qs::qread(file.path(data_analysis_path, "biomass_produced_comparison.qs"))
 
@@
 
-## Species vulnerability layers
+## Impacts of nutrient input
+
+*To detail here:*
+
+* How to convert feed and uneaten faeces into nutrients - just nitrogen?
+Carbon too?
+If just nitrogen, then can probably use the standard N = 6.25 x protein conversion to compare the feeds (lipids and carbohydrates have negligible protein).
+If doing carbon too, will need to find conversion rates for all of them, possibly splitting carbs/lipids into complex/simple, saturated/unsaturated, etc.
+* Source of species vulnerability layers
 
@@
 
+```{r weight and biomass data}
+farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
+  list.files(full.names = T)
+
+qs::qread(farmrun_files[1]) %>% names()
+weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
+biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
+```
+
+## Uneaten feed
+
+```{r uneaten feed data}
+#| code-summary: Load and prep uneaten feed data
+
+uneaten_total <- farmrun_files %>% 
+  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
+  bind_rows() %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  rename(uneat_mean = mean.x, biomass_mean = mean.y,
+         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
+  mutate(uneat_sd = uneat_sd/uneat_mean,
+         biomass_sd = biomass_sd/biomass_mean,
+         uneat_biom_mean = uneat_mean/biomass_mean,
+         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
+
+uneaten_total_stats <- uneaten_total %>% 
+  group_by(feed, farm_ID) %>% 
+  reframe(total = sum(uneat_biom_mean)) %>% 
+  group_by(feed) %>% 
+  reframe(min = minna(total),
+          max = maxna(total),
+          mean = meanna(total)) %>% 
+  mutate(min = min %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
+         max = max %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
+         mean = mean %>% set_units("g gfish-1") %>% set_units("g kgfish-1")) %>% 
+  mutate(min = round(min,2),
+         max = round(max,2),
+         mean = round(mean,2))
+```
+
+### Amount
+
+* Total reference uneaten feed across a cohort (548 days) ranged from `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]`.
+* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
+`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from
+`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`).
+* @fig-total-uneaten-perday shows the range of total uneaten feed per day across countries.
+
+```{r fig-total-uneaten-perday}
+#| fig-width: 9.5
+
+uneaten_total %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g gfish-1 d-1") %>% set_units("g kgfish-1 d-1"),
+         country = factor(country, levels = sorted_countries)) %>% 
+  ggplot(aes(x = country, y = uneat_biom_mean, fill = feed)) +
+  geom_boxplot() +
+  theme_classic() +
+  scale_fill_manual(values = feed_pal) +
+  labs(y = "Uneaten feed", x = "Country")
+```
+
+```{r uneaten composition}
+#| eval: false
+
+uneaten_P <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["P_uneat_stat"]]}) %>% bind_rows()
+uneaten_L <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["L_uneat_stat"]]}) %>% bind_rows()
+uneaten_C <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["C_uneat_stat"]]}) %>% bind_rows()
+
+uneaten_all <- uneaten_total %>% 
+  select(-contains("biom")) %>% 
+  merge(uneaten_P, by = c("farm_ID", "feed", "t")) %>% 
+  merge(uneaten_L, by = c("farm_ID", "feed", "t")) %>% 
+  merge(uneaten_C, by = c("farm_ID", "feed", "t")) %>% 
+  select(-c(contains("sd")))
+```
+
+* The composition of the uneaten feed is (obviously) the same as the total feed composition (@sec-feeds).
+
 ## Excreted faeces
@@
 
-fnms <- farmrun_reference_files <- file.path(output_cohort_growth_data_path) %>% 
-  list.files(full.names = T)
+# The following reads in all the total excretion data and converts the mean and sd values into values/biomass
+excreted_total <- farmrun_files %>% 
+  purrr::map(function(f) {qs::qread(f)[["total_excr_stat"]]}) %>% 
+  bind_rows() %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  rename(excr_mean = mean.x, biomass_mean = mean.y,
+         excr_sd = sd.x, biomass_sd = sd.y) %>% 
+  mutate(excr_sd = excr_sd/excr_mean,
+         biomass_sd = biomass_sd/biomass_mean,
+         excr_biom_mean = excr_mean/biomass_mean,
+         excr_biom_sd = sqrt(excr_sd^2+biomass_sd^2)*excr_biom_mean)
 
-# qs::qread(fnms[1]) %>% names()
-weight <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["weight_stat"]]})
-biomass <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["biomass_stat"]]})
-
-# The following reads in all the total excretion data, pairs it with the farm coordinates, and converts the mean and sd values into values/biomass
-excr_total <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["total_excr_stat"]]}) %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  mutate(sd.x = sd.x/mean.x,
-         sd.y = sd.x/mean.y,
-         mean.x = set_units(mean.x, "g d-1"),
-         mean.y = set_units(mean.y, "gfish"),
-         mean = mean.x/mean.y,
-         sd_pc = sqrt(sd.x^2+sd.y^2),
-         sd = sd_pc * mean,
-         prod_day = case_when(hemisphere == "S" ~ t-(274+365)+1, T ~ t-(121+365)+1)) %>% 
-  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
-
-excr_P <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["P_excr_stat"]]}) %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  mutate(sd.x = sd.x/mean.x,
-         sd.y = sd.x/mean.y,
-         mean.x = set_units(mean.x, "g d-1"),
-         mean.y = set_units(mean.y, "gfish"),
-         mean = mean.x/mean.y,
-         sd_pc = sqrt(sd.x^2+sd.y^2),
-         sd = sd_pc * mean) %>% 
-  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
-
-excr_L <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["L_excr_stat"]]}) %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  mutate(sd.x = sd.x/mean.x,
-         sd.y = sd.x/mean.y,
-         mean.x = set_units(mean.x, "g d-1"),
-         mean.y = set_units(mean.y, "gfish"),
-         mean = mean.x/mean.y,
-         sd_pc = sqrt(sd.x^2+sd.y^2),
-         sd = sd_pc * mean) %>% 
-  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
-
-excr_C <- purrr::map_dfr(fnms, function(fnm) {qs::qread(fnm)[["C_excr_stat"]]}) %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  mutate(sd.x = sd.x/mean.x,
-         sd.y = sd.x/mean.y,
-         mean.x = set_units(mean.x, "g d-1"),
-         mean.y = set_units(mean.y, "gfish"),
-         mean = mean.x/mean.y,
-         sd_pc = sqrt(sd.x^2+sd.y^2),
-         sd = sd_pc * mean) %>% 
-  select(-c(t_start, t_end, mean.x, mean.y, sd.x, sd.y))
+excreted_total_stats <- excreted_total %>% 
+  group_by(feed, farm_ID) %>% 
+  reframe(total = sum(excr_biom_mean)) %>% 
+  group_by(feed) %>% 
+  reframe(min = minna(total),
+          max = maxna(total),
+          mean = meanna(total)) %>% 
+  mutate(min = min %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
+         max = max %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
+         mean = mean %>% set_units("g gfish-1") %>% set_units("g kgfish-1")) %>% 
+  mutate(min = round(min,2),
+         max = round(max,2),
+         mean = round(mean,2))
 ```
 
-### Total amount
+* Total reference excreted faeces across a cohort (548 days) ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
+* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
+`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$) while uneaten future feed ranged from
+`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$).
+* @fig-total-excreted-perday shows the range of total excreted faeces per day across countries.
+
+```{r fig-total-excreted-perday}
+#| fig-width: 9
+
+excreted_total %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  mutate(excr_biom_mean = excr_biom_mean %>% set_units("g gfish-1 d-1") %>% set_units("g kgfish-1 d-1"),
+         country = factor(country, levels = sorted_countries)) %>% 
+  ggplot(aes(x = country, y = excr_biom_mean, fill = feed)) +
+  geom_boxplot() +
+  theme_classic() +
+  scale_fill_manual(values = feed_pal) +
+  labs(y = "Excreted faeces", x = "Country")
+```
+
+### Amount
 
@@
 
-df <- excr_total %>% 
-  select(-c(sd, sd_pc)) %>% 
-  pivot_wider(names_from = "feed", values_from = "mean") %>% 
+df <- excreted_total %>% 
+  select(-contains(c("sd", "biom"))) %>% 
+  pivot_wider(names_from = "feed", values_from = "excr_mean") %>% 
   mutate(past = past-reference,
@@
   mutate(reference = set_units(reference, "g kgfish-1 d-1"),
-         diff_perc = drop_units(diff/reference))
+         diff_perc = drop_units(diff/reference)) %>% 
+    merge(farm_coords, by = "farm_ID") %>% 
+  mutate(prod_day = t - t_start + 1)
 
@@
 
-df <- excr_total %>% 
-  select(-c(sd, sd_pc)) %>% 
-  pivot_wider(names_from = "feed", values_from = "mean") %>% 
+df <- excreted_total %>% 
+  select(-contains(c("sd", "excr_mean", "biomass"))) %>% 
+  pivot_wider(names_from = "feed", values_from = "excr_biom_mean") %>% 
   mutate(past = past-reference,
@@
   mutate(reference = set_units(reference, "g kgfish-1 d-1"),
-         diff = set_units(diff, "kg tfish-1 d-1"))
+         diff = set_units(diff, "kg tfish-1 d-1")) %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  mutate(prod_day = t-t_start+1)
 
@@
 
-## Uneaten feed (amount & composition)
+### Composition
+
+```{r excreted composition}
+#| eval: true
+
+excreted_P <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["P_excr_stat"]]}) %>% bind_rows()
+excreted_L <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["L_excr_stat"]]}) %>% bind_rows()
+excreted_C <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["C_excr_stat"]]}) %>% bind_rows()
+
+excreted_all <- excreted_total %>% 
+  select(-contains("biom")) %>% 
+  merge(excreted_P, by = c("farm_ID", "feed", "t")) %>% 
+  merge(excreted_L, by = c("farm_ID", "feed", "t")) %>% 
+  merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
+  select(-c(contains("sd"))) %>% 
+  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
+  mutate(protein = protein/excr_mean %>% set_units("d-1"),
+         lipids = lipids/excr_mean %>% set_units("d-1"),
+         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
+  select(-excr_mean)
+```
+
+Unlike the uneaten feed, the composition of excreted faeces differs from that of the incoming feed.
+
+* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)
+
+```{r composition-throughtime}
+#| eval: false
+
+excreted_all %>% 
+  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
+  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
+  group_by(farm_ID, feed, macro) %>% 
+  reframe(sd = sd(perc) %>% set_units("d-1"),
+          mean = mean(perc)) %>% 
+  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
+  geom_point(size = 2) +
+  geom_errorbar(width = 0.5) +
+  scale_color_manual(values = feed_pal) +
+  scale_fill_manual(values = feed_pal) +
+  facet_grid(rows = vars(macro)) +
+  theme_classic() +
+  labs(x = "Macronutrient", y = "Mean composition of faeces")
+```
 

### 2025-06-04 archive/08_manuscript/_manuscript/manuscript.qmd
Move manuscript files to root for deployment

--- 2025-06-04 _manuscript.qmd
@@
 library(rnaturalearthdata)
-library(rnaturalearthhires)
 library(dtplyr)
@@
 
-[This intro is copied verbatim from work done during one of the early workshops.]{.aside}
+[This is a note create with the `aside` class.]{.aside}
 
@@
 # Methods
-## Model and approach
-
-[Unfinished.
-Need to work out how much should be transposed from @baldan_r_2018.
-One thing that definitely needs to be stated is the individual ingredient (rather than whole food) tracking, the use of cohorts, and the new method for calculating population.]{.aside}
-
-We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
-The model simulates growth at an individual level, calculating the change in individual weight through time using:
-
-$$
-\frac{dw}{dt} = \frac{A-C}{\epsilon}
-$$
-
-Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
-Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
-Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
-All individuals have a fixed mortality rate to simulate stocking and harvesting.
-
-## Farm temperature forcings
 
@@
 
+## Farm temperature forcings
+
 ```{r farm temperature data}
@@
 Bottom: global distribution of mean temperatures.
-#| fig-height: 9
+#| fig-height: 6
 #| fig-width: 9.5
@@
   ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
-  geom_point(size = 2) +
+  geom_point(size = 2.5) +
   scale_colour_brewer(palette = "Set1") +
@@
 
+## Model and approach
+
+We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
+The model simulates growth at an individual level, calculating the change in individual weight through time using:
+
+$$
+\frac{dw}{dt} = \frac{A-C}{\epsilon}
+$$
+
+Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
+Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
+Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
+All individuals have a fixed mortality rate to simulate stocking and harvesting.
+
 [Need to put the cohort concept (and harvest timing) in here.]{.aside}
@@
 ### Feeding rate
-
-To detail here:
-
-* Functional response to temperature (species-specific)
-* Overfeeding parameters and how they come into play
-* Deminstration of how feeding response and actual food given vary with temperature?
 
@@
 * Salmon cohorts were always grown for 548 days
-* Salmon cohorts were initialised Spring.
-This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
-* Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
+* Salmon cohorts were put out in annually Spring, on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` when farm latitude < 0 and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` when farm latitude > 0.
+* Cohorts were put out every year, such that there was an annual overlap of 183 days where one cohort was nearing harvest and another was being initialised.
 
@@
 
-tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
+Table @tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
 
@@
 
-### Parameter sensitivity
+### Testing parameter sensitivity
 
@@
 
-[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed]{.aside}
-
 * Feed came from [@cottrell_origins_nodate; @cottrell_global_2020]
@@
 
-```{r pop-biom-data}
-coho_biom <- file.path(data_analysis_path, "biomass_produced_comparison.qs") %>% 
-  qs::qread()
-harv_size <- file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
-  qread()
-
-coho_biom_summ <- coho_biom %>% 
-  mutate(perc_diff = 100*(mean - tonnes_per_farm)/tonnes_per_farm)
-```
-
-Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed).
-A population timeseries was the generated using the standard mortality rate (`r unname(params['mortmyt'])` d$^{-1}$).
-Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.
-
-@fig-harvest-size shows the distribution of average individual harvest sizes across farms used to create the population timeseries as predicted by the fish-growth model.
-
-```{r fig-harvest-size, class.chunk = "aside"}
+New method is to take the average predicted individual harvest size for each farm, then working backwards with the standard mortality rate to generate a population for each farm that will produce the correct tonnage for each farm.
+@fig-harvest-size shows the  average individual harvest size at each farm as predicted by the fish-growth model, which was used to create the population inputs for the farm-level growth curves.
+
+```{r fig-harvest-size}
 #| fig-cap: Frequency distribution of harvest sizes across global farms, as predicted by the fish growth model
 
-harv_size %>% 
+file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
+  qread() %>% 
   mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
@@
 
-By this method, farm biomass as predicted by the model slightly overestimated farm tonnage.
-Predicted farm biomass was `r round(min(coho_biom_summ$perc_diff),1)`-`r round(max(coho_biom_summ$perc_diff),1)` higher than tonnage produced (@fig-biomass-produced).
-This variation was not correlated with mean farm temperature or total tonnage produced (@fig-biomass-variation).
-
-```{r fig-biomass-variation, class.chunk = "aside"}
-plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
-plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
-```
-
-```{r fig-biomass-produced, class.chunk = "aside"}
+This means that the population estimates aren't actual fish numbers, they're just a method that allows each farm location to approximate of the correct tonnage produced while to allowing comparisons between the different feeds.
+
+## Biomass produced
+
+```{r biomass produced}
 #| fig-cap: Modelled vs observed salmon biomass produced
+
+coho_biom <- qs::qread(file.path(data_analysis_path, "biomass_produced_comparison.qs"))
 
@@
 
-## Impacts of nutrient input
-
-*To detail here:*
-
-* How to convert feed and uneaten faeces into nutrients - just nitrogen?
-Carbon too?
-If just nitrogen, then can probably use the standard N = 6.25 x protein conversion to compare the feeds (lipids and carbohydrates have negligible protein).
-If doing carbon too, will need to find conversion rates for all of them, possibly splitting carbs/lipids into complex/simple, saturated/unsaturated, etc.
-* Source of species vulnerability layers
+## Species vulnerability layers
 
@@
 
-### Amount
-
 * Total reference uneaten feed across a cohort (548 days) ranged from `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]`.
@@
 
-### Amount
+### Total amount
 
@@
 
-df <- excreted_total %>% 
-  select(-contains(c("sd", "excr_mean", "biomass"))) %>% 
-  pivot_wider(names_from = "feed", values_from = "excr_biom_mean") %>% 
+df <- excr_total %>% 
+  select(-c(sd, sd_pc)) %>% 
+  pivot_wider(names_from = "feed", values_from = "mean") %>% 
   mutate(past = past-reference,
@@
   mutate(reference = set_units(reference, "g kgfish-1 d-1"),
-         diff = set_units(diff, "kg tfish-1 d-1")) %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  mutate(prod_day = t-t_start+1)
+         diff = set_units(diff, "kg tfish-1 d-1"))
 
@@
 
-### Composition
+### Excreted composition
 
 ```{r excreted composition}
-#| eval: true
+#| eval: false
 
@@
   merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
-  select(-c(contains("sd"))) %>% 
-  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
-  mutate(protein = protein/excr_mean %>% set_units("d-1"),
-         lipids = lipids/excr_mean %>% set_units("d-1"),
-         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
-  select(-excr_mean)
+  select(-c(contains("sd")))
 ```
@@
 
-* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)
-
-```{r composition-throughtime}
-#| eval: false
-
-excreted_all %>% 
-  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
-  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
-  group_by(farm_ID, feed, macro) %>% 
-  reframe(sd = sd(perc) %>% set_units("d-1"),
-          mean = mean(perc)) %>% 
-  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
-  geom_point(size = 2) +
-  geom_errorbar(width = 0.5) +
-  scale_color_manual(values = feed_pal) +
-  scale_fill_manual(values = feed_pal) +
-  facet_grid(rows = vars(macro)) +
-  theme_classic() +
-  labs(x = "Macronutrient", y = "Mean composition of faeces")
-```
+| Macro | Feed | Faeces |
+|:---------|:----:|:----:|
+| Protein       | `r `
+| Lipids        |
+| Carbohydrates |
 

### 2025-06-04 archive/08_manuscript/docs/manuscript.qmd
Move manuscript files to root for deployment

--- 2025-06-04 archive/08_manuscript/_manuscript/manuscript.qmd
@@
 
-```{r biomass produced}
+```{r biomass produced, class.chunk = "aside"}
 #| fig-cap: Modelled vs observed salmon biomass produced
@@
 ```{r excreted composition}
-#| eval: false
+#| eval: true
 
@@
   merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
-  select(-c(contains("sd")))
+  select(-c(contains("sd"))) %>% 
+  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
+  mutate(protein = protein/excr_mean %>% set_units("d-1"),
+         lipids = lipids/excr_mean %>% set_units("d-1"),
+         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
+  select(-excr_mean)
 ```
@@
 
-| Macro | Feed | Faeces |
-|:---------|:----:|:----:|
-| Protein       | `r `
-| Lipids        |
-| Carbohydrates |
+```{r composition-throughtime}
+excreted_all %>% 
+  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
+  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
+  group_by(farm_ID, feed, macro) %>% 
+  reframe(sd = sd(perc) %>% set_units("d-1"),
+          mean = mean(perc)) %>% 
+  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
+  geom_point(size = 2) +
+  geom_errorbar(width = 0.5) +
+  scale_color_manual(values = feed_pal) +
+  scale_fill_manual(values = feed_pal) +
+  facet_grid(rows = vars(macro)) +
+  theme_classic() +
+  labs(x = "Macronutrient", y = "Mean composition of faeces")
+```
 

### 2025-06-04 manuscript.qmd
Forgot about jekyll's underscore vendetta

--- 2025-06-04 _manuscript.qmd
@@
 
-filters:
-  - acronyms
+# filters:
+#   - acronyms
 
@@
   message: false
-  cache: true
+  cache: false
   freeze: auto
@@
 
-[Need to put the cohort concept (and harvest timing) in here.]{.aside}
+```{r patchwork map}
+#| fig-cap: |
+#|   Possibly use a patchwork map to show spatial results?
+#| fig-height: 9
+#| fig-width: 9.5
+
+worldmap <- ne_countries(scale = "large", returnclass = "sf")
+
+AUS_bounds <- c(144, 149.5, -39.75, -44)
+CAN1_bounds <- c(-132, -122, 47.75, 54.25)
+CAN2_bounds <- c(-70, -54, 43, 48.5)
+CHI_bounds <- c(-77.5, -62.5, -56, -25)
+EUR_bounds <- c(-26, 30, 51, 71)
+
+p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
+  geom_sf(fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
+  coord_sf() +
+  theme_classic()
+
+no_margins <- function() {
+  theme(legend.position = "none", 
+        plot.margin = margin(),
+        axis.title = element_blank())
+}
+
+p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
+p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
+p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
+p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
+p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()
+
+subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
+finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
+  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
+  theme(plot.margin = margin(0, 0, 0, 0))
+finalplot
+```
 
@@
 
-## Total nutrients (amount & source)
-
-```{r patchwork map}
-worldmap <- ne_countries(scale = "large", returnclass = "sf")
-
-AUS_bounds <- c(144, 149.5, -39.75, -44)
-CAN1_bounds <- c(-132, -122, 47.75, 54.25)
-CAN2_bounds <- c(-70, -54, 43, 48.5)
-CHI_bounds <- c(-77.5, -62.5, -56, -25)
-EUR_bounds <- c(-26, 30, 51, 71)
-
-p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
-  geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
-  coord_sf() +
-  theme_classic()
-
-no_margins <- function() {
-  theme(legend.position = "none", 
-        plot.margin = margin(),
-        axis.title = element_blank())
-}
-
-p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
-p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
-p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
-p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
-p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()
-
-subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
-finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
-  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
-  theme(plot.margin = margin(0, 0, 0, 0))
-finalplot
-```
+## Total nutrients
 
@@
 All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
-Major packages used include terra [@terra], targets [@targets], future [@future], furrr [@furrr], and the tidyverse [@tidyverse].
+Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
 For a full list of R packages used see the lockfile on [Github](https://www.github.com).

### 2025-06-04 manuscript.qmd
Moving text to Google doc

@@
 # Author roles: "writing – original draft", "writing – review & editing", "formal analysis", "funding acquisition", "conceptualization", "data curation", "investigation", "methodology", "project administration", "resources", "software", "supervision", "validation", "visualization"
-author:
-  - name: Tormey Reimer
-    orcid: 0000-0002-5983-2798
-    corresponding: true
-    email: tormey.reimer@utas.edu.au
-    role: 
-      - methodology: supporting
-      - analysis: lead
-      - writing: lead
-    affil-id: [1,2]
-  - name: Richard S. Cottrell
-    orcid: 0000-0002-6499-7503
-    corresponding: false
-    roles: 
-      - conceptualization: lead
-      - methodology: lead
-      - writing: supporting
-    # affil-id: [1,2]
-  - name: Alexandra Johne
-    orcid: 0000-0002-2816-7983
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    affil-id: 3
-  - name: Sowdamini Sesha Prasad
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Marceau Cormery
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Gage Clawson
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Scott Hadley
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Helen Hamilton
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Benjamin S. Halpern
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Catriona Macleod
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Camille White
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Julia L. Blanchard
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-      - methodology: supporting
-      - analysis: supporting
-      - editing: supporting
-    # affil-id: [3,2]
 
-affiliations:
-  - id: 1
-    name: Institute for Marine and Antarctic Studies
-    group: Fisheries & Aquaculture
-    address: 29 Nubeena Crescent
-    city: Taroona
-    region: TAS
-    country: Australia
-    postal-code: 7053
-    url: https://www.imas.utas.edu.au/
-  - id: 2
-    name: Centre for Marine Socioecology
-    url: https://marinesocioecology.org/
-  - id: 1
-    name: Institute for Marine and Antarctic Studies
-    group: Ecology & Biodiversity
-    # address: 29 Nubeena Crescent
-    # city: Taroona
-    # region: TAS
-    # country: Australia
-    # postal-code: 7053
-    url: https://www.imas.utas.edu.au/
-  # - id: 3
-  #   name: Heriott-Watt University, Institute for Life and Earth Sciences
-  #   department: School of Energy, Geoscience, Infrastructure and Society
-  #   address: Franklin Road
-  #   city: Stromness
-  #   region: Orkney
-  #   country: United Kingdom
-  #   postal-code: KW16 3AN
-  #   url: https://www.hw.ac.uk/
-# keywords:
-#   - keyword
-#   - keyword
-# abstract: |
-#   Any new aquaculture venture...
-# plain-language-summary: |
-#   Plain language summary goes here....
-# key-points:
-#   - Point 1
-#   - Point 2
 bibliography: ["refs.bib", "manual-refs.bib"]
@@
     grid:
-      sidebar-width: 350px
+      sidebar-width: 250px
       body-width: 1200px
@@
       gutter-width: 2em
-  # pdf:
-  #   papersize: a4
-  #   linestretch: 1.15
-  #   link-citations: true
-  #   keep-tex: true
-  #   template-partials:
-  #     - "title.tex"
-  #   include-in-header:
-  #     file: "header_extra.tex"
-
-# filters:
-#   - acronyms
 
@@
   message: false
-  cache: false
+  cache: true
   freeze: auto
@@
 
-install_unit("gfish")
-install_unit("kgfish", "1000 gfish")
-install_unit("tfish", "1000 kgfish")
+remove_unit("g_fish")
+remove_unit("kg_fish")
+remove_unit("t_fish")
+install_unit("g_fish")
+install_unit("kg_fish", "1000 g_fish")
+install_unit("t_fish", "1000 kg_fish")
 ```
@@
 pop_params <- qread(pop_params_file)
+
+feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
+cohort_pal <- c("1" = brewer.pal(9, "Set1")[1], "2" = brewer.pal(9, "Set1")[2], "3" = brewer.pal(9, "Set1")[3], "all" = "black")
 ```
 
-# Introduction
-
-[This intro is copied verbatim from work done during one of the early workshops.]{.aside}
-
-Aquaculture is now the dominant form of aquatic animal food (herein ‘seafood’) production and is expected to be the primary way we meet future seafood demand.
-Freshwater systems will likely continue to provide the majority of farmed seafood but marine aquaculture is also poised to expand substantially in numerous areas.
-Farmed marine fish and invertebrates are produced near exclusively in coastal waters, and nearly three quarters of this production is dependent on human-made feeds.
-Nearshore locations and feed inputs are necessary to maintain profitable and productive farming operations but coastal aquaculture generates a number of challenges.
-In the crowded coastal zone, aquaculture operations can conflict with other stakeholder uses such as recreation, fishing, renewable energy, transport, and tourism.
-And while farming marine fish typically generates a far smaller nutrient footprint than livestock farming, the overt nature of aquaculture in nearshore regions and evidence of  localised nutrient impacts around fish farms remains a primary public and scientific concern.
-Identifying strategies that reduce ecosystem impacts from fish farm waste therefore represents an important goal for improving marine aquaculture sustainability and maintaining the sector’s social licence to operate.
-
-Aquaculture feeds represent an important lever for reducing nutrient waste impacts around fish farms.
-Like all farmed animals, fish and invertebrates must digest the nutrients contained in feeds before they can be used for growth.
-Any nutrients left undigested are egested as solid waste, and dissolved wastes are excreted as metabolic waste products.
-Further, some feed inevitably remains uneaten and is lost to the surrounding ecosystem.
-Particulate organic matter (both feed and faeces) that settles can simplify benthic communities as the oxygen demand from its decomposition drives the production of sulphides that kill less mobile faunal, encouraging a lower diversity of opportunistic scavengers and the growth of bacterial mats (e.g., Beggiatoa spp).
-Thus, the chemical composition of the ingredients used in aquaculture feeds and their digestibility for the farmed species has significant implications for the nature and reactivity of the waste generate by marine aquaculture.
-
-Firstly the overall volume of nutrient waste is dictated by the nature and intensity of production, that is the farm size, the density of farmed animals and the feed requirements and efficiency of the species grown.
-SecondlDeposition of waste is heavily influenced by water depth and current speed at the farming site.
-Once
-
-As farmed fish and invertebrates are fed, whatever
-
-Nutand its impact on marine ecosystems is influenced by many factors. 
-* Farm size
-* Depth
-* Current speed
-* Benthic impact - sediment type/faunal assemblages/wider marine community
-* High turnover environments - nitrogen enriched areas
-* Feed influences all of these things
-
-The primary source of organic waste from fed aquaculture production comes from the excretion and faeces of the farmed animals and through uneaten feed that dissolves in the water column or settles on the benthos.
-The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals.
-
-## P2
-
-* Waste from aquaculture farms and it’s impact is influenced by many things but the composition of feeds plays a central role.
-* Waste from aquaculture farms has multiple sources. 
-* The primary source of organic waste comes from the faeces and excretion of the fish or invertebrates.
-* Uneaten feed produced another key source.
-* The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals
-* Many marine fish are naturally carnivorous so diets used to be high in fishmeal and oil but increasing fishmeal and oil prices along with concerns over the sustainability of marine ingredients have led to a reduction in their use across multiple farmed taxa
-* In lieu of fishmeal and oil, many plant-based ingredients such as soy protein concentrate, canola oil, and wheat gluten have replaced them. 
-* Changes in feed composition influences the digestibility of the nutrients held in each feed and can alter the composition of waste.
-* Of particular concern are changes (increases) to the presence of reactive nitrogen and phosphorus in coastal waters that could have an effect on eutrophication.
-
-## P3
-
-* Whether or not nutrients lead to eutrophication depends on the sensitivity of the receiving environment
-* Ecosystems that are already enriched through natural processes and whose biota is well adapted to substantial fluxes in available nutrients (e.g.
-upwelling zones, dynamic coastal communities) may be less sensitive while oligotrophic ecosystem are likely to see considerable changes under nutrient enrichment scenarios.
-* To understand the impact of aquaculture waste under present day or future scenarios we need to quantify the volume, nature, and location of mariculture waste and determine the sensitivity of the receiving environments to that waste.
-Yet only recent estimates even give us the estimated location of marine farms let alone the volume of nature of the waste produced.
-To address this gap, we use existing maps of mariculture location with a bioenergtic model
+This document was last updated at `r format(Sys.time(), "%H:%M")` on `r format(Sys.time(), "%d %b, %Y")`.
 
 # Methods
-## Model and approach
+### Feeding rate
 
-[Unfinished.
-Need to work out how much should be transposed from @baldan_r_2018.
-One thing that definitely needs to be stated is the individual ingredient (rather than whole food) tracking, the use of cohorts, and the new method for calculating population.]{.aside}
+To detail here:
 
-We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
-The model simulates growth at an individual level, calculating the change in individual weight through time using:
+* Functional response to temperature (species-specific)
+* Overfeeding parameters and how they come into play
+* Deminstration of how feeding response and actual food given vary with temperature?
 
-$$
-\frac{dw}{dt} = \frac{A-C}{\epsilon}
-$$
+```{r fig-functional-response-to-temperature}
+#| eval: false
+#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
 
-Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
-Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
-Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
-All individuals have a fixed mortality rate to simulate stocking and harvesting.
+df <- data.frame(water_temp = seq(-5, 26, 0.25))
+df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)
+df <- df %>% 
+mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * feeding,
+       food_prov = NA)
+for (i in 1:nrow(df)) {
+  df$food_prov[i] <- food_prov_rate(pop_params = pop_params, rel_feeding = df$feeding[i], ing_pot = df$ing_pot[i], 
+                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
+}
+df$ing_pot <- df$ing_pot/maxna(df$ing_pot)
+df$food_prov <- df$food_prov/maxna(df$ing_pot)
+
+df %>% 
+  ggplot(aes(x = water_temp, y = ing_pot)) +
+  geom_line(linewidth = 0.75) +
+  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
+  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
+  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
+  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
+  theme_classic() +
+  theme(text = element_text(colour = "black", family = "serif", size = 12))
+```
 
@@
 
-Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD).
-Farms with a mean temperature of $\leq 6^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms).
-The total number of farms included in this analysis was therefore `r nrow(farm_temp_means)`.
+Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$C to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$C, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$C ($\pm$ `r round(overall_sd, 1)`$^{\circ}$C SD).
+Farms with a mean temperature of $\leq$6$^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms).
+The total number of farms included in the analysis was therefore `r nrow(farm_temp_means)`.
 
@@
   theme(legend.position = "none", 
-        plot.margin = margin(),
+        plot.margin = margin(0, 0, 0, 0),
         axis.title = element_blank())
@@
 
-```{r fig-cohorts}
-#| fig-cap: Example of cohorts
-#| eval: false
-
-fnms <- output_cohort_growth_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("biomass")
-
-df <- fnms[1] %>% read_parquet() %>% 
-  filter(feed == "reference") %>% 
-  mutate(mean = set_units(mean, "g") %>% set_units("t"),
-         sd = set_units(sd, "g") %>% set_units("t"))
-
-ggplot(df, aes(x = yday, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
-  geom_line(linewidth = 0.75) +
-  geom_ribbon(linetype = "dotted", alpha = 0) +
-  scale_x_continuous(breaks = seq(0, 2000, 200)) +
-  labs(y = "Farm biomass", x = "Day of the year") +
-  theme_classic() +
-  theme(legend.position = "none", aspect.ratio = 0.75)
-
-yrs <- max(df$yday)/365
-harvests <- df %>% 
-  group_by(cohort) %>% 
-  reframe(mean = maxna(mean),
-          sd = maxna(sd))
-
-sum(harvests$mean)/yrs
-mean(harvests$sd)/yrs
-```
-
-### Feeding rate
-
-To detail here:
-
-* Functional response to temperature (species-specific)
-* Overfeeding parameters and how they come into play
-* Deminstration of how feeding response and actual food given vary with temperature?
-
-```{r fig-functional-response-to-temperature}
-#| eval: false
-#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
-
-df <- data.frame(water_temp = seq(-5, 26, 0.25))
-df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)
-df <- df %>% 
-mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * feeding,
-       food_prov = NA)
-for (i in 1:nrow(df)) {
-  df$food_prov[i] <- food_prov_rate(pop_params = pop_params, rel_feeding = df$feeding[i], ing_pot = df$ing_pot[i], 
-                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
-}
-df$ing_pot <- df$ing_pot/maxna(df$ing_pot)
-df$food_prov <- df$food_prov/maxna(df$ing_pot)
-
-df %>% 
-  ggplot(aes(x = water_temp, y = ing_pot)) +
-  geom_line(linewidth = 0.75) +
-  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
-  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
-  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
-  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
-  theme_classic() +
-  theme(text = element_text(colour = "black", family = "serif", size = 12))
-```
-
 ## Production parameters
 
-* Salmon cohorts were always grown for 548 days
-* Salmon cohorts were initialised Spring.
+Salmon were grown for 548 days and were initialised Spring.
 This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
-* Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
+Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
 
-## Parameterisation for Atlantic salmon
+## Model parameterisation
 
@@
 
-tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
+@tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
 
@@
 | $\alpha$             | `r unname(params['alpha'])`      | -                        | Feeding catabolism coefficient | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| $\epsilon_{P}$ | `r unname(params['epsprot'])` | J g protein$^{-1}$ | Energy content of protein | @baldan_r_2018 | 
-| $\epsilon_{L}$ | `r unname(params['epslip'])` | J g lipid$^{-1}$ | Energy content of lipid | @baldan_r_2018 |
-| $\epsilon_{C}$ | `r unname(params['epscarb'])` | J g carbohydrate$^{-1}$ | Energy content of carbohydrate | @baldan_r_2018 |
-| $\epsilon_{O_2}$ | `r unname(params['epsO2'])` | J g O2$^{-1}$ | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
+| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | J g$^{-1}$               | Energy content of protein      | @baldan_r_2018 | 
+| $\epsilon_{L}$       | `r unname(params['epslip'])`     | J g$^{-1}$               | Energy content of lipid        | @baldan_r_2018 |
+| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | J g$^{-1}$               | Energy content of carbohydrate | @baldan_r_2018 |
+| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | J g O$_2^{-1}$           | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
 | pk                   | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
@@
 | $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C.
-Coefficent for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
-| $T_{max}$ | `r unname(params['Tma'])` | $^{^\circ}$C | Maximum lethal temperature | Juvenile *Oncorhynchus tshawytscha* (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
-| $T_{opt}$ | `r unname(params['Toa'])` | $^{^\circ}$C | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
+Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
+| $T_{max}$            | `r unname(params['Tma'])`        | $^{\circ}$C              | Maximum lethal temperature | Juvenile *Oncorhynchus tshawytscha* (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
+| $T_{opt}$            | `r unname(params['Toa'])`        | $^{\circ}$C              | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
 Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0 $\pm$ 14.6 g, temps: 6, 10, 14, 18${\circ}$C |
-| $T_{min}$ | `r unname(params['Taa'])` | $^{^\circ}$C | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] | 
-| $\omega$ | `r unname(params['omega'])` | g O2 / g | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
+| $T_{min}$            | `r unname(params['Taa'])`        | $^{\circ}$C              | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] |
+| $\omega$             | `r unname(params['omega'])`      | g O$_2$ g$^{-1}$         | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
 | a                    | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
@@
 | $\Delta{W}$          | `r unname(params['deltaW'])`     | g                        | Dry weight standard deviation | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\overline{I_{max}}$ | `r unname(params['meanImax'])` | g g$^{-1}$ fish day$^{-1}$ | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\Delta{I_{max}}$ | `r unname(params['deltaImax'])` | g g$^{-1}$ fish day$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\overline{F}$ | `r unname(params['overFmean'])` | g g$^{-1}$ fish$ | Overfeeding rate mean |    |
-| $\Delta{F}$ | `r unname(params['overFdelta'])` | g g$^{-1}$ fish$ | Overfeeding rate standard deviation |    |
+| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
+| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
+| $\overline{F}$       | `r unname(params['overFmean'])`  | g g$^{-1}$ fish          | Overfeeding rate mean |    |
+| $\Delta{F}$          | `r unname(params['overFdelta'])` | g g$^{-1}$ fish          | Overfeeding rate standard deviation |    |
 | mort                 | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |
@@
 
-Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as:
-
-$$
-S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}
-$$
-
-where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-
+Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
 * All parameters in Table @tbl-params were tested across all farms (all temperatures)
-* Used a population of 100 in each farm
+* Used the full population of 5000 for the population parameters $\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, and $\Delta{F}$, and a population of 100 in each farm for all other parameters.
 
@@
 ```{r feeds}
-feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
 feed_params <- file.path(output_species_data_path, "feed_params.qs") %>% qs::qread()
@@
 
-[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed]{.aside}
+[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed?]{.aside}
 
-* Feed came from [@cottrell_origins_nodate; @cottrell_global_2020]
+* Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
 * The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
@@
 * Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
-* Within the reference feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
-* Within the reference feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
+* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
+* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
 
-## Population and biomass estimates
+## Model population and biomass
+
+```{r fig-cohorts}
+#| fig-cap: | 
+#|   Example of how the overlapping cohorts combine into a single farm production curve (in this case biomass).
+The left plot shows the farm biomass produced by each cohort from initialisation to harvest, while the right plot shows the combined farm biomass over the course of a single production period of 548 days.
+#| eval: true
+
+fnms <- output_farm_growth_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("reference")
+
+df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
+  as.data.frame() %>% 
+  mutate(mean = set_units(mean, "g") %>% set_units("t"),
+         sd = set_units(sd, "g") %>% set_units("t")) %>% 
+  select(-farm_ID)
+
+df <- rbind(
+  df %>% mutate(cohort = 1),
+  df %>% mutate(t = t+365, cohort = 2),
+  df %>% mutate(t = t+730, cohort = 3)
+) %>% 
+  mutate(t = (t-min(t))+1,
+         split = "Split by cohort")
+
+min_t <- min(df$t[df$cohort == 2])
+max_t <- max(df$t[df$cohort == 2])
+
+df_2 <- df %>% 
+  filter(t %in% min_t:max_t) %>% 
+  mutate(sd = sd/mean) %>% 
+  group_by(t) %>% 
+  reframe(sd = sqrt(sum(sd^2)),
+          mean = sum(mean),
+          sd = sd*mean) %>% 
+  mutate(cohort = "all",
+         split = "Totalled")
+
+df <- rbind(df, df_2) %>% 
+  mutate(cohort = as.factor(cohort))
+
+ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(linetype = "dotted", alpha = 0) +
+  facet_grid(cols = vars(split)) +
+  theme_classic() +
+  scale_x_continuous(breaks = seq(0, 1600, 120)) +
+  scale_colour_manual(values = cohort_pal) +
+  theme(legend.position = "none") +
+  labs(y = "Farm biomass", x = "Day of production")
+```
 
@@
 
-@fig-harvest-size shows the distribution of average individual harvest sizes across farms used to create the population timeseries as predicted by the fish-growth model.
-
 ```{r fig-harvest-size, class.chunk = "aside"}
-#| fig-cap: Frequency distribution of harvest sizes across global farms, as predicted by the fish growth model
+#| fig-cap: |
+#|   Frequency distribution of harvest sizes used to create the population timeseries for each farm, as predicted by the fish-growth model.
 
@@
 
+In general, data outputs comes in the following dimensions:
+
+* Location -> temperature -> farm_ID
+* Uneaten feed + excreted faeces = total inputs (g)
+* Day of production (impacted by location)
+
 * Main point is the difference between feeds (kg/t salmon).
-* Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
+* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)
 
@@
           mean = meanna(total)) %>% 
-  mutate(min = min %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
-         max = max %>% set_units("g gfish-1") %>% set_units("g kgfish-1"),
-         mean = mean %>% set_units("g gfish-1") %>% set_units("g kgfish-1")) %>% 
+  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
   mutate(min = round(min,2),
@@
   merge(farms_geometry, by = "farm_ID") %>% 
-  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g gfish-1 d-1") %>% set_units("g kgfish-1 d-1"),
+  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
          country = factor(country, levels = sorted_countries)) %>% 
@@
   merge(farms_geometry, by = "farm_ID") %>% 
-  mutate(excr_biom_mean = excr_biom_mean %>% set_units("g gfish-1 d-1") %>% set_units("g kgfish-1 d-1"),
+  mutate(excr_biom_mean = excr_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
          country = factor(country, levels = sorted_countries)) %>% 
@@
   pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
-  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
+  mutate(reference = set_units(reference, "g kg_fish-1 d-1"),
          diff_perc = drop_units(diff/reference)) %>% 
@@
 
-There was very little variation in the percentage difference (from reference) excreted with increasing overall excretion (@fig-total-excr-diff_perc), or through time (@fig-total-excr-diff_perc_2). 
 The difference in total excretion for the past feed ranged from 
@@
   pivot_longer(names_to = "feed", values_to = "diff", cols = c(past, future), names_transform = list(feed = as.factor)) %>% 
-  mutate(reference = set_units(reference, "g kgfish-1 d-1"),
-         diff = set_units(diff, "kg tfish-1 d-1")) %>% 
+  mutate(reference = set_units(reference, "g kg_fish-1 d-1"),
+         diff = set_units(diff, "kg t_fish-1 d-1")) %>% 
   merge(farm_coords, by = "farm_ID") %>% 
@@
   reframe(mean_diff = meanna(diff),
-          sd_diff = sdna(diff) %>% set_units("kg tfish-1 d-1")) %>% 
+          sd_diff = sdna(diff) %>% set_units("kg t_fish-1 d-1")) %>% 
   ggplot(aes(x = prod_day, y = mean_diff, ymin = mean_diff-sd_diff, ymax = mean_diff+sd_diff, colour = hemisphere, fill = hemisphere)) +
@@
 
+| Macro | Reference | Past | Future |
+|:-----------:|:---:|:---:|:---:|
+| Protein | `r tP_1` |  `r tP_2` |  `r tP_3` | 
+| Lipids | `r tL_1` | `r tL_2` |  `r tL_3` | 
+| Carbohydrates | `r tC_1` | `r tL_2` |  `r tL_3` |
+
 ## Total nutrients

### 2025-06-06 manuscript.qmd
Nicer map on Robinson/Mercator

@@
 
+```{r custom fuctions}
+#| code-summary: Function to create sf polygons from bounding boxes
+
+create_boxes <- function(box_list, label_positions, offset_deg) {
+  boxes <- list()
+  labels <- list()
+
+  for(i in seq_along(box_list)) {
+    name <- names(box_list)[i]
+    coords <- box_list[[i]]
+    pos <- label_positions[i]
+
+    # Create polygon from bounding box coordinates
+    box_coords <- matrix(c(
+      coords[1], coords[3],  # lonmin, latmin
+      coords[2], coords[3],  # lonmax, latmin  
+      coords[2], coords[4],  # lonmax, latmax
+      coords[1], coords[4],  # lonmin, latmax
+      coords[1], coords[3]   # close polygon
+    ), ncol = 2, byrow = TRUE)
+
+    # Create sf polygon
+    poly <- st_polygon(list(box_coords))
+    boxes[[i]] <- st_sfc(poly, crs = 4326)
+
+    # Calculate label position based on specification
+    label_coords <- get_label_position(coords, pos, offset_deg[i])
+    label_point <- st_point(c(label_coords[1], label_coords[2]))
+    labels[[i]] <- st_sfc(label_point, crs = 4326)
+  }
+
+  # Combine into sf objects
+  boxes_sf <- st_sf(
+    name = names(box_list),
+    letter = LETTERS[1:length(box_list)],
+    geometry = do.call(c, boxes)
+  )
+
+  labels_sf <- st_sf(
+    name = names(box_list), 
+    letter = LETTERS[1:length(box_list)],
+    geometry = do.call(c, labels)
+  )
+
+  return(list(boxes = boxes_sf, labels = labels_sf))
+}
+
+# Helper function to calculate label positions
+get_label_position <- function(coords, position, offset) {
+  lonmin <- coords[1]
+  lonmax <- coords[2]
+  latmin <- coords[3]
+  latmax <- coords[4]
+
+  # Parse position string
+  parts <- strsplit(position, "_")[[1]]
+  vertical <- parts[1]    # "top" or "bottom"
+  horizontal <- parts[2]  # "left" or "right"
+  location <- parts[3]    # "inside" or "outside"
+
+  # Base coordinates for corners
+  if(vertical == "bottom") {base_lat <- latmin} else {base_lat <- latmax}
+  if(horizontal == "right") {base_lon <- lonmax} else {base_lon <- lonmin}
+
+  # Apply offset for outside positioning
+  if(location == "outside") {
+    if(horizontal == "left") {base_lon <- base_lon-offset} else {base_lon <- base_lon+offset}
+    if(vertical == "top") {base_lat <- base_lat + offset} else {base_lat <- base_lat - offset}
+  }
+
+  return(c(base_lon, base_lat))
+}
+
+lim_robin <- function(lons = c(144.0, 149.5), lats = c(-39.75, -44.00)) {
+  coords <- data.frame(lon = lons, lat = lats) %>%
+    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
+    st_transform(crs = "+proj=robin") %>% 
+    st_coordinates()
+  list(
+    xlims = range(coords[, "X"]),
+    ylims = range(coords[, "Y"])
+  )
+}
+
+```
+
 This document was last updated at `r format(Sys.time(), "%H:%M")` on `r format(Sys.time(), "%d %b, %Y")`.
@@
 
-worldmap <- ne_countries(scale = "medium", returnclass = "sf")
+worldmap <- ne_countries(scale = "medium", returnclass = "sf") %>% st_transform(crs = "+proj=robin")
+graticules <- st_graticule(worldmap, lon = seq(-180, 180, 30), lat = seq(-90, 90, 30))
 
-p1 <- ggplot(data = worldmap, aes(geometry = geometry)) +
-  geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
+inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 47.75, 54.25),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-26, 30, 51, 71),
+  CHI = c(-77.5, -62.5, -56, -25),
+  AUS = c(144, 149.5, -39.75, -44)
+)
+labels_spec <- c(CAN1 = "bottom_left_outside", CAN2 = "bottom_right_outside", EUR = "bottom_left_outside", CHI = "top_left_outside", AUS = "bottom_left_outside")
+labels_offset <- c(CAN1 = 1, CAN2 = 2, EUR = 1.75, CHI = 1.75, AUS = 3.5)
+
+box_data <- create_boxes(box_list = inset_boxes, # see function create_boxes above
+                         label_positions = unname(labels_spec),
+                         offset_deg = unname(labels_offset))
+boxes_robinson <- st_transform(box_data$boxes, crs = "+proj=robin")
+labels_robinson <- st_transform(box_data$labels, crs = "+proj=robin")
+farm_temp_robinson <- st_sf(farm_temp_means) %>% st_transform(crs = "+proj=robin")
+
+p1 <- ggplot() +
+  geom_sf(data = graticules, color = "gray80", size = 0.3) +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_robinson, aes(color = mean_temp), size = 1) +
   coord_sf() +
-  theme_classic()
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 25,barheight = 1.5
+  )) +
+  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
+  geom_sf_text(data = labels_robinson, aes(label = letter), 
+               color = "darkred", size = 5, fontface = "bold", 
+               hjust = 0.5, vjust = 0.5) +
+  theme_void()
 
@@
 
-```{r patchwork map}
+```{r patchwork-map-mercator}
 #| fig-cap: |
@@
 #| fig-width: 9.5
-
-worldmap <- ne_countries(scale = "large", returnclass = "sf")
-
-AUS_bounds <- c(144, 149.5, -39.75, -44)
-CAN1_bounds <- c(-132, -122, 47.75, 54.25)
-CAN2_bounds <- c(-70, -54, 43, 48.5)
-CHI_bounds <- c(-77.5, -62.5, -56, -25)
-EUR_bounds <- c(-26, 30, 51, 71)
-
-p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
-  geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
-  coord_sf() +
-  theme_classic()
 
@@
 
-p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
-p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
-p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
-p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
-p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()
+inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 48.5, 54),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-23, 28.5, 52, 71),
+  CHI = c(-78, -62, -55.5, -27),
+  AUS = c(144, 149, -40.75, -43.75)
+)
 
-subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
-finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
-  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
-  theme(plot.margin = margin(0, 0, 0, 0))
-finalplot
+worldmap <- ne_countries(scale = "large", returnclass = "sf")
+p1 <- ggplot() +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 1) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 1.5, barheight = 20
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+p_Aus <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["AUS"]][1:2], ylim = inset_boxes_sm[["AUS"]][3:4])  +
+  draw_label("E", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["AUS"]][1], y = inset_boxes_sm[["AUS"]][3], 
+             hjust = 0, vjust = 1)
+p_Eur <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["EUR"]][1:2], ylim = inset_boxes_sm[["EUR"]][3:4]) +
+  draw_label("C", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["EUR"]][1], y = inset_boxes_sm[["EUR"]][4], 
+             hjust = -1, vjust = 1)
+p_Chi <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CHI"]][1:2], ylim = inset_boxes_sm[["CHI"]][3:4]) +
+  theme(legend.position = "right") +
+  draw_label("D", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CHI"]][1], y = inset_boxes_sm[["CHI"]][4], 
+             hjust = 0, vjust = 0)
+p_Can1 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN1"]][1:2], ylim = inset_boxes_sm[["CAN1"]][3:4]) +
+  draw_label("A", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN1"]][1], y = inset_boxes_sm[["CAN1"]][4], 
+             hjust = -1, vjust = 0)
+p_Can2 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN2"]][1:2], ylim = inset_boxes_sm[["CAN2"]][3:4]) +
+  draw_label("B", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN2"]][1], y = inset_boxes_sm[["CAN2"]][4], 
+             hjust = 0, vjust = 1)
+
+grid_1 <- cowplot::plot_grid(p_Can1, p_Can2, ncol = 2, rel_widths =  c(1, 1.35))
+grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
+grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
+
+cowplot::plot_grid(
+  grid_1, grid_3,
+  nrow = 2,
+  rel_heights = c(1, 1.5)        # relative row heights
+)
 ```

### 2025-06-06 _targets_sensitivities.R
Smaller sample for population-level parameters

@@ -5,7 +5,7 @@ library(parallelly)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 4, seconds_timeout = 90),
+  controller = crew_controller_local(workers = 18, seconds_timeout = 90),
   workspace_on_error = TRUE
 )
 
@@ -13,6 +13,10 @@ list(
   tar_target(
     tar_farm_IDs,
     farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID)
+  ),
+  tar_target(
+    tar_farm_ID_sample,
+    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(271)
   ),
   
   tar_target(tar_factors, factors),
@@ -179,76 +183,176 @@ list(
   tar_target(
     tar_sens_results_spec,
     command = {
-      tar_sens_run_spec %>%
+      cols <- colnames(tar_sens_run_spec_lo)[
+        !colnames(tar_sens_run_spec_lo) %in% c("adj_param", "farm_ID", "factor")
+      ]
+      rbind(
+        tar_sens_run_spec_lo,
+        tar_sens_run_spec_mi,
+        tar_sens_run_spec_hi
+      ) %>%
+        pivot_longer(cols = all_of(cols), names_to = "measure", values_to = "value", 
+                     names_transform = list(measure = as.factor)) %>% 
+        pivot_wider(names_from = "factor", values_from = "value", names_prefix = "fact_") %>% 
+        mutate(sensitivity = (fact_1.1-fact_0.9)/(0.2*fact_1)) %>% 
         group_by(adj_param, measure) %>%
         reframe(mean_sens = meanna(sensitivity),
                 sd_sens = sdna(sensitivity))
     },
-    pattern = tar_param_names_spec
+    pattern = map(tar_sens_run_spec_lo, tar_sens_run_spec_mi, tar_sens_run_spec_hi)
   ),
   
   tar_target(
-    tar_sens_run_pop, 
+    tar_sens_run_pop_lo, 
     command = {
-      purrr::map_dfr(factors, function(fact) {
-        adj_params <- sens_all_params
-        adj_params[tar_param_names_pop] <- adj_params[tar_param_names_pop] * factors
-        
-        sens <- farm_growth(
[…]

### 2025-06-06 manuscript.qmd
Composition comparison plot, and move sensitivities to supplementaries

@@
 library(ggpubr)
+library(cowplot)
 library(patchwork)
@@
 
+prettyplot <- function() {
+  theme_classic() +
+    theme(legend.position = "none",
+          text = element_text(family = "serif", size = 12, colour = "black"),
+          axis.title.x = element_text(vjust = 0.5),
+          axis.title.y = element_text(hjust = 0.5))
+}
+
 feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
@@
   labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
-  theme_classic() +
+  prettyplot() +
   theme(text = element_text(colour = "black", family = "serif", size = 12))
@@
   labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
-  theme_classic() +
+  prettyplot() +
   theme(legend.position = "top", legend.title = element_blank())
@@
   labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
-  theme_classic() +
+  prettyplot() +
   theme(legend.position = "top", legend.title = element_blank())
@@
 Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-* All parameters in Table @tbl-params were tested across all farms (all temperatures)
-* Used the full population of 5000 for the population parameters $\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, and $\Delta{F}$, and a population of 100 in each farm for all other parameters.
-
-```{r sensitivity data}
-sens_weight <- output_sens_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("results") %>% 
-  str_subset("weight") %>% 
-  qs::qread()
-
-sens_excr <- output_sens_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("results") %>% 
-  str_subset("total_excr") %>% 
-  qs::qread()
-
-sens_data <- rbind(sens_weight, sens_excr) %>% 
-  mutate(adj_param = factor(adj_param, levels = param_names$name))
-```
-
-Looking at @fig-param-sens-weight:
-
-* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
-* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
-There must be more up-to-date measurements for Atlantic salmon in particular.
-
-```{r fig-param-sens-weight}
-#| fig-cap: Impact of increasing each model parameter by 10% on final farm biomass (red) and total excreted nutrients (blue) over the whole production period.
-
-sens_data %>% 
-  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
-  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
-  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
-  geom_hline(aes(yintercept = 0), linetype = "dashed") +
-  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
-  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
-  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
-  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
-  labs(x = "Adjusted parameter", y = "Sensitivity") +
-  theme_classic() + 
-  theme(legend.position = "none", 
-        strip.text = element_blank(), 
-        aspect.ratio = 0.8,
-        text = element_text(size = 12),
-        axis.title.y = element_blank()) +
-  coord_flip()
-```
+All parameters in Table @tbl-params were tested.
+The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.
 
@@
 tL_1 <- sum(contribL_1)
-digestL <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1
+digestL_1 <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1
 
@@
 tL_2 <- sum(contribL_2)
-digestL <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2
+digestL_2 <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2
 
@@
 tL_3 <- sum(contribL_3)
-digestL <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3
+digestL_3 <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3
 
@@
 * The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
-* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
-* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
-* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
+* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL_1,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
+* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL_2,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
+* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL_3,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
 
@@
   facet_grid(cols = vars(split)) +
-  theme_classic() +
   scale_x_continuous(breaks = seq(0, 1600, 120)) +
   scale_colour_manual(values = cohort_pal) +
-  theme(legend.position = "none") +
+  prettyplot() +
   labs(y = "Farm biomass", x = "Day of production")
@@
   labs(y = "Frequency", x = "Harvest weight") +
-  theme_classic() +
-  theme(
-    legend.position = "none", 
-    aspect.ratio = 0.75
-  )
+  prettyplot() +
+  theme(aspect.ratio = 0.75)
 ```
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  theme_classic() +
   scale_x_continuous(limits = c(0,1700)) +
@@
   labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
-  theme_classic() +
+  prettyplot() +
   theme(legend.position = "top", legend.title = element_blank())
@@
 
+* Parameter sensitivity results are in supplementary @sec-parameter-sensitivity
+
 In general, data outputs comes in the following dimensions:
@@
 * Day of production (impacted by location)
-
 * Main point is the difference between feeds (kg/t salmon).
@@
 
-qs::qread(farmrun_files[1]) %>% names()
+# qs::qread(farmrun_files[1]) %>% names()
 weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
@@
   geom_boxplot() +
-  theme_classic() +
+  prettyplot() +
   scale_fill_manual(values = feed_pal) +
@@
   facet_grid(~feed) +
-  theme_classic()
+  prettyplot()
 ```
@@
   facet_wrap(~feed) +
-  theme_classic()
+  prettyplot()
 ```
@@
   select(-excr_mean)
+
+ec <- excreted_all %>% 
+  group_by(feed) %>% 
+  reframe(P = mean(protein),
+          C = mean(carbohydrates),
+          L = mean(lipids)) %>% 
+  mutate(source = "excreted") %>% 
+  rbind(data.frame(
+    feed = c("reference", "past", "future"),
+    P = c(tP_1, tP_2, tP_3),
+    C = c(tC_1, tC_2, tC_3),
+    L = c(tL_1, tL_2, tL_3),
+    source = rep("feed", 3)
+  )) %>% 
+  pivot_longer(cols = c(P,L,C), names_to = "macro", values_to = "value", 
+               names_transform = list(macro = as.factor), values_transform = list(value = as.numeric)) %>% 
+  mutate(source = factor(source, levels = c("feed", "excreted")),
+         macro = factor(macro, levels = c("P", "L", "C"), labels = c("Protein", "Lipids", "Carbohydrates")),
+         feed = factor(feed, levels = c("reference", "past", "future")),
+         source = factor(source, levels = c("feed", "excreted"), labels = c("Feed", "Faeces")))
 ```
@@
 Unlike the uneaten feed, the composition of excreted faeces differs from that of the incoming feed.
-
-* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)
-
-```{r composition-throughtime}
+[Note that composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)]{.aside}
+
+```{r composition-throughtime, class.chunk = "aside"}
 #| eval: false
@@
 
-| Macro | Reference | Past | Future |
-|:-----------:|:---:|:---:|:---:|
-| Protein | `r tP_1` |  `r tP_2` |  `r tP_3` | 
-| Lipids | `r tL_1` | `r tL_2` |  `r tL_3` | 
-| Carbohydrates | `r tC_1` | `r tL_2` |  `r tL_3` |
+```{r fig-composition-comparison}
+#| eval: true
+#| fig-cap: Comparison of the composition of the reference (blue), past (red) and future (green) feed and faeces of salmon fed each feed.
+
+ggplot(ec, aes(x = source, y = 100*value, fill = feed)) +
+  geom_col(colour = "black", position = position_dodge(width = 0.9), alpha = 0.75) +
+  facet_grid(cols = vars(macro)) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal) +
+  scale_y_continuous(breaks = seq(0, 60, 10)) +
+  labs(y = "Composition (%)", x = "Source")
+```
 
@@
 
+# Supplementary stuff
+
+## Parameter sensitivity {#sec-parameter-sensitivity}
+
+```{r sensitivity data}
+sens_weight <- output_sens_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("results") %>% 
+  str_subset("weight") %>% 
+  qs::qread()
+
+sens_excr <- output_sens_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("results") %>% 
+  str_subset("total_excr") %>% 
+  qs::qread()
+
+sens_data <- rbind(sens_weight, sens_excr) %>% 
+  mutate(adj_param = factor(adj_param, levels = param_names$name))
+```
+
+Looking at @fig-param-sens-weight:
+
+* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
+* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
+There must be more up-to-date measurements for Atlantic salmon in particular.
+
+```{r fig-param-sens-weight}
+#| fig-cap: Impact of increasing each model parameter by 10% on final farm biomass (red) and total excreted nutrients (blue) over the whole production period.
+
+sens_data %>% 
+  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
+  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
+  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
+  geom_hline(aes(yintercept = 0), linetype = "dashed") +
+  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
+  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
+  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
+  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
+  labs(x = "Adjusted parameter", y = "Sensitivity") +
+  prettyplot() +
+  theme(strip.text = element_blank(), 
+        aspect.ratio = 0.8,
+        axis.title.y = element_blank()) +
+  coord_flip()
+```
+
 # References

### 2025-06-09 manuscript.qmd
Updates to display feeds better

@@
 
-feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
-cohort_pal <- c("1" = brewer.pal(9, "Set1")[1], "2" = brewer.pal(9, "Set1")[2], "3" = brewer.pal(9, "Set1")[3], "all" = "black")
+feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
+cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
+macro_pal <- c(
+  "protein" = "darkred", "P" = "darkred", 
+  "carbohydrates" = "steelblue", "C" = "steelblue", 
+  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
+)
 ```
@@
   CAN2 = c(-70, -54, 43, 48.5),
-  EUR = c(-26, 30, 51, 71),
+  EUR = c(-26, 30, 51, 72),
   CHI = c(-77.5, -62.5, -56, -25),
-  AUS = c(144, 149.5, -39.75, -44)
+  AUS = c(144, 149.5, -44, -39.75)
 )
@@
 #| fig-cap: |
-#|   Possibly use a patchwork map to show spatial results?
+#|   Example of a patchwork
 #| fig-height: 9
@@
   CHI = c(-78, -62, -55.5, -27),
-  AUS = c(144, 149, -40.75, -43.75)
-)
+  AUS = c(144, 149, -43.75, -40.75)
+)
+
+inset_boxes_sm <- map(inset_boxes_sm, function(bx) {
+  list(
+    xlims = bx[1:2],
+    ylims = bx[3:4],
+    labx = bx[1],
+    laby = bx[4]
+    )
+})
 
@@
 
-p_Aus <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["AUS"]][1:2], ylim = inset_boxes_sm[["AUS"]][3:4])  +
-  draw_label("E", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["AUS"]][1], y = inset_boxes_sm[["AUS"]][3], 
-             hjust = 0, vjust = 1)
+p_Can1 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
+  draw_label("A", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN1"]][["labx"]], 
+             y = inset_boxes_sm[["CAN1"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Can2 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
+  draw_label("B", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN2"]][["labx"]], 
+             y = inset_boxes_sm[["CAN2"]][["laby"]], 
+             hjust = 0.5, vjust = 0)
 p_Eur <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["EUR"]][1:2], ylim = inset_boxes_sm[["EUR"]][3:4]) +
+  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
+           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
   draw_label("C", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["EUR"]][1], y = inset_boxes_sm[["EUR"]][4], 
-             hjust = -1, vjust = 1)
+             x = inset_boxes_sm[["EUR"]][["labx"]], 
+             y = inset_boxes_sm[["EUR"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
 p_Chi <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CHI"]][1:2], ylim = inset_boxes_sm[["CHI"]][3:4]) +
+  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
   theme(legend.position = "right") +
   draw_label("D", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CHI"]][1], y = inset_boxes_sm[["CHI"]][4], 
+             x = inset_boxes_sm[["CHI"]][["labx"]], 
+             y = inset_boxes_sm[["CHI"]][["laby"]], 
              hjust = 0, vjust = 0)
-p_Can1 <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CAN1"]][1:2], ylim = inset_boxes_sm[["CAN1"]][3:4]) +
-  draw_label("A", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CAN1"]][1], y = inset_boxes_sm[["CAN1"]][4], 
-             hjust = -1, vjust = 0)
-p_Can2 <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CAN2"]][1:2], ylim = inset_boxes_sm[["CAN2"]][3:4]) +
-  draw_label("B", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CAN2"]][1], y = inset_boxes_sm[["CAN2"]][4], 
-             hjust = 0, vjust = 1)
+p_Aus <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
+           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
+  draw_label("E", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["AUS"]][["labx"]], 
+             y = inset_boxes_sm[["AUS"]][["laby"]], 
+             hjust = 0, vjust = 0)
 
@@
 ```{r feeds}
-feed_params <- file.path(output_species_data_path, "feed_params.qs") %>% qs::qread()
-
-df <- feed_params[["reference"]]
-contribP_1 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_1 <- sum(contribP_1)
-digestP_1 <- sum(df[["Proteins"]]$digest * contribP_1)/tP_1
-
-contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_1 <- sum(contribL_1)
-digestL_1 <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1
-
-contribC_1 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_1 <- sum(contribC_1)
-digestC_1 <- sum(df[["Carbohydrates"]]$digest * contribC_1)/tC_1
-
-df <- feed_params[["past"]]
-contribP_2 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_2 <- sum(contribP_2)
-digestP_2 <- sum(df[["Proteins"]]$digest * contribP_2)/tP_2
-
-contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_2 <- sum(contribL_2)
-digestL_2 <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2
-
-contribC_2 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_2 <- sum(contribC_2)
-digestC_2 <- sum(df[["Carbohydrates"]]$digest * contribC_2)/tC_2
-
-df <- feed_params[["future"]]
-contribP_3 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_3 <- sum(contribP_3)
-digestP_3 <- sum(df[["Proteins"]]$digest * contribP_3)/tP_3
-
-contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_3 <- sum(contribL_3)
-digestL_3 <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3
-
-contribC_3 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_3 <- sum(contribC_3)
-digestC_3 <- sum(df[["Carbohydrates"]]$digest * contribC_3)/tC_3
-```
+feed_params <- file.path(output_species_data_path, "feed_params.qs") %>%
+  qs::qread()
+
+feed_summary <- map_dfr(names(feed_params), function(feed) {
+  df <- feed_params[[feed]]
+  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
+    contrib <- df[[macro]]$proportion * df[[macro]]$macro
+    total <- sum(contrib)
+    digest <- sum(df[[macro]]$digest * contrib) / total
+        tibble(
+      feed = feed,
+      macro = macro,
+      total = total,
+      digest = digest
+    )
+  })
+}) %>%
+  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
+         feed = factor(feed, levels = c("reference", "past", "future")),
+         total_r = total * 100 %>% round(1),
+         digest_r = digest * 100 %>% round(1))
+```
+
+Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
 
@@
 
-* Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
-* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
-* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
-* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
-* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL_1,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
-* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL_2,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
-* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL_3,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
+* The reference feed is `r filter(feed_summary, feed == "reference", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "reference", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "reference", macro == "C")$total_r`% carbohydrate.
+* The past feed is `r filter(feed_summary, feed == "past", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "past", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "past", macro == "C")$total_r`% carbohydrate.
+* The future feed is `r filter(feed_summary, feed == "future", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "future", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "future", macro == "C")$total_r`% carbohydrate.
+* Within the reference feed, protein is overall `r filter(feed_summary, feed == "reference", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "reference", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "reference", macro == "C")$digest_r`% digestible.
+* Within the past feed, protein is overall `r filter(feed_summary, feed == "past", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "past", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "past", macro == "C")$digest_r`% digestible.
+* Within the future feed, protein is overall `r filter(feed_summary, feed == "future", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "future", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "future", macro == "C")$digest_r`% digestible.
+
+```{r feed summary ideas}
+#| fig-cap: | 
+#|   Ideas for how to present the differences between feeds.
+Top plot shows the protein (red), lipids (yellow) and carbohydrate (blue) composition, with the digestible portion shown darker and the undigestible portion shown lighter.
+Bottom plot shows the proportion of each feed composed of each types of ingredient.
+
+p1 <- feed_summary %>%
+  mutate(digest_total = digest * total) %>% 
+  ggplot(aes(x = feed, y = total, fill = macro)) +
+  geom_col(position = "dodge", alpha = 0.55, colour = "black") +
+  geom_col(mapping = aes(y = digest_total), position = "dodge", alpha = 1, colour = "black") +
+  scale_fill_manual(values = macro_pal) +
+  scale_y_continuous(breaks = seq(0,0.5,0.1), labels = seq(0,50,10)) +
+  scale_x_discrete(labels = c("reference" = "Reference", "past" = "Past", "future" = "Future")) +
+  labs(x = "Feed", y = "Proportion (%)") +
+  prettyplot()
+
+feed_ings <- rbind(
+  feed_params[[1]][[1]] %>% mutate(feed = as.factor("reference")), 
+  feed_params[[2]][[1]] %>% mutate(feed = as.factor("past")), 
+  feed_params[[3]][[1]] %>% mutate(feed = as.factor("future"))
+) %>%
+  rename(protein = macro) %>%
+  mutate(
+    category = case_when(
+      str_detect(ingredient, "fish-oil") ~ "fish",
+      str_detect(ingredient, "fishmeal") ~ "fish",
+      str_detect(ingredient, "krill") ~ "other-marine",
+      str_detect(ingredient, "soy") ~ "legume",
+      str_detect(ingredient, "pea") ~ "legume",
+      str_detect(ingredient, "guar") ~ "legume",
+      str_detect(ingredient, "faba") ~ "legume",
+      str_detect(ingredient, "corn") ~ "wheat-corn",
+      str_detect(ingredient, "wheat") ~ "wheat-corn",
+      str_detect(ingredient, "chicken") ~ "chicken",
+      str_detect(ingredient, "bacteri") ~ "bact-fungi-micro",
+      str_detect(ingredient, "yeast") ~ "bact-fungi-micro",
+      str_detect(ingredient, "spirulina") ~ "bact-fungi-micro",
+      str_detect(ingredient, "bsf") ~ "insect",
+      T ~ "other-plant"
+    ) %>% 
+      factor(levels = c("fish", "other-marine", "chicken", "wheat-corn", "legume", "other-plant", "insect", "bact-fungi-micro"))
+  )
+
+p_ings <- feed_ings %>% 
+  mutate(feed = factor(feed, levels = c("reference", "past", "future"), labels = c("Reference", "Past", "Future"))) %>% 
+  group_by(feed, category) %>%
+  reframe(proportion = sum(proportion)) %>% 
+  ggplot(aes(x = "", y = proportion, fill = category)) +
+  geom_col(width = 1, colour = "black") +
+  coord_polar("y", start = 0) +
+  scale_fill_manual(
+    name = "Ingredient category",
+    values = c("fish" = "royalblue3", "other-marine" = "turquoise2", "chicken" = "hotpink1", "wheat-corn" = "moccasin", "legume" = "forestgreen", "other-plant" = "darkolivegreen1", "insect" = "firebrick3", "bact-fungi-micro" = "darkorange"),
+    labels = c("Fish meal or oil", "Other marine ingredients", "Chicken", "Wheat and corn", "Legumes", "Other plant ingredients", "Insects", "Bacteria, fungi or microalgae")) +
+  facet_grid(cols = vars(feed)) +
+  theme_void() +
+  theme(
+    text = element_text(family = "serif", size = 12, colour = "black"),
+    legend.position = "bottom",
+    strip.text = element_blank(),
+    strip.text.x = element_text(size = 14)
+  )
+
+plot_grid(p1, p_ings, nrow = 2)
+```
 
 ## Model population and biomass
+
+```{r raw biomass and weight data}
+farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
+  list.files(full.names = T)
+
+weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>%
+  bind_rows()
+biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>%
+  bind_rows()
+```
 
@@
 
-```{r weight and biomass data}
-farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
-  list.files(full.names = T)
-
-# qs::qread(farmrun_files[1]) %>% names()
-weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
-biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
-```
-
 ## Uneaten feed
@@
          uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
-
+```
+
+```{r uneaten feed analysis}
 uneaten_total_stats <- uneaten_total %>% 
@@
          mean = round(mean,2))
-```
-
-### Amount
-
-* Total reference uneaten feed across a cohort (548 days) ranged from `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]`.
-* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
+
+uneaten_total_compare <- uneaten_total %>% 
+  group_by(feed, farm_ID) %>% 
+  reframe(total = sum(uneat_biom_mean)) %>% 
+  pivot_wider(names_from = "feed", values_from = "total", id_cols = "farm_ID") %>% 
+  mutate(diff_past = past-reference,
+         diff_future = future-reference,
+         diffperc_past = diff_past/reference,
+         diffperc_future = diff_future/reference) %>% 
+  dplyr::select(-c(reference, future, past)) %>% 
+  pivot_longer(names_to = c("measure", "feed"), names_sep = "_", values_to = "value",
+               cols = contains("diff"), names_transform = list(measure = as.factor, feed = as.factor)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(value),
+          max = maxna(value),
+          mean = meanna(value)) %>% 
+  mutate(
+    min = case_when(measure == "diffperc" ~ 100*min,
+                    T ~ min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
+    max = case_when(measure == "diffperc" ~ 100*max,
+                    T ~ max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
+    mean = case_when(measure == "diffperc" ~ 100*mean,
+                     T ~ mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
+    )
+```
+
+Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
+`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
+`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
+`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish.
+
+* Differences between the feeds were very small, with the past scenario producing 
+* but slightly less uneaten feed was lost in the reference scenario. Uneaten past feed ranged from 
 `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from
@@
 
+### Amount
+
 * Total reference excreted faeces across a cohort (548 days) ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
@@
 ```
-
-### Amount
 

### 2025-06-09 docs/manuscript.qmd
Forgot about jekyll's underscore vendetta
Fix up macronutrient summary

--- 2025-06-04 manuscript.qmd
@@
 # Author roles: "writing – original draft", "writing – review & editing", "formal analysis", "funding acquisition", "conceptualization", "data curation", "investigation", "methodology", "project administration", "resources", "software", "supervision", "validation", "visualization"
-author:
-  - name: Tormey Reimer
-    orcid: 0000-0002-5983-2798
-    corresponding: true
-    email: tormey.reimer@utas.edu.au
-    role: 
-      - methodology: supporting
-      - analysis: lead
-      - writing: lead
-    affil-id: [1,2]
-  - name: Richard S. Cottrell
-    orcid: 0000-0002-6499-7503
-    corresponding: false
-    roles: 
-      - conceptualization: lead
-      - methodology: lead
-      - writing: supporting
-    # affil-id: [1,2]
-  - name: Alexandra Johne
-    orcid: 0000-0002-2816-7983
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    affil-id: 3
-  - name: Sowdamini Sesha Prasad
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Marceau Cormery
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Gage Clawson
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Scott Hadley
-    # orcid: 
-    corresponding: false
-    roles: 
-      - methodology: supporting
-    # affil-id: [3,2]
-  - name: Helen Hamilton
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Benjamin S. Halpern
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Catriona Macleod
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Camille White
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-    # affil-id: [3,2]
-  - name: Julia L. Blanchard
-    # orcid: 
-    corresponding: false
-    roles: 
-      - conceptualization: supporting
-      - methodology: supporting
-      - analysis: supporting
-      - editing: supporting
-    # affil-id: [3,2]
-
-affiliations:
-  - id: 1
-    name: Institute for Marine and Antarctic Studies
-    group: Fisheries & Aquaculture
-    address: 29 Nubeena Crescent
-    city: Taroona
-    region: TAS
-    country: Australia
-    postal-code: 7053
-    url: https://www.imas.utas.edu.au/
-  - id: 2
-    name: Centre for Marine Socioecology
-    url: https://marinesocioecology.org/
-  - id: 1
-    name: Institute for Marine and Antarctic Studies
-    group: Ecology & Biodiversity
-    # address: 29 Nubeena Crescent
-    # city: Taroona
-    # region: TAS
-    # country: Australia
-    # postal-code: 7053
-    url: https://www.imas.utas.edu.au/
-  # - id: 3
-  #   name: Heriott-Watt University, Institute for Life and Earth Sciences
-  #   department: School of Energy, Geoscience, Infrastructure and Society
-  #   address: Franklin Road
-  #   city: Stromness
-  #   region: Orkney
-  #   country: United Kingdom
-  #   postal-code: KW16 3AN
-  #   url: https://www.hw.ac.uk/
-# keywords:
-#   - keyword
-#   - keyword
-# abstract: |
-#   Any new aquaculture venture...
-# plain-language-summary: |
-#   Plain language summary goes here....
-# key-points:
-#   - Point 1
-#   - Point 2
+
 bibliography: ["refs.bib", "manual-refs.bib"]
@@
 pop_params <- qread(pop_params_file)
-```
-
-# Introduction
-
-[This intro is copied verbatim from work done during one of the early workshops.]{.aside}
-
-Aquaculture is now the dominant form of aquatic animal food (herein ‘seafood’) production and is expected to be the primary way we meet future seafood demand.
-Freshwater systems will likely continue to provide the majority of farmed seafood but marine aquaculture is also poised to expand substantially in numerous areas.
-Farmed marine fish and invertebrates are produced near exclusively in coastal waters, and nearly three quarters of this production is dependent on human-made feeds.
-Nearshore locations and feed inputs are necessary to maintain profitable and productive farming operations but coastal aquaculture generates a number of challenges.
-In the crowded coastal zone, aquaculture operations can conflict with other stakeholder uses such as recreation, fishing, renewable energy, transport, and tourism.
-And while farming marine fish typically generates a far smaller nutrient footprint than livestock farming, the overt nature of aquaculture in nearshore regions and evidence of  localised nutrient impacts around fish farms remains a primary public and scientific concern.
-Identifying strategies that reduce ecosystem impacts from fish farm waste therefore represents an important goal for improving marine aquaculture sustainability and maintaining the sector’s social licence to operate.
-
-Aquaculture feeds represent an important lever for reducing nutrient waste impacts around fish farms.
-Like all farmed animals, fish and invertebrates must digest the nutrients contained in feeds before they can be used for growth.
-Any nutrients left undigested are egested as solid waste, and dissolved wastes are excreted as metabolic waste products.
-Further, some feed inevitably remains uneaten and is lost to the surrounding ecosystem.
-Particulate organic matter (both feed and faeces) that settles can simplify benthic communities as the oxygen demand from its decomposition drives the production of sulphides that kill less mobile faunal, encouraging a lower diversity of opportunistic scavengers and the growth of bacterial mats (e.g., Beggiatoa spp).
-Thus, the chemical composition of the ingredients used in aquaculture feeds and their digestibility for the farmed species has significant implications for the nature and reactivity of the waste generate by marine aquaculture.
-
-Firstly the overall volume of nutrient waste is dictated by the nature and intensity of production, that is the farm size, the density of farmed animals and the feed requirements and efficiency of the species grown.
-SecondlDeposition of waste is heavily influenced by water depth and current speed at the farming site.
-Once
-
-As farmed fish and invertebrates are fed, whatever
-
-Nutand its impact on marine ecosystems is influenced by many factors. 
-* Farm size
-* Depth
-* Current speed
-* Benthic impact - sediment type/faunal assemblages/wider marine community
-* High turnover environments - nitrogen enriched areas
-* Feed influences all of these things
-
-The primary source of organic waste from fed aquaculture production comes from the excretion and faeces of the farmed animals and through uneaten feed that dissolves in the water column or settles on the benthos.
-The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals.
-
-## P2
-
-* Waste from aquaculture farms and it’s impact is influenced by many things but the composition of feeds plays a central role.
-* Waste from aquaculture farms has multiple sources. 
-* The primary source of organic waste comes from the faeces and excretion of the fish or invertebrates.
-* Uneaten feed produced another key source.
-* The nature and impact of this waste are influenced heavily by the composition of the feeds fed to farmed animals
-* Many marine fish are naturally carnivorous so diets used to be high in fishmeal and oil but increasing fishmeal and oil prices along with concerns over the sustainability of marine ingredients have led to a reduction in their use across multiple farmed taxa
-* In lieu of fishmeal and oil, many plant-based ingredients such as soy protein concentrate, canola oil, and wheat gluten have replaced them. 
-* Changes in feed composition influences the digestibility of the nutrients held in each feed and can alter the composition of waste.
-* Of particular concern are changes (increases) to the presence of reactive nitrogen and phosphorus in coastal waters that could have an effect on eutrophication.
-
-## P3
-
-* Whether or not nutrients lead to eutrophication depends on the sensitivity of the receiving environment
-* Ecosystems that are already enriched through natural processes and whose biota is well adapted to substantial fluxes in available nutrients (e.g.
-upwelling zones, dynamic coastal communities) may be less sensitive while oligotrophic ecosystem are likely to see considerable changes under nutrient enrichment scenarios.
-* To understand the impact of aquaculture waste under present day or future scenarios we need to quantify the volume, nature, and location of mariculture waste and determine the sensitivity of the receiving environments to that waste.
-Yet only recent estimates even give us the estimated location of marine farms let alone the volume of nature of the waste produced.
-To address this gap, we use existing maps of mariculture location with a bioenergtic model
+
+prettyplot <- function() {
+  theme_classic() +
+    theme(legend.position = "none",
+          text = element_text(family = "serif", size = 12, colour = "black"),
+          axis.title.x = element_text(vjust = 0.5),
+          axis.title.y = element_text(hjust = 0.5))
+}
+
+feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
+cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
+macro_pal <- c(
+  "protein" = "darkred", "P" = "darkred", 
+  "carbohydrates" = "steelblue", "C" = "steelblue", 
+  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
+)
+```
+
+```{r custom fuctions}
+#| code-summary: Function to create sf polygons from bounding boxes
+
+create_boxes <- function(box_list, label_positions, offset_deg) {
+  boxes <- list()
+  labels <- list()
+
+  for(i in seq_along(box_list)) {
+    name <- names(box_list)[i]
+    coords <- box_list[[i]]
+    pos <- label_positions[i]
+
+    # Create polygon from bounding box coordinates
+    box_coords <- matrix(c(
+      coords[1], coords[3],  # lonmin, latmin
+      coords[2], coords[3],  # lonmax, latmin  
+      coords[2], coords[4],  # lonmax, latmax
+      coords[1], coords[4],  # lonmin, latmax
+      coords[1], coords[3]   # close polygon
+    ), ncol = 2, byrow = TRUE)
+
+    # Create sf polygon
+    poly <- st_polygon(list(box_coords))
+    boxes[[i]] <- st_sfc(poly, crs = 4326)
+
+    # Calculate label position based on specification
+    label_coords <- get_label_position(coords, pos, offset_deg[i])
+    label_point <- st_point(c(label_coords[1], label_coords[2]))
+    labels[[i]] <- st_sfc(label_point, crs = 4326)
+  }
+
+  # Combine into sf objects
+  boxes_sf <- st_sf(
+    name = names(box_list),
+    letter = LETTERS[1:length(box_list)],
+    geometry = do.call(c, boxes)
+  )
+
+  labels_sf <- st_sf(
+    name = names(box_list), 
+    letter = LETTERS[1:length(box_list)],
+    geometry = do.call(c, labels)
+  )
+
+  return(list(boxes = boxes_sf, labels = labels_sf))
+}
+
+# Helper function to calculate label positions
+get_label_position <- function(coords, position, offset) {
+  lonmin <- coords[1]
+  lonmax <- coords[2]
+  latmin <- coords[3]
+  latmax <- coords[4]
+
+  # Parse position string
+  parts <- strsplit(position, "_")[[1]]
+  vertical <- parts[1]    # "top" or "bottom"
+  horizontal <- parts[2]  # "left" or "right"
+  location <- parts[3]    # "inside" or "outside"
+
+  # Base coordinates for corners
+  if(vertical == "bottom") {base_lat <- latmin} else {base_lat <- latmax}
+  if(horizontal == "right") {base_lon <- lonmax} else {base_lon <- lonmin}
+
+  # Apply offset for outside positioning
+  if(location == "outside") {
+    if(horizontal == "left") {base_lon <- base_lon-offset} else {base_lon <- base_lon+offset}
+    if(vertical == "top") {base_lat <- base_lat + offset} else {base_lat <- base_lat - offset}
+  }
+
+  return(c(base_lon, base_lat))
+}
+
+lim_robin <- function(lons = c(144.0, 149.5), lats = c(-39.75, -44.00)) {
+  coords <- data.frame(lon = lons, lat = lats) %>%
+    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
+    st_transform(crs = "+proj=robin") %>% 
+    st_coordinates()
+  list(
+    xlims = range(coords[, "X"]),
+    ylims = range(coords[, "Y"])
+  )
+}
+
+```
+
+This document was last updated at `r format(Sys.time(), "%H:%M")` on `r format(Sys.time(), "%d %b, %Y")`.
 
 # Methods
-## Model and approach
-
-[Unfinished.
-Need to work out how much should be transposed from @baldan_r_2018.
-One thing that definitely needs to be stated is the individual ingredient (rather than whole food) tracking, the use of cohorts, and the new method for calculating population.]{.aside}
-
-We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
-The model simulates growth at an individual level, calculating the change in individual weight through time using:
-
-$$
-\frac{dw}{dt} = \frac{A-C}{\epsilon}
-$$
-
-Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$). 
-Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
-Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
-All individuals have a fixed mortality rate to simulate stocking and harvesting.
-
-## Farm temperature forcings
-
-```{r farm info}
-#| code-summary: Get general farm info
-
-farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
-farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
-farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread() %>% 
-    mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N") %>% as.factor())
-
-farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
-  rename(farm_ID = farm_id)
-
-sorted_countries <- farm_coords %>% 
-  merge(farms_geometry, by = "farm_ID") %>% 
-  group_by(country) %>% 
-  reframe(av_lat = mean(lat)) %>% 
-  arrange(-av_lat) %>% 
-  pull(country) %>% 
-  unique()
-```
-
-```{r farm temperature data}
-#| code-summary: Get the farm temperature forcings
-
-farm_temp_means <- farm_ts_data %>% 
-  group_by(farm_ID) %>% 
-  reframe(mean_temp = mean(temp_c)) %>% 
-  merge(farms_geometry, by = "farm_ID") %>% 
-  merge(farm_coords, by = "farm_ID") %>% 
-  dplyr::filter(!farm_ID %in% farms_to_omit)
-
-overall_mean <- mean(farm_temp_means$mean_temp)
-overall_sd <- sd(farm_temp_means$mean_temp)
-
-rm(farm_ts_data)
-```
-
-Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$ to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$ ($\pm$ `r round(overall_sd, 1)` SD).
-Farms with a mean temperature of $\leq 6^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms).
-The total number of farms included in this analysis was therefore `r nrow(farm_temp_means)`.
-
-```{r fig-farm-mean-temps}
-#| fig-cap: |
-#|   Potential options for showing farm site mean temperatures.
-Top left: Mean temperature by latitude across countries.
-Top right: Frequency distribution of mean temperatures by hemisphere.
-Bottom: global distribution of mean temperatures.
-#| fig-height: 9
-#| fig-width: 9.5
-
-worldmap <- ne_countries(scale = "medium", returnclass = "sf")
-
-p1 <- ggplot(data = worldmap, aes(geometry = geometry)) +
-  geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
-  coord_sf() +
-  theme_classic()
-
-p2 <- farm_temp_means %>% 
-  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
-  geom_point(size = 2) +
-  scale_colour_brewer(palette = "Set1") +
-  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
-  theme_classic() +
-  theme(legend.position = "top", legend.title = element_blank())
-
-p3 <- farm_temp_means %>% 
-  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
-  ggplot(aes(x = mean_temp, fill = hemisphere)) +
-  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
-  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
-  theme_classic() +
-  theme(legend.position = "top", legend.title = element_blank())
-
-(p2 + p3) / p1 + plot_layout(heights = c(1, 1.5))
-```
-
-```{r patchwork map}
-#| fig-cap: |
-#|   Possibly use a patchwork map to show spatial results?
-#| fig-height: 9
-#| fig-width: 9.5
-
-worldmap <- ne_countries(scale = "large", returnclass = "sf")
-
-AUS_bounds <- c(144, 149.5, -39.75, -44)
-CAN1_bounds <- c(-132, -122, 47.75, 54.25)
-CAN2_bounds <- c(-70, -54, 43, 48.5)
-CHI_bounds <- c(-77.5, -62.5, -56, -25)
-EUR_bounds <- c(-26, 30, 51, 71)
-
-p_ALL <- ggplot(data = worldmap, aes(geometry = geometry)) +
-  geom_sf(fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(colour = mean_temp), size = 1.5) +
-  coord_sf() +
-  theme_classic()
-
-no_margins <- function() {
-  theme(legend.position = "none", 
-        plot.margin = margin(),
-        axis.title = element_blank())
-}
-
-p_Aus <- p_ALL + coord_sf(xlim = AUS_bounds[1:2], ylim = AUS_bounds[3:4], expand = FALSE) + no_margins()
-p_Eur <- p_ALL + coord_sf(xlim = EUR_bounds[1:2], ylim = EUR_bounds[3:4], expand = FALSE) + no_margins()
-p_Chi <- p_ALL + coord_sf(xlim = CHI_bounds[1:2], ylim = CHI_bounds[3:4], expand = FALSE) + no_margins()
-p_Can <- p_ALL + coord_sf(xlim = CAN1_bounds[1:2], ylim = CAN1_bounds[3:4], expand = FALSE) + no_margins()
-p_USA <- p_ALL + coord_sf(xlim = CAN2_bounds[1:2], ylim = CAN2_bounds[3:4], expand = FALSE) + no_margins()
-
-subplot <- (p_Eur/p_Aus) + plot_layout(heights = c(1.5, 1))
-finalplot <- (p_Can + p_USA) / (p_Chi + subplot) + 
-  plot_layout(widths = c(1, 1.5), heights = c(1, 2)) &
-  theme(plot.margin = margin(0, 0, 0, 0))
-finalplot
-```
-
-```{r fig-cohorts}
-#| fig-cap: Example of cohorts
-#| eval: false
-
-fnms <- output_cohort_growth_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("biomass")
-
-df <- fnms[1] %>% read_parquet() %>% 
-  filter(feed == "reference") %>% 
-  mutate(mean = set_units(mean, "g") %>% set_units("t"),
-         sd = set_units(sd, "g") %>% set_units("t"))
-
-ggplot(df, aes(x = yday, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
-  geom_line(linewidth = 0.75) +
-  geom_ribbon(linetype = "dotted", alpha = 0) +
-  scale_x_continuous(breaks = seq(0, 2000, 200)) +
-  labs(y = "Farm biomass", x = "Day of the year") +
-  theme_classic() +
-  theme(legend.position = "none", aspect.ratio = 0.75)
-
-yrs <- max(df$yday)/365
-harvests <- df %>% 
-  group_by(cohort) %>% 
-  reframe(mean = maxna(mean),
-          sd = maxna(sd))
-
-sum(harvests$mean)/yrs
-mean(harvests$sd)/yrs
-```
-
 ### Feeding rate
@@
 
+## Farm temperature forcings
+
+```{r farm info}
+#| code-summary: Get general farm info
+
+farms_to_omit <- file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs") %>% qs::qread()
+farm_ts_data <- file.path(output_farm_data_path, "farm_ts_data.qs") %>% qs::qread()
+farm_coords <- file.path(output_farm_data_path, "farm_coords.qs") %>% qs::qread() %>% 
+    mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N") %>% as.factor())
+
+farms_geometry <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread() %>% 
+  rename(farm_ID = farm_id)
+
+sorted_countries <- farm_coords %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  group_by(country) %>% 
+  reframe(av_lat = mean(lat)) %>% 
+  arrange(-av_lat) %>% 
+  pull(country) %>% 
+  unique()
+```
+
+```{r farm temperature data}
+#| code-summary: Get the farm temperature forcings
+
+farm_temp_means <- farm_ts_data %>% 
+  group_by(farm_ID) %>% 
+  reframe(mean_temp = mean(temp_c)) %>% 
+  merge(farms_geometry, by = "farm_ID") %>% 
+  merge(farm_coords, by = "farm_ID") %>% 
+  dplyr::filter(!farm_ID %in% farms_to_omit)
+
+overall_mean <- mean(farm_temp_means$mean_temp)
+overall_sd <- sd(farm_temp_means$mean_temp)
+
+rm(farm_ts_data)
+```
+
+Mean daily temperatures at the farms globally ranged from  from `r round(min(farm_temp_means$mean_temp), 1)`$^{\circ}$C to `r round(max(farm_temp_means$mean_temp), 1)`$^{\circ}$C, with an overall mean of `r round(overall_mean, 1)`$^{\circ}$C ($\pm$ `r round(overall_sd, 1)`$^{\circ}$C SD).
+Farms with a mean temperature of $\leq$6$^\circ$C were excluded (`r as.integer(length(farms_to_omit))` farms).
+The total number of farms included in the analysis was therefore `r nrow(farm_temp_means)`.
+
+```{r fig-farm-mean-temps}
+#| fig-cap: |
+#|   Potential options for showing farm site mean temperatures.
+Top left: Mean temperature by latitude across countries.
+Top right: Frequency distribution of mean temperatures by hemisphere.
+Bottom: global distribution of mean temperatures.
+#| fig-height: 9
+#| fig-width: 9.5
+
+worldmap <- ne_countries(scale = "medium", returnclass = "sf") %>% st_transform(crs = "+proj=robin")
+graticules <- st_graticule(worldmap, lon = seq(-180, 180, 30), lat = seq(-90, 90, 30))
+
+inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 47.75, 54.25),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-26, 30, 51, 72),
+  CHI = c(-77.5, -62.5, -56, -25),
+  AUS = c(144, 149.5, -44, -39.75)
+)
+labels_spec <- c(CAN1 = "bottom_left_outside", CAN2 = "bottom_right_outside", EUR = "bottom_left_outside", CHI = "top_left_outside", AUS = "bottom_left_outside")
+labels_offset <- c(CAN1 = 1, CAN2 = 2, EUR = 1.75, CHI = 1.75, AUS = 3.5)
+
+box_data <- create_boxes(box_list = inset_boxes, # see function create_boxes above
+                         label_positions = unname(labels_spec),
+                         offset_deg = unname(labels_offset))
+boxes_robinson <- st_transform(box_data$boxes, crs = "+proj=robin")
+labels_robinson <- st_transform(box_data$labels, crs = "+proj=robin")
+farm_temp_robinson <- st_sf(farm_temp_means) %>% st_transform(crs = "+proj=robin")
+
+p1 <- ggplot() +
+  geom_sf(data = graticules, color = "gray80", size = 0.3) +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_robinson, aes(color = mean_temp), size = 1) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 25,barheight = 1.5
+  )) +
+  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
+  geom_sf_text(data = labels_robinson, aes(label = letter), 
+               color = "darkred", size = 5, fontface = "bold", 
+               hjust = 0.5, vjust = 0.5) +
+  theme_void()
+
+p2 <- farm_temp_means %>% 
+  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
+  geom_point(size = 2) +
+  scale_colour_brewer(palette = "Set1") +
+  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
+  prettyplot() +
+  theme(legend.position = "top", legend.title = element_blank())
+
+p3 <- farm_temp_means %>% 
+  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
+  ggplot(aes(x = mean_temp, fill = hemisphere)) +
+  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
+  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
+  prettyplot() +
+  theme(legend.position = "top", legend.title = element_blank())
+
+(p2 + p3) / p1 + plot_layout(heights = c(1, 1.5))
+```
+
+```{r patchwork-map-mercator}
+#| fig-cap: |
+#|   Example of a patchwork
+#| fig-height: 9
+#| fig-width: 9.5
+
+no_margins <- function() {
+  theme(legend.position = "none", 
+        plot.margin = margin(0, 0, 0, 0),
+        axis.title = element_blank())
+}
+
+inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 48.5, 54),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-23, 28.5, 52, 71),
+  CHI = c(-78, -62, -55.5, -27),
+  AUS = c(144, 149, -43.75, -40.75)
+)
+
+inset_boxes_sm <- map(inset_boxes_sm, function(bx) {
+  list(
+    xlims = bx[1:2],
+    ylims = bx[3:4],
+    labx = bx[1],
+    laby = bx[4]
+    )
+})
+
+worldmap <- ne_countries(scale = "large", returnclass = "sf")
+p1 <- ggplot() +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 1) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 1.5, barheight = 20
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+p_Can1 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
+  draw_label("A", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN1"]][["labx"]], 
+             y = inset_boxes_sm[["CAN1"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Can2 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
+  draw_label("B", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN2"]][["labx"]], 
+             y = inset_boxes_sm[["CAN2"]][["laby"]], 
+             hjust = 0.5, vjust = 0)
+p_Eur <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
+           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
+  draw_label("C", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["EUR"]][["labx"]], 
+             y = inset_boxes_sm[["EUR"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Chi <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
+  theme(legend.position = "right") +
+  draw_label("D", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CHI"]][["labx"]], 
+             y = inset_boxes_sm[["CHI"]][["laby"]], 
+             hjust = 0, vjust = 0)
+p_Aus <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
+           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
+  draw_label("E", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["AUS"]][["labx"]], 
+             y = inset_boxes_sm[["AUS"]][["laby"]], 
+             hjust = 0, vjust = 0)
+
+grid_1 <- cowplot::plot_grid(p_Can1, p_Can2, ncol = 2, rel_widths =  c(1, 1.35))
+grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
+grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
+
+cowplot::plot_grid(
+  grid_1, grid_3,
+  nrow = 2,
+  rel_heights = c(1, 1.5)        # relative row heights
+)
+```
+
 ## Production parameters
 
-* Salmon cohorts were always grown for 548 days
-* Salmon cohorts were initialised Spring.
+Salmon were grown for 548 days and were initialised Spring.
 This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
-* Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
-
-## Parameterisation for Atlantic salmon
+Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
+
+## Model parameterisation
 
@@
 
-Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as:
-
-$$
-S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}
-$$
-
-where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-
-* All parameters in Table @tbl-params were tested across all farms (all temperatures)
-* Used a population of 100 in each farm
-
-```{r sensitivity data}
-sens_weight <- output_sens_data_path %>% 
+Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
+All parameters in Table @tbl-params were tested.
+The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.
+
+## Modelled experimental feeds {#sec-feeds}
+
+```{r feeds}
+feed_params <- file.path(output_species_data_path, "feed_params.qs") %>%
+  qs::qread()
+
+feed_summary <- map_dfr(names(feed_params), function(feed) {
+  df <- feed_params[[feed]]
+  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
+    contrib <- df[[macro]]$proportion * df[[macro]]$macro
+    total <- sum(contrib)
+    digest <- sum(df[[macro]]$digest * contrib) / total
+        tibble(
+      feed = feed,
+      macro = macro,
+      total = total,
+      digest = digest
+    )
+  })
+}) %>%
+  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
+         feed = factor(feed, levels = c("reference", "past", "future")),
+         total_r = total * 100 %>% round(1),
+         digest_r = digest * 100 %>% round(1))
+```
+
+Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
+
+[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed?]{.aside}
+
+The reference feed was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "reference", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "reference", macro == "C")$total, 1)`% carbohydrate, the past feed was 
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "past", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "past", macro == "C")$total, 1)`% carbohydrate, and the future feed was 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "future", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "C")$total, 1)`% carbohydrate.
+
+Ingredients are tracked seperately through the model with their own digestibility coefficients. Overall, proteins within the reference feed were 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`% digestible, proteins within the past feed were 
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`% digestible, and proteins within the future feed were 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% digestible.
+The digestibility of the other macronutrients are assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`% for carbohydrates and `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`% for lipids.
+
+```{r fig-feed-summary-ideas}
+#| fig-height: 7.5
+#| fig-cap: | 
+#|   Ideas for how to present the differences between feeds.
+Top plot shows the protein (red), lipids (yellow) and carbohydrate (blue) composition, with the digestible portion shown darker and the undigestible portion shown lighter.
+Bottom plot shows the proportion of each feed composed of each types of ingredient.
+
+p1 <- feed_summary %>%
+  mutate(digest_total = digest * total) %>% 
+  ggplot(aes(x = feed, y = total, fill = macro)) +
+  geom_col(position = "dodge", alpha = 0.55, colour = "black") +
+  geom_col(mapping = aes(y = digest_total), position = "dodge", alpha = 1, colour = "black") +
+  scale_fill_manual(values = macro_pal) +
+  scale_y_continuous(breaks = seq(0,0.5,0.1), labels = seq(0,50,10)) +
+  scale_x_discrete(labels = c("reference" = "Reference", "past" = "Past", "future" = "Future")) +
+  labs(x = "Feed", y = "Proportion (%)") +
+  prettyplot()
+
+feed_ings <- rbind(
+  feed_params[[1]][[1]] %>% mutate(feed = as.factor("reference")), 
+  feed_params[[2]][[1]] %>% mutate(feed = as.factor("past")), 
+  feed_params[[3]][[1]] %>% mutate(feed = as.factor("future"))
+) %>%
+  rename(protein = macro) %>%
+  mutate(
+    category = case_when(
+      str_detect(ingredient, "fish-oil") ~ "fish",
+      str_detect(ingredient, "fishmeal") ~ "fish",
+      str_detect(ingredient, "krill") ~ "other-marine",
+      str_detect(ingredient, "soy") ~ "legume",
+      str_detect(ingredient, "pea") ~ "legume",
+      str_detect(ingredient, "guar") ~ "legume",
+      str_detect(ingredient, "faba") ~ "legume",
+      str_detect(ingredient, "corn") ~ "wheat-corn",
+      str_detect(ingredient, "wheat") ~ "wheat-corn",
+      str_detect(ingredient, "chicken") ~ "chicken",
+      str_detect(ingredient, "bacteri") ~ "bact-fungi-micro",
+      str_detect(ingredient, "yeast") ~ "bact-fungi-micro",
+      str_detect(ingredient, "spirulina") ~ "bact-fungi-micro",
+      str_detect(ingredient, "bsf") ~ "insect",
+      T ~ "other-plant"
+    ) %>% 
+      factor(levels = c("fish", "other-marine", "chicken", "wheat-corn", "legume", "other-plant", "insect", "bact-fungi-micro"))
+  )
+
+p_ings <- feed_ings %>% 
+  mutate(feed = factor(feed, levels = c("reference", "past", "future"), labels = c("Reference", "Past", "Future"))) %>% 
+  group_by(feed, category) %>%
+  reframe(proportion = sum(proportion)) %>% 
+  ggplot(aes(x = "", y = proportion, fill = category)) +
+  geom_col(width = 1, colour = "black") +
+  coord_polar("y", start = 0) +
+  scale_fill_manual(
+    name = "Ingredient category",
+    values = c("fish" = "royalblue3", "other-marine" = "turquoise2", "chicken" = "hotpink1", "wheat-corn" = "moccasin", "legume" = "forestgreen", "other-plant" = "darkolivegreen1", "insect" = "firebrick3", "bact-fungi-micro" = "darkorange"),
+    labels = c("Fish meal or oil", "Other marine ingredients", "Chicken", "Wheat and corn", "Legumes", "Other plant ingredients", "Insects", "Bacteria, fungi or microalgae")) +
+  facet_grid(cols = vars(feed)) +
+  theme_void() +
+  theme(
+    text = element_text(family = "serif", size = 12, colour = "black"),
+    legend.position = "bottom",
+    legend.title = element_blank(), 
+    strip.text = element_blank(),
+    strip.text.x = element_text(size = 14)
+  )
+
+plot_grid(p1, p_ings, nrow = 2)
+```
+
+## Model population and biomass
+
+```{r raw biomass and weight data}
+farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
+  list.files(full.names = T)
+
+weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>%
+  bind_rows()
+biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>%
+  bind_rows()
+```
+
+```{r fig-cohorts}
+#| fig-cap: | 
+#|   Example of how the overlapping cohorts combine into a single farm production curve (in this case biomass).
+The left plot shows the farm biomass produced by each cohort from initialisation to harvest, while the right plot shows the combined farm biomass over the course of a single production period of 548 days.
+#| eval: true
+
+fnms <- output_farm_growth_data_path %>% 
   list.files(full.names = T) %>% 
-  str_subset("results") %>% 
-  str_subset("weight") %>% 
-  qs::qread()
-
-sens_excr <- output_sens_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("results") %>% 
-  str_subset("total_excr") %>% 
-  qs::qread()
-
-sens_data <- rbind(sens_weight, sens_excr) %>% 
-  mutate(adj_param = factor(adj_param, levels = param_names$name))
-```
-
-Looking at @fig-param-sens-weight:
-
-* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
-* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
-There must be more up-to-date measurements for Atlantic salmon in particular.
-
-```{r fig-param-sens-weight}
-#| fig-cap: Impact of increasing each model parameter by 10% on final farm biomass (red) and total excreted nutrients (blue) over the whole production period.
-
-sens_data %>% 
-  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens - sd_sens, ymax = mean_sens + sd_sens, fill = measure)) +
-  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
-  # geom_errorbar(position = position_dodge(width = 0.95), width = 0.3) +
-  geom_hline(aes(yintercept = 0), linetype = "dashed") +
-  scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
-  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
-  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
-  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
-  labs(x = "Adjusted parameter", y = "Sensitivity") +
-  theme_classic() + 
-  theme(legend.position = "none", 
-        strip.text = element_blank(), 
-        aspect.ratio = 0.8,
-        text = element_text(size = 12),
-        axis.title.y = element_blank()) +
-  coord_flip()
-```
-
-## Modelled experimental feeds {#sec-feeds}
-
-```{r feeds}
-feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
-feed_params <- file.path(output_species_data_path, "feed_params.qs") %>% qs::qread()
-
-df <- feed_params[["reference"]]
-contribP_1 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_1 <- sum(contribP_1)
-digestP_1 <- sum(df[["Proteins"]]$digest * contribP_1)/tP_1
-
-contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_1 <- sum(contribL_1)
-digestL <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1
-
-contribC_1 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_1 <- sum(contribC_1)
-digestC_1 <- sum(df[["Carbohydrates"]]$digest * contribC_1)/tC_1
-
-df <- feed_params[["past"]]
-contribP_2 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_2 <- sum(contribP_2)
-digestP_2 <- sum(df[["Proteins"]]$digest * contribP_2)/tP_2
-
-contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_2 <- sum(contribL_2)
-digestL <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2
-
-contribC_2 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_2 <- sum(contribC_2)
-digestC_2 <- sum(df[["Carbohydrates"]]$digest * contribC_2)/tC_2
-
-df <- feed_params[["future"]]
-contribP_3 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
-tP_3 <- sum(contribP_3)
-digestP_3 <- sum(df[["Proteins"]]$digest * contribP_3)/tP_3
-
-contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
-tL_3 <- sum(contribL_3)
-digestL <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3
-
-contribC_3 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
-tC_3 <- sum(contribC_3)
-digestC_3 <- sum(df[["Carbohydrates"]]$digest * contribC_3)/tC_3
-```
-
-[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed]{.aside}
-
-* Feed came from [@cottrell_origins_nodate; @cottrell_global_2020]
-* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
-* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
-* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
-* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
-* Within the reference feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
-* Within the reference feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.
-
-## Population and biomass estimates
+  str_subset("reference")
+
+df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
+  as.data.frame() %>% 
+  mutate(mean = set_units(mean, "g") %>% set_units("t"),
+         sd = set_units(sd, "g") %>% set_units("t")) %>% 
+  select(-farm_ID)
+
+df <- rbind(
+  df %>% mutate(cohort = 1),
+  df %>% mutate(t = t+365, cohort = 2),
+  df %>% mutate(t = t+730, cohort = 3)
+) %>% 
+  mutate(t = (t-min(t))+1,
+         split = "Split by cohort")
+
+min_t <- min(df$t[df$cohort == 2])
+max_t <- max(df$t[df$cohort == 2])
+
+df_2 <- df %>% 
+  filter(t %in% min_t:max_t) %>% 
+  mutate(sd = sd/mean) %>% 
+  group_by(t) %>% 
+  reframe(sd = sqrt(sum(sd^2)),
+          mean = sum(mean),
+          sd = sd*mean) %>% 
+  mutate(cohort = "all",
+         split = "Totalled")
+
+df <- rbind(df, df_2) %>% 
+  mutate(cohort = as.factor(cohort))
+
+ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(linetype = "dotted", alpha = 0) +
+  facet_grid(cols = vars(split)) +
+  scale_x_continuous(breaks = seq(0, 1600, 120)) +
+  scale_colour_manual(values = cohort_pal) +
+  prettyplot() +
+  labs(y = "Farm biomass", x = "Day of production")
+```
 
@@
 
+* Parameter sensitivity results are in supplementary @sec-parameter-sensitivity
+
+In general, data outputs comes in the following dimensions:
+
+* Location -> temperature -> farm_ID
+* Uneaten feed + excreted faeces = total inputs (g)
+* Day of production (impacted by location)
 * Main point is the difference between feeds (kg/t salmon).
-* Also interesting to see if difference between feeds varies geographically (correlates with mean/median/max temperature?)
-
-```{r weight and biomass data}
-farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
-  list.files(full.names = T)
-
-qs::qread(farmrun_files[1]) %>% names()
-weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
-biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
-```
+* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)
 
@@
 ```
+
+### Amount
 
@@
   facet_grid(~feed) +
-  theme_classic()
-```
-
-There was very little variation in the percentage difference (from reference) excreted with increasing overall excretion (@fig-total-excr-diff_perc), or through time (@fig-total-excr-diff_perc_2). 
+  prettyplot()
+```
+
 The difference in total excretion for the past feed ranged from 
@@
 
+```{r fig-composition-comparison}
+#| eval: true
+#| fig-cap: Comparison of the composition of the reference (blue), past (red) and future (green) feed and faeces of salmon fed each feed.
+
+ggplot(ec, aes(x = source, y = 100*value, fill = feed)) +
+  geom_col(colour = "black", position = position_dodge(width = 0.9), alpha = 0.75) +
+  facet_grid(cols = vars(macro)) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal) +
+  scale_y_continuous(breaks = seq(0, 60, 10)) +
+  labs(y = "Composition (%)", x = "Source")
+```
+
 ## Total nutrients

### 2025-06-09 manuscript.qmd
Fix up macronutrient summary

@@
 
-[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed?]{.aside}
-
-* The reference feed is `r filter(feed_summary, feed == "reference", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "reference", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "reference", macro == "C")$total_r`% carbohydrate.
-* The past feed is `r filter(feed_summary, feed == "past", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "past", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "past", macro == "C")$total_r`% carbohydrate.
-* The future feed is `r filter(feed_summary, feed == "future", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "future", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "future", macro == "C")$total_r`% carbohydrate.
-* Within the reference feed, protein is overall `r filter(feed_summary, feed == "reference", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "reference", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "reference", macro == "C")$digest_r`% digestible.
-* Within the past feed, protein is overall `r filter(feed_summary, feed == "past", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "past", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "past", macro == "C")$digest_r`% digestible.
-* Within the future feed, protein is overall `r filter(feed_summary, feed == "future", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "future", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "future", macro == "C")$digest_r`% digestible.
-
-```{r feed summary ideas}
+[Plan to put full details of ingredients in a supplementary section. But possibly report these stats in Results under Uneaten feed?]{.aside}
+
+The reference feed was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "reference", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "reference", macro == "C")$total, 1)`% carbohydrate, the past feed was 
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "past", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "past", macro == "C")$total, 1)`% carbohydrate, and the future feed was 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "future", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "C")$total, 1)`% carbohydrate.
+
+Ingredients are tracked seperately through the model with their own digestibility coefficients. Overall, proteins within the reference feed were 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`% digestible, proteins within the past feed were 
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`% digestible, and proteins within the future feed were 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% digestible.
+The digestibility of the other macronutrients are assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`% for carbohydrates and `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`% for lipids.
+
+```{r fig-feed-summary-ideas}
+#| fig-height: 7.5
 #| fig-cap: | 
@@
     legend.position = "bottom",
+    legend.title = element_blank(), 
     strip.text = element_blank(),
@@
 
-sens_data <- rbind(sens_weight, sens_excr) %>% 
-  mutate(adj_param = factor(adj_param, levels = param_names$name))
+sens_data <- rbind(sens_weight, sens_excr)
 ```
@@
 * These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
-There must be more up-to-date measurements for Atlantic salmon in particular.
 
@@
 #| fig-cap: Impact of increasing each model parameter by 10% on final farm biomass (red) and total excreted nutrients (blue) over the whole production period.
+
+sens_data <- sens_data %>% 
+  filter(measure %in% c("total_excr", "total_uneat"))
 
@@
   scale_y_continuous(breaks = seq(-30,30,5), limits = c(-10,30)) +
-  scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
-  scale_fill_manual(values = c(weight = "salmon", total_excr = "steelblue")) +
-  # scale_fill_manual(values = c("weight" = "salmon", "uneat" = "steelblue", "excr" = "darkgreen")) +
+  # scale_x_discrete(limits = rev(param_names$name), labels = rev(param_names$lab)) +
+  # scale_fill_manual(values = c(total_excr = "salmon", total_uneat = "steelblue")) +
   labs(x = "Adjusted parameter", y = "Sensitivity") +

### 2025-06-09 _targets_sensitivities.R

@@ -16,10 +16,9 @@ list(
   ),
   tar_target(
     tar_farm_ID_sample,
-    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(271)
+    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(25) # %>% sample(271)
   ),
   
-  tar_target(tar_factors, factors),
   tar_target(tar_param_names_pop, c("meanW", "deltaW", "meanImax", "deltaImax", "overFmean", "overFdelta")),
   tar_target(tar_param_names_spec, sens_params_names[!sens_params_names %in% tar_param_names_pop]),
   
@@ -238,7 +237,7 @@ list(
         catab = mean(sens[['catab_stat']][, 2], na.rm = T),
         O2 = sum(sens[['O2_stat']][, 2], na.rm = T),
         NH4 = sum(sens[['NH4_stat']][, 2], na.rm = T),
-        adj_param = as.factor(tar_param_names_spec)
+        adj_param = as.factor(tar_param_names_pop)
       ) %>%
         mutate(farm_ID = tar_farm_ID_sample,
                factor = factors[1])
@@ -282,7 +281,7 @@ list(
         catab = mean(sens[['catab_stat']][, 2], na.rm = T),
         O2 = sum(sens[['O2_stat']][, 2], na.rm = T),
         NH4 = sum(sens[['NH4_stat']][, 2], na.rm = T),
-        adj_param = as.factor(tar_param_names_spec)
+        adj_param = as.factor(tar_param_names_pop)
       ) %>%
         mutate(farm_ID = tar_farm_ID_sample,
                factor = factors[2])
@@ -326,7 +325,7 @@ list(
         catab = mean(sens[['catab_stat']][, 2], na.rm = T),
         O2 = sum(sens[['O2_stat']][, 2], na.rm = T),
         NH4 = sum(sens[['NH4_stat']][, 2], na.rm = T),
-        adj_param = as.factor(tar_param_names_spec)
+        adj_param = as.factor(tar_param_names_pop)
       ) %>%
         mutate(farm_ID = tar_farm_ID_sample,
                factor = factors[3])

### 2025-06-09 manuscript.qmd
Updates

@@
 #| fig-cap: |
-#|   Potential options for showing farm site mean temperatures.
+#|   Potential options for showing data spatially.
 Top left: Mean temperature by latitude across countries.
@@
   geom_sf(data = worldmap, fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 1) +
+  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 2) +
   coord_sf() +
@@
              y = inset_boxes_sm[["CAN2"]][["laby"]], 
-             hjust = 0.5, vjust = 0)
+             hjust = 0.5, vjust = 0.5)
 p_Eur <- p1 + 
@@
              y = inset_boxes_sm[["AUS"]][["laby"]], 
-             hjust = 0, vjust = 0)
+             hjust = 0, vjust = 0.5)
 
@@
 plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
-plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
+# plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
 ```
@@
 * Source of species vulnerability layers
+
+# Statistical analysis & code availability
+
+All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
+For a full list of R packages used see the lockfile on [Github](https://www.github.com).
+This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
 
@@
 `r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish. 
-
-* Differences between the feeds were very small, with the past scenario producing 
-* but slightly less uneaten feed was lost in the reference scenario. Uneaten past feed ranged from 
-`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from
-`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`).
-* @fig-total-uneaten-perday shows the range of total uneaten feed per day across countries.
+Differences between the feeds were very small, but slightly less feed was left uneaten in the reference scenario (@fig-total-uneaten-perday). Uneaten feed in the past scenario ranged from 
+`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to 
+`r uneaten_total_stats$max[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish (mean of 
+`r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish) while uneaten feed in the future scenario ranged from 
+`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to 
+`r uneaten_total_stats$max[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of 
+`r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`  g kg$^{-1}$ fish).
 
 ```{r fig-total-uneaten-perday}
-#| fig-width: 9.5
+#| fig-cap: |
+#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.
 
@@
 
-* The composition of the uneaten feed is (obviously) the same as the total feed composition (@sec-feeds).
+The composition of the uneaten feed is (obviously) the same as the total feed composition detailed in (@sec-feeds).
 
@@
 
-* Total reference excreted faeces across a cohort (548 days) ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
-* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
-`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$) while uneaten future feed ranged from
-`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$).
-* @fig-total-excreted-perday shows the range of total excreted faeces per day across countries.
+Overall, total excretion was lowest when when fish were fed the past feed and highest when fish were fed the reference feed (@fig-total-excreted-perday). 
+Total excreted faeces across a cohort (548 days) in the reference scenario ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to 
+`r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$ fish d$^{-1}$, with a mean of 
+`r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
+Total excreted faeces across a cohort in the past scenario ranged from 
+`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to 
+`r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
+`r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$).
+Total excreted faeces across a cohort in the future scenario ranged from 
+`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to 
+`r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
+`r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$).
 
 ```{r fig-total-excreted-perday}
-#| fig-width: 9
+#| fig-cap: |
+#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.
 
@@
 ```{r fig-total-excr-diff_perc, class.chunk = "aside"}
-#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.
+#| eval: false
+#| fig-cap: |
+#|   Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.
 
@@
   prettyplot()
-```
-
-The difference in total excretion for the past feed ranged from 
-`r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
-`r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%.
+
+# The difference in total excretion for the past feed ranged from 
+# `r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
+# `r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%. 
+```
 
 ```{r fig-total-excr-diff_perc_2, class.chunk = "aside"}
-#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.
+#| eval: false
+#| fig-cap: |
+#|   Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.
 
@@
 ```{r fig-total-excr-act_diff}
+#| eval: false
 #| fig-width: 6.25
@@
 
-# Statistical analysis & code availability
-
-All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
-Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
-For a full list of R packages used see the lockfile on [Github](https://www.github.com).
-This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
-
-# Supplementary stuff
+# Supplementary materials
 
@@
 
-Looking at @fig-param-sens-weight:
-
-* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
-* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
+The most sensitive parameter by far in @fig-param-sens-weight is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism). 
+These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
 

### 2025-06-09 docs/manuscript.qmd
Fix citations

@@
 library(furrr)
-library(RColorBrewer)
 library(purrr)
@@
 install_unit("t_fish", "1000 kg_fish")
+
+packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate")
+
+here("00_model_functions.R") %>% source()
 ```
@@
 )
-```
-
-```{r custom fuctions}
-#| code-summary: Function to create sf polygons from bounding boxes
-
-create_boxes <- function(box_list, label_positions, offset_deg) {
-  boxes <- list()
-  labels <- list()
-
-  for(i in seq_along(box_list)) {
-    name <- names(box_list)[i]
-    coords <- box_list[[i]]
-    pos <- label_positions[i]
-
-    # Create polygon from bounding box coordinates
-    box_coords <- matrix(c(
-      coords[1], coords[3],  # lonmin, latmin
-      coords[2], coords[3],  # lonmax, latmin  
-      coords[2], coords[4],  # lonmax, latmax
-      coords[1], coords[4],  # lonmin, latmax
-      coords[1], coords[3]   # close polygon
-    ), ncol = 2, byrow = TRUE)
-
-    # Create sf polygon
-    poly <- st_polygon(list(box_coords))
-    boxes[[i]] <- st_sfc(poly, crs = 4326)
-
-    # Calculate label position based on specification
-    label_coords <- get_label_position(coords, pos, offset_deg[i])
-    label_point <- st_point(c(label_coords[1], label_coords[2]))
-    labels[[i]] <- st_sfc(label_point, crs = 4326)
-  }
-
-  # Combine into sf objects
-  boxes_sf <- st_sf(
-    name = names(box_list),
-    letter = LETTERS[1:length(box_list)],
-    geometry = do.call(c, boxes)
-  )
-
-  labels_sf <- st_sf(
-    name = names(box_list), 
-    letter = LETTERS[1:length(box_list)],
-    geometry = do.call(c, labels)
-  )
-
-  return(list(boxes = boxes_sf, labels = labels_sf))
-}
-
-# Helper function to calculate label positions
-get_label_position <- function(coords, position, offset) {
-  lonmin <- coords[1]
-  lonmax <- coords[2]
-  latmin <- coords[3]
-  latmax <- coords[4]
-
-  # Parse position string
-  parts <- strsplit(position, "_")[[1]]
-  vertical <- parts[1]    # "top" or "bottom"
-  horizontal <- parts[2]  # "left" or "right"
-  location <- parts[3]    # "inside" or "outside"
-
-  # Base coordinates for corners
-  if(vertical == "bottom") {base_lat <- latmin} else {base_lat <- latmax}
-  if(horizontal == "right") {base_lon <- lonmax} else {base_lon <- lonmin}
-
-  # Apply offset for outside positioning
-  if(location == "outside") {
-    if(horizontal == "left") {base_lon <- base_lon-offset} else {base_lon <- base_lon+offset}
-    if(vertical == "top") {base_lat <- base_lat + offset} else {base_lat <- base_lat - offset}
-  }
-
-  return(c(base_lon, base_lat))
-}
-
-lim_robin <- function(lons = c(144.0, 149.5), lats = c(-39.75, -44.00)) {
-  coords <- data.frame(lon = lons, lat = lats) %>%
-    st_as_sf(coords = c("lon", "lat"), crs = 4326) %>%
-    st_transform(crs = "+proj=robin") %>% 
-    st_coordinates()
-  list(
-    xlims = range(coords[, "X"]),
-    ylims = range(coords[, "Y"])
-  )
-}
-
 ```
@@
 | $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | J g O$_2^{-1}$           | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
-| pk                   | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
+| $p_k$                | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
 | $k_0$                | `r unname(params['k0'])`         | -                        | Fasting catabolism at 0 $^{^\circ}$C | @macnaughton_using_2019 |
-| m                    | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| n                    | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
-| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C.
+| $m$                  | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
+| $n$                  | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
+| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{\circ}$C.
 Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
@@
 | $\omega$             | `r unname(params['omega'])`      | g O$_2$ g$^{-1}$         | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
-| a                    | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| k                    | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| eff                  | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
+| $a$                  | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
+| $k$                  | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
+| $eff$                | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
 | $\overline{W}$       | `r unname(params['meanW'])`      | g                        | Dry weight mean | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
@@
 | $\Delta{F}$          | `r unname(params['overFdelta'])` | g g$^{-1}$ fish          | Overfeeding rate standard deviation |    |
-| mort                 | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |
+| $mort$               | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |
 : Model growth parameters for Atlantic salmon {#tbl-params}
@@
 
-[Possibly replace this with a better summary of the ingredients that make up each feed, and report these stats in Results under Uneaten feed?]{.aside}
+[Plan to put full details of ingredients in a supplementary section. But possibly report these stats in Results under Uneaten feed?]{.aside}
 
@@
 * Source of species vulnerability layers
+
+# Statistical analysis & code availability
+
+All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+Major packages used include `r cite_packages(packages)`.
+For a full list of R packages used see the lockfile on [Github](https://www.github.com).
+This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
 
@@
 
-sens_data <- rbind(sens_weight, sens_excr) %>% 
-  mutate(adj_param = factor(adj_param, levels = param_names$name))
-```
-
-Looking at @fig-param-sens-weight:
-
-* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
-* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
-There must be more up-to-date measurements for Atlantic salmon in particular.
+sens_data <- rbind(sens_weight, sens_excr)
+```
+
+The most sensitive parameter by far in @fig-param-sens-weight is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism). 
+These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
 

### 2025-06-09 00_model_functions.R

@@ -261,4 +261,110 @@ farm_growth <- function(pop_params, species_params, feed_params, water_temp, tim
   return(out_list)
 }
 
+cite_pack <- function(package_name) {
+  version <- packageVersion(package_name)
+  paste0("package `", package_name, "`, version ", version, " [@", package_name, "]")
+}
+
+cite_packages <- function(packages) {
+  # Generate citations for each package
+  citations <- sapply(packages, function(pkg) {
+    version <- packageVersion(pkg)
+    paste0("`", pkg, "`, version ", version, " [@", pkg, "]")
+  })
+  
+  # Handle different cases based on number of packages
+  if (length(packages) == 1) {
+    return(paste0("package ", citations[1]))
+  } else if (length(packages) == 2) {
+    return(paste0("packages ", citations[1], " and ", citations[2]))
+  } else {
+    # More than 2 packages: use commas and "and" before last
+    first_part <- paste(citations[-length(citations)], collapse = ", ")
+    last_part <- citations[length(citations)]
+    return(paste0("packages ", first_part, ", and ", last_part))
+  }
+}
+
+create_boxes <- function(box_list, label_positions, offset_deg) {
+  boxes <- list()
+  labels <- list()
+  
+  for(i in seq_along(box_list)) {
+    name <- names(box_list)[i]
+    coords <- box_list[[i]]
+    pos <- label_positions[i]
+    
+    # Create polygon from bounding box coordinates
+    box_coords <- matrix(c(
+      coords[1], coords[3],  # lonmin, latmin
+      coords[2], coords[3],  # lonmax, latmin  
+      coords[2], coords[4],  # lonmax, latmax
+      coords[1], coords[4],  # lonmin, latmax
+      coords[1], coords[3]   # close polygon
+    ), ncol = 2, byrow = TRUE)
+    
+    # Create sf polygon
+    poly <- st_polygon(list(box_coords))
+    boxes[[i]] <- st_sfc(poly, crs = 4326)
+    
+    # Calculate label position based on specification
+    label_coords <- get_label_position(coords, pos, offset_deg[i])
+    label_point <- st_point(c(label_coords[1], label_coords[2]))
+    labels[[i]] <- st_sfc(label_point, crs = 4326)
+  }
+  
+  # Combine into sf objects
+  boxes_sf <- st_sf(
[…]

### 2025-06-10 docs/manuscript.qmd
Updates

@@
 
-## Production parameters
-
-Salmon were grown for 548 days and were initialised Spring.
+## Model parameterisation
+
+<!-- Salmon were grown for 548 days and were initialised in Spring.
 This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
-Cohorts were initialised anually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
-
-## Model parameterisation
+Cohorts were initialised annually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
+-->
 
@@
 
-@tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
-
-| Parameter | Value | Units | Description | Reference | 
-|:-------:|:----:|:----:|:----------------|:-------------------------|
-| $\alpha$             | `r unname(params['alpha'])`      | -                        | Feeding catabolism coefficient | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | J g$^{-1}$               | Energy content of protein      | @baldan_r_2018 |
-| $\epsilon_{L}$       | `r unname(params['epslip'])`     | J g$^{-1}$               | Energy content of lipid        | @baldan_r_2018 |
-| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | J g$^{-1}$               | Energy content of carbohydrate | @baldan_r_2018 |
-| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | J g O$_2^{-1}$           | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
-| $p_k$                | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
-| $k_0$                | `r unname(params['k0'])`         | -                        | Fasting catabolism at 0 $^{^\circ}$C | @macnaughton_using_2019 |
-| $m$                  | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| $n$                  | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
-| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{\circ}$C.
-Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
-| $T_{max}$            | `r unname(params['Tma'])`        | $^{\circ}$C              | Maximum lethal temperature | Juvenile *Oncorhynchus tshawytscha* (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
-| $T_{opt}$            | `r unname(params['Toa'])`        | $^{\circ}$C              | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
-Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0 $\pm$ 14.6 g, temps: 6, 10, 14, 18${\circ}$C |
-| $T_{min}$            | `r unname(params['Taa'])`        | $^{\circ}$C              | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] |
-| $\omega$             | `r unname(params['omega'])`      | g O$_2$ g$^{-1}$         | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
-| $a$                  | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| $k$                  | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| $eff$                | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
-| $\overline{W}$       | `r unname(params['meanW'])`      | g                        | Dry weight mean | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\Delta{W}$          | `r unname(params['deltaW'])`     | g                        | Dry weight standard deviation | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\overline{F}$       | `r unname(params['overFmean'])`  | g g$^{-1}$ fish          | Overfeeding rate mean |    |
-| $\Delta{F}$          | `r unname(params['overFdelta'])` | g g$^{-1}$ fish          | Overfeeding rate standard deviation |    |
-| $mort$               | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |
-: Model growth parameters for Atlantic salmon {#tbl-params}
+| Parameter | Value | Reference |
+|:------:|:------:|:-----------:|
+| $\alpha$             | `r unname(params['alpha'])`      | [@broekhuizen_modelling_1994] |
+| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
+| $\epsilon_{L}$       | `r unname(params['epslip'])`     | @baldan_r_2018 |
+| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | @baldan_r_2018 |
+| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | @elliott_energy_1975 |
+| $p_k$                | `r unname(params['pk'])`         | @macnaughton_using_2019 |
+| $k_0$                | `r unname(params['k0'])`         | @macnaughton_using_2019 |
+| $m$                  | `r unname(params['m'])`          | @broekhuizen_modelling_1994 | 
+| $n$                  | `r unname(params['n'])`          | @baldan_r_2018 |
+| $\beta C$            | `r unname(params['betac'])`      | @jonsson_thermal_2001 |
+| $T_{max}$            | `r unname(params['Tma'])`        | @poletto_unusual_2017 | 
+| $T_{opt}$            | `r unname(params['Toa'])`        | @jonsson_thermal_2001 | 
+| $T_{min}$            | `r unname(params['Taa'])`        | @vadboncoeur_lowering_2023 | 
+| $\omega$             | `r unname(params['omega'])`      | @baldan_r_2018 |
+| $a$                  | `r unname(params['a'])`          | @van_tien_development_2016 |
+| $k$                  | `r unname(params['k'])`          | @van_tien_development_2016 | 
+| $eff$                | `r unname(params['eff'])`        | @uglem_does_2020 | 
+| $\overline{W}$       | `r unname(params['meanW'])`      | @dempsey_estimating_2023 | 
+| $\Delta{W}$          | `r unname(params['deltaW'])`     | @dempsey_estimating_2023 | |
+| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | @lall_nutrition_2009 | 
+| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | @lall_nutrition_2009 | 
+| $\overline{F}$       | `r unname(params['overFmean'])`  | |
+| $\Delta{F}$          | `r unname(params['overFdelta'])` | |
+| $mort$               | `r unname(params['mortmyt'])`    | @tvete_towards_2023 |
+: Model growth parameters for Atlantic salmon (for double-checking numbers and reference list only) {#tbl-params}
 
@@
 
-Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
-
-[Plan to put full details of ingredients in a supplementary section. But possibly report these stats in Results under Uneaten feed?]{.aside}
-
 The reference feed was 
@@
 
-Ingredients are tracked seperately through the model with their own digestibility coefficients. Overall, proteins within the reference feed were 
-`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`% digestible, proteins within the past feed were 
-`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`% digestible, and proteins within the future feed were 
-`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% digestible.
-The digestibility of the other macronutrients are assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`% for carbohydrates and `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`% for lipids.
+Ingredients are tracked seperately through the model with their own digestibility coefficients. 
+Overall, protein digestibility was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`%,
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`%, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% and carbohydrate digestibility was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "C")$digest, 1)`%,
+`r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`%, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "C")$digest, 1)`%
+within the reference, past, and future feeds respectively. 
+The digestibility of lipids was assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`%.
 
@@
 
-*To detail here:*
-
-* How to convert feed and uneaten faeces into nutrients - just nitrogen?
-Carbon too?
-If just nitrogen, then can probably use the standard N = 6.25 x protein conversion to compare the feeds (lipids and carbohydrates have negligible protein).
-If doing carbon too, will need to find conversion rates for all of them, possibly splitting carbs/lipids into complex/simple, saturated/unsaturated, etc.
-* Source of species vulnerability layers
+General thoughts is that a risk-assessment approach is most compelling:
+
+* Hazard: Nutrient input. Present as a change between feeds (%?), relative to background levels (ratio?)
+  * Possibly ask Camille how the quotas for Tasmanian salmon are calculated
+  * Background levels are from [oceanhealthindex.org](https://knb.ecoinformatics.org/view/resource_map_doi:10.5063/F1610XPS) - double-check that it includes wastewater input AND agriculture - should include both - if they're not combined ask Ben because he has them combined somewhere
+  * If this is too uncertain perhaps combine into categorical (oligotrophic/eutrophic) classification?
+* Exposure: Species presence. Use IUCN/Aquamap data to estimate the % of each species range is occupied by farms
+  * give each farm a 1km radius, check for overlaps
+  * Gage already has the data to process the Aquamap data
+* Vulnerability: species vulnerability to eutrophication + nutrient input - from @butt_trait-based_2022. Possibly also use IUCN threat levels for prioritisation?
 
@@
 
-## Uneaten feed
+## Uneaten feed and faeces
 

### 2025-06-13 01_tidying_data.qmd
Script updates

@@
 format: html
-editor: visual
+editor: source
 ---
 
-Setup
-
-```{r}
-
+```{r setup}
 library(tidyverse)
@@
 library(qs)
+library(magrittr)
 
-#model functions
-source("src/dir.R")
-source("src/model_functions.R")
+source("00_dirs.R")
+source("00_model_functions.R")
+```
 
-#species of interest
-
-species <- c("atlantic_salmon", 
+```{r globals}
+# Specify species of interest
+species <- c(
+  "atlantic_salmon",
   "general_salmonid",
@@
   "pompano",
-             "milkfish")
+  "milkfish"
+)
 
-source(here("src/spatial_templates.R"))
-
+here("src/spatial_templates.R") %>% source()
 ```
 
-Make repo structure
+# Mariculture locations
 
-```{r}
+Pull in mariculture locations data from Clawson et al (2022) and save the species groups of interest.
 
-create_repo(this_path = here())
-
-```
-
-Make input and output folder structure for species of interest
-
-```{r}
-
-#deploy data folder structure for species
-
-map(.x = species, .f = create_species_folders)
-
-```
-
-Pull in mariculture locations data from Clawson et al 2022 and save the species groups of interest
-
-```{r}
-
-farm_locations <- read.csv(file.path(rdsi_dir, "raw_data/aquaculture-locations/all_marine_aquaculture_farms_sources_final.csv")) |> 
+```{r locations}
+farm_locations <- file.path(rdsi_dir, "raw_data/aquaculture-locations/all_marine_aquaculture_farms_sources_final.csv") %>% 
+  read.csv() %>% 
   filter(species_group %in% c("Salmonidae fish", "General marine fish"))
 
-qsave(x = farm_locations, file = "data/_general_data/farm_locations/locations.qs")
-
-```
-
-Modify Feed characterisation and save to all species forcings
-
-```{r}
-
-#import food characterisation data - this is calculated in an independent google drive document
-
-diet = "reference"
-
-Food_charactisation_list <- 
-  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
-  select(-c(5)) |> 
-  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
-  group_by(species) |> 
-  group_split()
-
-map(.x = Food_charactisation_list, .f = \(this_species_food){
-
-  this_species <- this_species_food$species |> unique()
-
-  this_species_food_df <- 
-    this_species_food |> 
-    relocate(prop, .before = "nutrient") |> 
-    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
-    mutate(prop = as.double(prop)) |> 
-    select(-species)
-
-  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")
-
-})
-
-#now repeat for future feed
-
-diet = "future"
-
-Food_charactisation_list <- 
-  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
-  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
-  group_by(species) |> 
-  group_split()
-
-map(.x = Food_charactisation_list, .f = \(this_species_food){
-
-  this_species <- this_species_food$species |> unique()
-
-  this_species_food_df <- 
-    this_species_food |> 
-    relocate(prop, .before = "nutrient") |> 
-    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
-    mutate(prop = as.double(prop)) |> 
-    select(-species)
-
-  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")
-
-})
-
-#now repeat for past feed
-
-diet = "past"
-
-Food_charactisation_list <- 
-  read_csv(sprintf("data/_general_data/diets/protein_lipid_carb_summaries_%s.csv", diet)) |> 
-  pivot_longer(names_to = "nutrient", values_to = "prop", cols = -species) |> 
-  group_by(species) |> 
-  group_split()
-
-map(.x = Food_charactisation_list, .f = \(this_species_food){
-
-  this_species <- this_species_food$species |> unique()
-
-  this_species_food_df <- 
-    this_species_food |> 
-    relocate(prop, .before = "nutrient") |> 
-    mutate(nutrient = as.character(paste0(str_to_sentence(nutrient), "s"))) |> 
-    mutate(prop = as.double(prop)) |> 
-    select(-species)
-
-  write.table(this_species_food_df, file = sprintf("data/%s/forcings/Food_characterization_%s.csv", this_species, diet), row.names = FALSE, col.names = FALSE, sep = ",")
-
-})
-
+qsave(farm_locations, "data/_general_data/farm_locations/locations.qs")
 ```
@@
 ```{r}
-
 nasa_dir <- "/mnt/rdsi/raw_data/NASA/GHRSST_L4_MUR_0.25_SST/"
@@
 
-#now gapfill the saved rasters
+# now gapfill the saved rasters
 
@@
 map(.x = raw_SST_files, .f = \(this_file){
-
   saveName <-  basename(this_file)
-
   message("Gapfilling ", saveName)
-
   this_rast <- rast(this_file)
-
   this_gf_rast <- focal(this_rast, w=7, fun = "mean", na.policy = "only")
-
   writeRaster(this_gf_rast, filename = sprintf("data/_general_data/SST/SST_gf_rasters/%s", saveName))
-
 })
-
 ```
@@
 
-vuln_scores <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv")) |> 
+vuln_scores <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv")) %>% 
   select(vuln_gf_id, eutrophication_nutrient_pollution)
 
-vuln_sd <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_sd.csv")) |> 
-  select(vuln_gf_id, eutrophication_nutrient_pollution) |> rename(sd=eutrophication_nutrient_pollution)
+vuln_sd <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_sd.csv")) %>% 
+  select(vuln_gf_id, eutrophication_nutrient_pollution) %>% rename(sd=eutrophication_nutrient_pollution)
 
@@
 full_vuln_df <- 
-  vuln_scores |> 
-  left_join(vuln_sd) |> 
+  vuln_scores %>% 
+  left_join(vuln_sd) %>% 
   left_join(vuln_tx)

### 2025-06-13 02_extracting_production_locations.qmd
Script updates

---
title: "Extracting production locations for each species to obtain environmental forcings"
format: html
editor: source
---

## Set up

```{r}

library(tidyverse)
library(here)
library(janitor)
library(sf)
library(qs)
library(countrycode)
library(terra)

source("src/dir.R")

species <- c("atlantic_salmon", 
             "general_salmonid", 
             "european_seabass", 
             "gilthead_seabream", 
             "large_yellow_croaker", 
             "japanese_seabass",
             "japanese_amberjack",
             "general_grouper",
             "pompano",
             "milkfish")

```

Isolate production data for species of interest

```{r}

aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))

(aquaculture_prod <- 
  aquaculture_raw |> 
  clean_names() |> 
  select(c(1:7, starts_with("x"))) |> 
  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
  mutate(year = gsub(pattern="x", replacement = "", year)) |> 
  filter(year %in% c(2015:2020)) |> 
  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) |> 
  summarise(production = sum(production)) |> 
    ungroup() |> 
     filter(environment_name=="Marine" & 
           !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                        "Abalones, winkles, conchs",
                                        "Mussels", 
                                        "Oysters",
                                        "Shrimps, prawns",
                                        "Crabs, sea-spiders",
                                         "Freshwater molluscs",
                                        "Squids, cuttlefishes, octopuses",
                                        "Pearls, mother-of-pearl, shells",
                                        "Miscellaneous aquatic plants",
                                        "Scallops, pectens"),
         !grepl("seaweeds" , asfis_species_name_3),
         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
     group_by(asfis_species_name_2) |> 
     summarise(production = mean(production)) |> 
  arrange(-production) |> 
    mutate(cum_prop = cumsum(production)/sum(production),
           prop = production/sum(production))
)

spp_names <- 
  aquaculture_prod |> 
  filter(asfis_species_name_2 %in% c("Atlantic salmon", 
                                     "Rainbow trout", 
                                     "European seabass", 
                                     "Large yellow croaker",
                                     "Gilthead seabream",
                                     "Coho(=Silver) salmon",
                                     "Japanese seabass", 
                                     "Japanese amberjack", 
                                     "Amberjacks nei",
                                     "Pompano", 
                                     "Milkfish") | 
           grepl(pattern = "rouper", asfis_species_name_2) & production > 1) |> 
  pull(asfis_species_name_2)

(mariculture_spp_prod <- 
    aquaculture_raw |> 
    clean_names() |> 
    select(c(1:7, starts_with("x"))) |> 
    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
    mutate(year = gsub(pattern="x", replacement = "", year)) |> 
    filter(year %in% c(2017)) |> 
    filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
             !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                          "Abalones, winkles, conchs",
                                          "Mussels", 
                                          "Oysters",
                                          "Shrimps, prawns",
                                          "Crabs, sea-spiders",
                                          "Freshwater molluscs",
                                          "Squids, cuttlefishes, octopuses",
                                          "Pearls, mother-of-pearl, shells",
                                          "Miscellaneous aquatic plants",
                                          "Scallops, pectens"),
           !grepl("seaweeds" , asfis_species_name_3),
           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) |> 
    summarise(production = sum(production)) |> 
    ungroup() |> 
    mutate(asfis_species_name_2 = case_when(asfis_species_name_2 == "Marine fishes nei" & country_name == "Viet Nam" ~ "Groupers nei",
                                            TRUE ~ asfis_species_name_2)) |> 
    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) |> 
    group_by(iso3c, country_name, year) |> 
    nest() |> 
    mutate(national_production = map(data, ~(sum(.$production)))) |> 
    unnest(cols = c(data, national_production)) |> 
    ungroup() |> 
    filter(asfis_species_name_2 %in% spp_names) |> 
    mutate(prop_production = production/national_production) |> 
    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                                asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
                                asfis_species_name_2 %in% c("Amberjacks nei") ~ "japanese_amberjack",
                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) |> 
  relocate(model_name, .before = asfis_species_name_2) |> 
  filter(prop_production>0) |> 
    mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
                                 TRUE ~ "General marine fish"))
    )

```

Pull in farm locations, add FAO Major fishing regions

```{r}
farms_sf <- qread(file = "data/_general_data/farm_locations/locations.qs") |> 
  st_as_sf(coords = c("X", "Y"), crs = "EPSG:4326") |> 
  mutate(row_num = row_number()) |> 
  group_by(row_num) |> 
  group_split()

FAO_shp <- read_sf(file.path(rdsi_dir, "raw_data/fao/FAO_AREAS_CWP_NOCOASTLINE")) |> filter(F_LEVEL == "MAJOR") |> select(F_CODE)

#test function
#this_farm <- farms_sf[[1]]

# define cores for parallel process

cores <- parallel::detectCores()-2

#  process set up

future::plan(strategy = "multisession", workers = cores)

#intersect farm points with FAO fishing code polygons

farm_fao_intersect <-

  furrr::future_map(.x = farms_sf, .f = \(this_farm){ # initiate parallel map function

  this_farm_fao_code <- st_intersection(this_farm, FAO_shp)

  return(this_farm_fao_code)

}) |> bind_rows() #combine to data frame

qsave(x = farm_fao_intersect, file = here("data/_general_data/farm_locations/locations_w_fishing_areas.qs"))

```

Check that farm locations for each country sit in the correct FAO fishing area - flag those where there is a misalignment

```{r}

# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.

mariculture_prod_all <- 
    aquaculture_raw |> 
    clean_names() |> 
    select(c(1:7, starts_with("x"))) |> 
    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
    mutate(year = gsub(pattern="x", replacement = "", year)) |> 
    filter(year %in% c(2017)) |> 
    filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
             !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
                                          "Abalones, winkles, conchs",
                                          "Mussels", 
                                          "Oysters",
                                          "Shrimps, prawns",
                                          "Crabs, sea-spiders",
                                          "Freshwater molluscs",
                                          "Squids, cuttlefishes, octopuses",
                                          "Pearls, mother-of-pearl, shells",
                                          "Miscellaneous aquatic plants",
                                          "Scallops, pectens"),
           !grepl("seaweeds" , asfis_species_name_3),
           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) |> 
    summarise(production = sum(production)) |> 
    ungroup() |> 
    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) |> 
    group_by(iso3c, country_name, year) |> 
    nest() |> 
    mutate(national_production = map(data, ~(sum(.$production)))) |> 
    unnest(cols = c(data, national_production)) |> 
    ungroup() |> 
  filter(production>0) |> 
  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
   mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                                asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) |> 
  relocate(model_name, .before = asfis_species_name_2) |> 
  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
                                 TRUE ~ "General marine fish")) |> 
 filter(asfis_species_name_2 %in% spp_names) |> 
  mutate(prop_production = production/national_production)

#Check that farm locations in mapped data are in the same FAO fishing regions as the production data

farm_fao_intersect <- qread(here("data/_general_data/farm_locations/locations_w_fishing_areas.qs"))

farm_list <- 
  farm_fao_intersect |> 
  group_by(iso3c, country, species_group) |> 
  group_split()

#Test function

this_country_region <- farm_list[[4]]

(fao_area_code_check <- 
  map_df(farm_list, \(this_country_region){

    farm_country_name <- this_country_region$country |> unique()
    farm_iso3c <- this_country_region$iso3c |> unique()
    farm_fao_code <- this_country_region$F_CODE |> unique() |> sort()
    farm_spp_grp <- this_country_region$species_group |> unique()

    prod_data <- 
      mariculture_prod_all |> 
      filter(iso3c == farm_iso3c & 
               fao_major_fishing_area_code %in% farm_fao_code & 
               country_name == farm_country_name & 
               farm_name == farm_spp_grp)

    prod_spp_group <- prod_data$farm_name |> unique()

    prod_fao_code <- prod_data$fao_major_fishing_area_code |> unique() |> sort()

    return(
      tibble(iso3c = farm_iso3c, 
             countryname = farm_country_name, 
             farm_spp_group = farm_spp_grp, 
             mapped_fishing_areas = paste(farm_fao_code, collapse = ' '), 
             production_fishing_areas = paste(prod_fao_code, collapse = ' ')) |> 
             mutate(same_fishing_area = mapped_fishing_areas == production_fishing_areas))

}) |> filter(!production_fishing_areas == "")
)

```

Assign species to individual farms

```{r}
farm_list <- 
  farm_fao_intersect |> 
  group_by(iso3c, country, species_group, F_CODE) |> 
  group_split()

map_spp_to_locations_list <-

  map(.x = farm_list, .f = \(this_country_region){

  this_iso3c <- this_country_region$iso3c |> unique()
  this_fao_code <- this_country_region$F_CODE |> unique()
  this_species_group <- this_country_region$species_group |> unique()

  message("Processing locations for ", this_species_group, " in ", this_iso3c, " and FAO fishing area ", this_fao_code)

  this_n_farms <- this_country_region |> nrow()

  this_country_region_spp_production_list <- 
    mariculture_spp_prod |> 
    filter(iso3c == this_iso3c, farm_name == this_species_group, fao_major_fishing_area_code == this_fao_code) |> 
    group_by(model_name, national_production) |> 
    summarise(production = sum(production),
              prop_production = production/national_production) |> 
    ungroup() |> 
    distinct() |> 
    group_by(model_name) |> 
    group_split()

  farm_locations_w_model_spp <- 
    map_df(.x = this_country_region_spp_production_list, .f = \(this_species_prop){

    this_spp_n_farms <- round(this_n_farms* this_species_prop$prop_production)

    set.seed(1234)
    indices <- sample(nrow(this_country_region), size = this_spp_n_farms)

    this_spp_locations <- this_country_region[indices,]
    this_spp_locations$model_name <- this_species_prop$model_name

    this_country_region <- this_country_region[-indices,]

     return(this_spp_locations)

  })

  return(farm_locations_w_model_spp)

})

map_spp_to_locations <- bind_rows(lapply(map_spp_to_locations_list, FUN = function(element) if(nrow(element) == 0) NULL else element)) #removes the NULL record returns

qsave(x = map_spp_to_locations, file = here("data/_general_data/farm_locations/locations_w_species_fao_area.qs"))
```

Stocking densities from the tonnage per farm and harvest size.

```{r}

farms_w_species <- qread("data/_general_data/farm_locations/locations_w_species_fao_area.qs")

harvest_sizes <- read_csv("data/_general_data/harvest_sizes/all_harvest_sizes.csv") |> select(-harvest_size_g)

production_cycle <- read_csv("data/_general_data/production_cycles/production_cycle.csv") |> select(species, days)

mortality_rates <- read_csv("data/_general_data/mortality_rates/all_mortality_rates.csv")

farms_w_stocking <- 
  farms_w_species |> 
  left_join(harvest_sizes, by = c("model_name" = "species")) |> 
  left_join(production_cycle, by = c("model_name" = "species")) |> 
  left_join(mortality_rates, by = c("model_name" = "species")) |> 
  mutate(harvest_n = tonnes_per_farm/harvest_size_t) |> 
  mutate(stocking_n = harvest_n * exp(daily_mort_rate*days))

qsave(x = farms_w_stocking, file =  "data/_general_data/farm_locations/locations_w_species_fao_area_stocking.qs")

```

### 2025-06-13 00_dirs.R

@@ -1,0 +1,49 @@
+# This sets up all the directories for the project so that all scripts use the same directory names
+library(here)
+library(stringr)
+
+# From run_individual
+this_species <- "atlantic_salmon"
+
+# Directory structure
+output_path <- here() %>% file.path("outputs")
+gendata_path <- here() %>% file.path("data", "_general_data")
+species_path <- here() %>% file.path("data", this_species)
+species_fig_path <- file.path(species_path, "figures")
+
+# Input paths
+input_farm_coords_path <- file.path(gendata_path, "farm_locations")
+input_farm_sst_path <- file.path(gendata_path, "SST")
+input_species_param_path <- file.path(species_path, "params")
+input_feed_profile_path <- file.path(gendata_path, "diets")
+input_spec_layers_path <- file.path(gendata_path, "species_layers")
+
+# Output paths
+output_farm_data_path <- file.path(output_path, "farm_data")
+output_species_data_path <- file.path(output_path, "species_data")
+output_sens_data_path <- file.path(output_path, "sensitivity_data")
+output_growth_data_path <- file.path(output_path, "farm_growth_data")
+output_cohorts_data_path <- file.path(output_path, "cohort_growth_data")
+output_model_farm_path <- file.path(output_path, "all_outputs_farm")
+output_model_cohort_path <- file.path(output_path, "all_outputs_cohort")
+total_uneaten_path <- file.path(output_path, "total_uneaten_cohort")
+total_excreted_path <- file.path(output_path, "total_excreted_cohort")
+data_analysis_path <- file.path(output_path, "data_analysis")
+
+# Create output directories
+dir.create(output_species_data_path, showWarnings = F)
+dir.create(output_sens_data_path, showWarnings = F)
+dir.create(output_farm_data_path, showWarnings = F)
+dir.create(output_growth_data_path, showWarnings = F)
+dir.create(output_cohorts_data_path, showWarnings = F)
+dir.create(output_model_farm_path, showWarnings = F)
+dir.create(output_model_cohort_path, showWarnings = F)
+dir.create(total_uneaten_path, showWarnings = F)
+dir.create(total_excreted_path, showWarnings = F)
+dir.create(data_analysis_path, showWarnings = F)
+
+
+
+# From extracting_temperature
+# this_path <- file.path("data", this_species) # now call species_path
+

### 2025-06-13 00_model_functions.R

@@ -29,6 +29,13 @@ maxna <- function(x, ...) max(x, na.rm = TRUE, ...)
 sdna <- function(x, ...) sd(x, na.rm = TRUE, ...)
 sumna <- function(x, ...) sum(x, na.rm = TRUE, ...)
 medianna <- function(x, ...) median(x, na.rm = TRUE, ...)
+find_read <- function(path, pattern){
+  file <- list.files(path, full.names = T, pattern = pattern)
+  if (length(file) > 1) {print("Multiple files found - try again")} else {
+    if (str_detect(file, ".qs")) {return(qs::qread(file))}
+    if (str_detect(file, ".parquet")) {return(arrow::read_parquet(file))}
+  }
+}
 
 # Parameters definition
 # species_params['alpha']         [-] Feeding catabolism coefficient
@@ -365,6 +372,20 @@ lim_robin <- function(lons = c(144.0, 149.5), lats = c(-39.75, -44.00)) {
     xlims = range(coords[, "X"]),
     ylims = range(coords[, "Y"])
   )
+}
+
+farm_to_cohort <- function(matrix, time_offset = 0) {
+  matrix %>% 
+    as.data.frame() %>% 
+    rename(t = V1, mean = V2, sd = V3) %>%
+    mutate(t = t + time_offset)
+}
+
+# Process each time period (current, +365 days, +730 days)
+combine_cohorts <- function(lst) {
+  bind_rows(farm_to_cohort(lst[[i]], 0),
+            farm_to_cohort(lst[[i]], 365),
+            farm_to_cohort(lst[[i]], 730))
 }
 
 # nolint end

### 2025-06-13 04_extracting_temperatures.R

@@ -18,15 +18,6 @@ library(tictoc)
 library(conflicted)
 conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
 
-# functions
-source("00_model_functions.R")
-
-# species paths
-this_species <- "atlantic_salmon"
-this_path <- file.path("data", this_species)
-fig_path <- file.path(this_path, "figures")
-prod_path <- file.path(this_path, "data_products")
-
 # Prep temperature forcings for each farm site
 # production_cycle <- read.csv("data/_general_data/production_cycles/production_cycle.csv") %>% 
 #   filter(species == this_species) %>% 
@@ -34,14 +25,15 @@ prod_path <- file.path(this_path, "data_products")
 #   pull(production_cycle_length)
 production_cycle <- 1100
 
-farms <-  qread("data/_general_data/farm_locations/locations_w_species_fao_area_stocking.qs") %>% 
+farms <- file.path(input_farm_coords_path, "locations_w_species_fao_area_stocking.qs") %>% 
+  qread() %>% 
   filter(model_name == this_species) %>% 
   select(-row_num) %>% 
   mutate(farm_id = row_number())
 
 hemi <- cbind(farms$farm_id, sf::st_coordinates(farms$geometry)) %>% 
   as.data.frame() %>% rename(farm_ID = V1, lon = X, lat = Y) %>% 
-  write_parquet("data/_general_data/farm_locations/farm_coords.parquet")
+  write_parquet(file.path(input_farm_coords_path, "farm_coords.parquet"))
 
 day_number <- seq(1:production_cycle)
 
@@ -51,7 +43,9 @@ temp_data <- purrr::map_dfc(.x = day_number, .f = function(day_number){
   rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
   message("Getting temperature data for all sites for ", this_species,  " - day ", day_number)
   
-  sst_test <- terra::rast(sprintf("data/_general_data/SST/SST_gf_rasters/sst_nasa_mur_L4_0.25_mean2010-2019_day_%s.tif", rast_day_number))
+  sst_test <- file.path(input_farm_sst_path, "SST_gf_rasters", 
+                        sprintf("sst_nasa_mur_L4_0.25_mean2010-2019_day_%s.tif", rast_day_number)) %>% 
+    terra::rast()
   
   terra::extract(sst_test, farms) %>%
[…]

### 2025-06-13 05_formulating_feeds.R

@@ -1,0 +1,63 @@
+# nolint start
+
+# Setup -----------------------------------------------------------------------------------------------------------
+library(arrow)
+library(sf)
+library(dplyr)
+library(tidyr)
+library(terra)
+library(magrittr)
+library(furrr)
+library(future)
+library(tictoc)
+library(ggplot2)
+library(fs)
+library(conflicted)
+library(stringr)
+library(readxl)
+library(units)
+library(qs)
+library(here)
+conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+
+here("00_model_functions.R") %>% source()
+here("00_dirs.R") %>% source()
+
+ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
+feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
+feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
+
+# Ingredients -----------------------------------------------------------------------------------------------------
+# Warning: there is no check here to ensure that protein+lipid+ash+carb = 1 in the incoming data. 
+# You must make sure that the proportions add up to 100% manually.
+ingreds <- ingred_inputs_file %>% 
+  read.csv() %>% 
+  mutate(ingredient = as.factor(ingredient))
+ingred_nms <- levels(ingreds$ingredient)
+
+# Feeds -----------------------------------------------------------------------------------------------------------
+feed_inputs <- feed_input_file %>% 
+  read.csv() %>% 
+  mutate(feed = as.factor(feed),
+         ingredient = as.factor(ingredient)) %>% 
+  merge(ingreds, by = "ingredient", all = T)
+feed_types <- levels(feed_inputs$feed)
+
+feed_params <- purrr::map(feed_types, function(ft) {
+  df <- feed_inputs %>% 
+    filter(feed == ft) 
+  list(
+    Proteins = df %>% 
+      select(ingredient, proportion, contains("protein"), -contains("feed")) %>%
+      rename(macro = protein, digest = protein_digestibility),
+    Carbohydrates = df %>% 
+      select(ingredient, proportion, contains("carb"), -contains("feed")) %>%
+      rename(macro = carb, digest = carb_digestibility),
+    Lipids = df %>% 
+      select(ingredient, proportion, contains("lipid"), -contains("feed")) %>%
+      rename(macro = lipid, digest = lipid_digestibility)
+  )
+}) %>% 
+  setNames(feed_types)
+
+qsave(feed_params, feed_params_file)

### 2025-06-13 06.0_run_atlantic_salmon_model.R

@@ -22,44 +22,26 @@ conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
 # functions
 source("00_model_functions.R")
 
-# species paths
-this_species <- "atlantic_salmon"
-this_path <- file.path("data", this_species)
-fig_path <- file.path(this_path, "figures")
-prod_path <- file.path(this_path, "data_products")
+# paths
+source("00_dirs.R")
 
 # STEP 1: Temperature forcings ------------------------------------------------------------------------------------
 # You don't need to do this again unless you make changes - all the important stuff is already saved
 source("04_extracting_temperatures.R")
 
-# STEP 2 - Run model ----------------------------------------------------------------------------------------------
+# STEP 2: Formulate feeds -----------------------------------------------------------------------------------------
+source("05_formulating_feeds.R")
+
+# STEP 3: Run model -----------------------------------------------------------------------------------------------
 ## Individuals ----------------------------------------------------------------------------------------------------
+overwrite <- F
 source("06.1_run_individual.R")
 
 ## Farm growth ----------------------------------------------------------------------------------------------------
+overwrite <- F
 source("06.2_run_farms.R")
 
-# source("10_process_targets_outputs.R")
-# Analysis --------------------------------------------------------------------------------------------------------
-## Combining previously processed data ----------------------------------------------------------------------------
-Sys.setenv(TAR_PROJECT = "project_farm")
-
-overwrite <- T
-source("11_process_targets_outputs_2.R")
-
-# Final data outputs ----------------------------------------------------------------------------------------------
-excr_fnms <- list.files("data/atlantic_salmon/data_products/processed_cohort", full.names = T) %>% str_subset("total_excr")
-
-excr_ls <- uneat_ls <- list()
-for (f in seq_along(excr_fnms)) {
-  excr_ls[[f]] <- excr_fnms[f] %>% arrow::read_parquet()
-  uneat_ls[[f]] <- uneat_fnms[f] %>% arrow::read_parquet()
-}
-excr_ls %>% bind_rows() %>% 
-  arrow::write_parquet("data/atlantic_salmon/data_products/total_excr_allfarms.parquet")
-uneat_ls %>% bind_rows() %>% 
-  arrow::write_parquet("data/atlantic_salmon/data_products/total_uneat_allfarms.parquet")
-
+# STEP 3: Analysis ------------------------------------------------------------------------------------------------
 source("12_data_analysis.R")
 
 # Benchmarking ----------------------------------------------------------------------------------------------------

### 2025-06-13 06.1_run_individual.R

@@ -24,31 +24,8 @@ conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
 # Set up parallel processing
 # plan(multisession, workers = parallelly::availableCores()-1)
 
-# Basic configuration
-overwrite <- F
-this_species <- "atlantic_salmon"
-
-# Directory structure
-output_path <- here() %>% file.path("outputs")
-gendata_path <- here() %>% file.path("data", "_general_data")
-species_path <- here() %>% file.path("data", this_species)
-
-# Input paths
-input_farm_coords_path <- file.path(gendata_path, "farm_locations")
-input_farm_sst_path <- file.path(gendata_path, "SST")
-input_species_param_path <- file.path(species_path, "params")
-input_feed_profile_path <- file.path(gendata_path, "diets")
-
-# Output paths
-output_farm_data_path <- file.path(output_path, "farm_data")
-output_species_data_path <- file.path(output_path, "species_data")
-output_sens_data_path <- file.path(output_path, "sensitivity_data")
-
-# Create output directories
-dir_create(c(output_farm_data_path, 
-             output_species_data_path, 
-             output_sens_data_path
-))
+here("00_model_functions.R") %>% source()
+here("00_dirs.R") %>% source()
 
 # Filenames
 farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
@@ -65,21 +42,6 @@ message(sprintf("Configuration:\n- Species: %s\n- Overwrite existing: %s\n- Outp
                this_species,
                ifelse(overwrite, "yes", "no"),
                output_path))
-
-# Helper functions ------------------------------------------------------------------------------------------------
-source("00_model_functions.R")
-file_exists_skip <- function(filepath, section_name, fn) {
-  if (file.exists(filepath) && !overwrite) {
-    message(sprintf("Skipping %s - file exists", section_name))
-    return(qs::qread(filepath))
-  } else {
-    tic()
-    result <- fn()
-    qs::qsave(result, filepath)
-    message(sprintf("Saved %s - %s", section_name, toc(quiet = T)$callback_msg))
-    return(result)
-  }
-}
 
 # Farm coordinates ------------------------------------------------------------------------------------------------
 farm_coords <- file_exists_skip(farm_coords_file, "farm coordinates", function() {
[…]

### 2025-06-13 06.2_run_farms.R

@@ -1,4 +1,3 @@
-# Disable all linters for this file
 # nolint start
 
 library(arrow)
@@ -20,55 +19,17 @@ library(here)
 library(progressr)
 conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
 
+here("00_model_functions.R") %>% source()
+here("00_dirs.R") %>% source()
+
 # Configuration ---------------------------------------------------------------------------------------------------
 # Set up parallel processing
 # plan(multisession, workers = parallelly::availableCores()-2)
 # plan(multisession, workers = works)
 
-# Basic configuration
-overwrite <- F
-this_species <- "atlantic_salmon"
-
-# Directory structure
-output_path <- here() %>% file.path("outputs")
-gendata_path <- here() %>% file.path("data", "_general_data")
-species_path <- here() %>% file.path("data", this_species)
-
-# Input paths
-input_farm_coords_path <- file.path(gendata_path, "farm_locations")
-input_farm_sst_path <- file.path(gendata_path, "SST")
-input_species_param_path <- file.path(species_path, "params")
-input_feed_profile_path <- file.path(gendata_path, "diets")
-
-# Output paths
-output_farm_data_path <- file.path(output_path, "farm_data")
-output_species_data_path <- file.path(output_path, "species_data")
-output_growth_data_path <- file.path(output_path, "farm_growth_data")
-output_cohorts_data_path <- file.path(output_path, "cohort_growth_data")
-output_model_farm_path <- file.path(output_path, "all_outputs_farm")
-output_model_cohort_path <- file.path(output_path, "all_outputs_cohort")
-total_uneaten_path <- file.path(output_path, "total_uneaten_cohort")
-total_excreted_path <- file.path(output_path, "total_excreted_cohort")
-
 # Filenames
-farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
 farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
-farm_ts_data_file <- file.path(output_farm_data_path, "farm_ts_data.qs")
-species_params_file <- file.path(output_species_data_path, "species_params.qs")
 sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
-pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
[…]

### 2025-06-13 12_data_analysis.R

@@ -22,28 +22,18 @@ suppressPackageStartupMessages({
   conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
 })
 
-# This script aims to take the outputs from the model and answer specific questions 
+# This script aims to take the model outputs from the targets pipeline and answer specific questions.
 # Paths & globals -------------------------------------------------------------------------------------------------
 source("00_model_functions.R")
+source("00_dirs.R")
 
-input_coho_path <- here() %>% file.path("outputs", "cohort_growth_data")
-input_farm_path <- here() %>% file.path("outputs", "farm_growth_data")
-cohort_comp_fnms <- input_coho_path %>% 
+cohort_comp_fnms <- output_cohorts_data_path %>% 
   list.files(full.names = T) %>% 
   str_subset("farmrun_comparisons")
-cohort_refe_fnms <- input_farm_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("farmrun_reference")
-cohort_past_fnms <- input_farm_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("farmrun_past")
-cohort_futu_fnms <- input_farm_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("farmrun_future")
 
-output_coho_path <- file.path("data", "atlantic_salmon", "data_products", "model_outputs_cohort")
-data_analysis_path <- file.path("outputs", "data_analysis")
-dir.create(data_analysis_path)
+aggregate_comparison_files <- output_cohorts_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("allfarms_comparisons")
 
 # * Main point is the difference between feeds. 
 # * This should be expressed in t/t salmon, so farm biomass is also important. 
@@ -51,47 +41,115 @@ dir.create(data_analysis_path)
 remove_unit("g_fish")
 remove_unit("kg_fish")
 remove_unit("t_fish")
-install_unit(symbol = "g_fish", name = "grams of salmon biomass")
+install_unit(symbol = "g_fish")
 install_unit(symbol = "kg_fish", def = "1000 g_fish")
 install_unit(symbol = "t_fish", def = "1000 kg_fish")
 
-# Biomass produced ------------------------------------------------------------------------------------------------
[…]

### 2025-06-13 _targets_farmruns.R

@@ -8,23 +8,49 @@ tar_option_set(
   workspace_on_error = TRUE
 )
 
-# Helper function to process each matrix
-farm_to_cohort <- function(matrix, time_offset = 0) {
-  matrix %>% 
-    as.data.frame() %>% 
-    rename(t = V1, mean = V2, sd = V3) %>%
-    mutate(t = t + time_offset)
-}
-
-# Process each time period (current, +365 days, +730 days)
-combine_cohorts <- function(lst) {
-  bind_rows(farm_to_cohort(lst[[i]], 0),
-            farm_to_cohort(lst[[i]], 365),
-            farm_to_cohort(lst[[i]], 730))
-}
+tar_source(files = c("00_model_functions.R", "00_dirs.R"))
 
 list(
+# Get previously saved data ---------------------------------------------------------------------------------------
+  tar_target(farms_to_omit_file, file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs"), format = "file"),
+  tar_target(farm_coords_file, file.path(output_farm_data_path, "farm_coords.qs"), format = "file"),
+  tar_target(farm_ts_data_file, file.path(output_farm_data_path, "farm_ts_data.qs"), format = "file"),
+  tar_target(species_params_file, file.path(output_species_data_path, "species_params.qs"), format = "file"),
+  tar_target(pop_params_file, file.path(output_species_data_path, "pop_params.qs"), format = "file"),
+  tar_target(feed_params_file, file.path(output_species_data_path, "feed_params.qs"), format = "file"),
+  tar_target(harvest_size_file, file.path(output_farm_data_path, "farm_harvest_size.qs"), format = "file"),
+  tar_target(farm_static_data_file, file.path(input_farm_coords_path, "atlantic_salmon_locations_w_temps.qs"), format = "file"),
+
+  tar_target(farms_to_omit, farms_to_omit_file %>% qs::qread()),
+  tar_target(farm_coords, farm_coords_file %>% qs::qread() %>% filter(!farm_ID %in% farms_to_omit)),
+  tar_target(farm_ts_data, farm_ts_data_file %>% qs::qread() %>% filter(!farm_ID %in% farms_to_omit)),
+  tar_target(species_params, species_params_file %>% qs::qread()),
+  tar_target(pop_params, pop_params_file %>% qs::qread()),
[…]

### 2025-06-13 _targets_sensitivities.R

@@ -16,7 +16,7 @@ list(
   ),
   tar_target(
     tar_farm_ID_sample,
-    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(25) # %>% sample(271)
+    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(271) # %>% sample(271)
   ),
   
   tar_target(tar_param_names_pop, c("meanW", "deltaW", "meanImax", "deltaImax", "overFmean", "overFdelta")),
@@ -334,7 +334,7 @@ list(
   ),
   
   tar_target(
-    tar_sens_results_pop,
+    tar_sens_results_pop_0,
     command = {
       cols <- colnames(tar_sens_run_pop_lo)[
         !colnames(tar_sens_run_pop_lo) %in% c("adj_param", "farm_ID", "factor")
@@ -347,11 +347,17 @@ list(
         pivot_longer(cols = all_of(cols), names_to = "measure", values_to = "value", 
                      names_transform = list(measure = as.factor)) %>% 
         pivot_wider(names_from = "factor", values_from = "value", names_prefix = "fact_") %>% 
-        mutate(sensitivity = (fact_1.1-fact_0.9)/(0.2*fact_1)) %>% 
+        mutate(sensitivity = (fact_1.1-fact_0.9)/(0.2*fact_1))
+    },
+    pattern = map(tar_sens_run_pop_lo, tar_sens_run_pop_mi, tar_sens_run_pop_hi)
+  ),
+  tar_target(
+    tar_sens_results_pop,
+    command = {
+      tar_sens_results_pop_0 %>% 
         group_by(adj_param, measure) %>%
         reframe(mean_sens = meanna(sensitivity),
                 sd_sens = sdna(sensitivity))
     },
-    pattern = map(tar_sens_run_pop_lo, tar_sens_run_pop_mi, tar_sens_run_pop_hi)
   )
 )

### 2025-06-13 archive/XX_spatial_templates.R

@@ -17,3 +17,4 @@ west_canada_bbox <- c(xmin =-140, xmax = -115, ymin = 45, ymax = 57)
 chile_bbox <- c(xmin = -82, xmax = -63, ymin = -57, ymax = -18)
 europe_iceland_bbox <- c(xmin = -29, xmax = 48, ymin = 46, ymax = 73)
 australia_bbox <- c(xmin = 143, xmax = 149, ymin = -44, ymax = -40)
+

### 2025-06-13 manuscript.qmd
Bit of cleanup

@@
 install_unit("t_fish", "1000 kg_fish")
+
+packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate")
+
+here("00_model_functions.R") %>% source()
+
+remove_unit("gN")
+install_unit("gN", "6.25 g") # 1/6.25
 ```
@@
 source(here("00_model_functions.R"))
-
-# Input paths
-input_farm_coords_path <- here() %>% file.path("data", "_general_data", "farm_locations")
-input_farm_sst_path <- here() %>% file.path("data", "_general_data", "SST")
-input_species_param_path <- here() %>% file.path("data", "atlantic_salmon", "params")
-input_feed_profile_path <- here() %>% file.path("data", "_general_data", "diets")
-
-# Output paths
-output_farm_data_path <- here() %>% file.path("outputs", "farm_data")
-output_species_data_path <- here() %>% file.path("outputs", "species_data")
-output_sens_data_path <- here() %>% file.path("outputs", "sensitivity_data")
-output_farm_growth_data_path <- here() %>% file.path("outputs", "farm_growth_data")
-output_cohort_growth_data_path <- here() %>% file.path("outputs", "cohort_growth_data")
-data_analysis_path <- here() %>% file.path("outputs", "data_analysis")
+source(here("00_dirs.R"))
 
@@
 sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
-sens_results_files <- file.path(output_sens_data_path) %>% str_subset("results")
+sens_results_files <- file.path(output_sens_data_path) %>% list.files(full.names = T) %>% str_subset("results")
 
@@
   unique()
+
+farms_geometry <- farms_geometry %>% 
+  mutate(country = factor(country, levels = sorted_countries))
 ```
@@
 
-p1 <- ggplot() +
+p_big_map <- ggplot() +
   geom_sf(data = graticules, color = "gray80", size = 0.3) +
@@
 
-(p2 + p3) / p1 + plot_layout(heights = c(1, 1.5))
+(p2 + p3) / p_big_map + plot_layout(heights = c(1, 1.5))
 ```
@@
 
-@tbl-params shows the parameter values used to model the growth of farmed Atlantic salmon.
-
-| Parameter | Value | Units | Description | Reference | 
-|:-------:|:----:|:----:|:----------------|:-------------------------|
-| $\alpha$             | `r unname(params['alpha'])`      | -                        | Feeding catabolism coefficient | *Salvelinus alpinus*, *Oncorhynchus mykiss* (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | J g$^{-1}$               | Energy content of protein      | @baldan_r_2018 | 
-| $\epsilon_{L}$       | `r unname(params['epslip'])`     | J g$^{-1}$               | Energy content of lipid        | @baldan_r_2018 |
-| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | J g$^{-1}$               | Energy content of carbohydrate | @baldan_r_2018 |
-| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | J g O$_2^{-1}$           | Energy consumed by the respiration of 1 g of oxygen | @elliott_energy_1975 |
-| pk                   | `r unname(params['pk'])`         | d$^{-1}$                 | Temperature coefficient for the fasting catabolism | @macnaughton_using_2019 |
-| $k_0$                | `r unname(params['k0'])`         | -                        | Fasting catabolism at 0 $^{^\circ}$C | @macnaughton_using_2019 |
-| m                    | `r unname(params['m'])`          | -                        | Weight exponent for anabolism | Experimentally-derived alue over a range of *Oncorhynchus*, *Perca* and *Salmo* species (temps: 8–13$^{\circ}$C) [@broekhuizen_modelling_1994] |
-| n                    | `r unname(params['n'])`          | -                        | Weight exponent for catabolism | @baldan_r_2018 |
-| $\beta C$            | `r unname(params['betac'])`      | -                        | Shape coefficient for the feeding function | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$\^{\circ}$C.
-Coefficient for mean daily energy intake of the moderately fast growing group, 0.4398 (mean fast group), 0.2214 (mean slow group) [@jonsson_thermal_2001] |
-| $T_{max}$            | `r unname(params['Tma'])`        | $^{\circ}$C              | Maximum lethal temperature | Juvenile *Oncorhynchus tshawytscha* (19.8 $\pm$ 0.02 g, acclimation temp: 15$^{^\circ}$C, 19${\circ}$C) [@poletto_unusual_2017] |
-| $T_{opt}$            | `r unname(params['Toa'])`        | $^{\circ}$C              | Optimal temperature | Fish size range: 2.25 $\pm$ 0.49 – 11.5 $\pm$ 5.29 g, temperature ranges: 5–24$^{^\circ}$C [@jonsson_thermal_2001].
-Alt value: 14°C [@handeland_effect_2008], *Salmo salar* initial size: 77.0 $\pm$ 14.6 g, temps: 6, 10, 14, 18${\circ}$C |
-| $T_{min}$            | `r unname(params['Taa'])`        | $^{\circ}$C              | Lowest feeding temperature | Fish essentially stop feeding when below 2$^{\circ}$C [@vadboncoeur_lowering_2023] |
-| $\omega$             | `r unname(params['omega'])`      | g O$_2$ g$^{-1}$         | Oxygen consumption:weight loss ratio | Calibrated value from @baldan_r_2018 | 
-| a                    | `r unname(params['a'])`          | J g tissue$^{-1}$        | Energy content of fish tissue | Alt value: 17.02350 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| k                    | `r unname(params['k'])`          | -                        | Weight exponent for energy content | Alt value: 1.65175 (nls model fitted to female Atlantic salmon data extracted and transformed from @jonsson_energy_2003 [@van_tien_development_2016] |
-| eff                  | `r unname(params['eff'])`        | -                        | Food ingestion efficiency | Range: 95-97% ingestion efficiency [@uglem_does_2020] | 
-| $\overline{W}$       | `r unname(params['meanW'])`      | g                        | Dry weight mean | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\Delta{W}$          | `r unname(params['deltaW'])`     | g                        | Dry weight standard deviation | Range of 100-150 given so used a mean of 125 and sd of 10 which over 1000 draws from a normal distribution delivers a minimum and maximum close to these numbers [@dempsey_estimating_2023] |
-| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate mean | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | g g$^{-1}$ fish d$^{-1}$ | Ingestion rate standard deviation | [FAO](https://www.fao.org/fileadmin/user_upload/affris/docs/tabl10.pdf) |
-| $\overline{F}$       | `r unname(params['overFmean'])`  | g g$^{-1}$ fish          | Overfeeding rate mean |    |
-| $\Delta{F}$          | `r unname(params['overFdelta'])` | g g$^{-1}$ fish          | Overfeeding rate standard deviation |    |
-| mort                 | `r unname(params['mortmyt'])`    | d$^{-1}$                 | Natural mortality rate | @tvete_towards_2023 |
-: Model growth parameters for Atlantic salmon {#tbl-params}
+| Parameter | Value | Reference |
+|:------:|:------:|:-----------:|
+| $\alpha$             | `r unname(params['alpha'])`      | @broekhuizen_modelling_1994 |
+| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
+| $\epsilon_{L}$       | `r unname(params['epslip'])`     | @baldan_r_2018 |
+| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | @baldan_r_2018 |
+| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | @elliott_energy_1975 |
+| $p_k$                | `r unname(params['pk'])`         | @macnaughton_using_2019 |
+| $k_0$                | `r unname(params['k0'])`         | @macnaughton_using_2019 |
+| $m$                  | `r unname(params['m'])`          | @broekhuizen_modelling_1994 | 
+| $n$                  | `r unname(params['n'])`          | @baldan_r_2018 |
+| $\beta C$            | `r unname(params['betac'])`      | @jonsson_thermal_2001 |
+| $T_{max}$            | `r unname(params['Tma'])`        | @poletto_unusual_2017 | 
+| $T_{opt}$            | `r unname(params['Toa'])`        | @jonsson_thermal_2001 | 
+| $T_{min}$            | `r unname(params['Taa'])`        | @vadboncoeur_lowering_2023 | 
+| $\omega$             | `r unname(params['omega'])`      | @baldan_r_2018 |
+| $a$                  | `r unname(params['a'])`          | @van_tien_development_2016 |
+| $k$                  | `r unname(params['k'])`          | @van_tien_development_2016 | 
+| $eff$                | `r unname(params['eff'])`        | @uglem_does_2020 | 
+| $\overline{W}$       | `r unname(params['meanW'])`      | @dempsey_estimating_2023 | 
+| $\Delta{W}$          | `r unname(params['deltaW'])`     | @dempsey_estimating_2023 | |
+| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | @lall_nutrition_2009 | 
+| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | @lall_nutrition_2009 | 
+| $\overline{F}$       | `r unname(params['overFmean'])`  | |
+| $\Delta{F}$          | `r unname(params['overFdelta'])` | |
+| $mort$               | `r unname(params['mortmyt'])`    | @tvete_towards_2023 |
+: Model growth parameters for Atlantic salmon (for double-checking numbers and reference list only) {#tbl-params}
 
@@
 All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
-Major packages used include `terra` [@terra], `targets` [@targets], `future` [@future], `furrr` [@furrr], `renv` [@renv], and the `tidyverse` [@tidyverse].
+Major packages used include `r cite_packages(packages)`.
 For a full list of R packages used see the lockfile on [Github](https://www.github.com).

### 2025-06-13 manuscript.qmd
Pre-run big files for speed

@@
 ```{r raw biomass and weight data}
-farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
+farmrun_files <- file.path(output_cohorts_data_path) %>% 
   list.files(full.names = T)
 
-weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>%
-  bind_rows()
-biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>%
-  bind_rows()
+weight <- find_read(output_cohorts_data_path, "allfarms_comparisons_weight_stat")
+biomass <- find_read(output_cohorts_data_path, "allfarms_comparisons_biomass_stat")
 ```
@@
 
-fnms <- output_farm_growth_data_path %>% 
+fnms <- output_growth_data_path %>% 
   list.files(full.names = T) %>% 
@@
 
-```{r uneaten feed data}
-#| code-summary: Load and prep uneaten feed data
-
-uneaten_total <- farmrun_files %>% 
-  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
-  bind_rows() %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  rename(uneat_mean = mean.x, biomass_mean = mean.y,
-         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
-  mutate(uneat_sd = uneat_sd/uneat_mean,
-         biomass_sd = biomass_sd/biomass_mean,
-         uneat_biom_mean = uneat_mean/biomass_mean,
-         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
+```{r inputs data}
+#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)
+
+mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
+mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
+N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
+N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
 ```

### 2025-06-18 02_extracting_production_locations.qmd
Updates for species_layers and background_nitrogen

@@
 
-```{r}
-
-library(tidyverse)
+```{r setup}
+library(tidyr)
+library(dplyr)
+library(magrittr)
 library(here)
@@
 
-source("src/dir.R")
+source(here("00_dir.R"))
 
@@
              "milkfish")
-
 ```
@@
 ```{r}
-
 aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))
@@
 (aquaculture_prod <- 
-  aquaculture_raw |> 
-  clean_names() |> 
-  select(c(1:7, starts_with("x"))) |> 
-  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
-  mutate(year = gsub(pattern="x", replacement = "", year)) |> 
-  filter(year %in% c(2015:2020)) |> 
-  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) |> 
-  summarise(production = sum(production)) |> 
-    ungroup() |> 
+  aquaculture_raw %>% 
+  clean_names() %>% 
+  select(c(1:7, starts_with("x"))) %>% 
+  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+  filter(year %in% c(2015:2020)) %>% 
+  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) %>% 
+  summarise(production = sum(production)) %>% 
+    ungroup() %>% 
      filter(environment_name=="Marine" & 
@@
          !grepl("seaweeds" , asfis_species_name_3),
-         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
-    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
-     group_by(asfis_species_name_2) |> 
-     summarise(production = mean(production)) |> 
-  arrange(-production) |> 
+         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
+     group_by(asfis_species_name_2) %>% 
+     summarise(production = mean(production)) %>% 
+  arrange(-production) %>% 
     mutate(cum_prop = cumsum(production)/sum(production),
@@
 spp_names <- 
-  aquaculture_prod |> 
+  aquaculture_prod %>% 
   filter(asfis_species_name_2 %in% c("Atlantic salmon", 
@@
                                      "Milkfish") | 
-           grepl(pattern = "rouper", asfis_species_name_2) & production > 1) |> 
+           grepl(pattern = "rouper", asfis_species_name_2) & production > 1) %>% 
   pull(asfis_species_name_2)
@@
 (mariculture_spp_prod <- 
-    aquaculture_raw |> 
-    clean_names() |> 
-    select(c(1:7, starts_with("x"))) |> 
-    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
-    mutate(year = gsub(pattern="x", replacement = "", year)) |> 
-    filter(year %in% c(2017)) |> 
+    aquaculture_raw %>% 
+    clean_names() %>% 
+    select(c(1:7, starts_with("x"))) %>% 
+    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+    mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+    filter(year %in% c(2017)) %>% 
     filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
@@
            !grepl("seaweeds" , asfis_species_name_3),
-           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
-    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) |> 
-    summarise(production = sum(production)) |> 
-    ungroup() |> 
+           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
+    summarise(production = sum(production)) %>% 
+    ungroup() %>% 
     mutate(asfis_species_name_2 = case_when(asfis_species_name_2 == "Marine fishes nei" & country_name == "Viet Nam" ~ "Groupers nei",
-                                            TRUE ~ asfis_species_name_2)) |> 
-    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) |> 
-    group_by(iso3c, country_name, year) |> 
-    nest() |> 
-    mutate(national_production = map(data, ~(sum(.$production)))) |> 
-    unnest(cols = c(data, national_production)) |> 
-    ungroup() |> 
-    filter(asfis_species_name_2 %in% spp_names) |> 
-    mutate(prop_production = production/national_production) |> 
-    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
+                                            TRUE ~ asfis_species_name_2)) %>% 
+    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
+    group_by(iso3c, country_name, year) %>% 
+    nest() %>% 
+    mutate(national_production = map(data, ~(sum(.$production)))) %>% 
+    unnest(cols = c(data, national_production)) %>% 
+    ungroup() %>% 
+    filter(asfis_species_name_2 %in% spp_names) %>% 
+    mutate(prop_production = production/national_production) %>% 
+    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
   mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
@@
                                 asfis_species_name_2 %in% c("Amberjacks nei") ~ "japanese_amberjack",
-                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) |> 
-  relocate(model_name, .before = asfis_species_name_2) |> 
-  filter(prop_production>0) |> 
+                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
+  relocate(model_name, .before = asfis_species_name_2) %>% 
+  filter(prop_production>0) %>% 
     mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
@@
 ```{r}
-farms_sf <- qread(file = "data/_general_data/farm_locations/locations.qs") |> 
-  st_as_sf(coords = c("X", "Y"), crs = "EPSG:4326") |> 
-  mutate(row_num = row_number()) |> 
-  group_by(row_num) |> 
+farms_sf <- qread(file = "data/_general_data/farm_locations/locations.qs") %>% 
+  st_as_sf(coords = c("X", "Y"), crs = "EPSG:4326") %>% 
+  mutate(row_num = row_number()) %>% 
+  group_by(row_num) %>% 
   group_split()
 
-FAO_shp <- read_sf(file.path(rdsi_dir, "raw_data/fao/FAO_AREAS_CWP_NOCOASTLINE")) |> filter(F_LEVEL == "MAJOR") |> select(F_CODE)
+FAO_shp <- read_sf(file.path(rdsi_dir, "raw_data/fao/FAO_AREAS_CWP_NOCOASTLINE")) %>% filter(F_LEVEL == "MAJOR") %>% select(F_CODE)
 
@@
 cores <- parallel::detectCores()-2
-
-#  process set up
-
 future::plan(strategy = "multisession", workers = cores)
 
-#intersect farm points with FAO fishing code polygons
-
-farm_fao_intersect <-
-
-  furrr::future_map(.x = farms_sf, .f = \(this_farm){ # initiate parallel map function
-
+# Intersect farm points with FAO fishing code polygons
+farm_fao_intersect <- furrr::future_map(.x = farms_sf, .f = \(this_farm){ # initiate parallel map function
     this_farm_fao_code <- st_intersection(this_farm, FAO_shp)
-
     return(this_farm_fao_code)
-
-}) |> bind_rows() #combine to data frame
+}) %>% bind_rows() #combine to data frame
 
 qsave(x = farm_fao_intersect, file = here("data/_general_data/farm_locations/locations_w_fishing_areas.qs"))
-
 ```
@@
 mariculture_prod_all <- 
-    aquaculture_raw |> 
-    clean_names() |> 
-    select(c(1:7, starts_with("x"))) |> 
-    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) |> 
-    mutate(year = gsub(pattern="x", replacement = "", year)) |> 
-    filter(year %in% c(2017)) |> 
+    aquaculture_raw %>% 
+    clean_names() %>% 
+    select(c(1:7, starts_with("x"))) %>% 
+    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+    mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+    filter(year %in% c(2017)) %>% 
     filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
@@
            !grepl("seaweeds" , asfis_species_name_3),
-           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) |> 
-    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) |> 
-    summarise(production = sum(production)) |> 
-    ungroup() |> 
-    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) |> 
-    group_by(iso3c, country_name, year) |> 
-    nest() |> 
-    mutate(national_production = map(data, ~(sum(.$production)))) |> 
-    unnest(cols = c(data, national_production)) |> 
-    ungroup() |> 
-  filter(production>0) |> 
-  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) |> 
+           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
+    summarise(production = sum(production)) %>% 
+    ungroup() %>% 
+    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
+    group_by(iso3c, country_name, year) %>% 
+    nest() %>% 
+    mutate(national_production = map(data, ~(sum(.$production)))) %>% 
+    unnest(cols = c(data, national_production)) %>% 
+    ungroup() %>% 
+  filter(production>0) %>% 
+  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
    mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
                                 asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
-                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) |> 
-  relocate(model_name, .before = asfis_species_name_2) |> 
+                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
+  relocate(model_name, .before = asfis_species_name_2) %>% 
   mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
-                                 TRUE ~ "General marine fish")) |> 
- filter(asfis_species_name_2 %in% spp_names) |> 
+                                 TRUE ~ "General marine fish")) %>% 
+ filter(asfis_species_name_2 %in% spp_names) %>% 
   mutate(prop_production = production/national_production)
@@
 farm_list <- 
-  farm_fao_intersect |> 
-  group_by(iso3c, country, species_group) |> 
+  farm_fao_intersect %>% 
+  group_by(iso3c, country, species_group) %>% 
   group_split()
@@
 
-    farm_country_name <- this_country_region$country |> unique()
-    farm_iso3c <- this_country_region$iso3c |> unique()
-    farm_fao_code <- this_country_region$F_CODE |> unique() |> sort()
-    farm_spp_grp <- this_country_region$species_group |> unique()
+    farm_country_name <- this_country_region$country %>% unique()
+    farm_iso3c <- this_country_region$iso3c %>% unique()
+    farm_fao_code <- this_country_region$F_CODE %>% unique() %>% sort()
+    farm_spp_grp <- this_country_region$species_group %>% unique()
 
     prod_data <- 
-      mariculture_prod_all |> 
+      mariculture_prod_all %>% 
       filter(iso3c == farm_iso3c & 
@@
 
-    prod_spp_group <- prod_data$farm_name |> unique()
+    prod_spp_group <- prod_data$farm_name %>% unique()
 
-    prod_fao_code <- prod_data$fao_major_fishing_area_code |> unique() |> sort()
+    prod_fao_code <- prod_data$fao_major_fishing_area_code %>% unique() %>% sort()
 
@@
              mapped_fishing_areas = paste(farm_fao_code, collapse = ' '), 
-             production_fishing_areas = paste(prod_fao_code, collapse = ' ')) |> 
+             production_fishing_areas = paste(prod_fao_code, collapse = ' ')) %>% 
              mutate(same_fishing_area = mapped_fishing_areas == production_fishing_areas))
 
-}) |> filter(!production_fishing_areas == "")
+}) %>% filter(!production_fishing_areas == "")
 )
@@
 farm_list <- 
-  farm_fao_intersect |> 
-  group_by(iso3c, country, species_group, F_CODE) |> 
+  farm_fao_intersect %>% 
+  group_by(iso3c, country, species_group, F_CODE) %>% 
   group_split()
@@
 
-  this_iso3c <- this_country_region$iso3c |> unique()
-  this_fao_code <- this_country_region$F_CODE |> unique()
-  this_species_group <- this_country_region$species_group |> unique()
+  this_iso3c <- this_country_region$iso3c %>% unique()
+  this_fao_code <- this_country_region$F_CODE %>% unique()
+  this_species_group <- this_country_region$species_group %>% unique()
 
@@
 
-  this_n_farms <- this_country_region |> nrow()
+  this_n_farms <- this_country_region %>% nrow()
 
   this_country_region_spp_production_list <- 
-    mariculture_spp_prod |> 
-    filter(iso3c == this_iso3c, farm_name == this_species_group, fao_major_fishing_area_code == this_fao_code) |> 
-    group_by(model_name, national_production) |> 
+    mariculture_spp_prod %>% 
+    filter(iso3c == this_iso3c, farm_name == this_species_group, fao_major_fishing_area_code == this_fao_code) %>% 
+    group_by(model_name, national_production) %>% 
     summarise(production = sum(production),
-              prop_production = production/national_production) |> 
-    ungroup() |> 
-    distinct() |> 
-    group_by(model_name) |> 
+              prop_production = production/national_production) %>% 
+    ungroup() %>% 
+    distinct() %>% 
+    group_by(model_name) %>% 
     group_split()
@@
 
-harvest_sizes <- read_csv("data/_general_data/harvest_sizes/all_harvest_sizes.csv") |> select(-harvest_size_g)
+harvest_sizes <- read_csv("data/_general_data/harvest_sizes/all_harvest_sizes.csv") %>% select(-harvest_size_g)
 
-production_cycle <- read_csv("data/_general_data/production_cycles/production_cycle.csv") |> select(species, days)
+production_cycle <- read_csv("data/_general_data/production_cycles/production_cycle.csv") %>% select(species, days)
 
@@
 farms_w_stocking <- 
-  farms_w_species |> 
-  left_join(harvest_sizes, by = c("model_name" = "species")) |> 
-  left_join(production_cycle, by = c("model_name" = "species")) |> 
-  left_join(mortality_rates, by = c("model_name" = "species")) |> 
-  mutate(harvest_n = tonnes_per_farm/harvest_size_t) |> 
+  farms_w_species %>% 
+  left_join(harvest_sizes, by = c("model_name" = "species")) %>% 
+  left_join(production_cycle, by = c("model_name" = "species")) %>% 
+  left_join(mortality_rates, by = c("model_name" = "species")) %>% 
+  mutate(harvest_n = tonnes_per_farm/harvest_size_t) %>% 
   mutate(stocking_n = harvest_n * exp(daily_mort_rate*days))

### 2025-06-18 07_species_layers.qmd
Updates for species_layers and background_nitrogen

---
title: "07_species_layers"
format: html
editor: source
---

```{r}
library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(here)
library(terra)
library(sf)
library(qs)
library(ggplot2)
library(countrycode)
library(terra)
library(tidyterra)
library(cowplot)
library(furrr)
library(rnaturalearth)
library(aquamapsdata) # https://raquamaps.github.io/aquamapsdata/articles/intro.html
library(worrms)
library(grid)

source("00_dirs.R")

overwrite <- F
```

# Base rasters for resolution

Create a blank raster with enough resolution to get farms in there (100m)

```{r base-raster}
base_rast <- rast(res = 0.1/111.32, extent = ext(-180, 180, -90, 90), crs = "EPSG:4326")

inset_boxes <- list(
  CAN1 = c(-132, -122, 47.75, 54.25),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-26, 30, 51, 72),
  CHI = c(-77.5, -62.5, -56, -25),
  AUS = c(144, 149.5, -44, -39.75)
)

inset_rasters <- list(
  CAN1 = crop(base_rast, ext(inset_boxes[["CAN1"]])),
  CAN2 = crop(base_rast, ext(inset_boxes[["CAN2"]])),
  EUR  = crop(base_rast, ext(inset_boxes[["EUR"]])),
  CHI  = crop(base_rast, ext(inset_boxes[["CHI"]])),
  AUS  = crop(base_rast, ext(inset_boxes[["AUS"]]))
)
```

# Farm circles

Give each farm a basic "circle of influence" - currently set at 2km. Possibility to reduce this/create a dispersion pattern later.

```{r farm-circles}
farm_circles_file <- file.path(output_farm_data_path, "farm_circles_2km.tif")

farm_circles_rast <- if (!file.exists(farm_circles_file) | overwrite) {
  # Read in farm locations (sf objects)
  farm_locs <- file.path(output_farm_data_path, "farm_geometry.qs") %>% 
    qread()

  # Create circular buffers for crude (~1km) area of impact and merge overlapping areas
  farm_circles <- st_sf(farm_id = farm_locs$farm_id, geometry = farm_locs$geometry) %>%
    st_transform(crs = crs(base_rast)) %>%  # transform to match background N projection
    st_buffer(dist = 2000) %>%  # 2 km radius circles - for maximum possible impact (temporary for testing method)
    st_union() %>%  # merge overlapping polygons
    st_sf() %>%  # convert back to sf object
    mutate(id = 1)  # add single ID for rasterization

  farm_rast <- rasterize(vect(farm_circles), base_rast, field = "id") # this takes a long time because the base raster is so fine
  writeRaster(farm_rast, farm_circles_file, overwrite = T)
  farm_rast
} else {
  rast(farm_circles_file)
}
```

Also save the individual areas of farm clusters so later species-overlaying is a bit faster.

```{r small-bb-farm-circles}
fa_list <- file.path(output_farm_data_path, sprintf("farm_circles_2km_inset_%s.tif", 1:5))
for (i in 1:5) {
  if (!file.exists(fa_list[i]) | overwrite) {
    fa_rast <- crop(farm_circles_rast, inset_rasters[[i]])
    writeRaster(fa_rast, fa_list[i])
  }
}

# Testing out different resolutions for the farm_circles
fa_rast_100m <- rast(fa_list[4])
fa_rast_250m <- aggregate(fa_rast_100m, fact = 2.5, fun = "modal")
fa_rast_500m <- aggregate(fa_rast_100m, fact = 5, fun = "modal")
fa_rast_1000m <- aggregate(fa_rast_100m, fact = 10, fun = "modal")

fa_ggplot <- function(df) {
  ggplot() +
    geom_spatraster(data = df, mapping = aes(fill = id), na.rm = T) +
    scale_fill_viridis_c(na.value = "transparent") +
    coord_sf(expand = FALSE) +
    theme_void()
}

plot_grid(
  fa_ggplot(fa_rast_100m),
  fa_ggplot(fa_rast_250m),
  fa_ggplot(fa_rast_500m),
  fa_ggplot(fa_rast_1000m),
  ncol = 2
)
```

# Species vulnerabilities

Using trait-based vulnerability data downloaded from @ohara_code_2021 [@butt_trait-based_2022].

``` {r vulnerability data}
vulnerabilities <- file.path(input_spec_layers_path, "spp_gp_vuln_w_distribution.csv") %>% 
  read.csv() %>% 
  mutate(spp_gp = str_to_sentence(spp_gp)) %>% 
  filter(stressor == "eutrophication_nutrient_pollution") %>% 
  mutate(taxon = as.factor(taxon)) %>% 
  mutate(spp_gp = str_remove(spp_gp, "\\s*\\([^)]*\\)")) %>%  # remove non-accepted names in parentheses
  filter(exposure_mod != 0) %>% 
  select(-contains("sd"), -stressor)

ggplot(vulnerabilities, aes(x = taxon, y = vuln, fill = taxon)) +
  geom_boxplot() +
  coord_flip()
```

## Species ranges

```{r aquamaps database}
# download_db(force = FALSE) # This step downloads the Aquamaps database, ~ 2GB. Only need to do this once
default_db("sqlite") # Need this step in order to set up to query database
```

```{r aquamaps-species-keys}
vuln_am_keys <- split(vulnerabilities, vulnerabilities$spp_gp) %>% 
  lapply(function(vdf) {
    keys <- am_search_fuzzy(vdf$spp_gp) %>% 
      mutate(key = as.character(key),
             terms = as.character(terms),
             spp_gp = vdf$spp_gp,
             genus_species = str_extract(terms, "^\\S+\\s+\\S+"))
    merge(vdf, keys, by = "spp_gp")
  }) %>% 
  bind_rows() %>% 
  # The vulnerabilities are applied at different levels depending on data available, which can affect distribution lookups
  mutate(
    match_level = case_when(
      genus_species == spp_gp ~ "species",
      str_detect(str_to_lower(genus_species), str_to_lower(spp_gp)) ~ "genus",
      str_detect(spp_gp, "ae$") ~ "family",
      str_detect(str_to_lower(terms), str_to_lower(spp_gp)) & !str_detect(str_to_lower(genus_species), str_to_lower(spp_gp)) ~ "common",
      str_detect(str_to_lower(terms), str_to_lower(spp_gp)) ~ "other_taxon",
      T ~ NA
    ),
    match_level = factor(match_level, levels = c("species", "genus", "family", "other_taxon", "common"))
  ) %>% 
  arrange(match_level) %>% 
  # Keep only one key (aquamaps dataset) per species, but there may be multiple vulnerabilities
  distinct(key, .keep_all = T)
```

### Get species rasters

```{r species-rasters}
all_keys <- vuln_am_keys$key
for (i in seq_along(all_keys)) {
  ras <- am_raster(key = all_keys[i]) %>% rast()
  names(ras) <- "probability"
  writeRaster(ras, file.path(input_aquamaps_path, str_c(all_keys[i], ".tif")), overwrite = T)
}
```

Convert to Gall projection for equal area?

# Calculate overlapping area

```{r species-area-setup}
vuln_am_keys <- vuln_am_keys %>% 
  mutate(total_species_area = NA,
         farm_overlap_area = NA,
         file_nm = file.path(input_aquamaps_path, str_c(key, ".tif"))) %>% 
  select(-terms)

fa_rasts <- list.files(output_farm_data_path, full.names = T, pattern = "farm_circles_2km_inset") %>% 
  as.list() %>% 
  lapply(function(fnm){
    rast(fnm) %>% aggregate(fact = 10, fun = "modal") # use 1km resolution for speed
  })
fa_exts <- lapply(fa_rasts, ext) %>% unlist()
```

Get the total overlap between the farm buffer circles (1km radius) and the species range (presence/absence). The data from aquamaps gives a probability of species presence (0-1) but that is not incorporated here (yet).

I tried to do this in parallel but `terra` has issues with parallel processing - couldn't get it to work. But it only takes ~25 minutes (with all the speed measures taken above).

```{r species-area}
for (sp in 1:nrow(vuln_am_keys)) {
  species_range_raster <- rast(vuln_am_keys$file_nm[sp])

  # Temporary - exclude cells where probability < 0.05 and set remaining cells to 1 for presence
  species_range_raster[species_range_raster < 0.05] <- NA 
  species_range_raster[!is.na(species_range_raster)] <- 1

  # Get total species range area
  vuln_am_keys$total_species_area[sp] <- global(
    cellSize(species_range_raster, unit = "km") * !is.na(species_range_raster), "sum", na.rm = TRUE
    )$sum

  # Check species extent against farm extents to see if it's worth continuing
  pre_check <- lapply(fa_rasts, function(ras) {
      check1 <- !is.null(terra::intersect(ext(ras), ext(species_range_raster))) # do extents overlap?
      if (check1) {
        check2 <- crop(species_range_raster, ras) %>% # is any value != NA?
          minmax() %>% as.vector() %>% is.na() %>% any() %>% isFALSE()
      } else {check2 <- F}
      all(check1, check2) # if any are F ~ F
    }) %>% unlist()

  # For areas worth overlaying (passed pre-check)
  overlap_rasts_fa <- fa_rasts[pre_check]
  overlap_rasts_sp <- lapply(overlap_rasts_fa, function(ras) {
      sp_rast <- crop(species_range_raster, ras)
      sp_rast <- resample(sp_rast, ras, method = "bilinear")
      overlap_mask <- !is.na(sp_rast) & !is.na(ras)
      global(cellSize(overlap_mask, unit = "km") * overlap_mask, "sum", na.rm = TRUE)$sum
    })
  vuln_am_keys$farm_overlap_area[sp] <- overlap_rasts_sp %>% unlist() %>% sum()

  if (sp %in% as.integer(seq(0,nrow(vuln_am_keys), length.out = 21))) {
    print(paste0(sp, " of ", nrow(vuln_am_keys), " done, ",
                 round(100*sp/nrow(vuln_am_keys),0), "% finished at ", Sys.time()))
  }
}

vuln_am_keys <- vuln_am_keys %>% 
  mutate(overlap_percent = 100*farm_overlap_area/total_species_area)

qsave(vuln_am_keys, file.path(impacts_path, "vulnerability_areaoverlap_allspecies.qs"))

vuln_am_keys <- vuln_am_keys %>% 
  filter(overlap_percent > 0) %>% 
  arrange(-overlap_percent)

qsave(vuln_am_keys, file.path(impacts_path, "vulnerability_areaoverlap_nonzero.qs"))
```

In this very crude and liberal estimation, the maximum exposure of any species to farm nutrient inputs was `r round(max(vuln_am_keys$overlap_percent), 2)`%.

```{roverlap-plot}
xbreaks <- c(min(vuln_am_keys$overlap_percent/100), max(vuln_am_keys$overlap_percent/100)) %>% log()
xbreaks <- seq(xbreaks[1], xbreaks[2], length.out = 5)
xlabels <- exp(xbreaks)

scientific_10 = function(x) {
  ifelse(
    x==0, "0",
    parse(text = sub("e[+]?", " %*% 10^", scales::scientific_format()(x)))
  )
}

ggplot(vuln_am_keys, aes(x = log(overlap_percent/100), y = vuln, colour = taxon)) +
  geom_point() +
  theme_classic() +
  scale_x_continuous(breaks = xbreaks, labels = scientific_10(xlabels)) +
  labs(y = "Vulnerability", x = "% overlap with species range")
```

### 2025-06-18 08_relative_N_inputs.qmd
Updates for species_layers and background_nitrogen

---
title: "08_relative_N_inputs"
format: html
editor: source
---

```{r setup}
library(tidyr)
library(dplyr)
library(magrittr)
library(stringr)
library(here)
library(terra)
library(sf)
library(qs)
library(ggplot2)
library(tidyterra)
library(cowplot)
library(rnaturalearth)

source("00_dirs.R")

overwrite <- F
```

# Base rasters for resolution

Create a blank raster with enough resolution to get farms in there (100m)

```{r base-raster}
base_rast <- rast(res = 0.1/111.32, extent = ext(-180, 180, -90, 90), crs = "EPSG:4326")

inset_boxes <- list(
  CAN1 = c(-132, -122, 47.75, 54.25),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-26, 30, 51, 72),
  CHI = c(-77.5, -62.5, -56, -25),
  AUS = c(144, 149.5, -44, -39.75)
)

inset_rasters <- list(
  CAN1 = crop(base_rast, ext(inset_boxes[["CAN1"]])),
  CAN2 = crop(base_rast, ext(inset_boxes[["CAN2"]])),
  EUR  = crop(base_rast, ext(inset_boxes[["EUR"]])),
  CHI  = crop(base_rast, ext(inset_boxes[["CHI"]])),
  AUS  = crop(base_rast, ext(inset_boxes[["AUS"]]))
)
```

# Raw background nitrogen

Data was downloaded from https://doi.org/10.5063/F1610XPS. Resolution is ~934 x 934 m in the Mollweide projection.

```{r raw-back-N}
back_N_rast <- file.path(input_Ndata_path, "nutrient_pollution_2013_raw.tif") %>% 
    rast()
back_N_rast
```

When extracting background N data, it was found that a lot of cells had no data. To try and fix this somewhat, I'm going to reproject the background N onto a slightly coarser grid.

```{r small-res-change}
back_N_rast <- back_N_rast %>% 
  project(rast(res = c(1000, 1000), extent = ext(back_N_rast), crs = crs(back_N_rast)),
          method  = "average")
back_N_rast
```

# Load modelled N data

```{r farm locations}
farm_locs <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread()
farm_sfs <- st_sf(farm_id = farm_locs$farm_id, geometry = farm_locs$geometry) %>% 
  st_transform(crs = crs(back_N_rast))
farm_rast <- farm_sfs %>% 
  rasterize(back_N_rast, field = "farm_id")
farm_rast
```

# Combine with background N

```{r}
# 2. Extract 3x3 neighborhood data for each farm point
# Get cell numbers for each farm point
farm_cells <- cellFromXY(back_N_rast, st_coordinates(farm_sfs))

# Function to get 5x5 neighborhood cell numbers
get_neighborhood_cells <- function(raster, center_cells) {
  # Get raster dimensions
  nrows <- nrow(raster)
  ncols <- ncol(raster)

  # Convert cell numbers to row/col indices
  rows <- rowFromCell(raster, center_cells)
  cols <- colFromCell(raster, center_cells)

  # Create all 25 neighbor offsets (including center) for 5x5 grid
  offsets <- expand.grid(row_offset = -2:2, col_offset = -2:2)

  # Initialize list to store results
  all_neighbors <- vector("list", length(center_cells))

  for(i in seq_along(center_cells)) {
    # Calculate neighbor row/col positions
    neighbor_rows <- rows[i] + offsets$row_offset
    neighbor_cols <- cols[i] + offsets$col_offset

    # Check bounds and filter valid cells
    valid_cells <- neighbor_rows >= 1 & neighbor_rows <= nrows & 
                   neighbor_cols >= 1 & neighbor_cols <= ncols

    # Convert back to cell numbers
    neighbor_cells <- cellFromRowCol(raster, 
                                   neighbor_rows[valid_cells], 
                                   neighbor_cols[valid_cells])

    # Create position labels for 5x5 grid
    row_names <- c("T2", "T1", "Crow", "B1", "B2")
    col_names <- c("L2", "L1", "Ccol", "R1", "R2")

    position_grid <- outer(row_names, col_names, paste, sep = "_")
    position_labels <- as.vector(position_grid)
    valid_positions <- position_labels[valid_cells]

    all_neighbors[[i]] <- data.frame(
      farm_id = farm_sfs$farm_id[i],
      cell_id = neighbor_cells,  # for overlap detection
      position = valid_positions,
      stringsAsFactors = FALSE
    )
  }
  return(do.call(rbind, all_neighbors))
}

# Get all neighborhood cells
neighborhood_data <- get_neighborhood_cells(back_N_rast, farm_cells) %>% 
  mutate(
    category = case_when(position == "Crow_Ccol" ~ "farm_direct",
                         position %in% c("T1_L1", "T1_Ccol", "T1_R1", "B1_L1", "B1_Ccol", "B1_R1", "Crow_L1", "Crow_R1") ~ "adjacent_1",
                         T ~ "adjacent_2"),
    category = factor(category, levels = c("farm_direct", "adjacent_1", "adjacent_2")),
    position = factor(position, levels = c(
      "T2_L2",   "T2_L1",   "T2_Ccol",   "T2_R1",   "T2_R2", 
      "T1_L2",   "T1_L1",   "T1_Ccol",   "T1_R1",   "T1_R2", 
      "Crow_L2", "Crow_L1", "Crow_Ccol", "Crow_R1", "Crow_R2", 
      "B1_L2",   "B1_L1",   "B1_Ccol",   "B1_R1",   "B1_R2", 
      "B2_L2",   "B2_L1",   "B2_Ccol",   "B2_R1",   "B2_R2"
    )))

# Extract nutrient values and combine with cell_ids
nutrient_values <- terra::extract(back_N_rast$nutrient_pollution_2013_raw, neighborhood_data$cell_id)
neighborhood_data <- cbind(neighborhood_data, nutrient_values) %>% 
  rename(np = nutrient_pollution_2013_raw)

# Fill gaps from original data with 8 neighbours
neighborhood_data_gaps <- neighborhood_data %>% filter(is.na(np))
for (i in 1:nrow(neighborhood_data_gaps)) {
  adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, cells = neighborhood_data_gaps$cell_id[i], directions = 8)
  neighborhood_data_gaps$np[i] <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
    pull(nutrient_pollution_2013_raw) %>% 
    mean(na.rm = T)
}
neighborhood_data <- neighborhood_data %>% 
  filter(!is.na(np)) %>% 
  rbind(neighborhood_data_gaps)
neighborhood_data %>% filter(is.na(np)) %>% nrow() # 3221 still blank
neighborhood_data %>% filter(is.na(np) & position == "Crow_Ccol") %>% nrow() # 87 of those are direct farm cells

# Fill gaps from original data with 16 neighbours
neighborhood_data_gaps <- neighborhood_data %>% filter(is.na(np))
for (i in 1:nrow(neighborhood_data_gaps)) {
  adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, cells = neighborhood_data_gaps$cell_id[i], directions = 16)
  neighborhood_data_gaps$np[i] <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
    pull(nutrient_pollution_2013_raw) %>% 
    mean(na.rm = T)
}
neighborhood_data <- neighborhood_data %>% 
  filter(!is.na(np)) %>% 
  rbind(neighborhood_data_gaps)
neighborhood_data %>% filter(is.na(np)) %>% nrow() # 4489 still blank
neighborhood_data %>% filter(is.na(np) & position == "Crow_Ccol") %>% nrow() # 149 of those are direct farm cells
```

```{r summary}
# Summary statistics
summary_stats <- neighborhood_data %>%
  group_by(farm_id, category) %>%
  reframe(
    mean = mean(np, na.rm = T),
    min = min(np, na.rm = T),
    max = max(np, na.rm = T),
    cells = n()
  )

# Maybe use adjacent farms to fill gaps?

ggplot(neighborhood_data, aes(x = category, y = log(np), fill = position)) +
  geom_boxplot()
```

# Plot mean nutrient pollution

```{r}
farm_N <- summary_stats %>% 
  filter(category == "farm_direct")

farm_N_sfs <- st_sf(farm_N = farm_N$mean, geometry = farm_locs$geometry) %>% 
  st_transform(crs = crs(back_N_rast))

plot(farm_N_sfs)
```

### 2025-06-18 manuscript.qmd
Updates for species_layers and background_nitrogen

@@
 
-packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate")
+packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate", "worrms", "aquamapsdata") %>% sort()
 
@@
   * Gage already has the data to process the Aquamap data
-* Vulnerability: species vulnerability to eutrophication + nutrient input - from @butt_trait-based_2022. Possibly also use IUCN threat levels for prioritisation?
+* Vulnerability: species vulnerability to eutrophication + nutrient input [@butt_trait-based_2022; @ohara_code_2021]. Possibly also use IUCN threat levels for prioritisation?
 
@@
 
-```{r uneaten feed analysis}
-uneaten_total_stats <- uneaten_total %>% 
-  group_by(feed, farm_ID) %>% 
-  reframe(total = sum(uneat_biom_mean)) %>% 
-  group_by(feed) %>% 
-  reframe(min = minna(total),
-          max = maxna(total),
-          mean = meanna(total)) %>% 
-  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
-  mutate(min = round(min,2),
-         max = round(max,2),
-         mean = round(mean,2))
-
-uneaten_total_compare <- uneaten_total %>% 
-  group_by(feed, farm_ID) %>% 
-  reframe(total = sum(uneat_biom_mean)) %>% 
-  pivot_wider(names_from = "feed", values_from = "total", id_cols = "farm_ID") %>% 
-  mutate(diff_past = past-reference,
-         diff_future = future-reference,
-         diffperc_past = diff_past/reference,
-         diffperc_future = diff_future/reference) %>% 
-  dplyr::select(-c(reference, future, past)) %>% 
-  pivot_longer(names_to = c("measure", "feed"), names_sep = "_", values_to = "value",
-               cols = contains("diff"), names_transform = list(measure = as.factor, feed = as.factor)) %>% 
+```{r inputs stats through time}
+#| eval: false
+#| code-summary: Show how inputs (mass and N) change through time (across all farms)
+
+mass_inputs_ts
+N_inputs_ts
+
+# Through time
+inputs_stats_ts <- inputs_df %>%
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_ts <- inputs_rel_df %>% 
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+# Total (at production end)
+inputs_stats_end <- inputs_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
   group_by(feed, measure) %>% 
-  reframe(min = minna(value),
-          max = maxna(value),
-          mean = meanna(value)) %>% 
-  mutate(
-    min = case_when(measure == "diffperc" ~ 100*min,
-                    T ~ min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
-    max = case_when(measure == "diffperc" ~ 100*max,
-                    T ~ max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
-    mean = case_when(measure == "diffperc" ~ 100*mean,
-                     T ~ mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end_diff <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(future = (future-reference)/reference,
+         past = (past-reference)/reference) %>% 
+  select(-reference) %>% 
+  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
+  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(diff),
+          max = maxna(diff),
+          sd = sdna(diff),
+          mean = meanna(diff))
+
+# Pull key values (uneaten feed)
+u_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
+u_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
+u_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
+u_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
+u_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
+u_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
+u_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
+u_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
+u_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)
+
+# Convert past and future values to % change values
+u_stmin2 <- (100*u_stmin2) %>% round(2)
+u_stmax2 <- (100*u_stmax2) %>% round(2)
+u_stmean2 <- (100*u_stmean2) %>% round(2)
+u_stmin3 <- (100*u_stmin3) %>% round(2)
+u_stmax3 <- (100*u_stmax3) %>% round(2)
+u_stmean3 <- (100*u_stmean3) %>% round(2)
+
+u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+
+# Pull key values (excreted faeces)
+e_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(min)
+e_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(max)
+e_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(mean)
+e_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(min)
+e_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(max)
+e_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(mean)
+e_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(min)
+e_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(max)
+e_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(mean)
+
+# Convert past and future values to % change values
+e_stmin2 <- (100*e_stmin2) %>% round(2)
+e_stmax2 <- (100*e_stmax2) %>% round(2)
+e_stmean2 <- (100*e_stmean2) %>% round(2)
+e_stmin3 <- (100*e_stmin3) %>% round(2)
+e_stmax3 <- (100*e_stmax3) %>% round(2)
+e_stmean3 <- (100*e_stmean3) %>% round(2)
+
+e_stmin1 <- e_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmax1 <- e_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmean1 <- e_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+```
+
+```{r waste inputs stats total}
+#| code-summary: Show how waste inputs change in total (at the end of a production period) across all farms
+
+mass_inputs_sep <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          mean_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass))
+
+twi_min <- mass_inputs_sep$min_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_max <- mass_inputs_sep$max_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_mean <- mass_inputs_sep$mean_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+
+# There were only very small differences in total uneaten feed between the different feeds, with the past feed increasing uneaten feed by `r u_stmin2`-`r u_stmax2`%  (mean of `r u_stmean2`%) and the future feed increasing uneaten feed by `r u_stmin3`-`r u_stmax3`%  (mean of `r u_stmean3`%).
+
+# * Total excreted faeces across a cohort fed the reference feed ranged from `r e_stmin1` to `r e_stmax1` g kg$^{-1}$ fish, with a mean of `r e_stmean1` g kg$^{-1}$ fish. 
+# * Past feed decreased excreted faeces by `r -1*e_stmin2`-`r -1*e_stmax2`%  (mean of `r -1*e_stmean2`%) 
+# * Future feed increased excreted faeces by `r e_stmin3`-`r e_stmax3`%  (mean of `r e_stmean3`%)
+```
+
+* Total waste inputs across a single production period of fish fed the reference feed ranged from `r twi_min[1]` to `r twi_max[1]` g kg$^{-1}$ fish, with a mean of `r twi_mean[1]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the past feed ranged from `r twi_min[2]` to `r twi_max[2]` g kg$^{-1}$ fish, with a mean of `r twi_mean[2]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the future feed ranged from `r twi_min[3]` to `r twi_max[3]` g kg$^{-1}$ fish, with a mean of `r twi_mean[3]` g kg$^{-1}$ fish.
+
+```{r fig-waste-inputs-total}
+#| fig-cap: | 
+#|   Total waste intputs (uneaten feed + excreted faeces) across the whole production period at each farm location.
+#| fig-width: 9.5
+
+mass_inputs_sep_geometry <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(farm_ID, feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          sd_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass)) %>% 
+  merge(farms_geometry, by = "farm_ID")
+
+mass_inputs_robinson <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units()) %>% 
+  st_sf() %>% 
+  st_transform(crs = "+proj=robin")
+
+ggplot() +
+  geom_sf(data = graticules, color = "gray80", size = 0.3) +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = mass_inputs_robinson, aes(color = mean_wpb), size = 1) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 25,barheight = 1.5
+  )) +
+  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
+  geom_sf_text(data = labels_robinson, aes(label = letter), 
+               color = "darkred", size = 5, fontface = "bold", 
+               hjust = 0.5, vjust = 0.5) +
+  theme_void()
+```
+
+```{r patchwork-waste-map-mercator}
+#| fig-cap: |
+#|   Example of a patchwork
+#| fig-height: 9
+#| fig-width: 9.5
+
+mass_inputs_patch <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units())
+
+p1 <- ggplot() +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = mass_inputs_patch, aes(color = mean_wpb, geometry = geometry), size = 2) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barwidth = 1.5, barheight = 20,
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+p_Can1 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
+  draw_label("A", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN1"]][["labx"]], 
+             y = inset_boxes_sm[["CAN1"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Can2 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
+  draw_label("B", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN2"]][["labx"]], 
+             y = inset_boxes_sm[["CAN2"]][["laby"]], 
+             hjust = 0.5, vjust = 0.5)
+p_Eur <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
+           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
+  draw_label("C", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["EUR"]][["labx"]], 
+             y = inset_boxes_sm[["EUR"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Chi <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
+  theme(legend.position = "right") +
+  draw_label("D", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CHI"]][["labx"]], 
+             y = inset_boxes_sm[["CHI"]][["laby"]], 
+             hjust = 0, vjust = 0)
+p_Aus <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
+           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
+  draw_label("E", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["AUS"]][["labx"]], 
+             y = inset_boxes_sm[["AUS"]][["laby"]], 
+             hjust = 0, vjust = 0.5)
+
+grid_1 <- cowplot::plot_grid(p_Can1, p_Can2, ncol = 2, rel_widths =  c(1, 1.35))
+grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
+grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
+
+cowplot::plot_grid(
+  grid_1, grid_3,
+  nrow = 2,
+  rel_heights = c(1, 1.5)        # relative row heights
 )
@@
 
-Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
-`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
-`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
-`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish. 
-Differences between the feeds were very small, but slightly less feed was left uneaten in the reference scenario (@fig-total-uneaten-perday). Uneaten feed in the past scenario ranged from 
-`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to 
-`r uneaten_total_stats$max[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish (mean of 
-`r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish) while uneaten feed in the future scenario ranged from 
-`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to 
-`r uneaten_total_stats$max[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of 
-`r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`  g kg$^{-1}$ fish).
-
-```{r fig-total-uneaten-perday}
-#| fig-cap: |
-#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.
-
-uneaten_total %>% 
-  merge(farms_geometry, by = "farm_ID") %>% 
-  mutate(uneat_biom_mean = uneat_biom_mean %>% set_units("g g_fish-1 d-1") %>% set_units("g kg_fish-1 d-1"),
-         country = factor(country, levels = sorted_countries)) %>% 
-  ggplot(aes(x = country, y = uneat_biom_mean, fill = feed)) +
-  geom_boxplot() +
-  prettyplot() +
-  scale_fill_manual(values = feed_pal) +
-  labs(y = "Uneaten feed", x = "Country")
-```
-
-```{r uneaten composition}
+```{r fig-total-excreted-perday}
 #| eval: false
-
-uneaten_P <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["P_uneat_stat"]]}) %>% bind_rows()
-uneaten_L <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["L_uneat_stat"]]}) %>% bind_rows()
-uneaten_C <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["C_uneat_stat"]]}) %>% bind_rows()
-
-uneaten_all <- uneaten_total %>% 
-  select(-contains("biom")) %>% 
-  merge(uneaten_P, by = c("farm_ID", "feed", "t")) %>% 
-  merge(uneaten_L, by = c("farm_ID", "feed", "t")) %>% 
-  merge(uneaten_C, by = c("farm_ID", "feed", "t")) %>% 
-  select(-c(contains("sd")))
-```
-
-The composition of the uneaten feed is (obviously) the same as the total feed composition detailed in (@sec-feeds).
-
-## Excreted faeces
-
-```{r excreted faeces data}
-#| code-summary: Load and prep all excretion data
-
-# The following reads in all the total excretion data and converts the mean and sd values into values/biomass
-excreted_total <- farmrun_files %>% 
-  purrr::map(function(f) {qs::qread(f)[["total_excr_stat"]]}) %>% 
-  bind_rows() %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  rename(excr_mean = mean.x, biomass_mean = mean.y,
-         excr_sd = sd.x, biomass_sd = sd.y) %>% 
-  mutate(excr_sd = excr_sd/excr_mean,
-         biomass_sd = biomass_sd/biomass_mean,
-         excr_biom_mean = excr_mean/biomass_mean,
-         excr_biom_sd = sqrt(excr_sd^2+biomass_sd^2)*excr_biom_mean)
-
-excreted_total_stats <- excreted_total %>% 
-  group_by(feed, farm_ID) %>% 
-  reframe(total = sum(excr_biom_mean)) %>% 
-  group_by(feed) %>% 
-  reframe(min = minna(total),
-          max = maxna(total),
-          mean = meanna(total)) %>% 
-  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
-  mutate(min = round(min,2),
-         max = round(max,2),
-         mean = round(mean,2))
-```
-
-### Amount
-
-Overall, total excretion was lowest when when fish were fed the past feed and highest when fish were fed the reference feed (@fig-total-excreted-perday). 
-Total excreted faeces across a cohort (548 days) in the reference scenario ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to 
-`r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$ fish d$^{-1}$, with a mean of 
-`r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
-Total excreted faeces across a cohort in the past scenario ranged from 
-`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to 
-`r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
-`r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$).
-Total excreted faeces across a cohort in the future scenario ranged from 
-`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to 
-`r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
-`r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$).
-
-```{r fig-total-excreted-perday}
 #| fig-cap: |
@@
 
-However, the actual difference in excreted faeces varied by feed, time in the production cycle, and location of the farm [@fig-total-excr-act_diff].
-
 ```{r fig-total-excr-act_diff}
@@
 
-### Composition
-
-```{r excreted composition}
-#| eval: true
-
-excreted_P <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["P_excr_stat"]]}) %>% bind_rows()
-excreted_L <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["L_excr_stat"]]}) %>% bind_rows()
-excreted_C <- farmrun_files %>% purrr::map(function(f) {qs::qread(f)[["C_excr_stat"]]}) %>% bind_rows()
-
-excreted_all <- excreted_total %>% 
-  select(-contains("biom")) %>% 
-  merge(excreted_P, by = c("farm_ID", "feed", "t")) %>% 
-  merge(excreted_L, by = c("farm_ID", "feed", "t")) %>% 
-  merge(excreted_C, by = c("farm_ID", "feed", "t")) %>% 
-  select(-c(contains("sd"))) %>% 
-  rename(protein = mean.x, lipids = mean.y, carbohydrates = mean) %>% 
-  mutate(protein = protein/excr_mean %>% set_units("d-1"),
-         lipids = lipids/excr_mean %>% set_units("d-1"),
-         carbohydrates = carbohydrates/excr_mean %>% set_units("d-1")) %>% 
-  select(-excr_mean)
-
-ec <- excreted_all %>% 
-  group_by(feed) %>% 
-  reframe(P = mean(protein),
-          C = mean(carbohydrates),
-          L = mean(lipids)) %>% 
-  mutate(source = "excreted") %>% 
-  rbind(data.frame(
-    feed = c("reference", "past", "future"),
-    P = c(tP_1, tP_2, tP_3),
-    C = c(tC_1, tC_2, tC_3),
-    L = c(tL_1, tL_2, tL_3),
-    source = rep("feed", 3)
-  )) %>% 
-  pivot_longer(cols = c(P,L,C), names_to = "macro", values_to = "value", 
-               names_transform = list(macro = as.factor), values_transform = list(value = as.numeric)) %>% 
-  mutate(source = factor(source, levels = c("feed", "excreted")),
-         macro = factor(macro, levels = c("P", "L", "C"), labels = c("Protein", "Lipids", "Carbohydrates")),
-         feed = factor(feed, levels = c("reference", "past", "future")),
-         source = factor(source, levels = c("feed", "excreted"), labels = c("Feed", "Faeces")))
-```
-
-Unlike the uneaten feed, the composition of excreted faeces differs from that of the incoming feed.
-[Note that composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)]{.aside}
-
-```{r composition-throughtime, class.chunk = "aside"}
+## Total nutrient inputs
+
+```{r protein raw data}
+#| code-summary: Load and prep macronutrients data (keep in g faeces/feed)
+
+N_inputs_df <- rbind(
+  farmrun_files %>% 
+    purrr::map(function(f) {qs::qread(f)[["P_excr_stat"]]}) %>% 
+    bind_rows() %>% 
+    mutate(measure = "excr"),
+  farmrun_files %>% 
+    purrr::map(function(f) {qs::qread(f)[["P_uneat_stat"]]}) %>% 
+    bind_rows() %>% 
+    mutate(measure = "uneat")
+) %>% 
+  mutate(measure = as.factor(measure),
+         t = as.integer(t))
+
+# Absolute inputs
+N_inputs_df <- N_inputs_df %>% 
+  mutate(mean = mean %>% set_units("g") %>% set_units("gN"),
+         sd = sd %>% set_units("g") %>% set_units("gN"))
+
+# Inputs relative to biomass produced
+N_inputs_rel_df <- N_inputs_df %>% 
+  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
+  rename(mean = mean.x, 
+         sd = sd.x, 
+         biomass_mean = mean.y,
+         biomass_sd = sd.y) %>% 
+  mutate(biomass_mean = biomass_mean %>% set_units("g_fish"),
+         biomass_sd = biomass_sd %>% set_units("g_fish"),
+         biomass_sd = biomass_sd/biomass_mean,
+         sd = sd/mean,
+         mean = mean/biomass_mean,
+         sd = sqrt(sd^2 + biomass_sd^2) * mean,
+         biomass_sd = biomass_sd * biomass_mean)
+```
+
+```{r fig-composition-comparison}
 #| eval: false
-
-excreted_all %>% 
-  pivot_longer(names_to = "macro", values_to = "perc", cols = c("protein", "lipids", "carbohydrates")) %>% 
-  mutate(macro = factor(macro, levels = c("protein", "lipids", "carbohydrates"))) %>% 
-  group_by(farm_ID, feed, macro) %>% 
-  reframe(sd = sd(perc) %>% set_units("d-1"),
-          mean = mean(perc)) %>% 
-  ggplot(aes(x = farm_ID, colour = feed, fill = feed, y = 100*mean, ymin = 100*(mean-sd), ymax = 100*(mean+sd))) +
-  geom_point(size = 2) +
-  geom_errorbar(width = 0.5) +
-  scale_color_manual(values = feed_pal) +
-  scale_fill_manual(values = feed_pal) +
-  facet_grid(rows = vars(macro)) +
-  theme_classic() +
-  labs(x = "Macronutrient", y = "Mean composition of faeces")
-```
-
-```{r fig-composition-comparison}
-#| eval: true
 #| fig-cap: Comparison of the composition of the reference (blue), past (red) and future (green) feed and faeces of salmon fed each feed.
@@
 
-## Total nutrients
+```{r composition stats}
+# Through time
+N_inputs_ts <- N_inputs_df %>%
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+N_inputs_rel_ts <- N_inputs_rel_df %>% 
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+# Total (at production end)
+N_inputs_end <- N_inputs_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+N_inputs_rel_end <- N_inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+N_inputs_rel_end_diff <- N_inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(future = (future-reference)/reference,
+         past = (past-reference)/reference) %>% 
+  select(-reference) %>% 
+  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
+  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(diff),
+          max = maxna(diff),
+          sd = sdna(diff),
+          mean = meanna(diff))
+
+# Pull key values (uneaten feed)
+u_stmin1 <- filter(N_inputs_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
+u_stmax1 <- filter(N_inputs_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
+u_stmean1 <- filter(N_inputs_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
+u_stmin2 <- filter(N_inputs_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
+u_stmax2 <- filter(N_inputs_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
+u_stmean2 <- filter(N_inputs_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
+u_stmin3 <- filter(N_inputs_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
+u_stmax3 <- filter(N_inputs_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
+u_stmean3 <- filter(N_inputs_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)
+
+# Convert past and future values to % change values
+u_stmin2 <- (100*u_stmin2) %>% round(2)
+u_stmax2 <- (100*u_stmax2) %>% round(2)
+u_stmean2 <- (100*u_stmean2) %>% round(2)
+u_stmin3 <- (100*u_stmin3) %>% round(2)
+u_stmax3 <- (100*u_stmax3) %>% round(2)
+u_stmean3 <- (100*u_stmean3) %>% round(2)
+
+u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+```
 

### 2025-06-18 00_dirs.R

@@ -17,6 +17,8 @@ input_farm_sst_path <- file.path(gendata_path, "SST")
 input_species_param_path <- file.path(species_path, "params")
 input_feed_profile_path <- file.path(gendata_path, "diets")
 input_spec_layers_path <- file.path(gendata_path, "species_layers")
+input_aquamaps_path <- file.path(input_spec_layers_path, "from_aquamaps")
+input_Ndata_path <- file.path(gendata_path, "background_nitrogen")
 
 # Output paths
 output_farm_data_path <- file.path(output_path, "farm_data")
@@ -29,6 +31,7 @@ output_model_cohort_path <- file.path(output_path, "all_outputs_cohort")
 total_uneaten_path <- file.path(output_path, "total_uneaten_cohort")
 total_excreted_path <- file.path(output_path, "total_excreted_cohort")
 data_analysis_path <- file.path(output_path, "data_analysis")
+impacts_path <- file.path(output_path, "nutrient_impacts")
 
 # Create output directories
 dir.create(output_species_data_path, showWarnings = F)
@@ -41,7 +44,7 @@ dir.create(output_model_cohort_path, showWarnings = F)
 dir.create(total_uneaten_path, showWarnings = F)
 dir.create(total_excreted_path, showWarnings = F)
 dir.create(data_analysis_path, showWarnings = F)
-
+dir.create(impacts_path, showWarnings = F)
 
 
 # From extracting_temperature

### 2025-06-18 00_model_functions.R

@@ -1,3 +1,8 @@
+# These packages are called here so that renv doesn't clean them
+library(devtools)
+library(yaml)
+library(gitcreds)
+
 ### Functions modified from Baldan et al 2018 R package for aquaculture. 
 ### https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0195732
 ### https://github.com/cran/RAC/tree/master/R
@@ -5,17 +10,15 @@
 # Disable all linters for this file
 # nolint start
 
-# Load required packages silently
-suppressWarnings(suppressPackageStartupMessages({
-  library(qs)
-  library(qs2) 
-  library(terra)
-  library(readxl)
-  library(matrixStats)
-  library(furrr)
-  library(future)
-  library(dplyr)
-}))
+# Load required packages
+library(qs)
+library(qs2) 
+library(terra)
+library(readxl)
+library(matrixStats)
+library(furrr)
+library(future)
+library(dplyr)
 
 make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
 fixnum <- function(n, digits = 4) {

### 2025-06-18 06.1_run_individual.R

@@ -170,9 +170,9 @@ factors <- c(0.9, 1, 1.1)
 Sys.setenv(TAR_PROJECT = "project_sensitivities")
 rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
 tar_validate()
-tar_outdated()
+tar_outdated(callr_function = NULL)
 targets::tar_make(
-  # names = contains("tar_sens_run_pop"),
+  # names = "tar_sens_results_spec",
   callr_function = NULL
 )
 

### 2025-06-18 06.2_run_farms.R

@@ -40,11 +40,7 @@ message(sprintf("Configuration:\n- Species: %s\n- Overwrite existing: %s\n- Outp
 # Main farm growth ------------------------------------------------------------------------------------------------
 Sys.setenv(TAR_PROJECT = "project_farmruns")
 rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
-targets::tar_make(
-  reporter = "balanced",
-  # callr_function = NULL,
-  seconds_meta_append = 90
-)
+targets::tar_make(seconds_meta_append = 90)
 
 tar_farm_IDs <- targets::tar_read(tar_farm_IDs)
 stat_names <- targets::tar_read(stat_names)

### 2025-06-18 _targets_sensitivities.R

@@ -5,7 +5,7 @@ library(parallelly)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 14, seconds_timeout = 90),
+  controller = crew_controller_local(workers = 6, seconds_timeout = 90),
   workspace_on_error = TRUE
 )
 

### 2025-06-20 00_model_functions.R
Loading packages so renv doesn't clean them

@@ -1,3 +1,5 @@
+# nolint start
+
 # These packages are called here so that renv doesn't clean them
 library(devtools)
 library(yaml)
@@ -6,9 +8,6 @@ library(gitcreds)
 ### Functions modified from Baldan et al 2018 R package for aquaculture. 
 ### https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0195732
 ### https://github.com/cran/RAC/tree/master/R
-
-# Disable all linters for this file
-# nolint start
 
 # Load required packages
 library(qs)

### 2025-06-20 targets/_targets_farmruns.R

@@ -2,7 +2,7 @@ library(targets)
 library(crew)
 
 tar_option_set(
-  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
+  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble", "qs"), 
   format = "qs", 
   controller = crew_controller_local(workers = 15),
   workspace_on_error = TRUE

### 2025-06-20 04_extracting_temperatures.qmd
Tidying scripts

---
title: "Extracting salmon farm temperature data"
author: Tormey Reimer
date: today
editor: source
---

# Introduction

The purpose of this markdown is to:

```{r setup}
#| code-summary: R setup

library(magrittr)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(terra)
library(qs)
library(here)
library(sf)
library(purrr)
library(furrr)
library(targets)
library(future)
library(arrow)
library(readxl)
library(units)
library(tictoc)
library(conflicted)
conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)

source("00_dirs.R")

overwrite <- F
```

# Farm locations

Get global farm locations and determine whether they're in the southern or northern hemisphere.

``` {r farm-locations}
#| code-summary: Get all farm locations

farms <- file.path(input_farm_coords_path, "locations_w_species_fao_area_stocking.qs") %>% 
  qread() %>% 
  filter(model_name == this_species) %>% 
  select(-row_num) %>% 
  mutate(farm_id = row_number())

hemi <- cbind(farms$farm_id, sf::st_coordinates(farms$geometry)) %>% 
  as.data.frame() %>% rename(farm_ID = V1, lon = X, lat = Y) %>% 
  write_parquet(file.path(input_farm_coords_path, "farm_coords.parquet"))
```

Get daily temperatures for a period of 1100 days (to cover 3 cohorts of 548 days each). Whether a farm is in the southern or northern hemisphere determines the cohorts' start date.

```{r daily-temperatures}
#| code-summary: Create typical year of SST for all farms

day_number <- seq(1:1100)
temp_data <- purrr::map_dfc(.x = day_number, .f = function(day_number){
  rast_day_number <- if_else(day_number <= 365, true = day_number, false = day_number-365)
  rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
  rast_day_number <- if_else(rast_day_number <= 365, true = rast_day_number, false = rast_day_number-365)
  message("Getting temperature data for all sites for ", this_species,  " - day ", day_number)

  sst_test <- file.path(input_farm_sst_path, "SST_gf_rasters", 
                        sprintf("sst_nasa_mur_L4_0.25_mean2010-2019_day_%s.tif", rast_day_number)) %>% 
    terra::rast()

  terra::extract(sst_test, farms) %>%
    mutate(day = paste0("day_", day_number)) %>%
    pivot_wider(names_from = "day", values_from = "focal_mean") %>%
    select(-ID)
}) %>%
  mutate(farm_id = row_number())
# If you want the sf object it's here!

farms_w_temp_df <- farms %>%
  left_join(temp_data, by = c("farm_id" = "farm_id")) %>%
  pivot_longer(names_to = "day", values_to = "temp_c", cols = starts_with("day_"))
```

# Missing data

``` {r missing-data}
#| code-summary: Check which farms have missing temp data

(
  missing_temp_farms <- farms_w_temp_df %>% 
    filter(temp_c %>% is.na()) %>% 
    group_by(farm_id) %>% 
    reframe(num_missing = n())
)

# How far apart in the sequence are the farms? If the previous is complete we should be able to use the one before in the same country
diff(missing_temp_farms$farm_id)

# Make the farm list
farm_list <- farms_w_temp_df %>%
  group_by(farm_id) %>% 
  group_split()
```

``` {r missing-data-fix}
#| code-summary: Loop through and assigned temp of farms missing temp data, to the farm adjacent (the nearest complete index before)

for(i in 1:length(farm_list)){
  message("Checking temp data for ", unique(farm_list[[i]]$farm_id)) 
  if(unique(is.na(farm_list[[i]]$temp_c))){ #if temp data is NA see below
    cat("Is the previous farm index the same country?")
    if(unique(farm_list[[i-1]]$country) == unique(farm_list[[i]]$country)){
      if(!unique(is.na(farm_list[[i-1]]$temp_c))){ # if the farm index before is NOT NA, use that.
        farm_list[[i]]$temp_c <- farm_list[[i-1]]$temp_c
      } else {
        farm_list[[i]]$temp_c <- farm_list[[i-2]]$temp_c.  #else use the farm index 2 before (the missing_farm_
      }
    } else {stop("Previous country index not the same")} #if the previous country is not the same country stop the loop
  }
}

# Check again - looks good - no values.
bind_rows(farm_list) %>%  filter(temp_c %>% is.na()) %>% pull(farm_id) %>% unique()

# Save the new locations data 
farms_w_temp_df <- bind_rows(farm_list)
```

``` {r save}
#| code-summary: Save data

# With geometry, for plotting
qsave(x = farms_w_temp_df, 
      file = file.path(input_farm_coords_path, sprintf("%s_locations_w_temps.qs", this_species)))

# Without geometry, for targets
sf::st_drop_geometry(farms_w_temp_df) %>%
  write_parquet(file.path(input_farm_sst_path, "farm_SST_extracted.parquet"))
```

# Omit farms

Farms are omitted if the mean farm temp <= 6$^\circ$C.

```{r omit farms}
#| code-summary: Get the mean temps for each farm and omit farms that are too cold

mean_farm_temp <- farm_list %>% 
  map_df(.f = function(x){
    data.frame(farm_id = unique(x$farm_id), 
               mean_temp = mean(x$temp_c),
               country = unique(x$country),
               volume = unique(x$tonnes_per_farm))
  })

farms_to_omit <- mean_farm_temp %>% 
  filter(mean_temp <= 6) %>% 
  pull(farm_id)

qsave(x = farms_to_omit, 
      file = file.path(input_farm_coords_path, sprintf("%s_farms_to_omit.qs", this_species)))
```

### 2025-06-20 05_formulating_feeds.qmd
Tidying scripts

---
title: "Formulating experimental feeds"
author: Tormey Reimer
date: today
editor: source
---

# Introduction

The purpose of this markdown is to:

```{r setup}
#| code-summary: R setup

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("00_model_functions.R") %>% source()
here("00_dirs.R") %>% source()

ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
overwrite <- F
```

# Import ingredients

There is no check or correction here to ensure that protein+lipid+ash+carb = 1 in the incoming data. This was checked manually prior to import.

``` {r import-ingredients}
#| code-summary: Ingredient details

ingreds <- ingred_inputs_file %>% 
  read.csv() %>% 
  mutate(ingredient = as.factor(ingredient))
ingred_nms <- levels(ingreds$ingredient)
```

# Import feeds

There is no check or correction here to ensure that ingredient proportions = 1 in the incoming data. This was checked manually prior to import.

``` {r import-feeds}
#| code-summary: Feed compositions

feed_inputs <- feed_input_file %>% 
  read.csv() %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "proportion"))) %>% 
  mutate(feed = as.factor(feed),
         ingredient = as.factor(ingredient)) %>% 
  merge(ingreds, by = "ingredient", all = T)

feed_types <- levels(feed_inputs$feed)
```

The following chunk allows as many ingredients and feeds to be added to the incoming data as needed, it will still be formatted into a form that the `targets` pipelines can use.

```{r formulate feeds}
#| code-summary: Format feeds as lists to feed into targets

feed_params <- purrr::map(feed_types, function(ft) {
  df <- feed_inputs %>% 
    filter(feed == ft & proportion != 0) 
  list(
    Proteins = df %>% 
      select(ingredient, proportion, contains("protein"), -contains("feed")) %>%
      rename(macro = protein, digest = protein_digestibility),
    Carbohydrates = df %>% 
      select(ingredient, proportion, contains("carb"), -contains("feed")) %>%
      rename(macro = carb, digest = carb_digestibility),
    Lipids = df %>% 
      select(ingredient, proportion, contains("lipid"), -contains("feed")) %>%
      rename(macro = lipid, digest = lipid_digestibility)
  )
}) %>% 
  setNames(feed_types)
```

```{r save}
qsave(feed_params, file.path(output_species_data_path, "feed_params.qs"))
```

### 2025-06-20 07_species_layers.qmd
Tidying scripts

@@
 title: "07_species_layers"
-format: html
 editor: source
@@
 
-```{r}
+```{r setup}
+#| include: false
+
 library(tidyr)
@@
 
-In this very crude and liberal estimation, the maximum exposure of any species to farm nutrient inputs was `r round(max(vuln_am_keys$overlap_percent), 2)`%.
+In this very crude and liberal estimation, the maximum exposure of any species to farm nutrient inputs was ~1.9%.
 

### 2025-06-20 manuscript.qmd
Tidying scripts

@@
     theme: simplex
-    css: ["extra.css"]
+    css: "extra.css"
     code-fold: true

### 2025-06-20 08_relative_N_inputs.qmd
Tidy script, save intermediates

@@
 title: "08_relative_N_inputs"
-format: html
+author: Tormey Reimer
+date: today
 editor: source
@@
 
+# Introduction
+
+The purpose of this markdown is to:
+
+1. Import and clean up background nitrogen data
+2. Overlay background nitrogen and Atlantic salmon farm locations
+3. Compare annual inputs from the different sources
+
 ```{r setup}
+#| code-summary: R setup
+
 library(tidyr)
@@
 library(rnaturalearth)
+library(purrr)
 
@@
 
-Create a blank raster with enough resolution to get farms in there (100m)
-
 ```{r base-raster}
-base_rast <- rast(res = 0.1/111.32, extent = ext(-180, 180, -90, 90), crs = "EPSG:4326")
+#| code-summary: Create some blank rasters with parameters to be used going forward
 
@@
 
-inset_rasters <- list(
-  CAN1 = crop(base_rast, ext(inset_boxes[["CAN1"]])),
-  CAN2 = crop(base_rast, ext(inset_boxes[["CAN2"]])),
-  EUR  = crop(base_rast, ext(inset_boxes[["EUR"]])),
-  CHI  = crop(base_rast, ext(inset_boxes[["CHI"]])),
-  AUS  = crop(base_rast, ext(inset_boxes[["AUS"]]))
-)
+base_wgs84 <- rast(res = c(0.008333333, 0.008333333), extent = ext(c(-180, 180, -90, 90)), crs = "EPSG:4326")
+base_molle <- rast(res = c(1000, 1000), extent = ext(c(-18040096, 18040096, -9020048, 9020048)), crs = "ESRI:54009")
+
+wgs84_insets <- inset_boxes %>% 
+  lapply(function(bx) {crop(base_wgs84, ext(bx))})
+
+molle_insets <- wgs84_insets %>% 
+  lapply(function(rs) {project(rs, crs(base_molle))}) %>% 
+  lapply(function(rs) {ext(rs)}) %>% 
+  lapply(function(ex) {crop(base_molle, ex)})
 ```
@@
 
-Data was downloaded from https://doi.org/10.5063/F1610XPS. Resolution is ~934 x 934 m in the Mollweide projection.
+Data for nutrient runoff from agriculture fertilisers and pesticides was downloaded from @halpern_recent_2019-1 [dataset here: @halpern_recent_2019].
 
-```{r raw-back-N}
-back_N_rast <- file.path(input_Ndata_path, "nutrient_pollution_2013_raw.tif") %>% 
-    rast()
-back_N_rast
+```{r raw-back-N-halpern}
+#| code-summary: Import data from @halpern_recent_2019 and crop/reproject for the 5 insets being used
+#| eval: false
+
+halpern_N_rast <- file.path(input_Ndata_path, "halpern_2019", "nutrient_pollution_2013_raw.tif") %>% rast()
+
+halpern_insets <- molle_insets %>% 
+  lapply(function(ins) {project(halpern_N_rast, ins, method = "cubic")})
+
+# Change to the Molleweide projection
+tuholske_N_rast <- file.path(input_Ndata_path, "tuholske_2021", "global_effluent_2015_tot_N.tif") %>% rast() 
+tuholske_insets <- molle_insets %>% 
+  lapply(function(ins) {project(tuholske_N_rast, ins, method = "cubic")})
+
+# The halpern data has NA values for land but the tuholske data does not
+tuholske_insets <- map2(tuholske_insets, halpern_insets, function(rast, mask) {
+  mask(rast, mask)
+})
+
+background_N_insets <- map2(halpern_insets, tuholske_insets, function(dat1, dat2) {dat1 + dat2})
+
+map2(names(halpern_insets), background_N_insets, function(nm, rast) {
+  writeRaster(rast, file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")))
+})
 ```
 
-When extracting background N data, it was found that a lot of cells had no data. To try and fix this somewhat, I'm going to reproject the background N onto a slightly coarser grid.
+Data for inputs of human sewage in coastal ecosystems was sourced from @tuholske_global_2021 [dataset here: @tuholske_mapping_2021]. 
+The data is in annual g N.
 
-```{r small-res-change}
-back_N_rast <- back_N_rast %>% 
-  project(rast(res = c(1000, 1000), extent = ext(back_N_rast), crs = crs(back_N_rast)),
-          method  = "average")
-back_N_rast
+```{r raw-back-N-tuholske}
+#| code-summary: Import data from @tuholske_global_2021 and crop/reproject for the 5 insets being used
+#| eval: false
+
+# Change to the Molleweide projection
+tuholske_N_rast <- file.path(input_Ndata_path, "tuholske_2021", "global_effluent_2015_tot_N.tif") %>% rast() 
+tuholske_insets <- molle_insets %>% 
+  lapply(function(ins) {project(tuholske_N_rast, ins, method = "cubic")})
+
+# The halpern data has NA values for land but the tuholske data does not
+tuholske_insets <- map2(tuholske_insets, halpern_insets, function(rast, mask) {
+  mask(rast, mask)
+})
+```
+
+```{r save-back-N}
+#| code-summary: Combine and save background N data
+
+background_N_insets <- map2(
+  halpern_insets, 
+  tuholske_insets, 
+  function(halpern, tuholske) {
+    halpern + tuholske
+  })
+
+map2(names(halpern_insets), background_N_insets, function(nm, rast) {
+  writeRaster(rast, file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")))
+})
+```
+
+```{r load-background-data}
+#| code-summary: Load previously saved inset rasters
+
+background_N_insets <- lapply(names(inset_boxes), function(nm) {
+  file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")) %>% rast()
+})
 ```
@@
 ```{r farm locations}
+#| code-summary: Bring in modelled salmon inputs data
+
 farm_locs <- file.path(output_farm_data_path, "farm_geometry.qs") %>% qs::qread()
 farm_sfs <- st_sf(farm_id = farm_locs$farm_id, geometry = farm_locs$geometry) %>% 
-  st_transform(crs = crs(back_N_rast))
-farm_rast <- farm_sfs %>% 
-  rasterize(back_N_rast, field = "farm_id")
-farm_rast
+  st_transform(crs = crs(base_molle))
+farm_id_insets <- background_N_insets %>% 
+  lapply(function(ins) {rasterize(farm_sfs, ins, field = "farm_id")})
 ```

### 2025-07-08 01_tidying_data.qmd
Tidying scripts
All changes

@@
 title: "Tidying data"
-format: html
+author: Richard Cottrell
+date: today
 editor: source
@@
 ```{r}
-
 aquamaps_0.5d <- data.table::fread(file.path(rdsi_data_dir, "aquamaps/aquamaps_0.6_depth_prepped.csv"))

### 2025-07-08 02_extracting_production_locations.qmd
Tidying scripts
All changes

@@
 title: "Extracting production locations for each species to obtain environmental forcings"
-format: html
+author: Richard Cottrell
+date: today
 editor: source
@@
 library(terra)
+library(units)
 
-source(here("00_dir.R"))
-
-species <- c("atlantic_salmon", 
-             "general_salmonid", 
-             "european_seabass", 
-             "gilthead_seabream", 
-             "large_yellow_croaker", 
-             "japanese_seabass",
-             "japanese_amberjack",
-             "general_grouper",
-             "pompano",
-             "milkfish")
+source(here("00_dirs.R"))
 ```
 
-Isolate production data for species of interest
+Isolate production data for Atlantic salmon.
+```{r rich-raw-processing}
+#| eval: false
 
-```{r}
 aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))

### 2025-07-08 04_extracting_temperatures.qmd
All changes

@@
 
-The purpose of this markdown is to:
+The purpose of this markdown is to extract daily temperature timeseries from SST data to drive fish growth in the correct places. The steps in this markdown are:
+
+1. Pull farm locations data (previously determined from FAO stocking locations)
+2. Record whether the farm is in the southern or north hemisphere (determines cohort stocking date)
+3. Pull SST data from .tif file and construct "typical" temperature year for each farm location
+4. Gapfill missing temperature data using closest farm in the same FAO stocking area
+5. Save temperature data both with and without geometry information
+6. Determine which farms have a mean temperature <=6 C (will be omitted)
 

### 2025-07-08 08_relative_N_inputs.qmd
All changes

@@
 source("00_dirs.R")
+feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")
 
-overwrite <- F
+prettyplot <- function() {
+  theme_classic() +
+    theme(legend.position = "none",
+          text = element_text(family = "serif", size = 12, colour = "black"),
+          axis.title.x = element_text(vjust = 0.5),
+          axis.title.y = element_text(hjust = 0.5))
+}
 ```
@@
 
-Data for nutrient runoff from agriculture fertilisers and pesticides was downloaded from @halpern_recent_2019-1 [dataset here: @halpern_recent_2019].
+Data for nutrient runoff from agriculture fertilisers and pesticides was downloaded from @halpern_recent_2019-1 [dataset here: @halpern_recent_2019]. The data is in annual tonnes N.
 
@@
 
-halpern_N_rast <- file.path(input_Ndata_path, "halpern_2019", "nutrient_pollution_2013_raw.tif") %>% rast()
+halpern_N_rast <- file.path(input_Ndata_path, "halpern_2019", "nutrient_pollution_2013_raw.tif") %>%
+  rast()
 
@@
   lapply(function(ins) {project(halpern_N_rast, ins, method = "cubic")})
-
-# Change to the Molleweide projection
-tuholske_N_rast <- file.path(input_Ndata_path, "tuholske_2021", "global_effluent_2015_tot_N.tif") %>% rast() 
-tuholske_insets <- molle_insets %>% 
-  lapply(function(ins) {project(tuholske_N_rast, ins, method = "cubic")})
-
-# The halpern data has NA values for land but the tuholske data does not
-tuholske_insets <- map2(tuholske_insets, halpern_insets, function(rast, mask) {
-  mask(rast, mask)
-})
-
-background_N_insets <- map2(halpern_insets, tuholske_insets, function(dat1, dat2) {dat1 + dat2})
-
-map2(names(halpern_insets), background_N_insets, function(nm, rast) {
-  writeRaster(rast, file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")))
-})
 ```
 
-Data for inputs of human sewage in coastal ecosystems was sourced from @tuholske_global_2021 [dataset here: @tuholske_mapping_2021]. 
-The data is in annual g N.
+Data for inputs of human sewage in coastal ecosystems was sourced from @tuholske_global_2021 [dataset here: @tuholske_mapping_2021]. The data is in annual g N.
 
@@
 
-# Change to the Molleweide projection
-tuholske_N_rast <- file.path(input_Ndata_path, "tuholske_2021", "global_effluent_2015_tot_N.tif") %>% rast() 
+tuholske_N_rast <- file.path(input_Ndata_path, "tuholske_2021", "global_effluent_2015_tot_N.tif") %>%
+  rast() 
+tuholske_N_rast <- tuholske_N_rast * 10^-6 # Change from g to t
+
+# Change to the Molleweide projection with insets
 tuholske_insets <- molle_insets %>% 
@@
 
-# The halpern data has NA values for land but the tuholske data does not
+# The halpern data has NA values for land but the tuholske data does not, so mask
 tuholske_insets <- map2(tuholske_insets, halpern_insets, function(rast, mask) {
@@
 #| code-summary: Combine and save background N data
+#| eval: false
 
@@
 map2(names(halpern_insets), background_N_insets, function(nm, rast) {
-  writeRaster(rast, file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")))
+  writeRaster(rast, 
+              file.path(input_Ndata_path, str_c("background_N_inset_", nm, ".tif")), 
+              overwrite = T)
 })
 ```
+
+The code above was only run once, background N rasters can now be loaded.
 
@@
 
-# Load modelled N data
+# Combine modelled N data with background N
 
@@
 
-# Combine with background N
+```{r matching cells}
+#| code-summary: Get background nitrogen data for farm cells
 
-```{r}
-# 2. Extract 3x3 neighborhood data for each farm point
+farm_cells <- map(background_N_insets, function(back_N_rast) {
   # Get cell numbers for each farm point
   farm_cells <- cellFromXY(back_N_rast, st_coordinates(farm_sfs))
+  farm_cells <- farm_locs %>% 
+    mutate(cell = farm_cells) %>% 
+    filter(!is.na(cell))
 
-# Function to get 5x5 neighborhood cell numbers
-get_neighborhood_cells <- function(raster, center_cells) {
-  # Get raster dimensions
-  nrows <- nrow(raster)
-  ncols <- ncol(raster)
+  # Extract nutrient values and combine with cell_ids
+  farm_cells$back_N <- terra::extract(back_N_rast$nutrient_pollution_2013_raw,
+                                      farm_cells$cell)$nutrient_pollution_2013_raw
 
-  # Convert cell numbers to row/col indices
-  rows <- rowFromCell(raster, center_cells)
-  cols <- colFromCell(raster, center_cells)
+  # Fill gaps from original data with 8 neighbours
+  farm_cells_gaps <- farm_cells %>% filter(is.na(back_N))
+  for (i in 1:nrow(farm_cells_gaps)) {
+    adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, 
+                          cells = farm_cells_gaps$cell[i], directions = 8)
+    adj_cells_N <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
+      pull(nutrient_pollution_2013_raw) %>% 
+      mean(na.rm = T)
+    farm_cells_gaps$back_N[i] <- adj_cells_N
+  }
+  farm_cells <- farm_cells %>% 
+    filter(!is.na(back_N)) %>% 
+    rbind(farm_cells_gaps)
 
-  # Create all 25 neighbor offsets (including center) for 5x5 grid
-  offsets <- expand.grid(row_offset = -2:2, col_offset = -2:2)
-
-  # Initialize list to store results
-  all_neighbors <- vector("list", length(center_cells))
-
-  for(i in seq_along(center_cells)) {
-    # Calculate neighbor row/col positions
-    neighbor_rows <- rows[i] + offsets$row_offset
-    neighbor_cols <- cols[i] + offsets$col_offset
-
-    # Check bounds and filter valid cells
-    valid_cells <- neighbor_rows >= 1 & neighbor_rows <= nrows & 
-                   neighbor_cols >= 1 & neighbor_cols <= ncols
-
-    # Convert back to cell numbers
-    neighbor_cells <- cellFromRowCol(raster, 
-                                   neighbor_rows[valid_cells], 
-                                   neighbor_cols[valid_cells])
-
-    # Create position labels for 5x5 grid
-    row_names <- c("T2", "T1", "Crow", "B1", "B2")
-    col_names <- c("L2", "L1", "Ccol", "R1", "R2")
-
-    position_grid <- outer(row_names, col_names, paste, sep = "_")
-    position_labels <- as.vector(position_grid)
-    valid_positions <- position_labels[valid_cells]
-
-    all_neighbors[[i]] <- data.frame(
-      farm_id = farm_sfs$farm_id[i],
-      cell_id = neighbor_cells,  # for overlap detection
-      position = valid_positions,
-      stringsAsFactors = FALSE
-    )
+  # Fill gaps from original data with 16 neighbours
+  farm_cells_gaps <- farm_cells %>% filter(is.na(back_N))
+  if (nrow(farm_cells_gaps) != 0) {
+      for (i in 1:nrow(farm_cells_gaps)) {
+      adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, 
+                            cells = farm_cells_gaps$cell[i], directions = 16)
+      adj_cells_N <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
+        pull(nutrient_pollution_2013_raw) %>% 
+        mean(na.rm = T)
+      farm_cells_gaps$back_N[i] <- adj_cells_N
     }
-  return(do.call(rbind, all_neighbors))
+    farm_cells <- farm_cells %>% 
+      filter(!is.na(back_N)) %>% 
+      rbind(farm_cells_gaps)
   }
 
-# Get all neighborhood cells
-neighborhood_data <- get_neighborhood_cells(back_N_rast, farm_cells) %>% 
-  mutate(
-    category = case_when(position == "Crow_Ccol" ~ "farm_direct",
-                         position %in% c("T1_L1", "T1_Ccol", "T1_R1", "B1_L1", "B1_Ccol", "B1_R1", "Crow_L1", "Crow_R1") ~ "adjacent_1",
-                         T ~ "adjacent_2"),
-    category = factor(category, levels = c("farm_direct", "adjacent_1", "adjacent_2")),
-    position = factor(position, levels = c(
-      "T2_L2",   "T2_L1",   "T2_Ccol",   "T2_R1",   "T2_R2", 
-      "T1_L2",   "T1_L1",   "T1_Ccol",   "T1_R1",   "T1_R2", 
-      "Crow_L2", "Crow_L1", "Crow_Ccol", "Crow_R1", "Crow_R2", 
-      "B1_L2",   "B1_L1",   "B1_Ccol",   "B1_R1",   "B1_R2", 
-      "B2_L2",   "B2_L1",   "B2_Ccol",   "B2_R1",   "B2_R2"
-    )))
-
-# Extract nutrient values and combine with cell_ids
-nutrient_values <- terra::extract(back_N_rast$nutrient_pollution_2013_raw, neighborhood_data$cell_id)
-neighborhood_data <- cbind(neighborhood_data, nutrient_values) %>% 
-  rename(np = nutrient_pollution_2013_raw)
-
-# Fill gaps from original data with 8 neighbours
-neighborhood_data_gaps <- neighborhood_data %>% filter(is.na(np))
-for (i in 1:nrow(neighborhood_data_gaps)) {
-  adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, cells = neighborhood_data_gaps$cell_id[i], directions = 8)
-  neighborhood_data_gaps$np[i] <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
-    pull(nutrient_pollution_2013_raw) %>% 
-    mean(na.rm = T)
-}
-neighborhood_data <- neighborhood_data %>% 
-  filter(!is.na(np)) %>% 
-  rbind(neighborhood_data_gaps)
-neighborhood_data %>% filter(is.na(np)) %>% nrow() # 3221 still blank
-neighborhood_data %>% filter(is.na(np) & position == "Crow_Ccol") %>% nrow() # 87 of those are direct farm cells
-
-# Fill gaps from original data with 16 neighbours
-neighborhood_data_gaps <- neighborhood_data %>% filter(is.na(np))
-for (i in 1:nrow(neighborhood_data_gaps)) {
-  adj_cells <- adjacent(back_N_rast$nutrient_pollution_2013_raw, cells = neighborhood_data_gaps$cell_id[i], directions = 16)
-  neighborhood_data_gaps$np[i] <- back_N_rast$nutrient_pollution_2013_raw[adj_cells[1,]] %>% 
-    pull(nutrient_pollution_2013_raw) %>% 
-    mean(na.rm = T)
-}
-neighborhood_data <- neighborhood_data %>% 
-  filter(!is.na(np)) %>% 
-  rbind(neighborhood_data_gaps)
-neighborhood_data %>% filter(is.na(np)) %>% nrow() # 4489 still blank
-neighborhood_data %>% filter(is.na(np) & position == "Crow_Ccol") %>% nrow() # 149 of those are direct farm cells
+  default_val <- exp(median(log(farm_cells$back_N), na.rm = T))
+  farm_cells$back_N[is.na(farm_cells$back_N)] <- default_val
+  farm_cells$back_N[farm_cells$back_N < 0] <- default_val
+  farm_cells
+}) %>% 
+  bind_rows()
 ```
 
-```{r summary}
-# Summary statistics
-summary_stats <- neighborhood_data %>%
-  group_by(farm_id, category) %>%
-  reframe(
-    mean = mean(np, na.rm = T),
-    min = min(np, na.rm = T),
-    max = max(np, na.rm = T),
-    cells = n()
-  )
+```{r combine with N input from farms}
 
-# Maybe use adjacent farms to fill gaps?
+N_input <- output_cohorts_data_path %>% list.files(full.names = T) %>% 
+  str_subset("allfarms") %>% 
+  str_subset("P_excr") %>% 
+  qs::qread() %>% 
+  mutate(mean = mean * 6.25) %>% 
+  group_by(farm_ID, feed) %>% 
+  reframe(mean = sum(mean) * 10^-6) %>% 
+  pivot_wider(names_from = feed, values_from = mean)
 
-ggplot(neighborhood_data, aes(x = category, y = log(np), fill = position)) +
-  geom_boxplot()
+N_comp <- merge(farm_cells, N_input, by.y = "farm_ID", by.x = "farm_id", all = T) %>% 
+  select(-cell) %>% 
+  mutate(reference = reference/back_N,
+         past = past/back_N,
+         future = future/back_N) %>% 
+  pivot_longer(names_to = "feed", names_transform = list(feed = as.factor),
+               values_to = "ratio", cols = c("reference", "past", "future")) %>% 
+  mutate(feed = factor(feed, levels = c("reference", "past", "future")))
 ```
 
-# Plot mean nutrient pollution
+# Analyse
 
-```{r}
-farm_N <- summary_stats %>% 
-  filter(category == "farm_direct")
+```{r summary-plots}
 
-farm_N_sfs <- st_sf(farm_N = farm_N$mean, geometry = farm_locs$geometry) %>% 
-  st_transform(crs = crs(back_N_rast))
+N_comp %>%
+  group_by(country, farm_id, feed) %>% 
+  reframe(mean = mean(ratio, na.rm = T)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(past = (past-reference)/reference,
+         future = (future-reference)/reference) %>% 
+  select(-reference) %>% 
+  pivot_longer(names_to = "feed", values_to = "mean_ratio", cols = c(past, future)) %>% 
+  ggplot(aes(x = country, y = mean_ratio, fill = feed)) +
+  geom_boxplot() +
+  prettyplot() +
+  scale_y_continuous(breaks = seq(0,1,0.2), labels = seq(0,100,20), limits = c(0,0.6)) +
+  scale_fill_manual(values = feed_pal) +
+  labs(y = "Mean change in N input ratio", x = "Country")
 
-plot(farm_N_sfs)
+N_comp %>% 
+  filter(log(ratio) < 20) %>%
+  ggplot(aes(x = country, y = log(ratio), fill = feed)) +
+  geom_boxplot() +
+  prettyplot() +
+  # scale_y_continuous(breaks = seq(0,1,0.2), labels = seq(0,100,20), limits = c(0,0.6)) +
+  scale_fill_manual(values = feed_pal) +
+  labs(y = "Mean change in N input ratio", x = "Country")
 ```

### 2025-07-08 00_model_functions.R

@@ -39,11 +39,8 @@ find_read <- function(path, pattern){
   }
 }
 
-# Parameters definition
+# Parameters definitions
 # species_params['alpha']         [-] Feeding catabolism coefficient
-# species_params['betaprot']      [-] Assimilation coefficient for protein - SUPERCEEDED by digestibility coefficient
-# species_params['betalip']       [-] Assimilation coefficient for lipid - SUPERCEEDED by digestibility coefficient
-# species_params['betacarb']      [-] Assimilation coefficient for carbohydrates - SUPERCEEDED by digestibility coefficient
 # species_params['epsprot']       [J/gprot] Energy content of protein
 # species_params['epslip']        [J/glip] Energy content of lipid
 # species_params['epscarb']       [J/gcarb] Energy content of carbohydrate

### 2025-07-08 06.2_run_farms.R

@@ -17,6 +17,7 @@ library(units)
 library(qs)
 library(here)
 library(progressr)
+library(targets)
 conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
 
 here("00_model_functions.R") %>% source()
@@ -40,10 +41,11 @@ message(sprintf("Configuration:\n- Species: %s\n- Overwrite existing: %s\n- Outp
 # Main farm growth ------------------------------------------------------------------------------------------------
 Sys.setenv(TAR_PROJECT = "project_farmruns")
 rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
-targets::tar_make(seconds_meta_append = 90)
+# targets::tar_outdated()
+targets::tar_make(names = c("tar_farmrun_past", "tar_farmrun_future"), shortcut = T, seconds_meta_append = 90)
 
-tar_farm_IDs <- targets::tar_read(tar_farm_IDs)
-stat_names <- targets::tar_read(stat_names)
+targets::tar_load(tar_farm_IDs)
+targets::tar_load(stat_names)
 farmrun_reference_files <- file.path(output_growth_data_path, sprintf("farmrun_reference_%s.qs", fixnum(tar_farm_IDs,4)))
 farmrun_past_files <- file.path(output_growth_data_path, sprintf("farmrun_past_%s.qs", fixnum(tar_farm_IDs,4)))
 farmrun_future_files <- file.path(output_growth_data_path, sprintf("farmrun_future_%s.qs", fixnum(tar_farm_IDs,4)))
@@ -51,24 +53,30 @@ farmrun_comparisons_files <- file.path(output_cohorts_data_path, sprintf("farmru
 
 # Save the intermediate farm growth data
 for (f in seq_along(tar_farm_IDs)) {
-  targets::tar_read(tar_farmrun_reference, branches = f) %>%
+  targets::tar_load(tar_farmrun_reference, branches = f) 
+  tar_farmrun_reference %>%
     setNames(stat_names) %>%
     lapply(function(x) {colnames(x) <- c("t", "mean", "sd"); x}) %>%
     lapply(function(x) {cbind(x, farm_ID = tar_farm_IDs[f])})  %>%
     qs::qsave(farmrun_reference_files[f])
-  targets::tar_read(tar_farmrun_past, branches = f) %>%
+  
+  targets::tar_load(tar_farmrun_past, branches = f) 
[…]

### 2025-07-08 02_extracting_production_locations.qmd
Updating FAO data

@@
 Isolate production data for Atlantic salmon.
+
+```{r clean-raw-data}
+quantity <- file.path(rawdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
+  read.csv() %>% 
+  clean_names() %>% 
+  mutate(value = set_units(value, "t")) %>% 
+  select(-measure)
+
+environment_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
+  read.csv() %>% 
+  distinct(Code, Name_En)
+
+quantity <- quantity %>% 
+  merge(environment_codes, by.x = "environment_alpha_2_code", by.y = "Code") %>%
+  rename(environment = Name_En) %>% 
+  filter(environment == "Marine") %>% 
+  select(-environment_alpha_2_code)
+
+species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
+  read.csv() %>% 
+  filter(str_detect(Scientific_Name, "Salmo")) %>% 
+  filter(Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae")) %>% 
+  distinct(X3A_Code, Scientific_Name)
+
+quantity <- quantity %>% 
+  merge(species_codes, by.x = "species_alpha_3_code", by.y = "X3A_Code") %>% 
+  filter(!is.na(Scientific_Name)) %>% 
+  select(-species_alpha_3_code)
+
+status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
+  read.csv() %>% 
+  distinct(Symbol, Name_En, Description_En)
+
+quantity <- quantity %>% 
+  merge(status_codes, by.x = "status", by.y = "Symbol") %>% 
+  rename(status_nm = Name_En,
+         status_description = Description_En) %>% 
+  select(-status)
+
+```
+
 ```{r rich-raw-processing}

### 2025-07-09 01_tidying_data.qmd
Working with rdsi data

@@
 # Specify species of interest
-species <- c(
-  "atlantic_salmon",
-  "general_salmonid",
-  "european_seabass",
-  "gilthead_seabream",
-  "large_yellow_croaker",
-  "japanese_seabass",
-  "japanese_amberjack",
-  "general_grouper",
-  "pompano",
-  "milkfish"
-)
+species <- c("atlantic_salmon", "general_salmonid")
 
@@
 #rename the NASA files 
-
 #SST_files <- list.files(file.path(rdsi_dir, "raw_data/NASA/GHRSST_L4_MUR_0.25_SST"), full.names = FALSE, pattern = ".nc")
-
 # map(SST_files, \(this_file){
@@
 # this_file <- SST_files[[1]]
-# 
 # this_year=2013
@@
 #initialise lists for each year
-
 years <- c(2010:2019)
@@
 # Add annual files to a list of files for each year
-
 for(y in 1:length(years)){
-
   this_year <- years[y]
-
   this_years_files <- SST_files[grep(paste0(this_year, "_"), SST_files)]
-
   this_years_files <- this_years_files[!grepl(paste0(this_year, "_0229"), this_years_files)]
-
   year_lists[[y]] <- this_years_files
-
 }
@@
 # Extract the daily files for each year and rasterize in a stack
-
 days <- c(1:365)
-
 this_day <- days[1]
-
 rast_list = vector(mode = "list", length = length(days))
@@
 map(days, \(this_day){
-
   this_days_file_list <- sapply(year_lists, "[[", this_day)
-
   message("SST layer for Day ", this_day)
-
   this_day_stack <- rast(this_days_file_list, subds = "analysed_sst")
-
   this_day_mean_rast <- app(this_day_stack, "mean", na.rm=TRUE)-273.15
-
   writeRaster(this_day_mean_rast, filename = sprintf(here("data/_general_data/SST/SST_rasters/sst_nasa_mur_L4_0.25_mean2010-2019_day_%s.tif"), this_day))
-
 })
@@
 # now gapfill the saved rasters
-
 raw_SST_files <- list.files("data/_general_data/SST/SST_rasters/", full.names = TRUE)
@@
 ```{r}
-
 vuln_scores <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv")) %>% 
@@
 qsave(x = full_vuln_df, file = here("data/_general_data/species_layers/vulnerabilities/marine_spp_vulnerabilities_eutrophication.qs"))
-
 ```
@@
 qsave(x = aquamaps_0.5d, file = here("data/_general_data/species_layers/distribution/aquamaps_0.5d.qs"))
-
 ```

### 2025-07-09 02_extracting_production_locations.qmd
Working with rdsi data

--- 2025-07-08 02_extracting_production_locations.qmd
@@
 library(units)
+library(readr)
 
@@
 
-Isolate production data for Atlantic salmon.
+Clean aquaculture production data from the FAO and isolate production data for Atlantic salmon.
+
+```{r clean-raw-data}
+# Get aquaculture quantity in tonnes live weight
+quantity <- file.path(rawdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
+  read.csv() %>% 
+  clean_names() %>% 
+  mutate(value = set_units(value, "t")) %>% 
+  select(-measure)
+
+# Apply environment codes and filter by "marine"
+environment_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
+  read.csv() %>% 
+  distinct(Code, Name_En)
+
+quantity <- quantity %>% 
+  merge(environment_codes, by.x = "environment_alpha_2_code", by.y = "Code") %>%
+  rename(environment = Name_En) %>% 
+  filter(environment == "Marine") %>% 
+  select(-environment_alpha_2_code)
+
+# Apply species codes and filter by relevant species groups
+species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
+  read.csv() %>% 
+  filter(str_detect(Scientific_Name, "Salmo")) %>% 
+  filter(Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae")) %>% 
+  distinct(X3A_Code, Scientific_Name)
+
+quantity <- quantity %>% 
+  merge(species_codes, by.x = "species_alpha_3_code", by.y = "X3A_Code") %>% 
+  filter(!is.na(Scientific_Name)) %>% 
+  select(-species_alpha_3_code)
+
+# Apply status codes and filter by relevant species groups
+status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
+  read.csv() %>% 
+  distinct(Symbol, Name_En, Description_En)
+
+quantity <- quantity %>% 
+  merge(status_codes, by.x = "status", by.y = "Symbol") %>% 
+  rename(status_nm = Name_En,
+         status_description = Description_En) %>% 
+  select(-status)
+```
+
 ```{r rich-raw-processing}
@@
 
-(aquaculture_prod <- 
-  aquaculture_raw %>% 
+(aquaculture_prod <- aquaculture_raw %>% 
   clean_names() %>% 
@@
 
-spp_names <- 
-  aquaculture_prod %>% 
+spp_names <- aquaculture_prod %>% 
   filter(asfis_species_name_2 %in% c("Atlantic salmon", 
@@
 
-(mariculture_spp_prod <- 
-    aquaculture_raw %>% 
+(mariculture_spp_prod <- aquaculture_raw %>% 
     clean_names() %>% 
@@
     )
-
 ```

### 2025-07-09 00_dirs.R

@@ -9,6 +9,7 @@ this_species <- "atlantic_salmon"
 output_path <- here() %>% file.path("outputs")
 gendata_path <- here() %>% file.path("data", "_general_data")
 rawdata_path <- here() %>% file.path("data", "raw")
+rdsi_dir <- "/mnt/rdsi"
 species_path <- here() %>% file.path("data", this_species)
 species_fig_path <- file.path(species_path, "figures")
 

### 2025-07-10 02_extracting_production_locations.qmd
Consolidating

@@
 library(readr)
+library(ggplot2)
 
@@
 
-Clean aquaculture production data from the FAO and isolate production data for Atlantic salmon.
+# Get production data
+
+Clean aquaculture production data from the FAO and isolate data for Atlantic salmon.
 
@@
   rename(environment = Name_En) %>% 
-  filter(environment == "Marine") %>% 
   select(-environment_alpha_2_code)
 
-# Apply species codes and filter by relevant species groups
+# Apply species codes
 species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
   read.csv() %>% 
-  filter(str_detect(Scientific_Name, "Salmo")) %>% 
-  filter(Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae")) %>% 
   distinct(X3A_Code, Scientific_Name)
@@
 
-# Apply status codes and filter by relevant species groups
+# Apply status codes
 status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
@@
   select(-status)
+
+# Apply country and area codes
+country_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_COUNTRY_GROUPS.csv") %>% 
+  read.csv() %>% 
+  select(UN_Code, Identifier, Name_En, ISO3_Code)
+area_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_WATERAREA_GROUPS.csv") %>% 
+  read.csv() %>% 
+  select(Code, Name_En)
+
+quantity <- quantity %>% 
+  merge(country_codes, by.x = "country_un_code", by.y = "UN_Code", all.x = T, all.y = F) %>% 
+  merge(area_codes, by.x = "area_code", by.y = "Code", all.x = T, all.y = F) %>% 
+  rename(
+    country = Name_En.x, 
+    fao_fishing_area = Name_En.y,
+    country_id = Identifier
+    )
+
+quantity <- quantity %>% 
+  mutate(
+    environment = as.factor(environment),
+    Scientific_Name = as.factor(Scientific_Name),
+    status_nm = as.factor(status_nm),
+    status_description = as.factor(status_description),
+    country = as.factor(country),
+    fao_fishing_area = as.factor(fao_fishing_area),
+    ISO3_Code = as.factor(ISO3_Code)
+  ) %>% 
+  filter(
+    Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae") &
+    environment == "Marine" & 
+    status_nm != "Not significant (<0.5)"
+    )
+
+qsave(quantity, file.path(species_path, "production", "aquaculture_quantity.qs"))
 ```
 
-```{r rich-raw-processing}
-#| eval: false
+Average production over years 2019:2023.
 
-aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))
+```{r aquaculture-production}
+prod <- quantity %>% 
+  filter(between(period, 2019, 2023)) %>% 
+  group_by(country, Scientific_Name, environment, ISO3_Code, fao_fishing_area) %>% 
+  reframe(production = mean(value))
 
-(aquaculture_prod <- aquaculture_raw %>% 
-  clean_names() %>% 
-  select(c(1:7, starts_with("x"))) %>% 
-  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
-  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
-  filter(year %in% c(2015:2020)) %>% 
-  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) %>% 
-  summarise(production = sum(production)) %>% 
-    ungroup() %>% 
-     filter(environment_name=="Marine" & 
-           !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
-                                        "Abalones, winkles, conchs",
-                                        "Mussels", 
-                                        "Oysters",
-                                        "Shrimps, prawns",
-                                        "Crabs, sea-spiders",
-                                         "Freshwater molluscs",
-                                        "Squids, cuttlefishes, octopuses",
-                                        "Pearls, mother-of-pearl, shells",
-                                        "Miscellaneous aquatic plants",
-                                        "Scallops, pectens"),
-         !grepl("seaweeds" , asfis_species_name_3),
-         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
-    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
-     group_by(asfis_species_name_2) %>% 
-     summarise(production = mean(production)) %>% 
-  arrange(-production) %>% 
-    mutate(cum_prop = cumsum(production)/sum(production),
-           prop = production/sum(production))
-)
+qsave(prod, file.path(species_path, "production", "aquaculture_production.qs"))
 
-spp_names <- aquaculture_prod %>% 
-  filter(asfis_species_name_2 %in% c("Atlantic salmon", 
-                                     "Rainbow trout", 
-                                     "European seabass", 
-                                     "Large yellow croaker",
-                                     "Gilthead seabream",
-                                     "Coho(=Silver) salmon",
-                                     "Japanese seabass", 
-                                     "Japanese amberjack", 
-                                     "Amberjacks nei",
-                                     "Pompano", 
-                                     "Milkfish") | 
-           grepl(pattern = "rouper", asfis_species_name_2) & production > 1) %>% 
-  pull(asfis_species_name_2)
-
-(mariculture_spp_prod <- aquaculture_raw %>% 
-    clean_names() %>% 
-    select(c(1:7, starts_with("x"))) %>% 
-    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
-    mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
-    filter(year %in% c(2017)) %>% 
-    filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
-             !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
-                                          "Abalones, winkles, conchs",
-                                          "Mussels", 
-                                          "Oysters",
-                                          "Shrimps, prawns",
-                                          "Crabs, sea-spiders",
-                                          "Freshwater molluscs",
-                                          "Squids, cuttlefishes, octopuses",
-                                          "Pearls, mother-of-pearl, shells",
-                                          "Miscellaneous aquatic plants",
-                                          "Scallops, pectens"),
-           !grepl("seaweeds" , asfis_species_name_3),
-           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
-    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
-    summarise(production = sum(production)) %>% 
-    ungroup() %>% 
-    mutate(asfis_species_name_2 = case_when(asfis_species_name_2 == "Marine fishes nei" & country_name == "Viet Nam" ~ "Groupers nei",
-                                            TRUE ~ asfis_species_name_2)) %>% 
-    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
-    group_by(iso3c, country_name, year) %>% 
-    nest() %>% 
-    mutate(national_production = map(data, ~(sum(.$production)))) %>% 
-    unnest(cols = c(data, national_production)) %>% 
-    ungroup() %>% 
-    filter(asfis_species_name_2 %in% spp_names) %>% 
-    mutate(prop_production = production/national_production) %>% 
-    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
-  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
-                                asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
-                                asfis_species_name_2 %in% c("Amberjacks nei") ~ "japanese_amberjack",
-                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
-  relocate(model_name, .before = asfis_species_name_2) %>% 
-  filter(prop_production>0) %>% 
-    mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
-                                 TRUE ~ "General marine fish"))
-    )
+ggplot(prod, aes(x = country, y = production)) +
+  geom_point() +
+  coord_flip()
 ```
 
-Pull in farm locations, add FAO Major fishing regions
+# Match farm locations to FAO regions
 
-```{r}
+Pull in farm locations, add FAO Major fishing regions.
+
+```{r FAO-fishing-regions-of-farms}
 farms_sf <- qread(file = "data/_general_data/farm_locations/locations.qs") %>% 
@@
 
-```{r}
-
+```{r fix-misalignment}
 # filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
-
-mariculture_prod_all <- 
-    aquaculture_raw %>% 
+mariculture_prod_all <- aquaculture_raw %>% 
   clean_names() %>% 
@@
 
-#Check that farm locations in mapped data are in the same FAO fishing regions as the production data
+# Check that farm locations in mapped data are in the same FAO fishing regions as the production data
 
@@
 ```
+
+# From Rich
+
+```{r rich-raw-processing}
+#| eval: false
+
+aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))
+
+(aquaculture_prod <- aquaculture_raw %>% 
+  clean_names() %>% 
+  select(c(1:7, starts_with("x"))) %>% 
+  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+  filter(year %in% c(2015:2020)) %>% 
+  group_by(asfis_species_name_2, asfis_species_name_3, environment_name, year) %>% 
+  summarise(production = sum(production)) %>% 
+    ungroup() %>% 
+     filter(environment_name=="Marine" & 
+           !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
+                                        "Abalones, winkles, conchs",
+                                        "Mussels", 
+                                        "Oysters",
+                                        "Shrimps, prawns",
+                                        "Crabs, sea-spiders",
+                                         "Freshwater molluscs",
+                                        "Squids, cuttlefishes, octopuses",
+                                        "Pearls, mother-of-pearl, shells",
+                                        "Miscellaneous aquatic plants",
+                                        "Scallops, pectens"),
+         !grepl("seaweeds" , asfis_species_name_3),
+         !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
+     group_by(asfis_species_name_2) %>% 
+     summarise(production = mean(production)) %>% 
+  arrange(-production) %>% 
+    mutate(cum_prop = cumsum(production)/sum(production),
+           prop = production/sum(production))
+)
+
+spp_names <- aquaculture_prod %>% 
+  filter(asfis_species_name_2 %in% c("Atlantic salmon", 
+                                     "Rainbow trout", 
+                                     "European seabass", 
+                                     "Large yellow croaker",
+                                     "Gilthead seabream",
+                                     "Coho(=Silver) salmon",
+                                     "Japanese seabass", 
+                                     "Japanese amberjack", 
+                                     "Amberjacks nei",
+                                     "Pompano", 
+                                     "Milkfish") | 
+           grepl(pattern = "rouper", asfis_species_name_2) & production > 1) %>% 
+  pull(asfis_species_name_2)
+
+(mariculture_spp_prod <- aquaculture_raw %>% 
+    clean_names() %>% 
+    select(c(1:7, starts_with("x"))) %>% 
+    pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+    mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+    filter(year %in% c(2017)) %>% 
+    filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
+             !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
+                                          "Abalones, winkles, conchs",
+                                          "Mussels", 
+                                          "Oysters",
+                                          "Shrimps, prawns",
+                                          "Crabs, sea-spiders",
+                                          "Freshwater molluscs",
+                                          "Squids, cuttlefishes, octopuses",
+                                          "Pearls, mother-of-pearl, shells",
+                                          "Miscellaneous aquatic plants",
+                                          "Scallops, pectens"),
+           !grepl("seaweeds" , asfis_species_name_3),
+           !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+    group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
+    summarise(production = sum(production)) %>% 
+    ungroup() %>% 
+    mutate(asfis_species_name_2 = case_when(asfis_species_name_2 == "Marine fishes nei" & country_name == "Viet Nam" ~ "Groupers nei",
+                                            TRUE ~ asfis_species_name_2)) %>% 
+    mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
+    group_by(iso3c, country_name, year) %>% 
+    nest() %>% 
+    mutate(national_production = map(data, ~(sum(.$production)))) %>% 
+    unnest(cols = c(data, national_production)) %>% 
+    ungroup() %>% 
+    filter(asfis_species_name_2 %in% spp_names) %>% 
+    mutate(prop_production = production/national_production) %>% 
+    filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
+  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
+                                asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
+                                asfis_species_name_2 %in% c("Amberjacks nei") ~ "japanese_amberjack",
+                                TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
+  relocate(model_name, .before = asfis_species_name_2) %>% 
+  filter(prop_production>0) %>% 
+    mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
+                                 TRUE ~ "General marine fish"))
+    )
+```
+
+```{r fix-misalignment}
+# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
+mariculture_prod_all <- aquaculture_raw %>% 
+  clean_names() %>% 
+  select(c(1:7, starts_with("x"))) %>% 
+  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
+  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
+  filter(year %in% c(2017)) %>% 
+  filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
+            !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
+                                        "Abalones, winkles, conchs",
+                                        "Mussels", 
+                                        "Oysters",
+                                        "Shrimps, prawns",
+                                        "Crabs, sea-spiders",
+                                        "Freshwater molluscs",
+                                        "Squids, cuttlefishes, octopuses",
+                                        "Pearls, mother-of-pearl, shells",
+                                        "Miscellaneous aquatic plants",
+                                        "Scallops, pectens"),
+          !grepl("seaweeds" , asfis_species_name_3),
+          !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
+  group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
+  summarise(production = sum(production)) %>% 
+  ungroup() %>% 
+  mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
+  group_by(iso3c, country_name, year) %>% 
+  nest() %>% 
+  mutate(national_production = map(data, ~(sum(.$production)))) %>% 
+  unnest(cols = c(data, national_production)) %>% 
+  ungroup() %>% 
+  filter(production>0) %>% 
+  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
+  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
+                              asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
+                              TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
+  relocate(model_name, .before = asfis_species_name_2) %>% 
+  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
+                                TRUE ~ "General marine fish")) %>% 
+  filter(asfis_species_name_2 %in% spp_names) %>% 
+  mutate(prop_production = production/national_production)
+
+# Check that farm locations in mapped data are in the same FAO fishing regions as the production data
+
+farm_fao_intersect <- qread(here("data/_general_data/farm_locations/locations_w_fishing_areas.qs"))
+
+farm_list <- 
+  farm_fao_intersect %>% 
+  group_by(iso3c, country, species_group) %>% 
+  group_split()
+
+#Test function
+
+this_country_region <- farm_list[[4]]
+
+(fao_area_code_check <- 
+  map_df(farm_list, \(this_country_region){
+
+    farm_country_name <- this_country_region$country %>% unique()
+    farm_iso3c <- this_country_region$iso3c %>% unique()
+    farm_fao_code <- this_country_region$F_CODE %>% unique() %>% sort()
+    farm_spp_grp <- this_country_region$species_group %>% unique()
+
+    prod_data <- 
+      mariculture_prod_all %>% 
+      filter(iso3c == farm_iso3c & 
+               fao_major_fishing_area_code %in% farm_fao_code & 
+               country_name == farm_country_name & 
+               farm_name == farm_spp_grp)
+
+    prod_spp_group <- prod_data$farm_name %>% unique()
+
+    prod_fao_code <- prod_data$fao_major_fishing_area_code %>% unique() %>% sort()
+
+    return(
+      tibble(iso3c = farm_iso3c, 
+             countryname = farm_country_name, 
+             farm_spp_group = farm_spp_grp, 
+             mapped_fishing_areas = paste(farm_fao_code, collapse = ' '), 
+             production_fishing_areas = paste(prod_fao_code, collapse = ' ')) %>% 
+             mutate(same_fishing_area = mapped_fishing_areas == production_fishing_areas))
+
+}) %>% filter(!production_fishing_areas == "")
+)
+
+```

### 2025-07-10 06_run_atlantic_salmon_model.qmd
Consolidating

---
title: "Individual Mariculture Modeling Analysis"
format: html
editor: source
---

# Introduction

This document runs individual mariculture modeling analyses for Atlantic salmon farms. It processes farm location data, species parameters, and conducts sensitivity analyses to understand the impact of various parameters on fish and farm growth measures.

```{r setup}
#| warning: false
#| message: false

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
```

```{r filenames}
# Set up parallel processing
# plan(multisession, workers = parallelly::availableCores()-1)

# Filenames
species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
farm_locations_parquet <- file.path(input_farm_coords_path, "farm_coords.parquet")
farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
farm_ts_data_file <- file.path(output_farm_data_path, "farm_ts_data.qs")
species_params_file <- file.path(output_species_data_path, "species_params.qs")
sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
farm_harvest_file <- file.path(output_farm_data_path, "farm_harvest_size.qs")
```

# Data for targets pipelines

Much of the actual analysis is run through targets pipelines. Therefore, we need to make sure that the files going into those pipelines are correct and up to date.

Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms.

```{r farm-coordinates}
times_N <- c("t_start" = 121, "t_end" = 121+547, "dt" = 1)
times_S <- c("t_start" = 274, "t_end" = 274+547, "dt" = 1)

farm_coords <- farm_locations_parquet %>% 
  read_parquet() %>% 
  mutate(t_start = case_when(lat > 0 ~ times_N['t_start'], TRUE ~ times_S['t_start']), 
          t_end = case_when(lat > 0 ~ times_N['t_end'], TRUE ~ times_S['t_end']),
          t_start = unname(t_start),
          t_end = unname(t_end))

qsave(farm_coords, farm_coords_file)

# Also save geometry for later
file.path(input_farm_coords_path, "atlantic_salmon_locations_w_temps.qs") %>% 
  qread() %>% 
  dplyr::filter(day == "day_1") %>% 
  dplyr::select(farm_id, geometry, country) %>% 
  qsave(farm_geometry_file)
```

## Farm Time Series Data

Process Sea Surface Temperature (SST) data for each farm location.

```{r farm-ts-data}
farms_to_omit <- qread(sprintf(file.path(input_farm_coords_path, "%s_farms_to_omit.qs"), this_species))
farm_SST_data <- read_parquet(file.path(input_farm_sst_path, "farm_SST_extracted.parquet"))
farm_IDs <- farm_SST_data %>%
  filter(!farm_id %in% farms_to_omit) %>%
  distinct(farm_id) %>%
  pull(farm_id)

farm_ts_data <- farm_SST_data %>%
  rename(farm_ID = farm_id) %>% 
  select(c(farm_ID, day, temp_c)) %>%
  mutate(day = str_split_i(day, "day_", 2) %>% as.integer())

qsave(farm_ts_data, farm_ts_data_file)
```

# Species and population parameters

Load species-specific parameters from Excel file.

```{r species-parameters}
species_params <- readxl::read_excel(
  path = species_params_excel["file"], 
  sheet = species_params_excel["sheet"]
)
vals <- species_params$Value
names(vals) <- species_params$Quantity
species_params <- vals[!is.na(vals)]
qsave(species_params, species_params_file)
```

Load population-specific parameters.

```{r population-parameters}
pop_params <- readxl::read_excel(path = pop_params_excel["file"])
vals <- pop_params$Value
names(vals) <- pop_params$Quantity
pop_params <- vals[!is.na(vals)]
qsave(pop_params, pop_params_file)
```

# Farm Harvest Size Calculations

Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline.

```{r farm-harvest-size}
Sys.setenv(TAR_PROJECT = "project_farmruns")

targets::tar_make(harvest_size)
targets::tar_load(harvest_size)
qsave(harvest_size, farm_harvest_file)

mean(harvest_size$weight)
min(harvest_size$weight)
max(harvest_size$weight)

ggplot(harvest_size, aes(x = weight)) +
  geom_histogram(fill = "salmon", alpha = 0.75, colour = "black")
```

# Sensitivity analysis

Run the sensitivity runs using the targets pipeline. 
Note that this can take a long time (hours), as the species parameters (19) are run for each farm (2721) and factor (3) and the population parameters (6) are run for a smaller number of farms (271) and factor with a simulated population of 500 fish.

```{r sensitivity-run}
Sys.setenv(TAR_PROJECT = "project_sensitivities")

targets::tar_validate()
targets::tar_visnetwork(targets_only = T)
targets::tar_outdated()
targets::tar_make(
  seconds_meta_append = 120
  )
```

## Process sensitivity results

Combine and visualise sensitivity analysis results.

```{r sensitivity-results}
targets::tar_load(sens_results_spec)
targets::tar_load(sens_results_pop)

sens_results <- rbind(
  sens_results_pop,
  sens_results_spec
)

sens_measures <- levels(sens_results$measure)
sens_results_files <- file.path(output_sens_data_path, paste0("sens_results_", sens_measures, ".qs"))
sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
sens_results_figfiles2 <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))

for (sm in seq_along(sens_measures)) {
  sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    qsave(sens_results_files[sm])

  p <- sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens)) +
    geom_col(fill = "salmon", alpha = 0.65, colour = "black") +
    geom_errorbar(width = 0.5) +
    coord_flip() +
    theme_classic()
  qsave(p, sens_results_figfiles[sm])
  ggsave(sens_results_figfiles2[sm])
}
```

# Run farms

```{r run-farms-pipeline}
Sys.setenv(TAR_PROJECT = "project_farmruns")

targets::tar_validate()
targets::tar_visnetwork(targets_only = T)
targets::tar_outdated()
targets::tar_make(seconds_meta_append = 90)
```

```{r farm-run-results}
targets::tar_load(cohort_results)
```

### 2025-07-10 00_model_functions.R

@@ -121,11 +121,11 @@ app_feed <- function(provided, ingested, prop, macro, digestibility) {
   assimilated <- ingested_amount * digestibility
   
   # Return only necessary values in a numeric vector
-  c(provided = sum(provided_amount),
-    ingested = sum(ingested_amount),
-    uneaten = sum(provided_amount - ingested_amount),
-    assimilated = sum(assimilated),
-    excreted = sum(ingested_amount - assimilated))
+  c(provided = sumna(provided_amount),
+    ingested = sumna(ingested_amount),
+    uneaten = sumna(provided_amount - ingested_amount),
+    assimilated = sumna(assimilated),
+    excreted = sumna(ingested_amount - assimilated))
 }
 
 fish_growth <- function(pop_params, species_params, water_temp, feed_params, times, init_weight, ingmax) {

### 2025-07-10 06.0_run_atlantic_salmon_model.R

@@ -1,59 +1,0 @@
-# Setup -----------------------------------------------------------------------------------------------------------
-library(magrittr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggplot2)
-library(terra)
-library(qs)
-library(here)
-library(sf)
-library(purrr)
-library(furrr)
-library(targets)
-library(future)
-library(arrow)
-library(readxl)
-library(units)
-library(tictoc)
-library(conflicted)
-conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
-
-# functions
-source("00_model_functions.R")
-
-# paths
-source("00_dirs.R")
-
-# STEP 1: Temperature forcings ------------------------------------------------------------------------------------
-# You don't need to do this again unless you make changes - all the important stuff is already saved
-source("04_extracting_temperatures.R")
-
-# STEP 2: Formulate feeds -----------------------------------------------------------------------------------------
-overwrite <- F
-source("05_formulating_feeds.R")
-
-# STEP 3: Run model -----------------------------------------------------------------------------------------------
-## Individuals ----------------------------------------------------------------------------------------------------
-overwrite <- F
-source("06.1_run_individual.R")
-
-## Farm growth ----------------------------------------------------------------------------------------------------
-overwrite <- F
-source("06.2_run_farms.R")
-
-# STEP 3: Analysis ------------------------------------------------------------------------------------------------
-source("12_data_analysis.R")
-
-# Benchmarking ----------------------------------------------------------------------------------------------------
-# rbenchmark::benchmark(
-#   df = {apportion_feed(provided = 10, ingested = 9,
-#                            prop = feed_params[['Carbohydrates']]$proportion,
-#                            macro = feed_params[['Carbohydrates']]$ing_carb,
-#                            digestibility = feed_params[['Carbohydrates']]$ing_carb_digestibility)},
-#   matrix = {apportion_feed_short(provided = 10, ingested = 9,
-#                              prop = feed_params[['Carbohydrates']]$proportion,
-#                              macro = feed_params[['Carbohydrates']]$ing_carb,
-#                              digestibility = feed_params[['Carbohydrates']]$ing_carb_digestibility)},
-#   replications = 1000
-# )

### 2025-07-10 06.1_run_individual.R

@@ -1,202 +1,0 @@
-# Disable all linters for this file
-# nolint start
-
-library(arrow)
-library(sf)
-library(dplyr)
-library(tidyr)
-library(terra)
-library(magrittr)
-library(furrr)
-library(future)
-library(tictoc)
-library(ggplot2)
-library(fs)
-library(conflicted)
-library(stringr)
-library(readxl)
-library(units)
-library(qs)
-library(here)
-library(targets)
-conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
-
-# Configuration ---------------------------------------------------------------------------------------------------
-# Set up parallel processing
-# plan(multisession, workers = parallelly::availableCores()-1)
-
-# Filenames
-species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
-pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
-farm_locations_parquet <- file.path(input_farm_coords_path, "farm_coords.parquet")
-farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
-farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
-farm_ts_data_file <- file.path(output_farm_data_path, "farm_ts_data.qs")
-species_params_file <- file.path(output_species_data_path, "species_params.qs")
-sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
-pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
-feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
-farm_harvest_file <- file.path(output_farm_data_path, "farm_harvest_size.qs")
-
-# Farm coordinates ------------------------------------------------------------------------------------------------
-farm_coords <- if (!file.exists(farm_coords_file)) {
-  times_N <- c("t_start" = 121, "t_end" = 121+547, "dt" = 1)
-  times_S <- c("t_start" = 274, "t_end" = 274+547, "dt" = 1)
-  
-  fc <- farm_locations_parquet %>% 
-    read_parquet() %>% 
-    mutate(t_start = case_when(lat > 0 ~ times_N['t_start'], TRUE ~ times_S['t_start']), 
[…]

### 2025-07-10 06.2_run_farms.R

@@ -1,95 +1,0 @@
-# nolint start
-
-library(arrow)
-library(sf)
-library(dplyr)
-library(tidyr)
-library(terra)
-library(magrittr)
-library(furrr)
-library(future)
-library(tictoc)
-library(fs)
-library(conflicted)
-library(stringr)
-library(readxl)
-library(units)
-library(qs)
-library(here)
-library(progressr)
-library(targets)
-conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
-
-here("00_model_functions.R") %>% source()
-here("00_dirs.R") %>% source()
-
-# Configuration ---------------------------------------------------------------------------------------------------
-# Set up parallel processing
-# plan(multisession, workers = parallelly::availableCores()-2)
-# plan(multisession, workers = works)
-
-# Filenames
-farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
-sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
-
-# Print configuration summary
-message(sprintf("Configuration:\n- Species: %s\n- Overwrite existing: %s\n- Output path: %s",
-               this_species,
-               ifelse(overwrite, "yes", "no"),
-               output_path))
-
-# Main farm growth ------------------------------------------------------------------------------------------------
-Sys.setenv(TAR_PROJECT = "project_farmruns")
-rm(list = grep("tar_", ls(), value = TRUE), envir = .GlobalEnv)
-# targets::tar_outdated()
-targets::tar_make(names = c("tar_farmrun_past", "tar_farmrun_future"), shortcut = T, seconds_meta_append = 90)
-
-targets::tar_load(tar_farm_IDs)
-targets::tar_load(stat_names)
-farmrun_reference_files <- file.path(output_growth_data_path, sprintf("farmrun_reference_%s.qs", fixnum(tar_farm_IDs,4)))
-farmrun_past_files <- file.path(output_growth_data_path, sprintf("farmrun_past_%s.qs", fixnum(tar_farm_IDs,4)))
-farmrun_future_files <- file.path(output_growth_data_path, sprintf("farmrun_future_%s.qs", fixnum(tar_farm_IDs,4)))
[…]

### 2025-07-10 12_data_analysis.R

@@ -1,29 +1,27 @@
 # nolint start
 
-# Setup -----------------------------------------------------------------------------------------------------------
-suppressPackageStartupMessages({
-  library(magrittr)
-  library(dplyr)
-  library(tidyr)
-  library(stringr)
-  library(terra)
-  library(qs)
-  library(here)
-  library(arrow)
-  library(units)
-  library(ggplot2)
-  library(sf)
-  library(units)
-  library(rnaturalearth)
-  library(rnaturalearthdata)
-  library(conflicted)
-  library(furrr)
-  library(future)
-  conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
-})
+# Setup ------------------------------------------------------------------------------------------------
+library(magrittr)
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(terra)
+library(qs)
+library(here)
+library(arrow)
+library(units)
+library(ggplot2)
+library(sf)
+library(units)
+library(rnaturalearth)
+library(rnaturalearthdata)
+library(conflicted)
+library(furrr)
+library(future)
+conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
 
 # This script aims to take the model outputs from the targets pipeline and answer specific questions.
-# Paths & globals -------------------------------------------------------------------------------------------------
+# Paths & globals --------------------------------------------------------------------------------------
 source("00_model_functions.R")
 source("00_dirs.R")
 
@@ -45,8 +43,8 @@ install_unit(symbol = "g_fish")
 install_unit(symbol = "kg_fish", def = "1000 g_fish")
 install_unit(symbol = "t_fish", def = "1000 kg_fish")
 
-# Different feeds -------------------------------------------------------------------------------------------------
-## Question 1 -----------------------------------------------------------------------------------------------------
+# Different feeds --------------------------------------------------------------------------------------
+## Question 1 ------------------------------------------------------------------------------------------
 # How does the change in feed affect daily and overall excretion and uneaten feed waste (P, L, C, total)?
 
 coho_biom <- aggregate_comparison_files %>% 
@@ -86,7 +84,7 @@ all_inputs <- all_inputs %>%
 
 qs::qsave(all_inputs, file.path(data_analysis_path, "all_waste_inputs.qs"))
 
[…]

### 2025-07-10 targets/_targets_farmruns.R

@@ -12,34 +12,69 @@ tar_source(files = c("00_model_functions.R", "00_dirs.R"))
 
 list(
 # Get previously saved data ---------------------------------------------------------------------------------------
-  tar_target(farms_to_omit_file, file.path(input_farm_coords_path, "atlantic_salmon_farms_to_omit.qs"), format = "file"),
   tar_target(farm_coords_file, file.path(output_farm_data_path, "farm_coords.qs"), format = "file"),
   tar_target(farm_ts_data_file, file.path(output_farm_data_path, "farm_ts_data.qs"), format = "file"),
   tar_target(species_params_file, file.path(output_species_data_path, "species_params.qs"), format = "file"),
   tar_target(pop_params_file, file.path(output_species_data_path, "pop_params.qs"), format = "file"),
   tar_target(feed_params_file, file.path(output_species_data_path, "feed_params.qs"), format = "file"),
-  tar_target(harvest_size_file, file.path(output_farm_data_path, "farm_harvest_size.qs"), format = "file"),
-  tar_target(farm_static_data_file, file.path(input_farm_coords_path, "atlantic_salmon_locations_w_temps.qs"), format = "file"),
+  tar_target(farm_production_file, file.path(input_farm_coords_path, "atlantic_salmon_locations_w_temps.qs"), format = "file"),
 
-  tar_target(farms_to_omit, farms_to_omit_file %>% qs::qread()),
-  tar_target(farm_coords, farm_coords_file %>% qs::qread() %>% filter(!farm_ID %in% farms_to_omit)),
-  tar_target(farm_ts_data, farm_ts_data_file %>% qs::qread() %>% filter(!farm_ID %in% farms_to_omit)),
-  tar_target(species_params, species_params_file %>% qs::qread()),
-  tar_target(pop_params, pop_params_file %>% qs::qread()),
-  tar_target(feed_params, feed_params_file %>% qs::qread()),
+  tar_target(farm_coords, qs::qread(farm_coords_file)),
   tar_target(
-    farm_harvest_size,
-    harvest_size_file %>%
-      qs::qread() %>%
-      select(c(farm_ID, weight)) %>%
-      mutate(weight = units::set_units(weight, "g"))
-  ), 
+    farm_IDs,
+    qs::qread(farm_ts_data_file) %>% 
+      distinct(farm_ID) %>% 
+      pull(farm_ID) #%>% sample(25)
+  ),
[…]

### 2025-07-10 targets/_targets_sensitivities.R

@@ -5,347 +5,209 @@ library(parallelly)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 6, seconds_timeout = 90),
+  controller = crew_controller_local(workers = 5, seconds_timeout = 90),
   workspace_on_error = TRUE
 )
 
+tar_source(c(
+  "00_dirs.R",
+  "00_model_functions.R"
+))
+
 list(
+  # Load previously saved data --------------------------------------------------------------------------------
+  tar_target(farm_coords_file, file.path(output_farm_data_path, "farm_coords.qs"), format = "file"),
+  tar_target(farm_ts_data_file, file.path(output_farm_data_path, "farm_ts_data.qs"), format = "file"),
+  tar_target(species_params_file, file.path(output_species_data_path, "species_params.qs"), format = "file"),
+  tar_target(pop_params_file, file.path(output_species_data_path, "pop_params.qs"), format = "file"),
+  tar_target(feed_params_file, file.path(output_species_data_path, "feed_params.qs"), format = "file"),
+
+  tar_target(farm_coords, qs::qread(farm_coords_file)),
   tar_target(
-    tar_farm_IDs,
-    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID)
+    farm_IDs,
+    qs::qread(farm_ts_data_file) %>% 
+      distinct(farm_ID) %>% 
+      pull(farm_ID)
   ),
   tar_target(
-    tar_farm_ID_sample,
-    farm_ts_data %>% distinct(farm_ID) %>% pull(farm_ID) %>% sample(271)
+    farm_IDs_sample,
+    farm_IDs %>% 
+      sample(as.integer(length(farm_IDs)*0.1)) #%>% sample(3)
   ),
-  
-  tar_target(tar_param_names_pop, c("meanW", "deltaW", "meanImax", "deltaImax", "overFmean", "overFdelta")),
-  tar_target(tar_param_names_spec, sens_params_names[!sens_params_names %in% tar_param_names_pop]),
-  
   tar_target(
-    tar_farm_ts,
-    command = {
-      farm_ts_data %>%
-        merge(farm_coords, by = "farm_ID") %>% 
-        dplyr::filter(farm_ID %in% tar_farm_IDs) %>%
[…]

### 2025-07-10 02_extracting_production_locations.qmd
All species

@@
   filter(
-    Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae") &
+    # Scientific_Name %in% c("Salmoniformes (=Salmonoidei)", "Salmo spp", "Salmo salar", "Salmonidae") &
     environment == "Marine" & 

### 2025-07-10 02_extracting_production_locations.qmd
Proper index of files

@@
 
-source(here("00_dirs.R"))
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```
@@
 ```{r aquaculture-production}
-prod <- quantity %>% 
-  filter(between(period, 2019, 2023)) %>% 
-  group_by(country, Scientific_Name, environment, ISO3_Code, fao_fishing_area) %>% 
+production <- quantity %>% 
+  filter(between(period, 2017, 2023)) %>% 
+  group_by(country, Scientific_Name, environment, ISO3_Code, fao_fishing_area, period) %>% 
   reframe(production = mean(value))
@@
 
-ggplot(prod, aes(x = country, y = production)) +
+ggplot(production, aes(x = country, y = production)) +
   geom_point() +
@@
 ```{r fix-misalignment}
-# filter country level production for all species in non-inland waters where production is greater than 0 tonnes.
-mariculture_prod_all <- aquaculture_raw %>% 
-  clean_names() %>% 
-  select(c(1:7, starts_with("x"))) %>% 
-  pivot_longer(names_to = "year", values_to = "production", cols= -c(1:7)) %>% 
-  mutate(year = gsub(pattern="x", replacement = "", year)) %>% 
-  filter(year %in% c(2017)) %>% 
-  filter(!grepl("Inland waters", fao_major_fishing_area_name)  & 
-            !asfis_species_name_3 %in% c("Clams, cockles, arkshells", 
-                                        "Abalones, winkles, conchs",
-                                        "Mussels", 
-                                        "Oysters",
-                                        "Shrimps, prawns",
-                                        "Crabs, sea-spiders",
-                                        "Freshwater molluscs",
-                                        "Squids, cuttlefishes, octopuses",
-                                        "Pearls, mother-of-pearl, shells",
-                                        "Miscellaneous aquatic plants",
-                                        "Scallops, pectens"),
-          !grepl("seaweeds" , asfis_species_name_3),
-          !grepl("molluscs|cucumber|invertebrates", asfis_species_name_2)) %>% 
-  group_by(country_name, asfis_species_name_2, asfis_species_name_3, fao_major_fishing_area_name, fao_major_fishing_area_code, year) %>% 
-  summarise(production = sum(production)) %>% 
-  ungroup() %>% 
-  mutate(iso3c = countrycode(sourcevar = country_name, origin = "country.name", destination = "iso3c", warn =TRUE)) %>% 
-  group_by(iso3c, country_name, year) %>% 
+mariculture_prod_all <- production %>% 
+  group_by(ISO3_Code, country, period) %>% 
   nest() %>% 
@@
   ungroup() %>% 
-  filter(production>0) %>% 
-  filter(!asfis_species_name_2 %in% c("Marine fishes nei")) %>% 
-  mutate(model_name = case_when(grepl("rouper", asfis_species_name_2) ~ "general_grouper", 
-                              asfis_species_name_2 %in% c("Coho(=Silver) salmon", "Rainbow trout") ~ "general_salmonid",
-                              TRUE ~ gsub(pattern = " ", replacement = "_", tolower(asfis_species_name_2)))) %>% 
-  relocate(model_name, .before = asfis_species_name_2) %>% 
-  mutate(farm_name = case_when(model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
-                                TRUE ~ "General marine fish")) %>% 
-  filter(asfis_species_name_2 %in% spp_names) %>% 
-  mutate(prop_production = production/national_production)
+  filter(drop_units(production) > 0) %>% 
+  mutate(
+    model_name = case_when(
+      grepl("Epinephelus|Mycteroperca|Serranidae", Scientific_Name) ~ "grouper", 
+      grepl("Oncorhynchus|Salmonidae", Scientific_Name) ~ "general_salmonid", 
+      grepl("Salmo salar", Scientific_Name) ~ "atlantic_salmon", 
+      grepl("Mytilus|Crassostrea|Ostreidae|Magallana", Scientific_Name) ~ "mussels_oysters",
+      grepl("Sparus", Scientific_Name) ~ "bream",       
+      grepl("Dicentrarchus", Scientific_Name) ~ "bass",       
+      grepl("Ulva|Saccharina|Eucheuma", Scientific_Name) ~ "general_seaweed",       
+      grepl("Acipenseridae", Scientific_Name) ~ "sturgeon",
+      grepl("Ariidae|Bagridae", Scientific_Name) ~ "catfish",
+      grepl("Astacidae|Cambaridae", Scientific_Name) ~ "crayfish",
+      grepl("Atherinidae", Scientific_Name) ~ "silversides",
+      grepl("Bothidae|Pleuronectidae", Scientific_Name) ~ "flounder",
+      grepl("Carangidae", Scientific_Name) ~ "jacks",
+      grepl("Cardiidae", Scientific_Name) ~ "cockles",
+      grepl("Characidae", Scientific_Name) ~ "tetras",
+      grepl("Cyprinidae", Scientific_Name) ~ "minnows",
+      grepl("Eleotridae", Scientific_Name) ~ "sleepers",
+      grepl("Ex Unionidae|Mytilidae", Scientific_Name) ~ "mussels",
+      grepl("Gerreidae", Scientific_Name) ~ "mojarras",
+      grepl("Gobiidae", Scientific_Name) ~ "gobies",
+      grepl("Lutjanidae", Scientific_Name) ~ "snappers",
+      grepl("Monacanthidae", Scientific_Name) ~ "filefish",
+      grepl("Mugilidae", Scientific_Name) ~ "mullets",
+      grepl("Octopodidae", Scientific_Name) ~ "octopus",
+      grepl("Palaemonidae|Penaeus", Scientific_Name) ~ "shrimp",
+      grepl("Palinuridae", Scientific_Name) ~ "lobsters",
+      grepl("Pectinidae", Scientific_Name) ~ "scallops",
+      grepl("Portunidae", Scientific_Name) ~ "crabs",
+      grepl("Sciaenidae", Scientific_Name) ~ "drums",
+      grepl("Scombridae", Scientific_Name) ~ "mackerels",
+      grepl("Scorpaenidae", Scientific_Name) ~ "rockfish",
+      grepl("Serranidae", Scientific_Name) ~ "groupers",
+      grepl("Soleidae", Scientific_Name) ~ "soles",
+      grepl("Sparidae", Scientific_Name) ~ "porgies",
+      grepl("Veneridae", Scientific_Name) ~ "clams",
+      TRUE ~ NA
+  )) %>% 
+  relocate(model_name, .before = Scientific_Name) %>% 
+  mutate(
+    farm_name = case_when(
+      model_name %in% c("atlantic_salmon", "general_salmonid") ~ "Salmonidae fish",
+      TRUE ~ "General marine fish"
+      ),
+      Scientific_Name = droplevels(Scientific_Name)
+    ) %>% 
+  # filter(is.na(model_name)) %>% 
+  mutate(prop_production = drop_units(production/national_production)) %>% 
+  arrange(prop_production)
+
+write.csv(mariculture_prod_all, "mariculture_production_all.csv")
 
@@
 
-```{r fix-misalignment}
+```{r fix-misalignment-orig}
 # filter country level production for all species in non-inland waters where production is greater than 0 tonnes.

### 2025-07-10 05_formulating_feeds.qmd
Proper index of files

@@
 
-here("00_model_functions.R") %>% source()
-here("00_dirs.R") %>% source()
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 
@@
 feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
-overwrite <- F
 ```

### 2025-07-10 06_run_atlantic_salmon_model.qmd
Proper index of files

@@
 conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)
+
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```

### 2025-07-10 index.qmd
Proper index of files

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
  freeze: auto
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
---

# Table of Contents

This project contains a comprehensive analysis of mariculture modelling from local to global scales. Below you'll find links to all the main documentation pages:

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data cleaning and preparation procedures |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | Temperature data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition analysis and formulation procedures |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model implementation and execution |
| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input patterns and their relative impacts |

# Data analysis

```{r setup}
#| include: false
#| eval: true
#| cache: false
#| message: false

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
# This markdown uses TinyTex - install with tinytex::install_tinytex()

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)

packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate", "worrms", "aquamapsdata") %>% sort()
```

```{r global-variables}
#| include: false

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")
install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")

# Filenames
farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
species_params_file <- file.path(output_species_data_path, "species_params.qs")
pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
sens_results_files <- file.path(output_sens_data_path) %>% 
    list.files(full.names = T) %>% 
    str_subset("results")

species_params <- qread(species_params_file)
pop_params <- qread(pop_params_file)

feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", "P" = "darkred", 
  "carbohydrates" = "steelblue", "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
)
```

### 2025-07-10 src/map_templates.R

@@ -1,0 +1,113 @@
+library(qs)
+library(dplyr)
+library(magrittr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(ggh4x)
+library(cowplot)
+library(sf)
+library(terra)
+library(rnaturalearth)
+library(rnaturalearthdata)
+library(rnaturalearthhires)
+
+# Define areas -------------------------------------------------
+# For drawing area boxes on the big map
+inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 47.75, 54.25),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-26, 30, 51, 72),
+  CHI = c(-77.5, -62.5, -56, -25),
+  AUS = c(144, 149.5, -44, -39.75)
+)
+
+# For the corresponding patchwork map lims
+inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
+  CAN1 = c(-132, -122, 48.5, 54),
+  CAN2 = c(-70, -54, 43, 48.5),
+  EUR = c(-23, 28.5, 52, 71),
+  CHI = c(-78, -62, -55.5, -27),
+  AUS = c(144, 149, -43.75, -40.75)
+) %>% 
+  map(function(bx) {
+    list(
+      xlims = bx[1:2],
+      ylims = bx[3:4],
+      labx = bx[1],
+      laby = bx[4]
+      )
+})
+
+labels_spec_robinson <- c(
+  CAN1 = "bottom_left_outside", 
+  CAN2 = "bottom_right_outside", 
+  EUR = "bottom_left_outside", 
+  CHI = "top_left_outside", 
+  AUS = "bottom_left_outside"
+)
+
+labels_offset_robinson <- c(
+  CAN1 = 1, 
+  CAN2 = 2, 
+  EUR = 1.75, 
+  CHI = 1.75, 
+  AUS = 3.5
+)
+
+labels_spec_mercator <- list(
+  CAN1 = c(h = -1, v = 0.5), 
+  CAN2 = c(h = 0.5, v = 0.5), 
+  EUR = c(h = -1, v = 0.5), 
+  CHI = c(h = 0, v = 0), 
+  AUS = c(h = 0, v = 0.5)
+)
+
+# The Robinson projection --------------------------------------
+worldmap_robinson <- ne_countries(scale = "medium", returnclass = "sf") %>% 
[…]

### 2025-07-10 src/model_functions.R

@@ -19,26 +19,6 @@ library(furrr)
 library(future)
 library(dplyr)
 
-make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
-fixnum <- function(n, digits = 4) {
-  vapply(n, function(x) {
-    str_flatten(c(rep("0", digits-nchar(as.character(x))), as.character(x)))
-  }, character(1))
-}
-meanna <- function(x, ...) mean(x, na.rm = TRUE, ...)
-minna <- function(x, ...) min(x, na.rm = TRUE, ...)
-maxna <- function(x, ...) max(x, na.rm = TRUE, ...)
-sdna <- function(x, ...) sd(x, na.rm = TRUE, ...)
-sumna <- function(x, ...) sum(x, na.rm = TRUE, ...)
-medianna <- function(x, ...) median(x, na.rm = TRUE, ...)
-find_read <- function(path, pattern){
-  file <- list.files(path, full.names = T, pattern = pattern)
-  if (length(file) > 1) {print("Multiple files found - try again")} else {
-    if (str_detect(file, ".qs")) {return(qs::qread(file))}
-    if (str_detect(file, ".parquet")) {return(arrow::read_parquet(file))}
-  }
-}
-
 # Parameters definitions
 # species_params['alpha']         [-] Feeding catabolism coefficient
 # species_params['epsprot']       [J/gprot] Energy content of protein
@@ -311,112 +291,6 @@ uni_farm_growth <- function(pop_params, species_params, feed_params, water_temp,
   }) %>% setNames(paste0(names(all_results2), "_stat"))
   
   return(out_list)
-}
-
-cite_pack <- function(package_name) {
-  version <- packageVersion(package_name)
-  paste0("package `", package_name, "`, version ", version, " [@", package_name, "]")
-}
-
-cite_packages <- function(packages) {
-  # Generate citations for each package
-  citations <- sapply(packages, function(pkg) {
-    version <- packageVersion(pkg)
-    paste0("`", pkg, "`, version ", version, " [@", pkg, "]")
-  })
-  
-  # Handle different cases based on number of packages
-  if (length(packages) == 1) {
-    return(paste0("package ", citations[1]))
-  } else if (length(packages) == 2) {
-    return(paste0("packages ", citations[1], " and ", citations[2]))
-  } else {
[…]

### 2025-07-10 src/other_functions.R

@@ -1,0 +1,139 @@
+make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
+fixnum <- function(n, digits = 4) {
+  vapply(n, function(x) {
+    str_flatten(c(rep("0", digits-nchar(as.character(x))), as.character(x)))
+  }, character(1))
+}
+meanna <- function(x, ...) mean(x, na.rm = TRUE, ...)
+minna <- function(x, ...) min(x, na.rm = TRUE, ...)
+maxna <- function(x, ...) max(x, na.rm = TRUE, ...)
+sdna <- function(x, ...) sd(x, na.rm = TRUE, ...)
+sumna <- function(x, ...) sum(x, na.rm = TRUE, ...)
+medianna <- function(x, ...) median(x, na.rm = TRUE, ...)
+find_read <- function(path, pattern){
+  file <- list.files(path, full.names = T, pattern = pattern)
+  if (length(file) > 1) {print("Multiple files found - try again")} else {
+    if (str_detect(file, ".qs")) {return(qs::qread(file))}
+    if (str_detect(file, ".parquet")) {return(arrow::read_parquet(file))}
+  }
+}
+
+cite_pack <- function(package_name) {
+  version <- packageVersion(package_name)
+  paste0("package `", package_name, "`, version ", version, " [@", package_name, "]")
+}
+
+cite_packages <- function(packages) {
+  # Generate citations for each package
+  citations <- sapply(packages, function(pkg) {
+    version <- packageVersion(pkg)
+    paste0("`", pkg, "`, version ", version, " [@", pkg, "]")
+  })
+  
+  # Handle different cases based on number of packages
+  if (length(packages) == 1) {
+    return(paste0("package ", citations[1]))
+  } else if (length(packages) == 2) {
+    return(paste0("packages ", citations[1], " and ", citations[2]))
+  } else {
+    # More than 2 packages: use commas and "and" before last
+    first_part <- paste(citations[-length(citations)], collapse = ", ")
+    last_part <- citations[length(citations)]
+    return(paste0("packages ", first_part, ", and ", last_part))
+  }
+}
+
+no_margins <- function() {
+  theme(legend.position = "none", 
+        plot.margin = margin(0, 0, 0, 0),
+        axis.title = element_blank())
+}
+
[…]

### 2025-07-22 05_formulating_feeds.qmd
Updates - new feed names

@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% purrr::walk(source)
 
 ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
-feed_input_file <- file.path(input_feed_profile_path, "all_feeds.csv")
+feed_input_file <- file.path(input_feed_profile_path, "all_feeds.xlsx")
 ```
@@
 feed_inputs <- feed_input_file %>% 
-  read.csv() %>% 
-  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "proportion"))) %>% 
+  read_excel(sheet = "testing") %>% 
+  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
   mutate(feed = as.factor(feed),

### 2025-07-22 06_run_atlantic_salmon_model.qmd
Updates - new feed names

@@
 ---
-title: "Individual Mariculture Modeling Analysis"
+title: "Run aquaculture model for Atlantic salmon"
 format: html
@@
 
-This document runs individual mariculture modeling analyses for Atlantic salmon farms.
+This document runs the aquaculture model for Atlantic salmon farms.
 It processes farm location data, species parameters, and conducts sensitivity analyses to understand the impact of various parameters on fish and farm growth measures.
 
-```{r setup}
+```{r}
+#| label: setup
 #| warning: false
@@
 library(magrittr)
+library(purrr)
 library(furrr)
@@
 
-```{r filenames}
+```{r}
+#| label: filenames
+
 # Set up parallel processing
@@
 
-```{r farm-coordinates}
+```{r}
+#| label: farm-coordinates
+
 times_N <- c("t_start" = 121, "t_end" = 121+547, "dt" = 1)
@@
 
-```{r farm-ts-data}
+```{r}
+#| label: farm-ts-data
+
 farms_to_omit <- qread(sprintf(file.path(input_farm_coords_path, "%s_farms_to_omit.qs"), this_species))
@@
 
-```{r species-parameters}
+```{r}
+#| label: species-parameters
+
 species_params <- readxl::read_excel(
@@
 
-```{r population-parameters}
+```{r}
+#| label: population-parameters
+
 pop_params <- readxl::read_excel(path = pop_params_excel["file"])
@@
 
-```{r farm-harvest-size}
+```{r}
+#| label: farm-harvest-size
+
 Sys.setenv(TAR_PROJECT = "project_farmruns")
 
+# Check that the feed will actually work
+targets::tar_make(test_reference_feed)
+targets::tar_load(test_reference_feed)
+
+# Get harvest sizes for all farms
 targets::tar_make(harvest_size)
 targets::tar_load(harvest_size)
-qsave(harvest_size, farm_harvest_file)
-
-mean(harvest_size$weight)
-min(harvest_size$weight)
-max(harvest_size$weight)
 
@@
   geom_histogram(fill = "salmon", alpha = 0.75, colour = "black")
+
+qsave(harvest_size, farm_harvest_file)
 ```
@@
 Run the sensitivity runs using the targets pipeline. 
-Note that this can take a long time (hours), as the species parameters (19) are run for each farm (2721) and factor (3) and the population parameters (6) are run for a smaller number of farms (271) and factor with a simulated population of 500 fish.
+Note that this can take a long time. 
+The species parameters (19) are run for a single fish in each farm (2721) and factor (3), which takes ~30 minutes.
+The population parameters (6) are run for a smaller number of farms (271) and each factor (3) with a simulated population of 500 fish, which takes ~30 hours.
 
-```{r sensitivity-run}
+```{r}
+#| label: sensitivity-run
+
 Sys.setenv(TAR_PROJECT = "project_sensitivities")
@@
 targets::tar_validate()
-targets::tar_visnetwork(targets_only = T)
-targets::tar_outdated()
+# targets::tar_visnetwork(targets_only = T)
+# targets::tar_outdated()
 targets::tar_make(
+  names = "sens_results_spec",
   seconds_meta_append = 120
@@
 
-```{r sensitivity-results}
+```{r}
+#| label: sensitivity-results
+
 targets::tar_load(sens_results_spec)
@@
 
-```{r run-farms-pipeline}
+Note that this also takes a long time - each branch of farmrun takes ~4.5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
+
+```{r}
+#| label: run-farms-pipeline
+
 Sys.setenv(TAR_PROJECT = "project_farmruns")
@@
 targets::tar_validate()
-targets::tar_visnetwork(targets_only = T)
-targets::tar_outdated()
-targets::tar_make(seconds_meta_append = 90)
+# targets::tar_visnetwork(targets_only = T)
+# targets::tar_outdated()
+targets::tar_make(farm_results, seconds_meta_append = 90)
+meta <- targets::tar_meta() %>% 
+  filter(grepl("farm_run", name))
+meta$seconds %>% mean()/60
 ```
 
-```{r farm-run-results}
+```{r}
+#| label: farm-run-results
+
 targets::tar_load(cohort_results)

### 2025-07-22 src/map_templates.R

@@ -11,6 +11,7 @@ library(terra)
 library(rnaturalearth)
 library(rnaturalearthdata)
 library(rnaturalearthhires)
+library(purrr)
 
 # Define areas -------------------------------------------------
 # For drawing area boxes on the big map

### 2025-07-22 targets/_targets_farmruns.R

@@ -4,11 +4,11 @@ library(crew)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble", "qs"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 15),
+  controller = crew_controller_local(workers = 10),
   workspace_on_error = TRUE
 )
 
-tar_source(files = c("00_model_functions.R", "00_dirs.R"))
+tar_source(files = list.files("src", pattern = "\\.R$", full.names = TRUE))
 
 list(
 # Get previously saved data ---------------------------------------------------------------------------------------
@@ -44,6 +44,39 @@ list(
     qs::qread(feed_params_file)[[feed_names]],
     pattern = feed_names
   ),
+  tar_target(
+    reference_feed,
+    qs::qread(feed_params_file)[["aas_2022"]]
+  ),
+
+  tar_target(
+    test_reference_feed,
+    command = {
+      fi <- sample(farm_IDs, 1)
+      farm_temp <- farm_ts_data %>%
+        filter(farm_ID == fi)
+      fg <- fish_growth(
+        pop_params = all_params,
+        species_params = all_params,
+        water_temp = farm_temp$temp_c,
+        feed_params = reference_feed,
+        times = c(t_start = min(farm_temp$day), t_end = max(farm_temp$day), dt = 1),
+        init_weight = all_params["meanW"],
+        ingmax = all_params["meanImax"]
+      )
+      fg %>%
+        as.data.frame() %>%
+        filter(!is.na(weight)) %>% 
+        slice_tail(n = 1) %>%
+        select(weight) %>%
+        mutate(
+          farm_ID = fi,
+          weight = weight %>% 
+            units::set_units("g") %>% 
+            units::drop_units()
+        )
+    }
+  ),
 
   tar_target(all_params, c(qs::qread(species_params_file), qs::qread(pop_params_file))),
 
@@ -57,7 +90,7 @@ list(
         pop_params = all_params,
         species_params = all_params,
         water_temp = farm_temp$temp_c,
-        feed_params = feed_params[["plant_dominant"]],
+        feed_params = reference_feed,
         times = c(t_start = min(farm_temp$day), t_end = max(farm_temp$day), dt = 1),
         init_weight = all_params["meanW"],
[…]

### 2025-07-22 targets/_targets_sensitivities.R

@@ -9,10 +9,7 @@ tar_option_set(
   workspace_on_error = TRUE
 )
 
-tar_source(c(
-  "00_dirs.R",
-  "00_model_functions.R"
-))
+tar_source(files = list.files("src", pattern = "\\.R$", full.names = TRUE))
 
 list(
   # Load previously saved data --------------------------------------------------------------------------------
@@ -45,7 +42,7 @@ list(
   ),
   tar_target(
     reference_feed,
-    qs::qread(feed_params_file)[["plant_dominant"]]
+    qs::qread(feed_params_file)[["aas_2022"]]
   ),
 
   # Get names of params to be adjusted

### 2025-07-23 05_formulating_feeds.qmd
Check for full feeds

@@
 
-There is no check or correction here to ensure that ingredient proportions = 1 in the incoming data. This was checked manually prior to import.
-
 ``` {r import-feeds}
@@
 feed_inputs <- feed_input_file %>% 
-  read_excel(sheet = "testing") %>% 
+  read_excel(sheet = "all_feeds") %>% 
   pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
@@
 feed_types <- levels(feed_inputs$feed)
+```
+
+Check that ingredient proportions sum to 1.
+
+```{r check-proportions}
+#| code-summary: Composition proportions
+
+feed_inputs <- feed_inputs %>% 
+  filter(!is.na(proportion) & proportion != 0) %>% 
+  group_by(feed) %>% 
+  mutate(
+    sum = sum(proportion),
+    proportion = proportion/sum
+  ) %>% 
+    ungroup()
 ```
@@
   df <- feed_inputs %>% 
-    filter(feed == ft & proportion != 0) 
+    filter(feed == ft) 
   list(

### 2025-07-23 06_run_atlantic_salmon_model.qmd
Check for full feeds

@@
 targets::tar_load(test_reference_feed)
+test_reference_feed # should be ~1430 g
 
 # Get harvest sizes for all farms
-targets::tar_make(harvest_size)
+targets::tar_make(names = c("harvest_size", "feed_params"))
 targets::tar_load(harvest_size)

### 2025-07-23 targets/_targets_farmruns.R

@@ -37,7 +37,11 @@ list(
   ),
   tar_target(
     feed_names,
-    qs::qread(feed_params_file) %>% names()
+    command = {
+      qs::qread(feed_params_file) %>% names()
+      # c("plant_dominant", "marine_dominant")
+    }
+    
   ),
   tar_target(
     feed_params,
@@ -46,7 +50,7 @@ list(
   ),
   tar_target(
     reference_feed,
-    qs::qread(feed_params_file)[["aas_2022"]]
+    qs::qread(feed_params_file)[["plant_dominant"]]
   ),
 
   tar_target(

### 2025-07-23 index.qmd
Dirs fix

@@
 # Filenames
-farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
-species_params_file <- file.path(output_species_data_path, "species_params.qs")
-pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
-feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
-sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
-sens_results_files <- file.path(output_sens_data_path) %>% 
-    list.files(full.names = T) %>% 
-    str_subset("results")
+# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
+# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
 
-species_params <- qread(species_params_file)
-pop_params <- qread(pop_params_file)
+species_params <- find_read(output_species_data_path, "species_params")
+pop_params <- find_read(output_species_data_path, "pop_params")
 
@@
   "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
+
+# Model functioning
+
+## Population and biomass
+
+```{r raw biomass and weight data}
+weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
+biomass_cohort <- find_read(output_model_cohort_path, "biomass_stat_all_farms")
+```
 )

### 2025-07-23 12_data_analysis.R

@@ -25,11 +25,11 @@ conflicts_prefer(dplyr::select(), dplyr::filter(), .quiet = T)
 source("00_model_functions.R")
 source("00_dirs.R")
 
-cohort_comp_fnms <- output_cohorts_data_path %>% 
+cohort_comp_fnms <- per_biomass_cohort_path %>% 
   list.files(full.names = T) %>% 
   str_subset("farmrun_comparisons")
 
-aggregate_comparison_files <- output_cohorts_data_path %>% 
+aggregate_comparison_files <- per_biomass_cohort_path %>% 
   list.files(full.names = T) %>% 
   str_subset("allfarms_comparisons")
 

### 2025-07-23 06_run_atlantic_salmon_model.qmd
Farm outputs processing

@@
 targets::tar_make(
-  names = "sens_results_spec",
   seconds_meta_append = 120
@@
 
-Note that this also takes a long time - each branch of farmrun takes ~4.5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
+Note that this takes a long time - each branch of farmrun takes ~5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
 
@@
 # targets::tar_outdated()
-targets::tar_make(farm_results, seconds_meta_append = 90)
+targets::tar_prune()
+
+targets::tar_make(seconds_meta_append = 90)
+
 meta <- targets::tar_meta() %>% 
   filter(grepl("farm_run", name))
-meta$seconds %>% mean()/60
+meta$seconds %>% mean()/60 # minutes per target
 ```
@@
 ```{r}
-#| label: farm-run-results
+#| label: all-farms-cohorts-results
 
+targets::tar_load(stat_names)
+targets::tar_load(farm_results)
 targets::tar_load(cohort_results)
+
+purrr::map(stat_names, function(stat_name) {
+  farm_results %>% 
+    filter(measure == stat_name) %>% 
+    qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
+
+  cohort_results %>% 
+    filter(measure == stat_name) %>% 
+    qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
+})
+
+rm(farm_results, cohort_results)
 ```
+
+```{r}
+#| label: per-biomass-ouputs
+
+farm_fnms <- list.files(output_model_farm_path, full.names = T)
+cohort_fnms <- list.files(output_model_cohort_path, full.names = T)
+
+farm_bioms <- farm_fnms %>% 
+  str_subset("biomass") %>% 
+  qs::qread() %>% 
+  distinct(farm_ID, feed, t, mean, sd)
+cohort_bioms <- cohort_fnms %>% 
+  str_subset("biomass") %>% 
+  qs::qread() %>% 
+  distinct(farm_ID, feed, t, mean, sd)
+
+stat_names <- stat_names[!stat_names %in% c("biomass_stat", "weight_stat", "dw_stat", "water_temp_stat", "T_response_stat", "rel_feeding_stat")]
+
+purrr::map(stat_names, function(stat_name) {
+  farm_fnms %>% 
+    str_subset(stat_name) %>% 
+    qs::qread() %>% 
+    merge(farm_bioms, by = c("farm_ID", "feed", "t")) %>% 
+    rename(
+      mean = mean.x,
+      sd = sd.x,
+      biom_mean = mean.y,
+      biom_sd = sd.y
+    ) %>% 
+    mutate(
+      biom_sd_mean = biom_sd/biom_mean,
+      mean_perbiom = mean/biom_mean,
+      sd_perbiom = (sd_mean+biom_sd_mean) * mean_perbiom
+    ) %>% 
+      qs::qsave(file.path(per_biomass_farm_path, str_c(stat_name, "_all_farms.qs")))
+
+  cohort_fnms %>% 
+    str_subset(stat_name) %>% 
+    qs::qread() %>% 
+    merge(cohort_bioms, by = c("farm_ID", "feed", "t")) %>% 
+    rename(
+      mean = mean.x,
+      sd = sd.x,
+      biom_mean = mean.y,
+      biom_sd = sd.y
+    ) %>% 
+    mutate(
+      biom_sd_mean = biom_sd/biom_mean,
+      mean_perbiom = mean/biom_mean,
+      sd_perbiom = (sd_mean+biom_sd_mean) * mean_perbiom
+    ) %>% 
+      qs::qsave(file.path(per_biomass_cohort_path, str_c(stat_name, "_all_farms.qs")))
+})
+```

### 2025-07-23 index.qmd
Farm outputs processing

@@
 #| include: false
+#| cache: false
 
@@
 
-feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
+feed_pal <- c(
+  "past" = "#E41A1C", 
+  "reference" = "#377EB8", 
+  "future" = "#4DAF4A",
+  "plant_dominant" = "#4DAF4A",
+  "marine_dominant" = "#377EB8",
+  "novel_inclusive" = "#E41A1C"
+)
 cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
 macro_pal <- c(
-  "protein" = "darkred", "P" = "darkred", 
-  "carbohydrates" = "steelblue", "C" = "steelblue", 
-  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
+  "protein" = "darkred", 
+  "P" = "darkred", 
+  "carbohydrates" = "steelblue", 
+  "C" = "steelblue", 
+  "lipids" = "darkgoldenrod1", 
+  "L" = "darkgoldenrod1"
+)
+
+prettyplot <- function() {
+  theme_classic() +
+    theme(
+      text = element_text(family = "sans", size = 12, colour = "black"),
+      legend.position = "none"
+    )
+}
+```
 
@@
 ```
+
+Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed, @fig-harvest-size).
+A population timeseries was then generated using the standard mortality rate (`r round(unname(pop_params['mortmyt'])*100, 3)` % d$^{-1}$).
+
+```{r}
+#| label: fig-harvest-size
+#| fig-cap: |
+#|   Frequency distribution of harvest sizes used to create the population timeseries for each farm, as predicted by the fish-growth model.
+
+harv_size <- find_read(output_farm_data_path, "farm_harvest_size")
+
+harv_size %>% 
+  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
+  select(c(farm_ID, weight)) %>% 
+  ggplot(aes(x = weight)) +
+  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
+  scale_y_continuous(limits = c(0,500)) +
+  labs(y = "Frequency", x = "Harvest weight") +
+  prettyplot() +
+  theme(aspect.ratio = 0.75)
+```
+
+Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.
+
+```{r}
+#| label: fig-cohorts
+#| eval: false
+#| fig-cap: | 
+#|   Example of how the overlapping cohorts combine into a single farm production curve (in this case biomass).
+The left plot shows the farm biomass produced by each cohort from initialisation to harvest, while the right plot shows the combined farm biomass over the course of a single production period of 548 days.
+
+fnms <- output_growth_data_path %>% 
+  list.files(full.names = T) %>% 
+  str_subset("reference")
+
+df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
+  as.data.frame() %>% 
+  mutate(mean = set_units(mean, "g") %>% set_units("t"),
+         sd = set_units(sd, "g") %>% set_units("t")) %>% 
+  select(-farm_ID)
+
+df <- rbind(
+  df %>% mutate(cohort = 1),
+  df %>% mutate(t = t+365, cohort = 2),
+  df %>% mutate(t = t+730, cohort = 3)
+) %>% 
+  mutate(t = (t-min(t))+1,
+         split = "Split by cohort")
+
+min_t <- min(df$t[df$cohort == 2])
+max_t <- max(df$t[df$cohort == 2])
+
+df_2 <- df %>% 
+  filter(t %in% min_t:max_t) %>% 
+  mutate(sd = sd/mean) %>% 
+  group_by(t) %>% 
+  reframe(sd = sqrt(sum(sd^2)),
+          mean = sum(mean),
+          sd = sd*mean) %>% 
+  mutate(cohort = "all",
+         split = "Totalled")
+
+df <- rbind(df, df_2) %>% 
+  mutate(cohort = as.factor(cohort))
+
+ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+  geom_line(linewidth = 0.75) +
+  geom_ribbon(linetype = "dotted", alpha = 0) +
+  facet_grid(cols = vars(split)) +
+  scale_x_continuous(breaks = seq(0, 1600, 120)) +
+  scale_colour_manual(values = cohort_pal) +
+  prettyplot() +
+  labs(y = "Farm biomass", x = "Day of production")
+```
+
+```{r}
+#| label: pop-biom-data
+
+biomass_farm <- find_read(output_model_farm_path, "biomass_stat") %>% 
+  group_by(farm_ID, feed) %>% 
+  slice_max(t) %>% 
+  ungroup()
+
+production <- find_read(output_farm_data_path, "farm_static_data") %>% 
+  merge(biomass_farm, by = "farm_ID", all.x = F) %>% 
+  mutate(
+    mean = set_units(mean, "g"),
+    diff = set_units(mean - tonnes_per_farm, "t"),
+    perc_diff = diff/tonnes_per_farm
+  ) %>% 
+  group_by(country, feed) %>% 
+  reframe(
+    min_percdiff = min(perc_diff),
+    max_percdiff = max(perc_diff),
+    mean_percdiff = mean(perc_diff)
   )
 ```
+
+By this method, farm biomass as predicted by the model predicted farm tonnage relatively accurately.
+Predicted farm biomass was within `r round(100*min(production$min_percdiff),1)`% -- `r round(100*max(production$max_percdiff),1)`% of tonnage produced.
+
+## Feed provision and feeding response to temperature {#sec-model-feeding}
+
+# Modelled experimental feeds {#sec-feeds}
+
+# Model sensitivity to parameter changes {#param-sensitivity}
+
+Parameter sensitivity was tested by varying each parameter by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
+All parameters in Table @tbl-params were tested.
+The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.
+
+```{r salmon-param-names}
+#| code-summary: Get parameter and sensitivity data
+
+params <- file.path(output_species_data_path, "sens_params.qs") %>% qs::qread()
+
+param_names <- tibble::tribble(
+  ~name,        ~lab,
+  "alpha",      bquote(alpha),
+  "epsprot",    bquote(epsilon["P"]),
+  "epslip",     bquote(epsilon["L"]),
+  "epscarb",    bquote(epsilon["C"]),
+  "epsO2",      bquote(epsilon["O"[2]]),
+  "pk",         bquote("pk"),
+  "k0",         bquote("k"[0]),
+  "m",          bquote("m"),
+  "n",          bquote("n"),
+  "betac",      bquote(beta*"C"),
+  "Tma",        bquote("T"["max"]),
+  "Toa",        bquote("T"["opt"]),
+  "Taa",        bquote("T"["min"]),
+  "omega",      bquote(omega),
+  "a",          bquote("a"),
+  "k",          bquote("k"),
+  "eff",        bquote("eff"),
+  "meanW",      bquote(bar("W")),
+  "deltaW",     bquote(Delta*"W"), 
+  "meanImax",   bquote(bar("I"["max"])),
+  "deltaImax",  bquote(Delta*"I"["max"]),
+  "overFmean",  bquote(bar("F")),
+  "overFdelta", bquote(Delta*"F"),
+  "mortmyt",    bquote("mort")
+)
+```
+
+```{r}
+#| label: sens-results
+
+sens_results_files <- file.path(output_sens_data_path) %>% 
+  list.files(full.names = T) %>% 
+  str_subset("results")
+```
+
+# Inputs {#inputs}
+
+```{r}
+#| label: farm-geometry
+
+farm_geometry <- find_read(output_farm_data_path, "farm_geometry")
+```
+
+```{r}
+#| label: input-data
+
+ins_P <- list.files(per_biomass_cohort_path, full.names = T) %>% 
+  str_subset("P_uneat|P_excr") %>% 
+  purrr::map(function(nm) {qs::qread(nm)}) %>% 
+  bind_rows()
+
+ins_tot <- list.files(per_biomass_cohort_path, full.names = T) %>% 
+  str_subset("total_uneat|total_excr") %>% 
+  purrr::map(function(nm) {qs::qread(nm)}) %>% 
+  bind_rows()
+```
+
+## Total inputs (uneaten and excreted)
+
+### Through time
+
+```{r}
+#| label: fig-uneat-excr-plot-ts
+#| fig-cap: Initial look at excreted and uneaten through time
+
+ins_tot %>% 
+  mutate(t = t-365) %>% 
+  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
+  group_by(country, feed, t, measure) %>% 
+  reframe(
+    sd_perbiom = sd(mean_perbiom),
+    mean_perbiom = mean(mean_perbiom)
+    ) %>% 
+  mutate(
+    mean_perbiom = mean_perbiom %>% 
+      set_units("g g_fish-1") %>% 
+      set_units("kg t_fish-1"),
+    sd_perbiom = sd_perbiom %>% 
+      set_units("g g_fish-1") %>% 
+      set_units("kg t_fish-1")
+  ) %>% 
+  ggplot(aes(
+    x = t, 
+    y = drop_units(mean_perbiom), 
+    ymin = drop_units(mean_perbiom-sd_perbiom), 
+    ymax = drop_units(mean_perbiom+sd_perbiom), 
+    colour = feed, 
+    fill = feed
+  )) +
+  geom_line() +
+  geom_ribbon(alpha = 0.25) +
+  facet_grid(
+    rows = vars(country),
+    cols = vars(measure),
+    scales = "free"
+  ) +
+  prettyplot() +
+  scale_colour_manual(values = feed_pal) +
+  scale_fill_manual(values = feed_pal) +
+  scale_y_continuous(
+    name = expression("Loss (kg g"^-1*")"),
+    breaks = seq(0, 1, 0.2)
+  )
+```
+
+```{r}
+#| label: uneat-excr-plot-perc-diff
+
+tmp <- ins_tot %>% 
+  mutate(t = t-365) %>% 
+  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
+  dplyr::select(-c(mean, sd_mean, sd, biom_mean, biom_sd, biom_sd_mean, sd_perbiom)) %>% 
+  group_by(country, t, measure) %>% 
+  pivot_wider(
+    names_from = feed, 
+    values_from = mean_perbiom
+  ) %>% 
+  mutate(
+    diff = plant_dominant - marine_dominant,
+    perc_diff = diff/plant_dominant
+  ) %>%
+  group_by(country, t, measure) %>% 
+  reframe(
+    mean_diff = mean(diff),
+    mean_perc_diff = mean(perc_diff),
+    sd_diff = sd(diff),
+    sd_perc_diff = sd(perc_diff)
+  )
+
+tmp <- tmp %>% 
+  group_by(measure, country) %>% 
+  reframe(
+    mean_t_perc_diff = mean(mean_perc_diff),
+    sd_t_perc_diff = sd(mean_perc_diff)
+    )
+```
+
+While the actual difference in excreted and uneaten feed (total loss) varied between countries and through time (@fig-uneat-excr-plot-ts), relative changes between the feeds remained consistent. 
+In both the US and Australia (all done so far), total excreted faeces was 
+`r round(100*tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`%) higher in the plant-dominant feed.
+Differences in total uneaten feed were much smaller at 
+`r round(100*-tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`%) lower in the plant-dominant feed.
+
+### At harvest
+
+```{r}
+#| label: uneat-excr-plot-end
+#| fig-cap: Caption
+
+ins_tot %>% 
+  group_by(farm_ID) %>%
+  arrange(farm_ID, t) %>%
+  mutate(
+    cumsum_mean = cumsum(mean_perbiom) %>% 
+      set_units("g g_fish-1") %>% 
+      set_units("kg t_fish-1"),
+    end_t = max(t)
+    ) %>% 
+  ungroup() %>% 
+  filter(t == end_t) %>% 
+  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
+  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
+  geom_boxplot() +
+  facet_grid(cols = vars(measure)) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal)
+```
+
+## N inputs
+
+```{r}
+#| label: N-loss-plot-total
+#| fig-cap: Caption
+
+ins_P %>% 
+  group_by(farm_ID) %>%
+  arrange(farm_ID, t) %>%
+  mutate(
+    cumsum_mean = cumsum(mean_perbiom)*6.25 %>% 
+      set_units("g g_fish-1") %>% 
+      set_units("kg t_fish-1"),
+    end_t = max(t)
+    ) %>% 
+  ungroup() %>% 
+  filter(t == end_t) %>% 
+  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
+  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
+  geom_boxplot() +
+  facet_grid(cols = vars(measure)) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal)
+```
+
+# Code and packages used
+
+All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+Major packages used include `r cite_packages(packages)`.
+
+For a full list of R packages used see the lockfile on [Github](https://www.github.com).
+This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

### 2025-07-23 manuscript.qmd
Docs fixup and render

@@
 
-This document was last updated at `r format(Sys.time(), "%H:%M")` on `r format(Sys.time(), "%d %b, %Y")`.
-
 # Methods
@@
 
-worldmap <- ne_countries(scale = "medium", returnclass = "sf") %>% st_transform(crs = "+proj=robin")
-graticules <- st_graticule(worldmap, lon = seq(-180, 180, 30), lat = seq(-90, 90, 30))
-
-inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
-  CAN1 = c(-132, -122, 47.75, 54.25),
-  CAN2 = c(-70, -54, 43, 48.5),
-  EUR = c(-26, 30, 51, 72),
-  CHI = c(-77.5, -62.5, -56, -25),
-  AUS = c(144, 149.5, -44, -39.75)
+farm_temp_robinson <- st_sf(farm_temp_means) %>% 
+  st_transform(crs = "+proj=robin")
+
+p_bigmap_robinson +
+  geom_sf(data = farm_temp_robinson, aes(color = mean_temp), size = 1) +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 25, barheight = 1.5
+  ))
+
+p2 <- farm_temp_means %>% 
+  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
+  geom_point(size = 2) +
+  scale_colour_brewer(palette = "Set1") +
+  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
+  prettyplot() +
+  theme(legend.position = "top", legend.title = element_blank())
+
+p3 <- farm_temp_means %>% 
+  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
+  ggplot(aes(x = mean_temp, fill = hemisphere)) +
+  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
+  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
+  prettyplot() +
+  theme(legend.position = "top", legend.title = element_blank())
+
+(p2 + p3) / p_big_map + plot_layout(heights = c(1, 1.5))
+```
+
+```{r patchwork-map-mercator}
+#| fig-cap: |
+#|   Example of a patchwork
+#| fig-height: 9
+#| fig-width: 9.5
+
+p_bigmap_temperature <- p_bigmap_mercator +
+  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 2) +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Mean temperature (°C)",
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 1.5, barheight = 20
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+p_insets <- get_insets_mercator(p_bigmap_temperature)
+
+grid_1 <- cowplot::plot_grid(
+  p_insets[["CAN1"]], p_insets[["CAN2"]], 
+  ncol = 2, rel_widths =  c(1, 1.35)
   )
-labels_spec <- c(CAN1 = "bottom_left_outside", CAN2 = "bottom_right_outside", EUR = "bottom_left_outside", CHI = "top_left_outside", AUS = "bottom_left_outside")
-labels_offset <- c(CAN1 = 1, CAN2 = 2, EUR = 1.75, CHI = 1.75, AUS = 3.5)
-
-box_data <- create_boxes(box_list = inset_boxes, # see function create_boxes above
-                         label_positions = unname(labels_spec),
-                         offset_deg = unname(labels_offset))
-boxes_robinson <- st_transform(box_data$boxes, crs = "+proj=robin")
-labels_robinson <- st_transform(box_data$labels, crs = "+proj=robin")
-farm_temp_robinson <- st_sf(farm_temp_means) %>% st_transform(crs = "+proj=robin")
-
-p_big_map <- ggplot() +
+grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
+grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
+
+cowplot::plot_grid(
+  grid_1, grid_3,
+  nrow = 2,
+  rel_heights = c(1, 1.5)        # relative row heights
+)
+```
+
+## Modelled experimental feeds {#sec-feeds}
+
+```{r feeds}
+feed_params <- file.path(output_species_data_path, "feed_params.qs") %>%
+  qs::qread()
+
+feed_summary <- map_dfr(names(feed_params), function(feed) {
+  df <- feed_params[[feed]]
+  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
+    contrib <- df[[macro]]$proportion * df[[macro]]$macro
+    total <- sum(contrib)
+    digest <- sum(df[[macro]]$digest * contrib) / total
+        tibble(
+      feed = feed,
+      macro = macro,
+      total = total,
+      digest = digest
+    )
+  })
+}) %>%
+  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
+         feed = factor(feed, levels = c("reference", "past", "future")),
+         total_r = total * 100 %>% round(1),
+         digest_r = digest * 100 %>% round(1))
+```
+
+The reference feed was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "reference", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "reference", macro == "C")$total, 1)`% carbohydrate, the past feed was 
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "past", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "past", macro == "C")$total, 1)`% carbohydrate, and the future feed was 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$total, 1)`% protein, 
+`r round(100*filter(feed_summary, feed == "future", macro == "L")$total, 1)`% lipid, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "C")$total, 1)`% carbohydrate.
+
+Ingredients are tracked seperately through the model with their own digestibility coefficients. 
+Overall, protein digestibility was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`%,
+`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`%, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% and carbohydrate digestibility was 
+`r round(100*filter(feed_summary, feed == "reference", macro == "C")$digest, 1)`%,
+`r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`%, and 
+`r round(100*filter(feed_summary, feed == "future", macro == "C")$digest, 1)`%
+within the reference, past, and future feeds respectively. 
+The digestibility of lipids was assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`%.
+
+```{r fig-feed-summary-ideas}
+#| fig-height: 7.5
+#| fig-cap: | 
+#|   Ideas for how to present the differences between feeds.
+Top plot shows the protein (red), lipids (yellow) and carbohydrate (blue) composition, with the digestible portion shown darker and the undigestible portion shown lighter.
+Bottom plot shows the proportion of each feed composed of each types of ingredient.
+
+p1 <- feed_summary %>%
+  mutate(digest_total = digest * total) %>% 
+  ggplot(aes(x = feed, y = total, fill = macro)) +
+  geom_col(position = "dodge", alpha = 0.55, colour = "black") +
+  geom_col(mapping = aes(y = digest_total), position = "dodge", alpha = 1, colour = "black") +
+  scale_fill_manual(values = macro_pal) +
+  scale_y_continuous(breaks = seq(0,0.5,0.1), labels = seq(0,50,10)) +
+  scale_x_discrete(labels = c("reference" = "Reference", "past" = "Past", "future" = "Future")) +
+  labs(x = "Feed", y = "Proportion (%)") +
+  prettyplot()
+
+feed_ings <- rbind(
+  feed_params[[1]][[1]] %>% mutate(feed = as.factor("reference")), 
+  feed_params[[2]][[1]] %>% mutate(feed = as.factor("past")), 
+  feed_params[[3]][[1]] %>% mutate(feed = as.factor("future"))
+) %>%
+  rename(protein = macro) %>%
+  mutate(
+    category = case_when(
+      str_detect(ingredient, "fish-oil") ~ "fish",
+      str_detect(ingredient, "fishmeal") ~ "fish",
+      str_detect(ingredient, "krill") ~ "other-marine",
+      str_detect(ingredient, "soy") ~ "legume",
+      str_detect(ingredient, "pea") ~ "legume",
+      str_detect(ingredient, "guar") ~ "legume",
+      str_detect(ingredient, "faba") ~ "legume",
+      str_detect(ingredient, "corn") ~ "wheat-corn",
+      str_detect(ingredient, "wheat") ~ "wheat-corn",
+      str_detect(ingredient, "chicken") ~ "chicken",
+      str_detect(ingredient, "bacteri") ~ "bact-fungi-micro",
+      str_detect(ingredient, "yeast") ~ "bact-fungi-micro",
+      str_detect(ingredient, "spirulina") ~ "bact-fungi-micro",
+      str_detect(ingredient, "bsf") ~ "insect",
+      T ~ "other-plant"
+    ) %>% 
+      factor(levels = c("fish", "other-marine", "chicken", "wheat-corn", "legume", "other-plant", "insect", "bact-fungi-micro"))
+  )
+
+p_ings <- feed_ings %>% 
+  mutate(feed = factor(feed, levels = c("reference", "past", "future"), labels = c("Reference", "Past", "Future"))) %>% 
+  group_by(feed, category) %>%
+  reframe(proportion = sum(proportion)) %>% 
+  ggplot(aes(x = "", y = proportion, fill = category)) +
+  geom_col(width = 1, colour = "black") +
+  coord_polar("y", start = 0) +
+  scale_fill_manual(
+    name = "Ingredient category",
+    values = c("fish" = "royalblue3", "other-marine" = "turquoise2", "chicken" = "hotpink1", "wheat-corn" = "moccasin", "legume" = "forestgreen", "other-plant" = "darkolivegreen1", "insect" = "firebrick3", "bact-fungi-micro" = "darkorange"),
+    labels = c("Fish meal or oil", "Other marine ingredients", "Chicken", "Wheat and corn", "Legumes", "Other plant ingredients", "Insects", "Bacteria, fungi or microalgae")) +
+  facet_grid(cols = vars(feed)) +
+  theme_void() +
+  theme(
+    text = element_text(family = "serif", size = 12, colour = "black"),
+    legend.position = "bottom",
+    legend.title = element_blank(), 
+    strip.text = element_blank(),
+    strip.text.x = element_text(size = 14)
+  )
+
+plot_grid(p1, p_ings, nrow = 2)
+```
+
+## Impacts of nutrient input
+
+General thoughts is that a risk-assessment approach is most compelling:
+
+* Hazard: Nutrient input. Present as a change between feeds (%?), relative to background levels (ratio?)
+  * Possibly ask Camille how the quotas for Tasmanian salmon are calculated
+  * Background levels are from [oceanhealthindex.org](https://knb.ecoinformatics.org/view/resource_map_doi:10.5063/F1610XPS) - double-check that it includes wastewater input AND agriculture - should include both - if they're not combined ask Ben because he has them combined somewhere
+  * If this is too uncertain perhaps combine into categorical (oligotrophic/eutrophic) classification?
+* Exposure: Species presence. Use IUCN/Aquamap data to estimate the % of each species range is occupied by farms
+  * give each farm a 1km radius, check for overlaps
+  * Gage already has the data to process the Aquamap data
+* Vulnerability: species vulnerability to eutrophication + nutrient input [@butt_trait-based_2022; @ohara_code_2021]. Possibly also use IUCN threat levels for prioritisation?
+
+# Results
+
+* Parameter sensitivity results are in supplementary @sec-parameter-sensitivity
+
+In general, data outputs comes in the following dimensions:
+
+* Location -> temperature -> farm_ID
+* Uneaten feed + excreted faeces = total inputs (g)
+* Day of production (impacted by location)
+* Main point is the difference between feeds (kg/t salmon).
+* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)
+
+## Uneaten feed and faeces
+
+```{r inputs data}
+#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)
+
+mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
+mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
+N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
+N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
+```
+
+```{r inputs stats through time}
+#| eval: false
+#| code-summary: Show how inputs (mass and N) change through time (across all farms)
+
+mass_inputs_ts
+N_inputs_ts
+
+# Through time
+inputs_stats_ts <- inputs_df %>%
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_ts <- inputs_rel_df %>% 
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+# Total (at production end)
+inputs_stats_end <- inputs_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end_diff <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(future = (future-reference)/reference,
+         past = (past-reference)/reference) %>% 
+  select(-reference) %>% 
+  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
+  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(diff),
+          max = maxna(diff),
+          sd = sdna(diff),
+          mean = meanna(diff))
+
+# Pull key values (uneaten feed)
+u_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
+u_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
+u_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
+u_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
+u_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
+u_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
+u_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
+u_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
+u_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)
+
+# Convert past and future values to % change values
+u_stmin2 <- (100*u_stmin2) %>% round(2)
+u_stmax2 <- (100*u_stmax2) %>% round(2)
+u_stmean2 <- (100*u_stmean2) %>% round(2)
+u_stmin3 <- (100*u_stmin3) %>% round(2)
+u_stmax3 <- (100*u_stmax3) %>% round(2)
+u_stmean3 <- (100*u_stmean3) %>% round(2)
+
+u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+
+# Pull key values (excreted faeces)
+e_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(min)
+e_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(max)
+e_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(mean)
+e_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(min)
+e_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(max)
+e_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(mean)
+e_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(min)
+e_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(max)
+e_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(mean)
+
+# Convert past and future values to % change values
+e_stmin2 <- (100*e_stmin2) %>% round(2)
+e_stmax2 <- (100*e_stmax2) %>% round(2)
+e_stmean2 <- (100*e_stmean2) %>% round(2)
+e_stmin3 <- (100*e_stmin3) %>% round(2)
+e_stmax3 <- (100*e_stmax3) %>% round(2)
+e_stmean3 <- (100*e_stmean3) %>% round(2)
+
+e_stmin1 <- e_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmax1 <- e_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmean1 <- e_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+```
+
+```{r waste inputs stats total}
+#| code-summary: Show how waste inputs change in total (at the end of a production period) across all farms
+
+mass_inputs_sep <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          mean_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass))
+
+twi_min <- mass_inputs_sep$min_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_max <- mass_inputs_sep$max_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_mean <- mass_inputs_sep$mean_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+
+# There were only very small differences in total uneaten feed between the different feeds, with the past feed increasing uneaten feed by `r u_stmin2`-`r u_stmax2`%  (mean of `r u_stmean2`%) and the future feed increasing uneaten feed by `r u_stmin3`-`r u_stmax3`%  (mean of `r u_stmean3`%).
+
+# * Total excreted faeces across a cohort fed the reference feed ranged from `r e_stmin1` to `r e_stmax1` g kg$^{-1}$ fish, with a mean of `r e_stmean1` g kg$^{-1}$ fish. 
+# * Past feed decreased excreted faeces by `r -1*e_stmin2`-`r -1*e_stmax2`%  (mean of `r -1*e_stmean2`%) 
+# * Future feed increased excreted faeces by `r e_stmin3`-`r e_stmax3`%  (mean of `r e_stmean3`%)
+```
+
+* Total waste inputs across a single production period of fish fed the reference feed ranged from `r twi_min[1]` to `r twi_max[1]` g kg$^{-1}$ fish, with a mean of `r twi_mean[1]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the past feed ranged from `r twi_min[2]` to `r twi_max[2]` g kg$^{-1}$ fish, with a mean of `r twi_mean[2]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the future feed ranged from `r twi_min[3]` to `r twi_max[3]` g kg$^{-1}$ fish, with a mean of `r twi_mean[3]` g kg$^{-1}$ fish.
+
+```{r fig-waste-inputs-total}
+#| fig-cap: | 
+#|   Total waste intputs (uneaten feed + excreted faeces) across the whole production period at each farm location.
+#| fig-width: 9.5
+
+mass_inputs_sep_geometry <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(farm_ID, feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          sd_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass)) %>% 
+  merge(farms_geometry, by = "farm_ID")
+
+mass_inputs_robinson <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units()) %>% 
+  st_sf() %>% 
+  st_transform(crs = "+proj=robin")
+
+ggplot() +
   geom_sf(data = graticules, color = "gray80", size = 0.3) +
   geom_sf(data = worldmap, fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_robinson, aes(color = mean_temp), size = 1) +
+  geom_sf(data = mass_inputs_robinson, aes(color = mean_wpb), size = 1) +
   coord_sf() +
@@
   guides(col = guide_colourbar(
-    title = "Mean temperature (°C)",
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
     direction = "horizontal", position = "bottom",
@@
   theme_void()
-
-p2 <- farm_temp_means %>% 
-  ggplot(aes(y = mean_temp, x = abs(lat), colour = country)) +
-  geom_point(size = 2) +
-  scale_colour_brewer(palette = "Set1") +
-  labs(x = expression("Absolute latitude ("*degree*")"), y = expression("Mean temperature ("*degree*"C)")) +
-  prettyplot() +
-  theme(legend.position = "top", legend.title = element_blank())
-
-p3 <- farm_temp_means %>% 
-  mutate(hemisphere = case_when(lat < 0 ~ "S", T ~ "N")) %>% 
-  ggplot(aes(x = mean_temp, fill = hemisphere)) +
-  geom_histogram(position = "identity", colour = "black", alpha = 0.5, binwidth = 0.5) +
-  labs(x = expression("Mean temperature ("*degree*"C)"), y = "Frequency") +
-  prettyplot() +
-  theme(legend.position = "top", legend.title = element_blank())
-
-(p2 + p3) / p_big_map + plot_layout(heights = c(1, 1.5))
-```
-
-```{r patchwork-map-mercator}
+```
+
+```{r patchwork-waste-map-mercator}
 #| fig-cap: |
@@
 
-no_margins <- function() {
-  theme(legend.position = "none", 
-        plot.margin = margin(0, 0, 0, 0),
-        axis.title = element_blank())
-}
-
-inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
-  CAN1 = c(-132, -122, 48.5, 54),
-  CAN2 = c(-70, -54, 43, 48.5),
-  EUR = c(-23, 28.5, 52, 71),
-  CHI = c(-78, -62, -55.5, -27),
-  AUS = c(144, 149, -43.75, -40.75)
-)
-
-inset_boxes_sm <- map(inset_boxes_sm, function(bx) {
-  list(
-    xlims = bx[1:2],
-    ylims = bx[3:4],
-    labx = bx[1],
-    laby = bx[4]
-    )
-})
-
-worldmap <- ne_countries(scale = "large", returnclass = "sf")
+mass_inputs_patch <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units())
+
 p1 <- ggplot() +
   geom_sf(data = worldmap, fill = "white", color = "dimgray") +
-  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 2) +
+  geom_sf(data = mass_inputs_patch, aes(color = mean_wpb, geometry = geometry), size = 2) +
   coord_sf() +
@@
   guides(col = guide_colourbar(
-    title = "Mean temperature (°C)",
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
     direction = "vertical", position = "right",
@@
     title.vjust = 1, title.hjust = 0.5,
-    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
-    barwidth = 1.5, barheight = 20
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barwidth = 1.5, barheight = 20,
   )) +
@@
 
-## Model parameterisation
-
-<!-- Salmon were grown for 548 days and were initialised in Spring.
-This was on day `r unique(farm_coords$t_start[farm_coords$lat < 0])` for farms in the southern hemisphere and day `r unique(farm_coords$t_start[farm_coords$lat > 0])` for farms in the northern hemisphere.
-Cohorts were initialised annually, such that there was an overlap of 183 days where one cohort was nearing harvest and another was being initialised.
--->
-
-```{r salmon params}
-#| code-summary: Get parameter and sensitivity data
-#| eval: true
-
-params <- file.path(output_species_data_path, "sens_params.qs") %>% qs::qread()
-
-param_names <- tibble::tribble(
-  ~name,        ~lab,
-  "alpha",      bquote(alpha),
-  "epsprot",    bquote(epsilon["P"]),
-  "epslip",     bquote(epsilon["L"]),
-  "epscarb",    bquote(epsilon["C"]),
-  "epsO2",      bquote(epsilon["O"[2]]),
-  "pk",         bquote("pk"),
-  "k0",         bquote("k"[0]),
-  "m",          bquote("m"),
-  "n",          bquote("n"),
-  "betac",      bquote(beta*"C"),
-  "Tma",        bquote("T"["max"]),
-  "Toa",        bquote("T"["opt"]),
-  "Taa",        bquote("T"["min"]),
-  "omega",      bquote(omega),
-  "a",          bquote("a"),
-  "k",          bquote("k"),
-  "eff",        bquote("eff"),
-  "meanW",      bquote(bar("W")),
-  "deltaW",     bquote(Delta*"W"), 
-  "meanImax",   bquote(bar("I"["max"])),
-  "deltaImax",  bquote(Delta*"I"["max"]),
-  "overFmean",  bquote(bar("F")),
-  "overFdelta", bquote(Delta*"F"),
-  "mortmyt",    bquote("mort")
-)
-```
-
-| Parameter | Value | Reference |
-|:------:|:------:|:-----------:|
-| $\alpha$             | `r unname(params['alpha'])`      | @broekhuizen_modelling_1994 |
-| $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
-| $\epsilon_{L}$       | `r unname(params['epslip'])`     | @baldan_r_2018 |
-| $\epsilon_{C}$       | `r unname(params['epscarb'])`    | @baldan_r_2018 |
-| $\epsilon_{O_2}$     | `r unname(params['epsO2'])`      | @elliott_energy_1975 |
-| $p_k$                | `r unname(params['pk'])`         | @macnaughton_using_2019 |
-| $k_0$                | `r unname(params['k0'])`         | @macnaughton_using_2019 |
-| $m$                  | `r unname(params['m'])`          | @broekhuizen_modelling_1994 | 
-| $n$                  | `r unname(params['n'])`          | @baldan_r_2018 |
-| $\beta C$            | `r unname(params['betac'])`      | @jonsson_thermal_2001 |
-| $T_{max}$            | `r unname(params['Tma'])`        | @poletto_unusual_2017 | 
-| $T_{opt}$            | `r unname(params['Toa'])`        | @jonsson_thermal_2001 | 
-| $T_{min}$            | `r unname(params['Taa'])`        | @vadboncoeur_lowering_2023 | 
-| $\omega$             | `r unname(params['omega'])`      | @baldan_r_2018 |
-| $a$                  | `r unname(params['a'])`          | @van_tien_development_2016 |
-| $k$                  | `r unname(params['k'])`          | @van_tien_development_2016 | 
-| $eff$                | `r unname(params['eff'])`        | @uglem_does_2020 | 
-| $\overline{W}$       | `r unname(params['meanW'])`      | @dempsey_estimating_2023 | 
-| $\Delta{W}$          | `r unname(params['deltaW'])`     | @dempsey_estimating_2023 | |
-| $\overline{I_{max}}$ | `r unname(params['meanImax'])`   | @lall_nutrition_2009 | 
-| $\Delta{I_{max}}$    | `r unname(params['deltaImax'])`  | @lall_nutrition_2009 | 
-| $\overline{F}$       | `r unname(params['overFmean'])`  | |
-| $\Delta{F}$          | `r unname(params['overFdelta'])` | |
-| $mort$               | `r unname(params['mortmyt'])`    | @tvete_towards_2023 |
-: Model growth parameters for Atlantic salmon (for double-checking numbers and reference list only) {#tbl-params}
-
-### Parameter sensitivity
-
-Parameter sensitivity was tested by varying each parameter in @tbl-params by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-All parameters in Table @tbl-params were tested.
-The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.
-
-## Modelled experimental feeds {#sec-feeds}
-
-```{r feeds}
-feed_params <- file.path(output_species_data_path, "feed_params.qs") %>%
-  qs::qread()
-
-feed_summary <- map_dfr(names(feed_params), function(feed) {
-  df <- feed_params[[feed]]
-  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
-    contrib <- df[[macro]]$proportion * df[[macro]]$macro
-    total <- sum(contrib)
-    digest <- sum(df[[macro]]$digest * contrib) / total
-        tibble(
-      feed = feed,
-      macro = macro,
-      total = total,
-      digest = digest
-    )
-  })
-}) %>%
-  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
-         feed = factor(feed, levels = c("reference", "past", "future")),
-         total_r = total * 100 %>% round(1),
-         digest_r = digest * 100 %>% round(1))
-```
-
-The reference feed was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "reference", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "reference", macro == "C")$total, 1)`% carbohydrate, the past feed was 
-`r round(100*filter(feed_summary, feed == "past", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "past", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "past", macro == "C")$total, 1)`% carbohydrate, and the future feed was 
-`r round(100*filter(feed_summary, feed == "future", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "future", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "C")$total, 1)`% carbohydrate.
-
-Ingredients are tracked seperately through the model with their own digestibility coefficients. 
-Overall, protein digestibility was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`%,
-`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`%, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% and carbohydrate digestibility was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "C")$digest, 1)`%,
-`r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`%, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "C")$digest, 1)`%
-within the reference, past, and future feeds respectively. 
-The digestibility of lipids was assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`%.
-
-```{r fig-feed-summary-ideas}
-#| fig-height: 7.5
-#| fig-cap: | 
-#|   Ideas for how to present the differences between feeds.
-Top plot shows the protein (red), lipids (yellow) and carbohydrate (blue) composition, with the digestible portion shown darker and the undigestible portion shown lighter.
-Bottom plot shows the proportion of each feed composed of each types of ingredient.
-
-p1 <- feed_summary %>%
-  mutate(digest_total = digest * total) %>% 
-  ggplot(aes(x = feed, y = total, fill = macro)) +
-  geom_col(position = "dodge", alpha = 0.55, colour = "black") +
-  geom_col(mapping = aes(y = digest_total), position = "dodge", alpha = 1, colour = "black") +
-  scale_fill_manual(values = macro_pal) +
-  scale_y_continuous(breaks = seq(0,0.5,0.1), labels = seq(0,50,10)) +
-  scale_x_discrete(labels = c("reference" = "Reference", "past" = "Past", "future" = "Future")) +
-  labs(x = "Feed", y = "Proportion (%)") +
-  prettyplot()
-
-feed_ings <- rbind(
-  feed_params[[1]][[1]] %>% mutate(feed = as.factor("reference")), 
-  feed_params[[2]][[1]] %>% mutate(feed = as.factor("past")), 
-  feed_params[[3]][[1]] %>% mutate(feed = as.factor("future"))
-) %>%
-  rename(protein = macro) %>%
-  mutate(
-    category = case_when(
-      str_detect(ingredient, "fish-oil") ~ "fish",
-      str_detect(ingredient, "fishmeal") ~ "fish",
-      str_detect(ingredient, "krill") ~ "other-marine",
-      str_detect(ingredient, "soy") ~ "legume",
-      str_detect(ingredient, "pea") ~ "legume",
-      str_detect(ingredient, "guar") ~ "legume",
-      str_detect(ingredient, "faba") ~ "legume",
-      str_detect(ingredient, "corn") ~ "wheat-corn",
-      str_detect(ingredient, "wheat") ~ "wheat-corn",
-      str_detect(ingredient, "chicken") ~ "chicken",
-      str_detect(ingredient, "bacteri") ~ "bact-fungi-micro",
-      str_detect(ingredient, "yeast") ~ "bact-fungi-micro",
-      str_detect(ingredient, "spirulina") ~ "bact-fungi-micro",
-      str_detect(ingredient, "bsf") ~ "insect",
-      T ~ "other-plant"
-    ) %>% 
-      factor(levels = c("fish", "other-marine", "chicken", "wheat-corn", "legume", "other-plant", "insect", "bact-fungi-micro"))
-  )
-
-p_ings <- feed_ings %>% 
-  mutate(feed = factor(feed, levels = c("reference", "past", "future"), labels = c("Reference", "Past", "Future"))) %>% 
-  group_by(feed, category) %>%
-  reframe(proportion = sum(proportion)) %>% 
-  ggplot(aes(x = "", y = proportion, fill = category)) +
-  geom_col(width = 1, colour = "black") +
-  coord_polar("y", start = 0) +
-  scale_fill_manual(
-    name = "Ingredient category",
-    values = c("fish" = "royalblue3", "other-marine" = "turquoise2", "chicken" = "hotpink1", "wheat-corn" = "moccasin", "legume" = "forestgreen", "other-plant" = "darkolivegreen1", "insect" = "firebrick3", "bact-fungi-micro" = "darkorange"),
-    labels = c("Fish meal or oil", "Other marine ingredients", "Chicken", "Wheat and corn", "Legumes", "Other plant ingredients", "Insects", "Bacteria, fungi or microalgae")) +
-  facet_grid(cols = vars(feed)) +
-  theme_void() +
-  theme(
-    text = element_text(family = "serif", size = 12, colour = "black"),
-    legend.position = "bottom",
-    legend.title = element_blank(), 
-    strip.text = element_blank(),
-    strip.text.x = element_text(size = 14)
-  )
-
-plot_grid(p1, p_ings, nrow = 2)
-```
-
-## Model population and biomass
-
-```{r raw biomass and weight data}
-farmrun_files <- file.path(output_cohorts_data_path) %>% 
-  list.files(full.names = T)
-
-weight <- find_read(output_cohorts_data_path, "allfarms_comparisons_weight_stat")
-biomass <- find_read(output_cohorts_data_path, "allfarms_comparisons_biomass_stat")
-```
-
-```{r fig-cohorts}
-#| fig-cap: | 
-#|   Example of how the overlapping cohorts combine into a single farm production curve (in this case biomass).
-The left plot shows the farm biomass produced by each cohort from initialisation to harvest, while the right plot shows the combined farm biomass over the course of a single production period of 548 days.
-#| eval: true
-
-fnms <- output_growth_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("reference")
-
-df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
-  as.data.frame() %>% 
-  mutate(mean = set_units(mean, "g") %>% set_units("t"),
-         sd = set_units(sd, "g") %>% set_units("t")) %>% 
-  select(-farm_ID)
-
-df <- rbind(
-  df %>% mutate(cohort = 1),
-  df %>% mutate(t = t+365, cohort = 2),
-  df %>% mutate(t = t+730, cohort = 3)
-) %>% 
-  mutate(t = (t-min(t))+1,
-         split = "Split by cohort")
-
-min_t <- min(df$t[df$cohort == 2])
-max_t <- max(df$t[df$cohort == 2])
-
-df_2 <- df %>% 
-  filter(t %in% min_t:max_t) %>% 
-  mutate(sd = sd/mean) %>% 
-  group_by(t) %>% 
-  reframe(sd = sqrt(sum(sd^2)),
-          mean = sum(mean),
-          sd = sd*mean) %>% 
-  mutate(cohort = "all",
-         split = "Totalled")
-
-df <- rbind(df, df_2) %>% 
-  mutate(cohort = as.factor(cohort))
-
-ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
-  geom_line(linewidth = 0.75) +
-  geom_ribbon(linetype = "dotted", alpha = 0) +
-  facet_grid(cols = vars(split)) +
-  scale_x_continuous(breaks = seq(0, 1600, 120)) +
-  scale_colour_manual(values = cohort_pal) +
-  prettyplot() +
-  labs(y = "Farm biomass", x = "Day of production")
-```
-
-```{r pop-biom-data}
-coho_biom <- file.path(data_analysis_path, "biomass_produced_comparison.qs") %>% 
-  qs::qread()
-harv_size <- file.path(output_farm_data_path, "farm_harvest_size.qs") %>% 
-  qread()
-
-coho_biom_summ <- coho_biom %>% 
-  mutate(perc_diff = 100*(mean - tonnes_per_farm)/tonnes_per_farm)
-```
-
-Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed).
-A population timeseries was the generated using the standard mortality rate (`r unname(params['mortmyt'])` d$^{-1}$).
-Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.
-
-```{r fig-harvest-size, class.chunk = "aside"}
-#| fig-cap: |
-#|   Frequency distribution of harvest sizes used to create the population timeseries for each farm, as predicted by the fish-growth model.
-
-harv_size %>% 
-  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
-  select(c(farm_ID, weight)) %>% 
-  ggplot(aes(x = weight)) +
-  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
-  scale_y_continuous(limits = c(0,500)) +
-  labs(y = "Frequency", x = "Harvest weight") +
-  prettyplot() +
-  theme(aspect.ratio = 0.75)
-```
-
-By this method, farm biomass as predicted by the model slightly overestimated farm tonnage.
-Predicted farm biomass was `r round(min(coho_biom_summ$perc_diff),1)`-`r round(max(coho_biom_summ$perc_diff),1)` higher than tonnage produced (@fig-biomass-produced).
-This variation was not correlated with mean farm temperature or total tonnage produced (@fig-biomass-variation).
-
-```{r fig-biomass-variation, class.chunk = "aside"}
-plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
-# plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
-```
-
-```{r fig-biomass-produced, class.chunk = "aside"}
-#| fig-cap: Modelled vs observed salmon biomass produced
-
-coho_biom %>% 
-  ggplot(aes(x = tonnes_per_farm, y = mean, colour = country)) +
-  geom_point(size = 2.5) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  scale_x_continuous(limits = c(0,1700)) +
-  scale_y_continuous(limits = c(0,1700)) +
-  scale_colour_brewer(palette = "Set1") +
-  labs(y = "Modelled biomass produced (t)", x = "Observed biomass produced (t)") +
-  prettyplot() +
-  theme(legend.position = "top", legend.title = element_blank())
-```
-
-## Impacts of nutrient input
-
-General thoughts is that a risk-assessment approach is most compelling:
-
-* Hazard: Nutrient input. Present as a change between feeds (%?), relative to background levels (ratio?)
-  * Possibly ask Camille how the quotas for Tasmanian salmon are calculated
-  * Background levels are from [oceanhealthindex.org](https://knb.ecoinformatics.org/view/resource_map_doi:10.5063/F1610XPS) - double-check that it includes wastewater input AND agriculture - should include both - if they're not combined ask Ben because he has them combined somewhere
-  * If this is too uncertain perhaps combine into categorical (oligotrophic/eutrophic) classification?
-* Exposure: Species presence. Use IUCN/Aquamap data to estimate the % of each species range is occupied by farms
-  * give each farm a 1km radius, check for overlaps
-  * Gage already has the data to process the Aquamap data
-* Vulnerability: species vulnerability to eutrophication + nutrient input [@butt_trait-based_2022; @ohara_code_2021]. Possibly also use IUCN threat levels for prioritisation?
-
-# Statistical analysis & code availability
-
-All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
-Major packages used include `r cite_packages(packages)`.
-For a full list of R packages used see the lockfile on [Github](https://www.github.com).
-This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
-
-# Results
-
-* Parameter sensitivity results are in supplementary @sec-parameter-sensitivity
-
-In general, data outputs comes in the following dimensions:
-
-* Location -> temperature -> farm_ID
-* Uneaten feed + excreted faeces = total inputs (g)
-* Day of production (impacted by location)
-* Main point is the difference between feeds (kg/t salmon).
-* Also interesting to see if difference between feeds varies geographically (correlates with latitude, or maybe mean/median/max temperature?)
-
-## Uneaten feed and faeces
-
-```{r inputs data}
-#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)
-
-mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
-mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
-N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
-N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
-```
-
-```{r inputs stats through time}
-#| eval: false
-#| code-summary: Show how inputs (mass and N) change through time (across all farms)
-
-mass_inputs_ts
-N_inputs_ts
-
-# Through time
-inputs_stats_ts <- inputs_df %>%
-  group_by(feed, t, measure) %>% 
-  reframe(min = minna(mean),
-          max = maxna(mean),
-          sd = sdna(mean) %>% set_units("g"),
-          mean = meanna(mean))
-
-inputs_stats_rel_ts <- inputs_rel_df %>% 
-  group_by(feed, t, measure) %>% 
-  reframe(min = minna(mean),
-          max = maxna(mean),
-          sd = sdna(mean) %>% set_units("g g_fish-1"),
-          mean = meanna(mean))
-
-# Total (at production end)
-inputs_stats_end <- inputs_df %>% 
-  group_by(feed, measure, farm_ID) %>% 
-  reframe(mean = sumna(mean)) %>% 
-  group_by(feed, measure) %>% 
-  reframe(min = minna(mean),
-          max = maxna(mean),
-          sd = sdna(mean) %>% set_units("g"),
-          mean = meanna(mean))
-
-inputs_stats_rel_end <- inputs_rel_df %>% 
-  group_by(feed, measure, farm_ID) %>% 
-  reframe(mean = sumna(mean)) %>% 
-  group_by(feed, measure) %>% 
-  reframe(min = minna(mean),
-          max = maxna(mean),
-          sd = sdna(mean) %>% set_units("g g_fish-1"),
-          mean = meanna(mean))
-
-inputs_stats_rel_end_diff <- inputs_rel_df %>% 
-  group_by(feed, measure, farm_ID) %>% 
-  reframe(mean = sumna(mean)) %>% 
-  pivot_wider(names_from = feed, values_from = mean) %>% 
-  mutate(future = (future-reference)/reference,
-         past = (past-reference)/reference) %>% 
-  select(-reference) %>% 
-  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
-  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
-  group_by(feed, measure) %>% 
-  reframe(min = minna(diff),
-          max = maxna(diff),
-          sd = sdna(diff),
-          mean = meanna(diff))
-
-# Pull key values (uneaten feed)
-u_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
-u_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
-u_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
-u_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
-u_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
-u_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
-u_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
-u_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
-u_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)
-
-# Convert past and future values to % change values
-u_stmin2 <- (100*u_stmin2) %>% round(2)
-u_stmax2 <- (100*u_stmax2) %>% round(2)
-u_stmean2 <- (100*u_stmean2) %>% round(2)
-u_stmin3 <- (100*u_stmin3) %>% round(2)
-u_stmax3 <- (100*u_stmax3) %>% round(2)
-u_stmean3 <- (100*u_stmean3) %>% round(2)
-
-u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-
-# Pull key values (excreted faeces)
-e_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(min)
-e_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(max)
-e_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(mean)
-e_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(min)
-e_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(max)
-e_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(mean)
-e_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(min)
-e_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(max)
-e_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(mean)
-
-# Convert past and future values to % change values
-e_stmin2 <- (100*e_stmin2) %>% round(2)
-e_stmax2 <- (100*e_stmax2) %>% round(2)
-e_stmean2 <- (100*e_stmean2) %>% round(2)
-e_stmin3 <- (100*e_stmin3) %>% round(2)
-e_stmax3 <- (100*e_stmax3) %>% round(2)
-e_stmean3 <- (100*e_stmean3) %>% round(2)
-
-e_stmin1 <- e_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-e_stmax1 <- e_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-e_stmean1 <- e_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
-```
-
-```{r waste inputs stats total}
-#| code-summary: Show how waste inputs change in total (at the end of a production period) across all farms
-
-mass_inputs_sep <- mass_inputs_end %>% 
-  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
-  dplyr::select(-c(total, biomass_total)) %>% 
-  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
-  mutate(total = excr+uneat) %>% 
-  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
-  group_by(feed, measure) %>% 
-  reframe(mean_wpb = meanna(waste_per_biomass),
-          mean_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
-          min_wpb = minna(waste_per_biomass),
-          max_wpb = maxna(waste_per_biomass))
-
-twi_min <- mass_inputs_sep$min_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
-twi_max <- mass_inputs_sep$max_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
-twi_mean <- mass_inputs_sep$mean_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
-
-# There were only very small differences in total uneaten feed between the different feeds, with the past feed increasing uneaten feed by `r u_stmin2`-`r u_stmax2`%  (mean of `r u_stmean2`%) and the future feed increasing uneaten feed by `r u_stmin3`-`r u_stmax3`%  (mean of `r u_stmean3`%).
-
-# * Total excreted faeces across a cohort fed the reference feed ranged from `r e_stmin1` to `r e_stmax1` g kg$^{-1}$ fish, with a mean of `r e_stmean1` g kg$^{-1}$ fish. 
-# * Past feed decreased excreted faeces by `r -1*e_stmin2`-`r -1*e_stmax2`%  (mean of `r -1*e_stmean2`%) 
-# * Future feed increased excreted faeces by `r e_stmin3`-`r e_stmax3`%  (mean of `r e_stmean3`%)
-```
-
-* Total waste inputs across a single production period of fish fed the reference feed ranged from `r twi_min[1]` to `r twi_max[1]` g kg$^{-1}$ fish, with a mean of `r twi_mean[1]` g kg$^{-1}$ fish.
-* Total waste inputs across a single production period of fish fed the past feed ranged from `r twi_min[2]` to `r twi_max[2]` g kg$^{-1}$ fish, with a mean of `r twi_mean[2]` g kg$^{-1}$ fish.
-* Total waste inputs across a single production period of fish fed the future feed ranged from `r twi_min[3]` to `r twi_max[3]` g kg$^{-1}$ fish, with a mean of `r twi_mean[3]` g kg$^{-1}$ fish.
-
-```{r fig-waste-inputs-total}
-#| fig-cap: | 
-#|   Total waste intputs (uneaten feed + excreted faeces) across the whole production period at each farm location.
-#| fig-width: 9.5
-
-mass_inputs_sep_geometry <- mass_inputs_end %>% 
-  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
-  dplyr::select(-c(total, biomass_total)) %>% 
-  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
-  mutate(total = excr+uneat) %>% 
-  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
-  group_by(farm_ID, feed, measure) %>% 
-  reframe(mean_wpb = meanna(waste_per_biomass),
-          sd_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
-          min_wpb = minna(waste_per_biomass),
-          max_wpb = maxna(waste_per_biomass)) %>% 
-  merge(farms_geometry, by = "farm_ID")
-
-mass_inputs_robinson <- mass_inputs_sep_geometry %>% 
-  filter(feed == "reference" & measure == "total") %>% 
-  mutate(mean_wpb = mean_wpb %>% drop_units()) %>% 
-  st_sf() %>% 
-  st_transform(crs = "+proj=robin")
-
-ggplot() +
-  geom_sf(data = graticules, color = "gray80", size = 0.3) +
-  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
-  geom_sf(data = mass_inputs_robinson, aes(color = mean_wpb), size = 1) +
-  coord_sf() +
-  scale_color_viridis_c(option = "turbo") +
-  guides(col = guide_colourbar(
-    title = expression("Mean waste inputs (g g fish"^-1*")"),
-    direction = "horizontal", position = "bottom",
-    label.position = "bottom", title.position = "top", 
-    title.vjust = 1, title.hjust = 0.5,
-    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
-    barwidth = 25,barheight = 1.5
-  )) +
-  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
-  geom_sf_text(data = labels_robinson, aes(label = letter), 
-               color = "darkred", size = 5, fontface = "bold", 
-               hjust = 0.5, vjust = 0.5) +
-  theme_void()
-```
-
-```{r patchwork-waste-map-mercator}
-#| fig-cap: |
-#|   Example of a patchwork
-#| fig-height: 9
-#| fig-width: 9.5
-
-mass_inputs_patch <- mass_inputs_sep_geometry %>% 
-  filter(feed == "reference" & measure == "total") %>% 
-  mutate(mean_wpb = mean_wpb %>% drop_units())
-
-p1 <- ggplot() +
-  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
-  geom_sf(data = mass_inputs_patch, aes(color = mean_wpb, geometry = geometry), size = 2) +
-  coord_sf() +
-  scale_color_viridis_c(option = "turbo") +
-  guides(col = guide_colourbar(
-    title = expression("Mean waste inputs (g g fish"^-1*")"),
-    direction = "vertical", position = "right",
-    label.position = "right", title.position = "top", 
-    title.vjust = 1, title.hjust = 0.5,
-    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
-    barwidth = 1.5, barheight = 20,
-  )) +
-  prettyplot() +
-  labs(y = "Latitude", x = "Longitude")
-
-p_Can1 <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
-           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
-  draw_label("A", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CAN1"]][["labx"]], 
-             y = inset_boxes_sm[["CAN1"]][["laby"]], 
-             hjust = -1, vjust = 0.5)
-p_Can2 <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
-           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
-  draw_label("B", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CAN2"]][["labx"]], 
-             y = inset_boxes_sm[["CAN2"]][["laby"]], 
-             hjust = 0.5, vjust = 0.5)
-p_Eur <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
-           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
-  draw_label("C", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["EUR"]][["labx"]], 
-             y = inset_boxes_sm[["EUR"]][["laby"]], 
-             hjust = -1, vjust = 0.5)
-p_Chi <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
-           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
-  theme(legend.position = "right") +
-  draw_label("D", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["CHI"]][["labx"]], 
-             y = inset_boxes_sm[["CHI"]][["laby"]], 
-             hjust = 0, vjust = 0)
-p_Aus <- p1 + 
-  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
-           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
-  draw_label("E", size = 14, fontface = "bold", 
-             x = inset_boxes_sm[["AUS"]][["labx"]], 
-             y = inset_boxes_sm[["AUS"]][["laby"]], 
-             hjust = 0, vjust = 0.5)
-
-grid_1 <- cowplot::plot_grid(p_Can1, p_Can2, ncol = 2, rel_widths =  c(1, 1.35))
-grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
-grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
-
-cowplot::plot_grid(
-  grid_1, grid_3,
-  nrow = 2,
-  rel_heights = c(1, 1.5)        # relative row heights
-)
-```
-
 ```{r fig-total-excreted-perday}

### 2025-07-23 src/dirs.R

@@ -26,12 +26,10 @@ input_Ndata_path <- file.path(gendata_path, "background_nitrogen")
 output_farm_data_path <- file.path(output_path, "farm_data")
 output_species_data_path <- file.path(output_path, "species_data")
 output_sens_data_path <- file.path(output_path, "sensitivity_data")
-output_growth_data_path <- file.path(output_path, "farm_growth_data")
-output_cohorts_data_path <- file.path(output_path, "cohort_growth_data")
+per_biomass_farm_path <- file.path(output_path, "per_biomass_outputs_farm")
+per_biomass_cohort_path <- file.path(output_path, "per_biomass_outputs_cohort")
 output_model_farm_path <- file.path(output_path, "all_outputs_farm")
 output_model_cohort_path <- file.path(output_path, "all_outputs_cohort")
-total_uneaten_path <- file.path(output_path, "total_uneaten_cohort")
-total_excreted_path <- file.path(output_path, "total_excreted_cohort")
 data_analysis_path <- file.path(output_path, "data_analysis")
 impacts_path <- file.path(output_path, "nutrient_impacts")
 
@@ -39,15 +37,12 @@ impacts_path <- file.path(output_path, "nutrient_impacts")
 dir.create(output_species_data_path, showWarnings = F)
 dir.create(output_sens_data_path, showWarnings = F)
 dir.create(output_farm_data_path, showWarnings = F)
-dir.create(output_growth_data_path, showWarnings = F)
-dir.create(output_cohorts_data_path, showWarnings = F)
+dir.create(per_biomass_farm_path, showWarnings = F)
+dir.create(per_biomass_cohort_path, showWarnings = F)
 dir.create(output_model_farm_path, showWarnings = F)
 dir.create(output_model_cohort_path, showWarnings = F)
-dir.create(total_uneaten_path, showWarnings = F)
-dir.create(total_excreted_path, showWarnings = F)
 dir.create(data_analysis_path, showWarnings = F)
 dir.create(impacts_path, showWarnings = F)
-
 
 # From extracting_temperature
 # this_path <- file.path("data", this_species) # now call species_path

### 2025-07-23 src/functions.R

@@ -1,3 +1,8 @@
+library(devtools)
+library(qs)
+library(arrow)
+library(stringr)
+
 make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
 fixnum <- function(n, digits = 4) {
   vapply(n, function(x) {

### 2025-07-23 src/map_templates.R

@@ -1,3 +1,4 @@
+library(devtools)
 library(qs)
 library(dplyr)
 library(magrittr)

### 2025-07-23 src/model_functions.R

@@ -293,10 +293,8 @@ uni_farm_growth <- function(pop_params, species_params, feed_params, water_temp,
   return(out_list)
 }
 
-farm_to_cohort <- function(matrix, time_offset = 0) {
-  matrix %>% 
-    as.data.frame() %>% 
-    rename(t = V1, mean = V2, sd = V3) %>%
+farm_to_cohort <- function(df, time_offset = 0) {
+  df %>% 
     mutate(t = t + time_offset)
 }
 

### 2025-07-23 targets/_targets_farmruns.R

@@ -22,18 +22,23 @@ list(
   tar_target(farm_coords, qs::qread(farm_coords_file)),
   tar_target(
     farm_IDs,
-    qs::qread(farm_ts_data_file) %>% 
-      distinct(farm_ID) %>% 
-      pull(farm_ID) #%>% sample(25)
+    command = {
+      # c(1:39, 2704:2721) # Australia and US only
+
+      qs::qread(farm_ts_data_file) %>% 
+        distinct(farm_ID) %>% 
+        pull(farm_ID)
+    }
   ),
   tar_target(
     farm_ts_data, 
     qs::qread(farm_ts_data_file) %>% 
-      merge(farm_coords, by = "farm_ID") %>% 
-      dplyr::filter(farm_ID %in% farm_IDs) %>%
+      merge(farm_coords, by = "farm_ID") %>%
+      filter(farm_ID == farm_IDs) %>%
       mutate(keep = case_when(day >= t_start & day <= t_end ~ T, T ~ F)) %>% 
       dplyr::filter(keep) %>% 
-      dplyr::select(farm_ID, day, temp_c)
+      dplyr::select(farm_ID, day, temp_c),
+    pattern = farm_IDs
   ),
   tar_target(
     feed_names,
@@ -88,14 +93,12 @@ list(
   tar_target(
     harvest_size,
     command = {
-      farm_temp <- farm_ts_data %>%
-        filter(farm_ID == farm_IDs)
       fg <- fish_growth(
         pop_params = all_params,
         species_params = all_params,
-        water_temp = farm_temp$temp_c,
+        water_temp = farm_ts_data$temp_c,
         feed_params = reference_feed,
-        times = c(t_start = min(farm_temp$day), t_end = max(farm_temp$day), dt = 1),
+        times = c(t_start = min(farm_ts_data$day), t_end = max(farm_ts_data$day), dt = 1),
         init_weight = all_params["meanW"],
         ingmax = all_params["meanImax"]
       ) 
@@ -111,17 +114,18 @@ list(
             units::drop_units()
         )
     },
-    pattern = farm_IDs
+    pattern = map(farm_IDs, farm_ts_data)
   ),
 
 # Prepare parameters ----------------------------------------------------------------------------------------------
   tar_target(
     stat_names,
-    c("weight_stat", "dw_stat", "water_temp_stat", "T_response_stat", "P_excr_stat", 
[…]

### 2025-07-23 targets/_targets_sensitivities.R

@@ -42,7 +42,7 @@ list(
   ),
   tar_target(
     reference_feed,
-    qs::qread(feed_params_file)[["aas_2022"]]
+    qs::qread(feed_params_file)[["plant_dominant"]]
   ),
 
   # Get names of params to be adjusted
@@ -52,60 +52,158 @@ list(
 
   tar_target(factors, c(0.9, 1, 1.1)),
   tar_target(
-    sens_run_spec, 
+    sens_run_spec_lo, 
     command = {
       # Pre-split farm temperature data for speed
       farm_ts_list <- split(farm_ts_data, farm_ts_data$farm_ID)
-
-      sens_farm <- purrr::map(factors, function(fact) {
         
-        # Adjust params by factor
-        adj_params <- all_params
-        adj_params[param_names_spec] <- adj_params[param_names_spec] * fact
+      # Adjust params by factor
+      adj_params <- all_params
+      adj_params[param_names_spec] <- adj_params[param_names_spec] * factors[1]
 
-        purrr::map2(farm_IDs, farm_ts_list, function(farm, ts) {
-          sens <- uni_farm_growth(
-            pop_params = adj_params,
-            species_params = adj_params,
-            water_temp = ts$temp_c,
-            feed_params = reference_feed,
-            times = c('t_start' = min(ts$day), 't_end' = max(ts$day), 'dt' = 1),
-            N_pop = rep(1, nrow(ts))
-          )
-          
-          data.frame(
-            weight = last(sens[['weight_stat']][, 2][!is.na(sens[['weight_stat']][, 2])]),
-            dw = mean(sens[['dw_stat']][, 2], na.rm = T),
-            total_excr = sum(sens[['total_excr_stat']][, 2], na.rm = T),
-            P_excr = sum(sens[['P_excr_stat']][, 2], na.rm = T),
-            L_excr = sum(sens[['L_excr_stat']][, 2], na.rm = T),
-            C_excr = sum(sens[['C_excr_stat']][, 2], na.rm = T),
-            total_uneat = sum(sens[['total_uneat_stat']][, 2], na.rm = T),
-            P_uneat = sum(sens[['P_uneat_stat']][, 2], na.rm = T),
-            L_uneat = sum(sens[['L_uneat_stat']][, 2], na.rm = T),
-            C_uneat = sum(sens[['C_uneat_stat']][, 2], na.rm = T),
[…]

### 2025-07-25 06_run_atlantic_salmon_model.qmd
Runs

@@
 
-Note that this takes a long time - each branch of farmrun takes ~5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
+Note that this takes a long time - each branch of farmrun takes ~5.3 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
 
@@
 
-targets::tar_make(seconds_meta_append = 90)
+targets::tar_make(
+  names = c("farm_run", "farm_results", "cohort_results"),
+  seconds_meta_append = 90
+)
 
@@
 targets::tar_load(stat_names)
-targets::tar_load(farm_results)
-targets::tar_load(cohort_results)
+targets::tar_load(farm_IDs)
+targets::tar_load(feed_names)
+branches <- length(stat_names) * length(farm_IDs) * length(feed_names)
+branches <- split(1:branches, ceiling(1:branches/length(farm_IDs)))
 
-purrr::map(stat_names, function(stat_name) {
+for (stat_name in stat_names) {
+  farm_results <- purrr::map(branches, function(br) {
+    targets::tar_load(farm_results, branches = br)
     farm_results %>% 
-    filter(measure == stat_name) %>% 
-    qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
+      filter(measure == stat_name)
+  })
+  farm_results <- bind_rows(farm_results)
+  qsave(farm_results, file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
 
+  cohort_results <- purrr::map(branches, function(br) {
+    targets::tar_load(cohort_results, branches = br)
     cohort_results %>% 
-    filter(measure == stat_name) %>% 
-    qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
+      filter(measure == stat_name)
   })
+  cohort_results <- bind_rows(cohort_results)
+  qsave(cohort_results, file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
+
+  print(str_c("Files saved for ", stat_name))
+}
 
@@
       mean_perbiom = mean/biom_mean,
-      sd_perbiom = (sd_mean+biom_sd_mean) * mean_perbiom
+      sd_perbiom = (sd/mean+biom_sd_mean) * mean_perbiom
     ) %>%

### 2025-07-25 targets/_targets_farmruns.R

@@ -4,7 +4,7 @@ library(crew)
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble", "qs"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 10),
+  controller = crew_controller_local(workers = 14),
   workspace_on_error = TRUE
 )
 
@@ -27,7 +27,7 @@ list(
 
       qs::qread(farm_ts_data_file) %>% 
         distinct(farm_ID) %>% 
-        pull(farm_ID)
+        pull(farm_ID) #%>% sample(272)
     }
   ),
   tar_target(

### 2025-07-28 src/model_functions.R
Final adjustment to feed provision

@@ -84,12 +84,12 @@ feeding_rate <- function(water_temp, species_params) {
     (species_params['betac'] * (species_params['Tma'] - species_params['Toa']))
 }
 
-food_prov_rate <- function(pop_params, water_temp, ing_pot, ing_pot_10, species_params) {
+food_prov_rate <- function(pop_params, water_temp, ing_pot, ing_pot_min, species_params) {
   # Use ifelse vectorization instead of individual if statements
   ifelse(
     water_temp > species_params['Taa'],
     ing_pot * (1 + rnorm(1, pop_params['overFmean'], pop_params['overFdelta'])),
-    ing_pot_10
+    ing_pot_min
   ) # old formula: 0.25 * 0.066 * weight^0.75
 }
 
@@ -135,7 +135,7 @@ fish_growth <- function(pop_params, species_params, water_temp, feed_params, tim
       pop_params = pop_params, 
       water_temp = result[i, 'water_temp'],
       ing_pot = result[i, 'ing_pot'],
-      ing_pot_10 = ingmax * (result[i, 'weight']^species_params['m']) * 0.1,
+      ing_pot_min = ingmax * (result[i, 'weight']^species_params['m']) * feeding_rate(species_params['Taa'], species_params),
       species_params
     )
     result[i, 'food_enc'] <- species_params['eff'] * result[i, 'food_prov']

### 2025-07-28 src/map_templates.R
Move patchwork mapping to function

@@ -95,12 +95,18 @@ worldmap_mercator <- ne_countries(scale = "large", returnclass = "sf")
 get_insets_mercator <- function(map) {
   map2(inset_boxes_sm, labels_spec_mercator, function(specs, labs) {
     map + 
-      coord_sf(xlim = specs[["xlims"]], 
-              ylim = specs[["ylims"]])  +
-      draw_label("A", size = 14, fontface = "bold", 
-                x = specs[["labx"]], 
-                y = specs[["laby"]], 
-                hjust = labs["h"], vjust = labs["h"])
+      coord_sf(
+        xlim = specs[["xlims"]], 
+        ylim = specs[["ylims"]]
+      )  +
+      draw_label(
+        "A", 
+        size = 14, 
+        fontface = "bold", 
+        x = specs[["labx"]], 
+        y = specs[["laby"]], 
+        hjust = labs["h"], vjust = labs["h"]
+      )
   })
 }
 
@@ -110,6 +116,30 @@ p_bigmap_mercator <- ggplot() +
   theme_void() +
   labs(y = "Latitude", x = "Longitude")
 
-p_insets_mercator <- get_insets_mercator(p_bigmap_mercator)
-
-
+patchwork_mercator <- function(bigmap) {
+  p_insets <- get_insets_mercator(bigmap)
+  
+  grid_canada <- plot_grid(
+    p_insets[["CAN1"]], 
+    p_insets[["CAN2"]], 
+    ncol = 2, 
+    rel_widths =  c(1, 1.35)
+  )
+  grid_notcanada <- plot_grid(
+    plot_grid(
+      p_insets[["p_Eur"]],  
+      p_insets[["p_Aus"]],  
+      nrow = 2, 
+      rel_heights = c(1, 1)
+    ), 
+    p_insets[["p_Chi"]],  
+    ncol = 2, 
+    rel_widths =  c(1, 1)
+  )
+  
+  plot_grid(
+    grid_canada, grid_notcanada,
+    nrow = 2,
+    rel_heights = c(1, 1.5)
+  )
+}

### 2025-07-28 index.qmd
Move functional response to index.qmd

@@
     fig.width: 8.5
+format:
+  html:
+    code-fold: true
 ---
@@
 
-This project contains a comprehensive analysis of mariculture modelling from local to global scales. Below you'll find links to all the main documentation pages:
+All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github. 
+While this page (the index) has code that runs prior to rendering, all code in the subsequent pages has not been run for rendering.
+
+## Main analysis
+
+The main analysis for this project focuses on the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.
 
@@
 |---------|:-------------------------------------------------|
-| **[Data Tidying](01_tidying_data.html)** | Initial data cleaning and preparation procedures |
+| **[Data Tidying](01_tidying_data.html)** | Initial data tidying and preparation |
 | **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
 | **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
-| **[Extracting Temperatures](04_extracting_temperatures.html)** | Temperature data extraction and processing for model inputs |
-| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition analysis and formulation procedures |
-| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model implementation and execution |
+| **[Extracting Temperatures](04_extracting_temperatures.html)** | SST data extraction and processing for model inputs |
+| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
+| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |
+
+## Extra analysis
+
+The extra analyses for this project involved some exploration into potential impacts of nutrient losses. This will likely not make it into the final manuscript.
+
+| Page | Description |
+|---------|:-------------------------------------------------|
 | **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
@@
 
-# Data analysis
-
 ```{r setup}
-#| include: false
-#| eval: true
 #| cache: false
@@
 library(RColorBrewer)
-conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect(), .quiet = T)
+conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
 # This markdown uses TinyTex - install with tinytex::install_tinytex()
@@
 install_unit("t_fish", "1000 kg_fish")
-
-# Filenames
-# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
-# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
 
@@
 ## Feed provision and feeding response to temperature {#sec-model-feeding}
+
+```{r}
+#| label: fig-functional-response-to-temperature
+#| eval: false
+#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
+
+all_params <- c(
+  find_read(output_species_data_path, "species_params"),
+  find_read(output_species_data_path, "pop_params")
+)
+
+func_T_resp <- data.frame(water_temp = seq(-5, 26, 0.25))
+weight <- 1000
+
+# Relative feeding rate with temperature
+func_T_resp$feeding_rate <- sapply(
+  FUN = feeding_rate, 
+  X = func_T_resp$water_temp, 
+  species_params = all_params
+)
+
+# Maximum potential ingestion (g) at temperature
+func_T_resp$ing_pot <- all_params['meanImax'] * (weight^all_params['m']) * func_T_resp$feeding_rate
+
+# Food provided is based on calculated potential ingestion BUT if temperature is too low they are still provided with the food that would be required at lowest temperature (when feeding rate is ~18.3%)
+func_T_resp$food_prov <- food_prov_rate(
+  water_temp = func_T_resp$water_temp, 
+  ing_pot = func_T_resp$ing_pot,
+  ing_pot_min = all_params['meanImax'] * (weight^all_params['m']) * feeding_rate(all_params['Taa'], all_params),
+  species_params = all_params,
+  pop_params = all_params
+)
+
+func_T_resp$food_enc <- all_params['eff'] * func_T_resp$food_prov
+func_T_resp <- func_T_resp %>% 
+  mutate(ing_act = pmin(food_enc, ing_pot))
+
+func_T_resp %>% 
+  ggplot(aes(x = water_temp, y = ing_act)) +
+  geom_line(linewidth = 0.75) +
+  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
+  # scale_y_continuous(breaks = seq(0,1.5,0.25)) +
+  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
+  labs(x = expression("Water temperature ("*degree*"C)"), y = "Feedd ingested/provided") +
+  prettyplot()
+```
+
+```{r}
+#| label: patchwork-map-mercator
+#| fig-cap: |
+#|   Example of a patchwork
+#| fig-height: 9
+#| fig-width: 9.5
+
+p_bigmap_feeding <- p_bigmap_mercator +
+  geom_sf(data = feeding, aes(color = prop_feed_eaten, geometry = geometry), size = 2) +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = "Proportion of provided feed eaten",
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 1.5, barheight = 20
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+patchwork_mercator(p_bigmap_feeding)
+```
 

### 2025-07-28 manuscript.qmd
Move functional response to index.qmd

@@
 * Deminstration of how feeding response and actual food given vary with temperature?
-
-```{r fig-functional-response-to-temperature}
-#| eval: false
-#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
-
-df <- data.frame(water_temp = seq(-5, 26, 0.25))
-df$feeding <- sapply(FUN = feeding_rate, X = df$water_temp, species_params = species_params)
-df <- df %>% 
-mutate(ing_pot = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * feeding,
-       food_prov = NA)
-for (i in 1:nrow(df)) {
-  df$food_prov[i] <- food_prov_rate(pop_params = pop_params, rel_feeding = df$feeding[i], ing_pot = df$ing_pot[i], 
-                                    ing_pot_10 = pop_params['meanImax'] * (pop_params['meanW']^species_params['m']) * 0.1)
-}
-df$ing_pot <- df$ing_pot/maxna(df$ing_pot)
-df$food_prov <- df$food_prov/maxna(df$ing_pot)
-
-df %>% 
-  ggplot(aes(x = water_temp, y = ing_pot)) +
-  geom_line(linewidth = 0.75) +
-  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
-  scale_y_continuous(breaks = seq(0,1.5,0.25)) +
-  scale_x_continuous(breaks = seq(-5,30,5), limits = c(-5,26)) +
-  labs(x = expression("Water temperature ("*degree*"C)"), y = "Relative food ingested/provided") +
-  prettyplot() +
-  theme(text = element_text(colour = "black", family = "serif", size = 12))
-```
 

### 2025-07-28 index.qmd
Move feed details to index.qmd

@@
 
+```{r}
+#| label: feed-details
+
+feed_params <- find_read(output_species_data_path, "feed_params")
+
+feed_summary <- map_dfr(names(feed_params), function(feed) {
+  df <- feed_params[[feed]]
+  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
+    contrib <- df[[macro]]$proportion * df[[macro]]$macro
+    total <- sum(contrib)
+    digest <- sum(df[[macro]]$digest * contrib) / total
+        tibble(
+      feed = feed,
+      macro = macro,
+      total = total,
+      digest = digest
+    )
+  })
+}) %>%
+  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
+         feed = factor(feed, levels = c("reference", "past", "future")),
+         total_r = total * 100 %>% round(1),
+         digest_r = digest * 100 %>% round(1))
+```
+
+| Feed | Protein (%, %) | Lipid (%, %) | Carbohydrate (%, %) |
+|------|:----------:|:----------:|:----------:|
+| Plant-dominant | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$digest, 1)`) | 
+                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$digest, 1)`) | 
+                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$digest, 1)`) |
+| Marine-dominant | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$digest, 1)`) | 
+                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$digest, 1)`) | 
+                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$digest, 1)`) |
+| Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`) | 
+                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`) | 
+                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`) |
+
 # Model sensitivity to parameter changes {#param-sensitivity}

### 2025-07-28 manuscript.qmd
Move feed details to index.qmd

@@
 ## Modelled experimental feeds {#sec-feeds}
-
-```{r feeds}
-feed_params <- file.path(output_species_data_path, "feed_params.qs") %>%
-  qs::qread()
-
-feed_summary <- map_dfr(names(feed_params), function(feed) {
-  df <- feed_params[[feed]]
-  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
-    contrib <- df[[macro]]$proportion * df[[macro]]$macro
-    total <- sum(contrib)
-    digest <- sum(df[[macro]]$digest * contrib) / total
-        tibble(
-      feed = feed,
-      macro = macro,
-      total = total,
-      digest = digest
-    )
-  })
-}) %>%
-  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
-         feed = factor(feed, levels = c("reference", "past", "future")),
-         total_r = total * 100 %>% round(1),
-         digest_r = digest * 100 %>% round(1))
-```
-
-The reference feed was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "reference", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "reference", macro == "C")$total, 1)`% carbohydrate, the past feed was 
-`r round(100*filter(feed_summary, feed == "past", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "past", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "past", macro == "C")$total, 1)`% carbohydrate, and the future feed was 
-`r round(100*filter(feed_summary, feed == "future", macro == "P")$total, 1)`% protein, 
-`r round(100*filter(feed_summary, feed == "future", macro == "L")$total, 1)`% lipid, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "C")$total, 1)`% carbohydrate.
-
-Ingredients are tracked seperately through the model with their own digestibility coefficients. 
-Overall, protein digestibility was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "P")$digest, 1)`%,
-`r round(100*filter(feed_summary, feed == "past", macro == "P")$digest, 1)`%, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "P")$digest, 1)`% and carbohydrate digestibility was 
-`r round(100*filter(feed_summary, feed == "reference", macro == "C")$digest, 1)`%,
-`r round(100*filter(feed_summary, feed == "past", macro == "C")$digest, 1)`%, and 
-`r round(100*filter(feed_summary, feed == "future", macro == "C")$digest, 1)`%
-within the reference, past, and future feeds respectively. 
-The digestibility of lipids was assumed to remain constant across all ingredients at `r round(100*filter(feed_summary, feed == "past", macro == "L")$digest, 1)`%.
 

### 2025-07-28 index.qmd
Functional responses to temperature

@@
 
-## Population and biomass
+```{r}
+#| label: location-data
 
-```{r raw biomass and weight data}
+farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
+  rename(farm_ID = farm_id)
+```
+
+## Population and biomass {#sec-population-biomass}
+
+```{r}
+#| label: raw biomass and weight data
+
 weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
@@
 
+@fig-functional-response-to-temperature shows the response of food ingested to temperature, and the food provided in response.
+
 ```{r}
 #| label: fig-functional-response-to-temperature
-#| eval: false
-#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dashed line), relative to maximum potential ingestion.
+#| fig-cap: Temperature changes in potential ingestion (solid line) and amount of food provided (dotted line), relative to maximum potential ingestion.
+The vertical dotted lines show the actual minimum and maximum daily temperatures experienced by farms represented in the model.
+
+tar_load(farm_ts_data)
+min_T <- min(farm_ts_data$temp_c)
+max_T <- max(farm_ts_data$temp_c)
 
@@
 
+max_ing <- max(func_T_resp$ing_act)
+
 func_T_resp %>% 
-  ggplot(aes(x = water_temp, y = ing_act)) +
+  ggplot(aes(x = water_temp, y = ing_act/max_ing)) +
   geom_line(linewidth = 0.75) +
-  geom_line(aes(y = food_prov), linewidth = 0.75, linetype = "dotted") +
+  geom_line(aes(y = food_prov/max_ing), linewidth = 0.75, linetype = "dotted") +
+  geom_vline(xintercept = min_T, linetype = "dotted") +
+  geom_vline(xintercept = max_T, linetype = "dotted") +
   # scale_y_continuous(breaks = seq(0,1.5,0.25)) +
@@
 #| label: patchwork-map-mercator
+#| eval: false
 #| fig-cap: |

### 2025-07-28 index.qmd
Feed details

@@
   mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
-         feed = factor(feed, levels = c("reference", "past", "future")),
+         feed = as.factor(feed),
          total_r = total * 100 %>% round(1),
@@
 
-| Feed | Protein (%, %) | Lipid (%, %) | Carbohydrate (%, %) |
+| Feed | Protein | Lipid | Carbohydrate |
 |------|:----------:|:----------:|:----------:|
-| Plant-dominant | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$digest, 1)`) | 
-                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$digest, 1)`) | 
-                   `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$digest, 1)`) |
-| Marine-dominant | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$digest, 1)`) | 
-                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$digest, 1)`) | 
-                    `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$digest, 1)`) |
-| Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`) | 
-                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`) | 
-                    `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)` (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`) |
+| Plant-dominant | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$digest, 1)`%) |
+| Marine-dominant | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$digest, 1)`%) |
+| Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`%) |
+: Feed macronutrient details (composition in feed, digestibility).
 
-# Model sensitivity to parameter changes {#param-sensitivity}
+## Model sensitivity to parameter changes {#sec-param-sensitivity}
 

### 2025-07-28 index.qmd
Clean up structure

@@
 
-## Main analysis
+## Main scripts
 
-The main analysis for this project focuses on the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.
+The main scripts for this project focus on setting up the model to examine the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.
 
@@
 
-## Extra analysis
+## Extra scripts
 
-The extra analyses for this project involved some exploration into potential impacts of nutrient losses. This will likely not make it into the final manuscript.
+The extra scripts for this project involved some exploration into potential impacts of nutrient losses. These will likely not make it into the final manuscript.
 
@@
 
-# Model functioning
+# Supplemental methods {#sec-supp-methods}
 
@@
 
-fnms <- output_growth_data_path %>% 
-  list.files(full.names = T) %>% 
-  str_subset("reference")
-
-df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
-  as.data.frame() %>% 
-  mutate(mean = set_units(mean, "g") %>% set_units("t"),
-         sd = set_units(sd, "g") %>% set_units("t")) %>% 
+df <- find_read(output_model_farm_path, "dw_") %>% 
+  mutate(
+    mean = set_units(mean, "g") %>% set_units("t"),
+    sd = set_units(sd, "g") %>% set_units("t")
+  ) %>% 
   select(-farm_ID)
@@
   filter(t %in% min_t:max_t) %>% 
-  mutate(sd = sd/mean) %>% 
   group_by(t) %>% 
-  reframe(sd = sqrt(sum(sd^2)),
+  reframe(
+    sd_mean = sqrt(sum(sd_mean^2)),
     mean = sum(mean),
-          sd = sd*mean) %>% 
-  mutate(cohort = "all",
-         split = "Totalled")
+    sd = sd_mean*mean
+  ) %>% 
+  mutate(
+    cohort = "all",
+    split = "Totalled"
+  )
 
@@
 
-# Modelled experimental feeds {#sec-feeds}
+## Modelled experimental feeds {#sec-feeds}
 
@@
 
-# Inputs {#inputs}
-
-```{r}
-#| label: farm-geometry
-
-farm_geometry <- find_read(output_farm_data_path, "farm_geometry")
-```
+# Results {#sec-results}
 
@@
 
-# Code and packages used
+# Code and packages used {#sec-code}
 

### 2025-07-30 06_run_atlantic_salmon_model.qmd
Finishing up run script

--- 2025-07-23 06_run_atlantic_salmon_model.qmd
@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% str_subset("map", negate = T) %>% walk(source)
 ```
@@
 targets::tar_load(test_reference_feed)
-test_reference_feed # should be ~1430 g
+test_reference_feed # should be ~1430 g, or really anything other than 0
 
@@
 targets::tar_make(
-  names = "sens_results_spec",
-  seconds_meta_append = 120
+  seconds_meta_append = 120,
+  callr_function = NULL
   )
@@
 
+qs::qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))
+
 sens_measures <- levels(sens_results$measure)
-sens_results_files <- file.path(output_sens_data_path, paste0("sens_results_", sens_measures, ".qs"))
 sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
@@
 for (sm in seq_along(sens_measures)) {
-  sens_results %>% 
-    filter(measure == sens_measures[sm]) %>% 
-    qsave(sens_results_files[sm])
-
   p <- sens_results %>% 
@@
 
-Note that this also takes a long time - each branch of farmrun takes ~4.5 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
+Note that this takes a long time - each branch of farmrun takes ~5.3 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
 
@@
 targets::tar_validate()
-# targets::tar_visnetwork(targets_only = T)
-# targets::tar_outdated()
-targets::tar_make(farm_results, seconds_meta_append = 90)
+targets::tar_outdated()
+targets::tar_prune()
+
+# Pre-run to reduce load
+targets::tar_make(
+  names = !c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
+  seconds_meta_append = 90,
+  callr_function = NULL
+)
+
+# Run results
+targets::tar_make(
+  names = c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
+  seconds_meta_append = 90,
+  shortcut = T,
+  callr_function = NULL
+)
+
 meta <- targets::tar_meta() %>% 
   filter(grepl("farm_run", name))
-meta$seconds %>% mean()/60
+meta$seconds %>% mean()/60 # average minutes per target
+```
+
+Load objects from the targets pipeline and save them as .qs files, which are much quicker to load down the line. This takes a few minutes to gather all the targets.
+
+```{r}
+#| label: all-farms-cohorts-results
+
+targets::tar_load(stat_names)
+targets::tar_load(farm_IDs)
+targets::tar_load(feed_names)
+
+print("Loading farm results...")
+targets::tar_load(farm_results)
+for (stat_name in stat_names) {
+  farm_results %>% 
+      filter(measure == stat_name) %>% 
+      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
+}
+rm(farm_results)
+
+print("Loading cohort results...")
+targets::tar_load(cohort_results)
+for (stat_name in stat_names) {
+  cohort_results %>% 
+      filter(measure == stat_name) %>% 
+      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
+}
+rm(cohort_results)
+
+targets::tar_load(biomass_produced)
+qsave(biomass_produced, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
 ```
@@
 ```{r}
-#| label: farm-run-results
 
-targets::tar_load(cohort_results)
 ```

### 2025-07-30 src/functions.R
Sum across production period functions

@@ -1,7 +1,15 @@
+suppressPackageStartupMessages(suppressWarnings({
+# These packages are called here so that renv doesn't clean them
 library(devtools)
+library(yaml)
+library(gitcreds)
+
 library(qs)
 library(arrow)
 library(stringr)
+library(units)
+library(magrittr)
+}))
 
 make_label <- function(lab){lab %>% str_remove_all("_stat") %>% str_replace_all("_", " ") %>% str_to_title()}
 fixnum <- function(n, digits = 4) {
@@ -32,7 +40,7 @@ cite_packages <- function(packages) {
   # Generate citations for each package
   citations <- sapply(packages, function(pkg) {
     version <- packageVersion(pkg)
-    paste0("`", pkg, "`, version ", version, " [@", pkg, "]")
+    paste0("`", pkg, "` version ", version, " [@", pkg, "]")
   })
   
   # Handle different cases based on number of packages
@@ -141,4 +149,36 @@ prettyplot <- function() {
           text = element_text(family = "serif", size = 12, colour = "black"),
           axis.title.x = element_text(vjust = 0.5),
           axis.title.y = element_text(hjust = 0.5))
+}
+
+# Sum values across a production period (with units)
+sum_prod <- function(path, pattern) {
+  find_read(path, pattern) %>% 
+    group_by(farm_ID, feed, measure) %>% 
+    reframe(
+      days = n() %>% set_units("d"),
+      total = sum(mean) %>% set_units("g"),
+      sd = sqrt(sumna(sd^2)),
+    ) %>%
+    mutate(
+      total_d = total/days,
+    )
+}
+
+# Convert daily values to daily values per biomass (with units)
+per_biom <- function(path, pattern) {
+  prepped_biomass <- farm_biomass %>% 
+    select(-measure) %>% 
+    rename(biom_mean = mean,
+           biom_sd = sd)
+
+  find_read(path, pattern) %>% 
+    merge(
+      prepped_biomass, 
+      by = c("farm_ID", "feed", "t")
+    ) %>% 
+    mutate(
+      mean_biom = (mean/biom_mean) %>% set_units("g g_fish-1"),
+      sd_biom = ratio_sd(mean, sd, biom_mean, biom_sd)
+    )
 }

### 2025-07-30 src/map_templates.R
Refining plot bounds

@@ -1,3 +1,4 @@
+suppressPackageStartupMessages(suppressWarnings({
 library(devtools)
 library(qs)
 library(dplyr)
@@ -13,24 +14,25 @@ library(rnaturalearth)
 library(rnaturalearthdata)
 library(rnaturalearthhires)
 library(purrr)
+}))
 
 # Define areas -------------------------------------------------
 # For drawing area boxes on the big map
 inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
-  CAN1 = c(-132, -122, 47.75, 54.25),
-  CAN2 = c(-70, -54, 43, 48.5),
+  CAN1 = c(-132, -122, 47.75, 54.1),
+  CAN2 = c(-69, -54.75, 43.25, 48.25),
   EUR = c(-26, 30, 51, 72),
   CHI = c(-77.5, -62.5, -56, -25),
   AUS = c(144, 149.5, -44, -39.75)
 )
 
-# For the corresponding patchwork map lims
+# For the corresponding patchwork map lims, basically the same, just a little refined
 inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
-  CAN1 = c(-132, -122, 48.5, 54),
-  CAN2 = c(-70, -54, 43, 48.5),
+  CAN1 = c(-131.5, -123, 48.25, 54.25),
+  CAN2 = c(-69, -55, 43.5, 48),
   EUR = c(-23, 28.5, 52, 71),
   CHI = c(-78, -62, -55.5, -27),
-  AUS = c(144, 149, -43.75, -40.75)
+  AUS = c(144.25, 148.5, -43.75, -40.75)
 ) %>% 
   map(function(bx) {
     list(
@@ -41,6 +43,7 @@ inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
       )
 })
 
+# Where should the inset labels be positioned in the big map
 labels_spec_robinson <- c(
   CAN1 = "bottom_left_outside", 
   CAN2 = "bottom_right_outside", 
@@ -58,14 +61,14 @@ labels_offset_robinson <- c(
 )
 
 labels_spec_mercator <- list(
-  CAN1 = c(h = -1, v = 0.5), 
-  CAN2 = c(h = 0.5, v = 0.5), 
-  EUR = c(h = -1, v = 0.5), 
-  CHI = c(h = 0, v = 0), 
[…]

### 2025-07-30 src/model_functions.R
Correct sd calculation

@@ -1,23 +1,18 @@
-# nolint start
-
-# These packages are called here so that renv doesn't clean them
-library(devtools)
-library(yaml)
-library(gitcreds)
-
-### Functions modified from Baldan et al 2018 R package for aquaculture. 
+### Main model functions here are modified from Baldan et al 2018 R package for aquaculture. 
 ### https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0195732
 ### https://github.com/cran/RAC/tree/master/R
 
-# Load required packages
+suppressPackageStartupMessages(suppressWarnings({
 library(qs)
-library(qs2) 
+library(qs2)
 library(terra)
 library(readxl)
 library(matrixStats)
 library(furrr)
 library(future)
 library(dplyr)
+library(msm)
+}))
 
 # Parameters definitions
 # species_params['alpha']         [-] Feeding catabolism coefficient
@@ -38,22 +33,6 @@ library(dplyr)
 # species_params['k']             [-] Weight exponent for energy content
 # species_params['eff']           [-] Food ingestion efficiency
 # species_params['fcr']           [-] Food conversion ratio
-
-get_farms <- function(farms_file, farm_ID, this_species){
-  qread(farms_file) %>% 
-    filter(model_name == this_species) %>% 
-    select(-row_num) %>% 
-    mutate(farm_id = row_number()) %>% 
-    filter(farm_id == farm_ID)
-}
-
-get_feed_params <- function(file){
-  df <- read.csv(file, header = F)
-  values <- as.numeric(df$V1)
-  names(values) <- df$V2
-  values <- values[!is.na(values)]
-  return(values)
-}
 
 generate_pop <- function(harvest_n, mort, times) {
   
@@ -84,6 +63,7 @@ feeding_rate <- function(water_temp, species_params) {
     (species_params['betac'] * (species_params['Tma'] - species_params['Toa']))
 }
 
+# Calculate how much food will be provided based on need
 food_prov_rate <- function(pop_params, water_temp, ing_pot, ing_pot_min, species_params) {
   # Use ifelse vectorization instead of individual if statements
   ifelse(
@@ -249,7 +229,7 @@ farm_growth <- function(pop_params, species_params, feed_params, water_temp, tim
   return(out_list)
 }
 
-# This is identical to the farm_growth function except without the Monte-Carlo sampling of initial weights (all uniform)
[…]

### 2025-07-30 targets/_targets_farmruns.R
Final adjustments

@@ -1,14 +1,18 @@
 library(targets)
-library(crew)
+# library(crew)
+library(magrittr)
 
 tar_option_set(
   packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble", "qs"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 14),
+  controller = crew::crew_controller_local(workers = 12, seconds_idle = 300),
   workspace_on_error = TRUE
 )
 
-tar_source(files = list.files("src", pattern = "\\.R$", full.names = TRUE))
+tar_source(
+  files = list.files("src", pattern = "\\.R$", full.names = TRUE) %>% 
+    setdiff("src/map_templates.R")
+)
 
 list(
 # Get previously saved data ---------------------------------------------------------------------------------------
@@ -24,10 +28,10 @@ list(
     farm_IDs,
     command = {
       # c(1:39, 2704:2721) # Australia and US only
-
       qs::qread(farm_ts_data_file) %>% 
+        filter(farm_ID != 2703) %>% # The only Russian farm
         distinct(farm_ID) %>% 
-        pull(farm_ID) #%>% sample(272)
+        pull(farm_ID)
     }
   ),
   tar_target(
@@ -46,7 +50,6 @@ list(
       qs::qread(feed_params_file) %>% names()
       # c("plant_dominant", "marine_dominant")
     }
-    
   ),
   tar_target(
     feed_params,
@@ -107,12 +110,7 @@ list(
         filter(!is.na(weight)) %>% 
         slice_tail(n = 1) %>%
         select(weight) %>%
-        mutate(
-          farm_ID = farm_IDs,
-          weight = weight %>% 
-            units::set_units("g") %>% 
-            units::drop_units()
-        )
+        mutate(farm_ID = farm_IDs)
     },
     pattern = map(farm_IDs, farm_ts_data)
   ),
@@ -144,7 +142,7 @@ list(
         't_start' = min(farm_ts_data$day),
         't_end' = max(farm_ts_data$day),
         'dt' = 1,
-        'nruns' = 5000,
+        'nruns' = 3000, # 3000
         'prod' = farm_production$tonnes_per_farm[farm_production$farm_id == farm_IDs]
       )
     },
@@ -190,55 +188,56 @@ list(
     pattern = cross(map(farm_IDs, N_pop, farm_ID_data, farm_ts_data), map(feed_params, feed_names))
   ),
 
[…]

### 2025-07-30 targets/_targets_sensitivities.R

@@ -24,12 +24,9 @@ list(
     farm_IDs,
     qs::qread(farm_ts_data_file) %>% 
       distinct(farm_ID) %>% 
-      pull(farm_ID)
-  ),
-  tar_target(
-    farm_IDs_sample,
-    farm_IDs %>% 
-      sample(as.integer(length(farm_IDs)*0.1)) #%>% sample(3)
+      filter(farm_ID != 2703) %>% # The only Russian farm
+      pull(farm_ID) %>% 
+      sample(271)
   ),
   tar_target(
     farm_ts_data, 
@@ -198,12 +195,14 @@ list(
   tar_target(
     sens_results_spec,
     command = {
-      cols <- colnames(sens_run_spec_lo)[!colnames(sens_run_spec_lo) %in% c("adj_param", "farm_ID", "factor")]
       sens <- rbind(
         sens_run_spec_lo,
         sens_run_spec_mi,
         sens_run_spec_hi
-      ) %>%
+      ) 
+      cols <- colnames(sens)[!colnames(sens) %in% c("adj_param", "farm_ID", "factor")]
+      
+      sens <- sens %>%
         pivot_longer(
           cols = all_of(cols), 
           names_to = "measure", 
@@ -216,6 +215,7 @@ list(
           names_prefix = "fact_"
         ) %>% 
         mutate(sensitivity = (fact_1.1-fact_0.9)/(0.2*fact_1)) 
+      
       sens %>% 
         group_by(adj_param, measure) %>%
         reframe(
@@ -229,162 +229,149 @@ list(
   tar_target(
     sens_run_pop_lo, 
     command = {
-      # Pre-split farm temperature data for speed
-      farm_ts_list <- filter(farm_ts_data, farm_ID %in% farm_IDs_sample)
-      farm_ts_list <- split(farm_ts_list, farm_ts_list$farm_ID)
+      ts <- filter(farm_ts_data, farm_ID == farm_IDs)
 
       # Adjust params by factor
       adj_params <- all_params
       adj_params[param_names_pop] <- adj_params[param_names_pop] * factors[1]
 
-      purrr::map2(farm_IDs_sample, farm_ts_list, function(farm, ts) {
-        sens <- farm_growth(
-          pop_params = adj_params,
-          species_params = adj_params,
-          water_temp = ts$temp_c,
-          feed_params = reference_feed,
[…]

### 2025-07-30 index.qmd
Latitude sorting of countries

@@
   rename(farm_ID = farm_id)
+
+farm_mean_lat <- farm_locs %>%
+  st_centroid() %>%
+  mutate(latitude = st_coordinates(.)[, "Y"]) %>%
+  st_drop_geometry() %>%
+  group_by(country) %>%
+  summarise(mean_latitude = mean(latitude, na.rm = TRUE)) %>% 
+  arrange(-mean_latitude)
+
+countries <- farm_mean_lat$country
+countries[str_detect(countries, "United States of America")] <- "USA"
+countries[str_detect(countries, "United Kingdom")] <- "UK"
+countries[str_detect(countries, "Russian Federation")] <- "Russia"
+
+farm_locs <- farm_locs %>% 
+  mutate(country = factor(country, levels = farm_mean_lat$country, labels = countries))
 ```

### 2025-07-30 index.qmd
Whole bunch of new analysis

@@
   cache: true
-  freeze: auto
 knitr: 
@@
   "marine_dominant" = "#377EB8",
-  "novel_inclusive" = "#E41A1C"
+  "novel_inclusive" = "#E41A1C",
+  "PD" = "#4DAF4A",
+  "MD" = "#377EB8",
+  "NI" = "#E41A1C"
 )
@@
 #| label: fig-cohorts
-#| eval: false
 #| fig-cap: | 
@@
 
-df <- find_read(output_model_farm_path, "dw_") %>% 
-  mutate(
-    mean = set_units(mean, "g") %>% set_units("t"),
-    sd = set_units(sd, "g") %>% set_units("t")
+farm_biomass <- find_read(output_model_farm_path, "biomass_stat") %>% 
+  filter(farm_ID == 722 & feed == "plant_dominant")
+
+cohort_biomass_split <- rbind(
+  farm_biomass %>% 
+    farm_to_cohort() %>% 
+    mutate(cohort = 1),
+  farm_biomass %>% 
+    farm_to_cohort(time_offset = 365) %>% 
+    mutate(cohort = 2),
+  farm_biomass %>% 
+    farm_to_cohort(time_offset = 730) %>% 
+    mutate(cohort = 3)
 ) %>% 
-  select(-farm_ID)
+  mutate(split = 0) %>% 
+  relocate(farm_ID, .before = t) %>% 
+  relocate(feed, .before = t)
 
-df <- rbind(
-  df %>% mutate(cohort = 1),
-  df %>% mutate(t = t+365, cohort = 2),
-  df %>% mutate(t = t+730, cohort = 3)
-) %>% 
-  mutate(t = (t-min(t))+1,
-         split = "Split by cohort")
+cohort_biomass <- find_read(output_model_cohort_path, "biomass_stat") %>% 
+  filter(farm_ID == 722 & feed == "plant_dominant") %>% 
+  mutate(cohort = "all", split = 1)
 
-min_t <- min(df$t[df$cohort == 2])
-max_t <- max(df$t[df$cohort == 2])
-
-df_2 <- df %>% 
-  filter(t %in% min_t:max_t) %>% 
-  group_by(t) %>% 
-  reframe(
-    sd_mean = sqrt(sum(sd_mean^2)),
-    mean = sum(mean),
-    sd = sd_mean*mean
+rbind(
+  cohort_biomass_split,
+  cohort_biomass
   ) %>% 
   mutate(
-    cohort = "all",
-    split = "Totalled"
-  )
-
-df <- rbind(df, df_2) %>% 
-  mutate(cohort = as.factor(cohort))
-
-ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
+    t = t-min(t)+1,
+    mean = mean %>% set_units("g") %>% set_units("t"),
+    sd = sd %>% set_units("g") %>% set_units("t")
+  ) %>% 
+  ggplot(aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
   geom_line(linewidth = 0.75) +
@@
   prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank()) +
   labs(y = "Farm biomass", x = "Day of production")
@@
 
+Sys.setenv(TAR_PROJECT = "project_farmruns")
 tar_load(farm_ts_data)
@@
 Parameter sensitivity was tested by varying each parameter by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-All parameters in Table @tbl-params were tested.
-The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.
+The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10 (@fig-sensitivity-results).
 
-```{r salmon-param-names}
-#| code-summary: Get parameter and sensitivity data
+```{r}
+#| label: salmon-param-names
 
-params <- file.path(output_species_data_path, "sens_params.qs") %>% qs::qread()
+params <- find_read(output_species_data_path, "sens_params")
 
@@
 ```{r}
-#| label: sens-results
+#| label: fig-sensitivity-results
+#| fig-cap: Sensitivity of individual fish weight (blue) and total farm excretion (red) to a 10% increase in each model parameter.
+Bars show mean values, error bars show standard deviation between farms.
+#| fig-width: 8
 
-sens_results_files <- file.path(output_sens_data_path) %>% 
-  list.files(full.names = T) %>% 
-  str_subset("results")
+sens_results <- find_read(output_sens_data_path, "sens_results") %>% 
+  filter(measure %in% c("total_excr", "weight") & adj_param != "nruns") %>% 
+  mutate(measure = droplevels(measure))
+
+sens_results %>% 
+  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens, fill = measure)) +
+  geom_col(position = position_dodge(), width = 0.95, alpha = 0.65, colour = "black") +
+  geom_errorbar(position = position_dodge(width = 0.95), width = 0.5) +
+  coord_flip() +
+  prettyplot() +
+  scale_x_discrete(breaks = param_names$name, labels = param_names$lab) +
+  scale_y_continuous(breaks = seq(-10, 30, 5)) +
+  scale_fill_brewer(palette = "Set1") +
+  labs(y = "Sensitivity", x = "Adjusted parameter")
 ```
@@
 
+## Biomass produced and feed provided
+
 ```{r}
-#| label: input-data
+#| label: fig-biom-prod-comparison
+#| fig-caption: Percentage difference in the biomass produced by farms fed the marine-dominant feed (blue) or the novel-inclusive feed (red), in comparison to the plant-dominant feed.
+#| class-chunk: aside
 
-ins_P <- list.files(per_biomass_cohort_path, full.names = T) %>% 
-  str_subset("P_uneat|P_excr") %>% 
-  purrr::map(function(nm) {qs::qread(nm)}) %>% 
-  bind_rows()
+biomass_produced <- find_read(output_model_farm_path, "biomass_produced_all_farms") %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID")
 
-ins_tot <- list.files(per_biomass_cohort_path, full.names = T) %>% 
-  str_subset("total_uneat|total_excr") %>% 
-  purrr::map(function(nm) {qs::qread(nm)}) %>% 
-  bind_rows()
+biomass_produced <- biomass_produced %>% 
+  select(-sd, -prod_t) %>% 
+  mutate(feed = factor(feed, labels = c("MD", "PD", "NI"))) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(MD = (MD-PD)/PD,
+         NI = (NI-PD)/PD) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    cols = c(MD, NI), 
+    names_to = "feed", 
+    names_transform = list(feed = as.factor),
+    values_to = "perc_diff"
+  )
+
+bps <- biomass_produced %>% 
+  group_by(feed) %>% 
+  reframe(
+    diff = mean(perc_diff),
+    sd = sd(perc_diff),
+    ) %>% 
+  mutate(
+    sign = case_when(diff < 0 ~ "less", T ~ "more"),
+    diff = round(100*diff, 2),
+    sd = round(100*sd, 2),
+    abs_diff = abs(diff)
+  )
+
+biomass_produced %>% 
+  ggplot(aes(x = country, y = 100*perc_diff, fill = feed)) +
+  geom_boxplot() +
+  scale_fill_manual(values = feed_pal) +
+  prettyplot() +
+  labs(x = "Country", y = "% difference")
 ```
 
-## Total inputs (uneaten and excreted)
-
-### Through time
+Overall, when farms were fed the marine-dominant feed they produced `r bps$abs_diff[bps$feed == "MD"]`% `r bps$sign[bps$feed == "MD"]` ($\pm$ `r bps$sd[bps$feed == "MD"]`%) biomass with the same population, and when farms were fed the novel-inclusive feed they produced `r bps$abs_diff[bps$feed == "NI"]`% `r bps$sign[bps$feed == "NI"]` ($\pm$ `r bps$sd[bps$feed == "NI"]`%) biomass than when fed the plant-dominant feed (@fig-biom-prod-comparison).
 
 ```{r}
-#| label: fig-uneat-excr-plot-ts
-#| fig-cap: Initial look at excreted and uneaten through time
+#| label: feed-prov-comparison
 
-ins_tot %>% 
-  mutate(t = t-365) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  group_by(country, feed, t, measure) %>% 
+feed_provided <- sum_prod(output_model_farm_path, "food_prov") %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID")
+
+feed_provided <- feed_provided %>% 
+  select(-sd, -total_d) %>% 
+  mutate(feed = factor(feed, labels = c("MD", "PD", "NI"))) %>% 
+  pivot_wider(names_from = feed, values_from = total) %>% 
+  mutate(MD = (MD-PD)/PD,
+         NI = (NI-PD)/PD) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    cols = c(MD, NI), 
+    names_to = "feed", 
+    names_transform = list(feed = as.factor),
+    values_to = "perc_diff"
+  ) %>% 
+  mutate(perc_diff = perc_diff %>% drop_units())
+
+fps <- feed_provided %>% 
+  group_by(feed) %>% 
   reframe(
-    sd_perbiom = sd(mean_perbiom),
-    mean_perbiom = mean(mean_perbiom)
+    diff = mean(perc_diff),
+    sd = sd(perc_diff),
     ) %>% 
   mutate(
-    mean_perbiom = mean_perbiom %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    sd_perbiom = sd_perbiom %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1")
-  ) %>% 
-  ggplot(aes(
-    x = t, 
-    y = drop_units(mean_perbiom), 
-    ymin = drop_units(mean_perbiom-sd_perbiom), 
-    ymax = drop_units(mean_perbiom+sd_perbiom), 
-    colour = feed, 
-    fill = feed
-  )) +
-  geom_line() +
-  geom_ribbon(alpha = 0.25) +
-  facet_grid(
-    rows = vars(country),
-    cols = vars(measure),
-    scales = "free"
-  ) +
-  prettyplot() +
-  scale_colour_manual(values = feed_pal) +
-  scale_fill_manual(values = feed_pal) +
-  scale_y_continuous(
-    name = expression("Loss (kg g"^-1*")"),
-    breaks = seq(0, 1, 0.2)
+    sign = case_when(diff < 0 ~ "less", T ~ "more"),
+    diff = round(100*diff, 2),
+    sd = round(100*sd, 2),
+    abs_diff = abs(diff)
   )
@@
 
+Farms were therefore provided `r fps$abs_diff[fps$feed == "MD"]`% `r fps$sign[fps$feed == "MD"]` ($\pm$ `r fps$sd[fps$feed == "MD"]`%) feed when fed the marine-dominant feed, and `r fps$abs_diff[fps$feed == "NI"]`% `r fps$sign[fps$feed == "NI"]` ($\pm$ `r fps$sd[fps$feed == "NI"]`%) feed when fed the novel-inclusive feed compared to the plant-dominant feed (@fig-feedprov-comparison).
+
 ```{r}
-#| label: uneat-excr-plot-perc-diff
+#| label: fig-feedprov-comparison
+#| fig-cap: Percentage difference in the total feed provided when farms were fed the marine-dominant feed (blue) or the novel-inclusive feed (red), in comparison to the plant-dominant feed.
+#| class-chunk: aside
 
-tmp <- ins_tot %>% 
-  mutate(t = t-365) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  dplyr::select(-c(mean, sd_mean, sd, biom_mean, biom_sd, biom_sd_mean, sd_perbiom)) %>% 
-  group_by(country, t, measure) %>% 
-  pivot_wider(
-    names_from = feed, 
-    values_from = mean_perbiom
+feed_provided %>% 
+  ggplot(aes(x = country, y = 100*perc_diff, fill = feed)) +
+  geom_boxplot() +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal) +
+  labs(x = "Country", y = "Mean feed provided (kg/kg salmon)")
+```
+
+```{r}
+#| label: feed-uneat-comparison
+
+uneaten_feed <- sum_prod(output_model_farm_path, "total_uneat") %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID")
+
+uneaten_feed <- uneaten_feed %>% 
+  select(-sd, -total_d) %>% 
+  mutate(feed = factor(feed, labels = c("MD", "PD", "NI"))) %>% 
+  pivot_wider(names_from = feed, values_from = total) %>% 
+  mutate(MD = (MD-PD)/PD,
+         NI = (NI-PD)/PD) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    cols = c(MD, NI), 
+    names_to = "feed", 
+    names_transform = list(feed = as.factor),
+    values_to = "perc_diff"
+  ) %>% 
+  mutate(perc_diff = perc_diff %>% drop_units())
+
+ufs <- uneaten_feed %>% 
+  group_by(feed) %>% 
+  reframe(
+    diff = mean(perc_diff),
+    sd = sd(perc_diff),
     ) %>% 
   mutate(
-    diff = plant_dominant - marine_dominant,
-    perc_diff = diff/plant_dominant
-  ) %>%
-  group_by(country, t, measure) %>% 
-  reframe(
-    mean_diff = mean(diff),
-    mean_perc_diff = mean(perc_diff),
-    sd_diff = sd(diff),
-    sd_perc_diff = sd(perc_diff)
-  )
-
-tmp <- tmp %>% 
-  group_by(measure, country) %>% 
-  reframe(
-    mean_t_perc_diff = mean(mean_perc_diff),
-    sd_t_perc_diff = sd(mean_perc_diff)
+    sign = case_when(diff < 0 ~ "less", T ~ "more"),
+    diff = round(100*diff, 3),
+    sd = round(100*sd, 2),
+    abs_diff = abs(diff)
   )
@@
 
-While the actual difference in excreted and uneaten feed (total loss) varied between countries and through time (@fig-uneat-excr-plot-ts), relative changes between the feeds remained consistent. 
-In both the US and Australia (all done so far), total excreted faeces was 
-`r round(100*tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`%) higher in the plant-dominant feed.
-Differences in total uneaten feed were much smaller at 
-`r round(100*-tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`%) lower in the plant-dominant feed.
+Consequently, farms lost `r ufs$abs_diff[ufs$feed == "MD"]`% `r ufs$sign[ufs$feed == "MD"]` ($\pm$ `r ufs$sd[ufs$feed == "MD"]`%) uneaten feed when fed the marine-dominant feed and `r ufs$abs_diff[ufs$feed == "NI"]`% `r ufs$sign[ufs$feed == "NI"]` ($\pm$ `r ufs$sd[ufs$feed == "NI"]`%) uneaten feed when fed the novel-inclusive feed compared to the plant-dominant feed.
 
-### At harvest
+### Summary
+
+| Feed | Change in biomass produced | Change in feed provided | Change in uneaten feed lost |
+|----------|-----|-----|-----|
+| Marine-dominant | `r bps$diff[bps$feed == "MD"]` | `r fps$diff[fps$feed == "MD"]` | `r ufs$diff[ufs$feed == "MD"]` |
+| Novel-inclusive | `r bps$diff[bps$feed == "NI"]` | `r fps$diff[fps$feed == "NI"]` | `r ufs$diff[ufs$feed == "NI"]` |
+
+# Inputs
+
+## Total inputs (mass)
 
 ```{r}
-#| label: uneat-excr-plot-end
-#| fig-cap: Caption
+#| label: total-inputs
 
-ins_tot %>% 
-  group_by(farm_ID) %>%
-  arrange(farm_ID, t) %>%
+# Total inputs, all times
+total_uneaten <- find_read(output_model_cohort_path, "total_uneat")
+total_excreted <- find_read(output_model_cohort_path, "total_excr")
+
+total_inputs <- rbind(total_uneaten, total_excreted) %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID") %>% 
+  select(-c(sd)) %>% 
+  pivot_wider(names_from = measure, values_from = mean, id_cols = c(farm_ID, feed, country, prod_t)) %>% 
+  mutate(perc_excr = total_excr_stat/(total_excr_stat+total_uneat_stat)) %>% 
+  select(-c(total_excr_stat, total_uneat_stat))
+
+# Total inputs, summed across production period
+total_uneaten_sum <- sum_prod(output_model_farm_path, "total_uneat")
+total_excreted_sum <- sum_prod(output_model_farm_path, "total_excr")
+
+total_inputs_sum <- rbind(total_uneaten_sum, total_excreted_sum) %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID") %>% 
+  select(-c(sd)) %>% 
+  pivot_wider(names_from = measure, values_from = total, id_cols = c(farm_ID, feed, country)) %>% 
+  mutate(perc_excr = total_excr_stat/(total_excr_stat+total_uneat_stat)) %>% 
+  select(-c(total_excr_stat, total_uneat_stat))
+
+tis <- total_inputs_sum %>% 
   mutate(
-    cumsum_mean = cumsum(mean_perbiom) %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    end_t = max(t)
-    ) %>% 
-  ungroup() %>% 
-  filter(t == end_t) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
-  geom_boxplot() +
-  facet_grid(cols = vars(measure)) +
-  prettyplot() +
-  scale_fill_manual(values = feed_pal)
+    perc_excr = drop_units(perc_excr),
+    feed = factor(
+      feed, 
+      levels = c("marine_dominant", "novel_inclusive", "plant_dominant"), 
+      labels = c("MD", "NI", "PD")
+    )
+  )
 ```
 
-## N inputs
+Total farm inputs (excreted matter and uneaten feed) were on average composed of
+`r round(100*mean(tis$perc_excr[tis$feed == "PD"]), 1)`% ($\pm$ `r round(100*sd(tis$perc_excr[tis$feed == "PD"]), 2)`%) excreted matter (`r 100-round(100*mean(tis$perc_excr[tis$feed == "PD"]), 1)`% uneaten feed) when farms were fed the plant-dominant feed,
+`r round(100*mean(tis$perc_excr[tis$feed == "MD"]), 1)`% ($\pm$ `r round(100*sd(tis$perc_excr[tis$feed == "MD"]), 2)`%) excreted matter (`r 100-round(100*mean(tis$perc_excr[tis$feed == "MD"]), 1)`% uneaten feed) when farms were fed the marine-dominant feed,
+`r round(100*mean(tis$perc_excr[tis$feed == "NI"]), 1)`% ($\pm$ `r round(100*sd(tis$perc_excr[tis$feed == "NI"]), 2)`%) excreted matter (`r 100-round(100*mean(tis$perc_excr[tis$feed == "MD"]), 1)`% uneaten feed) when farms were fed the novel-inclusive feed.
 
 ```{r}
-#| label: N-loss-plot-total
-#| fig-cap: Caption
+#| label: input-glimpse
+#| eval: false
 
-ins_P %>% 
-  group_by(farm_ID) %>%
-  arrange(farm_ID, t) %>%
+total_inputs_sum %>% 
+  ggplot(aes(x = country, y = perc_excr, fill = feed)) +
+  geom_boxplot()
+
+total_inputs_sum %>% 
+  filter(country == "Canada") %>% 
+  ggplot(aes(x = perc_excr)) +
+  geom_histogram()
+```
+
+```{r}
+#| label: fig-total-inputs-through-time
+#| class-chunk: aside
+
+total_inputs_tt <- rbind(total_uneaten, total_excreted) %>% 
+  merge(st_drop_geometry(farm_locs), by = "farm_ID") %>% 
+  mutate(measure = droplevels(measure),
+         feed = factor(
+           feed,
+           levels = c("marine_dominant", "novel_inclusive", "plant_dominant"),
+           labels = c("MD", "NI", "PD")
+         )) %>%
+  group_by(country, feed, prod_t, measure) %>% 
+  reframe(
+    # sd = sqrt(sumna(sd^2)),
+    mean = meanna(mean)
+  ) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(MD = (MD-PD)/PD,
+         NI = (NI-PD)/PD) %>% 
+  select(-PD) %>% 
+  pivot_longer(cols = c(MD, NI), names_to = "feed", values_to = "perc_diff", names_transform = list(feed = as.factor))
+
+# Shows that % change in uneaten/excreted feed between feeds is very consistent through time
+total_inputs_tt %>%
+  ggplot(aes(x = prod_t, y = perc_diff, colour = country, linetype = feed)) +
+  geom_line(linewidth = 0.75) +
+  facet_wrap(vars(measure)) +
+  prettyplot() +
+  theme(legend.position = "bottom")
+```
+
+The difference between feeds in the uneaten feed and excreted matter lost remained relatively consistent through time for each farm (@fig-total-inputs-through-time).
+
+```{r}
+#| label: total-inputs-map-data
+
+total_inputs_sum <- rbind(total_uneaten_sum, total_excreted_sum) %>% 
+  select(-c(sd)) %>% 
   mutate(
-    cumsum_mean = cumsum(mean_perbiom)*6.25 %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    end_t = max(t)
+    feed = factor(feed, levels = c("marine_dominant", "novel_inclusive", "plant_dominant"), labels = c("MD", "NI", "PD"))
     ) %>% 
-  ungroup() %>% 
-  filter(t == end_t) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
-  geom_boxplot() +
-  facet_grid(cols = vars(measure)) +
+  pivot_wider(
+    names_from = feed,
+    values_from = total,
+    id_cols = c(farm_ID, measure)
+  ) %>% 
+  mutate(
+    MD = (MD-PD)/PD,
+    NI = (NI-PD)/PD
+  ) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    cols = c(MD, NI),
+    names_to = "feed", names_transform = list(feed = as.factor),
+    values_to = "perc_diff", values_transform = list(perc_diff = drop_units)
+  ) %>% 
+  merge(farm_locs, by = "farm_ID") %>% 
+  st_as_sf()
+```
+
+Differences spatially:
+
+* It looks like the marine-dominant feed overall results in less inputs (higher digestibility)
+* It is interesting that the changes due to switching to the marine-dominant feed seem so random spatially
+* However the changes in the novel-inclusive feed are less variable, probably because the novel-inclusive feed is very similar to the plant-dominant feed.
+
+```{r}
+#| label: fig-total-inputs-big-map
+#| fig-width: 8.5
+#| fig-height: 10
+#| fig-cap: Percentage difference in total inputs when farms are fed the marine-dominant feed (top) or the novel-inclusive feed (bottom).
+
+p_bigmap_robinson +
+  geom_sf(
+    data = total_inputs_sum, 
+    aes(colour = 100*perc_diff, geometry = geometry), 
+    size = 2
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", limits = c(-30, 10)) +
+  guides(col = guide_colourbar(
+    title = expression("% Change in total inputs (from PD feed)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  facet_grid(rows = vars(feed)) +
   prettyplot() +
-  scale_fill_manual(values = feed_pal)
+  theme(strip.background = element_blank(), strip.text = element_blank(),
+        axis.title = element_blank(),
+        legend.position = "bottom")
+```
+
+```{r}
+#| label: total-inputs-patchwork-map
+#| cache: false
+
+p_mercator <- p_bigmap_mercator + 
+  geom_sf(
+    data = total_inputs_sum,
+    # data = filter(total_inputs_sum, feed == "MD"), 
+    aes(colour = 100*perc_diff, geometry = geometry), 
+    size = 2
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", limits = c(-30, 10)) +
+  facet_grid(cols = vars(feed)) +
+  prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank()) +
+  labs(y = "Latitude", x = "Longitude")
+
+ins <- get_insets_mercator(p_mercator)
+```
+
+```{r}
+#| label: fig-total-inputs-patchwork-map-CAN1
+#| fig-cap: Change in total inputs (west Canada)
+#| cache: false
+
+ins[[1]]
+```
+
+```{r}
+#| label: fig-total-inputs-patchwork-map-CAN2
+#| fig-cap: Change in total inputs (east Canada)
+#| cache: false
+
+ins[[2]]
+```
+
+```{r}
+#| label: fig-total-inputs-patchwork-map-EUR
+#| fig-cap: Change in total inputs (Europe)
+#| cache: false
+
+ins[[3]]
+```
+
+```{r}
+#| label: fig-total-inputs-patchwork-map-CHI
+#| fig-cap: Change in total inputs (Chile)
+#| cache: false
+
+ins[[4]]
+```
+
+```{r}
+#| label: fig-total-inputs-patchwork-map-AUS
+#| fig-cap: Change in total inputs (Australia)
+#| cache: false
+
+ins[[5]]
+```
+
+# N inputs
+
+```{r}
+#| label: N-inputs-map-data
+
+N_uneaten_sum <- sum_prod(output_model_farm_path, "P_uneat") %>% 
+  mutate(total = total * 6.25)
+N_excreted_sum <- sum_prod(output_model_farm_path, "P_excr") %>% 
+  mutate(total = total * 6.25)
+
+N_inputs_sum <- rbind(N_uneaten_sum, N_excreted_sum) %>% 
+  select(-c(sd, total_d)) %>% 
+  mutate(
+    feed = factor(feed, 
+                  levels = c("marine_dominant", "novel_inclusive", "plant_dominant"), 
+                  labels = c("MD", "NI", "PD"))
+    ) %>% 
+  pivot_wider(
+    names_from = feed,
+    values_from = total,
+    id_cols = c(farm_ID, measure)
+  ) %>% 
+  mutate(
+    MD = (MD-PD)/PD,
+    NI = (NI-PD)/PD
+  ) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    cols = c(MD, NI),
+    names_to = "feed", names_transform = list(feed = as.factor),
+    values_to = "perc_diff", values_transform = list(perc_diff = drop_units)
+  ) %>% 
+  merge(farm_locs, by = "farm_ID") %>% 
+  st_as_sf()
+```
+
+```{r}
+#| label: fig-N-inputs-boxplot
+
+N_inputs_sum_raw_0 <- rbind(N_uneaten_sum, N_excreted_sum) %>% 
+  select(-c(sd)) %>% 
+  mutate(
+    total_d = (total_d * 6.25) %>% set_units("kg d-1"),
+    feed = factor(feed, 
+                  levels = c("marine_dominant", "plant_dominant", "novel_inclusive"), 
+                  labels = c("MD", "PD", "NI"))
+    ) %>% 
+  merge(farm_locs, by = "farm_ID") %>% 
+  group_by(country, feed, measure) %>% 
+  reframe(mean = mean(total_d))
+
+N_inputs_sum_raw_1 <- N_inputs_sum_raw_0 %>% 
+  group_by(country, feed) %>% 
+  reframe(mean = sum(mean))
+
+N_inputs_sum_raw_0 <- N_inputs_sum_raw_0 %>% 
+  filter(measure == "P_excr_stat")
+
+ggplot(N_inputs_sum_raw_0, aes(x = country, y = mean, fill = feed)) +
+  geom_col(position = position_dodge(), width = 0.95, colour = "black", alpha = 0.75) +
+  geom_col(
+    data = N_inputs_sum_raw_1,
+    position = position_dodge(), width = 0.95, colour = "black", alpha = 0.25
+  ) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal) +
+  labs(x = "Country", y = "N inputs")
+```
+
+```{r}
+#| label: fig-N-inputs-big-map
+#| fig-width: 8.5
+#| fig-height: 10
+#| fig-cap: Percentage difference in N inputs when farms are fed the marine-dominant feed (top) or the novel-inclusive feed (bottom).
+
+p_bigmap_robinson +
+  geom_sf(data = total_inputs_sum, aes(colour = 100*perc_diff, geometry = geometry), size = 2) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", limits = c(-30, 10)) +
+  guides(col = guide_colourbar(
+    title = expression("% Change in N inputs (from PD feed)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  facet_grid(rows = vars(feed)) +
+  prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank(),
+        axis.title = element_blank(),
+        legend.position = "bottom")
+```
+
+```{r}
+#| label: N-inputs-patchwork-map
+#| cache: false
+
+p_mercator <- p_bigmap_mercator + 
+  geom_sf(data = N_inputs_sum, aes(colour = 100*perc_diff, geometry = geometry), size = 2) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", limits = c(-30, 10)) +
+  facet_grid(cols = vars(feed)) +
+  prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank()) +
+  labs(y = "Latitude", x = "Longitude")
+
+ins <- get_insets_mercator(p_mercator)
+```
+
+```{r}
+#| label: fig-N-inputs-patchwork-map-CAN1
+#| fig-cap: Change in N inputs (west Canada)
+#| cache: false
+
+ins[[1]]
+```
+
+```{r}
+#| label: fig-N-inputs-patchwork-map-CAN2
+#| fig-cap: Change in N inputs (east Canada)
+#| cache: false
+
+ins[[2]]
+```
+
+```{r}
+#| label: fig-N-inputs-patchwork-map-EUR
+#| fig-cap: Change in N inputs (Europe)
+#| cache: false
+
+ins[[3]]
+```
+
+```{r}
+#| label: fig-N-inputs-patchwork-map-CHI
+#| fig-cap: Change in N inputs (Chile)
+#| cache: false
+
+ins[[4]]
+```
+
+```{r}
+#| label: fig-N-inputs-patchwork-map-AUS
+#| fig-cap: Change in N inputs (Australia)
+#| cache: false
+
+ins[[5]]
 ```

### 2025-08-01 09_data_analysis.qmd
Analysis updates

---
title: "Process data from Atlantic salmon model runs"
format: html
editor: source
---

# Introduction

The purpose of this script is to take the raw model outputs and save them as files which answer (or go towards answering) specific questions. These files can then be directly called by index.qmd to quickly create plots or text summaries.

```{r}
#| label: setup
#| warning: false
#| message: false

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% 
  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
  str_subset("map", negate = T) %>% 
  walk(source)

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")
install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")
```

It becomes necessary at this point to explicitly declare the units of some outputs, and make clear whether they refer to individual fish within a farm (mean across nruns) or the whole farm (individual fish x population).

| Stat name | Unit | Description | Level |
|-------|-----|------------------------------------|
weight        | g | Mean weight of an individual fish within a farm | Individual |
dw            | g | Mean daily weight change per individual within a farm | Individual |
water_temp    | $^{\circ}$C | Mean daily temperature on farm | Farm |
T_response    | - | Temperature response of all fish within a farm (identical for all fish in a farm) | Farm |
P_excr        | g | Total excreted protein from the entire farm | Farm |
L_excr        | g | Total excreted lipid from the entire farm | Farm |
C_excr        | g | Total excreted carbohydrate from the entire farm | Farm |
P_uneat       | g | Total uneaten protein from the entire farm | Farm |
L_uneat       | g | Total uneaten lipid from the entire farm | Farm |
C_uneat       | g | Total uneaten carbohydrate from the entire farm | Farm |
food_prov     | g | Total food provided to the entire farm | Farm |
food_enc      | g | Total food encountered by each individual fish | Individual |
rel_feeding   | - | Temperature-driven relative feeding rate (identical for all fish in a farm) | Farm |
ing_pot       | g | Total ingestion potential of each (i.e. the maximum that can be eaten) | Individual |
ing_act       | g | Total actual ingestion of feed by fish in the entire farm | Farm |
E_assim       |  |  | Individual |
E_somat       |  |  | Individual |
anab          |  |  | Individual |
catab         |  |  | Individual |
O2            |  |  | Farm |
NH4           |  |  | Farm |
total_excr    | g | Total excretion from the entire farm (P+L+C) | Farm |
total_uneat   | g | Total uneaten feed from the entire farm (P+L+C) | Farm |
metab         |  |  | Individual |
biomass       | g | Mean weight of all fish within a farm (i.e. weight * population) | Farm |
: Summary of model outputs being used in this script. Note that all the outputs are daily values (i.e. value at day = t). None are summed across a production period.

# Raw output processing

For some of the outputs of the model, it makes sense to sum them across a production period and/or calculate their values per unit of biomass. 
```{r}
#| label: biomass-location-globals-farm

farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
  rename(farm_ID = farm_id) %>% 
  mutate(country = as.factor(country))

fish_weight <- find_read(output_model_farm_path, "weight")
farm_biomass <- find_read(output_model_farm_path, "biomass_stat")
biomass_produced <- find_read(output_model_farm_path, "biomass_produced")

# farm_biomass has had the final day (when fish are not fed) removed - this adds it back
all_biomass <- rbind(farm_biomass, biomass_produced)
qs::qsave(all_biomass, file.path(data_analysis_path, "all_biomass.qs"))

farm_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
all_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
```

Note that this next block takes a long time to run, almost entirely because of the proper calculation of the ratio standard deviation for the per biomass stats.

```{r}
#| label: summed-per-biomass-outputs

further_stats <- c(
  # Nutrients excreted
  "P_excr_stat", "L_excr_stat", "C_excr_stat", 
  # Nutrients uneaten
  "P_uneat_stat", "L_uneat_stat", "C_uneat_stat",
  # Food provided and eaten
  "food_prov_stat", "ing_act_stat",
  # Oxygen consumed, ammonium produced
  "O2_stat", "NH4_stat",
  # PLC uneaten and excreted
  "total_excr_stat", "total_uneat_stat"
)

analysis_names <- further_stats %>% str_remove("_stat")

print(str_c("Starting further stats processing at ", Sys.time()))

prepped_biomass <- farm_biomass %>% 
  select(-measure) %>% 
  rename(biom_mean = mean,biom_sd = sd)

prepped_biomass_produced <- biomass_produced %>% 
  select(-measure) %>% 
  rename(biom_mean = mean, biom_sd = sd) %>% 
  select(farm_ID, feed, biom_mean, biom_sd)

for (fs in seq_along(further_stats)) {
  # Model output
  out <- find_read(output_model_farm_path, further_stats[fs])

  # Total summed across the production period
  stat_summed <- out %>% 
    group_by(farm_ID, feed, measure) %>% 
    reframe(
      days = n(),
      total = sum(mean),
      sd = sqrt(sumna(sd^2)),
    ) %>% 
    merge(farm_locs, by = "farm_ID") %>% 
    relocate(country, .before = farm_ID) %>% 
    st_as_sf() %>% 
    mutate(
      days = days %>% set_units("d"),
      total = total %>% set_units("g"),
      sd = sd %>% set_units("g")
    )

  qs::qsave(stat_summed, file.path(data_analysis_path, str_c(analysis_names[fs], "_farm_summed.qs")))

  # Total per biomass (/g salmon)
  # This needs the "farm_biomass" global from above
  stat_per_biom <- out %>% 
    merge(
      prepped_biomass, 
      by = c("farm_ID", "feed", "t", "prod_t")
    ) %>% 
    mutate(
      mean_biom = mean/biom_mean,
      sd_biom = (mean/biom_mean) * sqrt((biom_sd/biom_mean)^2 + (sd/mean)^2)
    ) %>% 
    select(-c(mean, sd, biom_mean, biom_sd)) %>% 
    merge(farm_locs, by = "farm_ID") %>% 
    relocate(country, .before = farm_ID) %>% 
    st_as_sf() %>% 
    mutate(
      mean_biom = mean_biom %>% set_units("g g_fish-1"),
      sd_biom = sd_biom %>% set_units("g g_fish-1")
    )

  qs::qsave(stat_per_biom, file.path(data_analysis_path, str_c(analysis_names[fs], "_farm_per_biom.qs")))

  # Total per biomass (/g salmon) summed across the production period
  # This needs the "biomass_produced" global from above
  stat_per_biom_summed <- out %>% 
    group_by(farm_ID, feed, measure) %>% 
    reframe(
      days = n(),
      total = sum(mean),
      sd = sqrt(sumna(sd^2)),
    ) %>% 
    select(farm_ID, feed, measure, total, sd) %>% 
    merge(
      prepped_biomass_produced, 
      by = c("farm_ID", "feed")
    ) %>% 
    mutate(
      mean_biom = (total/biom_mean),
      sd_biom = (total/biom_mean) * sqrt((biom_sd/biom_mean)^2 + (sd/total)^2)
    ) %>% 
    select(-c(total, sd, biom_mean, biom_sd)) %>% 
    merge(farm_locs, by = "farm_ID") %>% 
    relocate(country, .before = farm_ID) %>% 
    st_as_sf() %>% 
    mutate(mean_biom = mean_biom %>% set_units("g g_fish-1"),
           sd_biom = sd_biom %>% set_units("g g_fish-1"))

  qs::qsave(stat_per_biom_summed, file.path(data_analysis_path, str_c(analysis_names[fs], "_farm_per_biom_summed.qs")))

  print(str_c(
    "Finished ", further_stats[fs], " at ", Sys.time(), " --- ", round(100*fs/length(further_stats),1), "% done"
  ))
}

rm(stat_summed, stat_per_biom, stat_per_biom_summed)
```

Similarly, some cohort stats can be expressed per biomass. The cohort stats are only really useful when talking about daily values on an operating farm (with the overlapping cohorts) and average values per day or year.

```{r}
#| label: biomass-location-globals-cohort

cohort_biomass <- find_read(output_model_cohort_path, "biomass_stat")
cohort_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
```

```{r}
#| label: summed-per-biomass-outputs-cohort
#| eval: false

further_stats <- c(
  # Nutrients excreted
  "P_excr_stat", "L_excr_stat", "C_excr_stat", 
  # Nutrients uneaten
  "P_uneat_stat", "L_uneat_stat", "C_uneat_stat",
  # Food provided and eaten
  "food_prov_stat", "ing_act_stat",
  # Oxygen consumed, ammonium produced
  "O2_stat", "NH4_stat",
  # PLC uneaten and excreted
  "total_excr_stat", "total_uneat_stat"
)

analysis_names <- further_stats %>% str_remove("_stat")

for (fs in seq_along(further_stats)) {
  # Model output
  out <- find_read(output_model_cohort_path, further_stats[fs])

  # # Total summed across the production period
  # stat_summed <- out %>% 
    # group_by(farm_ID, feed, measure) %>% 
    # reframe(
    #   days = n(),
    #   total = sum(mean),
    #   sd = sqrt(sumna(sd^2)),
    # ) %>% 
  #   merge(farm_locs, by = "farm_ID") %>% 
  #   relocate(country, .before = farm_ID) %>% 
  #   st_as_sf() %>% 
  #   mutate(days = days %>% set_units("d"),
  #          total = total %>% set_units("g"),
  #          sd = sd %>% set_units("g"))

  # Finish this - I want to have:
  # * Mean output per year (total, and per biomass)
  # * Mean, min and max output per day (total, and per biomass)

  # This needs the "cohort_biomass" global from above
  stat_per_biom <- per_biom_coho(out) %>% 
    merge(farm_locs, by = "farm_ID") %>% 
    relocate(country, .before = farm_ID) %>% 
    st_as_sf() %>% 
    mutate(mean_biom = mean_biom %>% set_units("g g_fish-1"),
           sd_biom = sd_biom %>% set_units("g g_fish-1"))

  qs::qsave(stat_per_biom, file.path(data_analysis_path, str_c(analysis_names[fs], "_cohort_per_biom.qs")))

  print(str_c(
    "Finished ", further_stats[fs], " at ", Sys.time(), " --- ", round(100*fs/length(further_stats),1), "% done"
  ))
}
```

# Biomass and feed provided/consumed questions

```{r}
#| label: biomass-produced-comparisons

biomass_produced <- find_read(output_model_farm_path, "biomass_produced") %>% 
  mutate(feed = factor(feed, 
                       levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
                       labels = c("MD", "PD", "NI"))) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(mean, sd),
    id_cols = c(farm_ID, measure)
  ) %>% 
  mutate(
    sd_MD = (1/mean_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/mean_PD) * sqrt(sd_NI^2 + sd_PD^2),
    mean_MD = (mean_MD-mean_PD)/mean_PD,
    mean_NI = (mean_NI-mean_PD)/mean_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "mean"))
  ) %>% 
  merge(farm_locs, by = c("farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(biomass_produced, aes(x = country, y = mean, fill = feed)) +
  geom_boxplot()

qs::qsave(biomass_produced, file.path(comparisons_path, "biomass_produced.qs"))
rm(biomass_produced)
```

## Are fish fed different feeds given more or less feed?

```{r}
#| label: food-provided-comparison

# Summed across the whole production period
food_prov_farm_summed <- find_read(data_analysis_path, "food_prov_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(feed = factor(feed, 
                       levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
                       labels = c("MD", "PD", "NI"))) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(food_prov_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(food_prov_farm_summed, file.path(comparisons_path, "food_prov_farm_summed.qs"))
rm(food_prov_farm_summed)

# Summed across the whole production period, per biomass of fish produced -  is this identical to FCE?
food_prov_farm_per_biom_summed <- find_read(data_analysis_path, "food_prov_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(food_prov_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
  geom_boxplot()

qs::qsave(food_prov_farm_per_biom_summed, file.path(comparisons_path, "food_prov_farm_per_biom_summed.qs"))
rm(food_prov_farm_per_biom_summed)
```

# Total inputs (mass) questions
## Does uneaten feed increase or decrease with novel feeds?

```{r}
#| label: uneaten-feed-comparisons

# Summed across the whole production period
total_uneat_farm_summed <- find_read(data_analysis_path, "total_uneat_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(feed = factor(feed, 
                       levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
                       labels = c("MD", "PD", "NI"))) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_uneat_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_uneat_farm_summed, file.path(comparisons_path, "total_uneat_farm_summed.qs"))
rm(total_uneat_farm_summed)

# Summed across the whole production period, per biomass of fish produced
total_uneat_farm_per_biom_summed <- find_read(data_analysis_path, "total_uneat_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_uneat_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_uneat_farm_per_biom_summed, file.path(comparisons_path, "total_uneat_farm_per_biom_summed.qs"))
rm(total_uneat_farm_per_biom_summed)
```

## Does excretion increase or decrease with novel feeds?

```{r}
#| label: excreted-comparison

# Summed across the whole production period
total_excr_farm_summed <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_excr_farm_summed, file.path(comparisons_path, "total_excr_farm_summed.qs"))
rm(total_excr_farm_summed)

# Summed across the whole production period, per biomass of fish produced
total_excr_farm_per_biom_summed <- find_read(data_analysis_path, "total_excr_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(total_excr_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(total_excr_farm_per_biom_summed, file.path(comparisons_path, "total_excr_farm_per_biom_summed.qs"))
rm(total_excr_farm_per_biom_summed)
```

## Do total inputs (mass, excreted and uneaten) increase or decrease with novel feeds?

```{r}
#| label: total-mass-inputs-comparison

total_mass_inputs_farm_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_summed"), 
  find_read(data_analysis_path, "total_excr_farm_summed")
) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed, days) %>% 
  reframe(
    total = sum(total),
    sd = sqrt(sum(sd^2)),
    measure = as.factor("excr_uneat")
  )
qs::qsave(total_mass_inputs_farm_summed, file.path(data_analysis_path, "total_mass_inputs_farm_summed.qs"))
rm(total_mass_inputs_farm_summed)

# Summed across the whole production period
total_mass_inputs_farm_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_summed"), 
  find_read(data_analysis_path, "total_excr_farm_summed")
) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed, days) %>% 
  reframe(
    total = sum(total),
    sd = sqrt(sum(sd^2)),
    measure = as.factor("excr_uneat")
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(total_mass_inputs_farm_summed, aes(x = country, y = total, fill = feed)) +
  geom_boxplot()

qs::qsave(total_mass_inputs_farm_summed, file.path(comparisons_path, "total_mass_inputs_farm_summed.qs"))
rm(total_mass_inputs_farm_summed)

# Summed across the whole production period, per biomass of fish produced
total_mass_inputs_farm_per_biom_summed <- rbind(
  find_read(data_analysis_path, "total_uneat_farm_per_biom_summed"), 
  find_read(data_analysis_path, "total_excr_farm_per_biom_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed) %>% 
  reframe(
    mean_biom = sum(mean_biom),
    sd_biom = sqrt(sum(sd_biom^2)),
    measure = as.factor("excr_uneat")
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(total_mass_inputs_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
  geom_boxplot()

qs::qsave(total_mass_inputs_farm_per_biom_summed, file.path(comparisons_path, "total_mass_inputs_farm_per_biom_summed.qs"))
rm(total_mass_inputs_farm_per_biom_summed)
```

## Does the proportion of total inputs (mass) attributed to excretion increase or decrease with novel feeds?

```{r}
#| label: proportion-of-waste-comparison

proportion_of_waste <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  rbind(find_read(data_analysis_path, "total_mass_inputs_farm_summed.qs")) %>% 
  mutate(
    measure = factor(
      measure, 
      levels = c("total_excr_stat", "excr_uneat"),
      labels = c("excr", "waste")
      )
  ) %>% 
  pivot_wider(
    names_from = measure,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, feed, days)
  ) %>% 
  mutate(
    total = total_excr/total_waste,
    sd = (total_excr/total_waste) * sqrt((sd_waste/total_waste)^2 + (sd_excr/total_excr)^2)
  ) %>% 
  select(-contains(c("waste", "excr")))

# Check that it looks reasonable
ggplot(proportion_of_waste, aes(x = country, y = total, fill = feed)) +
  geom_boxplot()

qs::qsave(proportion_of_waste, file.path(comparisons_path, "excr_proportion_of_waste.qs"))
rm(proportion_of_waste)
```

## Does total inputs (mass) of each macronutrient increase or decrease with novel feeds?

```{r}
#| label: PLC-mass-inputs-comparison

PLC_uneat_excr_farm_summed <- rbind(
    find_read(data_analysis_path, "P_uneat_farm_summed"), 
    find_read(data_analysis_path, "L_uneat_farm_summed"), 
    find_read(data_analysis_path, "C_uneat_farm_summed"),
    find_read(data_analysis_path, "P_excr_farm_summed"), 
    find_read(data_analysis_path, "L_excr_farm_summed"), 
    find_read(data_analysis_path, "C_excr_farm_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    measure = droplevels(measure),
    measure = factor(
      measure,
      labels = str_remove(levels(measure), "_stat")
    ),
    macro = as.factor(str_split_i(measure, "_", 1)),
    measure = as.factor(str_split_i(measure, "_", 2)),
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  )
# Check that it looks reasonable
# ggplot(PLC_uneat_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot() +
#   facet_grid(cols = vars(macro), rows = vars(measure))

qs::qsave(PLC_uneat_excr_farm_summed, file.path(data_analysis_path, "PLC_uneat_excr_farm_summed.qs"))
rm(PLC_uneat_excr_farm_summed)

# Summed across the whole production period
PLC_uneat_excr_farm_summed <- rbind(
    find_read(data_analysis_path, "P_uneat_farm_summed"), 
    find_read(data_analysis_path, "L_uneat_farm_summed"), 
    find_read(data_analysis_path, "C_uneat_farm_summed"),
    find_read(data_analysis_path, "P_excr_farm_summed"), 
    find_read(data_analysis_path, "L_excr_farm_summed"), 
    find_read(data_analysis_path, "C_excr_farm_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    measure = droplevels(measure),
    measure = factor(
      measure,
      labels = str_remove(levels(measure), "_stat")
    ),
    macro = as.factor(str_split_i(measure, "_", 1)),
    measure = as.factor(str_split_i(measure, "_", 2)),
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = c(feed, macro),
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD_P = (1/total_PD_P) * sqrt(sd_MD_P^2 + sd_PD_P^2),
    sd_NI_P = (1/total_PD_P) * sqrt(sd_NI_P^2 + sd_PD_P^2),
    total_MD_P = (total_MD_P-total_PD_P)/total_PD_P,
    total_NI_P = (total_NI_P-total_PD_P)/total_PD_P,
    sd_MD_P = (1/total_PD_P) * sqrt(sd_MD_P^2 + sd_PD_P^2),
    sd_NI_P = (1/total_PD_P) * sqrt(sd_NI_P^2 + sd_PD_P^2),
    total_MD_L = (total_MD_L-total_PD_L)/total_PD_L,
    total_NI_L = (total_NI_L-total_PD_L)/total_PD_L,
    sd_MD_P = (1/total_PD_P) * sqrt(sd_MD_P^2 + sd_PD_P^2),
    sd_NI_P = (1/total_PD_P) * sqrt(sd_NI_P^2 + sd_PD_P^2),
    total_MD_C = (total_MD_C-total_PD_C)/total_PD_C,
    total_NI_C = (total_NI_C-total_PD_C)/total_PD_C
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed", "macro"), names_sep = "_", names_transform = list(feed = as.factor, macro = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(PLC_uneat_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot() +
#   facet_grid(cols = vars(macro), rows = vars(measure))

qs::qsave(PLC_uneat_excr_farm_summed, file.path(comparisons_path, "PLC_uneat_excr_farm_summed.qs"))
rm(PLC_uneat_excr_farm_summed)

# Summed across the whole production period, per biomass of fish produced
PLC_uneat_excr_farm_per_biom_summed <- rbind(
    find_read(data_analysis_path, "P_uneat_farm_per_biom_summed"), 
    find_read(data_analysis_path, "L_uneat_farm_per_biom_summed"), 
    find_read(data_analysis_path, "C_uneat_farm_per_biom_summed"),
    find_read(data_analysis_path, "P_excr_farm_per_biom_summed"), 
    find_read(data_analysis_path, "L_excr_farm_per_biom_summed"), 
    find_read(data_analysis_path, "C_excr_farm_per_biom_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    measure = droplevels(measure),
    measure = factor(
      measure,
      labels = str_remove(levels(measure), "_stat")
    ),
    macro = as.factor(str_split_i(measure, "_", 1)),
    measure = as.factor(str_split_i(measure, "_", 2)),
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  rename(
    mean.biom = mean_biom,
    sd.biom = sd_biom
  ) %>% 
  pivot_wider(
    names_from = c(feed, macro),
    values_from = c(mean.biom, sd.biom), values_fn = list(mean.biom = drop_units, sd.biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd.biom_MD_P = (1/mean.biom_PD_P) * sqrt(sd.biom_MD_P^2 + sd.biom_PD_P^2),
    sd.biom_NI_P = (1/mean.biom_PD_P) * sqrt(sd.biom_NI_P^2 + sd.biom_PD_P^2),
    mean.biom_MD_P = (mean.biom_MD_P-mean.biom_PD_P)/mean.biom_PD_P,
    mean.biom_NI_P = (mean.biom_NI_P-mean.biom_PD_P)/mean.biom_PD_P,
    sd.biom_MD_L = (1/mean.biom_PD_L) * sqrt(sd.biom_MD_L^2 + sd.biom_PD_L^2),
    sd.biom_NI_L = (1/mean.biom_PD_L) * sqrt(sd.biom_NI_L^2 + sd.biom_PD_L^2),
    mean.biom_MD_L = (mean.biom_MD_L-mean.biom_PD_L)/mean.biom_PD_L,
    mean.biom_NI_L = (mean.biom_NI_L-mean.biom_PD_L)/mean.biom_PD_L,
    sd.biom_MD_C = (1/mean.biom_PD_C) * sqrt(sd.biom_MD_C^2 + sd.biom_PD_C^2),
    sd.biom_NI_C = (1/mean.biom_PD_C) * sqrt(sd.biom_NI_C^2 + sd.biom_PD_C^2),
    mean.biom_MD_C = (mean.biom_MD_C-mean.biom_PD_C)/mean.biom_PD_C,
    mean.biom_NI_C = (mean.biom_NI_C-mean.biom_PD_C)/mean.biom_PD_C
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed", "macro"), names_sep = "_", names_transform = list(feed = as.factor, macro = as.factor),
    cols = contains(c("sd.biom", "mean.biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(PLC_uneat_excr_farm_per_biom_summed, aes(x = country, y = mean.biom, fill = feed)) +
#   geom_boxplot() +
#   facet_grid(cols = vars(macro), rows = vars(measure))

qs::qsave(PLC_uneat_excr_farm_per_biom_summed, file.path(comparisons_path, "PLC_uneat_excr_farm_per_biom_summed.qs"))
rm(PLC_uneat_excr_farm_per_biom_summed)
```

## Does the proportion of total inputs (mass) attributed to each macronutrient increase or decrease with novel feeds?

```{r}
#| label: macronutrient-proportion-comparison

# Summed across the whole production period
PLC_proportion_farm_summed_1 <- rbind(
    find_read(data_analysis_path, "P_uneat_farm_summed"), 
    find_read(data_analysis_path, "L_uneat_farm_summed"), 
    find_read(data_analysis_path, "C_uneat_farm_summed"),
    find_read(data_analysis_path, "P_excr_farm_summed"), 
    find_read(data_analysis_path, "L_excr_farm_summed"), 
    find_read(data_analysis_path, "C_excr_farm_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    measure = droplevels(measure),
    measure = factor(
      measure,
      labels = str_remove(levels(measure), "_stat")
    ),
    macro = as.factor(str_split_i(measure, "_", 1)),
    measure = as.factor(str_split_i(measure, "_", 2)),
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = macro,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, feed, measure, days)
  ) %>% 
  mutate(
    total_sum = total_P+total_C+total_L,
    sd_sum = sqrt(sd_P^2+sd_C^2+sd_L^2),
    prop_P = total_P/total_sum,
    prop_C = total_C/total_sum,
    prop_L = total_L/total_sum,
    sd_P = ratio_sd(total_P, sd_P, total_sum, sd_sum),
    sd_C = ratio_sd(total_C, sd_C, total_sum, sd_sum),
    sd_L = ratio_sd(total_L, sd_P, total_sum, sd_sum),
  ) %>% 
  select(-contains(c("total", "sum"))) %>% 
  pivot_longer(
    names_to = c(".value", "macro"), names_sep = "_", names_transform = list(macro = as.factor),
    cols = contains(c("sd", "prop"))
  )

# Check that it looks reasonable
# ggplot(PLC_proportion_farm_summed_1, aes(x = measure, y = prop, fill = feed)) +
#   geom_col(position = "dodge") +
#   facet_grid(rows = vars(macro))

qs::qsave(PLC_proportion_farm_summed_1, file.path(data_analysis_path, "PLC_proportion_farm_summed.qs"))

PLC_proportion_farm_summed_2 <- PLC_proportion_farm_summed_1 %>% 
  pivot_wider(
    names_from = c(feed, macro),
    values_from = c(prop, sd),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD_P = (1/prop_PD_P) * sqrt(sd_MD_P^2 + sd_PD_P^2),
    sd_NI_P = (1/prop_PD_P) * sqrt(sd_NI_P^2 + sd_PD_P^2),
    prop_MD_P = (prop_MD_P-prop_PD_P)/prop_PD_P,
    prop_NI_P = (prop_NI_P-prop_PD_P)/prop_PD_P,
    sd_MD_L = (1/prop_PD_L) * sqrt(sd_MD_L^2 + sd_PD_L^2),
    sd_NI_L = (1/prop_PD_L) * sqrt(sd_NI_L^2 + sd_PD_L^2),
    prop_MD_L = (prop_MD_L-prop_PD_L)/prop_PD_L,
    prop_NI_L = (prop_NI_L-prop_PD_L)/prop_PD_L,
    sd_MD_C = (1/prop_PD_C) * sqrt(sd_MD_C^2 + sd_PD_C^2),
    sd_NI_C = (1/prop_PD_C) * sqrt(sd_NI_C^2 + sd_PD_C^2),
    prop_MD_C = (prop_MD_C-prop_PD_C)/prop_PD_C,
    prop_NI_C = (prop_NI_C-prop_PD_C)/prop_PD_C
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed", "macro"), names_sep = "_", names_transform = list(feed = as.factor, macro = as.factor),
    cols = contains(c("sd", "prop"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(PLC_proportion_farm_summed_2, aes(x = macro, y = prop, fill = feed)) +
#   geom_boxplot() +
#   facet_grid(cols = vars(measure))

qs::qsave(PLC_proportion_farm_summed_2, file.path(comparisons_path, "PLC_proportion_farm_summed.qs"))
rm(PLC_proportion_farm_summed_1, PLC_proportion_farm_summed_2)
```

# N inputs questions

This is very similar to the previous set of questions, however in this set only the protein outputs are considered and converted to nitrogen ($N=P\times 6.25$).

## Does N from uneaten feed increase or decrease with novel feeds?

```{r}
#| label: uneaten-feed-N-comparison

# Summed across the whole production period
N_uneat_farm_summed <- find_read(data_analysis_path, "P_uneat_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    total = total * 6.25,
    sd = sd * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_uneat_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_uneat_farm_summed, file.path(comparisons_path, "N_uneat_farm_summed.qs"))
rm(N_uneat_farm_summed)

# Summed across the whole production period, per biomass of fish produced
N_uneat_farm_per_biom_summed <- find_read(data_analysis_path, "P_uneat_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    mean_biom = mean_biom * 6.25,
    sd_biom = mean_biom * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_uneat_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_uneat_farm_per_biom_summed, file.path(comparisons_path, "N_uneat_farm_per_biom_summed.qs"))
rm(N_uneat_farm_per_biom_summed)
```

## Does N excretion increase or decrease with novel feeds?

```{r}
#| label: excreted-N-comparison

# Summed across the whole production period
N_excr_farm_summed <- find_read(data_analysis_path, "P_excr_farm_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    total = total * 6.25,
    sd = sd * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_excr_farm_summed, file.path(comparisons_path, "N_excr_farm_summed.qs"))
rm(N_excr_farm_summed)

# Summed across the whole production period, per biomass of fish produced
N_excr_farm_per_biom_summed <- find_read(data_analysis_path, "P_excr_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    mean_biom = mean_biom * 6.25,
    sd_biom = mean_biom * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_excr_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_excr_farm_per_biom_summed, file.path(comparisons_path, "N_excr_farm_per_biom_summed.qs"))
rm(N_excr_farm_per_biom_summed)
```

```{r}
#| label: total-N-comparison

# Summed across the whole production period
N_total_farm_summed <- rbind(
  find_read(data_analysis_path, "P_excr_farm_summed"),
  find_read(data_analysis_path, "P_uneat_farm_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    total = total * 6.25,
    sd = sd * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  group_by(country, farm_ID, feed, days) %>% 
  reframe(
    total = sum(total),
    sd = sqrt(sum(sd^2))
  ) %>% 
  mutate(measure = as.factor("total")) %>% 
  relocate(measure, .after = feed) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_total_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_total_farm_summed, file.path(data_analysis_path, "N_total_farm_summed.qs"))

N_total_farm_summed <- N_total_farm_summed %>% 
  st_drop_geometry() %>% 
  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
ggplot(N_total_farm_summed, aes(x = country, y = total, fill = feed)) +
  geom_boxplot()

qs::qsave(N_total_farm_summed, file.path(comparisons_path, "N_total_farm_summed.qs"))

# Summed across the whole production period, per biomass of fish produced
N_excr_farm_per_biom_summed <- find_read(data_analysis_path, "P_excr_farm_per_biom_summed") %>% 
  st_drop_geometry() %>% 
  mutate(
    mean_biom = mean_biom * 6.25,
    sd_biom = mean_biom * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    )
  ) %>% 
  pivot_wider(
    names_from = feed, names_sep = ".", 
    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
    id_cols = c(country, farm_ID, measure)
  ) %>% 
  mutate(
    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
    cols = contains(c("sd_biom", "mean_biom"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_excr_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_excr_farm_per_biom_summed, file.path(comparisons_path, "N_excr_farm_per_biom_summed.qs"))
rm(N_excr_farm_per_biom_summed)
```

```{r}

N_total_farm_summed <- rbind(
  find_read(data_analysis_path, "P_excr_farm_summed"),
  find_read(data_analysis_path, "P_uneat_farm_summed")
  ) %>% 
  st_drop_geometry() %>% 
  mutate(
    total = total * 6.25,
    sd = sd * 6.25,
    feed = factor(
      feed, 
      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
      labels = c("MD", "PD", "NI")
    ),
    measure = factor(
      measure, 
      levels = c("P_excr_stat", "P_uneat_stat"),
      labels = c("excr", "uneat")
      )
  ) %>% 
  rbind(N_total_farm_summed_0)

  pivot_wider(
    names_from = feed,
    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
    id_cols = c(country, farm_ID, measure, days)
  ) %>% 
  mutate(
    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
    total_MD = (total_MD-total_PD)/total_PD,
    total_NI = (total_NI-total_PD)/total_PD
  ) %>% 
  select(-contains("PD")) %>% 
  pivot_longer(
    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
    cols = contains(c("sd", "total"))
  ) %>% 
  merge(farm_locs, by = c("country", "farm_ID")) %>% 
  st_as_sf()

# Check that it looks reasonable
# ggplot(N_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
#   geom_boxplot()

qs::qsave(N_excr_farm_summed, file.path(comparisons_path, "N_excr_farm_summed.qs"))
rm(N_excr_farm_summed)
```

### 2025-08-01 index.qmd
Analysis updates

--- 2025-07-30 index.qmd
@@
 library(RColorBrewer)
+# library(lme4)
+library(car)
+library(emmeans)
+
 conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
@@
 
-```{r global-variables}
+```{r}
+#| label: global-variables
 #| include: false
@@
 
+long_feeds <- c("marine_dominant", "plant_dominant", "novel_inclusive")
+short_feeds <- c("MD", "PD", "NI")
+
 feed_pal <- c(
@@
 }
+```
+
+# Results {#sec-results}
+
+```{r}
+#| label: load-all-data-analysis
+
+# Biomass produced
+bpr1 <- find_read(output_model_farm_path, "biomass_produced") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(mean = mean(mean) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = mean)
+
+bpr2 <- find_read(comparisons_path, "biomass_produced") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(mean)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Feed provided
+fpr1 <- find_read(data_analysis_path, "food_prov_farm_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+fpr2 <- find_read(comparisons_path, "food_prov_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Feed provided per biomass
+fpr_pb1 <- find_read(data_analysis_path, "food_prov_farm_per_biom_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(mean_biom = mean(mean_biom) %>% set_units("g g_fish-1") %>% set_units("kg kg_fish-1") %>% drop_units() %>% round(2)) %>% 
+  pivot_wider(names_from = feed, values_from = mean_biom)
+
+fpr_pb2 <- find_read(comparisons_path, "food_prov_farm_per_biom_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(mean_biom)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Uneaten feed
+tuf1 <- find_read(data_analysis_path, "total_uneat_farm_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+tuf2 <- find_read(comparisons_path, "total_uneat_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Excreted waste
+tew1 <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+tew2 <- find_read(comparisons_path, "total_excr_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Total waste
+tow1 <- find_read(data_analysis_path, "total_mass_inputs_farm_summed") %>% 
+  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+tow2 <- find_read(comparisons_path, "total_mass_inputs_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Excretion proportion of waste
+epw <- find_read(comparisons_path, "excr_proportion_of_waste") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# Protein, lipid, carbs
+plc1 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed") %>% 
+  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed, measure, macro) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = c(feed, macro), values_from = total)
+
+# Proportion of PLC waste from excretion
+plc2 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed") %>% 
+  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed, measure, macro) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = c(feed, macro, measure), values_from = total) %>% 
+  mutate(
+    MD_C = round(100*MD_C_excr/(MD_C_excr+MD_C_uneat),1),
+    MD_L = round(100*MD_L_excr/(MD_L_excr+MD_L_uneat),1),
+    MD_P = round(100*MD_P_excr/(MD_P_excr+MD_P_uneat),1),
+    NI_C = round(100*NI_C_excr/(NI_C_excr+NI_C_uneat),1),
+    NI_L = round(100*NI_L_excr/(NI_L_excr+NI_L_uneat),1),
+    NI_P = round(100*NI_P_excr/(NI_P_excr+NI_P_uneat),1),
+    PD_C = round(100*PD_C_excr/(PD_C_excr+PD_C_uneat),1),
+    PD_L = round(100*PD_L_excr/(PD_L_excr+PD_L_uneat),1),
+    PD_P = round(100*PD_P_excr/(PD_P_excr+PD_P_uneat),1)
+  ) %>% 
+  select(-contains(c("excr", "uneat")))
+
+# % change in PLC waste
+plc3 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed") %>% 
+  group_by(feed, macro) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = c(feed, macro), values_from = diff)
+
+# N inputs, uneaten
+niu1 <- find_read(data_analysis_path, "P_uneat_farm_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds),
+         total = total * 6.25,
+         sd = sd * 6.25) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+niu2 <- find_read(comparisons_path, "N_uneat_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# N inputs, excreted
+nie1 <- find_read(data_analysis_path, "P_excr_farm_summed") %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds),
+         total = total * 6.25,
+         sd = sd * 6.25) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+nie2 <- find_read(comparisons_path, "N_excr_farm_summed") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+
+# N inputs, total
+nit1 <- find_read(data_analysis_path, "N_total_farm_summed.qs") %>% 
+  # mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(feed) %>% 
+  reframe(total = mean(total) %>% set_units("g") %>% set_units("t") %>% drop_units() %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = total)
+
+nit2 <- find_read(comparisons_path, "N_total_farm_summed.qs") %>% 
+  group_by(feed) %>% 
+  reframe(diff = (100*mean(total)) %>% round(1)) %>% 
+  pivot_wider(names_from = feed, values_from = diff)
+```
+
+@tbl-results-summary is a summary of all the results I've processed so far, basically trying to acertain all the major differences in inputs between the feeds.
+
+| Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
+|:--------------------------|:----------:|:----------:|:----------:|:----------:|:----------:|
+| Salmon biomass produced (t) | `r bpr1$PD` | `r bpr1$MD` | `r bpr1$NI` | `r bpr2$MD` | `r bpr2$NI` |
+| Feed provided (t) | `r fpr1$PD` | `r fpr1$MD` | `r fpr1$NI` | `r fpr2$MD` | `r fpr2$NI` |
+| Feed provided (kg/kg salmon) | `r fpr_pb1$PD` | `r fpr_pb1$MD` | `r fpr_pb1$NI` | `r fpr_pb2$MD` | `r fpr_pb2$NI` |
+| Uneaten feed (t) | `r tuf1$PD` | `r tuf1$MD` | `r tuf1$NI` | `r tuf2$MD` | `r tuf2$NI` |
+| Excreted waste (t) | `r tew1$PD` | `r tew1$MD` | `r tew1$NI` | `r tew2$MD` | `r tew2$NI` |
+| Total waste (E+U, t) | `r tow1$PD` | `r tow1$MD` | `r tow1$NI` | `r tow2$MD` | `r tow2$NI` |
+| Proportion of total waste composed of excretion (%) | `r epw$PD` | `r epw$MD` | `r epw$NI` |  |  |
+| Total protein waste (t) | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r plc3$MD_P` | `r plc3$NI_P` |
+| Total carbohydrate waste (t) | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r plc3$MD_C` | `r plc3$NI_C` |
+| Total lipid waste (t) | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r plc3$MD_L` | `r plc3$NI_L` |
+| Proportion of protein waste from excretion (%) | `r plc2$PD_P` | `r plc2$MD_P` | `r plc2$NI_P` |  |  |
+| Proportion of carbohydrate waste from excretion (%) | `r plc2$PD_C` | `r plc2$MD_C` | `r plc2$NI_C` |  |  |
+| Proportion of lipid waste from excretion (%) | `r plc2$PD_L` | `r plc2$MD_L` | `r plc2$NI_L` |  |  |
+| Total N from uneaten feed (t) | `r niu1$PD` | `r niu1$MD` | `r niu1$NI` | `r niu2$MD` | `r niu2$NI` |
+| Total N from excreted waste (t) | `r nie1$PD` | `r nie1$MD` | `r nie1$NI` | `r nie2$MD` | `r nie2$NI` |
+| Total N inputs (E+U, t) | `r nit1$PD` | `r nit1$MD` | `r nit1$NI` | `r nit2$MD` | `r nit2$NI` |
+: Summary of all results.
+Unless otherwise specified, values presented are means across all farms, summed across a single production period.
+Some cells of this table are blank - sometimes that means it doesn't make sense to fill that cell, but sometimes it means I haven't got to it yet.
+{#tbl-results-summary}
+
+So here are the major themes I'm getting from @tbl-results-summary:
+
+::: {.aside}
+*Note that when I refer to "FCE" here I'm talking about the PLC weight (protein + lipid + carbohydrate) weight of feed, which may differ from its actual weight because of the inclusion of minerals and non-digestible material.
+:::
+
+1.
+The NI diet was more efficient than the PD diet.
+When farms were fed the NI diet they had an average FCE* of `r fpr_pb1$NI`, compared to the average FCE of `r fpr_pb1$PD` when farms were fed the PD diet, and feeding the NI diet resulted in `r bpr2$NI`% more biomass produced with the same population compared to the PD diet.
+2. Despite this, nutrients lost to the environment were generally highest in the NI diet and lowest in the MD diet. 
+  * In terms of total waste inputs (bulk mass), the NI and PD diets were very similar (probably due to their very similar ingredient compositions).
+The MD diet had markedly lower total waste inputs than either the PD or NI diets.
+3.
+However, the PLC composition of nutrients was very different between the diets (@fig-PLC-waste-comparison).
+The PD diet had the lowest protein waste output and the NI diet had the highest, while the MD diet had the lowest carbohydrate and lipid waste outputs and the PD diet the highest.
+Overall, changing from the PD diet to the NI diet would result in a `r abs(plc3$NI_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively, while changing to the MD diet would result in a `r abs(plc3$MD_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively.
+4. Overall, nitrogen inputs were `r nit2$NI`% higher in the NI diet and `r nit2$MD`% higher in the MD diet.
+
+```{r}
+#| label: PLC-waste-comparison
+
+plc1 <- find_read(data_analysis_path, "PLC_uneat_excr_farm_summed")
+
+lm_P <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "P"))
+aov_P <- aov(lm_P)
+# summary(aov_P)
+
+emm <- emmeans(lm_P, "feed", "measure")
+tukey_results <- pairs(emm, adjust = "tukey")
+# print(tukey_results)
+
+lm_C <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "C"))
+aov_C <- aov(lm_C)
+# summary(aov_C)
+
+emm <- emmeans(lm_C, "feed", "measure")
+tukey_results <- pairs(emm, adjust = "tukey")
+# print(tukey_results)
+
+lm_L <- lm(drop_units(total) ~ feed * measure, data = filter(plc1, macro == "L"))
+aov_L <- aov(lm_L)
+# summary(aov_L)
+
+emm <- emmeans(lm_L, "feed", "measure")
+tukey_results <- pairs(emm, adjust = "tukey")
+# print(tukey_results)
+```
+
+```{r}
+#| label: fig-PLC-waste-comparison
+#| fig-cap: Mean waste lost to the environment in a complete production cycle when farms are fed the MD (blue), PD (green) or NI (red) diet. Errorbars show SD across all farms.
+
+plc1 %>%
+  group_by(measure, macro, feed) %>%
+  reframe(
+    sd = sd(total) %>% set_units("g") %>% set_units("t") %>% drop_units(),
+    total = mean(total) %>% set_units("t") %>% drop_units(), 
+  ) %>% 
+  mutate(
+    macro = factor(
+      macro, 
+      levels = c("P", "C", "L"),
+      labels = c("Protein", "Carbohydrate", "Lipid")
+    ),
+    measure = factor(
+      measure,
+      levels = c("excr", "uneat"),
+      labels = c("Excreted", "Uneaten")
+    )
+  ) %>% 
+  ggplot(aes(
+    x = measure, 
+    y = total, 
+    ymin = total-sd, ymax = total+sd,
+    fill = feed
+  )) +
+  geom_col(position = position_dodge(), width = 0.95, colour = "black") +
+  geom_errorbar(position = position_dodge(width = 0.95), width = 0.5) +
+  facet_grid(cols = vars(macro)) +
+  prettyplot() +
+  scale_fill_manual(values = feed_pal) +
+  labs(y = "Mean total waste (t)", x = "Source")
+```
+
+# Spatially
+
+```{r}
+#| label: fig-spatial-PLC
+#| fig-height: 12
+#| fig-cap: Total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), the PD feed (middle) or the NI feed (bottom).
+
+plc1 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed")
+
+N_ins <- rbind(
+  find_read(data_analysis_path, "P_excr_farm_per_biom_summed"),
+  find_read(data_analysis_path, "P_uneat_farm_per_biom_summed")
+) %>% 
+  st_drop_geometry() %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  group_by(country, farm_ID, feed) %>% 
+  reframe(
+    mean_biom = sum(mean_biom) %>% set_units("kg t_fish-1") %>% drop_units(), 
+    sd_biom = sqrt(sum(sd_biom^2)) %>% set_units("g g_fish-1") %>% set_units("kg t_fish-1") %>% drop_units()
+  ) %>% 
+  merge(farm_locs, by = c("country", "farm_ID")) %>% 
+  st_as_sf()
+
+p_bigmap_robinson +
+  geom_sf(
+    data = N_ins, 
+    aes(colour = mean_biom, geometry = geometry), 
+    size = 2
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + 
+  guides(col = guide_colourbar(
+    title = expression("Total N inputs (kg/t salmon)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top",
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  facet_grid(rows = vars(feed)) +
+  prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank(),
+        axis.title = element_blank(),
+        legend.position = "bottom")
+```
+
+```{r}
+#| label: protein-inputs-patchwork-map
+
+p_mercator <- p_bigmap_mercator +
+  geom_sf(
+    data = N_ins,
+    aes(colour = mean_biom, geometry = geometry), 
+    size = 2.5
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", breaks = seq(0, 120, 10)) + #, limits = c(-30, 10)
+  guides(col = guide_colourbar(
+    title = expression("Total N inputs (kg/t salmon)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top",
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  # facet_wrap(facets = vars(feed), nrow = 2, ncol = 2) +
+  prettyplot() +
+  theme(
+    # strip.background = element_blank(), strip.text = element_blank(),
+    legend.position = "bottom"
+  ) +
+  labs(y = "Latitude", x = "Longitude")
+
+ins <- get_insets_mercator(p_mercator)
+
+ins[[1]] + facet_grid(cols = vars(feed))
+ins[[2]] + facet_grid(rows = vars(feed))
+ins[[3]] + facet_grid(cols = vars(feed))
+ins[[4]] + facet_grid(cols = vars(feed))
+ins[[5]] + facet_grid(cols = vars(feed))
 ```
@@
 ```{r}
-#| label: sens-results
+#| label: fig-sensitivity-results
+#| fig-cap: Sensitivity of modelled individual fish weight (blue) and total farm excretion across a full production period (red) to a 10% increase in each model parameter.
+Bars show mean values, error bars show standard deviation between farms.
+#| fig-width: 8
 
-sens_results_files <- file.path(output_sens_data_path) %>% 
-  list.files(full.names = T) %>% 
-  str_subset("results")
-```
+sens_results <- find_read(output_sens_data_path, "sens_results") %>% 
+  filter(measure %in% c("total_excr", "weight") & adj_param != "nruns") %>% 
+  mutate(measure = droplevels(measure))
 
-# Results {#sec-results}
-
-```{r}
-#| label: input-data
-
-ins_P <- list.files(per_biomass_cohort_path, full.names = T) %>% 
-  str_subset("P_uneat|P_excr") %>% 
-  purrr::map(function(nm) {qs::qread(nm)}) %>% 
-  bind_rows()
-
-ins_tot <- list.files(per_biomass_cohort_path, full.names = T) %>% 
-  str_subset("total_uneat|total_excr") %>% 
-  purrr::map(function(nm) {qs::qread(nm)}) %>% 
-  bind_rows()
-```
-
-## Total inputs (uneaten and excreted)
-
-### Through time
-
-```{r}
-#| label: fig-uneat-excr-plot-ts
-#| fig-cap: Initial look at excreted and uneaten through time
-
-ins_tot %>% 
-  mutate(t = t-365) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  group_by(country, feed, t, measure) %>% 
-  reframe(
-    sd_perbiom = sd(mean_perbiom),
-    mean_perbiom = mean(mean_perbiom)
-    ) %>% 
-  mutate(
-    mean_perbiom = mean_perbiom %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    sd_perbiom = sd_perbiom %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1")
-  ) %>% 
-  ggplot(aes(
-    x = t, 
-    y = drop_units(mean_perbiom), 
-    ymin = drop_units(mean_perbiom-sd_perbiom), 
-    ymax = drop_units(mean_perbiom+sd_perbiom), 
-    colour = feed, 
-    fill = feed
-  )) +
-  geom_line() +
-  geom_ribbon(alpha = 0.25) +
-  facet_grid(
-    rows = vars(country),
-    cols = vars(measure),
-    scales = "free"
-  ) +
+sens_results %>% 
+  ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens, fill = measure)) +
+  geom_col(position = position_dodge(), width = 0.95, alpha = 0.65, colour = "black") +
+  geom_errorbar(position = position_dodge(width = 0.95), width = 0.5) +
+  coord_flip() +
   prettyplot() +
-  scale_colour_manual(values = feed_pal) +
-  scale_fill_manual(values = feed_pal) +
-  scale_y_continuous(
-    name = expression("Loss (kg g"^-1*")"),
-    breaks = seq(0, 1, 0.2)
-  )
-```
-
-```{r}
-#| label: uneat-excr-plot-perc-diff
-
-tmp <- ins_tot %>% 
-  mutate(t = t-365) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  dplyr::select(-c(mean, sd_mean, sd, biom_mean, biom_sd, biom_sd_mean, sd_perbiom)) %>% 
-  group_by(country, t, measure) %>% 
-  pivot_wider(
-    names_from = feed, 
-    values_from = mean_perbiom
-  ) %>% 
-  mutate(
-    diff = plant_dominant - marine_dominant,
-    perc_diff = diff/plant_dominant
-  ) %>%
-  group_by(country, t, measure) %>% 
-  reframe(
-    mean_diff = mean(diff),
-    mean_perc_diff = mean(perc_diff),
-    sd_diff = sd(diff),
-    sd_perc_diff = sd(perc_diff)
-  )
-
-tmp <- tmp %>% 
-  group_by(measure, country) %>% 
-  reframe(
-    mean_t_perc_diff = mean(mean_perc_diff),
-    sd_t_perc_diff = sd(mean_perc_diff)
-    )
-```
-
-While the actual difference in excreted and uneaten feed (total loss) varied between countries and through time (@fig-uneat-excr-plot-ts), relative changes between the feeds remained consistent. 
-In both the US and Australia (all done so far), total excreted faeces was 
-`r round(100*tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`%) higher in the plant-dominant feed.
-Differences in total uneaten feed were much smaller at 
-`r round(100*-tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`%) lower in the plant-dominant feed.
-
-### At harvest
-
-```{r}
-#| label: uneat-excr-plot-end
-#| fig-cap: Caption
-
-ins_tot %>% 
-  group_by(farm_ID) %>%
-  arrange(farm_ID, t) %>%
-  mutate(
-    cumsum_mean = cumsum(mean_perbiom) %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    end_t = max(t)
-    ) %>% 
-  ungroup() %>% 
-  filter(t == end_t) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
-  geom_boxplot() +
-  facet_grid(cols = vars(measure)) +
-  prettyplot() +
-  scale_fill_manual(values = feed_pal)
-```
-
-## N inputs
-
-```{r}
-#| label: N-loss-plot-total
-#| fig-cap: Caption
-
-ins_P %>% 
-  group_by(farm_ID) %>%
-  arrange(farm_ID, t) %>%
-  mutate(
-    cumsum_mean = cumsum(mean_perbiom)*6.25 %>% 
-      set_units("g g_fish-1") %>% 
-      set_units("kg t_fish-1"),
-    end_t = max(t)
-    ) %>% 
-  ungroup() %>% 
-  filter(t == end_t) %>% 
-  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
-  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
-  geom_boxplot() +
-  facet_grid(cols = vars(measure)) +
-  prettyplot() +
-  scale_fill_manual(values = feed_pal)
+  scale_x_discrete(breaks = param_names$name, labels = param_names$lab) +
+  scale_y_continuous(breaks = seq(-10, 30, 5)) +
+  scale_fill_brewer(palette = "Set1") +
+  labs(y = "Sensitivity", x = "Adjusted parameter")
 ```

### 2025-08-01 src/dirs.R

@@ -33,6 +33,7 @@ per_biomass_cohort_path <- file.path(output_path, "per_biomass_outputs_cohort")
 output_model_farm_path <- file.path(output_path, "all_outputs_farm")
 output_model_cohort_path <- file.path(output_path, "all_outputs_cohort")
 data_analysis_path <- file.path(output_path, "data_analysis")
+comparisons_path <- file.path(data_analysis_path, "feed_comparisons")
 impacts_path <- file.path(output_path, "nutrient_impacts")
 
 # Create output directories
@@ -44,6 +45,7 @@ dir.create(per_biomass_cohort_path, showWarnings = F)
 dir.create(output_model_farm_path, showWarnings = F)
 dir.create(output_model_cohort_path, showWarnings = F)
 dir.create(data_analysis_path, showWarnings = F)
+dir.create(comparisons_path, showWarnings = F)
 dir.create(impacts_path, showWarnings = F)
 
 # From extracting_temperature

### 2025-08-01 src/map_templates.R

@@ -28,7 +28,7 @@ inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
 
 # For the corresponding patchwork map lims, basically the same, just a little refined
 inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
-  CAN1 = c(-131.5, -123, 48.25, 54.25),
+  CAN1 = c(-130.5, -123, 48.25, 54.25),
   CAN2 = c(-69, -55, 43.5, 48),
   EUR = c(-23, 28.5, 52, 71),
   CHI = c(-78, -62, -55.5, -27),
@@ -63,7 +63,7 @@ labels_offset_robinson <- c(
 labels_spec_mercator <- list(
   CAN1 = c(l = "A", h = 0, v = 0), 
   CAN2 = c(l = "B", h = 0.75, v = 0), 
-  EUR = c(l = "C", h = -0.75, v = -0.5), 
+  EUR = c(l = "C", h = -0.75, v = 0.5), 
   CHI = c(l = "D", h = 0, v = 0), 
   AUS = c(l = "E", h = 0, v = 0)
 )
@@ -101,15 +101,15 @@ get_insets_mercator <- function(map) {
       coord_sf(
         xlim = specs[["xlims"]], 
         ylim = specs[["ylims"]]
-      )  +
-      draw_label(
-        labs["l"], 
-        size = 14, 
-        fontface = "bold", 
-        x = specs[["labx"]], 
-        y = specs[["laby"]], 
-        hjust = labs["h"], vjust = labs["h"]
-      )
+      )  #+
+      # draw_label(
+      #   labs["l"], 
+      #   size = 14, 
+      #   fontface = "bold", 
+      #   x = specs[["labx"]], 
+      #   y = specs[["laby"]], 
+      #   hjust = labs["h"], vjust = labs["h"]
+      # )
   })
 }
 

### 2025-08-01 06_run_atlantic_salmon_model.qmd
Minor adj

@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% str_subset("map", negate = T) %>% walk(source)
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  str_subset("map", negate = T) %>% 
+  walk(source)
 ```
@@
 targets::tar_load(test_reference_feed)
-test_reference_feed # should be ~1430 g, or really anything other than 0
+test_reference_feed # if weight = 0 then the feeds aren't processing properly
 
 # Get harvest sizes for all farms
-targets::tar_make(names = c("harvest_size", "feed_params"))
-targets::tar_load(harvest_size)
+targets::tar_make(names = contains(c("harvest_size", "feed_params")))
+targets::tar_load(harvest_size_chunked)
+harvest_size <- harvest_size_chunked %>% bind_rows()
 
@@
 targets::tar_make(
-  names = !c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
-  seconds_meta_append = 90,
-  callr_function = NULL
+  names = c("farm_IDs_chunked", "farm_ts_data_chunked", "farm_IDs", "test_reference_feed", "farm_temp_data_chunked", "harvest_size_chunked", "farm_static_data_chunked"), 
+  seconds_meta_append = 90#, callr_function = NULL
 )
@@
 targets::tar_make(
-  names = c("farm_run", "cohort_results", "biomass_produced", "farm_results"), 
+  names = c("farm_run_chunked", "stat_names", "farm_results_chunked", "biomass_produced_chunked", "cohort_results_chunked" ), 
   seconds_meta_append = 90,
-  shortcut = T,
-  callr_function = NULL
+  shortcut = T
 )
@@
 targets::tar_load(stat_names)
-targets::tar_load(farm_IDs)
+targets::tar_load(farm_IDs_chunked) %>% unlist()
 targets::tar_load(feed_names)
@@
 print("Loading farm results...")
-targets::tar_load(farm_results)
+targets::tar_load(farm_results_chunked)
 for (stat_name in stat_names) {
-  farm_results %>% 
+  farm_results_chunked %>% 
       filter(measure == stat_name) %>% 

### 2025-08-04 05_formulating_feeds.qmd
Diet similarity

@@
          ingredient = as.factor(ingredient)) %>% 
-  merge(ingreds, by = "ingredient", all = T)
+  merge(ingreds, by = "ingredient")
 
@@
 ```
+
+# Similarity
+
+For later - how similar are the diets?
+
+```{r}
+#| label: diet-similarity
+
+feed_simil <- feed_inputs %>% 
+  select(ingredient, feed, proportion) %>% 
+  as.data.frame() %>% 
+  pivot_wider(
+    names_from = feed,
+    values_from = proportion,
+    id_cols = ingredient,
+    values_fn = as.numeric
+  ) %>% 
+  mutate(
+    diff_PD_MD = abs(marine_dominant - plant_dominant),
+    diff_PD_NI = abs(novel_inclusive - plant_dominant)
+  )
+
+1 - sum(feed_simil$diff_PD_MD, na.rm = T)
+1 - sum(feed_simil$diff_PD_NI, na.rm = T)
+```

### 2025-08-04 06_run_atlantic_salmon_model.qmd
Chunk runs

@@
 targets::tar_load(stat_names)
-targets::tar_load(farm_IDs_chunked) %>% unlist()
+targets::tar_load(farm_IDs_chunked)
+farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
 targets::tar_load(feed_names)
@@
 targets::tar_load(farm_results_chunked)
+farm_results_chunked <- farm_results_chunked %>% 
+  bind_rows()
 for (stat_name in stat_names) {
@@
 }
-rm(farm_results)
+rm(farm_results_chunked)
 
 print("Loading cohort results...")
-targets::tar_load(cohort_results)
+targets::tar_load(cohort_results_chunked)
+cohort_results_chunked <- cohort_results_chunked %>% 
+  bind_rows()
 for (stat_name in stat_names) {
-  cohort_results %>% 
+  cohort_results_chunked %>% 
       filter(measure == stat_name) %>% 
@@
 }
-rm(cohort_results)
+rm(cohort_results_chunked)
 
-targets::tar_load(biomass_produced)
-qsave(biomass_produced, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
+targets::tar_load(biomass_produced_chunked)
+qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
+rm(biomass_produced_chunked)
 ```

### 2025-08-04 targets/_targets_farmruns.R

@@ -27,28 +27,35 @@ list(
   tar_target(
     farm_IDs,
     command = {
-      # c(1:39, 2704:2721) # Australia and US only
       qs::qread(farm_ts_data_file) %>% 
         filter(farm_ID != 2703) %>% # The only Russian farm
         distinct(farm_ID) %>% 
-        pull(farm_ID)
+        pull(farm_ID) #%>% sample(112)
     }
   ),
+
   tar_target(
-    farm_ts_data, 
-    qs::qread(farm_ts_data_file) %>% 
-      merge(farm_coords, by = "farm_ID") %>%
-      filter(farm_ID == farm_IDs) %>%
-      mutate(keep = case_when(day >= t_start & day <= t_end ~ T, T ~ F)) %>% 
-      dplyr::filter(keep) %>% 
-      dplyr::select(farm_ID, day, temp_c),
-    pattern = farm_IDs
+    farm_IDs_chunked,
+    split(farm_IDs, ceiling(seq_along(farm_IDs)/20))
   ),
+
+  tar_target(
+    farm_temp_data_chunked, 
+    command = {
+      qs::qread(farm_ts_data_file) %>% 
+        filter(farm_ID %in% farm_IDs_chunked[[1]]) %>%
+        merge(farm_coords, by = "farm_ID") %>%
+        mutate(keep = case_when(day >= t_start & day <= t_end ~ T, T ~ F)) %>% 
+        dplyr::filter(keep) %>% 
+        dplyr::select(farm_ID, day, temp_c)
+    },
+    pattern = farm_IDs_chunked
+  ),
+
   tar_target(
     feed_names,
     command = {
       qs::qread(feed_params_file) %>% names()
-      # c("plant_dominant", "marine_dominant")
     }
   ),
   tar_target(
@@ -56,6 +63,7 @@ list(
     qs::qread(feed_params_file)[[feed_names]],
     pattern = feed_names
   ),
+
   tar_target(
     reference_feed,
     qs::qread(feed_params_file)[["plant_dominant"]]
@@ -65,14 +73,16 @@ list(
     test_reference_feed,
     command = {
       fi <- sample(farm_IDs, 1)
-      farm_temp <- farm_ts_data %>%
-        filter(farm_ID == fi)
       fg <- fish_growth(
         pop_params = all_params,
         species_params = all_params,
-        water_temp = farm_temp$temp_c,
[…]

### 2025-08-04 index.qmd
Summarising some results

@@
 |---------|:-------------------------------------------------|
-| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
-| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input patterns and their relative impacts |
+| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers, to try and acertain impacts on vulnerable species |
+| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input (runoff) patterns and the relative impacts of farm nutrients |
 
@@
 pop_params <- find_read(output_species_data_path, "pop_params")
+
+farm_locs <- find_read(output_farm_data_path, "geometry") %>% 
+  rename(farm_ID = farm_id) %>% 
+  mutate(country = as.factor(country))
+countries_long <- farm_locs %>%
+  mutate(
+    longitude = map_dbl(geometry, ~st_coordinates(.x)[1]),
+    latitude = map_dbl(geometry, ~st_coordinates(.x)[2])
+  ) %>% 
+  st_drop_geometry() %>% 
+  group_by(country) %>% 
+  reframe(latitude = mean(latitude)) %>% 
+  arrange(-latitude) %>% 
+  pull(country) %>% 
+  as.character() 
+countries_short <- countries_long %>% 
+  str_replace("United States of America", "USA") %>% 
+  str_replace("Russian Federation", "Russia") %>% 
+  str_replace("United States of America", "USA")
+farm_locs <- farm_locs %>% 
+  mutate(
+    country = factor(
+      country, 
+      levels = countries_long,
+      labels = countries_short
+    ))
 
@@
 
+The NI diet was more efficient than the PD diet.
+When farms were fed the NI diet they had an average FCE* of `r fpr_pb1$NI`, compared to the average FCE of `r fpr_pb1$PD` when farms were fed the PD diet, and feeding the NI diet resulted in `r bpr2$NI`% more biomass produced with the same population compared to the PD diet.
+
+::: {.aside}
+*Note that when I refer to "FCE" here I'm talking about the "PLC weight" (weight of protein + lipid + carbohydrate) of feed, which may differ from its actual weight because of the inclusion of minerals and non-digestible material.
+:::
+
+Despite this, nutrients lost to the environment were generally highest in the NI diet and lowest in the MD diet. 
+In terms of total waste, the NI and PD diets were very similar.
+I initially thought that this was because the NI and PD diets are more similar than the MD and PD diets, but this doesn't match up with the numbers (PD and NI diets are 63.3% the same, while the PD and MD diets are 54.3% the same).
+The MD diet had markedly lower total waste than either the PD or NI diets.
+
+However, the composition of waste lost to the environment was very different between the diets, particularly in terms of proteins and carbohydrates (@fig-PLC-waste-comparison).
+The PD diet had the lowest protein waste output and the NI diet had the highest, while the MD diet had the lowest carbohydrate and lipid waste outputs and the PD diet the highest.
+Overall, changing from the PD diet to the NI diet would result in a `r abs(plc3$NI_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively, while changing to the MD diet would result in a `r abs(plc3$MD_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively.
+
+Consequently, while total waste was only `r tow2$NI`% higher when farms were fed the NI diet, protein waste was `r plc3$NI_P`% higher and nitrogen waste was `r nit2$NI`% higher relative to when farms were fed the PD diet.
+
+Proteins in the NI diet were only slightly less digestible than those used in the PD diet (@tbl-modelled-feeds), but this difference, combined with the higher protein content in the NI diet, resulted in the large difference in nitrogen lost to the environment.
+
 | Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
 |:--------------------------|:----------:|:----------:|:----------:|:----------:|:----------:|
-| Salmon biomass produced (t) | `r bpr1$PD` | `r bpr1$MD` | `r bpr1$NI` | `r bpr2$MD` | `r bpr2$NI` |
-| Feed provided (t) | `r fpr1$PD` | `r fpr1$MD` | `r fpr1$NI` | `r fpr2$MD` | `r fpr2$NI` |
-| Feed provided (kg/kg salmon) | `r fpr_pb1$PD` | `r fpr_pb1$MD` | `r fpr_pb1$NI` | `r fpr_pb2$MD` | `r fpr_pb2$NI` |
-| Uneaten feed (t) | `r tuf1$PD` | `r tuf1$MD` | `r tuf1$NI` | `r tuf2$MD` | `r tuf2$NI` |
-| Excreted waste (t) | `r tew1$PD` | `r tew1$MD` | `r tew1$NI` | `r tew2$MD` | `r tew2$NI` |
-| Total waste (E+U, t) | `r tow1$PD` | `r tow1$MD` | `r tow1$NI` | `r tow2$MD` | `r tow2$NI` |
+| Salmon biomass produced (t)                         | `r bpr1$PD`        | `r bpr1$MD`        | `r bpr1$NI`        | `r coln(bpr2$MD)`    | `r coln(bpr2$NI)`    |
+| Feed provided (t)                                   | `r fpr1$PD`        | `r fpr1$MD`        | `r fpr1$NI`        | `r coln(fpr2$MD)`    | `r coln(fpr2$NI)`    |
+| Feed provided (kg/kg salmon)                        | `r fpr_pb1$PD`     | `r fpr_pb1$MD`     | `r fpr_pb1$NI`     | `r coln(fpr_pb2$MD)` | `r coln(fpr_pb2$NI)` |
+| Uneaten feed (t)                                    | `r tuf1$PD`        | `r tuf1$MD`        | `r tuf1$NI`        | `r coln(tuf2$MD)`    | `r coln(tuf2$NI)`    |
+| Excreted waste (t)                                  | `r tew1$PD`        | `r tew1$MD`        | `r tew1$NI`        | `r coln(tew2$MD)`    | `r coln(tew2$NI)`    |
+| Total waste (E+U, t)                                | `r tow1$PD`        | `r tow1$MD`        | `r tow1$NI`        | `r coln(tow2$MD)`    | `r coln(tow2$NI)`    |
 | Proportion of total waste composed of excretion (%) | `r epw$PD`         | `r epw$MD`         | `r epw$NI`         |                      |                      |
-| Total protein waste (t) | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r plc3$MD_P` | `r plc3$NI_P` |
-| Total carbohydrate waste (t) | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r plc3$MD_C` | `r plc3$NI_C` |
-| Total lipid waste (t) | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r plc3$MD_L` | `r plc3$NI_L` |
+| Total protein waste (t)                             | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r coln(plc3$MD_P)`  | `r coln(plc3$NI_P)`  |
+| Total carbohydrate waste (t)                        | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r coln(plc3$MD_C)`  | `r coln(plc3$NI_C)`  |
+| Total lipid waste (t)                               | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r coln(plc3$MD_L)`  | `r coln(plc3$NI_L)`  |
 | Proportion of protein waste from excretion (%)      | `r plc2$PD_P`      | `r plc2$MD_P`      | `r plc2$NI_P`      |                      |                      |
@@
 | Proportion of lipid waste from excretion (%)        | `r plc2$PD_L`      | `r plc2$MD_L`      | `r plc2$NI_L`      |                      |                      |
-| Total N from uneaten feed (t) | `r niu1$PD` | `r niu1$MD` | `r niu1$NI` | `r niu2$MD` | `r niu2$NI` |
-| Total N from excreted waste (t) | `r nie1$PD` | `r nie1$MD` | `r nie1$NI` | `r nie2$MD` | `r nie2$NI` |
-| Total N inputs (E+U, t) | `r nit1$PD` | `r nit1$MD` | `r nit1$NI` | `r nit2$MD` | `r nit2$NI` |
+| Total N from uneaten feed (t)                       | `r niu1$PD`        | `r niu1$MD`        | `r niu1$NI`        | `r coln(niu2$MD)`    | `r coln(niu2$NI)`    |
+| Total N from excreted waste (t)                     | `r nie1$PD`        | `r nie1$MD`        | `r nie1$NI`        | `r coln(nie2$MD)`    | `r coln(nie2$NI)`    |
+| Total N inputs (E+U, t)                             | `r nit1$PD`        | `r nit1$MD`        | `r nit1$NI`        | `r coln(nit2$MD)`    | `r coln(nit2$NI)`    |
 : Summary of all results.
 Unless otherwise specified, values presented are means across all farms, summed across a single production period.
+In the % change columns, the colour of the text indicates whether there is an increase (red) or a decrease (green).
 Some cells of this table are blank - sometimes that means it doesn't make sense to fill that cell, but sometimes it means I haven't got to it yet.
 {#tbl-results-summary}
-
-So here are the major themes I'm getting from @tbl-results-summary:
-
-::: {.aside}
-*Note that when I refer to "FCE" here I'm talking about the PLC weight (protein + lipid + carbohydrate) weight of feed, which may differ from its actual weight because of the inclusion of minerals and non-digestible material.
-:::
-
-1.
-The NI diet was more efficient than the PD diet.
-When farms were fed the NI diet they had an average FCE* of `r fpr_pb1$NI`, compared to the average FCE of `r fpr_pb1$PD` when farms were fed the PD diet, and feeding the NI diet resulted in `r bpr2$NI`% more biomass produced with the same population compared to the PD diet.
-2. Despite this, nutrients lost to the environment were generally highest in the NI diet and lowest in the MD diet. 
-  * In terms of total waste inputs (bulk mass), the NI and PD diets were very similar (probably due to their very similar ingredient compositions).
-The MD diet had markedly lower total waste inputs than either the PD or NI diets.
-3.
-However, the PLC composition of nutrients was very different between the diets (@fig-PLC-waste-comparison).
-The PD diet had the lowest protein waste output and the NI diet had the highest, while the MD diet had the lowest carbohydrate and lipid waste outputs and the PD diet the highest.
-Overall, changing from the PD diet to the NI diet would result in a `r abs(plc3$NI_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively, while changing to the MD diet would result in a `r abs(plc3$MD_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively.
-4. Overall, nitrogen inputs were `r nit2$NI`% higher in the NI diet and `r nit2$MD`% higher in the MD diet.
 
@@
 
+::: {.aside}
+I accidentally used raw total waste in @fig-PLC-waste-comparison instead of waste per kg of biomass
+:::
+
 ```{r}
@@
       measure,
-      levels = c("excr", "uneat"),
-      labels = c("Excreted", "Uneaten")
+      levels = c("uneat", "excr"),
+      labels = c("Uneaten", "Excreted")
     )
@@
   labs(y = "Mean total waste (t)", x = "Source")
+```
+
+# N inputs only
+
+```{r}
+#| label: N-inputs-comparisons
+
+N_uneat <- find_read(comparisons_path, "N_uneat_farm_per_biom_summed")
+N_excr <- find_read(comparisons_path, "N_excr_farm_per_biom_summed")
+
+N_all <- rbind(N_uneat, N_excr) %>% 
+  st_drop_geometry() %>% 
+  mutate(
+    measure = droplevels(measure),
+    country = factor(country,
+                   levels = countries_long,
+                   labels = countries_short)
+  )
+
+# ggplot(N_all, aes(x = country, y = mean_biom, fill = feed)) +
+#   geom_boxplot() +
+#   facet_grid(cols = vars(measure)) +
+#   scale_fill_manual(values = feed_pal)
 ```
@@
 Sys.setenv(TAR_PROJECT = "project_farmruns")
-tar_load(farm_ts_data)
+farm_ts_data <- tar_read(farm_ts_data_chunked) %>% bind_rows()
 min_T <- min(farm_ts_data$temp_c)
@@
 | Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`%) |
-: Feed macronutrient details (composition in feed, digestibility).
+: Feed macronutrient details (composition in feed, digestibility). {#tbl-modelled-feeds}
 

### 2025-08-15 06_run_atlantic_salmon_model.qmd
Small QOL improvements

@@
   )
+tar_prune()
 ```
@@
 targets::tar_outdated()
-targets::tar_prune()
 
@@
 
-meta <- targets::tar_meta() %>% 
-  filter(grepl("farm_run", name))
-meta$seconds %>% mean()/60 # average minutes per target
+tar_prune()
+
+# meta <- targets::tar_meta() %>% 
+#   filter(grepl("farm_run", name))
+# meta$seconds %>% mean()/60 # average minutes per target
 ```

### 2025-08-15 index.qmd
Small QOL improvements

@@
   message: false
-  cache: true
+  cache: true # quarto render index.qmd --cache-refresh
 knitr: 
@@
     theme(
-      text = element_text(family = "sans", size = 12, colour = "black"),
-      legend.position = "none"
+      text = element_text(family = "serif", size = 14, colour = "black"),
+      legend.position = "none",
+      axis.title.y = element_text(margin = margin(r = 5)),
+      axis.title.x = element_text(margin = margin(t = 5))
     )
@@
 ```{r}
-#| label: fig-spatial-PLC
+#| label: fig-spatial-N-inputs
 #| fig-height: 12
 #| fig-cap: Total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), the PD feed (middle) or the NI feed (bottom).
-
-plc1 <- find_read(comparisons_path, "PLC_uneat_excr_farm_summed")
 
@@
     title.vjust = 1, title.hjust = 0.5,
-    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
     barheight = 1.5, barwidth = 20,
@@
   facet_grid(rows = vars(feed)) +
-  prettyplot() +
+  # prettyplot() +
   theme(strip.background = element_blank(), strip.text = element_blank(),
@@
 ```{r}
-#| label: protein-inputs-patchwork-map
+#| label: N-inputs-patchwork-map
 
@@
 harv_size %>% 
-  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
+  mutate(weight = weight %>% set_units("g") %>% set_units("kg") %>% drop_units()) %>% 
   select(c(farm_ID, weight)) %>% 
@@
   scale_y_continuous(limits = c(0,500)) +
-  labs(y = "Frequency", x = "Harvest weight") +
+  scale_x_continuous(breaks = seq(0,7,0.5)) +
+  labs(y = "Frequency", x = "Harvest weight (kg)") +
   prettyplot() +

### 2025-08-15 targets/_targets_farmruns.R

@@ -30,7 +30,7 @@ list(
       qs::qread(farm_ts_data_file) %>% 
         filter(farm_ID != 2703) %>% # The only Russian farm
         distinct(farm_ID) %>% 
-        pull(farm_ID) #%>% sample(112)
+        pull(farm_ID)
     }
   ),
 
@@ -55,7 +55,8 @@ list(
   tar_target(
     feed_names,
     command = {
-      qs::qread(feed_params_file) %>% names()
+      # qs::qread(feed_params_file) %>% names() # Take all names from the feeds file
+      c("marine_dominant", "plant_dominant") # OR specify only certain names
     }
   ),
   tar_target(

### 2025-09-04 07_methods_and_supplementaries/07_methods_and_supplementaries.qmd

@@
 
-source(here("src/spatial_templates.R"))
-source(here("src/model_functions.R"))
+source(here("00_model_functions.R"))
 
 # Sys.setenv(TAR_PROJECT = "project_main")
-base_path <- file.path("C:", "Users", "treimer", "Documents", "R-temp-files", "local_to_global_mariculture_modelling")
-targets_store <- file.path(base_path, "targets", "_targets_individual")
-farm_IDs <- tar_read(farm_IDs, store = targets_store)
+indi_store <- here() %>% file.path("04_targets_individual")
+farm_IDs <- tar_read(farm_IDs, store = indi_store)
 b1 <- sample(length(farm_IDs), 100, replace = F)
@@
 # This is the full idealised year (2 years?) of temperature data
-sst <- file.path(base_path, "data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()
+sst <- here() %>% file.path("data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()
 
 # This is the actual temperature curve for the farming period
-farm_temp <- tar_read(example_individual, store = targets_store, branches = b1)
+farm_temp <- tar_read(example_individual, store = indi_store, branches = b1)
 ```
@@
 
-species_params <- tar_read(species_params, store = targets_store)
-pop_params <- tar_read(pop_params, store = targets_store)
-weight <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
-SGR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
-FCR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)
+species_params <- tar_read(species_params, store = indi_store)
+pop_params <- tar_read(pop_params, store = indi_store)
+weight <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
+SGR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
+FCR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)
 
@@
 
-df <- data.frame(water_temp = seq(-5, 30, 0.25))
+df <- data.frame(water_temp = seq(0, 30, 0.25))
 df$resp <- exp(species_params['pk']*df$water_temp)
@@
 
-feed_params_protein <- tar_read(feed_params_protein, store = targets_store)
-feed_params_carbs <- tar_read(feed_params_carbs, store = targets_store)
-feed_params_lipids <- tar_read(feed_params_lipids, store = targets_store)
+feed_params_protein <- tar_read(feed_params_protein, store = indi_store)
+feed_params_carbs <- tar_read(feed_params_carbs, store = indi_store)
+feed_params_lipids <- tar_read(feed_params_lipids, store = indi_store)
 ```
@@
 #c(b1, b2, b3))
-ing_pot <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
-ing_act <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
-food_prov <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
+ing_pot <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
+ing_act <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
+food_prov <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
 ```
@@
 
-params <- tar_read(sens_all_params, store = targets_store)
+params <- tar_read(sens_all_params, store = indi_store)
 pnames <- names(params)

### 2025-09-04 08_relative_N_inputs.qmd
Proper index of files

@@
 
-source("00_dirs.R")
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")
@@
 
-N_input <- output_cohorts_data_path %>% list.files(full.names = T) %>% 
+N_input <- per_biomass_cohort_path %>% 
+  list.files(full.names = T) %>% 
   str_subset("allfarms") %>% 

### 2025-09-04 archive/04_atlantic_salmon_synthesis/04_atlantic_salmon_synthesis.qmd

---
title: "Synthesising the model outputs"
format: html
editor: source

execute:
  eval: false
  echo: false
  warning: false
  message: false
  cache: true
---

```{r setup}
#| code-summary: Setup

# library(tidyverse)
library(dplyr)
library(arrow)
library(magrittr)
library(here)
library(qs)
library(sf)
library(dtplyr)
library(future)
library(furrr)
library(stringr)
library(conflicted)
conflicts_prefer(dplyr::filter(), dplyr::select())

this_species <- "atlantic_salmon"
```

```{r locations files}
#| code-summary: Bring in spatial file with farm IDs

# locations_file <- qread(file = sprintf("data/_general_data/farm_locations/%s_locations_w_temps.qs", this_species)) %>% 
#   select(-c(day, temp_c)) %>% 
#   group_by(farm_id) %>% 
#   group_split() %>% 
#   map_df(.f = \(x){return(x %>% slice(1))})

locations_file <- qread(file = sprintf("data/_general_data/farm_locations/%s_locations_w_temps.qs", this_species)) %>% 
  select(-c(day, temp_c)) %>% 
  group_by(farm_id) %>% 
  slice_head(n = 1) %>% 
  ungroup()
```

We are primarily interested in biomass produced, excretion (ammonia), faeces, and wasted feed broken down to nitrogen.

REFERENCE FEED

Bring in relevant model outputs.

```{r}
this_feed <- "reference"

biomass_files <- list.files(path = here("data/atlantic_salmon/data_products/model_outputs/"), pattern = "biomass_", full.names = TRUE)

faeces_files <- list.files(path = here("data/atlantic_salmon/data_products/model_outputs/"), pattern = "excretion_", full.names = TRUE)

feed_waste_files <- list.files(path = here("data/atlantic_salmon/data_products/model_outputs/"), pattern = "feed_waste_", full.names = TRUE)

ammonia_files <- list.files(path = here("data/atlantic_salmon/data_products/model_outputs/"), pattern = "NH4_", full.names = TRUE)

weight_files <- list.files(path = here("data/atlantic_salmon/data_products/model_outputs/"), pattern = "weight_", full.names = TRUE)
```

Reference feeds - loop through the locations file to add the biomass, excretion, faeces, uneaten feed in N.

```{r}
feed_type <-  "reference"

commercial_size <- read.csv(sprintf(here("data/%s/params/Parameters_%s.csv"), this_species, feed_type)) %>% 
  filter(Description == "Commercial size") %>% 
  pull(Value) %>% 
  as.numeric()

farm_ids <- locations_file$farm_id
# this_id <- farm_ids[[29]]

#Set up multicore
future::plan(strategy = "multisession", workers = parallel::detectCores()-2)

farm_N_reference <- future_map(.x = farm_ids, .f = \(this_id){
  message("Synthesising nitrogen data at harvest this farmID_", this_id)

  weight_days <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(days)
  weights <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(weight)

  harvest_day <- 
    weight_days %>% 
    pluck(if(tail(weights, n=2)[1]>commercial_size){
      head(which(weights>commercial_size), n =2)[1]
    } else {
      tail(weight_days, n=2)[1]
      } )

# biomass
this_biomass_mean <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
  slice(harvest_day) %>% pull(biomass)/1e+6

this_biomass_lb <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
  slice(harvest_day) %>% pull(lower_bound)/1e+6

this_biomass_ub <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
  slice(harvest_day) %>% pull(upper_bound)/1e+6

# Weight
this_weight_mean <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(weight)

this_weight_lb <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(lower_bound)

this_weight_ub <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day)%>% pull(upper_bound)

# faeces 
this_faeces_mean <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_excretion) %>% sum()/6.25/1e+6

this_faeces_lb <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

this_faeces_ub <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

# feed waste
this_feed_waste_mean <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_waste) %>% sum()/6.25/1e+6

this_feed_waste_lb <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

this_feed_waste_ub <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

# excretion (NH4)
this_ammonia_mean <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
  slice(1:harvest_day) %>% pull(nh4_production) %>% sum()/1e+6

this_ammonia_lb <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
  slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/1e+6

this_ammonia_ub <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
  slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/1e+6

return(data.frame(
  farm_id = this_id, 
  biomass_mean = this_biomass_mean, 
  biomass_lb = this_biomass_lb, 
  biomass_ub = this_biomass_ub, 
  faeces_mean = this_faeces_mean, 
  faeces_lb = this_faeces_lb, 
  faeces_ub = this_faeces_ub, 
  excretion_mean = this_ammonia_mean, 
  excretion_lb = this_ammonia_lb, 
  excretion_ub = this_ammonia_ub, 
  feed_waste_mean = this_feed_waste_mean, 
  feed_waste_lb = this_feed_waste_lb, 
  feed_waste_ub = this_feed_waste_ub, 
  total_N_mean = sum(this_faeces_mean, this_ammonia_mean, this_feed_waste_mean), 
  total_N_lb = sum(this_faeces_lb, this_ammonia_lb, this_feed_waste_lb), 
  total_N_ub = this_feed_waste_ub
))
}) %>% bind_rows()

farm_N_reference_spatial <- 
  locations_file %>% 
  select(iso3c, country, tonnes_per_farm, geometry, farm_id) %>% 
  distinct() %>% 
  left_join(farm_N_reference)

qsave(x = farm_N_reference_spatial, file =  sprintf(here("data/atlantic_salmon/data_products/model_summaries/%s/nitrogen_summary.qs"), this_feed))

```

PAST FEEDS

Bring in the relevant model outputs.

```{r}

this_feed <- "past"

biomass_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "biomass_", full.names = TRUE)

faeces_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "excretion_", full.names = TRUE)

feed_waste_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "feed_waste_", full.names = TRUE)

ammonia_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "NH4_", full.names = TRUE)

weight_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "weight_", full.names = TRUE)

```

Past feeds - loop through the locations file to add the biomass, excretion, faeces, uneaten feed in N.

```{r}

feed_type <-  "past"

commercial_size <- read.csv(sprintf(here("data/%s/params/Parameters_%s.csv"), this_species, feed_type)) %>% filter(Description == "Commercial size") %>% pull(Value) %>% as.numeric()

farm_ids <- locations_file$farm_id

this_id <- farm_ids[[29]]

#Set up multicore

future::plan(strategy = "multisession", workers = parallel::detectCores()-2)

farm_N_past <-

  future_map(.x = farm_ids, .f = \(this_id){

  message("Synthesising nitrogen data at harvest this farmID_", this_id)

  weight_days <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(days)
  weights <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(upper_bound)

  harvest_day <- 
    weight_days %>% 
    pluck(if(tail(weights, n=2)[1]>commercial_size){
      head(which(weights>commercial_size), n =2)[1]
    } else {
      tail(weight_days, n=2)[1]
      } )

   #biomass
  this_biomass_mean <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(biomass)/1e+6

  this_biomass_lb <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(lower_bound)/1e+6

   this_biomass_ub <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(upper_bound)/1e+6

   #weight
   this_weight_mean <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(weight)

   this_weight_lb <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(lower_bound)

   this_weight_ub <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day)%>% pull(upper_bound)

  #faeces 
    this_faeces_mean <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_excretion) %>% sum()/6.25/1e+6

     this_faeces_lb <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

  this_faeces_ub <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

  #feed waste
  this_feed_waste_mean <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_waste) %>% sum()/6.25/1e+6

  this_feed_waste_lb <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

  this_feed_waste_ub <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

  #excretion (NH4)
  this_ammonia_mean <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(nh4_production) %>% sum()/1e+6

  this_ammonia_lb <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/1e+6

  this_ammonia_ub <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/1e+6

  return(data.frame(farm_id = this_id, biomass_mean = this_biomass_mean, biomass_lb = this_biomass_lb, biomass_ub = this_biomass_ub, faeces_mean = this_faeces_mean, faeces_lb = this_faeces_lb, faeces_ub = this_faeces_ub, excretion_mean = this_ammonia_mean, excretion_lb = this_ammonia_lb, excretion_ub = this_ammonia_ub, feed_waste_mean = this_feed_waste_mean, feed_waste_lb = this_feed_waste_lb, feed_waste_ub = this_feed_waste_ub, total_N_mean = sum(this_faeces_mean, this_ammonia_mean, this_feed_waste_mean), total_N_lb = sum(this_faeces_lb, this_ammonia_lb, this_feed_waste_lb), total_N_ub = this_feed_waste_ub))

}) %>% bind_rows()

farm_N_past_spatial <- 
  locations_file %>% 
  select(iso3c, country, tonnes_per_farm, geometry, farm_id) %>% 
  distinct() %>% 
  left_join(farm_N_past)

qsave(x = farm_N_past_spatial, file =  sprintf(here("data/atlantic_salmon/data_products/model_summaries/%s/nitrogen_summary.qs"), this_feed))

```

FUTURE FEEDS

Bring in the relevant model outputs.

```{r}

this_feed <- "future"

biomass_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "biomass_", full.names = TRUE)

faeces_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "excretion_", full.names = TRUE)

feed_waste_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "feed_waste_", full.names = TRUE)

ammonia_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "NH4_", full.names = TRUE)

weight_files <- list.files(path = sprintf(here("data/atlantic_salmon/data_products/model_outputs/%s"), this_feed), pattern = "weight_", full.names = TRUE)

```

Future feeds - loop through the locations file to add the biomass, excretion, faeces, uneaten feed in N.

```{r}

feed_type <-  "future"

commercial_size <- read.csv(sprintf(here("data/%s/params/Parameters_%s.csv"), this_species, feed_type)) %>% filter(Description == "Commercial size") %>% pull(Value) %>% as.numeric()

farm_ids <- locations_file$farm_id

this_id <- farm_ids[[29]]

#Set up multicore

future::plan(strategy = "multisession", workers = parallel::detectCores()-2)

farm_N_future <-

  future_map(.x = farm_ids, .f = \(this_id){

  message("Synthesising nitrogen data at harvest this farmID_", this_id)

  weight_days <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(days)
  weights <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% pull(upper_bound)

  harvest_day <- 
    weight_days %>% 
    pluck(if(tail(weights, n=2)[1]>commercial_size){
      head(which(weights>commercial_size), n =2)[1]
    } else {
      tail(weight_days, n=2)[1]
      } )

    #biomass
  this_biomass_mean <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(biomass)/1e+6

  this_biomass_lb <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(lower_bound)/1e+6

   this_biomass_ub <- qread(biomass_files[grep(pattern = sprintf("farmID_%s.qs", this_id), biomass_files)]) %>% 
    slice(harvest_day) %>% pull(upper_bound)/1e+6

   #weight
   this_weight_mean <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(weight)

   this_weight_lb <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day) %>% pull(lower_bound)

   this_weight_ub <- qread(weight_files[grep(pattern = sprintf("farmID_%s.qs", this_id), weight_files)]) %>% filter(days == harvest_day)%>% pull(upper_bound)

  #faeces 
    this_faeces_mean <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_excretion) %>% sum()/6.25/1e+6

     this_faeces_lb <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

  this_faeces_ub <- qread(faeces_files[grep(pattern = sprintf("farmID_%s.qs", this_id), faeces_files)]) %>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

  #feed waste
  this_feed_waste_mean <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(mean_waste) %>% sum()/6.25/1e+6

  this_feed_waste_lb <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/6.25/1e+6

  this_feed_waste_ub <- qread(feed_waste_files[grep(pattern = sprintf("farmID_%s.qs", this_id), feed_waste_files)])%>% filter(nutrient == "Protein") %>% slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/6.25/1e+6

  #excretion (NH4)
  this_ammonia_mean <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(nh4_production) %>% sum()/1e+6

  this_ammonia_lb <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(lower_bound) %>% sum()/1e+6

  this_ammonia_ub <- qread(ammonia_files[grep(pattern = sprintf("farmID_%s.qs", this_id), ammonia_files)]) %>% 
    slice(1:harvest_day) %>% pull(upper_bound) %>% sum()/1e+6

  return(data.frame(farm_id = this_id, biomass_mean = this_biomass_mean, biomass_lb = this_biomass_lb, biomass_ub = this_biomass_ub, faeces_mean = this_faeces_mean, faeces_lb = this_faeces_lb, faeces_ub = this_faeces_ub, excretion_mean = this_ammonia_mean, excretion_lb = this_ammonia_lb, excretion_ub = this_ammonia_ub, feed_waste_mean = this_feed_waste_mean, feed_waste_lb = this_feed_waste_lb, feed_waste_ub = this_feed_waste_ub, total_N_mean = sum(this_faeces_mean, this_ammonia_mean, this_feed_waste_mean), total_N_lb = sum(this_faeces_lb, this_ammonia_lb, this_feed_waste_lb), total_N_ub = this_feed_waste_ub))

}) %>% bind_rows()

farm_N_future_spatial <- 
  locations_file %>% 
  select(iso3c, country, tonnes_per_farm, geometry, farm_id) %>% 
  distinct() %>% 
  left_join(farm_N_future)

qsave(x = farm_N_future_spatial, file =  sprintf(here("data/atlantic_salmon/data_products/model_summaries/%s/nitrogen_summary.qs"), this_feed))

```

### 2025-09-04 archive/08_manuscript/manuscript.qmd

--- 2025-06-04 _manuscript.qmd
@@
 
-### Composition
+### Excreted composition
 
@@
 
-* Composition does not change through time or with increasing biomass (because digestibility does not change with fish size or temeprature)
-
 ```{r composition-throughtime}
-#| eval: false
-
 excreted_all %>% 

### 2025-09-04 docs/index.qmd

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true
  freeze: auto
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

# Table of Contents

All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github. 
While this page (the index) has code that runs prior to rendering, all code in the subsequent pages has not been run for rendering.

## Main analysis

The main analysis for this project focuses on the differences in total protein, carbohydrate, lipid and nitrogen losses between feeds.

| Page | Description |
|---------|:-------------------------------------------------|
| **[Data Tidying](01_tidying_data.html)** | Initial data tidying and preparation |
| **[Extracting Production Locations](02_extracting_production_locations.html)** | Identification and processing of mariculture production site locations |
| **[Assessing Species Potential](03_assessing_species_potential.html)** | Evaluation of species suitability for different locations |
| **[Extracting Temperatures](04_extracting_temperatures.html)** | SST data extraction and processing for model inputs |
| **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
| **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |

## Extra analysis

The extra analyses for this project involved some exploration into potential impacts of nutrient losses. This will likely not make it into the final manuscript.

| Page | Description |
|---------|:-------------------------------------------------|
| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers |
| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input patterns and their relative impacts |

```{r setup}
#| cache: false
#| message: false

library(magrittr)
library(units)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggh4x)
library(here)
library(ggpubr)
library(cowplot)
library(patchwork)
library(qs)
library(arrow)
library(targets)
library(sf)
library(terra)
library(rnaturalearth)
library(rnaturalearthdata)
library(rnaturalearthhires)
library(dtplyr)
library(furrr)
library(purrr)
library(future)
library(readxl)
library(conflicted)
library(lubridate)
library(RColorBrewer)
conflicts_prefer(dplyr::select(), dplyr::filter(), dplyr::intersect())
# This markdown uses TinyTex - install with tinytex::install_tinytex()

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)

packages <- c("magrittr", "dplyr", "tidyr", "stringr", "ggplot2", "arrow", "targets", "sf", "terra", "rnaturalearth", "furrr", "future", "units", "lubridate", "worrms", "aquamapsdata") %>% sort()
```

```{r global-variables}
#| include: false
#| cache: false

remove_unit("g_fish")
remove_unit("kg_fish")
remove_unit("t_fish")
install_unit("g_fish")
install_unit("kg_fish", "1000 g_fish")
install_unit("t_fish", "1000 kg_fish")

# Set up parallel processing
# plan(multisession, workers = parallelly::availableCores()-1)

# Filenames
# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))

species_params <- find_read(output_species_data_path, "species_params")
pop_params <- find_read(output_species_data_path, "pop_params")

feed_pal <- c(
  "past" = "#E41A1C", 
  "reference" = "#377EB8", 
  "future" = "#4DAF4A",
  "plant_dominant" = "#4DAF4A",
  "marine_dominant" = "#377EB8",
  "novel_inclusive" = "#E41A1C"
)
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", 
  "P" = "darkred", 
  "carbohydrates" = "steelblue", 
  "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", 
  "L" = "darkgoldenrod1"
)

prettyplot <- function() {
  theme_classic() +
    theme(
      text = element_text(family = "sans", size = 12, colour = "black"),
      legend.position = "none"
    )
}
```

# Model functioning

## Population and biomass

```{r raw biomass and weight data}
weight_cohort <- find_read(output_model_cohort_path, "weight_stat_all_farms")
biomass_cohort <- find_read(output_model_cohort_path, "biomass_stat_all_farms")
```

Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed, @fig-harvest-size). A population timeseries was then generated using the standard mortality rate (`r round(unname(pop_params['mortmyt'])*100, 3)` % d$^{-1}$).

```{r}
#| label: fig-harvest-size
#| fig-cap: |
#|   Frequency distribution of harvest sizes used to create the population timeseries for each farm, as predicted by the fish-growth model.

harv_size <- find_read(output_farm_data_path, "farm_harvest_size")

harv_size %>% 
  mutate(weight = weight %>% set_units("g") %>% set_units("kg")) %>% 
  select(c(farm_ID, weight)) %>% 
  ggplot(aes(x = weight)) +
  geom_histogram(binwidth = 0.25, colour = "black", fill = "salmon", alpha = 0.75) +
  scale_y_continuous(limits = c(0,500)) +
  labs(y = "Frequency", x = "Harvest weight") +
  prettyplot() +
  theme(aspect.ratio = 0.75)
```

Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.

```{r}
#| label: fig-cohorts
#| eval: false
#| fig-cap: | 
#|   Example of how the overlapping cohorts combine into a single farm production curve (in this case biomass). The left plot shows the farm biomass produced by each cohort from initialisation to harvest, while the right plot shows the combined farm biomass over the course of a single production period of 548 days.

fnms <- output_growth_data_path %>% 
  list.files(full.names = T) %>% 
  str_subset("reference")

df <- qs::qread(fnms[1])[["biomass_stat"]] %>% 
  as.data.frame() %>% 
  mutate(mean = set_units(mean, "g") %>% set_units("t"),
         sd = set_units(sd, "g") %>% set_units("t")) %>% 
  select(-farm_ID)

df <- rbind(
  df %>% mutate(cohort = 1),
  df %>% mutate(t = t+365, cohort = 2),
  df %>% mutate(t = t+730, cohort = 3)
) %>% 
  mutate(t = (t-min(t))+1,
         split = "Split by cohort")

min_t <- min(df$t[df$cohort == 2])
max_t <- max(df$t[df$cohort == 2])

df_2 <- df %>% 
  filter(t %in% min_t:max_t) %>% 
  mutate(sd = sd/mean) %>% 
  group_by(t) %>% 
  reframe(sd = sqrt(sum(sd^2)),
          mean = sum(mean),
          sd = sd*mean) %>% 
  mutate(cohort = "all",
         split = "Totalled")

df <- rbind(df, df_2) %>% 
  mutate(cohort = as.factor(cohort))

ggplot(df, aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = as.factor(cohort))) +
  geom_line(linewidth = 0.75) +
  geom_ribbon(linetype = "dotted", alpha = 0) +
  facet_grid(cols = vars(split)) +
  scale_x_continuous(breaks = seq(0, 1600, 120)) +
  scale_colour_manual(values = cohort_pal) +
  prettyplot() +
  labs(y = "Farm biomass", x = "Day of production")
```

```{r}
#| label: pop-biom-data

biomass_farm <- find_read(output_model_farm_path, "biomass_stat") %>% 
  group_by(farm_ID, feed) %>% 
  slice_max(t) %>% 
  ungroup()

production <- find_read(output_farm_data_path, "farm_static_data") %>% 
  merge(biomass_farm, by = "farm_ID", all.x = F) %>% 
  mutate(
    mean = set_units(mean, "g"),
    diff = set_units(mean - tonnes_per_farm, "t"),
    perc_diff = diff/tonnes_per_farm
  ) %>% 
  group_by(country, feed) %>% 
  reframe(
    min_percdiff = min(perc_diff),
    max_percdiff = max(perc_diff),
    mean_percdiff = mean(perc_diff)
  )
```

By this method, farm biomass as predicted by the model predicted farm tonnage relatively accurately. Predicted farm biomass was within `r round(100*min(production$min_percdiff),1)`% -- `r round(100*max(production$max_percdiff),1)`% of tonnage produced.

## Feed provision and feeding response to temperature {#sec-model-feeding}

# Modelled experimental feeds {#sec-feeds}

# Model sensitivity to parameter changes {#param-sensitivity}

Parameter sensitivity was tested by varying each parameter by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively. 
All parameters in Table @tbl-params were tested. The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10.

```{r salmon-param-names}
#| code-summary: Get parameter and sensitivity data

params <- file.path(output_species_data_path, "sens_params.qs") %>% qs::qread()

param_names <- tibble::tribble(
  ~name,        ~lab,
  "alpha",      bquote(alpha),
  "epsprot",    bquote(epsilon["P"]),
  "epslip",     bquote(epsilon["L"]),
  "epscarb",    bquote(epsilon["C"]),
  "epsO2",      bquote(epsilon["O"[2]]),
  "pk",         bquote("pk"),
  "k0",         bquote("k"[0]),
  "m",          bquote("m"),
  "n",          bquote("n"),
  "betac",      bquote(beta*"C"),
  "Tma",        bquote("T"["max"]),
  "Toa",        bquote("T"["opt"]),
  "Taa",        bquote("T"["min"]),
  "omega",      bquote(omega),
  "a",          bquote("a"),
  "k",          bquote("k"),
  "eff",        bquote("eff"),
  "meanW",      bquote(bar("W")),
  "deltaW",     bquote(Delta*"W"), 
  "meanImax",   bquote(bar("I"["max"])),
  "deltaImax",  bquote(Delta*"I"["max"]),
  "overFmean",  bquote(bar("F")),
  "overFdelta", bquote(Delta*"F"),
  "mortmyt",    bquote("mort")
)
```

```{r}
#| label: sens-results

sens_results_files <- file.path(output_sens_data_path) %>% 
  list.files(full.names = T) %>% 
  str_subset("results")
```

# Inputs {#inputs}

```{r}
#| label: farm-geometry

farm_geometry <- find_read(output_farm_data_path, "farm_geometry")
```

```{r}
#| label: input-data

ins_P <- list.files(per_biomass_cohort_path, full.names = T) %>% 
  str_subset("P_uneat|P_excr") %>% 
  purrr::map(function(nm) {qs::qread(nm)}) %>% 
  bind_rows()

ins_tot <- list.files(per_biomass_cohort_path, full.names = T) %>% 
  str_subset("total_uneat|total_excr") %>% 
  purrr::map(function(nm) {qs::qread(nm)}) %>% 
  bind_rows()
```

## Total inputs (uneaten and excreted)

### Through time

```{r}
#| label: fig-uneat-excr-plot-ts
#| fig-cap: Initial look at excreted and uneaten through time

ins_tot %>% 
  mutate(t = t-365) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  group_by(country, feed, t, measure) %>% 
  reframe(
    sd_perbiom = sd(mean_perbiom),
    mean_perbiom = mean(mean_perbiom)
    ) %>% 
  mutate(
    mean_perbiom = mean_perbiom %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    sd_perbiom = sd_perbiom %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1")
  ) %>% 
  ggplot(aes(
    x = t, 
    y = drop_units(mean_perbiom), 
    ymin = drop_units(mean_perbiom-sd_perbiom), 
    ymax = drop_units(mean_perbiom+sd_perbiom), 
    colour = feed, 
    fill = feed
  )) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_grid(
    rows = vars(country),
    cols = vars(measure),
    scales = "free"
  ) +
  prettyplot() +
  scale_colour_manual(values = feed_pal) +
  scale_fill_manual(values = feed_pal) +
  scale_y_continuous(
    name = expression("Loss (kg g"^-1*")"),
    breaks = seq(0, 1, 0.2)
  )
```

```{r}
#| label: uneat-excr-plot-perc-diff

tmp <- ins_tot %>% 
  mutate(t = t-365) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  dplyr::select(-c(mean, sd_mean, sd, biom_mean, biom_sd, biom_sd_mean, sd_perbiom)) %>% 
  group_by(country, t, measure) %>% 
  pivot_wider(
    names_from = feed, 
    values_from = mean_perbiom
  ) %>% 
  mutate(
    diff = plant_dominant - marine_dominant,
    perc_diff = diff/plant_dominant
  ) %>%
  group_by(country, t, measure) %>% 
  reframe(
    mean_diff = mean(diff),
    mean_perc_diff = mean(perc_diff),
    sd_diff = sd(diff),
    sd_perc_diff = sd(perc_diff)
  )

tmp <- tmp %>% 
  group_by(measure, country) %>% 
  reframe(
    mean_t_perc_diff = mean(mean_perc_diff),
    sd_t_perc_diff = sd(mean_perc_diff)
    )
```

While the actual difference in excreted and uneaten feed (total loss) varied between countries and through time (@fig-uneat-excr-plot-ts), relative changes between the feeds remained consistent. 
In both the US and Australia (all done so far), total excreted faeces was 
`r round(100*tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_excr_stat"], 1)`%) higher in the plant-dominant feed. 
Differences in total uneaten feed were much smaller at 
`r round(100*-tmp$mean_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`% ($\pm$ `r round(100*tmp$sd_t_perc_diff[tmp$country == "Australia" & tmp$measure == "total_uneat_stat"], 1)`%) lower in the plant-dominant feed.

### At harvest

```{r}
#| label: uneat-excr-plot-end
#| fig-cap: Caption

ins_tot %>% 
  group_by(farm_ID) %>%
  arrange(farm_ID, t) %>%
  mutate(
    cumsum_mean = cumsum(mean_perbiom) %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    end_t = max(t)
    ) %>% 
  ungroup() %>% 
  filter(t == end_t) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
  geom_boxplot() +
  facet_grid(cols = vars(measure)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal)
```

## N inputs

```{r}
#| label: N-loss-plot-total
#| fig-cap: Caption

ins_P %>% 
  group_by(farm_ID) %>%
  arrange(farm_ID, t) %>%
  mutate(
    cumsum_mean = cumsum(mean_perbiom)*6.25 %>% 
      set_units("g g_fish-1") %>% 
      set_units("kg t_fish-1"),
    end_t = max(t)
    ) %>% 
  ungroup() %>% 
  filter(t == end_t) %>% 
  merge(farm_geometry, by.x = "farm_ID", by.y = "farm_id") %>% 
  ggplot(aes(x = country, y = cumsum_mean, fill = feed)) +
  geom_boxplot() +
  facet_grid(cols = vars(measure)) +
  prettyplot() +
  scale_fill_manual(values = feed_pal)
```

# Code and packages used

All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
Major packages used include `r cite_packages(packages)`.

For a full list of R packages used see the lockfile on [Github](https://www.github.com).
This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].

### 2025-09-04 docs/manuscript.qmd

@@
 here("00_model_functions.R") %>% source()
+
+remove_unit("gN")
+install_unit("gN", "6.25 g") # 1/6.25
 ```
@@
 |:------:|:------:|:-----------:|
-| $\alpha$             | `r unname(params['alpha'])`      | [@broekhuizen_modelling_1994] |
+| $\alpha$             | `r unname(params['alpha'])`      | @broekhuizen_modelling_1994 |
 | $\epsilon_{P}$       | `r unname(params['epsprot'])`    | @baldan_r_2018 |
@@
 
-```{r uneaten feed data}
-#| code-summary: Load and prep uneaten feed data
-
-uneaten_total <- farmrun_files %>% 
-  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
-  bind_rows() %>% 
-  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
-  rename(uneat_mean = mean.x, biomass_mean = mean.y,
-         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
-  mutate(uneat_sd = uneat_sd/uneat_mean,
-         biomass_sd = biomass_sd/biomass_mean,
-         uneat_biom_mean = uneat_mean/biomass_mean,
-         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
-```
-
-```{r uneaten feed analysis}
-uneaten_total_stats <- uneaten_total %>% 
-  group_by(feed, farm_ID) %>% 
-  reframe(total = sum(uneat_biom_mean)) %>% 
-  group_by(feed) %>% 
-  reframe(min = minna(total),
-          max = maxna(total),
-          mean = meanna(total)) %>% 
-  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
-         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
-  mutate(min = round(min,2),
-         max = round(max,2),
-         mean = round(mean,2))
-
-uneaten_total_compare <- uneaten_total %>% 
-  group_by(feed, farm_ID) %>% 
-  reframe(total = sum(uneat_biom_mean)) %>% 
-  pivot_wider(names_from = "feed", values_from = "total", id_cols = "farm_ID") %>% 
-  mutate(diff_past = past-reference,
-         diff_future = future-reference,
-         diffperc_past = diff_past/reference,
-         diffperc_future = diff_future/reference) %>% 
-  dplyr::select(-c(reference, future, past)) %>% 
-  pivot_longer(names_to = c("measure", "feed"), names_sep = "_", values_to = "value",
-               cols = contains("diff"), names_transform = list(measure = as.factor, feed = as.factor)) %>% 
+```{r inputs data}
+#| code-summary: Load and prep uneaten feed and faeces data (keep in g faeces/feed)
+
+mass_inputs_ts <- find_read(data_analysis_path, "all_waste_inputs")
+mass_inputs_end <- find_read(data_analysis_path, "sumtotal_waste_inputs.qs")
+N_inputs_ts <- find_read(data_analysis_path, "all_N_inputs")
+N_inputs_end <- find_read(data_analysis_path, "sumtotal_N_inputs")
+```
+
+```{r inputs stats through time}
+#| eval: false
+#| code-summary: Show how inputs (mass and N) change through time (across all farms)
+
+mass_inputs_ts
+N_inputs_ts
+
+# Through time
+inputs_stats_ts <- inputs_df %>%
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_ts <- inputs_rel_df %>% 
+  group_by(feed, t, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+# Total (at production end)
+inputs_stats_end <- inputs_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
   group_by(feed, measure) %>% 
-  reframe(min = minna(value),
-          max = maxna(value),
-          mean = meanna(value)) %>% 
-  mutate(
-    min = case_when(measure == "diffperc" ~ 100*min,
-                    T ~ min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
-    max = case_when(measure == "diffperc" ~ 100*max,
-                    T ~ max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
-    mean = case_when(measure == "diffperc" ~ 100*mean,
-                     T ~ mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(mean),
+          max = maxna(mean),
+          sd = sdna(mean) %>% set_units("g g_fish-1"),
+          mean = meanna(mean))
+
+inputs_stats_rel_end_diff <- inputs_rel_df %>% 
+  group_by(feed, measure, farm_ID) %>% 
+  reframe(mean = sumna(mean)) %>% 
+  pivot_wider(names_from = feed, values_from = mean) %>% 
+  mutate(future = (future-reference)/reference,
+         past = (past-reference)/reference) %>% 
+  select(-reference) %>% 
+  pivot_longer(cols = c(past, future), names_to = "feed", values_to = "diff") %>% 
+  mutate(feed = factor(feed, levels = c("past", "future"))) %>% 
+  group_by(feed, measure) %>% 
+  reframe(min = minna(diff),
+          max = maxna(diff),
+          sd = sdna(diff),
+          mean = meanna(diff))
+
+# Pull key values (uneaten feed)
+u_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(min)
+u_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(max)
+u_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "uneat") %>% pull(mean)
+u_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(min)
+u_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(max)
+u_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "uneat") %>% pull(mean)
+u_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(min)
+u_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(max)
+u_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "uneat") %>% pull(mean)
+
+# Convert past and future values to % change values
+u_stmin2 <- (100*u_stmin2) %>% round(2)
+u_stmax2 <- (100*u_stmax2) %>% round(2)
+u_stmean2 <- (100*u_stmean2) %>% round(2)
+u_stmin3 <- (100*u_stmin3) %>% round(2)
+u_stmax3 <- (100*u_stmax3) %>% round(2)
+u_stmean3 <- (100*u_stmean3) %>% round(2)
+
+u_stmin1 <- u_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmax1 <- u_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+u_stmean1 <- u_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+
+# Pull key values (excreted faeces)
+e_stmin1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(min)
+e_stmax1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(max)
+e_stmean1 <- filter(inputs_stats_rel_end, feed == "reference", measure == "excr") %>% pull(mean)
+e_stmin2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(min)
+e_stmax2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(max)
+e_stmean2 <- filter(inputs_stats_rel_end_diff, feed == "past", measure == "excr") %>% pull(mean)
+e_stmin3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(min)
+e_stmax3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(max)
+e_stmean3 <- filter(inputs_stats_rel_end_diff, feed == "future", measure == "excr") %>% pull(mean)
+
+# Convert past and future values to % change values
+e_stmin2 <- (100*e_stmin2) %>% round(2)
+e_stmax2 <- (100*e_stmax2) %>% round(2)
+e_stmean2 <- (100*e_stmean2) %>% round(2)
+e_stmin3 <- (100*e_stmin3) %>% round(2)
+e_stmax3 <- (100*e_stmax3) %>% round(2)
+e_stmean3 <- (100*e_stmean3) %>% round(2)
+
+e_stmin1 <- e_stmin1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmax1 <- e_stmax1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+e_stmean1 <- e_stmean1 %>% set_units("g kg_fish-1") %>% drop_units() %>% round(2)
+```
+
+```{r waste inputs stats total}
+#| code-summary: Show how waste inputs change in total (at the end of a production period) across all farms
+
+mass_inputs_sep <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          mean_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass))
+
+twi_min <- mass_inputs_sep$min_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_max <- mass_inputs_sep$max_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+twi_mean <- mass_inputs_sep$mean_wpb[mass_inputs_sep$measure == "total"] %>% round(2)
+
+# There were only very small differences in total uneaten feed between the different feeds, with the past feed increasing uneaten feed by `r u_stmin2`-`r u_stmax2`%  (mean of `r u_stmean2`%) and the future feed increasing uneaten feed by `r u_stmin3`-`r u_stmax3`%  (mean of `r u_stmean3`%).
+
+# * Total excreted faeces across a cohort fed the reference feed ranged from `r e_stmin1` to `r e_stmax1` g kg$^{-1}$ fish, with a mean of `r e_stmean1` g kg$^{-1}$ fish. 
+# * Past feed decreased excreted faeces by `r -1*e_stmin2`-`r -1*e_stmax2`%  (mean of `r -1*e_stmean2`%) 
+# * Future feed increased excreted faeces by `r e_stmin3`-`r e_stmax3`%  (mean of `r e_stmean3`%)
+```
+
+* Total waste inputs across a single production period of fish fed the reference feed ranged from `r twi_min[1]` to `r twi_max[1]` g kg$^{-1}$ fish, with a mean of `r twi_mean[1]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the past feed ranged from `r twi_min[2]` to `r twi_max[2]` g kg$^{-1}$ fish, with a mean of `r twi_mean[2]` g kg$^{-1}$ fish.
+* Total waste inputs across a single production period of fish fed the future feed ranged from `r twi_min[3]` to `r twi_max[3]` g kg$^{-1}$ fish, with a mean of `r twi_mean[3]` g kg$^{-1}$ fish.
+
+```{r fig-waste-inputs-total}
+#| fig-cap: | 
+#|   Total waste intputs (uneaten feed + excreted faeces) across the whole production period at each farm location.
+#| fig-width: 9.5
+
+mass_inputs_sep_geometry <- mass_inputs_end %>% 
+  mutate(waste_per_biomass = set_units(total/biomass_total, "g kg_fish-1")) %>% 
+  dplyr::select(-c(total, biomass_total)) %>% 
+  pivot_wider(names_from = measure, values_from = waste_per_biomass) %>% 
+  mutate(total = excr+uneat) %>% 
+  pivot_longer(names_to = "measure", values_to = "waste_per_biomass", cols = c(total, excr, uneat), names_transform = list(measure = as.factor)) %>% 
+  group_by(farm_ID, feed, measure) %>% 
+  reframe(mean_wpb = meanna(waste_per_biomass),
+          sd_wpb = sdna(waste_per_biomass) %>% set_units("g kg_fish-1"),
+          min_wpb = minna(waste_per_biomass),
+          max_wpb = maxna(waste_per_biomass)) %>% 
+  merge(farms_geometry, by = "farm_ID")
+
+mass_inputs_robinson <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units()) %>% 
+  st_sf() %>% 
+  st_transform(crs = "+proj=robin")
+
+ggplot() +
+  geom_sf(data = graticules, color = "gray80", size = 0.3) +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = mass_inputs_robinson, aes(color = mean_wpb), size = 1) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
+    barwidth = 25,barheight = 1.5
+  )) +
+  geom_sf(data = boxes_robinson, fill = NA, color = "darkred", size = 1.65) +
+  geom_sf_text(data = labels_robinson, aes(label = letter), 
+               color = "darkred", size = 5, fontface = "bold", 
+               hjust = 0.5, vjust = 0.5) +
+  theme_void()
+```
+
+```{r patchwork-waste-map-mercator}
+#| fig-cap: |
+#|   Example of a patchwork
+#| fig-height: 9
+#| fig-width: 9.5
+
+mass_inputs_patch <- mass_inputs_sep_geometry %>% 
+  filter(feed == "reference" & measure == "total") %>% 
+  mutate(mean_wpb = mean_wpb %>% drop_units())
+
+p1 <- ggplot() +
+  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
+  geom_sf(data = mass_inputs_patch, aes(color = mean_wpb, geometry = geometry), size = 2) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo") +
+  guides(col = guide_colourbar(
+    title = expression("Mean waste inputs (g g fish"^-1*")"),
+    direction = "vertical", position = "right",
+    label.position = "right", title.position = "top", 
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1.5,
+    barwidth = 1.5, barheight = 20,
+  )) +
+  prettyplot() +
+  labs(y = "Latitude", x = "Longitude")
+
+p_Can1 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
+  draw_label("A", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN1"]][["labx"]], 
+             y = inset_boxes_sm[["CAN1"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Can2 <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
+  draw_label("B", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CAN2"]][["labx"]], 
+             y = inset_boxes_sm[["CAN2"]][["laby"]], 
+             hjust = 0.5, vjust = 0.5)
+p_Eur <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
+           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
+  draw_label("C", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["EUR"]][["labx"]], 
+             y = inset_boxes_sm[["EUR"]][["laby"]], 
+             hjust = -1, vjust = 0.5)
+p_Chi <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
+           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
+  theme(legend.position = "right") +
+  draw_label("D", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["CHI"]][["labx"]], 
+             y = inset_boxes_sm[["CHI"]][["laby"]], 
+             hjust = 0, vjust = 0)
+p_Aus <- p1 + 
+  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
+           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
+  draw_label("E", size = 14, fontface = "bold", 
+             x = inset_boxes_sm[["AUS"]][["labx"]], 
+             y = inset_boxes_sm[["AUS"]][["laby"]], 
+             hjust = 0, vjust = 0.5)
+
+grid_1 <- cowplot::plot_grid(p_Can1, p_Can2, ncol = 2, rel_widths =  c(1, 1.35))
+grid_2 <- cowplot::plot_grid(p_Eur,  p_Aus,  nrow = 2, rel_heights = c(1, 1))
+grid_3 <- cowplot::plot_grid(grid_2, p_Chi,  ncol = 2, rel_widths =  c(1, 1))
+
+cowplot::plot_grid(
+  grid_1, grid_3,
+  nrow = 2,
+  rel_heights = c(1, 1.5)        # relative row heights
 )

### 2025-09-04 07_how_many_runs_per_farm.qmd

---
title: "How many runs per farm are needed?"
format: html
editor: source
---

# Introduction

Originally, each farm was run with 5000 Monte-Carlo simulation runs. This takes quite a long time (4-5 minutes per farm and feed). But is this necessary?

```{r}
#| label: setup
#| warning: false
#| message: false

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% 
  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
  str_subset("map", negate = T) %>% 
  walk(source)

redo <- T
```

# Set up data for MC testing

Only need a small but representative sample of farms (n = 100).

```{r set-up-data}
#| code-summary: Take data from the farmrun pipeline for nrun testing

Sys.setenv(TAR_PROJECT = "project_farmruns")

# mani <- tar_manifest()

feed_params <- tar_read(reference_feed)
farm_static_data <- tar_read(farm_static_data_chunked)
farm_static_data <- split(farm_static_data, farm_static_data$farm_ID)
farm_ts_data <- tar_read(farm_ts_data_chunked)
all_params <- tar_read(all_params)

# Just use a representative sample
ts_means <- farm_ts_data %>% 
  imap(~ mutate(.x, farm_ID = as.integer(str_split_i(.y, "_", 6)))) %>% 
  lapply(function(df){
    df %>% 
      group_by(farm_ID) %>% 
      reframe(mean = mean(temp_c))
  }) %>% 
    bind_rows()

# Get a small but representative sample
samp <- ts_means %>%
  mutate(temp_bin = ntile(mean, 15)) %>%
  group_by(temp_bin) %>%
  slice_sample(n = 2) %>%
  ungroup() %>%
  pull(farm_ID)

farm_static_data <- farm_static_data[samp]
farm_ts_data <- farm_ts_data[samp]
```

```{r define-model-runs}
#| code-summary: Set up different farm runs as functions, define multisessions

# Set up parallel processing
plan(multisession, workers = parallelly::availableCores()-5)

# This is uniform
farm_run_singular <- function() {
  purrr::map2_dfr(farm_ts_data, farm_static_data, function(ts, static) {
    uni_farm_growth(
      pop_params = all_params,
      species_params = all_params,
      water_temp = ts$temp_c,
      feed_params = feed_params,
      times = c(t_start = static$t_start, t_end = static$t_end, dt = 1),
      N_pop = ts$Npop
    ) %>% 
      purrr::map_dfr(function(mat) {
        mat %>% 
          as.data.frame() %>% 
          rename(t = V1, mean = V2, sd = 0) %>% 
          mutate(
            farm_ID = as.integer(static$farm_ID),
            t = as.integer(t)
          )
      }, .id = "measure") %>% 
      mutate(measure = as.factor(measure))
  })
}

# This has the MC runs in it
farm_run_MC = function(n) {
  purrr::map2_dfr(farm_ts_data, farm_static_data, function(ts, static) {
    fg <- farm_growth(
      pop_params = all_params,
      species_params = all_params,
      water_temp = ts$temp_c,
      feed_params = feed_params,
      times = c(t_start = static$t_start, t_end = static$t_end, dt = 1),
      N_pop = ts$Npop,
      nruns = n
    )
    fg %>% 
      purrr::map_dfr(function(mat) {
        mat %>% 
          as.data.frame() %>% 
          rename(t = V1, mean = V2, sd = V3) %>% 
          mutate(
            farm_ID = as.integer(static$farm_ID),
            t = as.integer(t)
          )
      }, .id = "measure") %>% 
      mutate(measure = as.factor(measure))
  })
}
```

```{r save-nruns-5000}
#| code-summary: Run the model with 5000 nruns (default) and save

if (!file.exists(file.path(output_sens_data_path, "res_nruns_5000.qs")) | redo == T) {
  res_5000 <- farm_run_MC(5000) # Takes 4-5 minutes PER FARM
  res_5000 <- res_5000 %>% 
    mutate(nruns = as.factor(5000))

  qsave(res_5000, file.path(output_sens_data_path, "res_nruns_5000.qs"))
} else {
  res_5000 <- qread(file.path(output_sens_data_path, "res_nruns_5000.qs"))
}
```

# Test uniform farm run

First of all, how does the MC run approach using 5000 runs (the default) differ from only using a uniform fish weight/maximum ingestion?

```{r save-runs-1}
#| code-summary: Run the model with nrun = 1

if (!file.exists(file.path(output_sens_data_path, "res_nruns_1.qs")) | redo == T) {
  res_single <- farm_run_singular() %>% 
    mutate(nruns = as.factor(1), sd = 0) %>% 
    relocate(sd, .after = mean)

  qsave(res_single, file.path(output_sens_data_path, "res_nruns_1.qs"))
} else {
  res_single <- qread(file.path(output_sens_data_path, "res_nruns_1.qs"))
}
```

```{r fig-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs (with a range of fish weights/maximum ingestion values) and when only mean fish weight/maximum ingestion was used.

weight_single <- res_single %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_single, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

It looks like using only 1 nrun results in a gradual growing underestimation of individual weight with increasing time (@fig-1-nruns-weight-diff).

```{r fig-1-nruns-weight-diff}
#| fig-width: 8.5

df_diff <- rbind(weight_single, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_1 - nruns_5000)/nruns_5000)

ggplot(df_diff, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

# Try 100 nruns

```{r save-nruns-100}
#| code-summary: Run the model with 100 nruns and save

if (!file.exists(file.path(output_sens_data_path, "res_nruns_100.qs")) | redo == T) {
  res_100 <- farm_run_MC(100)
  res_100 <- res_100 %>% 
    mutate(nruns = as.factor(100))
  qsave(res_100, file.path(output_sens_data_path, "res_nruns_100.qs"))
} else {
  res_100 <- qread(file.path(output_sens_data_path, "res_nruns_100.qs"))
}
```

```{r fig-nruns-100-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs (with a range of fish weights/maximum ingestion values) and when only mean fish weight/maximum ingestion was used.

weight_100 <- res_100 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_100, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

Using 100 nruns instead of just one has eliminated the very obvious systematic underestimation of the error gap. The greatest difference is ~6% of the weight from the original 5000 nruns.

```{r fig-nruns-weight-100-diff}
#| fig-width: 8.5

df_diff <- rbind(weight_100, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_100 - nruns_5000)/nruns_5000)

ggplot(df_diff, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

# Try 250 nruns

```{r save-nruns-250}
#| code-summary: Run the model with 250 nruns and save

if (!file.exists(file.path(output_sens_data_path, "res_nruns_250.qs")) | redo == T) {
  res_250 <- farm_run_MC(250)
  res_250 <- res_250 %>% 
    mutate(nruns = as.factor(250))
  qsave(res_250, file.path(output_sens_data_path, "res_nruns_250.qs"))
} else {
  res_250 <- qread(file.path(output_sens_data_path, "res_nruns_250.qs"))
}
```

```{r fig-nruns-250-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs (with a range of fish weights/maximum ingestion values) and when only mean fish weight/maximum ingestion was used.

weight_250 <- res_250 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_250, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

The error is slightly smaller now (~4%, @fig-nruns-weight-250-diff) but I'll aim to get it to ~2% before I call it good.

```{r fig-nruns-weight-250-diff}
#| fig-width: 8.5

df_diff <- rbind(weight_250, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_250 - nruns_5000)/nruns_5000)

ggplot(df_diff, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

# Try 500 nruns

```{r save-nruns-500}
#| code-summary: Run the model with 500 nruns and save

if (!file.exists(file.path(output_sens_data_path, "res_nruns_500.qs")) | redo == T) {
  res_500 <- farm_run_MC(500)
  res_500 <- res_500 %>% 
    mutate(nruns = as.factor(500))
  qsave(res_500, file.path(output_sens_data_path, "res_nruns_500.qs"))
} else {
  res_500 <- qread(file.path(output_sens_data_path, "res_nruns_500.qs"))
}
```

```{r fig-nruns-500-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs (with a range of fish weights/maximum ingestion values) and when only mean fish weight/maximum ingestion was used.

weight_500 <- res_500 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_500, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

This number of runs results in a total mis-estimation of max 2% (fig-nruns-weight-500-diff), so I'd called that good enough.

```{r fig-nruns-weight-500-diff}
#| fig-width: 8.5

df_diff <- rbind(weight_500, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_500 - nruns_5000)/nruns_5000)

ggplot(df_diff, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r}

```

### 2025-09-04 index.qmd

@@
 
+```{r}
+#| label: fig-spatial-N-inputs-change
+#| fig-height: 12
+#| fig-cap: Change in total N inputs per unit biomass of salmon produced when farms are fed the MD feed (top), or the NI feed (bottom) compared to when farms are fed the PD feed.
+
+N_ins_comp <- rbind(
+  find_read(data_analysis_path, "P_excr_farm_per_biom_summed"),
+  find_read(data_analysis_path, "P_uneat_farm_per_biom_summed")
+  ) %>% 
+  st_drop_geometry() %>% 
+  select(-sd_biom) %>% 
+  mutate(feed = factor(feed, levels = long_feeds, labels = short_feeds)) %>% 
+  pivot_wider(
+    names_from = feed,
+    values_from = mean_biom,
+    values_fn = drop_units
+  ) %>% 
+  group_by(country, farm_ID) %>% 
+  reframe(
+    PD = sum(PD),
+    MD = sum(MD), 
+    NI = sum(NI)
+  ) %>% 
+  mutate(MD = (MD-PD),
+         NI = (NI-PD)) %>% 
+  select(-PD) %>% 
+  pivot_longer(
+    names_to = "feed",
+    values_to = "diff",
+    cols = c(MD, NI)
+  ) %>% 
+  mutate(
+    feed = factor(feed, levels = short_feeds),
+    feed = droplevels(feed),
+    diff = diff %>% set_units("g g_fish-1") %>% set_units("kg t_fish-1") %>% drop_units()
+  ) %>% 
+  merge(farm_locs, by = c("country", "farm_ID")) %>% 
+  st_as_sf()
+
+p_bigmap_robinson +
+  geom_sf(
+    data = N_ins_comp, 
+    aes(colour = diff, geometry = geometry), 
+    size = 2
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
+  guides(col = guide_colourbar(
+    title = expression("Difference in N inputs (kg/t salmon)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top",
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  facet_grid(rows = vars(feed)) +
+  # prettyplot() +
+  theme(strip.background = element_blank(), strip.text = element_blank(),
+        axis.title = element_blank(),
+        legend.position = "bottom")
+```
+
+```{r}
+#| label: N-inputs-change-patchwork-map
+#| fig-cap: Change in total N inputs per unit biomass of salmon produced when farms are fed the MD feed (A), or the NI feed (B) compared to when farms are fed the PD feed.
+
+p_mercator <- p_bigmap_mercator +
+  geom_sf(
+    data = N_ins_comp,
+    aes(colour = diff, geometry = geometry), 
+    size = 2.5
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
+  guides(col = guide_colourbar(
+    title = expression("Difference in N inputs (kg/t salmon)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top",
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  prettyplot() +
+  theme(
+    strip.background = element_blank(), strip.text = element_blank(),
+    legend.position = "bottom"
+  ) +
+  labs(y = "Latitude", x = "Longitude")
+
+facet_labels <- c(
+  "MD" = "A",
+  "NI" = "B"
+)
+
+ins <- get_insets_mercator(p_mercator)
+
+ins[[1]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
+ins[[2]] + facet_grid(rows = vars(feed), labeller = as_labeller(facet_labels))
+ins[[3]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
+ins[[4]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
+ins[[5]] + facet_grid(cols = vars(feed), labeller = as_labeller(facet_labels))
+```
+
 # Supplemental methods {#sec-supp-methods}

### 2025-10-21 05_formulating_feeds.qmd
Bit of cleanup

@@
 
-ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
+ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.xlsx")
 feed_input_file <- file.path(input_feed_profile_path, "all_feeds.xlsx")
@@
 ingreds <- ingred_inputs_file %>% 
-  read.csv() %>% 
+  read_excel(sheet = "all_ingredients") %>% 
   mutate(ingredient = as.factor(ingredient))
@@
 ```
+
+```{r}
+
+```

### 2025-10-21 06_run_atlantic_salmon_model.qmd
Bit of cleanup

@@
   seconds_meta_append = 90,
-  shortcut = T
+  shortcut = T # only if you've done the pre-run
 )

### 2025-10-21 src/model_functions.R

@@ -278,6 +278,11 @@ farm_to_cohort <- function(df, time_offset = 0) {
     mutate(t = t + time_offset)
 }
 
+farm_to_cohort_2 <- function(df, time_offset = 0) {
+  df %>% 
+    mutate(prod_t = prod_t + time_offset)
+}
+
 # Process each time period (current, +365 days, +730 days)
 combine_cohorts <- function(lst) {
   bind_rows(farm_to_cohort(lst[[i]], 0),

### 2025-10-21 targets/_targets_farmruns.R

@@ -30,6 +30,7 @@ list(
       qs::qread(farm_ts_data_file) %>% 
         filter(farm_ID != 2703) %>% # The only Russian farm
         distinct(farm_ID) %>% 
+        # slice_head(n = 24) %>% 
         pull(farm_ID)
     }
   ),
@@ -103,7 +104,7 @@ list(
 
   tar_target(all_params, c(qs::qread(species_params_file), qs::qread(pop_params_file))),
 
-  # Calculate harvest size for each farm
+# Prepare parameters and farm data --------------------------------------------------------------------------------
   tar_target(
     harvest_size_chunked,
     command = {
@@ -129,10 +130,6 @@ list(
     pattern = farm_temp_data_chunked
   ),
 
-# Prepare parameters ----------------------------------------------------------------------------------------------
-  tar_target(stat_names, levels(farm_run_chunked$measure)),
-
-# Run growth ------------------------------------------------------------------------------------------------------
   tar_target(
     farm_static_data_chunked,
     command = {
@@ -180,7 +177,7 @@ list(
     pattern = map(farm_static_data_chunked, harvest_size_chunked, farm_temp_data_chunked)
   ),
 
-
+# Run growth ------------------------------------------------------------------------------------------------------
   tar_target(
     farm_run_chunked,
     command = {
@@ -213,7 +210,6 @@ list(
     pattern = cross(map(farm_ts_data_chunked,farm_static_data_chunked), map(feed_params, feed_names))
   ),
 
-# Process growth ------------------------------------------------------------------------------------------------------
   tar_target(
     farm_results_chunked,
     command = {
@@ -225,6 +221,7 @@ list(
     pattern = cross(farm_run_chunked, stat_names)
   ),
 
+# Process results ------------------------------------------------------------------------------------------------------
   tar_target(
     biomass_produced_chunked,
     command = {

### 2025-10-21 05_formulating_feeds.qmd
New novel feeds with digestibility

--- 2025-08-04 05_formulating_feeds.qmd
@@
 
-The purpose of this markdown is to:
+The purpose of this markdown is to formulate all the feeds that will be used in the analysis. These feeds are:
+- marine_dominant: a "past" salmonid diet where most protein is sourced from marine-based ingredients.
+- plant_dominant: a "current" salmonid diet where most protein is sourced from land-based ingredients.
+- novel_inclusive_2: a potential future salmonid diet which includes some novel ingredients. This formulation uses maximal digestibility values.
+- novel_inclusive_1: a potential future salmonid diet which includes some novel ingredients. This formulation uses the same formulation as novel_inclusive_2, but with minimal digestibility values.
 
@@
 here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% purrr::walk(source)
-
-ingred_inputs_file <- file.path(input_feed_profile_path, "all_ingredients.csv")
-feed_input_file <- file.path(input_feed_profile_path, "all_feeds.xlsx")
 ```
@@
 
-There is no check or correction here to ensure that protein+lipid+ash+carb = 1 in the incoming data. This was checked manually prior to import.
+There is no check or correction here to ensure that protein + lipid + ash + carb = 1 in the incoming data. This was checked manually prior to import.
 
 ``` {r import-ingredients}
-#| code-summary: Ingredient details
+#| code-summary: Get ingredient details (PLC composition, digestibility)
 
-ingreds <- ingred_inputs_file %>% 
-  read.csv() %>% 
+ingreds <- file.path(input_feed_profile_path, "all_ingredients.xlsx") %>% 
+  read_excel(sheet = "all_ingredients") %>% 
   mutate(ingredient = as.factor(ingredient))
+
 ingred_nms <- levels(ingreds$ingredient)
@@
 
-feed_inputs <- feed_input_file %>% 
+feed_inputs <- file.path(input_feed_profile_path, "all_feeds.xlsx") %>% 
   read_excel(sheet = "all_feeds") %>% 
+  rename(novel_inclusive_1 = novel_inclusive)
+feed_inputs$novel_inclusive_2 <- feed_inputs$novel_inclusive_1 # same composition
+
+feed_inputs <- feed_inputs %>% 
   pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
-  mutate(feed = as.factor(feed),
-         ingredient = as.factor(ingredient)) %>% 
-  merge(ingreds, by = "ingredient")
+  mutate(
+    feed = as.factor(feed),
+    ingredient = as.factor(ingredient),
+    proportion = case_when(is.na(proportion) ~ 0, T ~ proportion)
+  ) %>% 
+  left_join(ingreds, by = "ingredient") %>% 
+  select(-prop_P, -P_digestibility)
+
+# Novel feeds use the minimum and maximum digestibility values
+feed_inputs <- feed_inputs %>% 
+  mutate(
+    protein_digestibility = case_when(
+      feed == "novel_inclusive_1" & !is.na(max_protein_digestibility) ~ max_protein_digestibility,
+      feed == "novel_inclusive_2" & !is.na(min_protein_digestibility) ~ min_protein_digestibility,
+      T ~ mean_protein_digestibility,
+    ),
+    carb_digestibility = case_when(
+      feed == "novel_inclusive_1" & !is.na(max_carb_digestibility) ~ max_carb_digestibility,
+      feed == "novel_inclusive_2" & !is.na(min_carb_digestibility) ~ min_carb_digestibility,
+      T ~ mean_carb_digestibility,
+    ),
+    lipid_digestibility = case_when(
+      feed == "novel_inclusive_1" & !is.na(max_lipid_digestibility) ~ max_lipid_digestibility,
+      feed == "novel_inclusive_2" & !is.na(min_lipid_digestibility) ~ min_lipid_digestibility,
+      T ~ mean_lipid_digestibility,
+    )
+  ) %>% 
+  select(-contains(c("min", "max", "mean")))
 
@@
   ) %>% 
-    ungroup()
+  ungroup() %>% 
+  select(-sum, -ash)
 ```
@@
     Proteins = df %>% 
-      select(ingredient, proportion, contains("protein"), -contains("feed")) %>%
+      select(ingredient, proportion, contains("protein")) %>% 
       rename(macro = protein, digest = protein_digestibility),
     Carbohydrates = df %>% 
-      select(ingredient, proportion, contains("carb"), -contains("feed")) %>%
+      select(ingredient, proportion, contains("carb")) %>% 
       rename(macro = carb, digest = carb_digestibility),
     Lipids = df %>% 
-      select(ingredient, proportion, contains("lipid"), -contains("feed")) %>%
+      select(ingredient, proportion, contains("lipid")) %>% 
       rename(macro = lipid, digest = lipid_digestibility)

### 2025-10-21 06_run_atlantic_salmon_model.qmd
New novel feeds with digestibility

--- 2025-08-15 06_run_atlantic_salmon_model.qmd
@@
 Sys.setenv(TAR_PROJECT = "project_farmruns")
+tar_prune() # will remove any targets objects no longer in pipeline
 
@@
 targets::tar_load(test_reference_feed)
-test_reference_feed # if weight = 0 then the feeds aren't processing properly
+test_reference_feed # if weight ~ 0 then the feeds aren't processing properly
 
@@
 # targets::tar_outdated()
+
 targets::tar_make(
@@
 
-Note that this takes a long time - each branch of farmrun takes ~5.3 minutes, and a maximum of ~12 workers can run at a time. The total therefore takes ~17 hours.
-
 ```{r}
@@
 targets::tar_make(
-  names = c("farm_IDs_chunked", "farm_ts_data_chunked", "farm_IDs", "test_reference_feed", "farm_temp_data_chunked", "harvest_size_chunked", "farm_static_data_chunked"), 
-  seconds_meta_append = 90#, callr_function = NULL
+  names = c("farm_static_data_chunked", "farm_temp_data_chunked", "farm_ts_data_chunked"), 
+  seconds_meta_append = 90
 )
@@
 targets::tar_make(
-  names = c("farm_run_chunked", "stat_names", "farm_results_chunked", "biomass_produced_chunked", "cohort_results_chunked" ), 
+  names = c("farm_run_chunked", "farm_full_results"), 
   seconds_meta_append = 90,
-  shortcut = T
+  shortcut = T # only if you've done the pre-run, above
 )

### 2025-10-21 07_species_layers.qmd
Proper index of files
New novel feeds with digestibility

@@
 library(rnaturalearth)
-library(aquamapsdata) # https://raquamaps.github.io/aquamapsdata/articles/intro.html
+# library(aquamapsdata) # https://raquamaps.github.io/aquamapsdata/articles/intro.html
 library(worrms)
@@
 
-source("00_dirs.R")
-
-overwrite <- F
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```

### 2025-10-21 targets/_targets_farmruns.R

@@ -1,11 +1,17 @@
-library(targets)
-# library(crew)
-library(magrittr)
+suppressPackageStartupMessages(suppressWarnings({
+  library(targets)
+  library(crew)
+  library(magrittr)
+  library(qs)
+  library(tidyverse)
+  library(arrow)
+}))
+
 
 tar_option_set(
-  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble", "qs"), 
+  # packages = c("arrow"), 
   format = "qs", 
-  controller = crew::crew_controller_local(workers = 12, seconds_idle = 300),
+  controller = crew::crew_controller_local(workers = 5, seconds_idle = 300),
   workspace_on_error = TRUE
 )
 
@@ -37,7 +43,7 @@ list(
 
   tar_target(
     farm_IDs_chunked,
-    split(farm_IDs, ceiling(seq_along(farm_IDs)/20))
+    split(farm_IDs, ceiling(seq_along(farm_IDs)/10))
   ),
 
   tar_target(
@@ -55,17 +61,13 @@ list(
 
   tar_target(
     feed_names,
-    command = {
-      # qs::qread(feed_params_file) %>% names() # Take all names from the feeds file
-      c("marine_dominant", "plant_dominant") # OR specify only certain names
-    }
+    command = {names(qs::qread(feed_params_file))}
   ),
   tar_target(
     feed_params,
     qs::qread(feed_params_file)[[feed_names]],
     pattern = feed_names
   ),
-
   tar_target(
     reference_feed,
     qs::qread(feed_params_file)[["plant_dominant"]]
@@ -207,54 +209,82 @@ list(
           mutate(measure = as.factor(measure))
       })
     },
-    pattern = cross(map(farm_ts_data_chunked,farm_static_data_chunked), map(feed_params, feed_names))
-  ),
-
-  tar_target(
-    farm_results_chunked,
-    command = {
-      farm_run_chunked %>% 
-        filter(measure == stat_names) %>% 
-        mutate(prod_t = t-min(t)+1) %>% 
-        filter(t != max(t))
-    },
-    pattern = cross(farm_run_chunked, stat_names)
+    pattern = cross(map(farm_ts_data_chunked, farm_static_data_chunked), map(feed_params, feed_names))
   ),
 
 # Process results ------------------------------------------------------------------------------------------------------
   tar_target(
-    biomass_produced_chunked,
[…]

### 2025-12-11 docs-working/01_tidying_data.qmd
Moving files around

--- 2025-07-09 01_tidying_data.qmd
@@
 date: today
-editor: source
+execute:
+  eval: false
 ---
 
-```{r setup}
+```{r setup, include=F, cache=F}
 library(tidyverse)
@@
 library(magrittr)
+library(purrr)
 
-source("00_dirs.R")
-source("00_model_functions.R")
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```

### 2025-12-11 docs-working/02_extracting_production_locations.qmd
Moving files around

--- 2025-07-10 02_extracting_production_locations.qmd
@@
 
-```{r setup}
+```{r setup, include=F, cache=F}
 library(tidyr)
@@
 library(ggplot2)
+library(purrr)
 
@@
 # Get aquaculture quantity in tonnes live weight
-quantity <- file.path(rawdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
+quantity <- file.path(bigdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
   read.csv() %>% 
@@
 # Apply environment codes and filter by "marine"
-environment_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
+environment_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
   read.csv() %>% 
@@
 # Apply species codes
-species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
+species_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
   read.csv() %>% 
@@
 # Apply status codes
-status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
+status_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
   read.csv() %>% 
@@
 # Apply country and area codes
-country_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_COUNTRY_GROUPS.csv") %>% 
+country_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_COUNTRY_GROUPS.csv") %>% 
   read.csv() %>% 
   select(UN_Code, Identifier, Name_En, ISO3_Code)
-area_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_WATERAREA_GROUPS.csv") %>% 
+area_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_WATERAREA_GROUPS.csv") %>% 
   read.csv() %>% 

### 2025-12-11 docs-working/03_assessing_species_potential.qmd
Moving files around

--- 2025-04-08 03_assessing_species_potential.qmd
@@
 title: "Assessing species potential"
-format: html
+author: Richard Cottrell
+date: today
 editor: source
@@
 
-```{r setup}
+```{r setup, include=F, cache=F}
 library(tidyverse)
@@
 library(rnaturalearth)
+library(purrr)
 
-source("src/dir.R")
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```

### 2025-12-11 docs-working/05_formulating_feeds.qmd
Moving files around

--- 2025-10-21 05_formulating_feeds.qmd
@@
 
-```{r setup}
+```{r setup, include=F, cache=F}
 #| code-summary: R setup
@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% purrr::walk(source)
+here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
 ```
@@
 
-There is no check or correction here to ensure that protein + lipid + ash + carb = 1 in the incoming data. This was checked manually prior to import.
+There is no check or correction here to ensure that protein + lipid + ash + carb = 1 in the incoming ingredient data. This was checked manually prior to import.
 
@@
 
+Unlike ingredients, the feeds do not need to be checked for sum = 1 prior to import. That check is done here.
+
 ``` {r import-feeds}
@@
 feed_inputs <- file.path(input_feed_profile_path, "all_feeds.xlsx") %>% 
-  read_excel(sheet = "all_feeds") %>% 
-  rename(novel_inclusive_1 = novel_inclusive)
-feed_inputs$novel_inclusive_2 <- feed_inputs$novel_inclusive_1 # same composition
+  read_excel(sheet = "all_feeds")
 
@@
   ) %>% 
-  left_join(ingreds, by = "ingredient") %>% 
-  select(-prop_P, -P_digestibility)
+  left_join(ingreds, by = "ingredient")
+```
 
-# Novel feeds use the minimum and maximum digestibility values
+Include the range of digestibility values so that feeds can be sampled (if required) within the targets pipeline.
+
+```{r min-max-values}
+#| code-summary: Novel feeds use the mean digestibility values
+
 feed_inputs <- feed_inputs %>% 
-  mutate(
-    protein_digestibility = case_when(
-      feed == "novel_inclusive_1" & !is.na(max_protein_digestibility) ~ max_protein_digestibility,
-      feed == "novel_inclusive_2" & !is.na(min_protein_digestibility) ~ min_protein_digestibility,
-      T ~ mean_protein_digestibility,
-    ),
-    carb_digestibility = case_when(
-      feed == "novel_inclusive_1" & !is.na(max_carb_digestibility) ~ max_carb_digestibility,
-      feed == "novel_inclusive_2" & !is.na(min_carb_digestibility) ~ min_carb_digestibility,
-      T ~ mean_carb_digestibility,
-    ),
-    lipid_digestibility = case_when(
-      feed == "novel_inclusive_1" & !is.na(max_lipid_digestibility) ~ max_lipid_digestibility,
-      feed == "novel_inclusive_2" & !is.na(min_lipid_digestibility) ~ min_lipid_digestibility,
-      T ~ mean_lipid_digestibility,
+  rename(
+    protein_digestibility = mean_protein_digestibility,
+    carb_digestibility = mean_carb_digestibility,
+    lipid_digestibility = mean_lipid_digestibility
   )
-  ) %>% 
-  select(-contains(c("min", "max", "mean")))
 
@@
 
+# Prepare for pipeline
+
 The following chunk allows as many ingredients and feeds to be added to the incoming data as needed, it will still be formatted into a form that the `targets` pipelines can use.
 
-```{r formulate feeds}
+```{r formulate-feeds}
 #| code-summary: Format feeds as lists to feed into targets
 
+feed_types <- levels(feed_inputs$feed)
+
 feed_params <- purrr::map(feed_types, function(ft) {
-  df <- feed_inputs %>% 
-    filter(feed == ft) 
+  # Filter by specified feed
+  df <- feed_inputs %>% filter(feed == ft)
+
   list(
@@
       select(ingredient, proportion, contains("protein")) %>% 
-      rename(macro = protein, digest = protein_digestibility),
+      rename(
+        macro = protein, 
+        digest = protein_digestibility,
+        min_digest = min_protein_digestibility,
+        max_digest = max_protein_digestibility
+      ),
     Carbohydrates = df %>% 
       select(ingredient, proportion, contains("carb")) %>% 
-      rename(macro = carb, digest = carb_digestibility),
+      rename(
+        macro = carb, 
+        digest = carb_digestibility,
+        min_digest = min_carb_digestibility,
+        max_digest = max_carb_digestibility
+      ),
     Lipids = df %>% 
       select(ingredient, proportion, contains("lipid")) %>% 
-      rename(macro = lipid, digest = lipid_digestibility)
+      rename(
+        macro = lipid, 
+        digest = lipid_digestibility,
+        min_digest = min_lipid_digestibility,
+        max_digest = max_lipid_digestibility
+      )
   )
@@
 ```{r save}
+#| code-summary: Save feed params file
+
 qsave(feed_params, file.path(output_species_data_path, "feed_params.qs"))
 ```
-
-# Similarity
-
-For later - how similar are the diets?
-
-```{r}
-#| label: diet-similarity
-
-feed_simil <- feed_inputs %>% 
-  select(ingredient, feed, proportion) %>% 
-  as.data.frame() %>% 
-  pivot_wider(
-    names_from = feed,
-    values_from = proportion,
-    id_cols = ingredient,
-    values_fn = as.numeric
-  ) %>% 
-  mutate(
-    diff_PD_MD = abs(marine_dominant - plant_dominant),
-    diff_PD_NI = abs(novel_inclusive - plant_dominant)
-  )
-
-1 - sum(feed_simil$diff_PD_MD, na.rm = T)
-1 - sum(feed_simil$diff_PD_NI, na.rm = T)
-```
-
-```{r}
-
-```

### 2025-12-11 docs-working/06_run_atlantic_salmon_model.qmd
Moving files around

--- 2025-10-21 06_run_atlantic_salmon_model.qmd
@@
 
-```{r}
-#| label: setup
+```{r setup, include=F}
 #| warning: false
@@
 
-```{r}
-#| label: filenames
-
-# Set up parallel processing
-# plan(multisession, workers = parallelly::availableCores()-1)
+```{r filenames}
+#| code-summary: Set up global filenames
 
@@
 
-Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms.
-
-```{r}
-#| label: farm-coordinates
+```{r farm-coordinates}
+#| code-summary: Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms
 
@@
 
-```{r}
+```{r farm-sst-data}
 #| label: farm-ts-data
@@
 
-# Species and population parameters
+## Species and population parameters
 
-Load species-specific parameters from Excel file.
-
-```{r}
-#| label: species-parameters
+```{r species-parameters}
+#| code-summary: Load species-specific parameters from Excel file
 
@@
 
-Load population-specific parameters.
-
-```{r}
-#| label: population-parameters
+```{r population-parameters}
+#| code-summary: Load population-specific parameters
 
@@
 
+## Feed digestibility
+
+```{r variable-digestibility}
+#| code-summary: Show the variability in feed digestibility generated by sampling digestibility values.
+
+Sys.setenv(TAR_PROJECT = "project_farmruns")
+
+# tar_make(names = c("feed_params", "feed_names"))
+
+tar_load(feed_params)
+tar_load(feed_names)
+
+feed_params <- feed_params %>% 
+  map2_dfr(., feed_names, function(fp, fn) {
+    ld <- filter(fp[["Lipids"]], macro != 0)
+    ld <- sum(ld$proportion * ld$digest)/sum(ld$proportion)
+
+    cd <- filter(fp[["Carbohydrates"]], macro != 0)
+    cd <- sum(cd$proportion * cd$digest)/sum(cd$proportion)
+
+    pd <- filter(fp[["Proteins"]], macro != 0)
+    pd <- sum(pd$proportion * pd$digest)/sum(pd$proportion)
+
+    data.frame(
+      protein_digestibility = pd,
+      carb_digestibility = cd,
+      lipid_digestibility = ld,
+      feed_name = fn
+    )
+  }) %>% 
+  pivot_longer(
+    cols = contains("digestibility"),
+    names_to = "macro", 
+    values_to = "digestibility"
+  ) %>% 
+  mutate(
+    macro = factor(
+      macro, 
+      levels = c("protein_digestibility", "lipid_digestibility", "carb_digestibility"),
+      labels = c("protein", "lipid", "carb")
+    ))
+
+feed_params %>% 
+  ggplot(aes(x = macro, y = digestibility, fill = feed_name)) +
+  geom_col(position = position_dodge(), alpha = 0.35) +
+  theme_classic()
+```
+
 # Farm Harvest Size Calculations
@@
 Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline.
+This also allows you to run some tests and make sure the pipeline is running correctly.
 
-```{r}
-#| label: farm-harvest-size
+```{r check-farmrun-pipeline}
+#| code-summary: Check that the pipeline will run correctly
 
 Sys.setenv(TAR_PROJECT = "project_farmruns")
-tar_prune() # will remove any targets objects no longer in pipeline
+# tar_validate()
+# tar_prune()
 
-# Check that the feed will actually work
-targets::tar_make(test_reference_feed)
-targets::tar_load(test_reference_feed)
-test_reference_feed # if weight ~ 0 then the feeds aren't processing properly
+# tar_make(test_reference_feed)
+tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
+```
+
+```{r farm-harvest-size, eval=F}
+#| code-summary: Run limited pipeline for harvest sizes and testing
+
+Sys.setenv(TAR_PROJECT = "project_farmruns")
 
 # Get harvest sizes for all farms
-targets::tar_make(names = contains(c("harvest_size", "feed_params")))
-targets::tar_load(harvest_size_chunked)
-harvest_size <- harvest_size_chunked %>% bind_rows()
+tar_make(names = contains(c("harvest_size", "feed_params")))
+```
+
+```{r save-harvest-size}
+#| code-summary: Save harvest size data
+
+tar_load(harvest_size_chunked)
+harvest_size <- bind_rows(harvest_size_chunked)
 
@@
 
-Run the sensitivity runs using the targets pipeline. 
-Note that this can take a long time. 
-The species parameters (19) are run for a single fish in each farm (2721) and factor (3), which takes ~30 minutes. 
-The population parameters (6) are run for a smaller number of farms (271) and each factor (3) with a simulated population of 500 fish, which takes ~30 hours.
+Run the sensitivity runs using the targets pipeline - note that this can take a long time.
+The species parameters (n=19) are run for a single fish in  a sample number of farms (n=272) and each factor (3).
+The population parameters (n=6) are run for 1000 fish in a sample number of farms (271) and each factor (3).
 
-```{r}
-#| label: sensitivity-run
+```{r check-sensitivity-pipeline}
+#| code-summary: Check that the sensitivities pipeline is running correctly
+
+Sys.setenv(TAR_PROJECT = "project_sensitivities")
+# tar_validate()
+# tar_visnetwork(targets_only = T)
+
+# tar_make(test_reference_feed)
+tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
+```
+
+```{r sensitivity-run, eval=F}
+#| code-summary: Run sensitivity pipeline
 
@@
 
-targets::tar_validate()
-# targets::tar_visnetwork(targets_only = T)
-# targets::tar_outdated()
-
-targets::tar_make(
-  seconds_meta_append = 120,
-  callr_function = NULL
-  )
+tar_make(seconds_meta_append = 300)
 tar_prune()
@@
 
-```{r}
-#| label: sensitivity-results
+```{r sensitivity-results}
+#| code-summary: Plot and save sensitivity results
 
-targets::tar_load(sens_results_spec)
-targets::tar_load(sens_results_pop)
+tar_load(sens_results_spec)
+tar_load(sens_results_pop)
 
@@
 
-qs::qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))
+qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))
 
@@
 
-```{r}
-#| label: run-farms-pipeline
+The following code runs the main pipeline in two stages.
+The pre-run prepares all the pre-requisites for the main results targets, to reduce load.
+The main run shortcuts past all the pre-run targets and does the main model runs and results processing.
+
+```{r run-farms-pipeline, eval=F}
+#| code-summary: Run the main pipeline
 
@@
 
-targets::tar_validate()
-targets::tar_outdated()
-
 # Pre-run to reduce load
-targets::tar_make(
-  names = c("farm_static_data_chunked", "farm_temp_data_chunked", "farm_ts_data_chunked"), 
+tar_make(
+  names = contains(c("data", "feed")),
   seconds_meta_append = 90
@@
 
+# tar_outdated()
+
 # Run results
-targets::tar_make(
+tar_make(
   names = c("farm_run_chunked", "farm_full_results"), 
-  seconds_meta_append = 90,
+  seconds_meta_append = 120,
   shortcut = T # only if you've done the pre-run, above
 )
-
-tar_prune()
-
-# meta <- targets::tar_meta() %>% 
-#   filter(grepl("farm_run", name))
-# meta$seconds %>% mean()/60 # average minutes per target
 ```
@@
 
-```{r}
-#| label: all-farms-cohorts-results
+```{r all-farms-cohorts-results}
+#| code-summary: Save pipeline objects as files
 
-targets::tar_load(stat_names)
-targets::tar_load(farm_IDs_chunked)
+tar_load(stat_names)
+tar_load(farm_IDs_chunked)
 farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
-targets::tar_load(feed_names)
+tar_load(feed_names)
 
 print("Loading farm results...")
-targets::tar_load(farm_results_chunked)
+tar_load(farm_results_chunked)
 farm_results_chunked <- farm_results_chunked %>% 
@@
 print("Loading cohort results...")
-targets::tar_load(cohort_results_chunked)
+tar_load(cohort_results_chunked)
 cohort_results_chunked <- cohort_results_chunked %>% 
@@
 
-targets::tar_load(biomass_produced_chunked)
+tar_load(biomass_produced_chunked)
 qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
@@
 ```
-
-```{r}
-
-```

### 2025-12-11 docs-working/07_methods_and_supplementaries/_manuscript/05_methods_and_supplementaries.qmd
Moving files around

--- 2025-04-08 07_methods_and_supplementaries/07_methods_and_supplementaries.qmd
@@
 # Model approach
+
+We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus.
+The model simulates growth at an individual level, calculating the change in individual weight through time using:
+
+$$
+\frac{dw}{dt} = \frac{A-C}{\epsilon}
+$$
+
+Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$).
+
+Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population.
+Size differences were achieved through different initial starting weights and ingestion rates for different finfish species.
+All individuals have a fixed mortality rate to simulate stocking and harvesting.
+
+* Parameterised for atlantic salmon
+* Farms with mean temperature < 8.5$^\circ$ were excluded
 

### 2025-12-11 docs-working/index.qmd
Moving files around

--- 2025-09-04 index.qmd
@@
 ---
-title: "Local to Global Mariculture Modelling"
+title: "Local-to-Global Mariculture Modelling"
 subtitle: "Project Documentation"
@@
 All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github.
-While this page (the index) has code that runs prior to rendering, all code in the subsequent pages has not been run for rendering.
 

### 2025-12-11 src/dirs.R

@@ -11,6 +11,7 @@ this_species <- "atlantic_salmon"
 output_path <- here() %>% file.path("outputs")
 gendata_path <- here() %>% file.path("data", "_general_data")
 rawdata_path <- here() %>% file.path("data", "raw")
+bigdata_path <- "D:/local_to_global_mariculture_modelling_data"
 rdsi_dir <- "/mnt/rdsi"
 species_path <- here() %>% file.path("data", this_species)
 species_fig_path <- file.path(species_path, "figures")
@@ -47,7 +48,3 @@ dir.create(output_model_cohort_path, showWarnings = F)
 dir.create(data_analysis_path, showWarnings = F)
 dir.create(comparisons_path, showWarnings = F)
 dir.create(impacts_path, showWarnings = F)
-
-# From extracting_temperature
-# this_path <- file.path("data", this_species) # now call species_path
-

### 2025-12-11 src/model_functions.R
Update meta

@@ -3,15 +3,12 @@
 ### https://github.com/cran/RAC/tree/master/R
 
 suppressPackageStartupMessages(suppressWarnings({
-library(qs)
-library(qs2)
-library(terra)
-library(readxl)
-library(matrixStats)
-library(furrr)
-library(future)
-library(dplyr)
-library(msm)
+  library(qs)
+  library(terra)
+  library(readxl)
+  library(matrixStats)
+  library(dplyr)
+  library(msm)
 }))
 
 # Parameters definitions
@@ -179,7 +176,7 @@ farm_growth <- function(pop_params, species_params, feed_params, water_temp, tim
   ingmaxes <- rnorm(nruns, mean = pop_params['meanImax'], sd = pop_params['deltaImax'])
   
   # Run parallel simulation for individuals
-  mc_results <- furrr::future_map2(init_weights, ingmaxes, function(init_w, ing_m) {
+  mc_results <- purrr::map2(init_weights, ingmaxes, function(init_w, ing_m) {
     mat <- fish_growth(
       pop_params = pop_params,
       species_params = species_params,
@@ -189,7 +186,7 @@ farm_growth <- function(pop_params, species_params, feed_params, water_temp, tim
       init_weight = init_w,
       ingmax = ing_m
     ) %>% unname()
-  }, .options = furrr::furrr_options(seed = TRUE))
+  })
   
   stat_names <- c("days", "weight", "dw", "water_temp", "T_response", "P_excr", "L_excr", "C_excr", "P_uneat", 
                   "L_uneat", "C_uneat", "food_prov", "food_enc", "rel_feeding", "ing_pot", "ing_act", "E_assim", 

### 2025-12-11 targets/_targets_farmruns.R

@@ -4,21 +4,25 @@ suppressPackageStartupMessages(suppressWarnings({
   library(magrittr)
   library(qs)
   library(tidyverse)
-  library(arrow)
+  # library(arrow)
 }))
 
-
 tar_option_set(
-  # packages = c("arrow"), 
   format = "qs", 
-  controller = crew::crew_controller_local(workers = 5, seconds_idle = 300),
-  workspace_on_error = TRUE
+  controller = crew::crew_controller_local(workers = 15, seconds_idle = 120),
+  workspace_on_error = TRUE,
+  garbage_collection = 10
 )
 
 tar_source(
   files = list.files("src", pattern = "\\.R$", full.names = TRUE) %>% 
     setdiff("src/map_templates.R")
 )
+
+# Globals
+farm_chunk_size <- 20
+inds_per_farm <- 1000
+farm_sample <- 2720 # For only runing a subset of farms (maximum 2720)
 
 list(
 # Get previously saved data ---------------------------------------------------------------------------------------
@@ -29,27 +33,27 @@ list(
   tar_target(feed_params_file, file.path(output_species_data_path, "feed_params.qs"), format = "file"),
   tar_target(farm_production_file, file.path(input_farm_coords_path, "atlantic_salmon_locations_w_temps.qs"), format = "file"),
 
-  tar_target(farm_coords, qs::qread(farm_coords_file)),
+  tar_target(farm_coords, qread(farm_coords_file)),
   tar_target(
     farm_IDs,
     command = {
-      qs::qread(farm_ts_data_file) %>% 
-        filter(farm_ID != 2703) %>% # The only Russian farm
+      qread(farm_ts_data_file) %>% 
+        filter(farm_ID != 2703) %>% # The only Russian farm?
         distinct(farm_ID) %>% 
-        # slice_head(n = 24) %>% 
+        slice_head(n = farm_sample) %>% 
         pull(farm_ID)
     }
   ),
 
   tar_target(
     farm_IDs_chunked,
-    split(farm_IDs, ceiling(seq_along(farm_IDs)/10))
+    split(farm_IDs, ceiling(seq_along(farm_IDs)/farm_chunk_size))
   ),
 
   tar_target(
     farm_temp_data_chunked, 
     command = {
-      qs::qread(farm_ts_data_file) %>% 
+      qread(farm_ts_data_file) %>% 
         filter(farm_ID %in% farm_IDs_chunked[[1]]) %>%
         merge(farm_coords, by = "farm_ID") %>%
[…]

### 2025-12-11 targets/_targets_sensitivities.R

@@ -1,16 +1,27 @@
-library(targets)
-library(crew)
-library(magrittr)
+suppressPackageStartupMessages(suppressWarnings({
+  library(targets)
+  library(crew)
+  library(magrittr)
+  library(qs)
+  library(tidyverse)
+  # library(arrow)
+  # library(tibble)
+}))
 
 tar_option_set(
-  packages = c("stringr", "magrittr", "tidyr", "arrow", "dplyr", "tibble"), 
   format = "qs", 
-  controller = crew_controller_local(workers = 5, seconds_timeout = 90),
-  workspace_on_error = TRUE
+  controller = crew_controller_local(workers = 15, seconds_timeout = 120),
+  workspace_on_error = TRUE,
+  garbage_collection = 20
 )
 
 tar_source(files = list.files("src", pattern = "\\.R$", full.names = TRUE) %>% 
     setdiff("src/map_templates.R"))
+
+# Globals
+inds_per_farm <- 1000
+farm_sample <- 272
+farm_chunk_size <- 10
 
 list(
   # Load previously saved data --------------------------------------------------------------------------------
@@ -20,31 +31,79 @@ list(
   tar_target(pop_params_file, file.path(output_species_data_path, "pop_params.qs"), format = "file"),
   tar_target(feed_params_file, file.path(output_species_data_path, "feed_params.qs"), format = "file"),
 
-  tar_target(farm_coords, qs::qread(farm_coords_file)),
+  tar_target(farm_coords, qread(farm_coords_file)),
   tar_target(
     farm_IDs,
-    qs::qread(farm_ts_data_file) %>% 
-      distinct(farm_ID) %>% 
-      filter(farm_ID != 2703) %>% # The only Russian farm
-      pull(farm_ID) %>% 
-      sample(271)
+    command = {
+      qread(farm_ts_data_file) %>% 
+        filter(farm_ID != 2703) %>% # The only Russian farm?
+        distinct(farm_ID) %>% 
+        pull(farm_ID) %>% 
+        sample(farm_sample)
+    }
   ),
+
+  tar_target(
+    farm_IDs_chunked,
+    split(farm_IDs, ceiling(seq_along(farm_IDs)/farm_chunk_size))
+  ),
+
   tar_target(
     farm_ts_data, 
-    qs::qread(farm_ts_data_file) %>% 
[…]

### 2025-12-15 docs-working/07_how_many_runs_per_farm.qmd
Updates

--- 2025-09-04 07_how_many_runs_per_farm.qmd
@@
 
-# Get a small but representative sample
+# Get a small sample
 samp <- ts_means %>%
@@
 
-This number of runs results in a total mis-estimation of max 2% (fig-nruns-weight-500-diff), so I'd called that good enough.
+This number of runs results in a total mis-estimation of max 2% (@fig-nruns-weight-500-diff), so I'd called that good enough.
 

### 2025-12-15 docs-working/index.qmd
Updates

@@
 execute:
-  eval: true
+  # eval: true
   echo: false

### 2025-12-15 targets/_targets_farmruns.R

@@ -22,7 +22,8 @@ tar_source(
 # Globals
 farm_chunk_size <- 20
 inds_per_farm <- 1000
-farm_sample <- 2720 # For only runing a subset of farms (maximum 2720)
+farm_sample <- 1000 # For only runing a subset of farms (multiples of farm_chunk_size, maximum 2720)
+reference_feed_name <- "marine_dominant_biomar"
 
 list(
 # Get previously saved data ---------------------------------------------------------------------------------------
@@ -102,11 +103,6 @@ list(
   ),
 
   tar_target(
-    reference_feed,
-    feed_params[["marine_dominant_biomar"]]
-  ),
-
-  tar_target(
     test_reference_feed,
     command = {
       fi <- sample(farm_IDs, 1)
@@ -114,7 +110,7 @@ list(
         pop_params = all_params,
         species_params = all_params,
         water_temp = farm_temp_data_chunked$temp_c[farm_temp_data_chunked$farm_ID == fi],
-        feed_params = reference_feed,
+        feed_params = feed_params[[reference_feed_name]],
         times = c(
           t_start = min(farm_temp_data_chunked$day[farm_temp_data_chunked$farm_ID == fi]), 
           t_end = max(farm_temp_data_chunked$day[farm_temp_data_chunked$farm_ID == fi]), 
@@ -149,7 +145,7 @@ list(
           pop_params = all_params,
           species_params = all_params,
           water_temp = temp$temp_c,
-          feed_params = reference_feed,
+          feed_params = feed_params[[reference_feed_name]],
           times = c(t_start = min(temp$day), t_end = max(temp$day), dt = 1),
           init_weight = all_params["meanW"],
           ingmax = all_params["meanImax"]
@@ -317,7 +313,8 @@ list(
         cohort_results_daily = cohort_results_daily
       )
     },
-    pattern = farm_run_chunked
+    pattern = farm_run_chunked,
+    iteration = "list"
   )
 
 )

### 2025-12-15 targets/_targets_sensitivities.R

@@ -10,7 +10,7 @@ suppressPackageStartupMessages(suppressWarnings({
 
 tar_option_set(
   format = "qs", 
-  controller = crew_controller_local(workers = 15, seconds_timeout = 120),
+  controller = crew_controller_local(workers = 6, seconds_timeout = 120),
   workspace_on_error = TRUE,
   garbage_collection = 20
 )
@@ -19,9 +19,10 @@ tar_source(files = list.files("src", pattern = "\\.R$", full.names = TRUE) %>%
     setdiff("src/map_templates.R"))
 
 # Globals
-inds_per_farm <- 1000
+inds_per_farm <- 250
 farm_sample <- 272
-farm_chunk_size <- 10
+farm_chunk_size <- 25
+reference_feed_name <- "marine_dominant_biomar"
 
 list(
   # Load previously saved data --------------------------------------------------------------------------------
@@ -66,11 +67,6 @@ list(
     pattern = farm_IDs_chunked
   ),
 
-  tar_target(
-    reference_feed,
-    qread(feed_params_file)[["marine_dominant_biomar"]]
-  ),
-
     tar_target(
     test_reference_feed,
     command = {
@@ -79,7 +75,7 @@ list(
         pop_params = all_params,
         species_params = all_params,
         water_temp = farm_ts_data$temp_c[farm_ts_data$farm_ID == fi],
-        feed_params = reference_feed,
+        feed_params = qread(feed_params_file)[[reference_feed_name]],
         times = c(
           t_start = min(farm_ts_data$day[farm_ts_data$farm_ID == fi]), 
           t_end = max(farm_ts_data$day[farm_ts_data$farm_ID == fi]), 
@@ -123,7 +119,7 @@ list(
           pop_params = adj_params,
           species_params = adj_params,
           water_temp = ts$temp_c,
-          feed_params = reference_feed,
+          feed_params = qread(feed_params_file)[[reference_feed_name]],
           times = c('t_start' = min(ts$day), 't_end' = max(ts$day), 'dt' = 1),
           N_pop = rep(1, nrow(ts))
         )
@@ -170,7 +166,7 @@ list(
           pop_params = adj_params,
           species_params = adj_params,
           water_temp = ts$temp_c,
-          feed_params = reference_feed,
+          feed_params = qread(feed_params_file)[[reference_feed_name]],
           times = c('t_start' = min(ts$day), 't_end' = max(ts$day), 'dt' = 1),
           N_pop = rep(1, nrow(ts))
         )
[…]

### 2025-12-15 docs-working/07_run_atlantic_salmon_model.qmd
Re-order notebooks

--- 2025-12-11 docs-working/06_run_atlantic_salmon_model.qmd
@@
 
-```{r farm-coordinates}
+```{r farm-coordinates, eval=F}
 #| code-summary: Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms
@@
 
-```{r farm-sst-data}
-#| label: farm-ts-data
+```{r farm-sst-data, eval=F}
+#| code-summary: Process Sea Surface Temperature (SST) data for each farm location.
 
@@
 
-```{r species-parameters}
+```{r species-parameters, eval=F}
 #| code-summary: Load species-specific parameters from Excel file
@@
 
-```{r population-parameters}
+```{r population-parameters, eval=F}
 #| code-summary: Load population-specific parameters
@@
 #| code-summary: Show the variability in feed digestibility generated by sampling digestibility values.
+#| fig-cap: Whole-feed digestibility of the feeds run in this analysis.
 
@@
       labels = c("protein", "lipid", "carb")
-    ))
+    ),
+    feed_name = as.factor(feed_name)
+  )
 
@@
   ggplot(aes(x = macro, y = digestibility, fill = feed_name)) +
-  geom_col(position = position_dodge(), alpha = 0.35) +
+  geom_col(position = position_dodge()) +
   theme_classic()
@@
 
-Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline.
-This also allows you to run some tests and make sure the pipeline is running correctly.
+First, let's test the pipeline to make sure that the feed input data is being processed correctly.
 
@@
 # tar_make(test_reference_feed)
+tar_load_globals()
+reference_feed_name
 tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
 ```
+
+Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline.
+This sets a "target population" for each farm and grounds the growth somewhat.
 
@@
 
-tar_load(harvest_size_chunked)
-harvest_size <- bind_rows(harvest_size_chunked)
+harvest_size <- tar_read(harvest_size_chunked) %>% 
+  bind_rows()
 
@@
 
-# tar_make(test_reference_feed)
+tar_make(test_reference_feed)
 tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
@@
 
-```{r sensitivity-run, eval=F}
+```{r sensitivity-run}
 #| code-summary: Run sensitivity pipeline
@@
 
-tar_make(seconds_meta_append = 300)
+tar_make(contains("spec"), seconds_meta_append = 300)
+tar_make(contains("pop"), shortcut = T, seconds_meta_append = 300)
 tar_prune()
@@
 
-tar_load(stat_names)
-tar_load(farm_IDs_chunked)
-farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
+Sys.setenv(TAR_PROJECT = "project_farmruns")
+farm_IDs_chunked <- tar_read(farm_IDs_chunked) %>% unname() %>% unlist()
 tar_load(feed_names)
 
-print("Loading farm results...")
-tar_load(farm_results_chunked)
-farm_results_chunked <- farm_results_chunked %>% 
-  bind_rows()
-for (stat_name in stat_names) {
-  farm_results_chunked %>% 
-      filter(measure == stat_name) %>% 
-      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
-}
-rm(farm_results_chunked)
+tar_load(farm_full_results)
+total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
+cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))
 
-print("Loading cohort results...")
-tar_load(cohort_results_chunked)
-cohort_results_chunked <- cohort_results_chunked %>% 
-  bind_rows()
-for (stat_name in stat_names) {
-  cohort_results_chunked %>% 
-      filter(measure == stat_name) %>% 
-      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
-}
-rm(cohort_results_chunked)
-
-tar_load(biomass_produced_chunked)
-qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
-rm(biomass_produced_chunked)
+qsave(total_ends, file.path(output_model_farm_path, "total_ends.qs"))
+qsave(cohort_results, file.path(output_model_cohort_path, "cohort_results.qs"))
+rm(farm_full_results)
 ```

### 2025-12-16 docs-working/05_formulating_feeds.qmd
Updates

@@
 
+library(tidyverse)
 library(arrow)
 library(sf)
-library(dplyr)
-library(tidyr)
 library(terra)
-library(magrittr)
-library(purrr)
 library(furrr)
@@
 library(tictoc)
-library(ggplot2)
 library(fs)
 library(conflicted)
-library(stringr)
 library(readxl)
@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  walk(source)
 ```

### 2025-12-16 docs-working/06_how_many_runs_per_farm.qmd
Updates

---
title: "How many runs per farm are needed?"
format: html
editor: source
---

# Introduction

Originally, each farm was run with 5000 Monte-Carlo simulation runs. This takes quite a long time (4-5 minutes per farm and feed). But is this necessary?

```{r, setup}
#| warning: false
#| message: false
#| echo: false

library(tidyverse)
library(arrow)
library(sf)
library(terra)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(fs)
library(conflicted)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% 
  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
  str_subset("map", negate = T) %>% 
  walk(source)

overwrite <- F # Make sure to set this to FALSE for quarto rendering
```

# Set up data for MC testing

Only use a small but representative sample of farms (n = 50) across the mean temperature spectrum.

```{r set-up-data}
#| code-summary: Take data from the farmrun pipeline for nrun testing
#| eval: false

Sys.setenv(TAR_PROJECT = "project_farmruns")

# mani <- tar_manifest()

feed_params <- tar_read(reference_feed)
farm_static_data <- tar_read(farm_static_data_chunked)
farm_static_data <- split(farm_static_data, farm_static_data$farm_ID)
farm_ts_data <- tar_read(farm_ts_data_chunked)
all_params <- tar_read(all_params)

ts_means <- farm_ts_data %>% 
  imap(~ mutate(.x, farm_ID = as.integer(str_split_i(.y, "_", 6)))) %>% 
  lapply(function(df){
    df %>% 
      group_by(farm_ID) %>% 
      reframe(mean = mean(temp_c))
  }) %>% 
    bind_rows()

# Get a small sample
samp <- ts_means %>%
  mutate(temp_bin = ntile(mean, 15)) %>%
  group_by(temp_bin) %>%
  slice_sample(n = 2) %>%
  ungroup() %>%
  pull(farm_ID)

farm_static_data <- farm_static_data[samp]
farm_ts_data <- farm_ts_data[samp]
```

```{r define-model-runs}
#| code-summary: Set up different farm runs as functions, define multisessions

# Set up parallel processing - make sure to comment this out when rendering with quarto
# plan(multisession, workers = parallelly::availableCores()-2)

# This is uniform
farm_run_singular <- function() {
  furrr::future_map2_dfr(farm_ts_data, farm_static_data, function(ts, static) {
    uni_farm_growth(
      pop_params = all_params,
      species_params = all_params,
      water_temp = ts$temp_c,
      feed_params = feed_params,
      times = c(t_start = static$t_start, t_end = static$t_end, dt = 1),
      N_pop = ts$Npop
    ) %>% 
      furrr::future_map_dfr(function(mat) {
        mat %>% 
          as.data.frame() %>% 
          rename(t = V1, mean = V2, sd = 0) %>% 
          mutate(
            farm_ID = as.integer(static$farm_ID),
            t = as.integer(t)
          )
        }, 
        .id = "measure",
        .options = furrr_options(seed = T)
      ) %>% 
      mutate(measure = as.factor(measure))
  },
  .options = furrr_options(seed = T),
  .progress = T
  )
}

# This has the MC runs in it
farm_run_MC = function(n) {
  furrr::future_map2_dfr(farm_ts_data, farm_static_data, function(ts, static) {
    fg <- farm_growth(
      pop_params = all_params,
      species_params = all_params,
      water_temp = ts$temp_c,
      feed_params = feed_params,
      times = c(t_start = static$t_start, t_end = static$t_end, dt = 1),
      N_pop = ts$Npop,
      nruns = n
    )
    fg %>% 
      furrr::future_map_dfr(function(mat) {
        mat %>% 
          as.data.frame() %>% 
          rename(t = V1, mean = V2, sd = V3) %>% 
          mutate(
            farm_ID = as.integer(static$farm_ID),
            t = as.integer(t)
          )
        }, 
        .id = "measure",
        .options = furrr_options(seed = T)
      ) %>% 
      mutate(measure = as.factor(measure))
  },
  .options = furrr_options(seed = T),
  .progress = T
  )
}
```

```{r save-nruns-5000}
#| code-summary: Run the model with 5000 nruns (default) and save

if (!file.exists(file.path(output_sens_data_path, "res_nruns_5000.qs")) | overwrite == T) {
  res_5000 <- farm_run_MC(5000)
  res_5000 <- res_5000 %>% mutate(nruns = as.factor(5000))
  qsave(res_5000, file.path(output_sens_data_path, "res_nruns_5000.qs"))
}

res_5000 <- qread(file.path(output_sens_data_path, "res_nruns_5000.qs"))
```

# Difference between uniform run and 5000 nruns

First of all, how does the MC run approach using 5000 runs (the default) differ from only using a uniform fish weight/maximum ingestion?

```{r save-nruns-1}
#| code-summary: Run the model with nrun = 1

if (!file.exists(file.path(output_sens_data_path, "res_nruns_1.qs")) | overwrite == T) {
  res_single <- farm_run_singular() %>% 
    mutate(nruns = as.factor(1), sd = 0) %>% 
    relocate(sd, .after = mean)

  qsave(res_single, file.path(output_sens_data_path, "res_nruns_1.qs"))
}

res_single <- qread(file.path(output_sens_data_path, "res_nruns_1.qs"))
```

```{r fig-1-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs (with a range of fish weights/maximum ingestion values) and when only mean fish weight/maximum ingestion was used.

weight_single <- res_single %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_single, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-1-nruns-weight-diff}
#| fig-width: 8.5

df_diff_1 <- rbind(weight_single, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_1 - nruns_5000)/nruns_5000)

ggplot(df_diff_1, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

# Difference between 5000 nruns and others

```{r save-nruns-other}
#| code-summary: Run the model with other numbers of nruns and save

for (i in c(100, 250, 500, 1000, 2500)) {
  fnm <- file.path(output_sens_data_path, paste0("res_nruns_", i, ".qs"))
  print(fnm)
  if (!file.exists(fnm) | overwrite == T) {
    res <- farm_run_MC(i) %>% mutate(nruns = as.factor(i))
    qsave(res, fnm)
  }
}

res_100 <- qread(file.path(output_sens_data_path, "res_nruns_100.qs"))
res_250 <- qread(file.path(output_sens_data_path, "res_nruns_250.qs"))
res_500 <- qread(file.path(output_sens_data_path, "res_nruns_500.qs"))
res_1000 <- qread(file.path(output_sens_data_path, "res_nruns_1000.qs"))
res_2500 <- qread(file.path(output_sens_data_path, "res_nruns_2500.qs"))
```

## Difference between 100 and 5000 nruns

```{r fig-100-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs vs 100 Monte-Carlo runs.

weight_100 <- res_100 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_100, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-100-nruns-weight-diff}
#| fig-width: 8.5
#| fig-cap: Difference in individual weight at each timestep when the farm has been run with 5000 vs 100 Monte-Carlo runs.

df_diff_100 <- rbind(weight_100, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_100 - nruns_5000)/nruns_5000)

ggplot(df_diff_100, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

## Difference between 250 and 5000 nruns

```{r fig-250-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs vs 250 Monte-Carlo runs.

weight_250 <- res_250 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_250, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-250-nruns-weight-diff}
#| fig-width: 8.5
#| fig-cap: Difference in individual weight at each timestep when the farm has been run with 5000 vs 250 Monte-Carlo runs.

df_diff_250 <- rbind(weight_250, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_250 - nruns_5000)/nruns_5000)

ggplot(df_diff_250, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

## Difference between 500 and 5000 nruns

```{r fig-500-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs vs 500 Monte-Carlo runs.

weight_500 <- res_500 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_500, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-500-nruns-weight-diff}
#| fig-width: 8.5
#| fig-cap: Difference in individual weight at each timestep when the farm has been run with 5000 vs 500 Monte-Carlo runs.

df_diff_500 <- rbind(weight_500, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_500 - nruns_5000)/nruns_5000)

ggplot(df_diff_500, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

## Difference between 1000 and 5000 nruns

```{r fig-1000-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs vs 1000 Monte-Carlo runs.

weight_1000 <- res_1000 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_1000, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-1000-nruns-weight-diff}
#| fig-width: 8.5
#| fig-cap: Difference in individual weight at each timestep when the farm has been run with 5000 vs 1000 Monte-Carlo runs.

df_diff_1000 <- rbind(weight_1000, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_1000 - nruns_5000)/nruns_5000)

ggplot(df_diff_1000, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

## Difference between 2500 and 5000 nruns

```{r fig-2500-nruns-weight}
#| fig-width: 8.5
#| fig-cap: Individual weight at each timestep, when the farm has been run with 5000 Monte-Carlo runs vs 2500 Monte-Carlo runs.

weight_2500 <- res_2500 %>% 
  filter(measure == "weight_stat")
weight_5000 <- res_5000 %>% 
  filter(measure == "weight_stat")

ggplot(
  rbind(weight_2500, weight_5000),
  aes(x = t, y = mean, ymin = mean-sd, ymax = mean+sd, colour = nruns, fill = nruns)
) +
  geom_line() +
  geom_ribbon(alpha = 0.25) +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

```{r fig-2500-nruns-weight-diff}
#| fig-width: 8.5
#| fig-cap: Difference in individual weight at each timestep when the farm has been run with 5000 vs 2500 Monte-Carlo runs.

df_diff_2500 <- rbind(weight_2500, weight_5000) %>% 
  select(-sd) %>% 
  pivot_wider(
    names_from = "nruns", names_prefix = "nruns_",
    values_from = mean
  ) %>% 
    mutate(nruns_diff = (nruns_2500 - nruns_5000)/nruns_5000)

ggplot(df_diff_2500, aes(x = t, y = 100*nruns_diff)) +
  geom_line() +
  facet_wrap(facets = vars(farm_ID), nrow = 5) +
  theme_classic()
```

# Summary

```{r summary}
df_diff <- data.frame(
  nruns = c(1, 100, 250, 500, 1000, 2500),
  max_diff = c(
    max(abs(df_diff_1$nruns_diff)),
    max(abs(df_diff_100$nruns_diff)),
    max(abs(df_diff_250$nruns_diff)),
    max(abs(df_diff_500$nruns_diff)),
    max(abs(df_diff_1000$nruns_diff)),
    max(abs(df_diff_2500$nruns_diff))
  )
)

ggplot(df_diff, aes(x = as.factor(nruns), y = 100*max_diff)) +
  geom_col() + theme_classic()
```

### 2025-12-16 docs-working/08_data_analysis.qmd
Updates

--- 2025-08-01 09_data_analysis.qmd
@@
 
-The purpose of this script is to take the raw model outputs and save them as files which answer (or go towards answering) specific questions.
-These files can then be directly called by index.qmd to quickly create plots or text summaries.
-
-```{r}
-#| label: setup
+This script takes outputs from the targets pipeline.
+
+```{r setup}
 #| warning: false
@@
 
+library(tidyverse)
 library(arrow)
 library(sf)
-library(dplyr)
-library(tidyr)
 library(terra)
 library(magrittr)
-library(purrr)
 library(furrr)
@@
 
+```{r filenames}
+#| code-summary: Set up global filenames
+
+# Filenames
+# species_params_excel <- c(file = file.path(input_species_param_path, "Species.xlsx"), sheet = "Atlantic salmon")
+# pop_params_excel <- c(file = file.path(input_species_param_path, "Population.xlsx"))
+# farm_locations_parquet <- file.path(input_farm_coords_path, "farm_coords.parquet")
+# farm_coords_file <- file.path(output_farm_data_path, "farm_coords.qs")
+# farm_geometry_file <- file.path(output_farm_data_path, "farm_geometry.qs")
+# farm_ts_data_file <- file.path(output_farm_data_path, "farm_ts_data.qs")
+# species_params_file <- file.path(output_species_data_path, "species_params.qs")
+# sens_params_file <- file.path(output_species_data_path, "sens_params.qs")
+# pop_params_file <- file.path(output_species_data_path, "pop_params.qs")
+# feed_params_file <- file.path(output_species_data_path, "feed_params.qs")
+# farm_harvest_file <- file.path(output_farm_data_path, "farm_harvest_size.qs")
+```
+
+# Look at raw outputs
+
+```{r raw-outputs}
+total_ends <- qread(file.path(output_model_farm_path, "total_ends.qs")) %>% 
+  mutate(
+    feed_group = as.factor(str_remove(feed, "_min|_max")),
+    feed_type = case_when(
+      str_detect(feed, "_min") ~ "min",
+      str_detect(feed, "_max") ~ "max",
+      T ~ "mean"
+    ) %>% as.factor(),
+    mean = set_units(mean, "g"),
+    sd = set_units(sd, "g"),
+    mean_biomass = set_units(mean, "g g_fish-1"),
+    sd_biomass = set_units(sd, "g g_fish-1")
+  )
+
+cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
+  mutate(
+    feed_group = as.factor(str_remove(feed, "_min|_max")),
+    feed_type = case_when(
+      str_detect(feed, "_min") ~ "min",
+      str_detect(feed, "_max") ~ "max",
+      T ~ "mean"
+    ) %>% as.factor()
+  )
+```
+
+# Feed provided and lost
+
+```{r feed-prov-lost}
+#| code-summary: Show differences between diets in feed provided and lost
+#| fig-cap: Mean food provided and uneaten feed lost to the environment (g/g salmon)
+
+feed_end <- total_ends %>% 
+  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
+  mutate(measure = droplevels(measure))
+
+ggplot(
+    feed_end, 
+    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
+  ) +
+  geom_boxplot() +
+  facet_wrap(facets = vars(measure), scales = "free") +
+  prettyplot_300()
+```
+
+# Faeces excreted
+
+```{r feed-prov-lost}
+#| code-summary: Show differences between diets in feed provided and lost
+
+feed_end <- total_ends %>% 
+  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
+  mutate(measure = droplevels(measure))
+
+ggplot(
+    feed_end, 
+    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
+  ) +
+  geom_boxplot() +
+  facet_wrap(facets = vars(measure), scales = "free") +
+  prettyplot_300()
+```
+
+# Total waste
+
 # Raw output processing

### 2025-12-16 docs-working/index.qmd
Updates

@@
 | **[Formulating Feeds](05_formulating_feeds.html)** | Feed composition formulation for model runs |
+| **[How many runs per farm?](06_how_man_runs_per_farm.html)** | Determining how many Monte-Carlo runs is enough |
 | **[Running Atlantic Salmon Model](06_run_atlantic_salmon_model.html)** | Atlantic salmon growth model execution |
-
-## Extra scripts
-
-The extra scripts for this project involved some exploration into potential impacts of nutrient losses. These will likely not make it into the final manuscript.
-
-| Page | Description |
-|---------|:-------------------------------------------------|
-| **[Species Layers](07_species_layers.html)** | Spatial analysis of species distribution layers, to try and acertain impacts on vulnerable species |
-| **[Relative N Inputs](08_relative_N_inputs.html)** | Analysis of nitrogen input (runoff) patterns and the relative impacts of farm nutrients |
+| **[Data Analysis](08_data_analysis.html)** | Analysing the outputs of the Atlantic salmon growth model |
+| **[Figures for manuscript](09_figures_for_manuscript.html)** | Code used to generate the specific figures used in the manuscript |
 

### 2025-12-16 src/display_globals.R

@@ -1,0 +1,51 @@
+suppressPackageStartupMessages(suppressWarnings({
+  library(tidyverse)
+}))
+
+# This function is designed to work with a DPI of 300
+prettyplot_300 <- function() {
+  theme_classic() +
+    theme(
+      text = element_text(family = "serif", size = 12, colour = "black"),
+      legend.position = "none",
+      axis.title.y = element_text(vjust = 0.5),
+      axis.title.x = element_text(vjust = 0.5),
+      legend.title = element_blank()
+    )
+}
+
+# This function is designed to work with a DPI of 600
+prettyplot_600 <- function() {
+  theme_classic() +
+    theme(
+      text = element_text(family = "serif", size = 12, colour = "black"),
+      legend.position = "none",
+      axis.title.y = element_text(vjust = 0.5),
+      axis.title.x = element_text(vjust = 0.5),
+      legend.title = element_blank()
+    )
+}
+
+long_feeds <- c("marine_dominant_biomar", "plant_dominant", "novel_inclusive")
+short_feeds <- c("MD", "PD", "NI")
+
+feed_pal <- c(
+  "past" = "#E41A1C", 
+  "reference" = "#377EB8", 
+  "future" = "#4DAF4A",
+  "plant_dominant" = "#4DAF4A",
+  "marine_dominant" = "#377EB8",
+  "novel_inclusive" = "#E41A1C",
+  "PD" = "#4DAF4A",
+  "MD" = "#377EB8",
+  "NI" = "#E41A1C"
+)
+cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
+macro_pal <- c(
+  "protein" = "darkred", 
+  "P" = "darkred", 
+  "carbohydrates" = "steelblue", 
+  "C" = "steelblue", 
+  "lipids" = "darkgoldenrod1", 
+  "L" = "darkgoldenrod1"
+)

### 2025-12-16 targets/_targets_farmruns.R

@@ -69,6 +69,19 @@ list(
     command = {
       list(
         "marine_dominant_biomar" = qread(feed_params_file)[["marine_dominant_biomar"]],
+        "marine_dominant_biomar_min" = qread(feed_params_file)[["marine_dominant_biomar"]] %>% 
+          lapply(function(el) {
+            el %>% 
+              mutate(digest = min_digest) %>% 
+              select(ingredient, proportion, macro, digest)
+          }),
+        "marine_dominant_biomar_max" = qread(feed_params_file)[["marine_dominant_biomar"]] %>% 
+          lapply(function(el) {
+            el %>% 
+              mutate(digest = max_digest) %>% 
+              select(ingredient, proportion, macro, digest)
+          }),
+        "animal_inclusive_biomar" = qread(feed_params_file)[["animal_inclusive_biomar"]],
         "animal_inclusive_biomar_min" = qread(feed_params_file)[["animal_inclusive_biomar"]] %>% 
           lapply(function(el) {
             el %>% 
@@ -81,6 +94,7 @@ list(
               mutate(digest = max_digest) %>% 
               select(ingredient, proportion, macro, digest)
           }),
+        "novel_inclusive_biomar" = qread(feed_params_file)[["novel_inclusive_biomar"]],
         "novel_inclusive_biomar_min" = qread(feed_params_file)[["novel_inclusive_biomar"]] %>% 
           lapply(function(el) {
             el %>% 
@@ -212,6 +226,7 @@ list(
   tar_target(
     farm_run_chunked,
     command = {
+      # error == T
       farm_static_data <- split(farm_static_data_chunked, farm_static_data_chunked$farm_ID)
       farm_ts_data <- farm_ts_data_chunked
       purrr::map2_dfr(farm_ts_data, farm_static_data, function(ts, static) {
@@ -219,7 +234,7 @@ list(
           pop_params = all_params,
           species_params = all_params,
           water_temp = ts$temp_c,
-          feed_params = feed_params,
+          feed_params = purrr::flatten(feed_params),
           times = c(t_start = static$t_start, t_end = static$t_end, dt = 1),
           N_pop = ts$Npop,
           nruns = inds_per_farm
@@ -245,13 +260,18 @@ list(
   tar_target(
     farm_full_results,
     command = {
+      # error == T
[…]

### 2025-12-17 docs-working/07_run_atlantic_salmon_model.qmd
Changes for working on Nectar

@@
 #| code-summary: Set up global filenames
+
+farm_script <- here("targets/_targets_farmruns.R")
+farm_store <- here("targets/_targets_farmruns")
+sens_script <- here("targets/_targets_sensitivities.R")
+sens_store <- here("targets/_targets_sensitivities")
 
@@
 
-Sys.setenv(TAR_PROJECT = "project_farmruns")
+# tar_make(names = c("feed_params", "feed_names"), script = farm_script, store = farm_store)
 
-# tar_make(names = c("feed_params", "feed_names"))
-
-tar_load(feed_params)
-tar_load(feed_names)
+tar_load(feed_params, store = farm_store)
+tar_load(feed_names, store = farm_store)
 
@@
 
-Sys.setenv(TAR_PROJECT = "project_farmruns")
-# tar_validate()
-# tar_prune()
+# Sys.setenv(TAR_PROJECT = "project_farmruns")
 
-# tar_make(test_reference_feed)
-tar_load_globals()
+tar_validate(script = farm_script, store = farm_store)
+# tar_prune(script = farm_script, store = farm_store)
+
+tar_make(test_reference_feed, script = farm_script, store = farm_store)
+tar_load_globals(script = farm_script)
 reference_feed_name
-tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
+tar_read(test_reference_feed, store = farm_store) # if weight ~ 0 then feeds aren't processing properly
 ```
@@
 
-Sys.setenv(TAR_PROJECT = "project_farmruns")
+# Sys.setenv(TAR_PROJECT = "project_farmruns")
 
 # Get harvest sizes for all farms
-tar_make(names = contains(c("harvest_size", "feed_params")))
+tar_make(names = contains(c("harvest_size", "feed_params")), script = farm_script, store = farm_store)
 ```
@@
 
-harvest_size <- tar_read(harvest_size_chunked) %>% 
+harvest_size <- tar_read(harvest_size_chunked, store = farm_store) %>% 
   bind_rows()
@@
 
-Sys.setenv(TAR_PROJECT = "project_sensitivities")
-# tar_validate()
-# tar_visnetwork(targets_only = T)
+# Sys.setenv(TAR_PROJECT = "project_sensitivities")
+# tar_validate(script = farm_script, store = farm_store)
+# tar_visnetwork(targets_only = T, script = farm_script, store = farm_store)
 
-tar_make(test_reference_feed)
-tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
+tar_make(test_reference_feed, script = sens_script, store = sens_store)
+tar_read(test_reference_feed, store = sens_store) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
 ```
@@
 
-Sys.setenv(TAR_PROJECT = "project_sensitivities")
+# Sys.setenv(TAR_PROJECT = "project_sensitivities")
 
-tar_make(contains("spec"), seconds_meta_append = 300)
-tar_make(contains("pop"), shortcut = T, seconds_meta_append = 300)
-tar_prune()
+tar_make(contains("spec"), seconds_meta_append = 300, script = sens_script, store = sens_store)
+tar_make(contains("pop"), seconds_meta_append = 300, script = sens_script, store = sens_store)
+# tar_prune(script = sens_script, store = sens_store)
 ```
@@
 
-tar_load(sens_results_spec)
-tar_load(sens_results_pop)
+tar_load(sens_results_spec, store = sens_store)
+tar_load(sens_results_pop, store = sens_store)
 
@@
 sens_measures <- levels(sens_results$measure)
-sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
-sens_results_figfiles2 <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))
+sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))
 
@@
     theme_classic()
-  qsave(p, sens_results_figfiles[sm])
-  ggsave(sens_results_figfiles2[sm])
+  ggsave(sens_results_figfiles[sm])
 }
@@
 
-Sys.setenv(TAR_PROJECT = "project_farmruns")
+# Sys.setenv(TAR_PROJECT = "project_farmruns")
 
@@
   names = contains(c("data", "feed")),
-  seconds_meta_append = 90
+  script = farm_script, store = farm_store
 )
 
-# tar_outdated()
+# tar_outdated(script = farm_script, store = farm_store)
 
-# Run results
+# Run whole pipeline
 tar_make(
-  names = c("farm_run_chunked", "farm_full_results"), 
-  seconds_meta_append = 120,
-  shortcut = T # only if you've done the pre-run, above
+  seconds_meta_append = 300,
+  script = farm_script, store = farm_store
 )
@@
 Sys.setenv(TAR_PROJECT = "project_farmruns")
-farm_IDs_chunked <- tar_read(farm_IDs_chunked) %>% unname() %>% unlist()
-tar_load(feed_names)
+farm_IDs_chunked <- tar_read(farm_IDs_chunked, script = farm_script, store = farm_store) %>% unname() %>% unlist()
+tar_load(feed_names, script = farm_script, store = farm_store)
 
-tar_load(farm_full_results)
+tar_load(farm_full_results, script = farm_script, store = farm_store)
 total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))

### 2025-12-17 docs-working/05_formulating_feeds.qmd
Moving data files

@@
 
-ingreds <- file.path(input_feed_profile_path, "all_ingredients.xlsx") %>% 
+ingreds <- file.path(bigdata_path, "all_ingredients.xlsx") %>% 
   read_excel(sheet = "all_ingredients") %>% 

### 2025-12-17 docs-working/05_formulating_feeds.qmd
Re-render

@@
 
-The purpose of this markdown is to formulate all the feeds that will be used in the analysis. These feeds are:
-- marine_dominant: a "past" salmonid diet where most protein is sourced from marine-based ingredients.
-- plant_dominant: a "current" salmonid diet where most protein is sourced from land-based ingredients.
-- novel_inclusive_2: a potential future salmonid diet which includes some novel ingredients. This formulation uses maximal digestibility values.
-- novel_inclusive_1: a potential future salmonid diet which includes some novel ingredients. This formulation uses the same formulation as novel_inclusive_2, but with minimal digestibility values.
+The purpose of this markdown is to formulate all the feeds that will be used in the analysis.
 
@@
 The following chunk allows as many ingredients and feeds to be added to the incoming data as needed, it will still be formatted into a form that the `targets` pipelines can use.
+This code does not create the "min" and "max" deigestibility versions of the feeds, they are created in the targets pipeline.
 

### 2025-12-17 docs-working/index.qmd
Re-render

@@
 title: "Local-to-Global Mariculture Modelling"
-subtitle: "Project Documentation"
-author: "Dr Tormey Reimer"
+subtitle: "Project Documentation - Index of files"
+author: "Tormey Reimer"
 date: today
 execute:
-  # eval: true
-  echo: false
-  warning: false
-  message: false
-  cache: true # quarto render index.qmd --cache-refresh
+  eval: false
 knitr: 
@@
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  walk(source)
 
@@
 
-@tbl-results-summary is a summary of all the results I've processed so far, basically trying to acertain all the major differences in inputs between the feeds.
-
-The NI diet was more efficient than the PD diet.
-When farms were fed the NI diet they had an average FCE* of `r fpr_pb1$NI`, compared to the average FCE of `r fpr_pb1$PD` when farms were fed the PD diet, and feeding the NI diet resulted in `r bpr2$NI`% more biomass produced with the same population compared to the PD diet.
-
-::: {.aside}
-*Note that when I refer to "FCE" here I'm talking about the "PLC weight" (weight of protein + lipid + carbohydrate) of feed, which may differ from its actual weight because of the inclusion of minerals and non-digestible material.
-:::
-
-Despite this, nutrients lost to the environment were generally highest in the NI diet and lowest in the MD diet. 
-In terms of total waste, the NI and PD diets were very similar.
-I initially thought that this was because the NI and PD diets are more similar than the MD and PD diets, but this doesn't match up with the numbers (PD and NI diets are 63.3% the same, while the PD and MD diets are 54.3% the same).
-The MD diet had markedly lower total waste than either the PD or NI diets.
-
-However, the composition of waste lost to the environment was very different between the diets, particularly in terms of proteins and carbohydrates (@fig-PLC-waste-comparison).
-The PD diet had the lowest protein waste output and the NI diet had the highest, while the MD diet had the lowest carbohydrate and lipid waste outputs and the PD diet the highest.
-Overall, changing from the PD diet to the NI diet would result in a `r abs(plc3$NI_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively, while changing to the MD diet would result in a `r abs(plc3$MD_P)`% increase in protein waste but a `r abs(plc3$NI_C)`% and `r abs(plc3$NI_L)`% reduction in carbohydrates and lipids respectively.
-
-Consequently, while total waste was only `r tow2$NI`% higher when farms were fed the NI diet, protein waste was `r plc3$NI_P`% higher and nitrogen waste was `r nit2$NI`% higher relative to when farms were fed the PD diet.
-
-Proteins in the NI diet were only slightly less digestible than those used in the PD diet (@tbl-modelled-feeds), but this difference, combined with the higher protein content in the NI diet, resulted in the large difference in nitrogen lost to the environment.
-
+```{r not-in-use}
 | Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
@@
 {#tbl-results-summary}
+```
 
@@
 ```
-
-::: {.aside}
-I accidentally used raw total waste in @fig-PLC-waste-comparison instead of waste per kg of biomass
-:::
 
@@
 
-Each farm's final population was calculated by dividing the production tonnage required by the average modelled individual harvest size for each farm (when feed reference feed, @fig-harvest-size).
-A population timeseries was then generated using the standard mortality rate (`r round(unname(pop_params['mortmyt'])*100, 3)` % d$^{-1}$).
-
 ```{r}
@@
 ```
-
-Using this method, a farm's 'population' is not a good representation of the actual number of individuals being farmed, but it ensures each farm location is producing the correct tonnage while allowing comparisons between the different feeds.
 
@@
 
-By this method, farm biomass as predicted by the model predicted farm tonnage relatively accurately.
-Predicted farm biomass was within `r round(100*min(production$min_percdiff),1)`% -- `r round(100*max(production$max_percdiff),1)`% of tonnage produced.
-
 ## Feed provision and feeding response to temperature {#sec-model-feeding}
-
-@fig-functional-response-to-temperature shows the response of food ingested to temperature, and the food provided in response.
 
@@
 
-| Feed | Protein | Lipid | Carbohydrate |
-|------|:----------:|:----------:|:----------:|
-| Plant-dominant | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "plant_dominant", macro == "C")$digest, 1)`%) |
-| Marine-dominant | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "marine_dominant", macro == "C")$digest, 1)`%) |
-| Novel-inclusive | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "P")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "L")$digest, 1)`%) | `r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$total, 1)`% (`r round(100*filter(feed_summary, feed == "novel_inclusive", macro == "C")$digest, 1)`%) |
-: Feed macronutrient details (composition in feed, digestibility). {#tbl-modelled-feeds}
-
 ## Model sensitivity to parameter changes {#sec-param-sensitivity}
-
-Parameter sensitivity was tested by varying each parameter by $\pm 10$% and calculating sensitivity as $S_p = \frac{(P_{1.1} - P_{0.9})}{0.2 \times P_1}$, where $S$ is the sensitivity of the measured variable to changes in parameter $p$, and $P_{1.1}$, $P_{0.9}$, and $P_{1}$ are the value of the measured variable when the model is run with parameter $p$ at 110%, 90%, and 100% of its value respectively.
-The population-level parameters ($\overline{W}$, $\Delta{W}$, $\overline{I_{max}}$, $\Delta{I_{max}}$, $\overline{F}$, $\Delta{F}$) were tested with a population of of 5000 on a random 10% of farms, while all other parameters were tested across all farms with a population of 10 (@fig-sensitivity-results).
 
@@
 
-All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
-Major packages used include `r cite_packages(packages)`.
+```{r not-in-use-cite}
+# All analysis was conducted in R version `r R.version[['major']]`.`r R.version[['minor']]` "`r R.version[['nickname']]`" [@R_base]. 
+# Major packages used include `r cite_packages(packages)`.
 
-For a full list of R packages used see the lockfile on [Github](https://www.github.com).
-This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms].
+# For a full list of R packages used see the lockfile on [Github](https://www.github.com).
+# This manuscript was written in Quarto [@quarto] using TinyTex [@tinytex] and the acronyms extension [@acronyms]. 
+```

### 2025-12-18 docs-working/05_formulating_feeds.qmd
Updates to feeds documentation

@@
 ```
+
+# Comparing feeds
+
+The three "biomar" feeds were designed to be isoenergetic.
+
+```{r feed-stats}
+#| code-summary: Calculate some stats about the feeds
+
+feed_stats <- feed_inputs %>% 
+  select(-contains(c("max", "min"))) %>% 
+  mutate(
+    ing_protein = proportion * protein,
+    ing_carb = proportion * carb,
+    ing_lipid = proportion * lipid,
+    digest_protein = ing_protein * protein_digestibility,
+    digest_carb = ing_carb * carb_digestibility,
+    digest_lipid = ing_lipid * lipid_digestibility,
+    E_protein = digest_protein * 17,
+    E_carb = digest_carb * 16.8,
+    E_lipid = digest_lipid * 37.6
+  ) %>% 
+  group_by(feed) %>% 
+  reframe(
+    total_protein = sum(ing_protein),
+    total_carb = sum(ing_carb),
+    total_lipid = sum(ing_lipid),
+    AD_protein = sum(digest_protein),
+    AD_carb = sum(digest_carb),
+    AD_lipid = sum(digest_lipid),
+    E_protein = sum(E_protein),
+    E_carb = sum(E_carb),
+    E_lipid = sum(E_lipid)
+    ) %>% 
+  mutate(
+    E = E_protein + E_carb + E_lipid,
+    group = case_when(str_detect(feed, "biomar") ~ "biomar", T ~ "other")
+  ) %>% 
+  relocate(group, .before = "feed") %>% 
+  arrange(group)
+
+feed_stats %>% 
+  select(group, feed, E)
+```
+
+```{r feed-macro-digestibility}
+#| code-summary: Code to generate plot
+#| fig-cap: Total protein, carbohydrate and lipid composition of each feed, with the undigestible portion shown as the lighter bars on top.
+
+merge(
+  feed_stats %>% 
+    select(feed, group, contains("total_")) %>% 
+    pivot_longer(
+      cols = contains("total"),
+      names_to = "macro", names_prefix = "total_",
+      values_to = "total"
+    ),
+  feed_stats %>% 
+    select(feed, group, contains("AD_")) %>% 
+    pivot_longer(
+      cols = contains("AD"),
+      names_to = "macro", names_prefix = "AD_",
+      values_to = "AD"
+    ),
+  by = c("feed", "group", "macro")
+  ) %>% 
+  mutate(feed = as.factor(feed)) %>%   
+  ggplot(aes(x = macro, fill = feed)) +
+  geom_col(aes(y = total), position = position_dodge(), alpha = 0.5, colour = "black") +
+  geom_col(aes(y = AD), position = position_dodge(), alpha = 0.75, colour = "black") +
+  theme_classic() +
+  facet_wrap(facets = vars(group))
+```
+
+```{r feed-energy}
+#| code-summary: Code to generate plot
+#| fig-cap: The proportion of energy derived from protein, carbohydrate and lipid within each feed.
+
+feed_stats %>% 
+  mutate(
+    E_protein = E_protein/E,
+    E_carb = E_carb/E,
+    E_lipid = E_lipid/E
+  ) %>% 
+  select(feed, group, contains("E_")) %>% 
+  pivot_longer(
+    cols = contains("E_"),
+    names_to = "macro", names_prefix = "E_",
+    values_to = "value"
+  ) %>% 
+  ggplot(aes(x = macro, y = value, fill = feed)) +
+  geom_col(position = position_dodge(), colour = "black") +
+  theme_classic() +
+  facet_wrap(facets = vars(group))
+```

### 2025-12-18 docs-working/08_data_analysis.qmd
Updates to feeds documentation

@@
 ```{r raw-outputs}
-total_ends <- qread(file.path(output_model_farm_path, "total_ends.qs")) %>% 
-  mutate(
-    feed_group = as.factor(str_remove(feed, "_min|_max")),
+total_ends <- file.path(output_model_farm_path, "total_ends.qs") %>% 
+  qread() %>% 
+  mutate(
+    feed_group = factor(
+      str_remove(feed, "_min|_max"), 
+      levels = long_feeds,
+      labels = short_feeds
+      ),
     feed_type = case_when(
@@
     sd = set_units(sd, "g"),
-    mean_biomass = set_units(mean, "g g_fish-1"),
-    sd_biomass = set_units(sd, "g g_fish-1")
-  )
-
-cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
-  mutate(
-    feed_group = as.factor(str_remove(feed, "_min|_max")),
+    mean_biomass = set_units(mean_biomass, "g g_fish-1"),
+    sd_biomass = set_units(sd_biomass, "g g_fish-1")
+  )
+
+cohort_results <- file.path(output_model_cohort_path, "cohort_results.qs") %>% 
+  qread() %>% 
+  mutate(
+    feed_group = factor(
+      str_remove(feed, "_min|_max"), 
+      levels = long_feeds,
+      labels = short_feeds
+      ),
     feed_type = case_when(
@@
       T ~ "mean"
-    ) %>% as.factor()
+      ) %>% as.factor(),
+    mean = set_units(mean, "g"),
+    sd = set_units(sd, "g"),
+    mean_biomass = set_units(mean_biomass, "g g_fish-1"),
+    sd_biomass = set_units(sd_biomass, "g g_fish-1")
   )

### 2025-12-18 docs-working/index.qmd
Updates to feeds documentation

@@
     ))
-
-long_feeds <- c("marine_dominant", "plant_dominant", "novel_inclusive")
-short_feeds <- c("MD", "PD", "NI")
-
-feed_pal <- c(
-  "past" = "#E41A1C", 
-  "reference" = "#377EB8", 
-  "future" = "#4DAF4A",
-  "plant_dominant" = "#4DAF4A",
-  "marine_dominant" = "#377EB8",
-  "novel_inclusive" = "#E41A1C",
-  "PD" = "#4DAF4A",
-  "MD" = "#377EB8",
-  "NI" = "#E41A1C"
-)
-cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
-macro_pal <- c(
-  "protein" = "darkred", 
-  "P" = "darkred", 
-  "carbohydrates" = "steelblue", 
-  "C" = "steelblue", 
-  "lipids" = "darkgoldenrod1", 
-  "L" = "darkgoldenrod1"
-)
-
-prettyplot <- function() {
-  theme_classic() +
-    theme(
-      text = element_text(family = "serif", size = 14, colour = "black"),
-      legend.position = "none",
-      axis.title.y = element_text(margin = margin(r = 5)),
-      axis.title.x = element_text(margin = margin(t = 5))
-    )
-}
 ```

### 2025-12-18 src/display_globals.R

@@ -26,19 +26,16 @@ prettyplot_600 <- function() {
     )
 }
 
-long_feeds <- c("marine_dominant_biomar", "plant_dominant", "novel_inclusive")
-short_feeds <- c("MD", "PD", "NI")
+long_feeds <- c("marine_dominant_biomar", "animal_inclusive_biomar", "novel_inclusive_biomar")
+short_feeds <- c("MD", "AI", "NI")
 
 feed_pal <- c(
-  "past" = "#E41A1C", 
-  "reference" = "#377EB8", 
-  "future" = "#4DAF4A",
-  "plant_dominant" = "#4DAF4A",
-  "marine_dominant" = "#377EB8",
-  "novel_inclusive" = "#E41A1C",
-  "PD" = "#4DAF4A",
+  "NI" = "#4DAF4A",
   "MD" = "#377EB8",
-  "NI" = "#E41A1C"
+  "AI" = "#E41A1C",
+  "novel_inclusive_biomar" = "#4DAF4A",
+  "marine_dominant_biomar" = "#377EB8",
+  "animal_inclusive_biomar" = "#E41A1C"
 )
 cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
 macro_pal <- c(

### 2025-12-18 docs-working/08_data_analysis.qmd
Updates to docs

--- 2025-12-16 docs-working/08_data_analysis.qmd
@@
 title: "Process data from Atlantic salmon model runs"
-format: html
-editor: source
+author: "Tormey Reimer"
+date: today
 ---
@@
   list.files(pattern = "\\.R$", full.names = TRUE) %>% 
-  str_subset("map", negate = T) %>% 
   walk(source)
@@
     sd = set_units(sd, "g"),
-    mean_biomass = set_units(mean, "g g_fish-1"),
-    sd_biomass = set_units(sd, "g g_fish-1")
-  )
-
-cohort_results <- qread(file.path(output_model_cohort_path, "cohort_results.qs")) %>% 
-  mutate(
-    feed_group = as.factor(str_remove(feed, "_min|_max")),
+    mean_biomass = set_units(mean_biomass, "g_fish"),
+    sd_biomass = set_units(sd_biomass, "g_fish"),
+    mean_per_biom = set_units(mean_per_biom, "g g_fish-1"),
+    sd_per_biom = set_units(sd_per_biom, "g g_fish-1")
+  )
+
+cohort_results <- file.path(output_model_cohort_path, "cohort_results.qs") %>% 
+  qread() %>% 
+  mutate(
+    feed_group = factor(
+      str_remove(feed, "_min|_max"), 
+      levels = long_feeds,
+      labels = short_feeds
+      ),
     feed_type = case_when(
@@
       T ~ "mean"
-    ) %>% as.factor()
-  )
-```
-
-# Feed provided and lost
+      ) %>% as.factor(),
+    mean = set_units(mean, "g"),
+    sd = set_units(sd, "g"),
+    mean_biomass = set_units(mean_biomass, "g_fish"),
+    sd_biomass = set_units(sd_biomass, "g_fish"),
+    mean_per_biom = set_units(mean_per_biom, "g g_fish-1"),
+    sd_per_biom = set_units(sd_per_biom, "g g_fish-1")
+  )
+```
+
+```{r basic-stats}
+#| code-summary: Code to generate plot
+#| fig-height: 12
+
+total_ends %>% 
+  filter(!measure %in% c("biomass_stat", "food_prov_stat")) %>% 
+  mutate(
+    measure = factor(measure, levels = c(
+      "C_excr_stat", "C_uneat_stat", 
+      "L_excr_stat", "L_uneat_stat", 
+      "P_excr_stat", "P_uneat_stat", 
+      "total_excr_stat", "total_uneat_stat"
+    )),
+    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1")
+  ) %>% 
+  ggplot(aes(x = feed_group, y = mean_per_biom, fill = feed_type)) +
+  geom_boxplot() +
+  facet_wrap(facets = vars(measure), scales = "free", ncol = 2) +
+  prettyplot_600() +
+  theme(legend.position = "right")
+
+# | Description | Plant-dominant | Marine-dominant | Novel-inclusive | Change from PD to MD (%) | Change from PD to NI (%) |
+# |:--------------------------|:----------:|:----------:|:----------:|:----------:|:----------:|
+# | Salmon biomass produced (t)                         | `r bpr1$PD`        | `r bpr1$MD`        | `r bpr1$NI`        | `r coln(bpr2$MD)`    | `r coln(bpr2$NI)`    |
+# | Feed provided (t)                                   | `r fpr1$PD`        | `r fpr1$MD`        | `r fpr1$NI`        | `r coln(fpr2$MD)`    | `r coln(fpr2$NI)`    |
+# | Feed provided (kg/kg salmon)                        | `r fpr_pb1$PD`     | `r fpr_pb1$MD`     | `r fpr_pb1$NI`     | `r coln(fpr_pb2$MD)` | `r coln(fpr_pb2$NI)` |
+# | Uneaten feed (t)                                    | `r tuf1$PD`        | `r tuf1$MD`        | `r tuf1$NI`        | `r coln(tuf2$MD)`    | `r coln(tuf2$NI)`    |
+# | Excreted waste (t)                                  | `r tew1$PD`        | `r tew1$MD`        | `r tew1$NI`        | `r coln(tew2$MD)`    | `r coln(tew2$NI)`    |
+# | Total waste (E+U, t)                                | `r tow1$PD`        | `r tow1$MD`        | `r tow1$NI`        | `r coln(tow2$MD)`    | `r coln(tow2$NI)`    |
+# | Proportion of total waste composed of excretion (%) | `r epw$PD`         | `r epw$MD`         | `r epw$NI`         |                      |                      |
+# | Total protein waste (t)                             | `r sum(plc1$PD_P)` | `r sum(plc1$MD_P)` | `r sum(plc1$NI_P)` | `r coln(plc3$MD_P)`  | `r coln(plc3$NI_P)`  |
+# | Total carbohydrate waste (t)                        | `r sum(plc1$PD_C)` | `r sum(plc1$MD_C)` | `r sum(plc1$NI_C)` | `r coln(plc3$MD_C)`  | `r coln(plc3$NI_C)`  |
+# | Total lipid waste (t)                               | `r sum(plc1$PD_L)` | `r sum(plc1$MD_L)` | `r sum(plc1$NI_L)` | `r coln(plc3$MD_L)`  | `r coln(plc3$NI_L)`  |
+# | Proportion of protein waste from excretion (%)      | `r plc2$PD_P`      | `r plc2$MD_P`      | `r plc2$NI_P`      |                      |                      |
+# | Proportion of carbohydrate waste from excretion (%) | `r plc2$PD_C`      | `r plc2$MD_C`      | `r plc2$NI_C`      |                      |                      |
+# | Proportion of lipid waste from excretion (%)        | `r plc2$PD_L`      | `r plc2$MD_L`      | `r plc2$NI_L`      |                      |                      |
+# | Total N from uneaten feed (t)                       | `r niu1$PD`        | `r niu1$MD`        | `r niu1$NI`        | `r coln(niu2$MD)`    | `r coln(niu2$NI)`    |
+# | Total N from excreted waste (t)                     | `r nie1$PD`        | `r nie1$MD`        | `r nie1$NI`        | `r coln(nie2$MD)`    | `r coln(nie2$NI)`    |
+# | Total N inputs (E+U, t)                             | `r nit1$PD`        | `r nit1$MD`        | `r nit1$NI`        | `r coln(nit2$MD)`    | `r coln(nit2$NI)`    |
+# : Summary of all results.
+Unless otherwise specified, values presented are means across all farms, summed across a single production period.
+In the % change columns, the colour of the text indicates whether there is an increase (red) or a decrease (green).
+Some cells of this table are blank - sometimes that means it doesn't make sense to fill that cell, but sometimes it means I haven't got to it yet.
+{#tbl-results-summary}
+```
+
+## Feed provided and lost
 
 ```{r feed-prov-lost}
-#| code-summary: Show differences between diets in feed provided and lost
-#| fig-cap: Mean food provided and uneaten feed lost to the environment (g/g salmon)
+#| code-summary: Code to generate plot
+#| fig-cap: Mean food provided and uneaten feed lost to the environment when feeds use minimum (blue), maximum (red) or mean (green) digestibility coefficients.
 
 feed_end <- total_ends %>% 
-  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
-  mutate(measure = droplevels(measure))
-
-ggplot(
-    feed_end, 
-    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
-  ) +
+  filter(measure %in% c("total_uneat_stat", "food_prov_stat"))
+
+feed_end %>% 
+  mutate(
+    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1"),
+    measure = droplevels(measure)
+    ) %>% 
+  ggplot(aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)) +
   geom_boxplot() +
@@
 
-# Faeces excreted
-
-```{r feed-prov-lost}
-#| code-summary: Show differences between diets in feed provided and lost
-
-feed_end <- total_ends %>% 
-  filter(measure %in% c("total_uneat_stat", "food_prov_stat")) %>% 
-  mutate(measure = droplevels(measure))
-
-ggplot(
-    feed_end, 
-    aes(x = feed_group, y = mean_per_biom, fill = feed_type, group = feed)
-  ) +
+## Faeces excreted and proportion of total waste
+
+```{r faeces-excreted}
+#| code-summary: Code to generate plot
+#| fig-cap: Mean faeces excreted and proportion of total waste coming from faeces when feeds use minimum (blue), maximum (red) or mean (green) digestibility coefficients.
+
+faeces_end <- total_ends %>% 
+  filter(measure %in% c("total_excr_stat", "total_uneat_stat")) %>% 
+  select(farm_ID, feed, feed_type, feed_group, measure, mean_per_biom) %>% 
+  mutate(
+    mean_per_biom = set_units(mean_per_biom, "g kg_fish-1") %>% drop_units(),
+    measure = droplevels(measure)
+    ) %>%
+  pivot_wider(
+    names_from = "measure",
+    values_from = "mean_per_biom"
+  ) %>% 
+  mutate(
+    total_waste = total_excr_stat + total_uneat_stat,
+    total_excr_prop = 100*total_excr_stat/total_waste
+  ) %>% 
+  select(-total_waste, total_uneat_stat) %>% 
+  pivot_longer(
+    cols = c(total_excr_stat, total_excr_prop),
+    names_to = "measure",
+    values_to = "value"
+  )
+
+faeces_end %>% 
+  ggplot(aes(x = feed_group, y = value, fill = feed_type, group = feed)) +
   geom_boxplot() +
@@
 
-# Total waste
-
-# Raw output processing
+# Farm locations
 
 For some of the outputs of the model, it makes sense to sum them across a production period and/or calculate their values per unit of biomass. 
-```{r}
-#| label: biomass-location-globals-farm
+```{r biomass-location-globals-farm}
 
@@
   mutate(country = as.factor(country))
-
-fish_weight <- find_read(output_model_farm_path, "weight")
-farm_biomass <- find_read(output_model_farm_path, "biomass_stat")
-biomass_produced <- find_read(output_model_farm_path, "biomass_produced")
-
-# farm_biomass has had the final day (when fish are not fed) removed - this adds it back
-all_biomass <- rbind(farm_biomass, biomass_produced)
-qs::qsave(all_biomass, file.path(data_analysis_path, "all_biomass.qs"))
-
-farm_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
-all_biomass %>% filter(farm_ID == 1) %>% pull(t) %>% unique() %>% length()
-```
+```
+
+# Daily results
+
+```{r daily-uneaten-excreted}
+
+daily_results_1 <- cohort_results %>% 
+  filter(measure %in% c("total_uneat_stat", "total_excr_stat")) %>% 
+  select(-c(mean, sd, mean_biomass, sd_biomass, sd_per_biom)) %>% 
+  group_by(feed_group, feed_type, feed, measure, prod_t) %>% 
+  reframe(
+    mean = mean(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    sd = sd(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    min = min(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    max = max(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")
+  )
+
+daily_results_1 %>% 
+  ggplot(aes(x = prod_t, y = mean, colour = feed, group = feed)) +
+  geom_line() +
+  facet_wrap(facets = vars(measure), scales = "free", nrow = 2) +
+  theme_classic()
+```
+
+# Spatial results
+
+## Total ends
+
+## Daily mean, min, max
+
+```{r}
+space_daily_results_1 <- cohort_results %>% 
+  filter(measure %in% c("total_uneat_stat", "total_excr_stat")) %>% 
+  select(-c(mean, sd, mean_biomass, sd_biomass, sd_per_biom)) %>% 
+  group_by(feed_group, feed_type, feed, measure, farm_ID) %>% 
+  reframe(
+    mean = mean(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    sd = sd(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    min = min(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
+    max = max(mean_per_biom) %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")
+  ) %>% 
+  merge(farm_locs, by = "farm_ID")
+
+p_bigmap_robinson +
+  geom_sf(
+    data = space_daily_results_1, 
+    aes(colour = drop_units(mean), geometry = geometry), 
+    size = 2
+  ) +
+  coord_sf() +
+  scale_color_viridis_c(option = "turbo", breaks = seq(10, 35, 5), limits = c(10,36)) + 
+  guides(col = guide_colourbar(
+    title = expression("Difference in N inputs (kg/t salmon)"),
+    direction = "horizontal", position = "bottom",
+    label.position = "bottom", title.position = "top",
+    title.vjust = 1, title.hjust = 0.5,
+    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 1,
+    barheight = 1.5, barwidth = 20,
+  )) +
+  facet_wrap(facets = vars(feed)) +
+  prettyplot_300() +
+  theme(
+    strip.background = element_blank(), 
+    strip.text = element_blank(),
+    axis.title = element_blank(),
+    legend.position = "bottom"
+  )
+```
+
+# Old stuff
 
@@
 
-```{r}
+```{r, eval=F}
 #| label: summed-per-biomass-outputs
@@
 
-```{r}
-#| label: biomass-location-globals-cohort
+```{r biomass-location-globals-cohort, eval=F}
 
@@
 
-```{r}
-#| label: summed-per-biomass-outputs-cohort
-#| eval: false
+```{r summed-per-biomass-outputs-cohort, eval=F}
 
@@
 
-```{r}
-#| label: biomass-produced-comparisons
+```{r biomass-produced-comparisons, eval=F}
 
@@
 
-```{r}
-#| label: food-provided-comparison
+```{r food-provided-comparison, eval=F}
 
@@
 
-```{r}
-#| label: uneaten-feed-comparisons
+```{r uneaten-feed-comparisons, eval=F}
 
@@
 
-## Does excretion increase or decrease with novel feeds?
-
-```{r}
-#| label: excreted-comparison
-
-# Summed across the whole production period
-total_excr_farm_summed <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  pivot_wider(
-    names_from = feed,
-    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
-    id_cols = c(country, farm_ID, measure, days)
-  ) %>% 
-  mutate(
-    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
-    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
-    total_MD = (total_MD-total_PD)/total_PD,
-    total_NI = (total_NI-total_PD)/total_PD
-  ) %>% 
-  select(-contains("PD")) %>% 
-  pivot_longer(
-    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
-    cols = contains(c("sd", "total"))
-  ) %>% 
-  merge(farm_locs, by = c("country", "farm_ID")) %>% 
-  st_as_sf()
-
-# Check that it looks reasonable
-# ggplot(total_excr_farm_summed, aes(x = country, y = total, fill = feed)) +
-#   geom_boxplot()
-
-qs::qsave(total_excr_farm_summed, file.path(comparisons_path, "total_excr_farm_summed.qs"))
-rm(total_excr_farm_summed)
-
-# Summed across the whole production period, per biomass of fish produced
-total_excr_farm_per_biom_summed <- find_read(data_analysis_path, "total_excr_farm_per_biom_summed") %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  pivot_wider(
-    names_from = feed, names_sep = ".", 
-    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
-    id_cols = c(country, farm_ID, measure)
-  ) %>% 
-  mutate(
-    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
-    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
-    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
-    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
-  ) %>% 
-  select(-contains("PD")) %>% 
-  pivot_longer(
-    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
-    cols = contains(c("sd_biom", "mean_biom"))
-  ) %>% 
-  merge(farm_locs, by = c("country", "farm_ID")) %>% 
-  st_as_sf()
-
-# Check that it looks reasonable
-# ggplot(total_excr_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
-#   geom_boxplot()
-
-qs::qsave(total_excr_farm_per_biom_summed, file.path(comparisons_path, "total_excr_farm_per_biom_summed.qs"))
-rm(total_excr_farm_per_biom_summed)
-```
-
-## Do total inputs (mass, excreted and uneaten) increase or decrease with novel feeds?
-
-```{r}
-#| label: total-mass-inputs-comparison
-
-total_mass_inputs_farm_summed <- rbind(
-  find_read(data_analysis_path, "total_uneat_farm_summed"), 
-  find_read(data_analysis_path, "total_excr_farm_summed")
-) %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  group_by(country, farm_ID, feed, days) %>% 
-  reframe(
-    total = sum(total),
-    sd = sqrt(sum(sd^2)),
-    measure = as.factor("excr_uneat")
-  )
-qs::qsave(total_mass_inputs_farm_summed, file.path(data_analysis_path, "total_mass_inputs_farm_summed.qs"))
-rm(total_mass_inputs_farm_summed)
-
-# Summed across the whole production period
-total_mass_inputs_farm_summed <- rbind(
-  find_read(data_analysis_path, "total_uneat_farm_summed"), 
-  find_read(data_analysis_path, "total_excr_farm_summed")
-) %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  group_by(country, farm_ID, feed, days) %>% 
-  reframe(
-    total = sum(total),
-    sd = sqrt(sum(sd^2)),
-    measure = as.factor("excr_uneat")
-  ) %>% 
-  pivot_wider(
-    names_from = feed,
-    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
-    id_cols = c(country, farm_ID, measure, days)
-  ) %>% 
-  mutate(
-    sd_MD = (1/total_PD) * sqrt(sd_MD^2 + sd_PD^2),
-    sd_NI = (1/total_PD) * sqrt(sd_NI^2 + sd_PD^2),
-    total_MD = (total_MD-total_PD)/total_PD,
-    total_NI = (total_NI-total_PD)/total_PD
-  ) %>% 
-  select(-contains("PD")) %>% 
-  pivot_longer(
-    names_to = c(".value", "feed"), names_sep = "_", names_transform = list(feed = as.factor),
-    cols = contains(c("sd", "total"))
-  ) %>% 
-  merge(farm_locs, by = c("country", "farm_ID")) %>% 
-  st_as_sf()
-
-# Check that it looks reasonable
-ggplot(total_mass_inputs_farm_summed, aes(x = country, y = total, fill = feed)) +
-  geom_boxplot()
-
-qs::qsave(total_mass_inputs_farm_summed, file.path(comparisons_path, "total_mass_inputs_farm_summed.qs"))
-rm(total_mass_inputs_farm_summed)
-
-# Summed across the whole production period, per biomass of fish produced
-total_mass_inputs_farm_per_biom_summed <- rbind(
-  find_read(data_analysis_path, "total_uneat_farm_per_biom_summed"), 
-  find_read(data_analysis_path, "total_excr_farm_per_biom_summed")
-  ) %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  group_by(country, farm_ID, feed) %>% 
-  reframe(
-    mean_biom = sum(mean_biom),
-    sd_biom = sqrt(sum(sd_biom^2)),
-    measure = as.factor("excr_uneat")
-  ) %>% 
-  pivot_wider(
-    names_from = feed, names_sep = ".", 
-    values_from = c(mean_biom, sd_biom), values_fn = list(mean_biom = drop_units, sd_biom = drop_units),
-    id_cols = c(country, farm_ID, measure)
-  ) %>% 
-  mutate(
-    sd_biom.MD = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.MD^2),
-    sd_biom.NI = (1/mean_biom.PD) * sqrt(sd_biom.PD^2 + sd_biom.NI^2),
-    mean_biom.MD = (mean_biom.MD-mean_biom.PD)/mean_biom.PD,
-    mean_biom.NI = (mean_biom.NI-mean_biom.PD)/mean_biom.PD
-  ) %>% 
-  select(-contains("PD")) %>% 
-  pivot_longer(
-    names_to = c(".value", "feed"), names_sep = "[.]", names_transform = list(feed = as.factor),
-    cols = contains(c("sd_biom", "mean_biom"))
-  ) %>% 
-  merge(farm_locs, by = c("country", "farm_ID")) %>% 
-  st_as_sf()
-
-# Check that it looks reasonable
-ggplot(total_mass_inputs_farm_per_biom_summed, aes(x = country, y = mean_biom, fill = feed)) +
-  geom_boxplot()
-
-qs::qsave(total_mass_inputs_farm_per_biom_summed, file.path(comparisons_path, "total_mass_inputs_farm_per_biom_summed.qs"))
-rm(total_mass_inputs_farm_per_biom_summed)
-```
-
-## Does the proportion of total inputs (mass) attributed to excretion increase or decrease with novel feeds?
-
-```{r}
-#| label: proportion-of-waste-comparison
-
-proportion_of_waste <- find_read(data_analysis_path, "total_excr_farm_summed") %>% 
-  st_drop_geometry() %>% 
-  mutate(
-    feed = factor(
-      feed, 
-      levels = c("marine_dominant", "plant_dominant", "novel_inclusive"),
-      labels = c("MD", "PD", "NI")
-    )
-  ) %>% 
-  rbind(find_read(data_analysis_path, "total_mass_inputs_farm_summed.qs")) %>% 
-  mutate(
-    measure = factor(
-      measure, 
-      levels = c("total_excr_stat", "excr_uneat"),
-      labels = c("excr", "waste")
-      )
-  ) %>% 
-  pivot_wider(
-    names_from = measure,
-    values_from = c(total, sd), values_fn = list(total = drop_units, sd = drop_units),
-    id_cols = c(country, farm_ID, feed, days)
-  ) %>% 
-  mutate(
-    total = total_excr/total_waste,
-    sd = (total_excr/total_waste) * sqrt((sd_waste/total_waste)^2 + (sd_excr/total_excr)^2)
-  ) %>% 
-  select(-contains(c("waste", "excr")))
-
-# Check that it looks reasonable
-ggplot(proportion_of_waste, aes(x = country, y = total, fill = feed)) +
-  geom_boxplot()
-
-qs::qsave(proportion_of_waste, file.path(comparisons_path, "excr_proportion_of_waste.qs"))
-rm(proportion_of_waste)
-```
-
 ## Does total inputs (mass) of each macronutrient increase or decrease with novel feeds?
 
-```{r}
+```{r, eval=F}
 #| label: PLC-mass-inputs-comparison
@@
 
-```{r}
+```{r, eval=F}
 #| label: macronutrient-proportion-comparison
@@
 
-```{r}
+```{r, eval=F}
 #| label: uneaten-feed-N-comparison
@@
 
-```{r}
+```{r, eval=F}
 #| label: excreted-N-comparison
@@
 
-```{r}
+```{r, eval=F}
 #| label: total-N-comparison
@@
 
-```{r}
+```{r, eval=F}
 

### 2025-12-18 index.qmd
Updates to docs

@@
 ---
-title: "Local to Global Mariculture Modelling"
-subtitle: "Project Documentation"
-author: "Dr Tormey Reimer"
+title: "Local-to-Global Mariculture Modelling"
+subtitle: "Project Documentation - Index of files"
+author: "Tormey Reimer"
 date: today
 execute:
-  eval: true
-  echo: false
-  warning: false
-  message: false
-  cache: true # quarto render index.qmd --cache-refresh
-knitr: 
-  opts_chunk:
-    fig.align: center
-    fig.width: 8.5
-format:
-  html:
-    code-fold: true
+  eval: false
 ---

### 2025-12-19 docs-working/01_tidying_data.qmd
Documentation updates

@@
 library(qs)
-library(magrittr)
-library(purrr)
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  walk(source)
 ```
@@
 ```{r locations}
-farm_locations <- file.path(rdsi_dir, "raw_data/aquaculture-locations/all_marine_aquaculture_farms_sources_final.csv") %>% 
+farm_locations <- file.path(bigdata_path, "all_marine_aquaculture_farms_sources_final.csv") %>% 
   read.csv() %>% 
@@
 ```{r}
-nasa_dir <- "/mnt/rdsi/raw_data/NASA/GHRSST_L4_MUR_0.25_SST/"
-
 #rename the NASA files 
@@
 
-SST_files <- list.files(file.path(rdsi_dir, "raw_data/NASA/GHRSST_L4_MUR_0.25_SST"), full.names = TRUE, pattern = ".nc")
+SST_files <- file.path(bigdata_path, "NASA/GHRSST_L4_MUR_0.25_SST") %>% 
+  list.files(full.names = TRUE, pattern = ".nc")
 
@@
 ```{r}
-vuln_scores <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv")) %>% 
+vuln_scores <- file.path(bigdata_path, "butt_spp_vuln_framework-publication/_output/vuln_gapfilled_score.csv") %>% 
+  read.csv() %>% 
   select(vuln_gf_id, eutrophication_nutrient_pollution)
 
-vuln_sd <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_sd.csv")) %>% 
-  select(vuln_gf_id, eutrophication_nutrient_pollution) %>% rename(sd=eutrophication_nutrient_pollution)
+vuln_sd <- file.path(bigdata_path, "butt_spp_vuln_framework-publication/_output/vuln_gapfilled_sd.csv") %>% 
+  read.csv() %>% 
+  select(vuln_gf_id, eutrophication_nutrient_pollution) %>% 
+  rename(sd = eutrophication_nutrient_pollution)
 
-vuln_tx <- read.csv(file.path(rdsi_data_dir, "marine_spp_vulnerabilities/butt_spp_vuln_framework-publication/_output/vuln_gapfilled_tx.csv"))
+vuln_tx <- file.path(bigdata_path, "butt_spp_vuln_framework-publication/_output/vuln_gapfilled_tx.csv") %>% 
+  read.csv()
 
@@
 
-qsave(x = full_vuln_df, file = here("data/_general_data/species_layers/vulnerabilities/marine_spp_vulnerabilities_eutrophication.qs"))
+qsave(full_vuln_df, here("data/_general_data/species_layers/vulnerabilities/marine_spp_vulnerabilities_eutrophication.qs"))
 ```

### 2025-12-19 docs-working/02_extracting_production_locations.qmd
Documentation updates

@@
 date: today
-editor: source
+execute:
+  eval: false
 ---
@@
 
-FAO_shp <- read_sf(file.path(rdsi_dir, "raw_data/fao/FAO_AREAS_CWP_NOCOASTLINE")) %>% filter(F_LEVEL == "MAJOR") %>% select(F_CODE)
+FAO_shp <- file.path(bigdata_path, "fao/FAO_AREAS_CWP_NOCOASTLINE") %>% 
+  read_sf() %>% 
+  filter(F_LEVEL == "MAJOR") %>% 
+  select(F_CODE)
 
@@
 )
-
 ```
@@
 
-map_spp_to_locations_list <-
-
-  map(.x = farm_list, .f = \(this_country_region){
+map_spp_to_locations_list <- map(.x = farm_list, .f = \(this_country_region){
 
@@
   })
-
   return(farm_locations_w_model_spp)
-
 })
@@
 ```{r}
-
 farms_w_species <- qread("data/_general_data/farm_locations/locations_w_species_fao_area.qs") 
-
 harvest_sizes <- read_csv("data/_general_data/harvest_sizes/all_harvest_sizes.csv") %>% select(-harvest_size_g)
-
 production_cycle <- read_csv("data/_general_data/production_cycles/production_cycle.csv") %>% select(species, days)
-
 mortality_rates <- read_csv("data/_general_data/mortality_rates/all_mortality_rates.csv")
@@
 qsave(x = farms_w_stocking, file =  "data/_general_data/farm_locations/locations_w_species_fao_area_stocking.qs")
-
 ```

### 2025-12-19 docs-working/03_assessing_species_potential.qmd
Documentation updates

@@
 library(rnaturalearth)
-library(purrr)
 
-here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  walk(source)
 ```
@@
 ```{r}
-aquaculture_raw <- read_csv(file.path(rdsi_dir, "raw_data/fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))
+aquaculture_raw <- read_csv(file.path(bigdata_path, "fao/FAO_fishstat_2020/global_aquaculture_production_1950_2020.csv"))
 

### 2025-12-19 docs-working/04_extracting_temperatures.qmd
Moving files around
Documentation updates

--- 2025-07-08 04_extracting_temperatures.qmd
@@
 
-```{r setup}
+```{r setup, include=F, cache=F}
 #| code-summary: R setup
 
-library(magrittr)
-library(dplyr)
-library(tidyr)
-library(stringr)
-library(ggplot2)
+library(tidyverse)
 library(terra)
@@
 library(sf)
-library(purrr)
 library(furrr)
-library(targets)
 library(future)
@@
 
-source("00_dirs.R")
-
-overwrite <- F
+here("src") %>% 
+  list.files(pattern = "\\.R$", full.names = TRUE) %>% 
+  walk(source)
 ```

### 2025-12-19 docs-working/08_data_analysis.qmd
Documentation updates

@@
 
-| Stat name | Unit | Description | Level |
+| Stat name | Unit | Description |
 |-------|-----|------------------------------------|

### 2025-12-19 docs-working/07_run_atlantic_salmon_model.qmd
Minor changes to pipeline

@@
 
-Sys.setenv(TAR_PROJECT = "project_farmruns")
-farm_IDs_chunked <- tar_read(farm_IDs_chunked, script = farm_script, store = farm_store) %>% unname() %>% unlist()
-tar_load(feed_names, script = farm_script, store = farm_store)
+# Sys.setenv(TAR_PROJECT = "project_farmruns")
 
-tar_load(farm_full_results, script = farm_script, store = farm_store)
+tar_load(
+  farm_full_results,
+  store = farm_store
+)
+
 total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
-cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))
+cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily")) %>% 
+  mutate(t = as.integer(t), prod_t = as.integer(prod_t))
 
-qsave(total_ends, file.path(output_model_farm_path, "total_ends.qs"))
-qsave(cohort_results, file.path(output_model_cohort_path, "cohort_results.qs"))
-rm(farm_full_results)
+qsave(total_ends, file.path(output_path, "total_ends.qs"))
+qsave(cohort_results, file.path(output_path, "cohort_results.qs"))
+
+rm(farm_full_results, total_ends, cohort_results)
+gc()
 ```

### 2025-12-19 src/functions.R

@@ -31,6 +31,11 @@ find_read <- function(path, pattern){
   }
 }
 
+split_df <- function(df, n_rows) {
+  groups <- rep(1:ceiling(nrow(df) / n_rows), each = n_rows, length.out = nrow(df))
+  split(df, groups)
+}
+
 cite_pack <- function(package_name) {
   version <- packageVersion(package_name)
   paste0("package `", package_name, "`, version ", version, " [@", package_name, "]")

### 2025-12-19 targets/_targets_farmruns.R

@@ -30,7 +30,7 @@ output_farm_data_path <- file.path(output_path, "farm_data")
 # Globals
 farm_chunk_size <- 20
 inds_per_farm <- 1000
-farm_sample <- 500 # For only runing a subset of farms (multiples of farm_chunk_size, maximum 2720)
+farm_sample <- 1000 # For only runing a subset of farms (multiples of farm_chunk_size, maximum 2720)
 reference_feed_name <- "marine_dominant_biomar"
 
 list(
